### 2020-10-03 manuscript/main.tex
initial manuscript push

% set document class
\documentclass[a4paper,notitlepage,12pt]{article}

% load packages
\usepackage[utf8]{inputenc}
\usepackage[a4paper, margin=0.8in]{geometry}
\usepackage{authblk}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{indentfirst}
\usepackage{xr-hyper} % for cross-referencing between documents
\usepackage{hyperref}
\usepackage{apacite}
\usepackage{float}
\usepackage{amsmath}
\usepackage[flushmargin]{footmisc}
\usepackage[flushleft]{threeparttable}
\usepackage{array}
\usepackage[font=small, labelfont=it]{caption}

% specify footnote margins
\renewcommand\footnotelayout{%
  \advance\leftskip 0.7cm
  \advance\rightskip 0.7cm
 }

% specify bibliography and link style
\bibliographystyle{apacite}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    citecolor=blue
}
\renewcommand\bibliographytypesize{\small}

% specific images path relative to the main .tex file 
\graphicspath{ {./figures/} }

% specify some custom commands
\renewcommand{\baselinestretch}{1.2}
\renewcommand*{\Authsep}{, }
\renewcommand*{\Authand}{, }
\renewcommand*{\Authands}{, }
\renewcommand*{\Affilfont}{\normalsize}

% set up the author block
\setlength{\affilsep}{2em}   % set the space between author and affiliation
\author[1]{Samuel Zorowitz}
\author[1,2]{Daniel Bennett}
\author[1,3]{Yael Niv}
\affil[1]{Princeton Neuroscience Institute, Princeton University, USA}
\affil[2]{Department of Psychiatry, Monash University, Australia}
\affil[3]{Department of Psychology, Princeton University, USA}

% specify the title
\title{Inattentive responding can induce spurious associations between task behaviour and symptom measures}

% turn date off
\date{}

% Define paragraph formatting
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

\begin{document}

\maketitle

% make abstract
\abstract{Abstract}

% page break before introduction
\clearpage

% Define paragraph formatting
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

\section{Introduction}

In recent years, online labor markets (e.g. Amazon Mechanical Turk, Prolific, Crowdflower) have become increasingly popular as a source of research participants in the behavioral sciences \cite{stewart2017crowdsourcing}, largely due to the ease with which these services allow for collecting large, diverse samples. Similarly, the advantages of online data collection platforms have been recognized for clinical research \cite{chandler2016conducting} and are increasingly used in studies of computational psychiatry. Here they are offer additional advantages. The ability to collect large samples facilitates transdiagnostic analysis, studying symptom co-occurrence and relation to behaviors \cite{gillan2016taking, rutledge2019machine}. Online platforms makes it easier to recruit and study otherwise difficult-to-reach populations \cite{strickland2019use}. Online platforms also make re-recruitment easier, making it possible to validate the reliability of measurements tools \cite{enkavi2019large} and possibly study longitudinal processes over long timescales \cite{kothe2019retention}. Some examples here: gillan

Paragraph 2: These advantages not without costs: online means giving up the control of the laboratory. Participants may be distracted, multi-tasking, and with different incentives than usual in-lab participants. Fortunately, many previous studies have found data quality on online crowdsourcing websites not altogether different or worse than in-lab samples. This isn't to say bad data doesn't exist: estimates vary, but non-negligible data bad and new issues arise. For the most part, however, noise has been treated as unsystematic something that can be overcome with increased samples  \cite{gillan2016taking, chandler2020participant}.

> Although typical undergraduate subject populations are often motivated to participate in studies because of an interest in psychology, MTurk participants are unsupervised and anonymous, complete surveys in unknown locations, and are motivated by financial incentives

We specifically want to draw attention to a less appreciated fact: when traits are rare, such as in psychiatry, careless responding is more likely to manifest as symptom endorsement \cite{chandler2020participant, ophir2020turker}. Rather than mask true correlations, this can induce spurious correlations in data. This effect is well documented in personality psychology, where the presence of careless respondents can induce correlations between questionnaires and bias estimated factors in factor analysis. To our knowledge, however, discussion of this point has been limited to associations between self-report measures and not with respect to behavioral experiments. There is no reason to expect, however, that this result should be limited to those domains and may similarly be an issue for computational psychiatry.

Paragraph 4: not enough to speculate -- must demonstrate this is an issue. what we gonna show: (a) the minority of individuals screen. (b) behavior and survey screens may not correlate. (c) these correlations do arise. We close with some recommendations based on simulations.

\section{Core Problem}

In this first section, we illustrate the core problem: namely, how C/IE responding can give rise to spurious correlations between measures of task behavior and self-reported symptoms. For our example, we have in mind a typical use case in computational psychiatry: a researcher runs a study involving a behavioral task and at least one self-report symptom measure. Specifically, we have in mind tasks where the primary outcome measure is an index of decision making. That is, we are primarily concerned with tasks where on each trial a participant must decide how to respond to some stimuli. This decision may be what is the appropriate response given some rule (e.g. color-naming in the Stroop task), which stimulus is greater (e.g. dot-motion in perceptual decision making, or which stimulus is the most valuable (e.g. decisions from description, bandit tasks). Importantly, what all of these tasks share is an explicit or implicit rule for accuracy. That is, we are not measuring idiosyncratic preferences: attentive participants should respond in a coherent and consistent fashion (e.g. prefer more valuable to less valuable).

To illustrate how C/IE responding can give rise to spurious correlations in these paradigms, we introduce a simple computational framework relating responding on behavioral and self-report measures. Beginning first with task behavior, we assume that a decision, $y_{i,j}$, with $k$ response levels made by participant $i$ on trial $j$ is governed by:

\begin{equation}
    p(y_{i,j} = k \mid \psi_i, \pi_i) = (1-\pi)\text{Cog}(\psi_i) + \frac{\pi}{k}
\end{equation}

Here, $\psi_i$ is the set of latent parameters of a cognitive model governing behavior on a particular task. For example, $\psi_i$ may correspond to the parameters of a drift diffusion model or Q-learning model. More importantly, $\pi_i$ is a lapse rate which controls the degree of C/IE responding. Specifically, a participant always responds consistent with the internal model when $\pi=0$, but only responds randomly when $\pi=1$. We note that this definition assumes that C/IE responding manifests only as statistically random responding. As will be discussed below, we believe this is an overly simplistic assumption, as there exist a great multitude of low-effort heuristic strategies beyond random responding a participant may engage in. We make this assumption in this section strictly for illustrative purposes.

Turning now to self-report behavior, we assume that a response, $y$, with $k$ response levels made by participant $i$ to item $j$ is governed by:

\begin{equation}
    p(y_{i,j} = k \mid \phi_i, \pi_i) = (1-\pi)\text{IRT}(\phi_i) + \frac{\pi}{k}
\end{equation}

Here, $\phi_i$ is a set of latent item response parameters governing a participant's pattern of endorsement (for a review see Burkner). Again, $\pi_i$ is a lapse rate. As above, we assume that C/IE responding manifests as statistically random responding (i.e. equal likelihood of endorsing all response levels). Of course, there exist alternate forms of C/IE responding on self-report measures (e.g. straight-lining, zig-zagging). To reiterate, we make this assumption for strictly illustrative purposes.

Crucially, we assume that the degree of C/IE responding by modality is related across individuals. That is, we assume a correlation between $\pi$ and $\pi$ such that participants more likely to engage in C/IE responding on one measure is also more likely to engage in C/IE responding on the other. As will be discussed below, we do not assume that the degree of C/IE responding for an individual is identical across modalities (i.e. $\pi \neq \pi$). Participants may be more (or less) motivated to respond carefully on certain modalities for a variety of reasons (e.g. task difficulty, participant abilities, monetary incentives). Regardless, we assume there exists some shared variance in C/IE responding by modality across individuals.

To illustrate how spurious correlations may arise, we used this framework to simulate four datasets under varying conditions (Figure 1). In each dataset, we simulated 1000 participants responses to both a behavioral and self-report measure. Crucially, we manipulated two key variables: the fraction of C/IE respondents and the skewness of the distribution of self-report scores. Specifically, we manipulated whether the fraction of C/IE respondents was 0\% (Figures 1a, 1c) or 15\% (Figures 1b, 1d), a rate similar to what has been reported in the literature. We independently manipulated whether the skew of the self-report total scores was symmetric (Figures 1a, 1b) or right-skewed (Figures 1c, 1d). We then computed Spearman correlations between behavior and self-report for 1000 random subsamples of 100 participants.

\begin{figure}[!b]
    \centering
    \includegraphics[scale=0.6]{figures/figure_01.png}
    \caption{Caption}
    \label{fig:simulations}
\end{figure}

We draw your attention to two key results of this simulation. First, under a model of statistical randomness, C/IE respondents will fall to the center of the range of total scores. This follows naturally from the definition of statistically random responding (i.e. the mean of a uniform distribution is the center of its range). As such when the distribution of total scores is symmetric, C/IE respondents will resemble the modal participant. However, when the distribution of total scores is asymmetric, C/IE respondents will show elevated (attenuated) total scores when the distribution is right-skewed (left-skewed). That is, for skewed symptom measures where higher scores indicate greater pathology, C/IE respondents will falsely appear as endorsing higher levels of illness.

Most importantly, this has consequences for the experimenter correlating behavior and self-report measures. In the absence of C/IE respondents, regardless of total score distribution, behavior-symptom correlations are centered at zero with false positive rates around the 5\% level (Figures 1a, 1c). Similarly, the presence of C/IE respondents does not impact behavior-symptom correlations when the total score distribution is symmetric (Figure 1b). When the total score distribution is asymmetric, however, the presence of C/IE respondents means the distribution of behavior-symptom correlations is no longer centered at zero and the false positive rate is substantially elevated (Figure 1d). In other words, the combination of asymmetric total scores and C/IE responding yields favorable conditions for spurious behavioral-symptom correlations. Crucially, this is precisely the sort of condition we find ourselves in psychiatry, where many symptoms of interest have low overall endorsement in the general population.

Thus, we have shown how spurious behavior-symptom correlations may arise in presence of C/IE respondents. However, as panel 1c suggests, removing these participants should prevent or decrease the likelihood of spurious correlations. Thus the question next turns to how common is this scenario.

Before moving on, we wish to address one portion of our assumptions: namely statistically random responding for self-report measures. Random responding in one heuristic pattern, but there are others. For example, C/IE participants also show straight-lining (i.e. choosing the same response level for most or all items) and zig-zagging (i.e. choosing adjacent response levels of successive items). We note that these heuristic strategies will also give rise to these problems in aggregate. By definition, zig-zagging will yield approximately uniform response patterns. In aggregate, a collection of straight-liners choosing different response levels will form a uniform distribution in aggregate that will also yield similar patterns of correlations.

[supplementary figure?]

\section{State of screening practices}

As demonstrated in the preceding section, the presence of C/IE respondents can yield spurious correlations between measures of task and self-report behaviors in scenarios common to psychiatry. As such, it is imperative for researchers to detect and remove these participants prior to analysis. This raises two questions: (1) do researchers screen participants of online studies for C/IE responding, and if so (2) what how do they do so? The answers to these questions should, in part, tell us how worried we need to be about the above pattern of results.

In this section, we conduct a cursory review of the literature to evaluate the state of screening practices in online studies of psychiatric behavior. Studies were identified through a set of searches in Google Scholar entailing permutations of keywords related to online labor platforms (e.g. "online", "mechanical turk", "prolific"), psychiatry, and behavioral tasks. Studies were included in the review insofar that they met the following criteria: (a) recruited participants online, (b) collected responses on at least one self-report symptom measure, and (c) collected responses to at least one experimental task. Using these criteria, we identified 49 studies suitable for inclusion (the complete list of studies and their associated search queries are included in the supplement). Next, we reviewed the methods of each study to identify whether (a) participants were excluded (or adjusted for) based on task and/or self-report behaviors and if so (b) what criteria were used. We note that the goal of this review was not to be exhaustive, but rather to provide a representative overview of the practices common in this subfield.

Summary statistics about the prevalence and types of screening are provided in Table 1. Turning first to exclusion criteria based on task behavior, the majority of studies in our sample (39/48; 81\%) used at least approach to identify C/IE respondents in task behavior. Of those studies, just over half used only one form of evaluation. Unsurprisingly, there was considerable heterogeneity in the methods used to screen task behavior across studies. Most common was screening based on performance accuracy (numbers), or responding above chance levels. Almost as common was screening based on response variability (numbers), or using. Less common methods were screening based on response times and failed comprehension checks. Briefly, we note that many studies excluded based on missing data but we do not consider that here as that many not reflect C/IE responding, but instead technical issues. In sum, the majority of studies utilized at least one method for screening behavioral data (though the method(s) used varied considerably across studies).

By comparison, only the minority of studies performed at least one form of screening for C/IE responding in self-report data. The majority of studies performing self-report screening employed only one method. By far, the most common method was the use of attention checks. Attention checks can be subdivided into different categories. For example, instructed items explicitly tell a participant which response option to choose; those failing to do so are presumably C/IE respondents. In contrast, infrequency items are those which have only one or a small set of valid responses. Most attention checks fell into the former category; only one study in sample reported using infrequency items. Most other studies using attention checks did not disclose the check they used; though there are valid reasons for doing so, this prevents us from knowing their methods. Far less were so-called unobtrusive or statistical methods. Only a handful of studies reported using screening based on personal consistency with repeat items, entropy, or outlier detection.

To summarize whereas screening for C/IE responding in task behavior is ostensibly the norm, screening self-report behavior is far less prevalent. Indeed, whereas approximately 80\% of studies used at least one method for screening behavioral data, fewer than 40\% of studies did the same for self-report data. One possible explanation for this pattern of results is that researchers assume that screening methods for task and self-report behaviors are equally sensitive to C/IE responding. That is, researchers may believe that both types of screening measures will detect the same participants and are as such redundant. If this is the case, to our knowledge this assumption has yet to be empirically demonstrated. Thus, we ran an experiment blah blah blah.

Before moving on, we pause to discuss two important pattern of results from this literature review. First, we found that the majority of studies used only one single method to detect C/IE responding. This is concerning for several reasons. First, multiple empirical investigations of self-report screening metrics have demonstrated that different metrics are sensitive to different heuristric strategies and employing only one may mean missing other bad data. Though this has been less researched in the. context of task behavior, it is likely no less true. For example, WSLS and accuracy. Similarly, metrics are a SNR issue and multiple metrics allow for better resolution of true and false positives.

Second, and more controversially, that the majroity of studies using instructed items is ocncerning. Less effective on MTurk. Empirical evidence that folks know to look for them. Popularly discussed on formums (link 1, linke 2). In our studies, have found less sensitive measure than others. We encourage researchers to swap or at least use multiple.

\begin{tabular}{ |p{3cm}||p{3cm}|p{3cm}|p{3cm}|  }
 \hline
 \multicolumn{2}{|c|}{Behavioral Screening} &
 \multicolumn{2}{|c|}{Self-Report Screening} \\
 \hline
 Accuracy & 18 (37\%) & Attention Check & 17 (35\%) \\
 Variability & 15 (31\%) & Instructed & 10 (20\%) \\
 Response Time & 7 (14\%) & Unspecified &  5 (10\%) \\
 Comprehension & 5 (10\%) & Unobtrusive &  4 (8\%) \\
 Other & 16 (33\%) & &  \\
 \hline
 At least 1 & 39 (80\%) & At least 1 & 19 (39\%) \\
 \hline
\end{tabular}

\section{Methods}

\subsection{Participants}

405 participants were recruited online to participate in a behavioral experiment in May, 2020. Approximately half of participants were recruited from Amazon Mechanical Turk (N=204), whereas the remaining half were recruited from Prolific (N=200). All participants consented to participate. Participants demographics are reported in Table S1. Importantly N participants admitted to participating twice: once on MTurk and once on Prolific, and were removed from all subsequent analyses.  All participants were paid at a rate of \$12/hr plus a performance bonus of up to blah (average rate: blah). All things approved by Princeton.

400 participants agreed to participate online during month of May 2020. 200 participants from MTurk. 200 participants from Prolific. All participants consented to participate. All participants were paid at a rate of \$12/hr plus a performance bonus of up to blah (average rate: blah). All things approved by Princeton IRB.

Importantly, participants from MTurk were recruited via CloudResearch (formally TurkPrime). Describe methods. Similarly describe methods for Prolific. Address MTurk screening requirement.

\subsection{Symptom Measures}

After consenting but prior to start of experiment, participants completed four measures: (1) GAD-7, (2) 7U7D, (3) BIS-BAS, (4) SHAPS. Importantly, these four were selected due to modal responding (two right-skewed, one symmetric, one left-skewed).

\textbf{GAD-7}

\textbf{7u7d}

\textbf{BIS/BAS}

\textbf{SHAPS}

Describe infrequency items. Describe recommendations, describe cat and mouse situation. Provide one example. All previously vetted.

\subsection{Reversal Learning Task}

Participants completed a 3-arm probabilistic learning task, similar to [citations]. On every trial, participants were able to choose one of three options. On any trial, there was always one best option, rewarding with 80\% probability; remaining arms rewarded with 20\% probability. Crucially, every 15 trials the contingencies switched such that one of the two suboptimal arms became optimal. Participants completed 90 total trials. Decision phase 2000ms, outcome phase 1000ms. The total experiment lasted 8 minutes.

The cover story was fishing. Three beaches, trying to catch the most fish. Participants explicitly told some beaches better than others, and that the best beach may change over time. Participants had to answer four comprehension check questions: [list questions]. Participants had to complete all comprehension checks to continue, but were never excluded (similar to Gillan). Note that this may have caused attrition.

\subsection{Survey Analysis}

\textbf{Infrequency fail}

\textbf{Entropy}

\textbf{Reliability}

\textbf{Mahalanobis D}

\textbf{Reading Times}

\subsection{Behavior Analysis}

\section{Results}

\subsection{Description}

What participant metadata to include? Percentage of overlap between MTurk and Prolific?

Description of infrequency item fails. Probably want to describe more fails on MTurk than Prolific.

\subsection{Agreement of screening metrics}

Paragraph 1: First we compare metrics based on Spearman correlation.

Paragraph 2: Second we compare metrics based on dice coefficient.

Paragraph 3: In sum, it seems to be that behavior and survey metrics may not always agree. That is, screening on behavior alone is not guaranteed inattentive survey responders. What are the consequences?

\subsection{Correlation Analysis}

\section{Simulation Results / Recommendations}

\section{Discussion}

Topic XX: Continuum of human effort

Topic XX: not a problem specific to online studies, but probably worse there due to lack of monitoring and different incentives.

Topic XX: how many to expect across platforms and by method. mturk vs. prolific differences. cat and mouse problems.

Topic XX: incentives for performance in online tasks

Topic XX: Accidentally screening out participants of interest

\section{Supplement}

\bibliography{main}

\end{document}

### 2020-10-03 data/__main__.py
data reorganization

@@ -1,0 +1,124 @@
+import os, json
+import numpy as np
+from os.path import dirname, join
+from pandas import DataFrame, concat
+ROOT_DIR = dirname(os.path.realpath(__file__))
+MTURK_DIR = os.path.join(ROOT_DIR, 'mturk')
+PROLIFIC_DIR = os.path.join(ROOT_DIR, 'prolific')
+
+#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
+### Main loop.
+#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
+
+## Preallocate space.
+METADATA = []
+SURVEYS = []
+DATA = []
+
+## Locate files.
+files = [os.path.join(ROOT_DIR,'mturk',f) for f in os.listdir(join(ROOT_DIR, 'mturk')) if f.endswith('json')] +\
+        [os.path.join(ROOT_DIR,'prolific',f) for f in os.listdir(join(ROOT_DIR, 'prolific')) if f.endswith('json')]
+files = sorted(files)
+
+for f in files:
+    
+    #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
+    ### Load JSON file.
+    #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
+    
+    ## Load file.
+    platform, subject = f.split(os.sep)[-2:]
+    subject = subject.replace('.json','')
+    
+    with open(f, 'r') as f:
+        JSON = json.load(f)
+        
+    #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
+    ### Assemble metadata.
+    #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
+    
+    ## Error-catching: exclude incomplete datasets.
+    try: 
+        demo, = [dd for dd in JSON if dd['trial_type'] == 'survey-demo']
+        comp = len([dd for dd in JSON if dd['trial_type'] == 'three-arm-comprehension'])
+    except ValueError:
+        print(f'Skipping {platform} {subject}')
+        continue
+    
+    ## Initialize dictionary.
+    total_time = np.round(JSON[-1]['time_elapsed'] * 1e-3, 0)
+    interactions = len(eval(JSON[-1]['interactions']))
[…]

### 2020-10-03 data/mturk/collate_data.py

@@ -1,121 +1,0 @@
-import os, json
-import numpy as np
-from os.path import dirname
-from pandas import DataFrame, concat
-ROOT_DIR = dirname(os.path.realpath(__file__))
-DATA_DIR = os.path.join(ROOT_DIR, 'data')
-RAW_DIR = os.path.join(ROOT_DIR, 'raw')
-
-#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
-### Main loop.
-#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
-
-## Locate files.
-files = sorted([f for f in os.listdir(RAW_DIR) if f.endswith('json')])
-
-## Preallocate space.
-METADATA = []
-SURVEYS = []
-DATA = []
-
-for f in files:
-    
-    ## Load file.
-    subject, = f.replace('.json','').split('_')
-    
-    with open(os.path.join(RAW_DIR, f), 'r') as f:
-        JSON = json.load(f)
-        
-    #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
-    ### Assemble behavioral data.
-    #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
-    
-    ## Assemble behavioral data.
-    data = DataFrame([dd for dd in JSON if dd['trial_type'] == 'three-arm-trial'])
-    n_missing = data.missing.sum()
-    data = data.query('missing==False')
-        
-    ## Error-catching: exclude incomplete datasets.
-    if data.shape[0] < 90: 
-        print(f'Skipping {subject}')
-        continue
-        
-    ## Define columns of interest.
-    cols = ['trial','correct','choice','key','rt','accuracy','outcome']
-    
-    ## Limit to columns of interest.
-    data = data[cols]
-    
-    ## Reformat columns.
-    data['rt'] = np.where(data['rt'] < 0, np.nan, data['rt'] * 1e-3).round(3)
-    
-    ## Insert subject ID. Append.
-    data.insert(0,'subject',subject)
-    DATA.append(data)    
-    
-    #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
-    ### Assemble metadata.
-    #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
-    
-    ## Gather surveys.
[…]

### 2020-10-03 data/prolific/collate_data.py

@@ -1,121 +1,0 @@
-import os, json
-import numpy as np
-from os.path import dirname
-from pandas import DataFrame, concat
-ROOT_DIR = dirname(os.path.realpath(__file__))
-DATA_DIR = os.path.join(ROOT_DIR, 'data')
-RAW_DIR = os.path.join(ROOT_DIR, 'raw')
-
-#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
-### Main loop.
-#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
-
-## Locate files.
-files = sorted([f for f in os.listdir(RAW_DIR) if f.endswith('json')])
-
-## Preallocate space.
-METADATA = []
-SURVEYS = []
-DATA = []
-
-for f in files:
-    
-    ## Load file.
-    subject, = f.replace('.json','').split('_')
-    
-    with open(os.path.join(RAW_DIR, f), 'r') as f:
-        JSON = json.load(f)
-        
-    #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
-    ### Assemble behavioral data.
-    #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
-    
-    ## Assemble behavioral data.
-    data = DataFrame([dd for dd in JSON if dd['trial_type'] == 'three-arm-trial'])
-    n_missing = data.missing.sum()
-    data = data.query('missing==False')
-        
-    ## Error-catching: exclude incomplete datasets.
-    if data.shape[0] < 90: 
-        print(f'Skipping {subject}')
-        continue
-        
-    ## Define columns of interest.
-    cols = ['trial','correct','choice','key','rt','accuracy','outcome']
-    
-    ## Limit to columns of interest.
-    data = data[cols]
-    
-    ## Reformat columns.
-    data['rt'] = np.where(data['rt'] < 0, np.nan, data['rt'] * 1e-3).round(3)
-    
-    ## Insert subject ID. Append.
-    data.insert(0,'subject',subject)
-    DATA.append(data)    
-    
-    #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
-    ### Assemble metadata.
-    #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
-    
-    ## Gather surveys.
[…]

### 2020-10-03 data/__main__.py
add demographics table

@@ -118,6 +118,11 @@ METADATA = DataFrame(METADATA).sort_values(['platform','subject'])
 SURVEYS = DataFrame(SURVEYS).sort_values(['platform','subject'])
 DATA = concat(DATA).sort_values(['platform','subject','trial'])
 
+## Update non-overlapping columns.
+METADATA.insert(11, 'other-platform', np.where(METADATA['prolific'].isnull(), METADATA['mturk'], METADATA['prolific']))
+METADATA.insert(12, 'prev-complete', np.where(METADATA['prolific-this-study'].isnull(), METADATA['mturk-this-study'], METADATA['prolific-this-study']))
+METADATA = METADATA.drop(columns=['prolific','prolific-this-study','mturk','mturk-this-study'])
+
 ## Save.
 METADATA.to_csv(os.path.join(ROOT_DIR, 'metadata.csv'), index=False)
 SURVEYS.to_csv(os.path.join(ROOT_DIR, 'surveys.csv'), index=False)

### 2020-10-27 analysis/scripts/fit_regression_mcmc.py
softmax regression

@@ -1,0 +1,136 @@
+import h5py, os, pystan
+import numpy as np
+from os.path import dirname
+from pandas import DataFrame, read_csv
+from scipy.stats import norm
+from stantools.io import load_model
+from stantools.model import waic
+from stantools.stats import phi_approx
+ROOT_DIR = dirname(dirname(os.path.realpath(__file__)))
+
+#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
+### Define parameters.
+#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
+
+## I/O parameters.
+stan_model = 'softmax_regression'
+
+## Sampling parameters.
+samples = 2000
+warmup = 1500
+chains = 4
+thin = 1
+n_jobs = 4
+
+#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
+### Load and prepare data.
+#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
+
+## Load data.
+data = read_csv(os.path.join(ROOT_DIR, 'data', 'data.csv'))
+
+## Restrict participants.
+reject = read_csv(os.path.join(ROOT_DIR, 'data', 'reject.csv'))
+data = data[data.subject.isin(reject.subject)].reset_index(drop=True)
+
+## Define reject index.
+reject_ix = np.where(reject.infreq > 0, 1, 0)
+
+#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
+### Assemble data for Stan.
+#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
+
+## Define metadata.
+N = data.subject.nunique()
+K = data.choice.nunique()
+T = data.trial.nunique()
+
+## Define convenience function.
+f = lambda x: np.roll(x, 1)
+
+## Define previous choice.
+data['prev_choice'] = data.groupby(['platform','subject']).choice.transform(f)
+
+## Main loop.
+X = []
+for k in range(3):
+
+    ## Iteratively construct lags.
+    for i in range(5):
+
+        ## First lag.
+        if not i:
+
+            ## Initialize previous reward kernel.
+            data[f'x{i+1}'] = data.groupby(['platform','subject']).outcome.transform(f)
[…]

### 2020-10-28 manuscripts/main.tex
add demographics table
progress: reorganization, regression results, manuscript updates

--- 2020-10-03 manuscript/main.tex
@@
 \usepackage[font=small, labelfont=it]{caption}
+\usepackage{booktabs} % for pretty tables
 
@@
 
-\section{Introduction}
+\section{Main}
 
-In recent years, online labor markets (e.g.
-Amazon Mechanical Turk, Prolific, Crowdflower) have become increasingly popular as a source of research participants in the behavioral sciences \cite{stewart2017crowdsourcing}, largely due to the ease with which these services allow for collecting large, diverse samples.
-Similarly, the advantages of online data collection platforms have been recognized for clinical research \cite{chandler2016conducting} and are increasingly used in studies of computational psychiatry.
-Here they are offer additional advantages.
-The ability to collect large samples facilitates transdiagnostic analysis, studying symptom co-occurrence and relation to behaviors \cite{gillan2016taking, rutledge2019machine}.
-Online platforms makes it easier to recruit and study otherwise difficult-to-reach populations \cite{strickland2019use}.
-Online platforms also make re-recruitment easier, making it possible to validate the reliability of measurements tools \cite{enkavi2019large} and possibly study longitudinal processes over long timescales \cite{kothe2019retention}.
-Some examples here: gillan
+Paragraph 1: Rise of online studies. Utility for clinical research. Need to define TASK somewhere here.
 
-Paragraph 2: These advantages not without costs: online means giving up the control of the laboratory.
-Participants may be distracted, multi-tasking, and with different incentives than usual in-lab participants.
-Fortunately, many previous studies have found data quality on online crowdsourcing websites not altogether different or worse than in-lab samples.
-This isn't to say bad data doesn't exist: estimates vary, but non-negligible data bad and new issues arise.
-For the most part, however, noise has been treated as unsystematic something that can be overcome with increased samples  \cite{gillan2016taking, chandler2020participant}.
+Paragraph 2: Drawbacks to online studies. Noise. Data quality overview. Focus on unsystematic noise.
 
-> Although typical undergraduate subject populations are often motivated to participate in studies because of an interest in psychology, MTurk participants are unsupervised and anonymous, complete surveys in unknown locations, and are motivated by financial incentives
+Paragraph 3: Noise is not systematic. As has been pointed out, careless responding can overinflate prevalence of symptoms and can yield spurious correlations. OR Need to define TASK somewhere here.
 
-We specifically want to draw attention to a less appreciated fact: when traits are rare, such as in psychiatry, careless responding is more likely to manifest as symptom endorsement \cite{chandler2020participant, ophir2020turker}.
-Rather than mask true correlations, this can induce spurious correlations in data.
-This effect is well documented in personality psychology, where the presence of careless respondents can induce correlations between questionnaires and bias estimated factors in factor analysis.
-To our knowledge, however, discussion of this point has been limited to associations between self-report measures and not with respect to behavioral experiments.
-There is no reason to expect, however, that this result should be limited to those domains and may similarly be an issue for computational psychiatry.
+Paragraph 4: Not clear the extent to which this is an issue.
+For example, if screening in both types of data, might be not an issue.
+Even without screening, behavioral screening might be enough.
+Finally, behavior is complex and might not show up.
 
-Paragraph 4: not enough to speculate -- must demonstrate this is an issue.
-what we gonna show: (a) the minority of individuals screen.
-(b) behavior and survey screens may not correlate.
-(c) these correlations do arise.
-We close with some recommendations based on simulations.
-
-\section{Core Problem}
-
-In this first section, we illustrate the core problem: namely, how C/IE responding can give rise to spurious correlations between measures of task behavior and self-reported symptoms.
-For our example, we have in mind a typical use case in computational psychiatry: a researcher runs a study involving a behavioral task and at least one self-report symptom measure.
-Specifically, we have in mind tasks where the primary outcome measure is an index of decision making.
-That is, we are primarily concerned with tasks where on each trial a participant must decide how to respond to some stimuli.
-This decision may be what is the appropriate response given some rule (e.g.
-color-naming in the Stroop task), which stimulus is greater (e.g.
-dot-motion in perceptual decision making, or which stimulus is the most valuable (e.g.
-decisions from description, bandit tasks).
-Importantly, what all of these tasks share is an explicit or implicit rule for accuracy.
-That is, we are not measuring idiosyncratic preferences: attentive participants should respond in a coherent and consistent fashion (e.g.
-prefer more valuable to less valuable).
-
-To illustrate how C/IE responding can give rise to spurious correlations in these paradigms, we introduce a simple computational framework relating responding on behavioral and self-report measures.
-Beginning first with task behavior, we assume that a decision, $y_{i,j}$, with $k$ response levels made by participant $i$ on trial $j$ is governed by:
-
-\begin{equation}
-    p(y_{i,j} = k \mid \psi_i, \pi_i) = (1-\pi)\text{Cog}(\psi_i) + \frac{\pi}{k}
-\end{equation}
-
-Here, $\psi_i$ is the set of latent parameters of a cognitive model governing behavior on a particular task.
-For example, $\psi_i$ may correspond to the parameters of a drift diffusion model or Q-learning model.
-More importantly, $\pi_i$ is a lapse rate which controls the degree of C/IE responding.
-Specifically, a participant always responds consistent with the internal model when $\pi=0$, but only responds randomly when $\pi=1$.
-We note that this definition assumes that C/IE responding manifests only as statistically random responding.
-As will be discussed below, we believe this is an overly simplistic assumption, as there exist a great multitude of low-effort heuristic strategies beyond random responding a participant may engage in.
-We make this assumption in this section strictly for illustrative purposes.
-
-Turning now to self-report behavior, we assume that a response, $y$, with $k$ response levels made by participant $i$ to item $j$ is governed by:
-
-\begin{equation}
-    p(y_{i,j} = k \mid \phi_i, \pi_i) = (1-\pi)\text{IRT}(\phi_i) + \frac{\pi}{k}
-\end{equation}
-
-Here, $\phi_i$ is a set of latent item response parameters governing a participant's pattern of endorsement (for a review see Burkner).
-Again, $\pi_i$ is a lapse rate.
-As above, we assume that C/IE responding manifests as statistically random responding (i.e.
-equal likelihood of endorsing all response levels).
-Of course, there exist alternate forms of C/IE responding on self-report measures (e.g.
-straight-lining, zig-zagging).
-To reiterate, we make this assumption for strictly illustrative purposes.
-
-Crucially, we assume that the degree of C/IE responding by modality is related across individuals.
-That is, we assume a correlation between $\pi$ and $\pi$ such that participants more likely to engage in C/IE responding on one measure is also more likely to engage in C/IE responding on the other.
-As will be discussed below, we do not assume that the degree of C/IE responding for an individual is identical across modalities (i.e.
-$\pi \neq \pi$).
-Participants may be more (or less) motivated to respond carefully on certain modalities for a variety of reasons (e.g.
-task difficulty, participant abilities, monetary incentives).
-Regardless, we assume there exists some shared variance in C/IE responding by modality across individuals.
-
-To illustrate how spurious correlations may arise, we used this framework to simulate four datasets under varying conditions (Figure 1).
-In each dataset, we simulated 1000 participants responses to both a behavioral and self-report measure.
-Crucially, we manipulated two key variables: the fraction of C/IE respondents and the skewness of the distribution of self-report scores.
-Specifically, we manipulated whether the fraction of C/IE respondents was 0\% (Figures 1a, 1c) or 15\% (Figures 1b, 1d), a rate similar to what has been reported in the literature.
-We independently manipulated whether the skew of the self-report total scores was symmetric (Figures 1a, 1b) or right-skewed (Figures 1c, 1d).
-We then computed Spearman correlations between behavior and self-report for 1000 random subsamples of 100 participants.
-
-\begin{figure}[!b]
-    \centering
-    \includegraphics[scale=0.6]{figures/figure_01.png}
-    \caption{Caption}
-    \label{fig:simulations}
-\end{figure}
-
-We draw your attention to two key results of this simulation.
-First, under a model of statistical randomness, C/IE respondents will fall to the center of the range of total scores.
-This follows naturally from the definition of statistically random responding (i.e.
-the mean of a uniform distribution is the center of its range).
-As such when the distribution of total scores is symmetric, C/IE respondents will resemble the modal participant.
-However, when the distribution of total scores is asymmetric, C/IE respondents will show elevated (attenuated) total scores when the distribution is right-skewed (left-skewed).
-That is, for skewed symptom measures where higher scores indicate greater pathology, C/IE respondents will falsely appear as endorsing higher levels of illness.
-
-Most importantly, this has consequences for the experimenter correlating behavior and self-report measures.
-In the absence of C/IE respondents, regardless of total score distribution, behavior-symptom correlations are centered at zero with false positive rates around the 5\% level (Figures 1a, 1c).
-Similarly, the presence of C/IE respondents does not impact behavior-symptom correlations when the total score distribution is symmetric (Figure 1b).
-When the total score distribution is asymmetric, however, the presence of C/IE respondents means the distribution of behavior-symptom correlations is no longer centered at zero and the false positive rate is substantially elevated (Figure 1d).
-In other words, the combination of asymmetric total scores and C/IE responding yields favorable conditions for spurious behavioral-symptom correlations.
-Crucially, this is precisely the sort of condition we find ourselves in psychiatry, where many symptoms of interest have low overall endorsement in the general population.
-
-Thus, we have shown how spurious behavior-symptom correlations may arise in presence of C/IE respondents.
-However, as panel 1c suggests, removing these participants should prevent or decrease the likelihood of spurious correlations.
-Thus the question next turns to how common is this scenario.
-
-Before moving on, we wish to address one portion of our assumptions: namely statistically random responding for self-report measures.
-Random responding in one heuristic pattern, but there are others.
-For example, C/IE participants also show straight-lining (i.e.
-choosing the same response level for most or all items) and zig-zagging (i.e.
-choosing adjacent response levels of successive items).
-We note that these heuristic strategies will also give rise to these problems in aggregate.
-By definition, zig-zagging will yield approximately uniform response patterns.
-In aggregate, a collection of straight-liners choosing different response levels will form a uniform distribution in aggregate that will also yield similar patterns of correlations.
-
-[supplementary figure?]
-
-\section{State of screening practices}
-
-As demonstrated in the preceding section, the presence of C/IE respondents can yield spurious correlations between measures of task and self-report behaviors in scenarios common to psychiatry.
-As such, it is imperative for researchers to detect and remove these participants prior to analysis.
-This raises two questions: (1) do researchers screen participants of online studies for C/IE responding, and if so (2) what how do they do so?
-The answers to these questions should, in part, tell us how worried we need to be about the above pattern of results.
-
-In this section, we conduct a cursory review of the literature to evaluate the state of screening practices in online studies of psychiatric behavior.
-Studies were identified through a set of searches in Google Scholar entailing permutations of keywords related to online labor platforms (e.g.
-"online", "mechanical turk", "prolific"), psychiatry, and behavioral tasks.
-Studies were included in the review insofar that they met the following criteria: (a) recruited participants online, (b) collected responses on at least one self-report symptom measure, and (c) collected responses to at least one experimental task.
-Using these criteria, we identified 49 studies suitable for inclusion (the complete list of studies and their associated search queries are included in the supplement).
-Next, we reviewed the methods of each study to identify whether (a) participants were excluded (or adjusted for) based on task and/or self-report behaviors and if so (b) what criteria were used.
-We note that the goal of this review was not to be exhaustive, but rather to provide a representative overview of the practices common in this subfield.
-
-Summary statistics about the prevalence and types of screening are provided in Table 1.
-Turning first to exclusion criteria based on task behavior, the majority of studies in our sample (39/48; 81\%) used at least approach to identify C/IE respondents in task behavior.
-Of those studies, just over half used only one form of evaluation.
-Unsurprisingly, there was considerable heterogeneity in the methods used to screen task behavior across studies.
-Most common was screening based on performance accuracy (numbers), or responding above chance levels.
-Almost as common was screening based on response variability (numbers), or using.
-Less common methods were screening based on response times and failed comprehension checks.
-Briefly, we note that many studies excluded based on missing data but we do not consider that here as that many not reflect C/IE responding, but instead technical issues.
-In sum, the majority of studies utilized at least one method for screening behavioral data (though the method(s) used varied considerably across studies).
-
-By comparison, only the minority of studies performed at least one form of screening for C/IE responding in self-report data.
-The majority of studies performing self-report screening employed only one method.
-By far, the most common method was the use of attention checks.
-Attention checks can be subdivided into different categories.
-For example, instructed items explicitly tell a participant which response option to choose; those failing to do so are presumably C/IE respondents.
-In contrast, infrequency items are those which have only one or a small set of valid responses.
-Most attention checks fell into the former category; only one study in sample reported using infrequency items.
-Most other studies using attention checks did not disclose the check they used; though there are valid reasons for doing so, this prevents us from knowing their methods.
-Far less were so-called unobtrusive or statistical methods.
-Only a handful of studies reported using screening based on personal consistency with repeat items, entropy, or outlier detection.
-
-To summarize whereas screening for C/IE responding in task behavior is ostensibly the norm, screening self-report behavior is far less prevalent.
-Indeed, whereas approximately 80\% of studies used at least one method for screening behavioral data, fewer than 40\% of studies did the same for self-report data.
-One possible explanation for this pattern of results is that researchers assume that screening methods for task and self-report behaviors are equally sensitive to C/IE responding.
-That is, researchers may believe that both types of screening measures will detect the same participants and are as such redundant.
-If this is the case, to our knowledge this assumption has yet to be empirically demonstrated.
-Thus, we ran an experiment blah blah blah.
-
-Before moving on, we pause to discuss two important pattern of results from this literature review.
-First, we found that the majority of studies used only one single method to detect C/IE responding.
-This is concerning for several reasons.
-First, multiple empirical investigations of self-report screening metrics have demonstrated that different metrics are sensitive to different heuristric strategies and employing only one may mean missing other bad data.
-Though this has been less researched in the.
-context of task behavior, it is likely no less true.
-For example, WSLS and accuracy.
-Similarly, metrics are a SNR issue and multiple metrics allow for better resolution of true and false positives.
-
-Second, and more controversially, that the majroity of studies using instructed items is ocncerning.
-Less effective on MTurk.
-Empirical evidence that folks know to look for them.
-Popularly discussed on formums (link 1, linke 2).
-In our studies, have found less sensitive measure than others.
-We encourage researchers to swap or at least use multiple.
-
-\begin{tabular}{ |p{3cm}||p{3cm}|p{3cm}|p{3cm}|  }
- \hline
- \multicolumn{2}{|c|}{Behavioral Screening} &
- \multicolumn{2}{|c|}{Self-Report Screening} \\
- \hline
- Accuracy & 18 (37\%) & Attention Check & 17 (35\%) \\
- Variability & 15 (31\%) & Instructed & 10 (20\%) \\
- Response Time & 7 (14\%) & Unspecified &  5 (10\%) \\
- Comprehension & 5 (10\%) & Unobtrusive &  4 (8\%) \\
- Other & 16 (33\%) & &  \\
- \hline
- At least 1 & 39 (80\%) & At least 1 & 19 (39\%) \\
- \hline
-\end{tabular}
-
-\section{Methods}
-
-\subsection{Participants}
-
-405 participants were recruited online to participate in a behavioral experiment in May, 2020.
-Approximately half of participants were recruited from Amazon Mechanical Turk (N=204), whereas the remaining half were recruited from Prolific (N=200).
-All participants consented to participate.
-Participants demographics are reported in Table S1.
-Importantly N participants admitted to participating twice: once on MTurk and once on Prolific, and were removed from all subsequent analyses.
-All participants were paid at a rate of \$12/hr plus a performance bonus of up to blah (average rate: blah).
-All things approved by Princeton.
-
-400 participants agreed to participate online during month of May 2020.
-200 participants from MTurk.
-200 participants from Prolific.
-All participants consented to participate.
-All participants were paid at a rate of \$12/hr plus a performance bonus of up to blah (average rate: blah).
-All things approved by Princeton IRB.
-
-Importantly, participants from MTurk were recruited via CloudResearch (formally TurkPrime). Describe methods. Similarly describe methods for Prolific. Address MTurk screening requirement.
-
-\subsection{Symptom Measures}
-
-After consenting but prior to start of experiment, participants completed four measures: (1) GAD-7, (2) 7U7D, (3) BIS-BAS, (4) SHAPS.
-Importantly, these four were selected due to modal responding (two right-skewed, one symmetric, one left-skewed).
-
-\textbf{GAD-7}
-
-\textbf{7u7d}
-
-\textbf{BIS/BAS}
-
-\textbf{SHAPS}
-
-Describe infrequency items. Describe recommendations, describe cat and mouse situation. Provide one example. All previously vetted.
-
-\subsection{Reversal Learning Task}
-
-Participants completed a 3-arm probabilistic learning task, similar to [citations].
-On every trial, participants were able to choose one of three options.
-On any trial, there was always one best option, rewarding with 80\% probability; remaining arms rewarded with 20\% probability.
-Crucially, every 15 trials the contingencies switched such that one of the two suboptimal arms became optimal.
-Participants completed 90 total trials.
-Decision phase 2000ms, outcome phase 1000ms.
-The total experiment lasted 8 minutes.
-
-The cover story was fishing.
-Three beaches, trying to catch the most fish.
-Participants explicitly told some beaches better than others, and that the best beach may change over time.
-Participants had to answer four comprehension check questions: [list questions].
-Participants had to complete all comprehension checks to continue, but were never excluded (similar to Gillan).
-Note that this may have caused attrition.
-
-\subsection{Survey Analysis}
-
-\textbf{Infrequency fail}
-
-\textbf{Entropy}
-
-\textbf{Reliability}
-
-\textbf{Mahalanobis D}
-
-\textbf{Reading Times}
-
-\subsection{Behavior Analysis}
+Paragraph 5: our current results call into question.
 
@@
 
-\subsection{Description}
+\subsection{Screening for C/IE responding is common for task behavior but not for self-report behavior}
 
-What participant metadata to include? Percentage of overlap between MTurk and Prolific?
+The presence of C/IE responding in a dataset can result in spurious correlations between measures of behavior.
+As such, it is imperative for researchers to detect and remove those participants whom complete online experiments with insufficient effort.
+The extent to which experimenters evaluate the quality of both the task and self-report data they collect is unclear.
+We suspect that whereas screening of task data is standard practice, the screening of self-report data is far less prevalent in online human behavioral research.
 
-Description of infrequency item fails. Probably want to describe more fails on MTurk than Prolific.
+To provide quantitative support to this claim, we performed a cursory literature review of online human behavioral studies.
+(See Methods for details of the literature search and the list of studies included.) Briefly, we identified studies for inclusion through searches on Google Scholar using permutations of query terms related to online labor platforms, experimental paradigms, and symptom measures.
+We included studies that (a) recruited participants online, (b) measured behavior on at least one experimental task, and (c) measured behavior on at least one self-report symptom measure.
+This resulted in the inclusion of 49 studies.
+We then evaluated whether and how those studies performed task and self-report behavior screening.
+We note that this review was not meant to be systematic, but instead to provide a representative overview of the screening practices common to online behavioral studies.
 
-\subsection{Agreement of screening metrics}
+Summary statistics about the prevalence and types of screening practices are provided in Table~\ref{tab:screening}.
+Of the 49 online behavioral studies meeting inclusion criteria, roughly 80\% (39/49) used at least one approach to identify C/IE responding in task behavior.
+Of those studies, just over half relied on a single evaluative method.
+As might be expected, there was considerable heterogeneity in task behavior screening methods.
+Most common was identifying participants whose performance was indistinguishable from chance-level on some measure of accuracy.
+Almost as common was screening based on response variability, or identifying participants who predominantly responded in the same fashion (e.g.
+used only 1 key).
+Less common approaches were screening based on response times and instruction comprehension questions.
 
-Paragraph 1: First we compare metrics based on Spearman correlation.
+In contrast, only the minority of online behavioral studies in our sample used at least one approach to identify C/IE responding in self-report behavior.
+Of those studies the most common method was the use of attention checks, which operate under the assumption that certain responses are unlikely under inattentive responding.
+Attention checks can be subdivided into different categories such as instructed items, where participants are explicitly told which response to select, and infrequency items, where only one or a small set of responses are valid.
+Of those studies that specified what type of attention check was used, instructed items were the most common form of attention check.
+Only a handful of studies employed statistical or so-called unobtrusive screening methods such as outlier detection or personal consistency.
 
-Paragraph 2: Second we compare metrics based on dice coefficient.
+In sum whereas screening for C/IE responding in task behavior is ostensibly the norm for online behavioral studies, screening self-report behavior is far less prevalent.
+One possible explanation for this pattern of results is that researchers (implicitly) assume that screening both task and self-report behavior is redundant.
+That is, researchers may believe that task and self-report screening methods will identify the same participants as having exhibited C/IE responding.
+To our knowledge, however, this crucial assumption has never been empirically verified.
+In the next section, we explicitly test this hypothesis in a large sample of online participants.
 
-Paragraph 3: In sum, it seems to be that behavior and survey metrics may not always agree.
-That is, screening on behavior alone is not guaranteed inattentive survey responders.
-What are the consequences?
+\begin{table}[t]
+\centering
+\setlength{\tabcolsep}{12pt}
+\begin{tabular}{lrrrr}
+\toprule
+& \multicolumn{2}{c}{Task Screening} & \multicolumn{2}{c}{Self-Report Screening} \\
+\cmidrule(lr){2-3} \cmidrule(lr){4-5}
+Frequency & \multicolumn{2}{c}{N=39 (80\%)} & \multicolumn{2}{c}{N=19 (39\%)} \\
+\midrule
+Method & Accuracy & 18 (46\%) & Attention Check & 17 (89\%) \\
+& Variability & 15 (38\%) & Instructed & 10 (53\%) \\
+& Response Time & 7 (18\%) & Unspecified & 5 (26\%) \\
+& Comprehension & 5 (13\%) & Unobtrusive & 4 (21\%) \\
+& Other & 16 (41\%) \\
+\bottomrule
+\end{tabular}
+\caption{The prevalence and types of task and self-report behavior screening practices in a representative sample (N=49) of online behavioral studies.}
+\label{tab:screening}
+\end{table}
 
-\subsection{Correlation Analysis}
+Before continuing, we wish to briefly highlight two additional results from our literature review.
+First, we found that the majority of studies used only one single method to detect C/IE responding.
+This is worrisome from the perspective of signal detection theory.
+As has been previously reported, measures of C/IE responding have different sensitivities: some measures will identify only the worst participants, whereas others will flag many more respondents.
+As such, using only a single measure runs the risk of false positives (in the case of high sensitivity) and false negatives (in the case of low sensitivity).
+Similarly, different measures are sensitive to different \emph{types} of C/IE responding.
+Using only one measure may thus only identify a subset of C/IE respondents.
+As has been discussed elsewhere, the use of multiple measures is encouraged to more accurately and sensitively identify C/IE responding in a dataset.
 
-\section{Simulation Results / Recommendations}
+Second, we found that the majority of studies that did screen self-report data relied on instructed items.
+This is separately worrisome as a growing body of research disputes their efficacy for online studies.
+There is empirical evidence that these items are less sensitive online elsewhere.
+A quick search online reveals that instructed items are frequently discussed in forums used by workers in online labor markets.
+Most concerning, there is empirical evidence that of a subset of participants that screen for these items and respond randomly where else.
+We encourage other methods and, as above, a multitude of methods.
+
+\subsection{Task and self-report measures of C/IE responding}
+
+To measure the correspondence between measures of C/IE responding based on task and self-report behaviors, we conducted an behavioral experiment in two prominent online labor marketplaces (see Methods for complete details).
+In total, 400 participants were recruited from Amazon Mechanical Turk (N=) and Prolific (N=) to complete an online study comprised of one behavioral task and several self-report symptom measures.
+We recruited participants from both platforms in order to improve the generalizability of our findings.
+The demographics of each sample are summarized in Table XX.
+
+Participants completed a 3-arm probabilistic reversal learning bandit task.
+During the task, participants were presented with three options and could only choose one, after which they received feedback (reward or no-reward).
+Participants were instructed to choose the option that yielded reward most often, which they would learn through trial-and-error.
+Feedback was probabilistic such that the best option on a given trial returned reward on 80\% of trials and the other options only 20\%.
+Importantly, the best option changed every 15 trials.
+Participants were made explicitly aware that the best option would change over time, but they were not told when or how often this would occur.
+Participants completed 90 trials of the task (5 total reversals).
+
+Prior to the start of the behavioral experiment, participants also completed four standard self-report symptom measures: the generalized anxiety disorder scale (GAD7), the 7-up/7-down, the BIS/BAS, and the Snaith-Hamilton Pleasure Scale.
+The measures were selected to provide a range of response distributions.
+For example, the GAD-7 and 7-up/7-down are substantially asymmetric.
+
+To measure the level of correspondence between task- and self-report-based measures of C/IE responding, we computed a number of metrics from the task and self-report behavior of each subject.
+For the task behavior, we estimated the following metrics: response variability, accuracy, win-stay lose-shift, and fraction of trials with suspicious response times.
+For the self-report behavior, we estimated the following metrics: number of suspicious responses to infrequency items, inter-item standard deviation (ISD), personal reliability, Mahalanobis distance, and the per-item reading time.
+
+To provide an overall sense of the quality of the data, we first focus on the task accuracy and infrequency scores.
+Based on task accuracy, XX\% of participants were flagged as exhibiting C/IE responding.
+That is, XX\% of participants showed accuracy levels at levels indistinguishable from chance.
+In contrast, the infrequnecy items flagged XX\% of participants as exhibiting C/IE responding.
+This discrepancy between identification rates is already suggestive of differences between task and self-report screening measures.
+Interestingly, the rates of flagged participants differed by platform.
+
+Give overall rates here. Basically want to discuss: (1) different by platform, (2) different by method.
+
+Core result 1: continuous (spearman) correlaiton analysis.
+
+\subsection{}
 
@@
 
+\section{Methods}
+
 \section{Supplement}

### 2020-10-28 laverna/__init__.py

@@ -1,6 +1,0 @@
-"""laverna: code for simulating careless/inattentive behavior"""
-
-__version__ = '0.1'
-
-from .ordinal import simulate_item_response
-from . import task

### 2020-10-28 laverna/ordinal.py

@@ -1,59 +1,0 @@
-import numpy as np
-from numba import njit
-
-@njit
-def inv_logit(arr):
-    """Fast inverse logistic function."""
-    return 1. / (1. + np.exp(-arr))
-
-@njit
-def phi_approx(arr):
-    '''Elementwise fast approximation of the cumulative unit normal.'''
-    return inv_logit(0.07056 * arr ** 3 + 1.5976 * arr)
-
-def simulate_item_response(tau, mu, xi, link='probit'):
-    """Simulate ordinal responses for single item.
-    
-    Parameters
-    ----------
-    tau : array, shape (n_thresh,)
-        Ordinal thresholds.
-    mu : array, shape (n_sub,)
-        Subject latent traits.
-    xi : array, shape (n_sub,)
-        Subject lapse rates.
-    link : probit | inv_logit | function
-        Oridinal threshold function.
-        
-    Returns
-    -------
-    Y : array, shape (n_sub, n_items)
-        Ordinal responses.
-    """
-    
-    ## Ensure arrays.
-    mu = np.array(mu)
-    xi = np.array(xi)
-    
-    ## Error-catching: 
-    assert np.ndim(mu) == 1
-    assert np.ndim(xi) == 1
-    assert mu.size == xi.size
-            
-    ## Define link function.
-    if link == 'probit': link = phi_approx
-    elif link == 'inv_logit': link = inv_logit    
-        
-    ## Compute likelihood of response.
-    theta = link(np.subtract.outer(tau, mu)).T
-    theta = np.column_stack([np.zeros(mu.size), theta, np.ones(mu.size)])
-    theta = np.diff(theta)
-    
-    ## Incorporate lapse.
-    theta = (1 - xi[:,np.newaxis]) * theta + xi[:,np.newaxis] / theta.shape[1]
-    
-    ## Simulate responses.
-    f = lambda p: np.random.multinomial(1,p)
-    Y = np.apply_along_axis(f, 1, theta).argmax(axis=1)
-    
-    return Y

### 2020-10-28 laverna/task/__init__.py

@@ -1,3 +1,0 @@
-"""Simulation of task behavior."""
-
-from ._reversal import (simulate_reversal_task, ReversalTask)

### 2020-10-28 laverna/task/_reversal.py

@@ -1,144 +1,0 @@
-"""Multi-arm reversal learning task."""
-
-import numpy as np
-from numba import njit
-
-@njit
-def softmax(arr):
-    """Scale-robust softmax function"""
-    arr = np.exp(arr - np.max(arr))
-    return arr / arr.sum()
-
-
-def simulate_reversal_task(blocks, n_arms=3, p_target=0.8, p_other=0.2, size=1):
-    """Simulate games of reversal learning task.
-    
-    Parameters
-    ----------
-    blocks : array, shape (n_blocks,)
-        Array of ints, each denoting the length of a block.
-    n_arms : int
-        Number of bandit arms.
-    p_target : float in range [0-1]
-        Probability of reward for target arm.
-    p_other: float in range [0-1]
-        Probability of reward for remaining arms.
-    size: int
-        Number of games to simulate
-        
-    Returns
-    -------
-    rewards : array, shape (n_games, n_trials, n_arms)
-        Binary rewards.
-    pi : array, shape (n_games, n_blocks)
-        Optimal choice.
-    """
-    
-    ## Initialize targets.
-    P = np.random.multinomial(1, np.ones(n_arms) / n_arms, size)
-    P = np.where(P, p_target, p_other)
-    
-    ## Main loop.
-    R = []; pi = [] 
-    for n_trials in blocks:
-        
-        ## Store optimal choice.
-        pi.append(P.argmax(axis=1))
-        
-        ## Simulate block of outcomes. Store.
-        r = np.random.binomial(1, P, size=(n_trials,size,n_arms))
-        R.append(r)
-    
-        ## Iteratively shift rows.
-        for i, j in enumerate(np.random.choice([1,-1], size, replace=True)):
-            P[i] = np.roll(P[i], j)
-                
-    ## Concatenate outcomes.
-    R = np.row_stack(R).swapaxes(0,1)
-    pi = np.stack(pi, axis=1)
-                
-    return R, pi
-
-
-class ReversalTask(object):
-    """Train agents on reversal learning task. 
-    
-    Parameters
-    ----------
-    beta : array, shape (n_agents,)
-        Inverse temperature.
-    eta : array, shape (n_agents,)
-        Learning rate (between 0 & 1).
-    xi : array, shape (n_agents,)
-       Lapse rate (between 0 & 1).    
-    """
-    
-    def __init__(self, beta, eta, xi):
-        
-        ## Define parameters.
-        self.beta = np.array(beta)
[…]

### 2020-10-28 setup.py

@@ -1,47 +1,0 @@
-#! /usr/bin/env python
-#
-# Copyright (c) 2020 Niv Lab
-# https://nivlab.princeton.edu/
-
-import os, sys
-from setuptools import setup, find_packages
-path = os.path.abspath(os.path.dirname(__file__))
-
-## Metadata
-DISTNAME = 'laverna'
-MAINTAINER = 'Sam Zorowitz'
-MAINTAINER_EMAIL = 'zorowitz@princeton.edu'
-DESCRIPTION = 'Code for simulating low-effort behavior'
-URL = 'https://github.com/nivlab/silver-screen'
-LICENSE = 'MIT'
-DOWNLOAD_URL = 'https://github.com/nivlab/silver-screen'
-
-with open(os.path.join(path, 'README.md'), encoding='utf-8') as readme_file:
-    README = readme_file.read()
-
-with open(os.path.join(path, 'requirements.txt')) as requirements_file:
-    # Parse requirements.txt, ignoring any commented-out lines.
-    requirements = [line for line in requirements_file.read().splitlines()
-                    if not line.startswith('#')]
-    
-VERSION = None
-with open(os.path.join('laverna', '__init__.py'), 'r') as fid:
-    for line in (line.strip() for line in fid):
-        if line.startswith('__version__'):
-            VERSION = line.split('=')[1].strip().strip('\'')
-            break
-if VERSION is None:
-    raise RuntimeError('Could not determine version')
-
-setup(name=DISTNAME,
-      maintainer=MAINTAINER,
-      maintainer_email=MAINTAINER_EMAIL,
-      description=DESCRIPTION,
-      url=URL,
-      version=VERSION,
-      download_url=DOWNLOAD_URL,
-      long_description=README,
-      packages=find_packages(exclude=['docs', 'tests']),
-      install_requires=requirements,
-      license=LICENSE
-)

### 2020-10-30 manuscripts/main.tex
manuscript updates

@@
 To measure the correspondence between measures of C/IE responding based on task and self-report behaviors, we conducted an behavioral experiment in two prominent online labor marketplaces (see Methods for complete details).
-In total, 400 participants were recruited from Amazon Mechanical Turk (N=) and Prolific (N=) to complete an online study comprised of one behavioral task and several self-report symptom measures.
+In total, 386 total participants from Amazon Mechanical Turk (N=186) and Prolific (N=200) completed an online study comprised of one behavioral task and several self-report symptom measures.
 We recruited participants from both platforms in order to improve the generalizability of our findings.
-The demographics of each sample are summarized in Table XX.
+The demographics of each sample are reported in the Supplement.
 
@@
 For the self-report behavior, we estimated the following metrics: number of suspicious responses to infrequency items, inter-item standard deviation (ISD), personal reliability, Mahalanobis distance, and the per-item reading time.
+Each metric was selected because it has previously been used.
 
-To provide an overall sense of the quality of the data, we first focus on the task accuracy and infrequency scores.
-Based on task accuracy, XX\% of participants were flagged as exhibiting C/IE responding.
-That is, XX\% of participants showed accuracy levels at levels indistinguishable from chance.
-In contrast, the infrequnecy items flagged XX\% of participants as exhibiting C/IE responding.
-This discrepancy between identification rates is already suggestive of differences between task and self-report screening measures.
-Interestingly, the rates of flagged participants differed by platform.
-
-Give overall rates here. Basically want to discuss: (1) different by platform, (2) different by method.
+To provide an overall sense of the quality of the data, we first focus on the task accuracy and the infrequency item metrics as these represent the most common screening methods of each behavioral modality.
+Only 26 participants (7\%) were flagged as exhibiting choice behavior at or above chance levels.
+In contrast, 85 participants (22\%) responded suspiciously to one or more of the infrequency items while completing of self-report symptom inventories.
+This discrepancy in the proportion of participants flagged by each method is consistent with previous studies which have found differing sensitivities to C/IE responding.
+Notably, the proportions of flagged participants were marginally but significantly greater on Mechanical Turk compared to Prolific for both accuracy ($z=2.224, p=0.026$) and infrequency ($z = 2.223, p = 0.026$) metrics.
 
@@
 
+\subsection{Literature Review}
+
+\subsection{Experiment}
+
+\subsubsection{Sample}
+
+409 total participants were recruited to participate in an online behavioral experiment in May, 2020.
+Specifically, 208 participants were recruited from Amazon Mechanical Turk (MTurk) and 201 participants were recruited from Prolific.
+This study was approved by the Institutional Review Board of Princeton University (\#5291), and all participants provided written informed consent.
+Total study duration was approximately 10 minutes per participant.
+Participants received monetary compensation for their time (rate \$12/hr), plus an incentive-compatible bonus based on task performance.
+
+Participants from Mechanical Turk were recruited with the aid of CloudResearch services and were eligible if they resided in the United States or Canada.
+Following recent recommendations, Mechanical Turk workers were not excluded based on HIT approval rate or number of HITs approved.
+Participants from Prolific were similarly eligible if they resided in the United States.
+No other exclusion criteria were applied during recruitment.
+
+The data from multiple participants who completed the experiment were excluded prior to analysis.
+Three participants (all Mechanical Turk) were excluded due to missing data.
+In addition, 20 participants were excluded for having previously completed the experiment on the other platform (MTurk: N=19, Prolific: N=1).
+This left a final sample of N=386 participants (MTurk: N=186, Prolific: N=200) for analysis.
+The demographics of the sample split by labor market is provided in Table S1.
+Notably, the participants recruited from MTurk were older ($M = 7.7 \ \text{yrs}, t = 6.567, p < 0.001$) and comprised of fewer women ($z = 6.567, p = 0.011$).
+Interestingly, 38\% of MTurk users in our sample reported also completing work on Prolific, whereas only 14\% of Prolific users in our sample reported completing work on MTurk.
+
+\subsubsection{Experimental Task}
+
+Participants performed a probabilistic reversal learning task, explicitly designed to be similar to previous computational psychiatry studies.
+On every trial of the task, participants were presented with three choice options and were required to choose one.
+After their choice, participants were presented with probabilistic feedback: a reward (1 point) or a non-reward (0 points).
+On any trial one choice option dominated the others.
+When chosen, the dominant option yielded reward with 80\% probability; the subordinate options yielded reward with only 20\% probability.
+Importantly, dominant option changed every 15 trials.
+Participants completed 90 trials of the task (1 learning block, 5 reversal blocks).
+
+As a cover story, the probabilistic reversal learning task was introduced to participants as a fishing game.
+In the game, each choice option was a beach scene made distinguishable by a colored surfboard with unique symbol.
+Participants were told they were choosing which beach to fish at.
+Feedback was presented as either a fish (1 point) or trash (0 points).
+Participants were instructed to earn the most points possible by learning (through trial-and-error) and choosing the best choice option.
+Participants were also instructed that the best option could change during the task, but were not informed about how often or when this would occur (see the Supplement for the complete instructions).
+Prior to beginning the experiment, participants had to correctly answer four comprehension questions about the instructions.
+Failing to correctly answer all items forced the participant to start the instructions over.
+
+The task was programmed in jsPsych and distributed using custom web-application software. Both the experiment code and
+
+\subsubsection{Self-Report Measures}
+
+Prior to completing the reversal learning task, participants completed 5 self-report symptom measures.
+The symptom measures were selected for inclusion based on their frequency in clinical research and for having an assorted range of response distributions (e.g.
+symmetric, right-skewed, left-skewed).
+
+\textbf{Seven-Up/Seven-Down}: The Seven-Up/Seven-Down (7u/7d) scale is a 14-item measure of manic and depressive tendencies.
+It is an abbreviation of the General Behavior Inventory, wherein only items that maximally discriminated between depression and mania were included.
+It has good psychometric properties and predictive validity.
+Items are scored on 4-point scale from 0 (Never or hardly ever) to 3 (Very often; almost constantly).
+Total scores on both subscales are usually strongly right-skewed, with few participants exhibiting moderate to high levels of symptom endorsement.
+
+\textbf{Generalized Anxiety Disorder-7}: the Generalized Anxiety Disorder-7 (GAD-7) is a 7-item measure of general anxiety.
+It has good psychometric properties in primary care settings and in the general population.
+The GAD-7 assesses how much a respondent has been bothered by each of seven core anxiety symptoms over the last 2 weeks.
+Items are scored on 4-point scale from 0 (not at all) to 3 (nearly every day).
+Total scores on the GAD-7 are usually right-skewed, with few participants exhibiting moderate to high levels of symptom endorsement.
+
+\textbf{Behavioral Inhibition/Behavioral Activation Scales}: the Behavioral Inhibition and Behavioral Activation Scales (BIS/BAS) are a measure of approach and avoidance motivations.
+The original 42-item measure was recently abbreviated to a 14-item measure, which we use here.
+
+\textbf{Snaith-Hamilton Pleasure Scale}:
+
+\textbf{Penn State Worry Questionnaire}:
+
+\subsection{Analysis}
+
+\subsubsection{Correspondence of screening measures}
+
+To measure the correspondence of task- and self-report-based screening metrics, we estimated a number of standard measures of data quality from each participant's task and self-report behavior.
+Beginning first with the self-report data, we included five common measures of data quality, each described below.
+
+\textbf{Infrequency items}: We embedded four infrequency items across the self-report measures.
+The infrequency items were questions that should have only one response.
+We measured the number of suspicious responses made by each participant.
+For thresholded analyses, participants were flagged if they responded incorrectly to any of these items.
+
+\textbf{Inter-item standard deviation}: The inter-item standard deviation (ISD) is an intrapersonal measure of response variability. For a given subscale $j$, the ISD is defined as:
+
+\begin{equation*}
+    ISD_j = \sqrt{\frac{\sum^k_{j=1}(x_j - \bar{x_i})^2}{k-1}}
+\end{equation*}
+
+where $x_j$ is a participant's response to item $j$, $x_i$ is a respondent's average score across all scale items, and $k$ is the total number of scale items.
+The ISD measures the level of dispersion around a participant's average response, and has previously been shown to be sensitive to C/IE responding.
+A composite ISD was computed per participant by summing across each individual subscale.
+
+\textbf{Personal reliability}: The personality reliability coefficient was computed by correlating the average score of random split-halves of items for each subscale.
+1000 random split-halves were computed per subscale and participant.
+A composite score was computed per participant by summing across each individual subscale.
+Lower scores indicate greater response inconsistency.
+
+\textbf{Mahalanobis D}: The Mahalanobis distance is an outlier detection method. For a participant $i$, the Mahalanobis D is defined as:
+
+\begin{equation*}
+    D = \sqrt{(X_i - \bar{X})^T \cdot \Sigma^{-1}_{XX} \cdot (X_i - \bar{X})^T }
+\end{equation*}
+
+where $(X_i - \bar{X})$ represents the vector of mean-centered item responses for participant $i$ and $\Sigma^{-1}_{XX}$ represents the inverted covariance matrix of all items.
+s.
+Larger deviation from the normative response pattern yields higher D values and is considered a potential indicator of C/IE responding.
+A single $D$ statistic was computed for each of the participants using all self-report items.
+
+\textbf{Response Time}: One checks were based on time measurements, with a reading-speed threshold of 10 words per second (Sisso, 2019).
+
+In addition, four measures of data quality were computed from the task behavior data. These are described in turn below.
+
+\textbf{Variability}:
+
+\textbf{Accuracy}:
+
+\textbf{Win-Stay Lose-Shift}:
+
+\textbf{Response Times}:
+
+In three analyses, we measured the correspondence of the metrics above.
+In the first analysis, the similarity of the unthresholded (continuous) metrics were computed via pairwise Spearman correlations.
+For significance testing, we performed a permutation test with 5000 null shuffles and corrected for multiple comparisons using family-wise error rates.
+In the second and third analyses, the similarity of the thresholded metrics were computed via pairwise Dice coefficients.
+The metrics were thresholded taking the top 25\% and 10\% worst respondents for each metric.
+For significance testing, we again performed a permutation test with 5000 null shuffles and corrected for multiple comparisons using family-wise error rates.
+
+\pagebreak
 \section{Supplement}
 
-\bibliography{main}
+\begin{table}
+\centering
+\setlength{\tabcolsep}{15pt}
+\begin{tabular}{ rrrrr }
+\toprule
+& \multicolumn{2}{c}{MTurk} & \multicolumn{2}{c}{Prolific} \\
+\cmidrule(lr){2-3} \cmidrule(lr){4-5}
+Total & \multicolumn{2}{c}{N=186} & \multicolumn{2}{c}{N=200} \\
+\midrule
+Age & N & \% & N & \% \\
+\cmidrule(lr){1-5}
+18-25   &      16 &   8.6 &       78 &  39.0 \\
+26-35   &      76 &  40.9 &       69 &  34.5 \\
+36-45   &      46 &  24.7 &       31 &  15.5 \\
+46-55   &      22 &  11.8 &       13 &   6.5 \\
+55+     &      26 &  14.0 &        9 &   4.5 \\
+\midrule
+Gender & N & \% & N & \% \\
+\cmidrule(lr){1-5}
+Female             &    83 &  44.6 &    112 &  56.0 \\
+Male               &   103 &  55.4 &     85 &  42.5 \\
+Other              &     0 &   0.0 &      3 &   1.5 \\
+\midrule
+Ethnicity & N & \% & N & \% \\
+\cmidrule(lr){1-5}
+Hispanic or Latino     &    15 &   8.1 &     10 &   5.0 \\
+Not Hispanic or Latino &   168 &  90.3 &    183 &  91.5 \\
+Rather not say         &     2 &   1.1 &      7 &   3.5 \\
+Unknown                &     1 &   0.5 &      0 &   0.0 \\
+\midrule
+Race & N & \% & N & \% \\
+\cmidrule(lr){1-5}
+African American                 &    21 &  11.3 &      7 &   3.5 \\
+Asian                                     &     5 &   2.7 &     53 &  26.5 \\
+White                                     &   151 &  81.2 &    121 &  60.5 \\
+Multiracial                               &     6 &   3.2 &      4 &   2.0 \\
+Rather not say                            &     1 &   0.5 &     12 &   6.0 \\
+\midrule
+*Use other platform & N & \% & N & \% \\
+\cmidrule(lr){1-5}
+Yes            &      71 &  38.2 &       28 &  14.0 \\
+No             &     115 &  61.8 &      172 &  86.0 \\
+\bottomrule
+\end{tabular}
+\caption{The demographics of each sample by online labor market.
+On average, the samples were similar though the sample from Mechanical Turk was older (t = 6.567, p $<$ 0.001) and comprised of fewer women (z = 6.567, p = 0.011).
+*Note: the demographics do not include 20 participants (MTurk: N=19; Prolific: N=1) excluded for participating in the study twice, once per platform.}
+\label{tab:demographics}
+\end{table}
+
+% \bibliography{main}
 

### 2020-11-01 manuscripts/main.tex
checkpointing progress

@@
 
+In recent years, online labor markets (e.g.
+Amazon Mechanical Turk, Prolific, Crowdflower) have become increasingly popular as a source of research participants in the behavioral sciences \cite{stewart2017crowdsourcing}, largely due to the ease with which these services allow for collecting large, diverse samples.
+Similarly, the advantages of online data collection platforms have been recognized for clinical research \cite{chandler2016conducting} and are increasingly used in studies of computational psychiatry.
+Here they are offer additional advantages.
+The ability to collect large samples facilitates transdiagnostic analysis, studying symptom co-occurrence and relation to behaviors \cite{gillan2016taking, rutledge2019machine}.
+Online platforms makes it easier to recruit and study otherwise difficult-to-reach populations \cite{strickland2019use}.
+Online platforms also make re-recruitment easier, making it possible to validate the reliability of measurements tools \cite{enkavi2019large} and possibly study longitudinal processes over long timescales \cite{kothe2019retention}.
+Some examples here: gillan
+
+Paragraph 2: These advantages not without costs: online means giving up the control of the laboratory.
+Participants may be distracted, multi-tasking, and with different incentives than usual in-lab participants.
+Fortunately, many previous studies have found data quality on online crowdsourcing websites not altogether different or worse than in-lab samples.
+This isn't to say bad data doesn't exist: estimates vary, but non-negligible data bad and new issues arise.
+For the most part, however, noise has been treated as unsystematic something that can be overcome with increased samples  \cite{gillan2016taking, chandler2020participant}.
+
+> Although typical undergraduate subject populations are often motivated to participate in studies because of an interest in psychology, MTurk participants are unsupervised and anonymous, complete surveys in unknown locations, and are motivated by financial incentives
+
+We specifically want to draw attention to a less appreciated fact: when traits are rare, such as in psychiatry, careless responding is more likely to manifest as symptom endorsement \cite{chandler2020participant, ophir2020turker}.
+Rather than mask true correlations, this can induce spurious correlations in data.
+This effect is well documented in personality psychology, where the presence of careless respondents can induce correlations between questionnaires and bias estimated factors in factor analysis.
+To our knowledge, however, discussion of this point has been limited to associations between self-report measures and not with respect to behavioral experiments.
+There is no reason to expect, however, that this result should be limited to those domains and may similarly be an issue for computational psychiatry.
+
+Paragraph 4: not enough to speculate -- must demonstrate this is an issue.
+what we gonna show: (a) the minority of individuals screen.
+(b) behavior and survey screens may not correlate.
+(c) these correlations do arise.
+We close with some recommendations based on simulations.
+
 \section{Results}
@@
 
-To measure the correspondence between measures of C/IE responding based on task and self-report behaviors, we conducted an behavioral experiment in two prominent online labor marketplaces (see Methods for complete details).
-In total, 386 total participants from Amazon Mechanical Turk (N=186) and Prolific (N=200) completed an online study comprised of one behavioral task and several self-report symptom measures.
-We recruited participants from both platforms in order to improve the generalizability of our findings.
-The demographics of each sample are reported in the Supplement.
+In order to the measure the correspondence of screening metrics estimated from task and self-report behavior, we conducted an online behavioral experiment.
+A finale sample of 386 participants from the Amazon Mechanical Turk (N=186) and Prolific (N=200) online labor markets completed the study and were included for analysis (see Methods for details).
+As part of the experiment, participants completed a probabilistic reversal learning task and 5 self-report symptom measures.
+The reversal learning task required participants to learn through trial-and-error which of three choice options yielded reward most often.
+The self-report measures assayed psychiatric symptoms related to depression, mania, anxiety, reward motivation, and anhedonia.
+The self-report measures were intentionally chosen based on previous literature to have a variety of response distributions.
 
-Participants completed a 3-arm probabilistic reversal learning bandit task.
-During the task, participants were presented with three options and could only choose one, after which they received feedback (reward or no-reward).
-Participants were instructed to choose the option that yielded reward most often, which they would learn through trial-and-error.
-Feedback was probabilistic such that the best option on a given trial returned reward on 80\% of trials and the other options only 20\%.
-Importantly, the best option changed every 15 trials.
-Participants were made explicitly aware that the best option would change over time, but they were not told when or how often this would occur.
-Participants completed 90 trials of the task (5 total reversals).
-
-Prior to the start of the behavioral experiment, participants also completed four standard self-report symptom measures: the generalized anxiety disorder scale (GAD7), the 7-up/7-down, the BIS/BAS, and the Snaith-Hamilton Pleasure Scale.
-The measures were selected to provide a range of response distributions.
-For example, the GAD-7 and 7-up/7-down are substantially asymmetric.
-
-To measure the level of correspondence between task- and self-report-based measures of C/IE responding, we computed a number of metrics from the task and self-report behavior of each subject.
-For the task behavior, we estimated the following metrics: response variability, accuracy, win-stay lose-shift, and fraction of trials with suspicious response times.
-For the self-report behavior, we estimated the following metrics: number of suspicious responses to infrequency items, inter-item standard deviation (ISD), personal reliability, Mahalanobis distance, and the per-item reading time.
-Each metric was selected because it has previously been used.
+We then estimated measures of C/IE responding from each participant's task and self-report behavior (see Methods for full description).
+In line with the narrative review, we screened participants' task behavior for C/IE responding using the following metrics: response variability, or the fraction of responses using only one key; accuracy, or the fraction of choices of the dominant response option; win-stay lose-shift rates, or the difference in likelihood of repeating the previous choice following a rewarded vs.
+unrewarded trial; and fraction of suspicious response times.
+In line with previous studies, we screened participants' self-report behavior for C/IE responding using the following metrics: infrequency items, or the number of suspicious responses to bogus items; inter-item standard deviation, or the dispersion of responses around a participant's modal response on a given subscale; personal reliability, or the correlation between multiple random split-halves of a participant's responses; Mahalonbis distance, or the extent to which a participant is an outlier with respect to the total sample of participants; and reading time, or the average time taken responding to each item.
 
@@
 This discrepancy in the proportion of participants flagged by each method is consistent with previous studies which have found differing sensitivities to C/IE responding.
-Notably, the proportions of flagged participants were marginally but significantly greater on Mechanical Turk compared to Prolific for both accuracy ($z=2.224, p=0.026$) and infrequency ($z = 2.223, p = 0.026$) metrics.
+Though we will not address platform differences here, we note the proportions of flagged participants were marginally but significantly greater on Mechanical Turk compared to Prolific for both accuracy ($z=2.224, p=0.026$) and infrequency ($z = 2.223, p = 0.026$) metrics.
 
-Core result 1: continuous (spearman) correlaiton analysis.
+As a first test of correspondence between the behavior and self-report metrics, we computed pairwise correlations on the unthresholded (continuous) metric data using Spearman's rank correlation.
+We tested for significant correlations using a permutation test with 5000 permutations of the data, correcting for multiple comparisons using the family-wise error rate.
+The resulting pairwise correlation matrix is presented in Figure 1a.
+With the exception of reading time, the self-report metrics exhibited moderate to strong intra-item correlations.
+The strong correlations between ISD, personal reliability, and Mahalonobis D are unsurprising as these have been previously shown to be sensitive to statistically random responding.
+Their correlations with the infrequency items provides face validity for the latter.
+The lack of correlation with reading time is consistent with previous research and evidence that workers wait to submit pages to avoid suspicion.
 
-\subsection{}
+The pattern of correlations for the task-based metrics is noticeably different.
+The only significant correlation surviving multiple corrections is between accuracy and win-stay lose-shift.
+This makes intuitive sense as, by definition, a sensitivity to rewarding and unrewarding outcomes should guide a participant to choosing the dominant response option.
+Crucially, there were few surviving correlations between task- and self-report-based metrics.
+Only accuracy showed any significant correspondence between self-report based measures (specifically the infrequency items, personality reliability, and the Mahalonobis distance).
+Even still, the degree of correspondence between these metrics was roughly half that observed for the correlations between self-report metrics.
+This is initial evidence that task- and self-report-based measures of C/IE responding are not redundant.
+
+A second way to measure the correspondence of the screening metrics is to compare the overlap in the sets of participants each metric flags after thresholding.
+Though measures like accuracy and infrequency have relatively clear threshold cutoffs (e.g.
+chance level performance), the majority of the metrics evaluated here do not.
+As such, we evaluated the metrics with respect to the top 25\% and 10\% of suspicious participants flagged by each measure.
+Conveniently, these percentiles roughly correspond to the fraction of participants flagged by the infrequency items and accuracy metrics, respectively.
+For each percentile threshold, we computed pairwise similarities on the thresholded metric data using Dice similarity.
+As above, we tested for significant correlations using a permutation test with 5000 permutations of the data, correcting for multiple comparisons using the family-wise error rate.
+
+The pairwise Dice similarity matrix at the 25\% and 10\% percentiles are presented in Figure 1b and 1c, respectively.
+At both threshold levels, the pattern of results resembles what was observed for the unthresholded correlations.
+With the exception of reading time again, the self-report metrics show moderate to strong levels of agreement when flagging the most suspicious participants.
+Conversely, the task-based metrics show little agreement with exception of the accuracy and win-stay lose-shift metrics.
+Again we find that on average the self-report and task metrics exhibit chance levels of agreement, with the exception of accuracy.
+As before, where there are significant correspondence between self-report and task metrics, they are roughly half that observed for correspondence among the self-report metrics.
+
+In sum, the correlation analyses suggest that demonstrate that in principle task- and self-report-based measures of C/IE responding should not be assumed to be redundant.
+If anything, the current data suggests that metrics derived from these two types of behavioral data show low overall levels of correspondence, at least in comparison to within-modality levels of correspondence.
+It is worth emphasizing that, in the threshold-based analyses, the highest level of correspondence never exceeded 0.4.
+That is, these two types of metrics are flagging different participants in the majority of cases.
+Though there may be instances where these metrics are in greater agreement (a point we will come back to in the discussion), an experimenter simply cannot assume that task-based screening is sufficient to identify all C/IE responding in self-report data.
+
+Before turning to the consequences of failing to screen on self-report data, we first want to demonstrate that the self-report metrics are indeed sensitive to C/IE responding.
+Though much previous work using these metrics have already done so, it is worth verifying this is the case in the present data.
+Since we are measuring the relationship between task and self-report for the first time, it behooves us to make sure that these metrics are indeed sensitive.
+
+The first approach is to compare the proportion of participants meeting clinical cutoffs before and after screening.
+In the following, we will use only infrequency items to screen out C/IE responding.
+Specifically, we will use a conservative threshold and cite as evidence any suspicious response to an infrequency item as evidence of C/IE responding.
+The fraction of participants at or above clinical levels of symptom endorsement for each symptom measure is reported in Table XX.
+Using a clinical cutoff score of 12, we observe substantial reductions in the fraction of participants endorsing moderate-to-high levels of symptoms on the the mania (7u) and depression (7d) subscales of the Seven-up/Seven-down symptom measure.
+Importantly, this screening reduces the overall rate of clinical endorsement in the remaining sample to levels observed in epidemiological studies of mania and depression.
+Similarly, using a clinical cutoff score of 10, we observe a similarly substantial reduction in the fraction of participants endorsing high levels of anxiety symptoms on the GAD-7.
+Interestingly, a substantial proportion of participants still endorse high levels of anxiety though this may reflect the time period in which this data was collected (during COVID-19 pandemic).
+Finally, SHAPS...
+
+A second approach is to compare the internal consistency of the measures in the flagged vs.
+non-flagged samples.
+Because these symptom questionnaires are vetted in clinical populations, if the flagged participants were simply psychiatric participants with noisier responding we should still expect the internal consistency to be valid.
+We compute the internal consistency of each measure as the mean pairwise Spearman correlation of items within each subscale.
+The correlation structure is presented in Figure XX.
+As can be visually observed, the internal consistency (on-diagonal blocks) are on noticeably reduced between the two groups.
+We compare this difference statistically of the average of these scores using permutation testing by permuting the labels of the participants (flagged vs.
+non-flagged).
+We do this to control for differences in sample size between the two groups.
+We found a significant difference, indicating that this reduction is credible above and above differences in group size.
+This is additional that suggests that the flagged participants are truly engaging in C/IE responding.
+
+\subsection{Spurious correlations}
+
+Paragraph 1: Distributions of responses between groups
+
+Paragraph 2: behavioral metrics
+
+Paragraph 3: Correlation structure
+
+Paragraph 4: Correlation structure by sample size
+
+Paragraph 5: Model-agnostic analysis
 
@@
 
-Topic XX: Continuum of human effort
+Paragraph 1:N: restate results
 
-Topic XX: not a problem specific to online studies, but probably worse there due to lack of monitoring and different incentives.
+Paragraph N+1: low correspondence between different measures highlights the need for utilizing multiple measures.
+this study highlights that metrics may be differentially sensitive, but also sensitive to different types of motivation.
+accuracy was insufficient on its own.
+This is worrisome as this as that is the modal screening form.
+However, the results also suggest that infrequency items were not perfectly sensitive on their own, as evidenced by mania.
+given that our literature review highlighted that many folks using only one method, this is concerning.
 
-Topic XX: how many to expect across platforms and by method. mturk vs. prolific differences. cat and mouse problems.
+Paragraph N+2: Relatedly, these results suggest that low-effort responding is not straightforward.
+Participants may feel unmotivated in some parts, but not others.
+This no doubt reflects, in part, the difficulty of the objective.
+Our RL task was not particularly difficult, so low effort could still do reasonable well.
+Separately, our experiments are setup to incentivize performance only on task but not self-report.
 
-Topic XX: incentives for performance in online tasks
+Paragraph N+3: Briefly worth addressing platform differences. Should say differences are not surprising but we don't think that should be cause for alarm. Cite Cloudresearch tools. Cite better checks.
 
-Topic XX: Accidentally screening out participants of interest
+Paragraph N+4: Limitations
+
+Paragraph N+5: Future directions 1: how big of a problem is this. how many bad subjects do you need?
+
+Paragraph N+6: Future directions 2: answers to above is in part limited by lack of better models of low-effort responding.
+more effort to study what heuristic responses would look like.
+And are these rational?
+
+Paragraph N+7: Future directions 3: really making sure we're not throwing baby out with bathwater. confirm actually low-effort vs. psychiatric
+
+Conclusion:
 
@@
 \subsection{Literature Review}
+
+To quantify the prevalence and types of data screening practices, we conducted a literature review of online behavioral studies.
 
@@
 
-The task was programmed in jsPsych and distributed using custom web-application software. Both the experiment code and
+The task was programmed in jsPsych and distributed using custom web-application software. Both the experiment code and web-software is publicly available.
 

### 2020-11-01 analysis/data/__main__.py

@@ -123,6 +123,18 @@ METADATA.insert(11, 'other-platform', np.where(METADATA['prolific'].isnull(), ME
 METADATA.insert(12, 'prev-complete', np.where(METADATA['prolific-this-study'].isnull(), METADATA['mturk-this-study'], METADATA['prolific-this-study']))
 METADATA = METADATA.drop(columns=['prolific','prolific-this-study','mturk','mturk-this-study'])
 
+## Update BIS/Bas.
+cols = ['bisbas-q01','bisbas-q02','bisbas-q03','bisbas-q04',
+        'bisbas-q05','bisbas-q06','bisbas-q07','bisbas-q08',
+        'bisbas-q09','bisbas-q10','bisbas-q11','bisbas-q12']
+SURVEYS[cols] = (3 - SURVEYS[cols].astype(int)) + 1
+
+## Update SHAPS.
+cols = ['shaps-q01','shaps-q02','shaps-q03','shaps-q04','shaps-q05',
+        'shaps-q06','shaps-q07','shaps-q08','shaps-q09','shaps-q10',
+        'shaps-q11','shaps-q12','shaps-q13','shaps-q14']
+SURVEYS[cols] = 3 - SURVEYS[cols].astype(int)
+
 ## Save.
 METADATA.to_csv(os.path.join(ROOT_DIR, 'metadata.csv'), index=False)
 SURVEYS.to_csv(os.path.join(ROOT_DIR, 'surveys.csv'), index=False)

### 2020-11-01 analysis/scripts/fit_1pl_mcmc.py
added rasch model

@@ -1,0 +1,110 @@
+import h5py, os, pystan
+import numpy as np
+from os.path import dirname
+from pandas import DataFrame, read_csv
+from stantools.io import load_model
+ROOT_DIR = dirname(dirname(os.path.realpath(__file__)))
+
+#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
+### Define parameters.
+#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
+
+## I/O parameters.
+stan_model = '1pl_logistic'
+
+## Sampling parameters.
+samples = 2000
+warmup = 1500
+chains = 4
+thin = 1
+n_jobs = 4
+
+## Define subscales.
+subscales = [
+    ['7u7d-q01','7u7d-q03','7u7d-q04','7u7d-q06','7u7d-q07','7u7d-q08','7u7d-q12'],
+    ['7u7d-q02','7u7d-q05','7u7d-q09','7u7d-q10','7u7d-q11','7u7d-q13','7u7d-q14'],
+    ['gad7-q01','gad7-q02','gad7-q03','gad7-q04','gad7-q05','gad7-q06','gad7-q07'],
+    ['bisbas-q01','bisbas-q02','bisbas-q03','bisbas-q04'],
+    ['bisbas-q05','bisbas-q06','bisbas-q07','bisbas-q08'],
+    ['bisbas-q09','bisbas-q10','bisbas-q11','bisbas-q12'],
+    ['shaps-q01','shaps-q02','shaps-q03','shaps-q04','shaps-q05',
+     'shaps-q06','shaps-q07','shaps-q08','shaps-q09','shaps-q10',
+     'shaps-q11','shaps-q12','shaps-q13','shaps-q14'],
+]
+
+#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
+### Load and prepare data.
+#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
+
+## Load survey data.
+surveys = read_csv(os.path.join(ROOT_DIR, 'data','surveys.csv'))
+
+## Restrict participants.
+reject = read_csv(os.path.join(ROOT_DIR, 'data', 'reject.csv'))
+surveys = surveys[surveys.subject.isin(reject.subject)].reset_index(drop=True)
+
+## Restrict to desired items.
+surveys = surveys[np.concatenate(subscales)]
+
[…]

### 2020-11-01 manuscripts/main.tex
updated sanity checks

@@
 
+\begin{table}[t]
+\centering
+\setlength{\tabcolsep}{6pt}
+\begin{tabular}{lcccccc}
+\toprule
+& \multicolumn{2}{c}{Avg. Total Score} & \multicolumn{2}{c}{Fraction} & \multicolumn{2}{c}{Cronbach's $\alpha$} \\
+\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7}
+ Subscale & No Fail & Any Fail & No Fail & Any Fail & No Fail & Any Fail \\
+\midrule
+7-up    &  3.87 &  10.15 &  0.04 &  0.45 &  0.84 &  0.84 \\
+7-down   &  4.75 &  10.68 &  0.09 &  0.46 &  0.94 &  0.88 \\
+GAD7  &  4.86 &   9.73 &  0.17 &  0.56 &  0.92 &  0.87 \\
+PSWQ  &  4.78 &   6.74 &  0.07 &   0.08 &  0.93 &  0.81 \\
+BIS   &  7.74 &   7.92 &   - &   - &  0.83 &  0.62 \\
+BAS-R &  6.38 &   7.38 &   - &   - &  0.71 &  0.60 \\
+BAS-D &  9.35 &   8.79 &   - &   - &  0.86 &  0.69 \\
+SHAPS &  8.02 &  10.85 &   0.15 &   0.29 &  0.90 &  0.81 \\
+\bottomrule
+\end{tabular}
+\caption{}
+\label{tab:screening}
+\end{table}
+
 \subsection{Spurious correlations}

### 2021-02-23 manuscripts/main.tex
manuscript update because if i lose this i will never forgive myself

--- 2020-10-30 manuscripts/main.tex
@@
 \usepackage{hyperref}
-\usepackage{apacite}
 \usepackage{float}
 \usepackage{amsmath}
+\usepackage[backend=biber,style=nature]{biblatex}
 \usepackage[flushmargin]{footmisc}
@@
 
-% specify bibliography and link style
-\bibliographystyle{apacite}
+% specify link style
+\addbibresource{main.bib}
+\renewcommand*{\bibfont}{\small}
 \hypersetup{
@@
 }
-\renewcommand\bibliographytypesize{\small}
 
@@
 
-\section{Main}
+\section{Introduction}
 
-Paragraph 1: Rise of online studies. Utility for clinical research. Need to define TASK somewhere here.
+In recent years, online labour markets (e.g.
+Amazon Mechanical Turk, Prolific, Crowdflower) have become increasingly popular as a source of research participants in the behavioral sciences \cite{stewart2017crowdsourcing}, in no small part due to the ease with which these services allow for recruitment of large, diverse samples.
+The advantages of online data collection have also begun to be recognized in psychiatric research \cite{chandler2016conducting}, where this method offers several distinct advantages over traditional approaches to participant recruitment.
+The ability to assess psychiatric symptom severity in large general-population samples makes possible large-scale transdiagnostic analysis \cite{gillan2016taking, rutledge2019machine}, and facilitates recruitment from difficult-to-reach participant populations \cite{strickland2019use}.
+Online labour markets also facilitate re-recruitment, making them an attractive option for validating the psychometric properties of assessment tools \cite{enkavi2019large} or studying clinical processes longitudinally \cite{kothe2019retention}.
 
-Paragraph 2: Drawbacks to online studies. Noise. Data quality overview. Focus on unsystematic noise.
+With the advantages of online data collection also come specific drawbacks.
+Since participants recruited from online labour markets are typically completing experiments in their homes, they may be more likely to be distracted or multi-tasking during an experiment.
+Similarly, unsupervised participants may be more likely to use careless/insufficient effort (C/IE) response strategies with the intention to minimise expenditure of time and cognitive effort (e.g., responding randomly on self-report surveys or behavioural tasks).
+Among researchers using online labour markets, a common view is that poor-quality data resulting from C/IE responding can simply be treated as a source of unsystematic measurement error that can be overcome with increased sample sizes \cite{gillan2016taking, chandler2020participant}.
+Similarly, it is common practice in online behavioural research to mitigate poor-quality data using the same screening methods that are typically used in in-person data collection (e.g., excluding participants who perform at- or below-chance on behavioural tasks).
 
-Paragraph 3: Noise is not systematic. As has been pointed out, careless responding can overinflate prevalence of symptoms and can yield spurious correlations. OR Need to define TASK somewhere here.
+Here we wish to draw attention to an underappreciated feature of online psychiatric research using self-report symptom surveys.
+In such surveys, participants rate their endorsement of various psychiatric symptoms and, since most individuals in the general population tend to endorse no or few symptoms in many symptom domains, the resulting ground-truth symptom distributions tend to be heavily positively skewed.
+In this situation, the assumption that C/IE responding merely increases unsystematic measurement noise becomes untenable.
+Because of the positive skew in the ground-truth symptom distribution, participants who respond carelessly to the symptom survey are more likely to report higher levels of symptom endorsement relative to participants who complete the survey accurately \cite{chandler2020participant, ophir2020turker}.
+Consequently, unless C/IE survey responses are carefully identified and removed, a considerable proportion of putatively symptomatic individuals in an online sample may, in fact, be participants who have not engaged with the experiment with sufficient effort.
 
-Paragraph 4: Not clear the extent to which this is an issue.
-For example, if screening in both types of data, might be not an issue.
-Even without screening, behavioral screening might be enough.
-Finally, behavior is complex and might not show up.
+When participants complete both symptom surveys and behavioral tasks (a common study design in computational psychiatry), this artefact has the potential to induce spurious correlations between symptom self-reports and task behavior.
+Concretely, if the same participants who engage in C/IE responding on surveys (and who therefore inaccurately report high levels of psychiatric symptoms) also respond carelessly on behavioral tasks, then we would expect to observe an entirely spurious correlation emerge between greater symptom severity and worse task performance (see Figure \ref{fig:simulation}).
+A similar effect has been well documented in personality psychology, where the presence of careless respondents can induce correlations between questionnaires and bias estimated factors in factor analysis \cite{huang2012detecting, robinson2014inaccurate, huang2015insufficient, chandler2020participant, arias2020little}.
+To our knowledge, however, the potential for C/IE responding to induce spurious correlations between symptom endorsement and task behavior has not previously been noted in the burgeoning field of computational psychiatry.
 
-Paragraph 5: our current results call into question.
+\begin{figure}[t]
+\includegraphics[width=16cm]{../figures/main_01.png}
+\centering
+\caption{Caption TK here}
+\label{fig:simulation}
+\end{figure}
+
+Here we demonstrate the real risk that C/IE responding can lead to spurious symptom-task correlations in computational psychiatry research.
+First, we asked to what extent researchers in computational psychiatry screen self-report data from online samples.
+We found that the majority of these studies did not screen participants' survey data at all, and that very few followed best-practice recommendations for survey data screening.
+We then asked whether behavioural screening alone was sufficient to identify participants engaging in C/IE responding on psychiatric symptom surveys.
+In a new dataset from two separate online labour marketplaces, we found that screening based on task behaviour fails to adequately identify participants engaging in C/IE responding on surveys.
+Lastly, we investigated whether, under these circumstances, C/IE responding led to spurious correlations between symptom severity and task performance for positively-skewed symptom measures.
+Consistent with the logic set out above, we confirmed that failure to appropriately screen out C/IE survey responding in the proof-of-concept dataset that we collected would have produced a number of spurious correlations between task behaviour and self-reported symptoms of depression and anxiety.
 
@@
 
-\subsection{Screening for C/IE responding is common for task behavior but not for self-report behavior}
+\subsection{Screening for C/IE responding is common for task behavior but not for self-report surveys}
 
-The presence of C/IE responding in a dataset can result in spurious correlations between measures of behavior.
-As such, it is imperative for researchers to detect and remove those participants whom complete online experiments with insufficient effort.
+When the rate of symptom endorsement is low in the general population, participants who engage in C/IE responding on self-report symptom measures may appear as putative symptomatic individuals.
+If the same participants also perform a behavioural task with insufficient effort, they may in turn induce spurious correlations between measures of task behavior and self-report symptoms.
+The risk for erroneous inferences, however, is attenuated if experimenters identify and remove those participants.
+As such, it is imperative for researchers to screen for C/IE responding in their data.
 The extent to which experimenters evaluate the quality of both the task and self-report data they collect is unclear.
@@
 
-To provide quantitative support to this claim, we performed a cursory literature review of online human behavioral studies.
-(See Methods for details of the literature search and the list of studies included.) Briefly, we identified studies for inclusion through searches on Google Scholar using permutations of query terms related to online labor platforms, experimental paradigms, and symptom measures.
-We included studies that (a) recruited participants online, (b) measured behavior on at least one experimental task, and (c) measured behavior on at least one self-report symptom measure.
-This resulted in the inclusion of 49 studies.
-We then evaluated whether and how those studies performed task and self-report behavior screening.
-We note that this review was not meant to be systematic, but instead to provide a representative overview of the screening practices common to online behavioral studies.
+To test the empirical support for this claim, we performed a narrative literature review of online human behavioral studies (see Methods for details of the literature search and the Github repository for the full list of included studies).
+Briefly, we identified studies for inclusion through searches on Google Scholar using permutations of query terms related to online labour platforms, experimental paradigms, and symptom measures.
+We included studies that (a) recruited participants online, (b) measured behavior on at least one experimental task, and (c) measured responses on at least one self-report symptom measure.
+We then evaluated whether and how each of the resulting 49 studies performed task and self-report data screening.
+We note that this review was not meant to be systematic, but instead to provide a representative overview of common screening methods in online behavioral studies.
 
-Summary statistics about the prevalence and types of screening practices are provided in Table~\ref{tab:screening}.
-Of the 49 online behavioral studies meeting inclusion criteria, roughly 80\% (39/49) used at least one approach to identify C/IE responding in task behavior.
-Of those studies, just over half relied on a single evaluative method.
-As might be expected, there was considerable heterogeneity in task behavior screening methods.
-Most common was identifying participants whose performance was indistinguishable from chance-level on some measure of accuracy.
-Almost as common was screening based on response variability, or identifying participants who predominantly responded in the same fashion (e.g.
-used only 1 key).
-Less common approaches were screening based on response times and instruction comprehension questions.
+Summary statistics concerning the prevalence and types of screening methods are provided in Table~\ref{tab:screening}.
+Of the 49 online behavioral studies meeting inclusion criteria, roughly 80\% (39/49) used at least one method to identify C/IE responding in task behavior.
+Of those studies, just over half relied on a single screening method, with considerable heterogeneity in behavior screening methods across studies.
+Most common (46\% of all studies) was identifying participants whose performance was indistinguishable from chance-level on some measure of accuracy.
+Almost as common (38\%) was screening based on low response variability (i.e., excluding participants who predominantly responded in the same fashion across trials, such as using only a single response key).
 
-In contrast, only the minority of online behavioral studies in our sample used at least one approach to identify C/IE responding in self-report behavior.
-Of those studies the most common method was the use of attention checks, which operate under the assumption that certain responses are unlikely under inattentive responding.
-Attention checks can be subdivided into different categories such as instructed items, where participants are explicitly told which response to select, and infrequency items, where only one or a small set of responses are valid.
-Of those studies that specified what type of attention check was used, instructed items were the most common form of attention check.
+In contrast, only a minority (19/49, or 39\%) of online behavioral studies in our sample screened for C/IE responding in self-report symptom measures.
+Of those studies the most common method was the use of attention checks, which operate under the assumption that certain responses to these prompts are unlikely under attentive responding, such that participants who do not give the correct response are likely to be engaged in C/IE responding.
+Attention checks can be subdivided into instructed items (in which participants are explicitly told which response to select; e.g., `Please select ``Strongly Agree"'), and infrequency items (in which some responses are logically invalid; e.g., endorsing 'Agree' for the question `I competed in the 1917 Summer Olympic Games').
+Of those studies that specified what type of attention check was used, instructed items were the most common method.
+As we discuss further below, this is notable because best-practice recommendations for data collection in personality psychology explicitly counsel against using instructed-item attention checks.
 Only a handful of studies employed statistical or so-called unobtrusive screening methods such as outlier detection or personal consistency.
 
-In sum whereas screening for C/IE responding in task behavior is ostensibly the norm for online behavioral studies, screening self-report behavior is far less prevalent.
-One possible explanation for this pattern of results is that researchers (implicitly) assume that screening both task and self-report behavior is redundant.
-That is, researchers may believe that task and self-report screening methods will identify the same participants as having exhibited C/IE responding.
-To our knowledge, however, this crucial assumption has never been empirically verified.
-In the next section, we explicitly test this hypothesis in a large sample of online participants.
+In sum, screening methods for C/IE responding vary widely across the studies that we reviewed.
+Whereas screening for C/IE responding in task behavior is relatively common for online behavioral studies, screening of self-report survey data is far less prevalent.
+Though at first this pattern may seem troubling, low rates of survey data screening are not necessarily an issue if screening on task behavior alone is sufficient to remove participants engaging in C/IE responding.
+That is, screening on survey data may be redundant if there is a high degree of correspondence between task- and survey-based screening methods.
+To our knowledge, however, this assumption has never been empirically tested.
+In the next section, we explicitly test this hypothesis in a large sample of online participants completing a battery of self-report surveys and a behavioural task.
 
@@
 \centering
-\setlength{\tabcolsep}{12pt}
-\begin{tabular}{lrrrr}
+\setlength{\tabcolsep}{8pt}
+\begin{tabular}{lllllll}
 \toprule
-& \multicolumn{2}{c}{Task Screening} & \multicolumn{2}{c}{Self-Report Screening} \\
-\cmidrule(lr){2-3} \cmidrule(lr){4-5}
-Frequency & \multicolumn{2}{c}{N=39 (80\%)} & \multicolumn{2}{c}{N=19 (39\%)} \\
+& \multicolumn{2}{c}{Task Screening} & \multicolumn{4}{c}{Self-Report Screening} \\
+\cmidrule(lr){2-3} \cmidrule(lr){4-7}
+Frequency & \multicolumn{2}{c}{N=39 (80\%)} & \multicolumn{4}{c}{N=19 (39\%)} \\
 \midrule
-Method & Accuracy & 18 (46\%) & Attention Check & 17 (89\%) \\
-& Variability & 15 (38\%) & Instructed & 10 (53\%) \\
-& Response Time & 7 (18\%) & Unspecified & 5 (26\%) \\
-& Comprehension & 5 (13\%) & Unobtrusive & 4 (21\%) \\
-& Other & 16 (41\%) \\
+Measure & Accuracy & 18 (37\%) & \multicolumn{2}{l}{Attention Check} & & 17 (35\%) \\
+& Variability & 15 (31\%) & & \textit{Instructed} & & 10 (20\%) \\
+& Response Time & \ 7 (14\%) & & \textit{Unspecified} & & 5 (10\%) \\
+& Comprehension Check & \ \ 5 (10\%) & \multicolumn{2}{l}{Unobtrusive} & & \ 4 (8\%) \\
+& Other & 16 (33\%) \\
 \bottomrule
 \end{tabular}
-\caption{The prevalence and types of task and self-report behavior screening practices in a representative sample (N=49) of online behavioral studies.}
+\caption{The prevalence and types of task and self-report data screening practices in a sample (N=49) of online behavioral studies.}
 \label{tab:screening}
@@
 This is worrisome from the perspective of signal detection theory.
-As has been previously reported, measures of C/IE responding have different sensitivities: some measures will identify only the worst participants, whereas others will flag many more respondents.
+As has been previously reported \cite{desimone2018dirty}, measures of C/IE responding vary in their sensitivities: some measures will identify only the most careless participants, whereas others will flag many more participants.
 As such, using only a single measure runs the risk of false positives (in the case of high sensitivity) and false negatives (in the case of low sensitivity).
-Similarly, different measures are sensitive to different \emph{types} of C/IE responding.
-Using only one measure may thus only identify a subset of C/IE respondents.
-As has been discussed elsewhere, the use of multiple measures is encouraged to more accurately and sensitively identify C/IE responding in a dataset.
+Similarly, screening methods vary in their sensitivity to different patterns of C/IE responding \cite{curran2016methods}.
+Using only one measure may thus only identify a subset of careless respondents.
+As has been discussed elsewhere, the use of multiple screening methods is encouraged to more accurately and sensitively identify C/IE responding in a dataset \cite{curran2016methods, barends2019noncompliant}.
 
-Second, we found that the majority of studies that did screen self-report data relied on instructed items.
-This is separately worrisome as a growing body of research disputes their efficacy for online studies.
-There is empirical evidence that these items are less sensitive online elsewhere.
-A quick search online reveals that instructed items are frequently discussed in forums used by workers in online labor markets.
-Most concerning, there is empirical evidence that of a subset of participants that screen for these items and respond randomly where else.
-We encourage other methods and, as above, a multitude of methods.
+Second, we found that the majority of studies that did screen self-report survey data relied on instructed attention checks.
+This is potentially problematic, since a growing body of research disputes the efficacy of instructed items as attention checks for online studies \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}.
+Indeed, instructed attention checks are often discussed on forums for workers of online labour markets\footnote{Several examples of such discussions can be found at the Github repository for this project:  \url{github.com/nivlab/silver-screen}}, and scripts have even been developed with the purpose to highlight words most commonly used in instructed attention checks.
+Unsurprisingly, then, it has been documented that subsets of participants may actively seek out instructed items in surveys and respond randomly elsewhere \cite{barends2019noncompliant}.
+In line with best-practice recommendations for online survey research, therefore, we encourage experimenters to use alternate means of screening for C/IE responding for self-report survey data (e.g., infrequency-item attention checks) \cite{huang2015detecting}.
 
-\subsection{Task and self-report measures of C/IE responding}
+\subsection{Careless participants appear symptomatic when the overall level of symptom endorsement is low}
 
-To measure the correspondence between measures of C/IE responding based on task and self-report behaviors, we conducted an behavioral experiment in two prominent online labor marketplaces (see Methods for complete details).
-In total, 386 total participants from Amazon Mechanical Turk (N=186) and Prolific (N=200) completed an online study comprised of one behavioral task and several self-report symptom measures.
-We recruited participants from both platforms in order to improve the generalizability of our findings.
-The demographics of each sample are reported in the Supplement.
+In the majority of the papers reviewed above, experimenters relied solely on behavioural screening to exclude participants who engaged in C/IE responding during an experiment.
+Nevertheless, even with behavioural screening, it is still possible that spurious behaviour-symptom correlations might emerge if there is low correspondence between behavioural and survey-based C/IE screening methods (since high correspondence between methods would entail that behavioural screening alone would exclude participants who would have failed survey screening).
 
-Participants completed a 3-arm probabilistic reversal learning bandit task.
-During the task, participants were presented with three options and could only choose one, after which they received feedback (reward or no-reward).
-Participants were instructed to choose the option that yielded reward most often, which they would learn through trial-and-error.
-Feedback was probabilistic such that the best option on a given trial returned reward on 80\% of trials and the other options only 20\%.
-Importantly, the best option changed every 15 trials.
-Participants were made explicitly aware that the best option would change over time, but they were not told when or how often this would occur.
-Participants completed 90 trials of the task (5 total reversals).
+In order to the measure the correspondence of screening measures estimated from task and self-report behavior, we conducted an online behavioral experiment involving a simple behavioral task and a battery of self-report psychiatric symptom measures (see Methods for details).
+A final sample of 386 participants from the Amazon Mechanical Turk (N=186) and Prolific (N=200) online labour markets completed a probabilistic reversal learning task and 5 self-report symptom measures.
+The reversal learning task required participants to learn through trial-and-error which of three choice options yielded reward most often, and was modeled after similar tasks used to probe reinforcement learning deficits in psychiatric disorders \cite{huang2017computational, waltz2007probabilistic, mukherjee_reward_2020}.
+The self-report measures assayed psychiatric symptoms related to depression, mania, anxiety, reward motivation, and anhedonia, and were chosen based on previous literature to have a variety of expected response distributions (symmetric and asymmetric).
+In line with current best-practice recommendations in personality psychology, each self-report instrument included one `infrequency' item that could be used to identify C/IE responses in survey data (see Methods for a list of infrequency items).
+To minimize any influence of fatigue, the entire experiment (surveys \& task) was designed to require 10 minutes on average to complete (observed mean = 10.28 minutes).
+For similar reasons, participants completed the surveys prior to beginning the task.
 
-Prior to the start of the behavioral experiment, participants also completed four standard self-report symptom measures: the generalized anxiety disorder scale (GAD7), the 7-up/7-down, the BIS/BAS, and the Snaith-Hamilton Pleasure Scale.
-The measures were selected to provide a range of response distributions.
-For example, the GAD-7 and 7-up/7-down are substantially asymmetric.
+To assess the overall quality of the data, we examined the number of participants flagged by the choice accuracy and infrequency item screening measures (i.e.
+two most common screening measures identified in our literature review).
+Only 26 participants (7\%) were flagged as exhibiting choice behavior in the reversal learning task at or below chance levels.
+In contrast, 85 participants (22\%) responded suspiciously on one or more of the infrequency items when completing the self-report symptom measures.
+This discrepancy in the proportion of participants flagged by each method is consistent with previous research which have found varying levels of sensitivity to C/IE responding across screening methods \cite{desimone2018dirty}.
+Though we will not address platform differences here, we note the proportions of flagged participants were marginally but significantly greater on Mechanical Turk compared to Prolific for both accuracy (MTurk: N=18/186; Prolific: N=8/200; $z=2.22, p=0.026$) and infrequency (MTurk: 50/186; Prolific: 35/200; $z = 2.22, p = 0.026$) measures.
 
-To measure the level of correspondence between task- and self-report-based measures of C/IE responding, we computed a number of metrics from the task and self-report behavior of each subject.
-For the task behavior, we estimated the following metrics: response variability, accuracy, win-stay lose-shift, and fraction of trials with suspicious response times.
-For the self-report behavior, we estimated the following metrics: number of suspicious responses to infrequency items, inter-item standard deviation (ISD), personal reliability, Mahalanobis distance, and the per-item reading time.
-Each metric was selected because it has previously been used.
+\begin{figure}[t!]
+\includegraphics[width=16cm]{../figures/main_02a.png}
+\centering
+\caption{Caption TK here}
+\label{fig:distributions}
+\end{figure}
 
-To provide an overall sense of the quality of the data, we first focus on the task accuracy and the infrequency item metrics as these represent the most common screening methods of each behavioral modality.
-Only 26 participants (7\%) were flagged as exhibiting choice behavior at or above chance levels.
-In contrast, 85 participants (22\%) responded suspiciously to one or more of the infrequency items while completing of self-report symptom inventories.
-This discrepancy in the proportion of participants flagged by each method is consistent with previous studies which have found differing sensitivities to C/IE responding.
-Notably, the proportions of flagged participants were marginally but significantly greater on Mechanical Turk compared to Prolific for both accuracy ($z=2.224, p=0.026$) and infrequency ($z = 2.223, p = 0.026$) metrics.
+According to our hypothesis, a prerequisite for spurious behavior-symptom correlations to emerge is a mean-shift in the average level of symptom endorsement in participants engaging in C/IE responding relative to attentive participants, which might occur when the overall rate of symptom endorsement is low.
+As such, we visually inspected for each of the self-report measures the distribution of symptom scores in participants flagged by the infrequency measure vs.
+those that were not (hereafter referred to as `careless' or `attentive`, respectively; Figure \ref{fig:distributions}).
+In line with our predictions, the average level of symptom endorsement was noticeably exaggerated in careless participants relative to attentive participants for the symptom measures where symptom scores were positively-skewed (e.g.
+7-up, 7-down, GAD-7).
+In contrast, where there was a greater range of symptom endorsement, the distributions of symptom scores between the two groups of participants were less noticeably distinct.
 
-Core result 1: continuous (spearman) correlaiton analysis.
+\begin{table}[!t]
+\centering
+\setlength{\tabcolsep}{6pt}
+\begin{tabular}{lccccccc}
+\toprule
+& & \multicolumn{2}{c}{Total Score} & \multicolumn{2}{c}{Clinical Levels} & \multicolumn{2}{c}{Cronbach's $\alpha$} \\
+\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8}
+ Subscale & Skew & Attentive & Careless & Attentive & Careless & Attentive & Careless \\
+\midrule
+\midrule
+7u    &  0.81 &    3.87 &   10.15 &     0.04 &     0.45 &    0.84 &    0.84 \\
+7d    &  0.76 &    4.75 &   10.68 &     0.09 &     0.46 &    0.94 &    0.88 \\
+GAD7  &  0.75 &    4.86 &    9.73 &     0.17 &     0.56 &    0.92 &    0.87 \\
+BIS   &  0.78 &    7.74 &    7.92 &        - &        - &    0.83 &    0.62 \\
+BAS   &  0.17 &   15.73 &   16.16 &        - &        - &    0.84 &    0.71 \\
+SHAPS &  0.26 &    8.02 &   10.85 &     0.15 &     0.29 &    0.90 &    0.81 \\
+PSWQ  &  0.19 &    4.78 &    6.74 &     0.07 &     0.08 &    0.93 &    0.81 \\
+\bottomrule
+\end{tabular}
+\caption{}
+\label{tab:screening}
+\end{table}
 
-\subsection{}
+To verify the infrequency item method as an accurate assay of C/IE responding, we performed three validation analyses.
+The first approach is to compare the proportion of participants meeting the cutoff for clinical psychopathology among careless versus attentive participants(Table \ref{tab:screening}).
+On the most positively-skewed measures, the fraction of participants scoring at or above clinical levels of symptom endorsement was dramatically inflated in careless responders.
+For example, previous studies of prevalence of generalized anxiety disorder found that roughly 5\% of the general population met the clinical threshold at a score of 10 or higher on the GAD-7 \cite{lowe2008validation, hinz2017psychometric}.
+Though clinical thresholds have not been established for the 7-up/7-down, recent work has suggested scores of 12 or higher as useful for discriminating between those with and without clinical levels of pathology \cite{youngstrom2020evaluating}.
+Though the fraction of participants meeting threshold for these measures in the attentive group was within the expected range of prevalence given epidemiological data, the exaggerated rates in the flagged group are suggestive of C/IE responding.\footnote{Interestingly, compared to previous literature the proportion of participants meeting threshold on the GAD-7 was elevated.
+We suspect this may reflect elevated rates of state anxiety during the COVID-19 pandemic, when this data was collected.}
+
+The second approach was to compare the estimated internal consistency of the self-report measures between the careless and attentive groups.
+The logic is that, if C/IE responding manifests as a tendency to respond randomly, we should expect to see a decrease in the consistency of a measure in the careless group (as has been previously reported; \cite{maniaci2014caring, desimone2018dirty, desimone2018differential}).
+Accordingly, on the majority of measures we observed a reduction in Cronbach's $\alpha$ in the careless group relative to the attentive group (Table \ref{tab:screening}).
+A permutation test confirmed that the average decrease in internal consistency across measures was greater than would be expected by chance even controlling for the difference in the number of participants between the two groups ($t = 4.25, p = 0.006$).
+
+The third and final approach is to statistically quantify the degree to which participants responded to the items in the self-report symptom inventory in a stereotyped fashion; that is, to determine if participants exhibited patterns in their responses that were independent of the contents of the items.
+To do so, we fit a random intercept item factor analysis model \cite{maydeu2006random} to the self report data (see Methods for details).
+Briefly, an intercept term is estimated for each participant which quantifies their bias towards using particular response options (e.g.
+leftmost, rightmost) regardless of what that option signifies for a particular self-report measure.
+We observed a credible difference between the average value of this intercept between the two groups (stats here), such that participants suspected of C/IE responding were biased towards using the right-half of the response options on the self-report symptom inventory.
+This translates to a tendency to endorse greater illness on the 7-up/7-down and GAD-7 (where the rightmost options indicate greater frequency of symptoms) but translates to a tendency to endorse \emph{less} illness on the SHAPS and BIS (where the rightmost options indicate lower frequency of symptoms) despite these inventories measuring strongly correlated constructs (i.e.
+depression and anhedonia, anxiety and behavioral inhibition).
+This pattern also helps explain why the distributions of symptom scores between attentive and careless participants on the SHAPS appear to be similar despite the low rates of symptom endorsement usually observed on the SHAPS \cite{snaith1995scale}.
+
+In sum, we found that almost a quarter of participants in our online sample were suspected of C/IE responding when screened using the infrequency-item measure, in contrast to only 7\% of participants flagged when using task accuracy as a screening measure.
+Importantly, participants suspected of C/IE responding were more likely to appear as symptomatic on self-report measures where symptom endorsement was rare on average.
+Furthermore, using three independent analyses, we identified evidence that validates the infrequency-item measures as sensitive to C/IE responding.
+These validation analyses also identified multiple forms of C/IE responding.
+Though the Cronbach's alpha result suggests at least some participants were engaging in random responding, the item response model analysis identified participants who exhibited a preference for the rightmost response options regardless of their semantic content.
+That C/IE responding in this data manifested in more than one way (consistent with previous reports \cite{curran2016methods}) further highlights the importance of utilizing multiple screening methods, a point we will return to in the discussion.
+
+\subsection{Low correspondence between task and self-report measures of C/IE responding}
+
+Next, we evaluated the degree of correspondence between behavioral and self-report screening measures.
+This allowed us to determine whether screening on behavior alone was sufficient to identify and remove careless participants.
+In line with the narrative review, we computed multiple measures of C/IE responding from each participant's task behaviour and survey responses (see Methods for full description).
+For task behaviour, we computed the following screening measures: response variability (the fraction of responses using only one key), accuracy (the fraction of choices of the reward-maximizing response option), win-stay lose-shift rates (the difference in likelihood of repeating the previous choice following rewarded vs.
+unrewarded trials), and fraction of excessively fast response times.
+In line with previous studies, for self-report responses we screened participants' data for C/IE responding using the following measures: infrequency items (the number of suspicious responses to infrequency items), inter-item standard deviation (ISD; the variability of responses around a participant's modal response), personal reliability (the correlation between split-halves of a participant's responses), Mahalonobis distance (the extent to which a participant is an outlier with respect to all participants), and reading time (the average time taken to respond to each item).
+
+To measure the degree of correspondence between these behavioral and self-report screening measures, we performed two complementary analyses.
+First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation.
+The resulting pairwise similarity matrices are presented in Figure \ref{fig:correspondence} (left panel).
+After correcting for multiple comparisons, there were few significant correlations between the behavioral and self-report measures.
+Only choice accuracy showed significant associations with any self-report measure (specifically the infrequency and Mahalonobis distance measures).
+Crucially, the size of these observed correlations were roughly half that observed for the correlations between the self-report measures.
+This is worrisome as it suggests that, though there is some relation between C/IE responding on tasks and self-report inventories, it is not strong enough to reliably detect careless participants in self-report data from task data alone.
+
+\begin{figure}[!t]
+\includegraphics[width=16cm, trim=0 0 3cm 0]{../figures/main_02b.png}
+\centering
+\caption{Caption TK here}
+\label{fig:correspondence}
+\end{figure}
+
+To complement the correlational analysis, we also estimated the pairwise level of agreement on the binarized measures using the Dice similarity coefficient.
+This second approach quantifies the degree of overlap between the set of would-be excluded participants based on different screening measures under a common exclusion rate.
+Though measures like accuracy have relatively clear threshold cutoffs (e.g.
+chance level performance), the majority of the measures evaluated here do not.
+As such, we evaluated the measures with respect to the top 10\% of suspicious participants flagged by each measure, corresponding roughly to the fraction of participants having performed at chance levels on the reversal learning task.
+The results of the same analysis repeated for the top 25\% of suspicious participants (corresponding roughly to the fraction of participants flagged by the infrequency item measure) produced similar results, and is included in the supplement.)
+
+The resulting pairwise similarity matrices for each approach are presented in Figure \ref{fig:correspondence} (right panel).
+The pattern of results are largely consistent with the correlational analysis: few pairs of task and self-report screening measures achieved levels of agreement greater than what would be expected by chance.
+The only significant cross-modality pair identified -- between the infrequency item and choice accuracy measures -- has a similarly coefficient less than 0.4.
+In other words, when these two measures are used to identify the top 10\% most suspicious participants, they agree on only two out of every five participants.
+Screening on choice accuracy alone (the most common method identified in our narrative review) would fail to identify the majority of participants most likely engaging in C/IE responding as determined by the infrequency items.
+
+To conclude this section, we found across two complementary analyses that measures of C/IE responding in task and self-report data were not redundant.
+That is, contrary to common implicit assumptions in online behavioural research, detecting and removing careless participants based on behavioral data alone would not be sufficient for ensuring quality self-report data in our sample.
+Though we cannot extrapolate from this one dataset to conclude that this will always be the case, we can nevertheless conclude that experimenters cannot simply assume that screening on self-report data is redundant with screening on task behavior (and vice-versa).
+While tendencies towards C/IE responding in tasks and self-report inventories may be associated, our results show that both types of screening are likely to be necessary to ensure acceptable data quality.
+
+\subsection{Spurious symptom-behaviour correlations produced by C/IE responding}
+
+Here we detail the potential consequences of screening only on task behavior in our data.
+To do this, we estimated the pairwise correlations between the symptom scores of each of the self-report measures and several measures of performance on the reversal learning task.
+This analysis emulated a typical computational psychiatry analysis, in which the results of primary interest are the correlations between task behaviour and self-reported psychiatric symptom severity.
+
+For each participant, we computed both descriptive and model-based measures of behaviour on the reversal learning task.
+Descriptive measures included accuracy (the fraction of choices of the reward-maximizing response option), points (the total number of points accumulated over the game), win-stay rates (the fraction of trials on which a participant repeated the previous trial's choice following a reward outcome), lose-shift rates (the fraction of trials on which a participant deviated from the previous trial's choice following a non-reward outcome), perseveration (the number of trials on which a participant continued to choose the previously dominant response option following a reversal).
+The model-based measures included the parameters of commonly-used reinforcement model of choice behavior, i.e.
+$Q$-learning with asymmetric learning rates (see Method for further details): choice sensitivity ($\beta$,  inverse temperature), positive learning rate ($\eta_p$, learning rate following a positive reward prediction error), negative learning rate ($\eta_n$, learning rate following a negative reward prediction error), and learning rate asymmetry ($\kappa$, difference between $\eta_p$ and $\eta_n$ in a transformed space).
+We chose these task performance measures as they have been previously used to assess performance in clinical samples \cite{huang2017computational, brolsma2020challenging, mukherjee_reward_2020, ritschel2017neural}.
+
+To understand the effects of applying different forms of screening, we estimated the correlations between each unique pairing of a self-report symptom measure and measure of behavior under four different conditions: no screening, screening only on task behavior (i.e.
+accuracy above chance), screening only on self-report responses (i.e.
+pass responses on all infrequency items), or both.
+The resulting pairwise behavior-symptom correlations following each screening procedure are presented in Figure \ref{fig:correlations}.
+To note, these correlational analyses were not corrected for multiple comparisons as the intended purpose here is to emulate a conventional analysis where fewer statistical tests would be performed, as dictated by one's hypotheses.
+
+\begin{figure}[!t]
+\includegraphics[width=16cm]{../figures/main_03a.png}
+\centering
+\caption{Caption TK here}
+\label{fig:correlations}
+\end{figure}
+
+When no rejections based on for C/IE responding was applied (i.e.
+all participants in this sample were included; top left, Figure \ref{fig:correlations}), many significant correlations emerged between measures of task behavior and symptom scores.
+Consistent with our predictions, the majority of these correlations involved symptom measures with asymmetric total score distributions.
+Attending to only the most skewed measures (i.e.
+7-up/7-down, GAD-7), symptom endorsement was correlated with almost every behavioral measure.
+That is, significant correlations were not restricted only to behavioral measures often used as proxies for participant effort (e.g.
+accuracy, inverse temperature $\beta$) but also to measures of previous theoretical interest.
+Conversely, we found few significant correlations among symptom measures with more symmetric distributions.
+This is despite the fact these scales measure similar symptoms and syndromes (e.g.
+anxiety \& worry, depression \& anhedonia).
+
+Next, we rejected participants based on task behavior screening (i.e.
+choice accuracy, removing the 7\% of participants exhibiting behavior indistinguishable from chance; top right, Figure \ref{fig:correlations}).
+The pattern of correlations was largely unchanged: we again found many significant correlations between measures of behavior and asymmetric symptom measures, but almost no significant correlations involving symmetric symptom measures.
+Looking again at the most skewed symptom measures, all correlations involving accuracy and the inverse temperature were preserved.
+In sum, rejections based on the most common form of behavioral screening (i.e.
+performance accuracy) had little effect on behavior-symptom correlations as compared to no screening.
+
+We then rejected participants based on self-report screening  (i.e.
+infrequency item, removing the 22\% of participants endorsing 1 or more suspicious responses; bottom left, Figure \ref{fig:correlations}).
+In stark contrast, the number of significant correlations was markedly reduced.
+Notably, no significant correlations remained between the 7-down depression scale and any measure of task behavior after performing rejections based on self-report behavior.
+Similarly, fewer (but not no) significant correlations were observed between the most skewed symptom measures and proxy measures of task attentiveness (e.g.
+accuracy, inverse temperature).
+Finally, and interestingly, the pattern of correlations were largely similar when rejections were applied based on both task and self-report screening measures.
+
+The preceding results suggest that many of the significant behavior-symptom correlations observed prior to rejections are in line with our predictions; that is, spurious correlations driven by C/IE responding when symptom endorsement is rare on average.
+This leads us to conclude that behavioural screening alone did not adequately protect against spurious symptom-behaviour correlations in the presence of skewed distributions of symptom endorsement.
+This can be illustrated using the example of the 7-down scale, a measure of trait depression.
+If we had not screened participants based on their self-report data, we would have erroneously concluded that there were many significant associations between reversal learning task performance and self-reported depression.
+As it was, screening on self-report data allowed us to identify that each of these depression-behaviour correlations was likely to be entirely spurious.
+
+One possible objection to this interpretation is that the reduction in significant correlations following self-report screening and rejection was driven, not by the effective identification and removal of C/IE respondents, but simply by virtue of removing over 20\% of the sample.
+That is, rejections may have simply reduced the statistical power of analyses without changing the the estimated effect size.
+To see if this was the case, we compared the average (absolute) correlation size before and after rejections were applied (the complete tables of correlations are included in the supplement).
+On average, we observed a significant reduction in correlation effect sizes [add numbers] following rejections, suggesting that the reduction in significant correlations following screening was unlikely to be driven solely by a reduction in statistical power.
+
+Next, we investigated how spurious correlations depended on sample size.
+To do so, we performed a bootstrapping analysis where we held fixed the proportion of participants engaging in C/IE responding (i.e.
+5\%, 10\%, 15\%, 20\%) and increased the total number of participants.
+Across all analyses, we measured the correlation and between the 7-down depression scale and learning rate asymmetry ($\kappa$), which we previously identified as likely exhibiting a spurious association.
+
+The outputs of the bootstrapping analysis are presented in Figure \ref{fig:bootstrap}.
+Unsurprisingly, the absolute magnitude of the behavior-symptom correlation increased with the proportion of inattentive participants (left panel).
+Interestingly, correlation magnitude was largely independent of sample size.
+Crucially, we found false-positive rates for spurious correlations \emph{increased} with increases in sample size in our data.
+This runs counter to a common assumption that larger sample sizes are protective against spurious correlations because they serve to mitigate measurement error.
+Although this is certainly the case for unsystematic measurement error, this intuition no longer holds in the regime of systematic measurement error (i.e., larger sample sizes reduce the variance of estimates, but do not alter not their bias).
+Instead, our results suggest that, holding the proportion of C/IE responding constant, the false-positive rate for behavioural-symptom correlations will become increasingly inflated as the sample size increases.
+The reason for this is that both the precision of the estimated correlation, and the statistical power to detect said correlation, increases with increasing sample size.
+This result runs counter to the assumption that greater measurement error in online samples can be mitigated by simply collecting more data.
+
+\begin{figure}[!t]
+\includegraphics[width=16cm]{../figures/main_03b.png}
+\centering
+\caption{Caption TK here}
+\label{fig:bootstrap}
+\end{figure}
+
+Of course, it is important to note that these results do not give a complete picture of the likely effects of C/IE responding on symptom-behaviour correlations.
+A full picture would require investigating the effects of C/IE responding over numerous different task designs, symptoms measures, sample sizes, and proportions of careless responders.
+Nevertheless, the results of this bootstrapping analysis suggest that spurious correlations driven by C/IE responding are likely to be a considerable source of potential error wherever large online samples are collected with asymmetric distributions of symptom endorsement.
+Indeed, it is also worth highlighting that false positive rates were inflated (above the expected 5\% level given $\alpha = 0.05$) even with only 5\% of the bootstrapped participant samples engaging in C/IE responding, which further highlights how pernicious this issue is.
+
+\subsection{C/IE responding manifests as qualitatively distinct behavioral strategy}
+
+In this final section, we employ a theory-agnostic modeling approach to better understand how participants suspected of engaging in C/IE responding performed on the probabilistic reversal learning task.
+This analysis was motivated by two interrelated aims.
+First was to better understand why there was low correspondence between screening measures derived from task and self-report data; that is, to determine why participants flagged by the infrequency items were not necessarily more likely to perform at chance.
+The second was to better understand how the particular pattern of behavior-symptom correlations from the previous section emerged.
+The results of this section are specific to the particular reversal-learning task that we used here, and it is likely that qualitatively different patterns would be likely to emerge in different behavioural tasks.
+
+To characterize participants' choice behavior, we adapted the softmax regression model from \cite{seymour2012serotonin}.
+Briefly, in this model the propensity for a participant to choose an option is a function of the sum of weights corresponding to the recent history of trial events (e.g.
+rewarding outcomes, non-rewarding outcomes, previous choices; see Methods for details).
+In other words, the model estimates for each participant how much their choice on some trial was influenced by the events of the preceding five trials.
+
+The regression weights, averaged within attentive and careless participants, for each event are presented in Figure \ref{fig:regression}.
+Comparing attentive participants to those suspected of engaging in C/IE responding, we observed a credible difference (i.e.
+95\% highest densitivity intervals excluded zero) only for the $T-1$ weight for previous choice.
+Attentive participants were more likely to repeat their previous choice (i.e.
+greater choice hysteresis) than were careless participants.
+Though careless participants did appear to show less sensitivity to the history of rewards and nonrewards, the 95\% highest density intervals did not exclude zero.
+
+\begin{figure}[!b]
+\includegraphics[width=16cm]{../figures/main_03c.png}
+\centering
+\caption{Caption TK here}
+\label{fig:regression}
+\end{figure}
+
+This result may be initially surprising, since one might expect choice hysteresis to result in more perseveration errors following contingency reversals, and since results reported in the previous section indicated that C/IE responding was associated with more perseveration errors.
+What is important to keep in mind, however, is that choice hysteresis is adaptive in this probabilistic reversal learning task.
+Since rewards in this task are probabilistic, participants should display a degree of hysteresis once the reward-maximizing response option has been identified, ignoring the occasional non-rewarding outcome from this option.
+In contrast to this adaptive strategy, we found that participants engaging in C/IE responding exhibited a qualitatively different behavioral strategy more akin to a win-stay lose-shift heuristic.
+
+This, in conjunction with overall reduced outcome sensitivity ($\beta$), explains the pre-screening pattern of correlations with win-stay and lose-shift rates.
+But what of the learning rate asymmetries?
+That learning rate asymmetries ostensibly relate to C/IE responding is puzzling at first given that the softmax regression results show no credible differences in the sensitivity to history of rewarding and non-rewarding outcomes.
+This too can be explained by choice hysteresis.
+Previous work has established that, when choice hysteresis is not accounted for in reinforcement learning models, it can manifest as positive learning rate asymmetries \cite{Katahira2018-ke}.
+As such, given that attentive participants show increased repetition, which our reinforcement learning model did not explicitly account for, we should expect to find a negative (positive) correlation between positive (negative) learning rates and C/IE responding.
+Indeed, this is precisely the pattern of correlations observed above.
+
+To conclude, the theory-agnostic analysis of task behavior revealed that careless participants were less likely to engage in adaptive choice hysteresis and instead showed a pattern of responding more akin to win-stay lose-shift heuristic.
+This finding helps clarify in part why we observed low correspondence between task and self-report screening measures: on average, careless participants were not engaging in random responding (which would have been detected by the accuracy screening measure) but instead in satisficing behaviors.
+Most importantly, the results present another hidden danger of C/IE responding.
+When participants utilize heuristic decision-making, this may manifest in difficult-to-predict forms when computational models are misspecified.
+Thus, C/IE responding may not only drive spurious correlations but also spurious inferences about what behavior-symptom correlations entail.
 
@@
 
-Topic XX: Continuum of human effort
+Recap paragraph goes here
 
-Topic XX: not a problem specific to online studies, but probably worse there due to lack of monitoring and different incentives.
+One way of conceptualizing the results presented here is through the lens of rational allocation of mental effort \cite{kool2018mental}.
+In any experiment, attentive responding is more effortful than careless responding.
+As such, participants completing an online task must perform a cost-benefit analysis---implicitly or otherwise---to decide how much effort to exert in responding.
+The variables which factor into such calculations are presumably manifold and likely include features of the experiment (e.g., task difficulty, monetary incentives), facets of the individual (e.g., subjective effort costs, intrinsic motivation, conscientiousness), and features of the online labor market itself (e.g., opportunity costs, repercussions for careless responding).
+To the extent to which at least some of these factors are stable within an experiment, we would expect that C/IE responding is somewhat correlated within individuals across experiment components (as we have shown here with correlations between task and self-report responding).
 
-Topic XX: how many to expect across platforms and by method. mturk vs. prolific differences. cat and mouse problems.
+Viewed from the perspective of effort expenditure, our results suggest that participants appraised this cost/benefit trade-off differently for the behavioural task and the self-report surveys.
+Specifically, we found that only 7\% of participants were at chance-level performance in the task---compared to more than 22\% of participants who failed one or more attention check items in the self-report surveys---and that measures of C/IE responding were weakly or not at all correlated between task behavior and self-report responses.
+This suggests the motivation for effortful responding was greater in the behavioural tasks, though precisely why is unclear.
+One possibility is that we gave participants a monetary incentive for attentive responding only during the task (a common practice, according to our narrative review).
+A second possibility is that participants expected fewer consequences for C/IE responding during the self-report surveys, a reasonable assumption in light of how infrequently previous experiments have screened self-report data.
+Alternatively, participants may have found the gamified behavioural task more engaging or the self-report inventory more tedious.
+Whatever the reason, this discrepancy reinforces our observations concerning the inadequacy of behavioural-task screening as a stand-alone method for identifying C/IE responding.
+Since, in general, participants will appraise costs and benefits of effortful responding differently for behavioural tasks and self-report surveys, screening for C/IE responding on one data modality will almost never be suitable for identifying it in the other.
+A corollary of this is that the exact pattern of correspondence in C/IE responding across data modalities that we observed is a contingent feature of our study design; other study designs---for instance, using a more difficult behavioural task---would be expected to result in different patterns of correspondence.
 
-Topic XX: incentives for performance in online tasks
+One complicating factor for the argument that we have presented here is that C/IE responding may manifest in other ways than simply random responding for both behavioural tasks and self-report surveys.
+Indeed, in general there are more ways to respond carelessly than to respond attentively to a task or self-report inventory (e.g., random response selection, straight-lining, zig-zagging, side bias) \cite{curran2016methods}.
+Similarly, in the present work we observed that a win-stay lose-shift pattern emerged as a dominant strategy in the behavioral task among participants suspected of C/IE responding.
+As above, we posit that the specific strategy for responding that a participant adopts is likely to reflect the idiosyncratic integration of multiple perceived benefits (e.g.
+time saved, effort avoided) and costs (e.g.
+loss of performance bonuses, risk of detection and pay forfeited).
+As has been previously documented \cite{desimone2018dirty}, the presence of multiple response strategies makes it clear why certain screening measures are more or less likely to correlate.
+For example, the inter-item standard deviation and personal reliability measures are both sensitive to statistically random responding, but less sensitive to straight-lining.
+Most importantly, a diversity of heuristic response strategies highlights the need for many screening measures of C/IE responding, each sensitive to different heuristic strategies.
 
-Topic XX: Accidentally screening out participants of interest
+Here we have focused on the potential for C/IE responding to result in spurious symptom-behavior correlations when rates of symptom endorsement are low, a case common to online computational psychiatry research.
+Beyond this, we should emphasize that a diversity of heuristic response strategies entails that there is more than one mechanism by which spurious correlations can emerge.
+To the extent that a only mean-shift between attentive and careless participants is a prerequisite, this is not the only situation where one might expect spurious correlations to emerge \cite{huang2015insufficient}.
+For example, random responding on items with \emph{high} base-rate endorsement could yield spurious correlations with precisely the opposite pattern observed here.
+Conversely, an abundance of straight-lining may actually suppress correlations when symptom endorsement is low.
+In sum, without more understanding about the various types of heuristic responding and when each is likely to occur in a sample, it is difficult to predict a priori exactly what patterns of systematic bias may arise for a given study.
+This is further impetus for experimenters to be wary of C/IE responding and to use a variety of screening measures to detect it.
+
+One potential concern with performing rigorous screening (i.e., participant exclusion) based on C/IE detection methods is that we might inadvertently introduce an overcontrol bias \cite{elwert2014endogenous}.
+So far we have been treating a tendency towards C/IE responding as independent from psychopathology; however, to the extent that C/IE responding reflects lack of motivation \cite{barch2015mechanisms}, avoidance of effort \cite{cohen2001impairments, culbreth2016negative}, or more frequent lapses of attention \cite{kane2016individual, robison2017neurotic}, one might hypothesise an association between these two dimensions of individual differences.
+In such cases, it is plausible that rigorous screening of C/IE responding might lead to the differential exclusion of truly symptomatic participants.
+
+Although in theory this overcontrol bias may reduce power to detect legitimate symptom-behaviour correlations, for this to seriously impact results it would have to be the case that correlations were driven by symptomatic participants whose motivation or cognition were impacted to the extent that they frequently endorsed improbable or impossible responses to infrequency-item checks (e.g., responding `Agree' to ``I competed in the 1917 Olympic Games").
+We would argue that even if such participants truly are experiencing severe symptoms, there is likely to be limited utility in measuring these symptoms using a self-report measure that they are unable to complete veridically.
+A similar rationale underlies the widespread use of semi-structured interviews and other clinician-report measures rather than self-report measures for in-clinic psychiatric research.
+We would argue that, if the psychiatric phenomenon being studied is such that this issue warrants concern, the research question may be better suited to an in-person study design involving participants in the clinic who meet full diagnostic criteria than a correlational design involving an online convenience sample.
+
+Notwithstanding the above, one response to this legitimate concern is to advocate a graded approach to screening and excluding participants \cite{Kim2018-ev}.
+That is, participants should be screened with respect to a multitude of measures and only the most offending participants be removed, thereby reducing the risk of inducing bias.
+Alternatively, another possibility is to use sensitivity analysis as an alternative to exclusion, testing whether full-sample observed correlations are robust to the exclusion of participants flagged by measures of C/IE responding.
+We note that the more strict screening approach used in the present study did not preclude us from identifying symptomatic participants or behavior-symptom correlations.
+Indeed, we found in our sample roughly 10\% of participants endorsing symptoms consistent with clinical levels of depression, and approximately 20\% consistent with clinical levels of acute anxiety.
+These estimates are within the realm of epidemiological norms [citations].
+We also observed some positive correlations between anxiety and choice behavior that were consistent with effects found in previous literature [citations].
+For example, we found higher lose-shift rates and greater learning rates following negative prediction errors.
+This suggests that the screening methods employed here were not so aggressive as to attenuate behavior-symptom correlations that would be expected from the literature.
+
+There were several notable limitations to this proof-of-concept study.
+We used a small set of screening measures, and did not employ other recommended procedures (e.g.
+logging each key/mouse interaction during survey administration to detect form filling software or other forms of speeded responding \cite{buchanan2018methods}).
+Thus, we cannot be confident that all of the flagged participants were indeed engaging in C/IE responding; similarly, we cannot be certain that we correctly excluded all participants engaged in C/IE responding.
+We studied behavior-symptom correlations for only one task and a small self-report symptom battery.
+It remains to be seen how generalizable our findings are, although our study design was inspired by experiments prevalent in the online computational psychiatry literature.
+As suggested above, future studies may find greater correspondence between task and self-report screening measures for more difficult behavioral experiments.
+
+The present study highlights the need for future work on the prevalence of C/IE responding in online samples and its interactions with task-symptom correlations.
+Many open questions remain, including under what conditions might task and symptom screening measures better correspond, what screening measures are most effective and when, and under what conditions are spurious correlations more likely to arise.
+One especially pressing question is how sample size affects the likelihood of obtaining spurious correlations.
+The results of a bootstrapping analysis in our data suggest that false positive rates are likely to increase with increasing sample sizes, but this remains to be confirmed in future empirical work.
+As computational psychiatry studies move towards larger samples to characterize heterogeneity in symptoms (and to increase statistical power), it will be important to understand how sample size may exaggerate the effects of systematic error.
+
+In summary, moving forward we would strongly recommend that experimenters employ some form of self-report screening method, preferably one recommended by the best-practices literature (see Box 1 for a list of concrete recommendations).
+Our narrative review found that, to date, the majority of online studies assessing behavior-symptom correlations have not used self-report screening, and our results demonstrate that stand-alone task-behaviour screening is likely to be insufficient.
+Our results also demonstrate that inadequate screening is likely not merely to result in increased measurement error, as commonly assumed, but may also induce spurious correlations between behavioural task metrics and self-reported psychiatric symptom levels.
+For these reasons, we encourage experimenters to use a variety of data-quality checks for online studies and to be transparent in their reporting of how screening was conducted, how many participants are flagged under each measure, and what thresholds are used for rejection.
+
+More broadly, we encourage experimenters in computational psychiatry to be mindful of the myriad reasons why participants may perform worse on a behavioral task.
+Furthermore, we would encourage researchers wherever possible to design experiments where the signature of some symptomology is could not also be explained by C/IE responding (e.g.
+\cite{hunter2019excessive}).
+Finally, we conclude by noting that it is preferable to prevent C/IE responding than to account for it after the fact \cite{ward2018applying}.
+As such, we recommend researchers take pains to ensure their experiments are promote engagement, minimize fatigue and confusion, and pay fairly and ethically.
+
+%% BOX 1 %%
+\newpage
+\textbf{Box 1: Recommendations for future research}
+
+Here we offer several concrete recommendations for future research investigating symptom-behaviour correlations in online samples.
+
+\begin{itemize}
+
+    \item Use multiple screening methods to detect different types of C/IE responding.
+At a minimum, we recommend screening of both behavioral and self-report data.
+Within self-report data, we recommend using methods sensitive to multiple distinct patterns of C/IE responding (e.g., random responding, straight-lining, side bias) and, if possible, to log all page interactions.
+
+    \item When collecting self-report questionnaire data, include attention-check items that flag participants who may be engaging in C/IE responding.
+We would recommend following best-practice guidelines [citation] in using infrequency-item checks rather than instructed-item checks.
+Participants flagged by suspicious responses on attention-check items should either be excluded from further analysis, or assessed using sensitivity analyses to ensure that observed full-sample correlations are robust to their exclusion.
+
+    \item We found that spurious correlations predominantly affected self-report instruments for which the expected distributions of symptom scores were asymmetric (either positively or negatively skewed).
+As such, we would recommend that, \textit{ceteris paribus}, symmetrically-distributed measures of a given construct should be preferred to asymmetrically-distributed measures.
+Of course, given that the frequency of many psychiatric symptoms in the general population is itself positively skewed, this will not always be feasible.
+
+    \item Scales with reverse-coded items may be used to quantify the consistency of participants' responses between reverse-coded and non-reverse-coded measures of the same latent construct.
+With some care, this may be used to identify C/IE responding even for measures that do not include attention-check items \cite{emons2009detection}.
+Similarly, it may be beneficial to include multiple self-report surveys of the same construct to measure consistency across scales.
+
+    \item In our experience, we have found it instructive to occasionally review discussions on public forums for participants of online labour markets (e.g.
+Reddit, TurkerNation).
+Doing so helps an experimenter stay on top of what screening methods would-be participants are already aware of.
+Moreover, checking the forums is useful to ensure your research group is in good standing with the participant community and to better understand the labour platforms from participants' perspectives.
+
+    \item In general, it is preferable to prevent C/IE responding than to account for it after the fact \cite{ward2018applying}.
+As such, in designing studies, researchers should consider that confusion, fatigue, and low task motivation are likely to contribute to C/IE responding.
+In general, we would expect prolonged, fatiguing, confusing, or poorly-paid studies to be associated with more C/IE responding than brief, engaging, clear, and well-paid studies.
+
+    \item Consider whether the online methodology is truly appropriate for the research question.
+In particular, if the project studies syndromes associated with considerable difficulty in task or survey engagement (e.g., severe ADHD, acute mania), then high-symptom-endorsement participants are likely to produce responses that cannot be distinguished from C/IE responding.
+If this is a potential concern, then correlational research with online convenience samples is likely not the appropriate methodology for the research question.
+
+\end{itemize}
+
+This is not an exhaustive list, and one overarching recommendation is that researchers studying individual differences in psychiatric symptom endorsement should engage meaningfully with methodological research from the psychological measurement literature, where many of these questions have long been studied [citations].
+
+\newpage
+%% END BOX 1 %%
 
@@
 
+To characterize common data screening practices in online computational psychiatry studies, we performed a narrative literature review \cite{grant2009typology}.
+We identified studies for inclusion through searches on Google Scholar using permutations of query terms related to online labour platforms (e.g.
+"mechanical turk", "prolific", "online"), experimental paradigms (e.g.
+"experiment", "cognitive control", "reinforcement learning"), and symptom measures (e.g.
+"psychiatry", "mental illness", "depression").
+We included studies that (a) recruited participants online through a labour platform, (b) measured behaviour on at least one experimental task, and (c) measured responses on at least one self-report symptom measure.
+Through this approach, we identified for inclusion 49 studies spanning 2015 through 2020.
+
+Two of the authors (S.Z., D.B.) then evaluated whether and how each of these studies performed data quality screening for both the collected task and self-report data.
+Specifically, we confirmed whether a study had performed a particular type of data screening, where the categories were themselves chosen based on commonalities in methods which emerged across the studies.
+In addition, we assessed the total number of screening measures each study used and how monetary bonuses were paid to participants (if at all).
+The fully annotated review of studies can be found in the Github repository for this project (\url{github.com/nivlab/silver-screen}).
+Finally, we note that this review was not meant to be systematic, but instead to provide a representative overview of common practices in online behavioral studies.
+
 \subsection{Experiment}
@@
 
-409 total participants were recruited to participate in an online behavioral experiment in May, 2020.
+409 total participants were recruited to participate in an online behavioral experiment in late June - early July, 2020.
 Specifically, 208 participants were recruited from Amazon Mechanical Turk (MTurk) and 201 participants were recruited from Prolific.
@@
 Total study duration was approximately 10 minutes per participant.
-Participants received monetary compensation for their time (rate \$12/hr), plus an incentive-compatible bonus based on task performance.
+Participants received monetary compensation for their time (rate USD \$12/hr), plus an incentive-compatible bonus up to \$0.25 based on task performance.
 
-Participants from Mechanical Turk were recruited with the aid of CloudResearch services and were eligible if they resided in the United States or Canada.
-Following recent recommendations, Mechanical Turk workers were not excluded based on HIT approval rate or number of HITs approved.
-Participants from Prolific were similarly eligible if they resided in the United States.
+Participants were eligible if they resided in the United States or Canada; participants from MTurk were recruited with the aid of CloudResearch services \cite{litman2017turkprime}.
+(Note: This study was conducted prior to the introduction of Cloudresearch's new data quality filters \cite{cloudresearch_2020}).
+Following recent recommendations \cite{robinson2019tapped}, MTurk workers were not excluded based on work approval rate or number of previous jobs approved.
 No other exclusion criteria were applied during recruitment.
@@
 The data from multiple participants who completed the experiment were excluded prior to analysis.
-Three participants (all Mechanical Turk) were excluded due to missing data.
-In addition, 20 participants were excluded for having previously completed the experiment on the other platform (MTurk: N=19, Prolific: N=1).
+Three participants (all MTurk) were excluded due to missing data.
+In addition, we excluded 20 participants who disclosed that they had also completed the experiment on the other platform (MTurk: N=19, Prolific: N=1).
 This left a final sample of N=386 participants (MTurk: N=186, Prolific: N=200) for analysis.
-The demographics of the sample split by labor market is provided in Table S1.
+The demographics of the sample split by labour market is provided in Table S1.
 Notably, the participants recruited from MTurk were older ($M = 7.7 \ \text{yrs}, t = 6.567, p < 0.001$) and comprised of fewer women ($z = 6.567, p = 0.011$).
@@
 When chosen, the dominant option yielded reward with 80\% probability; the subordinate options yielded reward with only 20\% probability.
-Importantly, dominant option changed every 15 trials.
+The dominant option changed randomly to one of the two previously subordinate options every 15 trials.
 Participants completed 90 trials of the task (1 learning block, 5 reversal blocks).
 
-As a cover story, the probabilistic reversal learning task was introduced to participants as a fishing game.
-In the game, each choice option was a beach scene made distinguishable by a colored surfboard with unique symbol.
+As a cover story, the probabilistic reversal learning task was introduced to participants as a fishing game in which each choice option was a beach scene made distinguishable by a colored surfboard with unique symbol.
 Participants were told they were choosing which beach to fish at.
@@
 
-The task was programmed in jsPsych and distributed using custom web-application software. Both the experiment code and
+The task was programmed in jsPsych \cite{deleeuw_2015_jspsych} and distributed using custom web-application software.
+Both the experiment code (\url{github.com/nivlab/ThreeArmJS}) and web-software (\url{github.com/nivlab/nivturk}) are publicly available.
 
-\subsubsection{Self-Report Measures}
+\subsubsection{Symptom Measures}
 
-Prior to completing the reversal learning task, participants completed 5 self-report symptom measures.
-The symptom measures were selected for inclusion based on their frequency in clinical research and for having an assorted range of response distributions (e.g.
-symmetric, right-skewed, left-skewed).
+Prior to completing the reversal learning task, participants completed five self-report symptom measures.
+The symptom measures were selected for inclusion based on their frequency in clinical research, and for having an expected mixture of symmetric and asymmetric score distributions.
 
-\textbf{Seven-Up/Seven-Down}: The Seven-Up/Seven-Down (7u/7d) scale is a 14-item measure of manic and depressive tendencies.
-It is an abbreviation of the General Behavior Inventory, wherein only items that maximally discriminated between depression and mania were included.
-It has good psychometric properties and predictive validity.
-Items are scored on 4-point scale from 0 (Never or hardly ever) to 3 (Very often; almost constantly).
-Total scores on both subscales are usually strongly right-skewed, with few participants exhibiting moderate to high levels of symptom endorsement.
+\textbf{Seven-Up/Seven-Down}: The Seven-Up/Seven-Down (7u/7d; \cite{youngstrom_2013_susd}) scale is a 14-item measure of lifetime propensity towards depressive and hypomanic symptoms.
+It is an abbreviation of the General Behavior Inventory \cite{depue1981behavioral}, wherein only items that maximally discriminated between depression and mania were included.
+Items are scored on a 4-point scale from 0 ("Never or hardly ever") to 3 ("Very often or almost constantly").
+Total symptom scores on both subscales range from 0 to 21, and are usually strongly right-skewed, with few participants exhibiting moderate to high levels of symptom endorsement.
 
-\textbf{Generalized Anxiety Disorder-7}: the Generalized Anxiety Disorder-7 (GAD-7) is a 7-item measure of general anxiety.
-It has good psychometric properties in primary care settings and in the general population.
+\textbf{Generalized Anxiety Disorder-7}: the Generalized Anxiety Disorder-7 (GAD-7; \cite{spitzer2006brief}) is a 7-item measure of general anxiety.
 The GAD-7 assesses how much a respondent has been bothered by each of seven core anxiety symptoms over the last 2 weeks.
-Items are scored on 4-point scale from 0 (not at all) to 3 (nearly every day).
-Total scores on the GAD-7 are usually right-skewed, with few participants exhibiting moderate to high levels of symptom endorsement.
+Items are scored on a 4-point scale from 0 ("not at all") to 3 ("nearly every day").
+Total scores on the GAD-7 range from 0 to 21, and are usually right-skewed, with few participants exhibiting moderate to high levels of symptom endorsement.
 
-\textbf{Behavioral Inhibition/Behavioral Activation Scales}: the Behavioral Inhibition and Behavioral Activation Scales (BIS/BAS) are a measure of approach and avoidance motivations.
-The original 42-item measure was recently abbreviated to a 14-item measure, which we use here.
+\textbf{Behavioral Inhibition/Behavioral Activation Scales}: the Behavioral Inhibition and Behavioral Activation Scales (BIS/BAS; \cite{carver1994behavioral}) are a measure of reward and punishment sensitivity.
+The original 42-item measure was recently abbreviated to a 14-item measure \cite{pagliaccio2016revising}, which we use here.
+Items are scored on a 4-point scale from 1 ("very true for me") to 4 ("very false for me").
+We note that in order to maintain consistency with the other symptom measures, the order of the BIS/BAS response options was reversed during administration such that "very false for me" and "very true for me" were the left- and rightmost anchors, respectively.
 
-\textbf{Snaith-Hamilton Pleasure Scale}:
+\textbf{Snaith-Hamilton Pleasure Scale}: the Snaith-Hamilton Pleasure Scale is a 14-item measure of anhedonia \cite{snaith1995scale}.
+Items are scored on a 4-point scale from 0 ("strongly agree") to 3 ("strongly disagree"), where higher scores indicate greater pathology.
+Items are typically binarized before scoring (either disagree response receives a score of 1), and total symptom scores of 3 or greater indicate pathology.
+More recent research, however, has suggested using the sum of unthresholded scores instead \cite{franken2007assessment}.
+Here we present the unthresholded symptom scores, except for when we compute the fraction of participants meeting clinical threshold for which we use the binarized measure.
 
-\textbf{Penn State Worry Questionnaire}:
+\textbf{Penn State Worry Questionnaire}: the Penn State Worry Questionnaire is a measure of worry symptoms \cite{meyer1990development}.
+The original 16-item was recently abbreviated to a 3-item measure \cite{kertz2014psychometric}, which we use here.
+Items are scored on a 5-point scale from 1 ("not at all typical of me") to 5 ("very typical of me"), where higher scores indicate greater pathology.
+Total symptom scores range from 1 to 15 and are usually uniformly distributed.
 
@@
 
-To measure the correspondence of task- and self-report-based screening metrics, we estimated a number of standard measures of data quality from each participant's task and self-report behavior.
-Beginning first with the self-report data, we included five common measures of data quality, each described below.
+To measure the correspondence of task- and self-report-based screening measures, we estimated a number of standard measures of data quality from each participant's task behaviour (four in total) and self-report responses (five in total).
+Beginning first with the self-report data, we describe each below.
 
-\textbf{Infrequency items}: We embedded four infrequency items across the self-report measures.
-The infrequency items were questions that should have only one response.
-We measured the number of suspicious responses made by each participant.
-For thresholded analyses, participants were flagged if they responded incorrectly to any of these items.
+\subparagraph{Infrequency items}
 
-\textbf{Inter-item standard deviation}: The inter-item standard deviation (ISD) is an intrapersonal measure of response variability. For a given subscale $j$, the ISD is defined as:
+Infrequency items are questions for which all or virtually all attentive participants should provide the same response.
+We embedded four infrequency items across the self-report measures.
+Specifically, we used the following questions:
+
+\begin{enumerate}
+  \item Over the last two weeks, how much time did you spend worrying about the 1977 Olympics? 
+  \item Have there been times of a couple days or more when you were able to stop breathing entirely (without the aid of medical equipment)?
+  \item I would feel bad if a loved one unexpectedly died.
+  \item I would be able to lift a 1 lb (0.5 kg) weight.
+\end{enumerate}
+
+Prior to conducting the study, the infrequency items were piloted on an independent sample of participants to ensure that they elicited one dominant response.
+In the main study, we measured the number of suspicious responses made by each participant to these questions.
+For thresholded analyses, participants were flagged if they responded incorrectly to one or more of these items.
+
+\subparagraph{Inter-item standard deviation} The inter-item standard deviation (ISD) is an estimate of a participant's response consistency on a self-report measure \cite{marjanovic2015inter}, defined as:
 
 \begin{equation*}
-    ISD_j = \sqrt{\frac{\sum^k_{j=1}(x_j - \bar{x_i})^2}{k-1}}
+    ISD = \sqrt{\frac{\sum^k_{i=1}(y_j - \bar{y})^2}{k-1}}
 \end{equation*}
 
-where $x_j$ is a participant's response to item $j$, $x_i$ is a respondent's average score across all scale items, and $k$ is the total number of scale items.
-The ISD measures the level of dispersion around a participant's average response, and has previously been shown to be sensitive to C/IE responding.
-A composite ISD was computed per participant by summing across each individual subscale.
+where $y_i$ is a participant's response to item $i$, $x_i$ is a participant's average score across all  items, and $k$ is the total number of items for a self-report measure.
+A composite ISD measure was estimated per participant by summing across each of the seven self-report scales.
+Larger ISD values indicate lower response consistency.
 
-\textbf{Personal reliability}: The personality reliability coefficient was computed by correlating the average score of random split-halves of items for each subscale.
-1000 random split-halves were computed per subscale and participant.
-A composite score was computed per participant by summing across each individual subscale.
-Lower scores indicate greater response inconsistency.
+\subparagraph{Personal reliability}
 
-\textbf{Mahalanobis D}: The Mahalanobis distance is an outlier detection method. For a participant $i$, the Mahalanobis D is defined as:
+The personal reliability coefficient is an estimate of a participant's response consistency on a self-report measure, estimated by correlating the average scores from split-halves of their responses.
+To avoid any item-order bias, a participant's personal reliability coefficient for a particular self-report measure was computed from the average correlation from 1000 random split-halves.
+A composite reliability measure was generated per participant by averaging across each of the seven self-report scales.
+Smaller reliability coefficients indicate lower response consistency.
+\subparagraph{Mahalanobis D} The Mahalanobis distance is a multivariate outlier detection measure, which estimates how dissimilar a participant is relative to all others.
+For a participant $i$, the Mahalanobis D is defined as:
 
@@
 where $(X_i - \bar{X})$ represents the vector of mean-centered item responses for participant $i$ and $\Sigma^{-1}_{XX}$ represents the inverted covariance matrix of all items.
-s.
-Larger deviation from the normative response pattern yields higher D values and is considered a potential indicator of C/IE responding.
-A single $D$ statistic was computed for each of the participants using all self-report items.
+Greater Mahalanobis D values indicate larger deviations from the average pattern of responding.
 
-\textbf{Response Time}: One checks were based on time measurements, with a reading-speed threshold of 10 words per second (Sisso, 2019).
+\subparagraph{Reading Time} The reading time is the total number of seconds spent filling out a particular self-report measure, adjusted for that measure's total number of items \cite{ophir2020turker}.
+A total reading time estimate was estimated for each participant by summing across the adjusted time for each of the seven self-report measures.
+Shorter scores are indicative of less time having been spent on each item.
 
-In addition, four measures of data quality were computed from the task behavior data. These are described in turn below.
+\subparagraph{Variability} Choice variability was defined as the fraction of trials of the most used response option per participant.
+Choice variability could range from 0.33 (all response options used equally) to 1.00 (only one response option used).
+Values closer to 1.00 are indicative of more careless responding during the task.
 
-\textbf{Variability}:
+\subparagraph{Accuracy} Choice accuracy was defined as the fraction of choices of the reward-maximizing response option.
+For a task with 90 trials and three response options, a one-tailed binomial test at $\alpha=0.05$ reveals chance-level performance to be 37 or fewer correct choices (41\%).
+Lower accuracy values are indicative of more inattentive responding during the task.
 
-\textbf{Accuracy}:
+\subparagraph{Win-Stay Lose-Shift} Win-stay lose-shift (WSLS) measures a participant's tendency to stay with a choice option following a reward versus shifting to a new choice option following a non-reward.
+WSLS thus measures a participant's sensitivity to reward feedback on the screen.
+WSLS was estimated per participant via regression, where the current choice (stay, switch) predicted by the previous trial's outcome (reward, non-reward) and a stationary intercept.
+Here we used the first (slope) term to represent a participant's WSLS tendency.
+Lower values of this term indicate less sensitivity to reward feedback and are thus indicative of more careless responding during the task.
 
-\textbf{Win-Stay Lose-Shift}:
+\subparagraph{Response Times} Suspicious response time was defined as the proportion of trials with an outlier response time, here measured as responses faster than 200ms.
+Greater proportions of outlier response times are indicative of more careless responding during the task.
 
-\textbf{Response Times}:
+\subparagraph{Correspondence Analysis} We measured the correspondence of the above screening measures via two complimentary approaches.
+First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation.
+Second, we estimated the pairwise rate of agreement on the binarized measures using the Dice similarity coefficient (looking at the top 10\% and 25\% most suspicious respondents for each measure).
+The former approach estimates two measures monotonic association, whereas the latter approach estimates their agreement as to which participants were most likely engaging in C/IE responding.
+For significance testing, we used permutation testing wherein a null distribution of similarity scores (i.e.
+Spearman's correlation, Dice coefficient) was generated for each pair of screening measures by iteratively permuting participants' identities within measures and re-estimating the similarity.
+P-values were computed by comparing the observed score to its respective null distribution.
+We corrected for multiple comparisons using family-wise error rates \cite{winkler2014permutation}.
 
-In three analyses, we measured the correspondence of the metrics above.
-In the first analysis, the similarity of the unthresholded (continuous) metrics were computed via pairwise Spearman correlations.
-For significance testing, we performed a permutation test with 5000 null shuffles and corrected for multiple comparisons using family-wise error rates.
-In the second and third analyses, the similarity of the thresholded metrics were computed via pairwise Dice coefficients.
-The metrics were thresholded taking the top 25\% and 10\% worst respondents for each metric.
-For significance testing, we again performed a permutation test with 5000 null shuffles and corrected for multiple comparisons using family-wise error rates.
+\subsubsection{Correlations between behaviour and symptom measures}
+
+To quantify the effects of both task and self-report data screening on behavior-symptom correlations, we estimated the pairwise correlations between the symptom scores of each of the self-report measures and several measures of performance on the reversal learning task.
+For each participant, we computed both descriptive and model-based measures of behaviour on the reversal learning task.
+We describe each in turn below.
+
+\subparagraph{Descriptive measures} Descriptive task measures included the following: accuracy, or the proportion of choices of the reward-maximizing response option; points, or the total number of points accumulated over the game; win-stay rate, or the fraction of trials on which a participant stayed with the previous choice option following a reward; lose-stay rate, or the fraction of trials on which a participant switched from the previous choice option following a non-reward; and perseveration, or the number of trials on which a participant chose the previously reward-maximizing response option following a reversal.
+
+\subparagraph{Model-based measures} The model-based measures were derived from a common reinforcement learning model of choice behavior, i.e.
+the risk-sensitive temporal difference learning model \cite{niv2012neural}.
+In this model, the expected value of a choice option, $Q(s)$, is learned through cycle of choice and reward feedback.
+Specifically, following a decision and reward feedback, the value of the chosen option is updated according to:
+
+\begin{equation*}
+    Q_{t+1}(s) = Q_{t}(s) + \eta \cdot \delta_{t}
+\end{equation*}
+
+where $\eta$ is the learning rate bounded in the range $[0,1]$ (controlling the extent to which value reflects the most recent outcomes) and $\delta$ is the reward prediction error, defined as:
+
+\begin{equation*}
+    \delta_t = r_t - Q_{t}(s)
+\end{equation*}
+
+In the risk-sensitive temporal difference learning model, there are separate learning rates for positive and negative prediction errors, such that positive and negative prediction errors have asymmetric effects on learning.
+For example, the effect of negative prediction errors on learned values is larger than that of positive errors if $\eta^+ < \eta^-$, and vice versa if $\eta^+ > \eta^-$.
+
+Finally, decision-making according to the model is dictated by a softmax choice rule:
+
+\begin{equation*}
+    p(y_t = s) = \frac{\exp \left( \beta \cdot Q(s) \right)}{\sum_i^S \exp \left( \beta \cdot Q(s) \right)}
+\end{equation*}
+
+where $\beta$ is the inverse temperature, controlling a participant's sensitivity to the expected value of the choice options.
+
+In sum then, the model-based approach describes a participant's choice behavior as a function of three parameters ($\beta, \eta^+, \eta^-$).
+These parameters were estimated within a Bayesian framework using Hamiltonian Monte Carlo as implemented in Stan (v2.25) \cite{stan}.
+Four separate chains with randomised start values each took 2000 samples from the posterior.
+The first 1500 samples from each chain were discarded.
+As a result, 2000 post-warmup samples from the joint posterior were retained.
+The $\hat{R}$ values for 98\% of parameters was less than 1.1, indicating acceptable convergence between chains, and there were no divergent transitions in any chain.
+Participant parameters were fit individually (i.e.
+not hierarchically) so as to prevent in parameter estimation any bias via partial-pooling between participants responding attentively versus carelessly.
+Parameters were sampled using non-centred parameterisations (i.e., all parameters were sampled separately from a unit normal before being transformed to the appropriate range).
+Of note, the learning rates were estimated via an offset method such that $\eta^+ = \eta + \kappa$ and $\eta^- = \eta - \kappa$, where $\kappa$ is an offset parameter controlling the extent of an asymmetry between the two learning rates.
+This parameter was also entered into the behaviour-symtom correlational analyses.
+Full Stan code for all models is available in the Github repository for this project (\url{github.com/nivlab/silver-screen}).
+
+\subparagraph{Correlational analysis} Behaviour-symptom correlations (after various forms of screening and exclusion) were estimated using Spearman's rank correlation.
+Significance testing was performed using the percentile bootstrap method \cite{wilcox2018guide} so as to avoid making any parametric assumptions.
+The correlational analyses were not corrected for multiple comparisons, as the intended purpose here is to emulate a conventional analysis where fewer statistical tests would be performed, as dictated by one's hypotheses.
+
+\subsubsection{Theory-agnostic choice analysis} In the final analysis, we use a theory-agnostic modeling approach to characterize the choice behavior of attentive participants and those suspected of C/IE responding.
+To do so, we adapted the softmax regression model from \cite{seymour2012serotonin}.
+The softmax regression model estimates the influence of the history of past rewards, non-rewards, and choices on a participant's current choice.
+
+Specifically, the influence of the history of particular type of event is defined as:
+
+\begin{equation*}
+    \sum_i^K w = x_{t-1} \cdot w_{t-1} + x_{t-2} \cdot w_{t-2} +  \ldots + x_{t-k} \cdot w_{t-k}
+\end{equation*}
+
+where $x_{t-i}$ is a binary indicator (0,1) denoting if an event (i.e.
+reward, non-reward, previous choice) occurred on trial $t-i$ and $w_{t-1}$ is the associated decision weight.
+These weights were estimated for rewards, non-rewards, and previous choices up to five trials in the past.
+
+The overall tendency to choose a particular choice option is dictated by a softmax choice rule:
+
+\begin{equation*}
+    p(y_t = i) = \frac{ \exp \left( \sum w_i^\text{reward} + \sum w_i^\text{nonreward} + \sum w_i^\text{choice} \right) }{ \sum_i \exp \left( \sum w_i^\text{reward} + \sum w_i^\text{nonreward} + \sum w_i^\text{choice} \right) }
+\end{equation*}
+
+Note that these weights were fit independently; that is, we did not employ an exponential kernel to parameterize the decay of the weights at successively distant trial lags.
+
+In sum then, the theory-agnostic model describes a participant's choice behavior as a function of 15 parameters.
+These parameters were estimated within a Bayesian framework using Hamiltonian Monte Carlo as implemented in Stan (v2.25) \cite{stan}.
+Four separate chains with randomised start values each took 2000 samples from the posterior.
+The first 1500 samples from each chain were discarded.
+As a result, 2000 post-warmup samples from the joint posterior were retained.
+The $\hat{R}$ values for all parameters was less than 1.1, indicating acceptable convergence between chains, and there were no divergent transitions in any chain.
+Participant parameters were fit individually (i.e.
+not hierarchically) so as to prevent in parameter estimation any bias via partial-pooling between participants responding attentively versus carelessly.
+Parameters were sampled with Gaussian priors with $\mu = 0$ and $\sigma = 5$.
+Full Stan code for all models is available in the Github repository for this project (\url{github.com/nivlab/silver-screen}).
+
+\printbibliography
 
@@
 \section{Supplement}
+\setcounter{table}{0}
+\renewcommand{\thetable}{S\arabic{table}}
 
-\begin{table}
+\subsection{Participant Demographics}
+
+\begin{table}[!h]
 \centering
+\small
 \setlength{\tabcolsep}{15pt}
@@
 \midrule
-*Use other platform & N & \% & N & \% \\
+Use other platform & N & \% & N & \% \\
 \cmidrule(lr){1-5}
@@
 \end{tabular}
-\caption{The demographics of each sample by online labor market.
+\caption{The demographics of each sample by online labour market.
 On average, the samples were similar though the sample from Mechanical Turk was older (t = 6.567, p $<$ 0.001) and comprised of fewer women (z = 6.567, p = 0.011).
-*Note: the demographics do not include 20 participants (MTurk: N=19; Prolific: N=1) excluded for participating in the study twice, once per platform.}
+Note: the demographics do not include 20 participants (MTurk: N=19; Prolific: N=1) excluded for participating in the study twice, once per platform.}
 \label{tab:demographics}
@@
 
-% \bibliography{main}
+\subsection{Task Instructions}
+
+The following are the instructions given to participants for the probabalistic reversal learning task.
+As a reminder, the task was given a fishing-themed cover story.
+Each paragraph below denotes one screen of instructions.
+
+\textit{Welcome to the fishing game! We will now give you some instructions on how to play the game. Use the buttons below (or the arrow keys) to navigate the instructions.}
+
+\textit{In the fishing game, there are three beaches you can fish at.
+Each beach has its own unique surfboard.
+(The colors and pictures on the surfboards are there just to help you tell the beaches apart – they don’t have any special meaning other than that.)}
+
+\textit{On each turn you will be shown three beaches, and you will choose which one you want to fish at. You can make your choice using the left, up, and right arrow keys.}
+
+\textit{When you fish at a beach, you will either catch a fish or you will catch trash. Try to catch fish, and try not to catch trash!}
+
+\textit{Some beaches are better than others.
+You are more likely to catch fish at some beaches (though you will still sometimes catch trash), and you are more likely to catch trash at other beaches (though you still sometimes catch fish).}
+
+\textit{The beaches will change over time. As times goes by, you may be less likely to catch fish at a beach where you were previously catching many fish.}
+
+\textit{Your goal is to catch as many fish as you can. You will receive a performance bonus up to \$0.25 that depends on how many fish you catch.}
+
+\textit{Now we will ask you some questions about the game.
+You must answer all questions correctly to proceed.
+Feel free to read back through the instructions if there is anything you are not certain about.}
+
+Following the instructions, participants completed a brief comprehension check where they were asked the following questions about the task:
+
+\begin{enumerate}
+    \item True or False: Your goal is to catch as many fish as you can. (True)
+    \item True or False: You are more likely to catch fish at some beaches than others. (True)
+    \item True or False: You will always catch fish at the best beach. (False)
+    \item True or False: How likely you are to catch a fish at a beach stays the same over time. (False)
+    \item True or False: The number of fish you catch will affect your final performance bonus. (True)
+\end{enumerate}
+
+Participants were required to answer all of the items correctly before they could proceed to the task.
+If they failed to do so, they restarted the instructions.
+There was no upper limit as to how many times a participant could loop through the instructions (the large majority of participants passed the comprehension check on their first try).
+
+\subsection{Correspondence of screening measures}
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{rccccccccc}
+\toprule
+{} &      INF &      ISD &      REL &      MAH &    READ &     VAR &     ACC &   WSLS & RT \\
+\midrule
+INF  &        - &          &          &          &         &         &         &        &    \\
+ISD  &   0.372* &        - &          &          &         &         &         &        &    \\
+REL  &  -0.408* &  -0.811* &        - &          &         &         &         &        &    \\
+MAH  &   0.406* &   0.843* &  -0.643* &        - &         &         &         &        &    \\
+READ &   -0.111 &   0.193* &  -0.168* &    0.138 &       - &         &         &        &    \\
+VAR  &   -0.061 &   -0.029 &    0.058 &   -0.024 &  -0.026 &       - &         &        &    \\
+ACC  &  -0.206* &   -0.154 &    0.099 &  -0.182* &  -0.074 &   0.027 &       - &        &    \\
+WSLS &    0.060 &    0.102 &   -0.089 &    0.115 &   0.103 &  -0.060 &  0.221* &      - &    \\
+RT   &    0.040 &   -0.019 &    0.014 &    0.013 &  -0.158 &  -0.007 &  -0.094 &  -0.05 &  - \\
+\bottomrule
+\end{tabular}
+\caption{Spearman correlation of measures}
+\end{table}
 

### 2021-03-29 manuscripts/main.tex
checkpointing progress

@@
 \author[1]{Samuel Zorowitz}
-\author[1,2]{Daniel Bennett}
-\author[1,3]{Yael Niv}
+\author[1,2]{Yael Niv}
+\author[1,3]{Daniel Bennett}
 \affil[1]{Princeton Neuroscience Institute, Princeton University, USA}
-\affil[2]{Department of Psychiatry, Monash University, Australia}
-\affil[3]{Department of Psychology, Princeton University, USA}
+\affil[2]{Department of Psychology, Princeton University, USA}
+\affil[3]{Department of Psychiatry, Monash University, Australia}
 
 % specify the title
-\title{Inattentive responding can induce spurious associations between task behaviour and symptom measures}
+\title{Inattentive responding can induce spurious associations between task behavior and symptom measures}
 
@@
 \begin{document}
+%TC:ignore
 
@@
 % make abstract
-\abstract{Abstract}
+\abstract{
+A common research design in the field of computational psychiatry involves leveraging the power of online participant recruitment to assess correlations between behaviour in cognitive tasks and the self-reported severity of psychiatric symptoms in large, diverse samples.
+Although large online samples have many advantages for psychiatric research, some potential pitfalls of this research design are not widely understood.
+Here we detail circumstances in which entirely spurious correlations may arise between task behaviour and symptom severity as a result of inadequate screening of careless or low-effort responding on psychiatric symptom surveys.
+Specifically, since many psychiatric symptom surveys have asymmetric ground-truth score distributions in the general population, participants who respond carelessly on these surveys will show apparently elevated symptom levels.
+If these participants are similarly careless in their task performance, and are not excluded from analysis, this may result in a spurious association between greater symptom scores and worse behavioural task performance.
+Here, we demonstrate exactly this pattern of results in $N = 386$ participants recruited online to complete a self-report symptom battery and a short reversal-learning choice task.
+We show that many behaviour-symptom correlations are entirely abolished when participants flagged for careless responding on surveys are excluded from analysis.
+We also show that exclusion based on task performance alone is not sufficient to prevent these spurious correlations.
+Of note, we demonstrate that false-positive rates for these spurious correlations \emph{increase} with sample size, contrary to common assumptions.
+We offer guidance on how researchers using this general experimental design can guard against this issue in future research; in particular, we recommend the adoption of screening methods for self-report measures that are currently uncommon in the field.
+}
 
@@
 \setlength{\parskip}{1em}
+
+%TC:endignore
 
@@
 Since participants recruited from online labour markets are typically completing experiments in their homes, they may be more likely to be distracted or multi-tasking during an experiment.
-Similarly, unsupervised participants may be more likely to use careless/insufficient effort (C/IE) response strategies with the intention to minimise expenditure of time and cognitive effort (e.g., responding randomly on self-report surveys or behavioural tasks).
+Similarly, unsupervised participants may be more likely to use heuristic response strategies with the intention to minimise expenditure of time and cognitive effort (e.g., responding randomly on self-report surveys or behavioral tasks).
+Here, we will refer to such inattentive or low-effort behaviors as careless/insufficient effort (C/IE) responding \cite{huang2012detecting, curran2016methods}.
 Among researchers using online labour markets, a common view is that poor-quality data resulting from C/IE responding can simply be treated as a source of unsystematic measurement error that can be overcome with increased sample sizes \cite{gillan2016taking, chandler2020participant}.
-Similarly, it is common practice in online behavioural research to mitigate poor-quality data using the same screening methods that are typically used in in-person data collection (e.g., excluding participants who perform at- or below-chance on behavioural tasks).
+Similarly, it is common practice in online behavioral research to mitigate poor-quality data using the same screening methods that are typically used in in-person data collection (e.g., excluding participants who perform at- or below-chance on behavioral tasks).
 
 Here we wish to draw attention to an underappreciated feature of online psychiatric research using self-report symptom surveys.
-In such surveys, participants rate their endorsement of various psychiatric symptoms and, since most individuals in the general population tend to endorse no or few symptoms in many symptom domains, the resulting ground-truth symptom distributions tend to be heavily positively skewed.
+In such surveys, participants rate their endorsement of various psychiatric symptoms and, since most individuals in the general population tend to endorse no or few symptoms in many symptom domains, the resulting ground-truth symptom distributions tend to be heavily positively skewed \cite{lowe2008validation, tomitaka2018distributional}.
 In this situation, the assumption that C/IE responding merely increases unsystematic measurement noise becomes untenable.
 Because of the positive skew in the ground-truth symptom distribution, participants who respond carelessly to the symptom survey are more likely to report higher levels of symptom endorsement relative to participants who complete the survey accurately \cite{chandler2020participant, ophir2020turker}.
-Consequently, unless C/IE survey responses are carefully identified and removed, a considerable proportion of putatively symptomatic individuals in an online sample may, in fact, be participants who have not engaged with the experiment with sufficient effort.
-
-When participants complete both symptom surveys and behavioral tasks (a common study design in computational psychiatry), this artefact has the potential to induce spurious correlations between symptom self-reports and task behavior.
-Concretely, if the same participants who engage in C/IE responding on surveys (and who therefore inaccurately report high levels of psychiatric symptoms) also respond carelessly on behavioral tasks, then we would expect to observe an entirely spurious correlation emerge between greater symptom severity and worse task performance (see Figure \ref{fig:simulation}).
-A similar effect has been well documented in personality psychology, where the presence of careless respondents can induce correlations between questionnaires and bias estimated factors in factor analysis \cite{huang2012detecting, robinson2014inaccurate, huang2015insufficient, chandler2020participant, arias2020little}.
-To our knowledge, however, the potential for C/IE responding to induce spurious correlations between symptom endorsement and task behavior has not previously been noted in the burgeoning field of computational psychiatry.
+Consequently, unless C/IE survey responses are carefully identified and removed, a considerable proportion of putatively symptomatic individuals in an online sample may, in fact, be participants who have not engaged with the experiment with sufficient attention or effort.
+
+When participants complete both symptom surveys and behavioral tasks---a common study design in computational psychiatry---this artefact has the potential to induce spurious correlations between symptom self-reports and task behavior.
+That is, while C/IE behavior is traditionally thought of as a source of noise that can result in type II (false negative) errors, here we suggest that in large-scale online psychiatric studies it can instead result in type I (false positive) errors.
+Concretely, if the same participants who engage in C/IE responding on surveys (and who therefore inaccurately report high levels of psychiatric symptoms) also respond with insufficient effort on behavioral tasks, this can cause experimenters to observe an entirely spurious correlation between greater symptom severity and worse task performance (see Figure \ref{fig:simulation}).
+A similar effect has been well documented in personality psychology, where the presence of C/IE responding can induce correlations between questionnaires, and bias estimated factors in factor analysis \cite{huang2012detecting, robinson2014inaccurate, huang2015insufficient, chandler2020participant, arias2020little}.
 
@@
 \centering
-\caption{Caption TK here}
+\captionsetup{width=0.88\textwidth}
+\caption{Simulated example of how spurious behavior-symptom correlations can arise when symptom endorsement is rare.
+\textit{Left:} When symptoms are moderately common in the general population, C/IE respondents (blue) are indistinguishable from attentive participants (red) in self-report measures (x-axis, marginal distribution shown on top).
+Despite the lower task performance of C/IE respondents (y-axis), no correlation arises between symptom scores and task performance (dots are participants drawn from the shown distributions, with \~15\% C/IE participants; dashed line shows the (lack of) correlation.) \textit{Right:} When symptoms are rare in the general population, careless respondents appear symptomatic in self-report measures.
+As a result, self-report symptom scores show a significant correlation with task performance.}
 \label{fig:simulation}
@@
 
-Here we demonstrate the real risk that C/IE responding can lead to spurious symptom-task correlations in computational psychiatry research.
-First, we asked to what extent researchers in computational psychiatry screen self-report data from online samples.
-We found that the majority of these studies did not screen participants' survey data at all, and that very few followed best-practice recommendations for survey data screening.
-We then asked whether behavioural screening alone was sufficient to identify participants engaging in C/IE responding on psychiatric symptom surveys.
-In a new dataset from two separate online labour marketplaces, we found that screening based on task behaviour fails to adequately identify participants engaging in C/IE responding on surveys.
+Here, we demonstrate the real risk that C/IE responding can lead to spurious symptom-task correlations in computational psychiatry research.
+First, we asked to what extent recent studies in computational psychiatry screen participants based on self-report symptom data.
+We found that the majority of these studies did not screen participants' survey data at all, and that very few followed best-practice recommendations for survey data screening \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}.
+We then asked whether behavioral screening alone was sufficient to identify participants engaging in C/IE responding on psychiatric symptom surveys.
+In a new dataset from two separate online labour marketplaces, we found that screening based on task behavior fails to adequately identify participants engaging in C/IE responding on surveys.
 Lastly, we investigated whether, under these circumstances, C/IE responding led to spurious correlations between symptom severity and task performance for positively-skewed symptom measures.
-Consistent with the logic set out above, we confirmed that failure to appropriately screen out C/IE survey responding in the proof-of-concept dataset that we collected would have produced a number of spurious correlations between task behaviour and self-reported symptoms of depression and anxiety.
+Consistent with the logic set out above, we confirmed that failure to appropriately screen out C/IE survey responding in the proof-of-concept dataset that we collected would have produced a number of spurious correlations between task behavior and self-reported symptoms of depression and anxiety that are abolished when data are screened properly.
 
@@
 
-When the rate of symptom endorsement is low in the general population, participants who engage in C/IE responding on self-report symptom measures may appear as putative symptomatic individuals.
-If the same participants also perform a behavioural task with insufficient effort, they may in turn induce spurious correlations between measures of task behavior and self-report symptoms.
-The risk for erroneous inferences, however, is attenuated if experimenters identify and remove those participants.
-As such, it is imperative for researchers to screen for C/IE responding in their data.
-The extent to which experimenters evaluate the quality of both the task and self-report data they collect is unclear.
-We suspect that whereas screening of task data is standard practice, the screening of self-report data is far less prevalent in online human behavioral research.
-
-To test the empirical support for this claim, we performed a narrative literature review of online human behavioral studies (see Methods for details of the literature search and the Github repository for the full list of included studies).
-Briefly, we identified studies for inclusion through searches on Google Scholar using permutations of query terms related to online labour platforms, experimental paradigms, and symptom measures.
-We included studies that (a) recruited participants online, (b) measured behavior on at least one experimental task, and (c) measured responses on at least one self-report symptom measure.
-We then evaluated whether and how each of the resulting 49 studies performed task and self-report data screening.
-We note that this review was not meant to be systematic, but instead to provide a representative overview of common screening methods in online behavioral studies.
-
-Summary statistics concerning the prevalence and types of screening methods are provided in Table~\ref{tab:screening}.
-Of the 49 online behavioral studies meeting inclusion criteria, roughly 80\% (39/49) used at least one method to identify C/IE responding in task behavior.
-Of those studies, just over half relied on a single screening method, with considerable heterogeneity in behavior screening methods across studies.
-Most common (46\% of all studies) was identifying participants whose performance was indistinguishable from chance-level on some measure of accuracy.
+First, we sought to what extent recent online studies screen participants in a way that would reduce the risk of spurious correlations due to C/IE participants.
+We performed a narrative literature review of 49 online human behavioral studies, and evaluated whether and how each study performed task and self-report data screening (see Methods for details of the literature search).
+
+Among studies that we reviewed, approximately 80\% (39/49) used at least one method to identify C/IE responding in task behavior (see Table \ref{tab:screening}).
+Of these, just over half relied on a single screening method, with considerable heterogeneity in behavior screening methods across studies.
+Most common (46\% of all studies) was identifying participants whose performance was statistically indistinguishable from chance-level on some measure of accuracy.
 Almost as common (38\%) was screening based on low response variability (i.e., excluding participants who predominantly responded in the same fashion across trials, such as using only a single response key).
 
-In contrast, only a minority (19/49, or 39\%) of online behavioral studies in our sample screened for C/IE responding in self-report symptom measures.
-Of those studies the most common method was the use of attention checks, which operate under the assumption that certain responses to these prompts are unlikely under attentive responding, such that participants who do not give the correct response are likely to be engaged in C/IE responding.
-Attention checks can be subdivided into instructed items (in which participants are explicitly told which response to select; e.g., `Please select ``Strongly Agree"'), and infrequency items (in which some responses are logically invalid; e.g., endorsing 'Agree' for the question `I competed in the 1917 Summer Olympic Games').
+In contrast, only a minority (19/49, or 39\%) of studies screened for C/IE responding in self-report symptom measures.
+The most common survey screening method was the use of attention checks, which are prompts for which most responses are unlikely given attentive responding.
+Participants who do not give the correct response to these prompts are therefore likely to be engaged in C/IE responding.
+Attention checks can be subdivided into instructed items (in which participants are explicitly told which response to select; e.g., `Please select ``Strongly Agree"'), and infrequency items (in which some responses are logically invalid or exceedingly improbable; e.g., endorsing 'Agree' for the question `I competed in the 1917 Summer Olympic Games').
 Of those studies that specified what type of attention check was used, instructed items were the most common method.
-As we discuss further below, this is notable because best-practice recommendations for data collection in personality psychology explicitly counsel against using instructed-item attention checks.
+As we discuss further below, this is notable because best-practice recommendations for data collection in personality psychology explicitly counsel \emph{against} using instructed-item attention checks \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}.
 Only a handful of studies employed statistical or so-called unobtrusive screening methods such as outlier detection or personal consistency.
 
-In sum, screening methods for C/IE responding vary widely across the studies that we reviewed.
-Whereas screening for C/IE responding in task behavior is relatively common for online behavioral studies, screening of self-report survey data is far less prevalent.
-Though at first this pattern may seem troubling, low rates of survey data screening are not necessarily an issue if screening on task behavior alone is sufficient to remove participants engaging in C/IE responding.
+In sum, whereas screening for C/IE responding in task behavior was relatively common for online behavioral studies, screening of self-report survey data was far less prevalent.
+Although this pattern may seem troubling, low rates of survey data screening are not necessarily an issue if screening on task behavior alone is sufficient to remove participants engaging in C/IE responding.
 That is, screening on survey data may be redundant if there is a high degree of correspondence between task- and survey-based screening methods.
-To our knowledge, however, this assumption has never been empirically tested.
-In the next section, we explicitly test this hypothesis in a large sample of online participants completing a battery of self-report surveys and a behavioural task.
+
+In the next section, we explicitly test this hypothesis in a large sample of online participants completing a battery of self-report surveys and a behavioral task.
+Specifically, we measure the correspondence between the common task- and survey-based screening methods, as identified in our literature review, so that the results are informative with respect to the average online psychiatry study.
 
@@
 \centering
+\small
 \setlength{\tabcolsep}{8pt}
-\begin{tabular}{lllllll}
+\begin{tabular}{lllrllr}
 \toprule
@@
 Measure & Accuracy & 18 (37\%) & \multicolumn{2}{l}{Attention Check} & & 17 (35\%) \\
-& Variability & 15 (31\%) & & \textit{Instructed} & & 10 (20\%) \\
-& Response Time & \ 7 (14\%) & & \textit{Unspecified} & & 5 (10\%) \\
-& Comprehension Check & \ \ 5 (10\%) & \multicolumn{2}{l}{Unobtrusive} & & \ 4 (8\%) \\
-& Other & 16 (33\%) \\
+& Variability & 15 (31\%) & & Instructed & & 10 (20\%) \\
+& Response Time & \ 7 (14\%) & & Infrequency & & 2 \, (4\%) \\
+& Comprehension Check & \ \ 5 (10\%) & & Unspecified & & 5 (10\%) \\
+& Other & 16 (33\%) & \multicolumn{2}{l}{Unobtrusive} & & \ 4 \, (8\%) \\
 \bottomrule
 \end{tabular}
-\caption{The prevalence and types of task and self-report data screening practices in a sample (N=49) of online behavioral studies.}
+\captionsetup{width=0.88\textwidth}
+\caption{The prevalence and types of task and self-report data screening practices in a sample (N=49) of recent online behavioral studies.}
 \label{tab:screening}
@@
 
+\subsection{Careless participants appear symptomatic when the overall level of symptom endorsement is low}
+
+%In the majority of the papers reviewed above, experimenters relied solely on behavioral screening to exclude participants who engaged in C/IE responding during an experiment.
+Nevertheless, even with behavioral screening, it is still possible that spurious behavior-symptom correlations might emerge if there is low correspondence between behavioral and survey-based C/IE screening methods (since high correspondence between methods would entail that behavioral screening alone would exclude participants who would have failed survey screening).
+
+To measure the correspondence of screening measures estimated from task and self-report behavior, we conducted an online behavioral experiment involving a simple decision-making task and a battery of commonly used self-report psychiatric symptom measures (see Methods).
+A final sample of 386 participants from the Amazon Mechanical Turk (N=186) and Prolific (N=200) online labour markets completed a probabilistic reversal-learning task and 5 self-report symptom measures.
+The reversal-learning task required participants to learn through trial-and-error which of three options yielded reward most often, and was modeled after similar tasks used to probe reinforcement-learning deficits in psychiatric disorders \cite{waltz2007probabilistic, mukherjee_reward_2020}.
+The five self-report symptom measures were the 7-up (which measures symptoms of hypomania), the 7-down (which measures symptoms of depression), the GAD-7, (which measures generalized anxiety symptoms), the BIS/BAS (which measures reward and punishment motivations), the SHAPS (which measures anhedonia symptoms), and the PSWQ (which measures worry symptoms), and were chosen based on previous literature to have a variety of expected response distributions (symmetric and asymmetric).
+In line with current best-practice recommendations in personality psychology \cite{huang2015detecting}, each self-report instrument included one `infrequency' item that could be used to identify C/IE responses in survey data (see Methods for a list of infrequency items).
+The entire experiment (surveys and task) was designed to require 10 minutes on average to complete (observed mean = 10.28 minutes).
+To minimize any influence of fatigue on survey responding, participants completed the surveys prior to beginning the task.
+
+%To assess the overall quality of the data, we examined the number of participants flagged by the choice accuracy and infrequency item screening measures (i.e.
+two most common screening measures identified in our literature review).
+Only 26 participants (7\%) were flagged as exhibiting choice behavior at or below statistically chance levels in the reversal-learning task.
+In contrast, 85 participants (22\%) endorsed a logically invalid or improbable response on one or more of the infrequency items when completing the self-report symptom measures.
+This discrepancy in the proportion of participants flagged by each method is consistent with previous research, which found varying levels of sensitivity to C/IE responding across screening methods \cite{desimone2018dirty}.
+The proportion of participants flagged for C/IE responding was marginally but significantly greater on Mechanical Turk compared to Prolific for both task (MTurk: N=18/186; Prolific: N=8/200; $z=2.22, p=0.026$) and survey data (MTurk: 50/186; Prolific: 35/200; $z = 2.22, p = 0.026$).
+
+\begin{figure}[t!]
+\includegraphics[width=16cm]{../figures/main_02a.png}
+\centering
+\captionsetup{width=0.88\textwidth}
+\caption{Raincloud plots of total symptom scores in attentive (red) and C/IE (blue) participants.
+Each colored dot represents the symptom score for one participant.
+The black dots display the average score within each group (error bars denote 95\% bootstrap confidence interval).
+The scales are ordered according to their estimated skew from top-left (7-up) to bottom-right (PSWQ).
+The average level of symptom endorsement is most markedly different between groups in measures with lowest overall rates of endorsement.}
+\label{fig:distributions}
+\end{figure}
+
+We hypothesise that spurious behavior-symptom correlations may emerge due to a mean-shift in the average level of symptom endorsement in participants engaging in C/IE responding relative to attentive participants.
+In turn, a mean-shift is expected to occur when the overall rate of symptom endorsement is low.
+To assess this, we visually inspected for each self-report measure the distribution of symptom scores in participants flagged by the infrequency measure vs.
+those that were not (Figure \ref{fig:distributions}).
+In line with our predictions, the average level of symptom endorsement was noticeably exaggerated in C/IE-responding participants for the symptom measures where symptom scores were most positively-skewed (7-up, 7-down, GAD-7; Table \ref{tab:validation}).
+In contrast, where there was higher rates of symptom endorsement overall, the distributions of symptom scores between the two groups of participants were less noticeably distinct.
+
+\begin{table}[!t]
+\centering
+\small
+\setlength{\tabcolsep}{6pt}
+\begin{tabular}{lccccccc}
+\toprule
+& & \multicolumn{2}{c}{Total Score} & \multicolumn{2}{c}{Cronbach's $\alpha$} & \multicolumn{2}{c}{\% Clinical Cutoff} \\
+\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8}
+ Subscale & Skew & Attentive & C/IE & Attentive & C/IE & No Screening & With Screening \\
+\midrule
+7-up   &  0.81 &    3.87 &   10.15 &    0.84 &    0.84 &     13.0\% &      4.0\% \\
+7-down &  0.76 &    4.75 &   10.68 &    0.94 &    0.88 &     17.4\% &      9.3\% \\
+GAD-7  &  0.75 &    4.86 &    9.73 &    0.92 &    0.87 &     25.9\% &     17.3\% \\
+BIS    &  0.78 &    7.74 &    7.92 &    0.83 &    0.62 &        - &        - \\
+BAS    &  0.17 &   15.73 &   16.16 &    0.84 &    0.71 &        - &        - \\
+SHAPS  &  0.26 &    8.02 &   10.85 &    0.90 &    0.81 &     17.9\% &     14.6\% \\
+PSWQ   &  0.19 &    4.78 &    6.74 &    0.93 &    0.81 &      7.3\% &      7.0\% \\
+\bottomrule
+\end{tabular}
+\captionsetup{width=0.88\textwidth}
+\caption{Descriptive statistics of the self-report symptom measures between attentive and C/IE participants.
+Skew: the empirical skewness of the distribution of total symptom scores.
+Total score: the average symptom score between attentive and C/IE participants.
+Cronbach's $\alpha$: a measure of response consistency, where greater values closer to 1 indicate greater consistency in responses.
+\% Clinical Cutoff: the percentage of participants reaching threshold for clinical symptomology before and after screening based on the infrequency measure.
+(The BIS/BAS scales do not have clinical thresholds.)}
+\label{tab:validation}
+\end{table}
+
+Hereafter, we use the infrequency-item method as a primary means of identifying C/IE responding in our data.
+To verify this approach, we conducted three validation analyses.
+The first analysis compared estimated internal consistency of self-report measures between the C/IE and attentive groups.
+The logic is that, if C/IE responding manifests as a tendency to respond randomly, we should expect to see a decrease in the consistency of a measure in the C/IE responding group \cite{maniaci2014caring, desimone2018dirty, desimone2018differential}.
+In line with this reasoning, we observed a reduction in Cronbach's $\alpha$ in the C/IE group for the majority of survey instruments (Table \ref{tab:validation}).
+A permutation test confirmed that the average decrease in internal consistency across measures was greater than would be expected by chance given the difference in participant numbers between groups ($t = 3.69, p = 0.021$).
+
+Second, we quantified the degree to which participants responded to self-report symptom surveys in a stereotyped fashion; that is, we determined if participants exhibited patterns in their responses that were independent of the contents of the survey items.
+We fit a random-intercept item factor-analysis model \cite{maydeu2006random} to self-report data (see Methods), and for each participant we estimated an intercept parameter that quantified their bias towards using responses on the left or right side of the response scale, regardless of what that response signifies for a particular self-report measure (e.g., low on one symptom scale versus high on another).
+We observed a credible difference between the average value of this intercept for the two groups ($\Delta \text{intercept} = 0.67, 95\% \ \text{HDI} = [-0.76, -0.57]$), such that C/IE participants were biased towards using the right-half of survey response options.
+This translates to a tendency to endorse \emph{more severe} symptoms on the 7-up/7-down and GAD-7 scales (where the rightmost options indicate greater frequency of symptoms) but \emph{less severe} symptoms on the SHAPS and BIS (where the rightmost options indicate lower frequency of symptoms) despite these inventories measuring strongly correlated constructs (i.e.
+depression and anhedonia, anxiety and behavioral inhibition).
+
+Finally, we compared the proportion of participants meeting the cutoff for clinical levels of psychopathology before and after excluding participants based on their responses to the infrequency items.
+Previous studies have found that applying such measures reduced the prevalence of clinical symptomology in online samples towards ground truth rates from epidemiological studies \cite{ophir2020turker}.
+On the most positively-skewed measures, the fraction of participants reaching clinical levels of symptom endorsement prior to screening was greater than what would be expected (Table \ref{tab:validation}).
+For example, 13.0\% of participants scored at or above clinical thresholds for (hypo)mania on the 7-up scale in our sample prior to screening, compared with a 12-month prevalence of 5\% in the general population \cite{merikangas2007lifetime, merikangas2012true}, but this rate was reduced to 4.0\% (in line with the population prevalence estimates) after exclusion of C/IE respondents.
+We observed a similar pattern for both major depressive disorder and anxiety\footnote{Interestingly, compared to previous literature the proportion of participants meeting threshold on the GAD-7 was elevated.
+We suspect this may reflect elevated rates of state anxiety during the COVID-19 pandemic \cite{yarrington2021impact}, when these data were collected, as well as elevated ground-truth rates of anxiety among the self-selected group of people who choose to work on online labour markets.} (population prevalence estimates of 7\% and 5\% respectively; \cite{kessler2012twelve, lowe2008validation, hinz2017psychometric}).
+In line with previous research, we interpret these inflated rates of clinical symptomology in our sample prior to screening as suggestive of C/IE responding \cite{ophir2020turker}.
+
+\subsection{Low correspondence between task and self-report measures of C/IE responding}
+
+Next, we evaluated the degree of correspondence between behavioral and self-report screening measures in order to determine whether screening on behavior alone was sufficient to identify and remove careless participants.
+In line with the literature review, we computed multiple measures of C/IE responding from each participant's task behavior and survey responses (see Methods for description of measures).
+To measure the degree of correspondence between these behavioral and self-report screening measures, we performed two complementary analyses.
+First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation.
+The resulting pairwise similarity matrices are presented in Figure \ref{fig:correspondence} (left panel).
+After correcting for multiple comparisons, there were few significant correlations between the behavioral and self-report screening measures.
+Only choice accuracy showed significant associations with any self-report measure (specifically, the infrequency and Mahalonobis distance measures).
+Crucially, the sizes of these observed correlations were roughly half those observed for the correlations between the self-report measures.
+This is worrisome as it suggests that, although there is some relationship between C/IE responding on tasks and self-report inventories, the relationship is not strong enough to ensure reliable detection of careless participants using task data alone.
+
+\begin{figure}[!t]
+\includegraphics[width=16cm, trim=0 0 3cm 0]{../figures/main_02b.png}
+\centering
+\captionsetup{width=0.88\textwidth}
+\caption{Similarity of task and self-report data screening measures.
+Each tile corresponds to the Spearman rank correlation (left) and Dice similarity coefficient (right) between two screening measures.
+Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times.
+Similarity scores have been thresholded after correcting for multiple comparisons.
+Numbers denote the strength of statistically significant correlations.
+Cross-modality correlations between task-behavior (left) and infrequency-item self-report measures (bottom) are in the dashed rectangle.}
+\label{fig:correspondence}
+\end{figure}
+
+Second, we used the Dice similarity coefficient to quantify agreement between different screening methods in the set of participants flagged for exclusion (Figure \ref{fig:correspondence}, right panel).
+This approach quantifies the degree of overlap between the set of would-be excluded participants based on different screening measures under a common exclusion rate.
+Though some measures have relatively clear threshold cutoffs (e.g., chance level performance for task accuracy), the majority of the measures evaluated here do not.
+As such, we evaluated the measures with respect to the top 10\% of ``suspect" participants flagged by each measure, corresponding roughly to the fraction of participants having performed at chance levels on the reversal-learning task \footnote{Results of the same analysis repeated for the top 25\% of ``suspicious" participants (corresponding roughly to the fraction of participants flagged by the infrequency-item measure) produced similar results, and are included in the supplement.}.
+Results were largely consistent with the correlation analysis: few pairs of task and self-report screening measures achieved levels of agreement greater than what would be expected by chance.
+The only significant cross-modality pair identified --- between the infrequency item and choice accuracy measures --- has a similarly coefficient less than 0.4.
+In other words, when these two measures are used to identify the top 10\% of participants most strongly suspected of C/IE responding, they agree on only two out of every five participants.
+Screening on choice accuracy alone (the most common method identified in our literature review) would fail to identify the majority of participants most likely engaging in C/IE responding as determined by the infrequency items.
+
+Taken together, these results suggest that measures of C/IE responding in task and self-report data do not identify the same set of participants.
+This means that solely excluding participants on the basis of poor behavioural performance---the most common approach in online studies---is unlikely to identify participants who engage in C/IE responding on self-report surveys.
+
+\subsection{Spurious symptom-behavior correlations produced by C/IE responding}
+
+Here we examine the potential consequences of screening only on task behavior in our data.
+To do this, we estimated the pairwise correlations between the symptom scores of each of the self-report measures and several measures of performance on the reversal learning task.
+This analysis emulated a typical computational psychiatry analysis, in which the results of primary interest are the correlations between task behavior and self-reported psychiatric symptom severity.
+
+For each participant, we computed both descriptive and computational-model-based measures of behavior on the reversal learning task (see Methods).
+To understand the effects of applying different forms of screening, we estimated the correlations between each unique pairing of a self-report symptom measure and measure of behavior under four different conditions: no screening, screening only on task behavior (i.e.
+only participants whose choice accuracy was above chance), screening only on self-report responses (i.e.
+only participants who responded correctly on all infrequency items), or both.
+The resulting pairwise behavior-symptom correlations following each screening procedure are presented in Figure \ref{fig:correlations}.
+We note that we did not correct these correlation analyses for multiple comparisons, since our purpose was to demonstrate the extent of this issue across multiple behavioral measures and self-report symptoms.
+Any one of these correlations considered individually can be thought of as emulating a conventional analysis where fewer statistical tests would be performed.
+
+\begin{figure}[!t]
+\includegraphics[width=17cm]{../figures/main_03a.png}
+\centering
+\captionsetup{width=0.88\textwidth}
+\caption{Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions.
+Only statistically significant correlations are specified (not corrected for multiple comparisons).
+Black Xs indicate significant correlations ablated under screening.
+No Screening = no exclusions; Accuracy Only = exclusions based on chance-level performance in the reversal-learning task; Infrequency Only = exclusions based on invalid or improbable responses to infrequency items; Both Types = exclusions based on the previous two measures.
+Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
+\label{fig:correlations}
+\end{figure}
+
+When no rejections based on C/IE responding was applied (i.e.
+all participants were included in the analysis; Figure \ref{fig:correlations}A), many significant correlations emerged between measures of task behavior and symptom scores, in particular for 4 of the self-report instruments (7-up, which measures symptoms of hypomania; 7-down, which measures symptoms of depression; GAD-7, which measures generalized anxiety symptoms; and BIS, which measures tendencies related to behavioral inhibition).
+Consistent with our predictions, the majority of these correlations involved symptom measures with asymmetric total score distributions.
+Attending to only the most skewed measures (i.e.
+7-up, 7-down, GAD-7), symptom endorsement was correlated with almost every behavioral measure.
+That is, significant correlations were not restricted only to general behavioral measures often used as proxies for participant effort (e.g.
+accuracy, inverse temperature $\beta$) but also to measures of specific theoretical interest, such as asymmetry of learning from positive and negative reward prediction errors ($\kappa$).
+Conversely, we found few significant correlations among symptom measures with more symmetric distributions.
+This is despite the fact these scales measure similar symptoms and syndromes (e.g.
+anxiety as measured by the GAD-7 and worry as measured by the PSWQ; depression as measured by the 7-down and anhedonia as measured by the SHAPS).
+
+Next, we excluded participants from analysis based on task-behavior screening (i.e.
+choice accuracy, removing the 7\% of participants exhibiting behavior indistinguishable from chance; Figure \ref{fig:correlations}B).
+The pattern of correlations was largely unchanged: we again found many significant correlations between measures of behavior and asymmetric symptom measures, but almost no significant correlations involving symmetric symptom measures.
+This suggests that rejection of participants based on the most common form of behavioral screening (i.e.
+performance accuracy) had little effect on behavior-symptom correlations as compared to no screening.
+
+In stark contrast, when we rejected participants based on self-report screening  (removing 22\% of participants who endorsed one or more invalid or improbable responses on the infrequency items; Figure \ref{fig:correlations}C), the number of significant correlations was markedly reduced, particularly for several of the most skewed symptom measures (7-down, GAD-7) and proxy measures of task attentiveness (e.g.
+accuracy, inverse temperature).
+This pattern of correlations were largely similar when rejections were applied based on both task and self-report screening measures (Figure \ref{fig:correlations}D).
+We also note also that with stricter screening, the remaining significant correlations were, for the most part (but not always), weaker.
+
+These findings suggest that many of the significant behavior-symptom correlations observed without strict participant screening may indeed be spurious correlations driven by C/IE responding.
+This was particularly the case for self-report instruments that have skewed response distributions resulting from uncommon symptom endorsement on average.
+Importantly, screening based on task behavior alone did not adequately protect against spurious symptom-behavior correlations in the presence of skewed distributions of symptom endorsement.
+For instance, consider the 7-down scale, a measure of trait depression: had we not screened participants based on infrequency items, we would have erroneously concluded that there were many significant associations between reversal-learning task performance and self-reported depression.
+Screening on self-report data allowed us to identify that each of these depression-behavior correlations was likely to be entirely spurious.
+
+One possible objection to this interpretation is that the reduction in significant correlations following self-report screening and rejection was a result of the smaller sample size after removal of C/IE respondents (which comprised over 20\% of the sample).
+To test this alternative hypothesis, we compared the average (absolute) correlation size before and after infrequency-based exclusions were applied, restricted to correlations that were no longer significant afterward screening (the complete tables of correlations are included in the supplement).
+On average, we observed a significant reduction in correlation effect sizes ($\Delta \rho = -0.05, t = -2.87, p = 0.012$).
+following rejections, suggesting that the reduction in significant correlations following screening was unlikely to be driven solely by a reduction in statistical power.
+
+Next, we investigated how spurious correlations depended on sample size.
+To do so, we performed a bootstrapping analysis where we held fixed the proportion of participants engaging in C/IE responding (i.e.
+5\%, 10\%, 15\%, 20\%) and increased the total number of participants.
+Across all analyses, we measured the correlation and between the 7-down depression scale and learning-rate asymmetry ($\kappa$), which we previously identified as likely exhibiting a spurious association.
+
+The outputs of the bootstrapping analysis are presented in Figure \ref{fig:bootstrap}.
+We found that, although estimated correlation magnitudes were independent of sample size (x-axis, left panel), the absolute magnitude of the behavior-symptom correlation increased with the proportion of C/IE participants (different coloured circles, left panel).
+Crucially, we found false-positive rates for spurious correlations \emph{increased} with increases in sample size in our data (right panel).
+This runs counter to a common assumption that larger sample sizes are protective against spurious correlations because they serve to mitigate measurement error.
+Although this assumption is correct for unsystematic measurement error, it no longer holds in the regime of systematic measurement error (where larger sample sizes reduce the variance of estimates, but do not alter their bias).
+Instead, our results suggest that, holding the proportion of C/IE responding constant, the false-positive rate for behavioral-symptom correlations will become increasingly inflated as the sample size increases.
+
+\begin{figure}[!t]
+\includegraphics[width=16cm]{../figures/main_03b.png}
+\centering
+\captionsetup{width=0.88\textwidth}
+\caption{False positive rates for spurious correlations \emph{increase} with sample size.
+\textit{Left:} Bootstrapped Spearman correlations between learning rate asymmetry ($\kappa$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants.
+The grey error bars indicate 95\% bootstrap confidence intervals.
+The thick dotted lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size.
+\textit{Right:} False positive rates for learning rate asymmetry ($\kappa$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants.
+False positive rate was calculated as the proportion of bootstrap samples in which the correlation between $\kappa$ and 7-down was statistically significant.}
+\label{fig:bootstrap}
+\end{figure}
+
+\subsection{C/IE responding manifests as qualitatively distinct behavioral strategy}
+
+Finally, we employed a theory-agnostic modeling approach to better understand how participants suspected of engaging in C/IE responding performed on the probabilistic reversal-learning task.
+This analysis was motivated by two interrelated aims.
+First was to better understand why there was low correspondence between screening measures derived from task and self-report data; that is, to determine why participants flagged by the infrequency items were not necessarily more likely to perform at chance.
+The second was to better understand  the provenance of the particular pattern of behavior-symptom correlations we found.
+
+To characterize participants' choice behavior, we adapted the softmax regression model from \cite{seymour2012serotonin}.
+This model estimates, for each participant, how much their propensity to choose an option depends on the recent history of trial events (rewarding outcomes, non-rewarding outcomes, and choices from the preceding 5 trials; see Methods).
+The regression weights for each event, averaged within attentive and careless participants, are presented in Figure \ref{fig:regression}.
+Comparing attentive participants to those suspected of engaging in C/IE responding, we observed a credible difference (i.e.
+95\% highest density intervals excluded zero) only for the $T-1$ weight for previous choice.
+Attentive participants were more likely to repeat their previous choice (i.e.
+greater choice hysteresis) than were careless participants.
+
+\begin{figure}[!b]
+\includegraphics[width=16cm]{../figures/main_03c.png}
+\centering
+\captionsetup{width=0.88\textwidth}
+\caption{Softmax regression decision weights in attentive (red) and careless (blue) participants.
+The weights dictate the extent to which the recent history of rewards, nonrewards, or previous choices influence current choice.
+$^* p<0.05$}
+\label{fig:regression}
+\end{figure}
+
+This result may be initially surprising, since one might expect choice hysteresis to result in more perseveration errors following contingency reversals, and since results reported in the previous section indicated that C/IE responding was associated with more perseveration errors.
+However, choice hysteresis is adaptive in this probabilistic reversal-learning task.
+Since rewards in the task are probabilistic, ignoring unrewarding outcomes and instead performing the same response once the reward-maximizing response option has been identified is optimal, until the reversal occurs and is identified.
+Interestingly, participants engaging in C/IE responding were also numerically (though not significantly) less affected by previous outcomes, suggesting that their behavior was not more adaptive, but rather just more random.
+
+This pattern of results, also mirrored in overall reduced outcome sensitivity ($\beta$), explains the pre-screening pattern of correlations with win-stay and lose-shift rates.
+But what of the learning rate asymmetries?
+%That learning rate asymmetries ostensibly relate to C/IE responding is puzzling at first given that the softmax regression results show no credible differences in the sensitivity to history of rewarding and non-rewarding outcomes.
+This too can be explained by choice hysteresis.
+Previous work has established that, when choice hysteresis is not accounted for in reinforcement learning models, it can manifest as positive learning rate asymmetries \cite{Katahira2018-ke}.
+As such, given that attentive participants show increased repetition, which our reinforcement learning model did not explicitly account for, we should expect to find a negative (positive) correlation between positive (negative) learning rates and C/IE responding.
+Indeed, this is precisely the pattern of correlations observed above.
+
+To conclude, the theory-agnostic analysis of task behavior revealed that careless participants were less likely to engage in adaptive choice hysteresis and instead showed a pattern of responding more akin to win-stay lose-shift heuristic.
+This finding helps clarify in part why we observed low correspondence between task and self-report screening measures: on average, careless participants were not engaging in random responding (which would have been detected by the accuracy screening measure) but instead in satisficing behaviors.
+Most importantly, the results present another hidden danger of C/IE responding.
+When participants utilize heuristic decision-making, this may manifest in difficult-to-predict forms when computational models are misspecified.
+Thus, C/IE responding may not only drive spurious correlations but also spurious inferences about what behavior-symptom correlations entail.
+
+\section{Discussion}
+
+In this manuscript, we highlighted a particular set of circumstances, common in computational psychiatry research done on large online samples, in which spurious correlations may arise between task behavior and self-reported symptomology.
+When the ground-truth prevalence of a symptom is low in the general population, participants who respond carelessly on measures assessing this symptom may erroneously appear as symptomatic.
+A less careful pattern of responding on tasks used to measure cognitive constructs can then masquerade as a correlation between alteration in these constructs and symptom dimensions.
+We found empirical evidence for this pernicious pattern in participants recruited from two popular online labour platforms.
+False-positive rates for these spurious correlations \emph{increased} with sample size, because the correlations are due to measurement bias, not measurement noise.
+Importantly, we found that screening on task behavior alone was insufficient to identify participants engaging in C/IE responding and avoid the false-positive correlations.
+Unfortunately, a literature review identified this type of screening as the most common practice in online computational psychiatry studies.
+We recommend instead to screen and exclude participants based on responding on surveys, a practice that abolished many spurious behaviour-symptom correlations in our data.
+
+One way of conceptualizing our results is through the lens of rational allocation of mental effort \cite{kool2018mental}.
+In any experiment, attentive responding is more effortful than careless responding.
+As such, participants completing an online task must perform a cost-benefit analysis---implicitly or otherwise---to decide how much effort to exert in responding.
+The variables that factor into such calculations are presumably manifold and likely include features of the experiment (e.g., task difficulty, monetary incentives), facets of the participant (e.g., subjective effort costs, intrinsic motivation, conscientiousness), and features of the online labor market itself (e.g., opportunity costs, repercussions for careless responding).
+
+Viewed from the perspective of effort expenditure, our results suggest that participants appraised the cost/benefit trade-off differently for behavioral tasks and self-report surveys.
+Specifically, we found that only 7\% of participants were at chance-level performance in our (easy) task, compared to more than 22\% of participants who failed one or more (even easier) attention-check items in the self-report surveys.
+Moreover, different measures of C/IE responding were weakly or not at all correlated between task behavior and self-report responses.
+This suggests the motivation for effortful responding was greater in the behavioral task, though precisely why is unclear.
+One possibility is that we gave participants a monetary incentive for attentive responding only during the task (a common practice, according to our literature review).
+A second possibility is that participants expected fewer consequences for C/IE responding during the self-report surveys, a reasonable assumption in light of how infrequently previous experiments have screened self-report data.
+Alternatively, participants may have found the gamified behavioral task more engaging or the self-report inventory more tedious.
+Regardless of the reason, this discrepancy reinforces our observations concerning the inadequacy of behavioral-task screening as a stand-alone method for identifying C/IE responding.
+Since, in general, participants may appraise costs and benefits of effortful responding differently for behavioral tasks and self-report surveys, screening for C/IE responding on one data modality may in general be unsuitable for identifying it in the other.
+We therefore recommend screening on each component of an experiment.
+
+One complicating factor for our argument is that C/IE responding may manifest in other ways than simply random responding for both behavioral tasks and self-report surveys.
+Indeed, in general there are more ways to respond carelessly than to respond attentively to a task or self-report inventory (e.g., random response selection, straight-lining, zig-zagging, acquiescence bias) \cite{curran2016methods}.
+Indeed, we observed that a win-stay lose-shift pattern emerged as a dominant strategy in the behavioral task among participants suspected of C/IE responding.
+The specific response strategy a participant adopts is likely to reflect the idiosyncratic integration of multiple perceived benefits (e.g.
+time saved, effort avoided) and costs (e.g.
+loss of performance bonuses, risk of detection and pay forfeited).
+As has been previously documented \cite{desimone2018dirty}, the presence of multiple response strategies makes it clear why certain screening measures are more or less likely to correlate.
+For example, the inter-item standard deviation and personal reliability measures are both sensitive to statistically random responding, but less sensitive to straight-lining.
+Most importantly, a diversity of heuristic response strategies highlights the need for many screening measures of C/IE responding, each sensitive to different heuristic strategies.
+
+Here we have focused on the potential for C/IE responding to result in spurious symptom-behavior correlations when rates of symptom endorsement are low, a case common to online computational psychiatry research.
+Beyond this, we should emphasize that a diversity of heuristic response strategies entails that there is more than one mechanism by which spurious correlations can emerge.
+To the extent that the only prerequisite is a mean-shift between attentive and careless participants, ours is not the only situation where one might expect spurious correlations to emerge \cite{huang2015insufficient}.
+For example, random responding on items with \emph{high} base-rate endorsement could yield spurious correlations with precisely the opposite pattern observed here.
+Conversely, straight-lining may actually suppress correlations when symptom endorsement is low.
+In sum, without more understanding about the various types of heuristic responding and when each is likely to occur in a sample, it is difficult to predict {\it a priori} the patterns of systematic bias that may arise for a given study.
+This is further impetus for experimenters to be wary of C/IE responding and to use a variety of screening measures to detect it.
+
+One concern with performing rigorous screening and exclusion of participants based on C/IE detection methods is that we might inadvertently introduce an overcontrol bias \cite{elwert2014endogenous}.
+That is, we have been treating a tendency towards C/IE responding as independent from psychopathology; however, to the extent that C/IE responding reflects lack of motivation \cite{barch2015mechanisms}, avoidance of effort \cite{cohen2001impairments, culbreth2016negative}, or more frequent lapses of attention \cite{kane2016individual, robison2017neurotic}, one might hypothesise a true underlying association between psychopathology and careless responding in online studies.
+In such cases, it is plausible that rigorous screening of C/IE responding might lead to the differential exclusion of truly symptomatic participants.
+
+Although, in theory, overcontrol bias may reduce power to detect legitimate symptom-behavior correlations, for overcontrol based on self-report questionnaires to seriously impact results it would have to be the case that symptomatic participants frequently endorsed improbable or impossible responses to infrequency-item checks (e.g., responding `Agree' to ``I competed in the 1917 Olympic Games").
+We would argue that even if such participants truly are experiencing severe symptoms of motivation or attention, there is likely to be limited utility in measuring these symptoms using a self-report measure that they are unable to complete veridically.
+A similar rationale underlies the widespread use of semi-structured interviews and other clinician-report measures rather than self-report measures for in-clinic psychiatric research.
+We would argue that, if the psychiatric phenomenon being studied is such that this issue warrants concern, the research question may be better suited to an in-person study design involving participants in the clinic who meet full diagnostic criteria than a correlational design involving an online convenience sample.
+
+Notwithstanding the above, one response to this legitimate concern is to take a graded approach to screening and excluding participants \cite{Kim2018-ev}.
+That is, participants could be screened with respect to a multitude of measures and only the consistently flagged participants be removed, thereby reducing the risk of inducing bias.
+Another possibility is to use sensitivity analysis as an alternative to exclusion, testing whether full-sample observed correlations are robust to the exclusion of participants flagged by measures of C/IE responding.
+We note that the strict screening approach used in the present study did not preclude us from identifying symptomatic participants or behavior-symptom correlations.
+Indeed, we found in our sample roughly 10\% of participants endorsing symptoms consistent with clinical levels of depression, and approximately 20\% consistent with clinical levels of acute anxiety.
+These estimates are within the realm of epidemiological norms \cite{kessler2012twelve, lowe2008validation, yarrington2021impact}..
+We also observed some positive correlations between anxiety and choice behavior that were consistent with effects found in previous literature \cite{huang2017computational, harle2017anhedonia, garrett2018updating}.
+For example, we found higher lose-shift rates and higher learning rates following negative prediction errors correlated with self-reported anxiety.
+This suggests that the screening methods we employed were not so aggressive as to attenuate behavior-symptom correlations that would be expected from the literature.
+
+There are several notable limitations to this proof-of-concept study.
+We used a small set of screening measures, and did not employ other recommended procedures (e.g.
+logging each key/mouse interaction during survey administration to detect form-filling software or other forms of speeded responding \cite{buchanan2018methods}).
+Thus, we cannot be confident that all of the flagged participants were indeed engaging in C/IE responding; similarly, we cannot be certain that we correctly excluded all participants engaged in C/IE responding.
+We studied behavior-symptom correlations for only one task and a small self-report symptom battery.
+It remains to be seen how generalizable our findings are, although our study design was inspired by experiments prevalent in the online computational psychiatry literature.
+As suggested above, future studies may find greater correspondence between task and self-report screening measures for more difficult behavioral experiments.
+Finally, we should note that, unlike previous studies in which some participants were explicitly instructed to respond carelessly \cite{buchanan2018methods}, we do not have access to ``ground truth'' regarding which participants were engaging in C/IE responding.
+Future work testing the efficacy of different screening metrics for identifying instructed C/IE responding may help to identify some of the issues that we have identified here.
+
+The present study highlights the need for future work on the prevalence of C/IE responding in online samples and its interactions with task-symptom correlations.
+Many open questions remain, including under what conditions task- and symptom-screening measures might better correspond, what screening measures are most effective and when, and under what conditions spurious correlations are more likely to arise.
+One especially pressing question is how sample size affects the likelihood of obtaining spurious correlations.
+The results of a bootstrapping analysis in our data suggest that false positive rates are likely to increase with sample size.
+As computational psychiatry studies move towards larger samples to characterize heterogeneity in symptoms (and to increase statistical power), it will be important to understand how sample size may exaggerate the effects of systematic error.
+
+\section{Conclusions}
+
+Moving forward, we would strongly recommend that experimenters employ some form of self-report screening method, preferably one recommended by the best-practices literature (see Box 1 for a list of concrete recommendations).
+Our literature review found that, to date, the majority of online studies assessing behavior-symptom correlations have not used self-report screening, and our results demonstrate that stand-alone task-behavior screening is likely to be insufficient.
+Our results also demonstrate that inadequate screening is likely not merely to result in increased measurement error, as commonly assumed, but may also induce spurious correlations between behavioral task metrics and self-reported psychiatric symptom levels.
+For these reasons, we encourage experimenters to use a variety of data-quality checks for online studies and to be transparent in their reporting of how screening was conducted, how many participants are flagged under each measure, and what thresholds are used for rejection.
+
+More broadly, we encourage experimenters in computational psychiatry to be mindful of the myriad reasons why participants may perform worse on a behavioral task.
+Wherever possible, researchers are encouraged to design experiments where the signature of some symptomology could not also be explained by C/IE responding (e.g.
+\cite{eldar2015interaction, hunter2019excessive}).
+Finally, we conclude by noting that it is preferable to prevent C/IE responding than to account for it after the fact \cite{ward2018applying}.
+As such, we recommend researchers take pains to ensure their experiments promote engagement, minimize fatigue and confusion, and reimburse participants fairly and ethically.
+
+% offcut material below
+
 Before continuing, we wish to briefly highlight two additional results from our literature review.
-First, we found that the majority of studies used only one single method to detect C/IE responding.
+First, we found that the majority of studies used only a single method to detect C/IE responding.
 This is worrisome from the perspective of signal detection theory.
@@
 This is potentially problematic, since a growing body of research disputes the efficacy of instructed items as attention checks for online studies \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}.
-Indeed, instructed attention checks are often discussed on forums for workers of online labour markets\footnote{Several examples of such discussions can be found at the Github repository for this project:  \url{github.com/nivlab/silver-screen}}, and scripts have even been developed with the purpose to highlight words most commonly used in instructed attention checks.
+Indeed, instructed attention checks are often discussed on forums for workers of online labour markets\footnote{Several examples of such discussions can be found at the Github repository for this project: \url{github.com/nivlab/sciops}}, and scripts have even been developed with the purpose to highlight words most commonly used in instructed attention checks.
 Unsurprisingly, then, it has been documented that subsets of participants may actively seek out instructed items in surveys and respond randomly elsewhere \cite{barends2019noncompliant}.
 In line with best-practice recommendations for online survey research, therefore, we encourage experimenters to use alternate means of screening for C/IE responding for self-report survey data (e.g., infrequency-item attention checks) \cite{huang2015detecting}.
-
-\subsection{Careless participants appear symptomatic when the overall level of symptom endorsement is low}
-
-In the majority of the papers reviewed above, experimenters relied solely on behavioural screening to exclude participants who engaged in C/IE responding during an experiment.
-Nevertheless, even with behavioural screening, it is still possible that spurious behaviour-symptom correlations might emerge if there is low correspondence between behavioural and survey-based C/IE screening methods (since high correspondence between methods would entail that behavioural screening alone would exclude participants who would have failed survey screening).
-
-In order to the measure the correspondence of screening measures estimated from task and self-report behavior, we conducted an online behavioral experiment involving a simple behavioral task and a battery of self-report psychiatric symptom measures (see Methods for details).
-A final sample of 386 participants from the Amazon Mechanical Turk (N=186) and Prolific (N=200) online labour markets completed a probabilistic reversal learning task and 5 self-report symptom measures.
-The reversal learning task required participants to learn through trial-and-error which of three choice options yielded reward most often, and was modeled after similar tasks used to probe reinforcement learning deficits in psychiatric disorders \cite{huang2017computational, waltz2007probabilistic, mukherjee_reward_2020}.
-The self-report measures assayed psychiatric symptoms related to depression, mania, anxiety, reward motivation, and anhedonia, and were chosen based on previous literature to have a variety of expected response distributions (symmetric and asymmetric).
-In line with current best-practice recommendations in personality psychology, each self-report instrument included one `infrequency' item that could be used to identify C/IE responses in survey data (see Methods for a list of infrequency items).
-To minimize any influence of fatigue, the entire experiment (surveys \& task) was designed to require 10 minutes on average to complete (observed mean = 10.28 minutes).
-For similar reasons, participants completed the surveys prior to beginning the task.
-
-To assess the overall quality of the data, we examined the number of participants flagged by the choice accuracy and infrequency item screening measures (i.e.
-two most common screening measures identified in our literature review).
-Only 26 participants (7\%) were flagged as exhibiting choice behavior in the reversal learning task at or below chance levels.
-In contrast, 85 participants (22\%) responded suspiciously on one or more of the infrequency items when completing the self-report symptom measures.
-This discrepancy in the proportion of participants flagged by each method is consistent with previous research which have found varying levels of sensitivity to C/IE responding across screening methods \cite{desimone2018dirty}.
-Though we will not address platform differences here, we note the proportions of flagged participants were marginally but significantly greater on Mechanical Turk compared to Prolific for both accuracy (MTurk: N=18/186; Prolific: N=8/200; $z=2.22, p=0.026$) and infrequency (MTurk: 50/186; Prolific: 35/200; $z = 2.22, p = 0.026$) measures.
-
-\begin{figure}[t!]
-\includegraphics[width=16cm]{../figures/main_02a.png}
-\centering
-\caption{Caption TK here}
-\label{fig:distributions}
-\end{figure}
-
-According to our hypothesis, a prerequisite for spurious behavior-symptom correlations to emerge is a mean-shift in the average level of symptom endorsement in participants engaging in C/IE responding relative to attentive participants, which might occur when the overall rate of symptom endorsement is low.
-As such, we visually inspected for each of the self-report measures the distribution of symptom scores in participants flagged by the infrequency measure vs.
-those that were not (hereafter referred to as `careless' or `attentive`, respectively; Figure \ref{fig:distributions}).
-In line with our predictions, the average level of symptom endorsement was noticeably exaggerated in careless participants relative to attentive participants for the symptom measures where symptom scores were positively-skewed (e.g.
-7-up, 7-down, GAD-7).
-In contrast, where there was a greater range of symptom endorsement, the distributions of symptom scores between the two groups of participants were less noticeably distinct.
-
-\begin{table}[!t]
-\centering
-\setlength{\tabcolsep}{6pt}
-\begin{tabular}{lccccccc}
-\toprule
-& & \multicolumn{2}{c}{Total Score} & \multicolumn{2}{c}{Clinical Levels} & \multicolumn{2}{c}{Cronbach's $\alpha$} \\
-\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8}
- Subscale & Skew & Attentive & Careless & Attentive & Careless & Attentive & Careless \\
-\midrule
-\midrule
-7u    &  0.81 &    3.87 &   10.15 &     0.04 &     0.45 &    0.84 &    0.84 \\
-7d    &  0.76 &    4.75 &   10.68 &     0.09 &     0.46 &    0.94 &    0.88 \\
-GAD7  &  0.75 &    4.86 &    9.73 &     0.17 &     0.56 &    0.92 &    0.87 \\
-BIS   &  0.78 &    7.74 &    7.92 &        - &        - &    0.83 &    0.62 \\
-BAS   &  0.17 &   15.73 &   16.16 &        - &        - &    0.84 &    0.71 \\
-SHAPS &  0.26 &    8.02 &   10.85 &     0.15 &     0.29 &    0.90 &    0.81 \\
-PSWQ  &  0.19 &    4.78 &    6.74 &     0.07 &     0.08 &    0.93 &    0.81 \\
-\bottomrule
-\end{tabular}
-\caption{}
-\label{tab:screening}
-\end{table}
-
-To verify the infrequency item method as an accurate assay of C/IE responding, we performed three validation analyses.
-The first approach is to compare the proportion of participants meeting the cutoff for clinical psychopathology among careless versus attentive participants(Table \ref{tab:screening}).
-On the most positively-skewed measures, the fraction of participants scoring at or above clinical levels of symptom endorsement was dramatically inflated in careless responders.
-For example, previous studies of prevalence of generalized anxiety disorder found that roughly 5\% of the general population met the clinical threshold at a score of 10 or higher on the GAD-7 \cite{lowe2008validation, hinz2017psychometric}.
-Though clinical thresholds have not been established for the 7-up/7-down, recent work has suggested scores of 12 or higher as useful for discriminating between those with and without clinical levels of pathology \cite{youngstrom2020evaluating}.
-Though the fraction of participants meeting threshold for these measures in the attentive group was within the expected range of prevalence given epidemiological data, the exaggerated rates in the flagged group are suggestive of C/IE responding.\footnote{Interestingly, compared to previous literature the proportion of participants meeting threshold on the GAD-7 was elevated.
-We suspect this may reflect elevated rates of state anxiety during the COVID-19 pandemic, when this data was collected.}
-
-The second approach was to compare the estimated internal consistency of the self-report measures between the careless and attentive groups.
-The logic is that, if C/IE responding manifests as a tendency to respond randomly, we should expect to see a decrease in the consistency of a measure in the careless group (as has been previously reported; \cite{maniaci2014caring, desimone2018dirty, desimone2018differential}).
-Accordingly, on the majority of measures we observed a reduction in Cronbach's $\alpha$ in the careless group relative to the attentive group (Table \ref{tab:screening}).
-A permutation test confirmed that the average decrease in internal consistency across measures was greater than would be expected by chance even controlling for the difference in the number of participants between the two groups ($t = 4.25, p = 0.006$).
-
-The third and final approach is to statistically quantify the degree to which participants responded to the items in the self-report symptom inventory in a stereotyped fashion; that is, to determine if participants exhibited patterns in their responses that were independent of the contents of the items.
-To do so, we fit a random intercept item factor analysis model \cite{maydeu2006random} to the self report data (see Methods for details).
-Briefly, an intercept term is estimated for each participant which quantifies their bias towards using particular response options (e.g.
-leftmost, rightmost) regardless of what that option signifies for a particular self-report measure.
-We observed a credible difference between the average value of this intercept between the two groups (stats here), such that participants suspected of C/IE responding were biased towards using the right-half of the response options on the self-report symptom inventory.
-This translates to a tendency to endorse greater illness on the 7-up/7-down and GAD-7 (where the rightmost options indicate greater frequency of symptoms) but translates to a tendency to endorse \emph{less} illness on the SHAPS and BIS (where the rightmost options indicate lower frequency of symptoms) despite these inventories measuring strongly correlated constructs (i.e.
-depression and anhedonia, anxiety and behavioral inhibition).
-This pattern also helps explain why the distributions of symptom scores between attentive and careless participants on the SHAPS appear to be similar despite the low rates of symptom endorsement usually observed on the SHAPS \cite{snaith1995scale}.
 
@@
 These validation analyses also identified multiple forms of C/IE responding.
-Though the Cronbach's alpha result suggests at least some participants were engaging in random responding, the item response model analysis identified participants who exhibited a preference for the rightmost response options regardless of their semantic content.
-That C/IE responding in this data manifested in more than one way (consistent with previous reports \cite{curran2016methods}) further highlights the importance of utilizing multiple screening methods, a point we will return to in the discussion.
-
-\subsection{Low correspondence between task and self-report measures of C/IE responding}
-
-Next, we evaluated the degree of correspondence between behavioral and self-report screening measures.
-This allowed us to determine whether screening on behavior alone was sufficient to identify and remove careless participants.
-In line with the narrative review, we computed multiple measures of C/IE responding from each participant's task behaviour and survey responses (see Methods for full description).
-For task behaviour, we computed the following screening measures: response variability (the fraction of responses using only one key), accuracy (the fraction of choices of the reward-maximizing response option), win-stay lose-shift rates (the difference in likelihood of repeating the previous choice following rewarded vs.
-unrewarded trials), and fraction of excessively fast response times.
-In line with previous studies, for self-report responses we screened participants' data for C/IE responding using the following measures: infrequency items (the number of suspicious responses to infrequency items), inter-item standard deviation (ISD; the variability of responses around a participant's modal response), personal reliability (the correlation between split-halves of a participant's responses), Mahalonobis distance (the extent to which a participant is an outlier with respect to all participants), and reading time (the average time taken to respond to each item).
-
-To measure the degree of correspondence between these behavioral and self-report screening measures, we performed two complementary analyses.
-First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation.
-The resulting pairwise similarity matrices are presented in Figure \ref{fig:correspondence} (left panel).
-After correcting for multiple comparisons, there were few significant correlations between the behavioral and self-report measures.
-Only choice accuracy showed significant associations with any self-report measure (specifically the infrequency and Mahalonobis distance measures).
-Crucially, the size of these observed correlations were roughly half that observed for the correlations between the self-report measures.
-This is worrisome as it suggests that, though there is some relation between C/IE responding on tasks and self-report inventories, it is not strong enough to reliably detect careless participants in self-report data from task data alone.
-
-\begin{figure}[!t]
-\includegraphics[width=16cm, trim=0 0 3cm 0]{../figures/main_02b.png}
-\centering
-\caption{Caption TK here}
-\label{fig:correspondence}
-\end{figure}
-
-To complement the correlational analysis, we also estimated the pairwise level of agreement on the binarized measures using the Dice similarity coefficient.
-This second approach quantifies the degree of overlap between the set of would-be excluded participants based on different screening measures under a common exclusion rate.
-Though measures like accuracy have relatively clear threshold cutoffs (e.g.
-chance level performance), the majority of the measures evaluated here do not.
-As such, we evaluated the measures with respect to the top 10\% of suspicious participants flagged by each measure, corresponding roughly to the fraction of participants having performed at chance levels on the reversal learning task.
-The results of the same analysis repeated for the top 25\% of suspicious participants (corresponding roughly to the fraction of participants flagged by the infrequency item measure) produced similar results, and is included in the supplement.)
-
-The resulting pairwise similarity matrices for each approach are presented in Figure \ref{fig:correspondence} (right panel).
-The pattern of results are largely consistent with the correlational analysis: few pairs of task and self-report screening measures achieved levels of agreement greater than what would be expected by chance.
-The only significant cross-modality pair identified -- between the infrequency item and choice accuracy measures -- has a similarly coefficient less than 0.4.
-In other words, when these two measures are used to identify the top 10\% most suspicious participants, they agree on only two out of every five participants.
-Screening on choice accuracy alone (the most common method identified in our narrative review) would fail to identify the majority of participants most likely engaging in C/IE responding as determined by the infrequency items.
-
-To conclude this section, we found across two complementary analyses that measures of C/IE responding in task and self-report data were not redundant.
-That is, contrary to common implicit assumptions in online behavioural research, detecting and removing careless participants based on behavioral data alone would not be sufficient for ensuring quality self-report data in our sample.
-Though we cannot extrapolate from this one dataset to conclude that this will always be the case, we can nevertheless conclude that experimenters cannot simply assume that screening on self-report data is redundant with screening on task behavior (and vice-versa).
-While tendencies towards C/IE responding in tasks and self-report inventories may be associated, our results show that both types of screening are likely to be necessary to ensure acceptable data quality.
-
-\subsection{Spurious symptom-behaviour correlations produced by C/IE responding}
-
-Here we detail the potential consequences of screening only on task behavior in our data.
-To do this, we estimated the pairwise correlations between the symptom scores of each of the self-report measures and several measures of performance on the reversal learning task.
-This analysis emulated a typical computational psychiatry analysis, in which the results of primary interest are the correlations between task behaviour and self-reported psychiatric symptom severity.
-
-For each participant, we computed both descriptive and model-based measures of behaviour on the reversal learning task.
-Descriptive measures included accuracy (the fraction of choices of the reward-maximizing response option), points (the total number of points accumulated over the game), win-stay rates (the fraction of trials on which a participant repeated the previous trial's choice following a reward outcome), lose-shift rates (the fraction of trials on which a participant deviated from the previous trial's choice following a non-reward outcome), perseveration (the number of trials on which a participant continued to choose the previously dominant response option following a reversal).
-The model-based measures included the parameters of commonly-used reinforcement model of choice behavior, i.e.
-$Q$-learning with asymmetric learning rates (see Method for further details): choice sensitivity ($\beta$,  inverse temperature), positive learning rate ($\eta_p$, learning rate following a positive reward prediction error), negative learning rate ($\eta_n$, learning rate following a negative reward prediction error), and learning rate asymmetry ($\kappa$, difference between $\eta_p$ and $\eta_n$ in a transformed space).
-We chose these task performance measures as they have been previously used to assess performance in clinical samples \cite{huang2017computational, brolsma2020challenging, mukherjee_reward_2020, ritschel2017neural}.
-
-To understand the effects of applying different forms of screening, we estimated the correlations between each unique pairing of a self-report symptom measure and measure of behavior under four different conditions: no screening, screening only on task behavior (i.e.
-accuracy above chance), screening only on self-report responses (i.e.
-pass responses on all infrequency items), or both.
-The resulting pairwise behavior-symptom correlations following each screening procedure are presented in Figure \ref{fig:correlations}.
-To note, these correlational analyses were not corrected for multiple comparisons as the intended purpose here is to emulate a conventional analysis where fewer statistical tests would be performed, as dictated by one's hypotheses.
-
-\begin{figure}[!t]
-\includegraphics[width=16cm]{../figures/main_03a.png}
-\centering
-\caption{Caption TK here}
-\label{fig:correlations}
-\end{figure}
-
-When no rejections based on for C/IE responding was applied (i.e.
-all participants in this sample were included; top left, Figure \ref{fig:correlations}), many significant correlations emerged between measures of task behavior and symptom scores.
-Consistent with our predictions, the majority of these correlations involved symptom measures with asymmetric total score distributions.
-Attending to only the most skewed measures (i.e.
-7-up/7-down, GAD-7), symptom endorsement was correlated with almost every behavioral measure.
-That is, significant correlations were not restricted only to behavioral measures often used as proxies for participant effort (e.g.
-accuracy, inverse temperature $\beta$) but also to measures of previous theoretical interest.
-Conversely, we found few significant correlations among symptom measures with more symmetric distributions.
-This is despite the fact these scales measure similar symptoms and syndromes (e.g.
-anxiety \& worry, depression \& anhedonia).
-
-Next, we rejected participants based on task behavior screening (i.e.
-choice accuracy, removing the 7\% of participants exhibiting behavior indistinguishable from chance; top right, Figure \ref{fig:correlations}).
-The pattern of correlations was largely unchanged: we again found many significant correlations between measures of behavior and asymmetric symptom measures, but almost no significant correlations involving symmetric symptom measures.
-Looking again at the most skewed symptom measures, all correlations involving accuracy and the inverse temperature were preserved.
-In sum, rejections based on the most common form of behavioral screening (i.e.
-performance accuracy) had little effect on behavior-symptom correlations as compared to no screening.
-
-We then rejected participants based on self-report screening  (i.e.
-infrequency item, removing the 22\% of participants endorsing 1 or more suspicious responses; bottom left, Figure \ref{fig:correlations}).
-In stark contrast, the number of significant correlations was markedly reduced.
-Notably, no significant correlations remained between the 7-down depression scale and any measure of task behavior after performing rejections based on self-report behavior.
-Similarly, fewer (but not no) significant correlations were observed between the most skewed symptom measures and proxy measures of task attentiveness (e.g.
-accuracy, inverse temperature).
-Finally, and interestingly, the pattern of correlations were largely similar when rejections were applied based on both task and self-report screening measures.
-
-The preceding results suggest that many of the significant behavior-symptom correlations observed prior to rejections are in line with our predictions; that is, spurious correlations driven by C/IE responding when symptom endorsement is rare on average.
-This leads us to conclude that behavioural screening alone did not adequately protect against spurious symptom-behaviour correlations in the presence of skewed distributions of symptom endorsement.
-This can be illustrated using the example of the 7-down scale, a measure of trait depression.
-If we had not screened participants based on their self-report data, we would have erroneously concluded that there were many significant associations between reversal learning task performance and self-reported depression.
-As it was, screening on self-report data allowed us to identify that each of these depression-behaviour correlations was likely to be entirely spurious.
-
-One possible objection to this interpretation is that the reduction in significant correlations following self-report screening and rejection was driven, not by the effective identification and removal of C/IE respondents, but simply by virtue of removing over 20\% of the sample.
-That is, rejections may have simply reduced the statistical power of analyses without changing the the estimated effect size.
-To see if this was the case, we compared the average (absolute) correlation size before and after rejections were applied (the complete tables of correlations are included in the supplement).
-On average, we observed a significant reduction in correlation effect sizes [add numbers] following rejections, suggesting that the reduction in significant correlations following screening was unlikely to be driven solely by a reduction in statistical power.
-
-Next, we investigated how spurious correlations depended on sample size.
-To do so, we performed a bootstrapping analysis where we held fixed the proportion of participants engaging in C/IE responding (i.e.
-5\%, 10\%, 15\%, 20\%) and increased the total number of participants.
-Across all analyses, we measured the correlation and between the 7-down depression scale and learning rate asymmetry ($\kappa$), which we previously identified as likely exhibiting a spurious association.
-
-The outputs of the bootstrapping analysis are presented in Figure \ref{fig:bootstrap}.
-Unsurprisingly, the absolute magnitude of the behavior-symptom correlation increased with the proportion of inattentive participants (left panel).
-Interestingly, correlation magnitude was largely independent of sample size.
-Crucially, we found false-positive rates for spurious correlations \emph{increased} with increases in sample size in our data.
-This runs counter to a common assumption that larger sample sizes are protective against spurious correlations because they serve to mitigate measurement error.
-Although this is certainly the case for unsystematic measurement error, this intuition no longer holds in the regime of systematic measurement error (i.e., larger sample sizes reduce the variance of estimates, but do not alter not their bias).
-Instead, our results suggest that, holding the proportion of C/IE responding constant, the false-positive rate for behavioural-symptom correlations will become increasingly inflated as the sample size increases.
-The reason for this is that both the precision of the estimated correlation, and the statistical power to detect said correlation, increases with increasing sample size.
-This result runs counter to the assumption that greater measurement error in online samples can be mitigated by simply collecting more data.
-
-\begin{figure}[!t]
-\includegraphics[width=16cm]{../figures/main_03b.png}
-\centering
-\caption{Caption TK here}
-\label{fig:bootstrap}
-\end{figure}
-
-Of course, it is important to note that these results do not give a complete picture of the likely effects of C/IE responding on symptom-behaviour correlations.
+Though the Cronbach's $\alpha$ result suggested at least some participants were engaging in random responding, the item-response model analysis identified participants who exhibited a preference for the rightmost response options regardless of their semantic content.
+That C/IE responding in these data manifested in more than one way is consistent with previous reports \cite{curran2016methods}, and further highlights the importance of utilizing multiple screening methods.
+
+It is important to note that these results do not give a complete picture of the likely effects of C/IE responding on symptom-behavior correlations.
 A full picture would require investigating the effects of C/IE responding over numerous different task designs, symptoms measures, sample sizes, and proportions of careless responders.
 Nevertheless, the results of this bootstrapping analysis suggest that spurious correlations driven by C/IE responding are likely to be a considerable source of potential error wherever large online samples are collected with asymmetric distributions of symptom endorsement.
-Indeed, it is also worth highlighting that false positive rates were inflated (above the expected 5\% level given $\alpha = 0.05$) even with only 5\% of the bootstrapped participant samples engaging in C/IE responding, which further highlights how pernicious this issue is.
-
-\subsection{C/IE responding manifests as qualitatively distinct behavioral strategy}
-
-In this final section, we employ a theory-agnostic modeling approach to better understand how participants suspected of engaging in C/IE responding performed on the probabilistic reversal learning task.
-This analysis was motivated by two interrelated aims.
-First was to better understand why there was low correspondence between screening measures derived from task and self-report data; that is, to determine why participants flagged by the infrequency items were not necessarily more likely to perform at chance.
-The second was to better understand how the particular pattern of behavior-symptom correlations from the previous section emerged.
-The results of this section are specific to the particular reversal-learning task that we used here, and it is likely that qualitatively different patterns would be likely to emerge in different behavioural tasks.
-
-To characterize participants' choice behavior, we adapted the softmax regression model from \cite{seymour2012serotonin}.
-Briefly, in this model the propensity for a participant to choose an option is a function of the sum of weights corresponding to the recent history of trial events (e.g.
-rewarding outcomes, non-rewarding outcomes, previous choices; see Methods for details).
-In other words, the model estimates for each participant how much their choice on some trial was influenced by the events of the preceding five trials.
-
-The regression weights, averaged within attentive and careless participants, for each event are presented in Figure \ref{fig:regression}.
-Comparing attentive participants to those suspected of engaging in C/IE responding, we observed a credible difference (i.e.
-95\% highest densitivity intervals excluded zero) only for the $T-1$ weight for previous choice.
-Attentive participants were more likely to repeat their previous choice (i.e.
-greater choice hysteresis) than were careless participants.
-Though careless participants did appear to show less sensitivity to the history of rewards and nonrewards, the 95\% highest density intervals did not exclude zero.
-
-\begin{figure}[!b]
-\includegraphics[width=16cm]{../figures/main_03c.png}
-\centering
-\caption{Caption TK here}
-\label{fig:regression}
-\end{figure}
-
-This result may be initially surprising, since one might expect choice hysteresis to result in more perseveration errors following contingency reversals, and since results reported in the previous section indicated that C/IE responding was associated with more perseveration errors.
-What is important to keep in mind, however, is that choice hysteresis is adaptive in this probabilistic reversal learning task.
-Since rewards in this task are probabilistic, participants should display a degree of hysteresis once the reward-maximizing response option has been identified, ignoring the occasional non-rewarding outcome from this option.
-In contrast to this adaptive strategy, we found that participants engaging in C/IE responding exhibited a qualitatively different behavioral strategy more akin to a win-stay lose-shift heuristic.
-
-This, in conjunction with overall reduced outcome sensitivity ($\beta$), explains the pre-screening pattern of correlations with win-stay and lose-shift rates.
-But what of the learning rate asymmetries?
-That learning rate asymmetries ostensibly relate to C/IE responding is puzzling at first given that the softmax regression results show no credible differences in the sensitivity to history of rewarding and non-rewarding outcomes.
-This too can be explained by choice hysteresis.
-Previous work has established that, when choice hysteresis is not accounted for in reinforcement learning models, it can manifest as positive learning rate asymmetries \cite{Katahira2018-ke}.
-As such, given that attentive participants show increased repetition, which our reinforcement learning model did not explicitly account for, we should expect to find a negative (positive) correlation between positive (negative) learning rates and C/IE responding.
-Indeed, this is precisely the pattern of correlations observed above.
-
-To conclude, the theory-agnostic analysis of task behavior revealed that careless participants were less likely to engage in adaptive choice hysteresis and instead showed a pattern of responding more akin to win-stay lose-shift heuristic.
-This finding helps clarify in part why we observed low correspondence between task and self-report screening measures: on average, careless participants were not engaging in random responding (which would have been detected by the accuracy screening measure) but instead in satisficing behaviors.
-Most importantly, the results present another hidden danger of C/IE responding.
-When participants utilize heuristic decision-making, this may manifest in difficult-to-predict forms when computational models are misspecified.
-Thus, C/IE responding may not only drive spurious correlations but also spurious inferences about what behavior-symptom correlations entail.
-
-\section{Discussion}
-
-Recap paragraph goes here
-
-One way of conceptualizing the results presented here is through the lens of rational allocation of mental effort \cite{kool2018mental}.
-In any experiment, attentive responding is more effortful than careless responding.
-As such, participants completing an online task must perform a cost-benefit analysis---implicitly or otherwise---to decide how much effort to exert in responding.
-The variables which factor into such calculations are presumably manifold and likely include features of the experiment (e.g., task difficulty, monetary incentives), facets of the individual (e.g., subjective effort costs, intrinsic motivation, conscientiousness), and features of the online labor market itself (e.g., opportunity costs, repercussions for careless responding).
-To the extent to which at least some of these factors are stable within an experiment, we would expect that C/IE responding is somewhat correlated within individuals across experiment components (as we have shown here with correlations between task and self-report responding).
-
-Viewed from the perspective of effort expenditure, our results suggest that participants appraised this cost/benefit trade-off differently for the behavioural task and the self-report surveys.
-Specifically, we found that only 7\% of participants were at chance-level performance in the task---compared to more than 22\% of participants who failed one or more attention check items in the self-report surveys---and that measures of C/IE responding were weakly or not at all correlated between task behavior and self-report responses.
-This suggests the motivation for effortful responding was greater in the behavioural tasks, though precisely why is unclear.
-One possibility is that we gave participants a monetary incentive for attentive responding only during the task (a common practice, according to our narrative review).
-A second possibility is that participants expected fewer consequences for C/IE responding during the self-report surveys, a reasonable assumption in light of how infrequently previous experiments have screened self-report data.
-Alternatively, participants may have found the gamified behavioural task more engaging or the self-report inventory more tedious.
-Whatever the reason, this discrepancy reinforces our observations concerning the inadequacy of behavioural-task screening as a stand-alone method for identifying C/IE responding.
-Since, in general, participants will appraise costs and benefits of effortful responding differently for behavioural tasks and self-report surveys, screening for C/IE responding on one data modality will almost never be suitable for identifying it in the other.
-A corollary of this is that the exact pattern of correspondence in C/IE responding across data modalities that we observed is a contingent feature of our study design; other study designs---for instance, using a more difficult behavioural task---would be expected to result in different patterns of correspondence.
-
-One complicating factor for the argument that we have presented here is that C/IE responding may manifest in other ways than simply random responding for both behavioural tasks and self-report surveys.
-Indeed, in general there are more ways to respond carelessly than to respond attentively to a task or self-report inventory (e.g., random response selection, straight-lining, zig-zagging, side bias) \cite{curran2016methods}.
-Similarly, in the present work we observed that a win-stay lose-shift pattern emerged as a dominant strategy in the behavioral task among participants suspected of C/IE responding.
-As above, we posit that the specific strategy for responding that a participant adopts is likely to reflect the idiosyncratic integration of multiple perceived benefits (e.g.
-time saved, effort avoided) and costs (e.g.
-loss of performance bonuses, risk of detection and pay forfeited).
-As has been previously documented \cite{desimone2018dirty}, the presence of multiple response strategies makes it clear why certain screening measures are more or less likely to correlate.
-For example, the inter-item standard deviation and personal reliability measures are both sensitive to statistically random responding, but less sensitive to straight-lining.
-Most importantly, a diversity of heuristic response strategies highlights the need for many screening measures of C/IE responding, each sensitive to different heuristic strategies.
-
-Here we have focused on the potential for C/IE responding to result in spurious symptom-behavior correlations when rates of symptom endorsement are low, a case common to online computational psychiatry research.
-Beyond this, we should emphasize that a diversity of heuristic response strategies entails that there is more than one mechanism by which spurious correlations can emerge.
-To the extent that a only mean-shift between attentive and careless participants is a prerequisite, this is not the only situation where one might expect spurious correlations to emerge \cite{huang2015insufficient}.
-For example, random responding on items with \emph{high} base-rate endorsement could yield spurious correlations with precisely the opposite pattern observed here.
-Conversely, an abundance of straight-lining may actually suppress correlations when symptom endorsement is low.
-In sum, without more understanding about the various types of heuristic responding and when each is likely to occur in a sample, it is difficult to predict a priori exactly what patterns of systematic bias may arise for a given study.
-This is further impetus for experimenters to be wary of C/IE responding and to use a variety of screening measures to detect it.
-
-One potential concern with performing rigorous screening (i.e., participant exclusion) based on C/IE detection methods is that we might inadvertently introduce an overcontrol bias \cite{elwert2014endogenous}.
-So far we have been treating a tendency towards C/IE responding as independent from psychopathology; however, to the extent that C/IE responding reflects lack of motivation \cite{barch2015mechanisms}, avoidance of effort \cite{cohen2001impairments, culbreth2016negative}, or more frequent lapses of attention \cite{kane2016individual, robison2017neurotic}, one might hypothesise an association between these two dimensions of individual differences.
-In such cases, it is plausible that rigorous screening of C/IE responding might lead to the differential exclusion of truly symptomatic participants.
-
-Although in theory this overcontrol bias may reduce power to detect legitimate symptom-behaviour correlations, for this to seriously impact results it would have to be the case that correlations were driven by symptomatic participants whose motivation or cognition were impacted to the extent that they frequently endorsed improbable or impossible responses to infrequency-item checks (e.g., responding `Agree' to ``I competed in the 1917 Olympic Games").
-We would argue that even if such participants truly are experiencing severe symptoms, there is likely to be limited utility in measuring these symptoms using a self-report measure that they are unable to complete veridically.
-A similar rationale underlies the widespread use of semi-structured interviews and other clinician-report measures rather than self-report measures for in-clinic psychiatric research.
-We would argue that, if the psychiatric phenomenon being studied is such that this issue warrants concern, the research question may be better suited to an in-person study design involving participants in the clinic who meet full diagnostic criteria than a correlational design involving an online convenience sample.
-
-Notwithstanding the above, one response to this legitimate concern is to advocate a graded approach to screening and excluding participants \cite{Kim2018-ev}.
-That is, participants should be screened with respect to a multitude of measures and only the most offending participants be removed, thereby reducing the risk of inducing bias.
-Alternatively, another possibility is to use sensitivity analysis as an alternative to exclusion, testing whether full-sample observed correlations are robust to the exclusion of participants flagged by measures of C/IE responding.
-We note that the more strict screening approach used in the present study did not preclude us from identifying symptomatic participants or behavior-symptom correlations.
-Indeed, we found in our sample roughly 10\% of participants endorsing symptoms consistent with clinical levels of depression, and approximately 20\% consistent with clinical levels of acute anxiety.
-These estimates are within the realm of epidemiological norms [citations].
-We also observed some positive correlations between anxiety and choice behavior that were consistent with effects found in previous literature [citations].
-For example, we found higher lose-shift rates and greater learning rates following negative prediction errors.
-This suggests that the screening methods employed here were not so aggressive as to attenuate behavior-symptom correlations that would be expected from the literature.
-
-There were several notable limitations to this proof-of-concept study.
-We used a small set of screening measures, and did not employ other recommended procedures (e.g.
-logging each key/mouse interaction during survey administration to detect form filling software or other forms of speeded responding \cite{buchanan2018methods}).
-Thus, we cannot be confident that all of the flagged participants were indeed engaging in C/IE responding; similarly, we cannot be certain that we correctly excluded all participants engaged in C/IE responding.
-We studied behavior-symptom correlations for only one task and a small self-report symptom battery.
-It remains to be seen how generalizable our findings are, although our study design was inspired by experiments prevalent in the online computational psychiatry literature.
-As suggested above, future studies may find greater correspondence between task and self-report screening measures for more difficult behavioral experiments.
-
-The present study highlights the need for future work on the prevalence of C/IE responding in online samples and its interactions with task-symptom correlations.
-Many open questions remain, including under what conditions might task and symptom screening measures better correspond, what screening measures are most effective and when, and under what conditions are spurious correlations more likely to arise.
-One especially pressing question is how sample size affects the likelihood of obtaining spurious correlations.
-The results of a bootstrapping analysis in our data suggest that false positive rates are likely to increase with increasing sample sizes, but this remains to be confirmed in future empirical work.
-As computational psychiatry studies move towards larger samples to characterize heterogeneity in symptoms (and to increase statistical power), it will be important to understand how sample size may exaggerate the effects of systematic error.
-
-In summary, moving forward we would strongly recommend that experimenters employ some form of self-report screening method, preferably one recommended by the best-practices literature (see Box 1 for a list of concrete recommendations).
-Our narrative review found that, to date, the majority of online studies assessing behavior-symptom correlations have not used self-report screening, and our results demonstrate that stand-alone task-behaviour screening is likely to be insufficient.
-Our results also demonstrate that inadequate screening is likely not merely to result in increased measurement error, as commonly assumed, but may also induce spurious correlations between behavioural task metrics and self-reported psychiatric symptom levels.
-For these reasons, we encourage experimenters to use a variety of data-quality checks for online studies and to be transparent in their reporting of how screening was conducted, how many participants are flagged under each measure, and what thresholds are used for rejection.
-
-More broadly, we encourage experimenters in computational psychiatry to be mindful of the myriad reasons why participants may perform worse on a behavioral task.
-Furthermore, we would encourage researchers wherever possible to design experiments where the signature of some symptomology is could not also be explained by C/IE responding (e.g.
-\cite{hunter2019excessive}).
-Finally, we conclude by noting that it is preferable to prevent C/IE responding than to account for it after the fact \cite{ward2018applying}.
-As such, we recommend researchers take pains to ensure their experiments are promote engagement, minimize fatigue and confusion, and pay fairly and ethically.
+Indeed, it is also worth highlighting that false positive rates were inflated (well above the expected 5\% level given $\alpha = 0.05$) even with only 5\% of the bootstrapped participant samples engaging in C/IE responding, which further highlights how pernicious this issue is.
+% end offcut material
 
@@
 
-Here we offer several concrete recommendations for future research investigating symptom-behaviour correlations in online samples.
+Here we offer several concrete recommendations for future research investigating symptom-behavior correlations in online samples.
 
@@
 At a minimum, we recommend screening of both behavioral and self-report data.
-Within self-report data, we recommend using methods sensitive to multiple distinct patterns of C/IE responding (e.g., random responding, straight-lining, side bias) and, if possible, to log all page interactions.
+Within self-report data, we recommend using methods sensitive to multiple distinct patterns of C/IE responding (e.g., random responding, straight-lining, side bias) and, if possible, to log all page interactions (e.g., mouse clicks, keyboard presses).
 
     \item When collecting self-report questionnaire data, include attention-check items that flag participants who may be engaging in C/IE responding.
-We would recommend following best-practice guidelines [citation] in using infrequency-item checks rather than instructed-item checks.
+We recommend following best-practice guidelines [citation] in using infrequency-item checks rather than instructed-item checks.
 Participants flagged by suspicious responses on attention-check items should either be excluded from further analysis, or assessed using sensitivity analyses to ensure that observed full-sample correlations are robust to their exclusion.
@@
     \item We found that spurious correlations predominantly affected self-report instruments for which the expected distributions of symptom scores were asymmetric (either positively or negatively skewed).
-As such, we would recommend that, \textit{ceteris paribus}, symmetrically-distributed measures of a given construct should be preferred to asymmetrically-distributed measures.
-Of course, given that the frequency of many psychiatric symptoms in the general population is itself positively skewed, this will not always be feasible.
-
-    \item Scales with reverse-coded items may be used to quantify the consistency of participants' responses between reverse-coded and non-reverse-coded measures of the same latent construct.
+As such, symmetrically-distributed measures of a given construct should be preferred to asymmetrically-distributed measures (though this will often be infeasible given that the frequency of many psychiatric symptoms in the general population is itself positively skewed).
+
+    \item Scales with reverse-coded items can be used to quantify the consistency of participants' responses between reverse-coded and non-reverse-coded measures of the same latent construct.
 With some care, this may be used to identify C/IE responding even for measures that do not include attention-check items \cite{emons2009detection}.
@@
 
-    \item In our experience, we have found it instructive to occasionally review discussions on public forums for participants of online labour markets (e.g.
+    \item In our experience, we have found it instructive to review discussions on public forums for participants of online labour markets (e.g.
 Reddit, TurkerNation).
-Doing so helps an experimenter stay on top of what screening methods would-be participants are already aware of.
-Moreover, checking the forums is useful to ensure your research group is in good standing with the participant community and to better understand the labour platforms from participants' perspectives.
-
-    \item In general, it is preferable to prevent C/IE responding than to account for it after the fact \cite{ward2018applying}.
-As such, in designing studies, researchers should consider that confusion, fatigue, and low task motivation are likely to contribute to C/IE responding.
-In general, we would expect prolonged, fatiguing, confusing, or poorly-paid studies to be associated with more C/IE responding than brief, engaging, clear, and well-paid studies.
-
-    \item Consider whether the online methodology is truly appropriate for the research question.
-In particular, if the project studies syndromes associated with considerable difficulty in task or survey engagement (e.g., severe ADHD, acute mania), then high-symptom-endorsement participants are likely to produce responses that cannot be distinguished from C/IE responding.
-If this is a potential concern, then correlational research with online convenience samples is likely not the appropriate methodology for the research question.
+Doing so helps an experimenter identify what screening methods would-be participants are already aware of and prepared to answer correctly.
+
+    \item Consider carefully whether the online methodology is truly appropriate for the research question.
+In particular, if the project studies syndromes associated with considerable difficulty in task or survey engagement (e.g., severe ADHD, acute mania), symptomatic participants are likely to produce responses that cannot be distinguished from C/IE responding.
+In this case, correlational research with online samples is likely not the best methodology for the research question.
 
@@
 
-This is not an exhaustive list, and one overarching recommendation is that researchers studying individual differences in psychiatric symptom endorsement should engage meaningfully with methodological research from the psychological measurement literature, where many of these questions have long been studied [citations].
+This is not an exhaustive list, and one overarching recommendation is that researchers studying individual differences in psychiatric symptom endorsement should engage meaningfully with methodological research from the psychological measurement literature, where many of these questions have long been studied \cite{huang2015insufficient, curran2016methods, thomas2017validity, desimone2018dirty, ophir2020turker}.
 
@@
 
+All code, data, and analysis materials are publicly available at \url{github.com/nivlab/sciops}.
+
 \subsection{Literature Review}
@@
 We identified studies for inclusion through searches on Google Scholar using permutations of query terms related to online labour platforms (e.g.
-"mechanical turk", "prolific", "online"), experimental paradigms (e.g.
-"experiment", "cognitive control", "reinforcement learning"), and symptom measures (e.g.
-"psychiatry", "mental illness", "depression").
-We included studies that (a) recruited participants online through a labour platform, (b) measured behaviour on at least one experimental task, and (c) measured responses on at least one self-report symptom measure.
+``mechanical turk", ``prolific", ``online"), experimental paradigms (e.g.
+``experiment", ``cognitive control", ``reinforcement learning"), and symptom measures (e.g.
+``psychiatry", ``mental illness", ``depression").
+We included studies that (a) recruited participants online through a labour platform, (b) measured behavior on at least one experimental task, and (c) measured responses on at least one self-report symptom measure.
 Through this approach, we identified for inclusion 49 studies spanning 2015 through 2020.
@@
 In addition, we assessed the total number of screening measures each study used and how monetary bonuses were paid to participants (if at all).
-The fully annotated review of studies can be found in the Github repository for this project (\url{github.com/nivlab/silver-screen}).
 Finally, we note that this review was not meant to be systematic, but instead to provide a representative overview of common practices in online behavioral studies.
@@
 Participants were eligible if they resided in the United States or Canada; participants from MTurk were recruited with the aid of CloudResearch services \cite{litman2017turkprime}.
-(Note: This study was conducted prior to the introduction of Cloudresearch's new data quality filters \cite{cloudresearch_2020}).
+(Note: This study was conducted prior to the introduction of CloudResearch's new data quality filters \cite{cloudresearch_2020}).
 Following recent recommendations \cite{robinson2019tapped}, MTurk workers were not excluded based on work approval rate or number of previous jobs approved.
@@
 
-Participants performed a probabilistic reversal learning task, explicitly designed to be similar to previous computational psychiatry studies.
+Participants performed a probabilistic reversal learning task, explicitly designed to be similar to previous computational psychiatry studies \cite{waltz2007probabilistic, mukherjee_reward_2020}.
 On every trial of the task, participants were presented with three choice options and were required to choose one.
@@
 The task was programmed in jsPsych \cite{deleeuw_2015_jspsych} and distributed using custom web-application software.
-Both the experiment code (\url{github.com/nivlab/ThreeArmJS}) and web-software (\url{github.com/nivlab/nivturk}) are publicly available.
+The experiment code is available at \url{github.com/nivlab/ThreeArmJS}, and the web-software is available at \url{github.com/nivlab/nivturk}.
+A playable demo of the task is available at \url{nivlab.github.io/ThreeArmJS}.
 
@@
 It is an abbreviation of the General Behavior Inventory \cite{depue1981behavioral}, wherein only items that maximally discriminated between depression and mania were included.
-Items are scored on a 4-point scale from 0 ("Never or hardly ever") to 3 ("Very often or almost constantly").
+Items are scored on a 4-point scale from 0 (``Never or hardly ever") to 3 (``Very often or almost constantly").
 Total symptom scores on both subscales range from 0 to 21, and are usually strongly right-skewed, with few participants exhibiting moderate to high levels of symptom endorsement.
@@
 The GAD-7 assesses how much a respondent has been bothered by each of seven core anxiety symptoms over the last 2 weeks.
-Items are scored on a 4-point scale from 0 ("not at all") to 3 ("nearly every day").
+Items are scored on a 4-point scale from 0 (``not at all") to 3 (``nearly every day").
 Total scores on the GAD-7 range from 0 to 21, and are usually right-skewed, with few participants exhibiting moderate to high levels of symptom endorsement.
@@
 The original 42-item measure was recently abbreviated to a 14-item measure \cite{pagliaccio2016revising}, which we use here.
-Items are scored on a 4-point scale from 1 ("very true for me") to 4 ("very false for me").
-We note that in order to maintain consistency with the other symptom measures, the order of the BIS/BAS response options was reversed during administration such that "very false for me" and "very true for me" were the left- and rightmost anchors, respectively.
+Items are scored on a 4-point scale from 1 (``very true for me") to 4 (``very false for me").
+Total scores on the BAS subscale range from 8 to 32, whereas total scores on the BIS subscale range from 4 to 16.
+Previous reports have found total scores to be symmetrically distributed \cite{cooper2007behavioural}.
+Importantly, in order to maintain presentation consistency with the other symptom measures, the order of the BIS/BAS response options was reversed during administration such that ``very false for me" and ``very true for me" were the left- and rightmost anchors, respectively.
 
 \textbf{Snaith-Hamilton Pleasure Scale}: the Snaith-Hamilton Pleasure Scale is a 14-item measure of anhedonia \cite{snaith1995scale}.
-Items are scored on a 4-point scale from 0 ("strongly agree") to 3 ("strongly disagree"), where higher scores indicate greater pathology.
-Items are typically binarized before scoring (either disagree response receives a score of 1), and total symptom scores of 3 or greater indicate pathology.
-More recent research, however, has suggested using the sum of unthresholded scores instead \cite{franken2007assessment}.
-Here we present the unthresholded symptom scores, except for when we compute the fraction of participants meeting clinical threshold for which we use the binarized measure.
+Items are scored on a 4-point scale from 0 (``strongly agree") to 3 (``strongly disagree"), where higher scores indicate greater pathology.
+Total scores on the SHAPS range from 0 to 42, and have previously been found to be somewhat right-skewed \cite{franken2007assessment, leventhal2015measuring}, with only the minority of participants exhibiting moderate to high levels of symptom endorsement.
+Importantly, as with the BIS/BAS, the order of the SHAPS response options was reversed during administration such that ``strongly disagree" and ``strongly agree" were the left- and rightmost anchors, respectively.
 
@@
 The original 16-item was recently abbreviated to a 3-item measure \cite{kertz2014psychometric}, which we use here.
-Items are scored on a 5-point scale from 1 ("not at all typical of me") to 5 ("very typical of me"), where higher scores indicate greater pathology.
+Items are scored on a 5-point scale from 1 (``not at all typical of me") to 5 (``very typical of me"), where higher scores indicate greater pathology.
 Total symptom scores range from 1 to 15 and are usually uniformly distributed.
@@
 
+All statistical models fit as part of the analyses (described in detail below) were estimated within a Bayesian framework using Hamiltonian Monte Carlo as implemented in Stan (v2.26) \cite{stan}.
+For all models, four separate chains with randomised start values each took 2000 samples from the posterior.
+The first 1500 samples from each chain were discarded.
+As a result, 2000 post-warmup samples from the joint posterior were retained.
+Unless otherwise noted, the $\hat{R}$ values for all parameters was less than 1.1, indicating acceptable convergence between chains, and there were no divergent transitions in any chain.
+
+\subsubsection{Validation analyses}
+
+To validate the infrequency items as an efficacious measure of C/IE responding, we performed three complimentary analyses. We describe each in turn below.
+
+\subparagraph{Cronbach's $\alpha$} In the first validation analysis we compared Cronbach's $\alpha$, a measure of internal consistency, when estimated from attentive participants and participants flagged by the infrequency items.
+To control for the unbalanced numbers of participants in these groups, we performed a permutation test.
+First, we estimated Cronbach's $\alpha$ was estimated for each subscale and group.
+Next, we computed the average difference in Cronbach's $\alpha$ between the two groups.
+Then we created a null distribution for this statistic by repeating the same analysis but permuting group membership (i.e.
+randomly assigning participants to either group), holding fixed the sizes of both groups.
+This procedure was performed 5000 times.
+To compute a p-value, we tallied the number of null statistics equal to or (absolutely) greater than the observed test statistic.
+
+\subparagraph{Random intercept item factor analysis} In the second validation analysis, we employ random intercept item factor analysis \cite{maydeu2006random} to detect heuristic patterns of responding.
+In the model, the probability of observing response level $k$ (of $K$ total levels) from participant $i$ on item $j$ is defined as:
+
+\begin{equation*}
+    p( \ y_{ij} = k \ ) = \left\{ \begin{array}{ll}
+1 - \text{logit}^{-1}( \mu_i + x_j\cdot \theta_i - c_{j,1})  &  \text{if } y = 1 \\[4pt]
+\text{logit}^{-1}( \mu_i + x_j\cdot \theta_i - c_{j,y-1}) - \text{logit}^{-1}( \mu_i + x_j\cdot \theta_i - c_{j,y}) & \text{if } 1 < y < K \\[4pt]
+\text{logit}^{-1}( \mu_i + x_j\cdot \theta_i - c_{j,K-1}) - 0  &  \text{if } y = K
+\end{array} \right.
+\end{equation*}
+
+where $\mu_i$ is an intercept for participant $i$; $\theta_i$ is a vector of latent factor scores for participant $i$; $x_j$ is a vector of factor loadings for item $j$; $c_j$ is a vector of ordinal cutpoints for item $j$; and $y_{ij}$ is the observed response for participant $i$ on item $j$.
+
+In this analysis, we did not estimate the factor loadings but instead treated them as observed.
+Specifically, we defined the factor loading for each item as a one-hot vector where the only nonzero entry denoted that item's corresponding subscale.
+In other words, all of the items from a given subscale were assigned to their own unique factor (which was fixed to one).
+As such, the model estimated one factor score per participant and subscale (akin to the 1-parameter ordinal logistic model).
+
+Crucially, each participant's responses were also predicted by a random intercept term, $\mu_i$, which was not factor specific but instead was fit across all items.
+This intercept then reflects a participant's overall bias towards a response level.
+In our analysis, we coded the response levels such that the smallest value indicated endorsing the leftmost anchor (irrespective of semantic content) and the largest value indicated endorsing the rightmost anchor (irrespective of semantic content).
+Because the leftmost response option corresponds to symptomology on some scales (SHAPS), and a lack of symptomology for others (GAD-7, 7-up/7-down), we would not expect a consistent nonzero bias in this random intercept term for an attentive participant.
+
+\subparagraph{Clinical cutoffs} In the third and final validation analysis, we compared the proportion of participants in our sample reaching the threshold for clinical symptomology before and after applying exclusions.
+For the GAD-7, previous research has suggested a clinical cutoff score of 10 or higher \cite{lowe2008validation, hinz2017psychometric}.
+Though the 7-up/7-down scales do not have firmly established clinical cutoffs recent work has suggested a cutoff score of 12 or higher \cite{youngstrom2020evaluating}, which we use here.
+Finally, the original authors of the SHAPS scale recommended as a cutoff a score of 3 or more when the items are binarized (1 = ``strongly disagree", ``agree"; 0 = ``strongly agree", ``agree").
+We use this scoring approach in Table \ref{tab:validation}.
+
 \subsubsection{Correspondence of screening measures}
 
-To measure the correspondence of task- and self-report-based screening measures, we estimated a number of standard measures of data quality from each participant's task behaviour (four in total) and self-report responses (five in total).
+To measure the correspondence of task- and self-report-based screening measures, we estimated a number of standard measures of data quality from each participant's task behavior (four in total) and self-report responses (five in total).
 Beginning first with the self-report data, we describe each below.
@@
 Second, we estimated the pairwise rate of agreement on the binarized measures using the Dice similarity coefficient (looking at the top 10\% and 25\% most suspicious respondents for each measure).
-The former approach estimates two measures monotonic association, whereas the latter approach estimates their agreement as to which participants were most likely engaging in C/IE responding.
+The former approach estimates two measures' monotonic association, whereas the latter approach estimates their agreement as to which participants were most likely engaging in C/IE responding.
 For significance testing, we used permutation testing wherein a null distribution of similarity scores (i.e.
@@
 
-\subsubsection{Correlations between behaviour and symptom measures}
+\subsubsection{Correlations between behavior and symptom measures}
 
 To quantify the effects of both task and self-report data screening on behavior-symptom correlations, we estimated the pairwise correlations between the symptom scores of each of the self-report measures and several measures of performance on the reversal learning task.
-For each participant, we computed both descriptive and model-based measures of behaviour on the reversal learning task.
+For each participant, we computed both descriptive and model-based measures of behavior on the reversal learning task.
 We describe each in turn below.
 
-\subparagraph{Descriptive measures} Descriptive task measures included the following: accuracy, or the proportion of choices of the reward-maximizing response option; points, or the total number of points accumulated over the game; win-stay rate, or the fraction of trials on which a participant stayed with the previous choice option following a reward; lose-stay rate, or the fraction of trials on which a participant switched from the previous choice option following a non-reward; and perseveration, or the number of trials on which a participant chose the previously reward-maximizing response option following a reversal.
-
-\subparagraph{Model-based measures} The model-based measures were derived from a common reinforcement learning model of choice behavior, i.e.
-the risk-sensitive temporal difference learning model \cite{niv2012neural}.
+\subparagraph{Descriptive measures} Descriptive task measures included the following: accuracy (the fraction of choices of the reward-maximizing response option), points (the total number of points accumulated over the game), win-stay rates (the fraction of trials on which a participant repeated the previous trial's choice following a reward outcome), lose-shift rates (the fraction of trials on which a participant deviated from the previous trial's choice following a non-reward outcome), and perseveration (the number of trials on which a participant continued to choose the previously dominant response option following a reversal in task contingencies).
+
+\subparagraph{Model-based measures} The model-based measures were derived from a common reinforcement learning model of choice behavior, the risk-sensitive temporal difference learning model \cite{niv2012neural}.
 In this model, the expected value of a choice option, $Q(s)$, is learned through cycle of choice and reward feedback.
@@
 In the risk-sensitive temporal difference learning model, there are separate learning rates for positive and negative prediction errors, such that positive and negative prediction errors have asymmetric effects on learning.
-For example, the effect of negative prediction errors on learned values is larger than that of positive errors if $\eta^+ < \eta^-$, and vice versa if $\eta^+ > \eta^-$.
+For example, the effect of negative prediction errors on learned values is larger than that of positive errors if $\eta_p+ < \eta_n$, and vice versa if $\eta_p > \eta_n$.
 
@@
 where $\beta$ is the inverse temperature, controlling a participant's sensitivity to the expected value of the choice options.
-
-In sum then, the model-based approach describes a participant's choice behavior as a function of three parameters ($\beta, \eta^+, \eta^-$).
-These parameters were estimated within a Bayesian framework using Hamiltonian Monte Carlo as implemented in Stan (v2.25) \cite{stan}.
-Four separate chains with randomised start values each took 2000 samples from the posterior.
-The first 1500 samples from each chain were discarded.
-As a result, 2000 post-warmup samples from the joint posterior were retained.
-The $\hat{R}$ values for 98\% of parameters was less than 1.1, indicating acceptable convergence between chains, and there were no divergent transitions in any chain.
-Participant parameters were fit individually (i.e.
-not hierarchically) so as to prevent in parameter estimation any bias via partial-pooling between participants responding attentively versus carelessly.
+In sum then, the model-based approach describes a participant's choice behavior as a function of three parameters ($\beta, \eta_p, \eta_n$).
+
+We fit the reinforcement learning model to each participants' choice behavior using Stan (details above).
+Notably, 11 participants (3\% of sample) had parameter estimates with poor convergence, i.e.
+$\hat{R} > 1.1$; their parameters were removed from the correlation analysis.
+Participants' parameters were fit individually (i.e.
+not hierarchically) so as to prevent bias during parameter estimation from partial-pooling between attentive and C/IE participants.
 Parameters were sampled using non-centred parameterisations (i.e., all parameters were sampled separately from a unit normal before being transformed to the appropriate range).
-Of note, the learning rates were estimated via an offset method such that $\eta^+ = \eta + \kappa$ and $\eta^- = \eta - \kappa$, where $\kappa$ is an offset parameter controlling the extent of an asymmetry between the two learning rates.
-This parameter was also entered into the behaviour-symtom correlational analyses.
-Full Stan code for all models is available in the Github repository for this project (\url{github.com/nivlab/silver-screen}).
-
-\subparagraph{Correlational analysis} Behaviour-symptom correlations (after various forms of screening and exclusion) were estimated using Spearman's rank correlation.
+Of note, the learning rates were estimated via an offset method such that $\eta_p = \eta + \kappa$ and $\eta_n = \eta - \kappa$, where $\kappa$ is an offset parameter controlling the extent of an asymmetry between the two learning rates.
+This parameter was also entered into the behavior-symptom correlation analyses.
+
+We confirmed the model adequately fit participants' choice behavior through a series of posterior checks (see the Supplement).
+In particular, we confirmed the model recapitulated the group-average learning curves for each block of the experiment.
+Moreover, we confirmed that the model was able to recover reasonably well the choice accuracy for each participant.
+
+The model-based measures included for analysis were: choice sensitivity ($\beta$,  inverse temperature), positive learning rate ($\eta_p$), negative learning rate ($\eta_n$), and learning rate asymmetry ($\kappa = \frac{\eta_p-\eta_n}{\eta_p+\eta_n}$, normalized difference between $\eta_p$ and $\eta_n$).
+We chose these measures as they have been previously used to assess performance in clinical samples \cite{huang2017computational, brolsma2020challenging, mukherjee_reward_2020, ritschel2017neural}.
+
+\subparagraph{Correlation analysis} behavior-symptom correlations (after various forms of screening and exclusion) were estimated using Spearman's rank correlation.
 Significance testing was performed using the percentile bootstrap method \cite{wilcox2018guide} so as to avoid making any parametric assumptions.
-The correlational analyses were not corrected for multiple comparisons, as the intended purpose here is to emulate a conventional analysis where fewer statistical tests would be performed, as dictated by one's hypotheses.
+These correlation analyses were not corrected for multiple comparisons, since our overarching purpose was to demonstrate the extent of this issue across multiple behavioral measures and self-report symptoms.
+Any one of these correlations considered individually can be thought of as emulating a conventional analysis where fewer statistical tests would be performed.
 
@@
 
-where $x_{t-i}$ is a binary indicator (0,1) denoting if an event (i.e.
+where $x_{t-i}$ is a binary indicator [0,1] denoting if an event (i.e.
 reward, non-reward, previous choice) occurred on trial $t-i$ and $w_{t-1}$ is the associated decision weight.
@@
 Note that these weights were fit independently; that is, we did not employ an exponential kernel to parameterize the decay of the weights at successively distant trial lags.
-
 In sum then, the theory-agnostic model describes a participant's choice behavior as a function of 15 parameters.
-These parameters were estimated within a Bayesian framework using Hamiltonian Monte Carlo as implemented in Stan (v2.25) \cite{stan}.
-Four separate chains with randomised start values each took 2000 samples from the posterior.
-The first 1500 samples from each chain were discarded.
-As a result, 2000 post-warmup samples from the joint posterior were retained.
-The $\hat{R}$ values for all parameters was less than 1.1, indicating acceptable convergence between chains, and there were no divergent transitions in any chain.
-Participant parameters were fit individually (i.e.
-not hierarchically) so as to prevent in parameter estimation any bias via partial-pooling between participants responding attentively versus carelessly.
+
+We fit the softmax regression model using Stan (details above).Participant parameters were fit individually (i.e.
+not hierarchically)  so as to prevent bias during parameter estimation from partial-pooling between attentive and C/IE participants.
 Parameters were sampled with Gaussian priors with $\mu = 0$ and $\sigma = 5$.
-Full Stan code for all models is available in the Github repository for this project (\url{github.com/nivlab/silver-screen}).
 
 \printbibliography
-
 \pagebreak
-\section{Supplement}
+
+%TC:ignore
+
+\section*{Supplement}
+\setcounter{figure}{0}
 \setcounter{table}{0}
@@
 
-\subsection{Participant Demographics}
+\subsection*{Participant Demographics}
 
@@
 \end{tabular}
+\captionsetup{width=0.88\textwidth}
 \caption{The demographics of each sample by online labour market.
@@
 
-\subsection{Task Instructions}
+\subsection*{Task Instructions}
 
@@
 
-\subsection{Correspondence of screening measures}
+\subsection*{Correspondence of screening measures}
+
+The following are the unthresholded results of the screening measure correspondence analyses.
 
@@
 \centering
+\small
 \begin{tabular}{rccccccccc}
@@
 \end{tabular}
-\caption{Spearman correlation of measures}
+\captionsetup{width=0.88\textwidth}
+\caption{Spearman's rank correlations of task and self-report data screening measures.
+Each entry corresponds to the Spearman correlation between two screening measures.
+Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times.
+*Denotes statistical significance after correcting for multiple comparisons.}
 \end{table}
 
+\begin{table}[h!]
+\centering
+\small
+\begin{tabular}{rccccccccc}
+\toprule
+{} &     INF &     ISD &     REL &    MAH &   READ &    VAR &     ACC &  WSLS & RT \\
+\midrule
+INF  &       - &         &         &        &        &        &         &       &    \\
+ISD  &  0.462* &       - &         &        &        &        &         &       &    \\
+REL  &  0.484* &  0.691* &       - &        &        &        &         &       &    \\
+MAH  &  0.516* &  0.732* &  0.619* &      - &        &        &         &       &    \\
+READ &   0.319 &   0.165 &   0.165 &  0.216 &      - &        &         &       &    \\
+VAR  &   0.208 &   0.216 &   0.238 &  0.259 &  0.292 &      - &         &       &    \\
+ACC  &  0.379* &   0.312 &   0.258 &  0.344 &  0.237 &  0.282 &       - &       &    \\
+WSLS &   0.253 &   0.247 &   0.227 &  0.258 &  0.299 &  0.303 &  0.505* &     - &    \\
+RT   &   0.267 &   0.219 &   0.271 &  0.271 &  0.333 &  0.251 &   0.239 &  0.26 &  - \\
+\bottomrule
+\end{tabular}
+\captionsetup{width=0.88\textwidth}
+\caption{Dice similarity coefficients (top 10\%) for task and self-report data screening measures.
+Each entry corresponds to the Dice coefficient between two screening measures for the 10\% most suspicious participants.
+Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times.
+*Denotes statistical significance after correcting for multiple comparisons.}
+\end{table}
+
+\begin{table}[h!]
+\centering
+\small
+\begin{tabular}{rccccccccc}
+\toprule
+{} &     INF &     ISD &     REL &    MAH &    READ &    VAR &     ACC &   WSLS & RT \\
+\midrule
+INF  &       - &         &         &        &         &        &         &        &    \\
+ISD  &  0.355* &       - &         &        &         &        &         &        &    \\
+REL  &  0.355* &  0.564* &       - &        &         &        &         &        &    \\
+MAH  &  0.355* &  0.667* &  0.359* &      - &         &        &         &        &    \\
+READ &  0.290* &   0.231 &   0.154 &  0.231 &       - &        &         &        &    \\
+VAR  &   0.116 &   0.080 &   0.080 &  0.160 &   0.133 &      - &         &        &    \\
+ACC  &  0.269* &   0.137 &   0.164 &  0.192 &   0.247 &  0.171 &       - &        &    \\
+WSLS &   0.242 &   0.103 &   0.154 &  0.205 &   0.231 &  0.240 &  0.630* &      - &    \\
+RT   &   0.164 &   0.105 &   0.132 &  0.184 &  0.289* &  0.164 &   0.225 &  0.237 &  - \\
+\bottomrule
+\end{tabular}
+\captionsetup{width=0.88\textwidth}
+\caption{Dice similarity coefficients (top 25\%) for task and self-report data screening measures.
+Each entry corresponds to the Dice coefficient between two screening measures for the 25\% most suspicious participants.
+Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times.
+*Denotes statistical significance after correcting for multiple comparisons.}
+\end{table}
+
+\subsection*{Correlations between behavior and symptom measures}
+
+The following are the unthresholded results of the correlation analyses between task behavior and self-reported symptoms.
+
+\begin{table}[h!]
+\centering
+\small
+\begin{tabular}{rccccccc}
+\toprule
+{} &       7u &       7d &    GAD-7 &      BIS &     BAS &   SHAPS &    PSWQ \\
+\midrule
+Acc      &  -0.295* &  -0.166* &  -0.093* &  -0.134* &  -0.020 &  -0.051 &  -0.037 \\
+Pts      &  -0.225* &   -0.076 &   -0.023 &  -0.144* &  -0.061 &  -0.051 &   0.024 \\
+WS       &  -0.327* &  -0.160* &  -0.129* &  -0.171* &  -0.006 &  -0.048 &  -0.062 \\
+LS       &   0.285* &   0.158* &   0.146* &    0.050 &  -0.037 &   0.000 &  0.110* \\
+Pers     &   0.134* &    0.066 &    0.032 &   0.166* &   0.018 &   0.080 &  -0.004 \\
+$\beta$  &  -0.370* &  -0.157* &  -0.114* &  -0.185* &   0.017 &  -0.063 &  -0.043 \\
+$\eta_p$ &  -0.097* &  -0.105* &  -0.101* &   -0.033 &  -0.020 &  -0.015 &  -0.041 \\
+$\eta_n$ &   0.168* &   0.094* &   0.108* &   -0.050 &  -0.056 &  -0.020 &   0.042 \\
+$\kappa$ &  -0.208* &  -0.151* &  -0.161* &    0.026 &   0.016 &  -0.006 &  -0.064 \\
+\bottomrule
+\end{tabular}
+\captionsetup{width=0.88\textwidth}
+\caption{Spearman correlations between task behavior and self-report symptom measures when no screening and rejections have been applied.
+Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.
+*Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
+\end{table}
+
+\begin{table}[h!]
+\centering
+\small
+\begin{tabular}{rccccccc}
+\toprule
+{} &       7u &       7d &    GAD-7 &      BIS &     BAS &   SHAPS &    PSWQ \\
+\midrule
+Acc      &  -0.263* &  -0.144* &  -0.105* &  -0.106* &  -0.009 &  -0.020 &  -0.033 \\
+Pts      &  -0.187* &   -0.042 &   -0.020 &  -0.126* &  -0.055 &  -0.028 &   0.036 \\
+WS       &  -0.291* &  -0.137* &  -0.123* &  -0.161* &  -0.019 &   0.006 &  -0.044 \\
+LS       &   0.314* &   0.170* &   0.156* &    0.034 &  -0.036 &  -0.037 &  0.124* \\
+Pers     &    0.083 &    0.022 &    0.011 &   0.151* &   0.010 &   0.076 &  -0.021 \\
+$\beta$  &  -0.332* &  -0.134* &  -0.109* &  -0.173* &   0.010 &  -0.040 &  -0.023 \\
+$\eta_p$ &   -0.056 &   -0.089 &  -0.105* &   -0.013 &  -0.029 &   0.034 &  -0.035 \\
+$\eta_n$ &   0.259* &   0.134* &   0.122* &   -0.021 &  -0.063 &   0.019 &   0.053 \\
+$\kappa$ &  -0.226* &  -0.150* &  -0.162* &    0.015 &   0.009 &  -0.015 &  -0.064 \\
+\bottomrule
+\end{tabular}
+\captionsetup{width=0.88\textwidth}
+\caption{Spearman correlations between task behavior and self-report symptom measures after applying rejections based on choice accuracy (7\% of sample).
+Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.
+*Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
+\end{table}
+
+\begin{table}[h!]
+\centering
+\small
+\begin{tabular}{rccccccc}
+\toprule
+{} &       7u &      7d &    GAD-7 &      BIS &     BAS &   SHAPS &    PSWQ \\
+\midrule
+Acc      &  -0.210* &  -0.048 &    0.009 &   -0.082 &  -0.020 &  -0.005 &   0.009 \\
+Pts      &  -0.167* &   0.040 &    0.070 &  -0.107* &  -0.046 &  -0.011 &   0.071 \\
+WS       &  -0.220* &  -0.045 &   -0.008 &  -0.143* &  -0.025 &   0.001 &   0.016 \\
+LS       &   0.219* &   0.084 &   0.113* &    0.019 &  -0.021 &  -0.050 &   0.082 \\
+Pers     &    0.088 &  -0.028 &   -0.024 &   0.127* &   0.006 &   0.048 &  -0.052 \\
+$\beta$  &  -0.257* &  -0.038 &    0.047 &  -0.180* &  -0.011 &  -0.032 &   0.056 \\
+$\eta_p$ &   -0.052 &  -0.064 &   -0.079 &   -0.015 &  -0.008 &   0.004 &  -0.055 \\
+$\eta_n$ &   0.165* &   0.067 &   0.141* &   -0.037 &  -0.089 &  -0.030 &   0.054 \\
+$\kappa$ &  -0.154* &  -0.071 &  -0.156* &    0.039 &   0.045 &   0.011 &  -0.068 \\
+\bottomrule
+\end{tabular}
+\caption{Spearman correlations between task behavior and self-report symptom measures after applying rejections based on infrequency items (22\% of sample).
+Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.
+*Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
+\end{table}
+
+\begin{table}[h!]
+\centering
+\small
+\begin{tabular}{rccccccc}
+\toprule
+{} &       7u &      7d &    GAD-7 &      BIS &     BAS &   SHAPS &    PSWQ \\
+\midrule
+Acc      &  -0.229* &  -0.090 &   -0.072 &   -0.053 &   0.016 &   0.034 &  -0.040 \\
+Pts      &  -0.177* &   0.016 &    0.011 &   -0.086 &  -0.013 &   0.025 &   0.038 \\
+WS       &  -0.227* &  -0.085 &   -0.057 &  -0.131* &  -0.025 &   0.049 &  -0.007 \\
+LS       &   0.236* &   0.094 &   0.107* &    0.008 &  -0.016 &  -0.075 &   0.079 \\
+Pers     &    0.095 &  -0.007 &    0.014 &   0.110* &  -0.015 &   0.037 &  -0.025 \\
+$\beta$  &  -0.255* &  -0.072 &   -0.008 &  -0.165* &  -0.011 &  -0.015 &   0.028 \\
+$\eta_p$ &   -0.045 &  -0.088 &  -0.108* &    0.004 &  -0.000 &   0.049 &  -0.073 \\
+$\eta_n$ &   0.196* &   0.046 &   0.098* &   -0.015 &  -0.085 &   0.008 &   0.024 \\
+$\kappa$ &  -0.171* &  -0.072 &  -0.145* &    0.035 &   0.043 &   0.001 &  -0.063 \\
+\bottomrule
+\end{tabular}
+\captionsetup{width=0.88\textwidth}
+\caption{Spearman correlations between task behavior and self-report symptom measures after applying rejections based on both choice accuracy and infrequency items.
+Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.
+*Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
+\end{table}
+
+\subsection*{Posterior predictive check}
+
+\begin{figure}[!h]
+\includegraphics[width=16cm]{../figures/supp_01.png}
+\centering
+\captionsetup{width=0.88\textwidth}
+\caption{Posterior predictive checks for the risk-sensitive temporal difference learning model.
+\textit{Top:} Observed (black) and predicted (grey) learning curves averaged across the group.
+\textit{Bottom left:} Observed versus predicted choice accuracy for each participant.
+\textit{Bottom right:} Distribution of average predictive density across participants.}
+\label{fig:posterior_check}
+\end{figure}
+
+%TC:endignore
+
 \end{document}

### 2021-04-02 analysis/scripts/preprocess_correlates.py
two fixes: normalize learning rate asymmetries, add bootstrapping analysis

@@ -104,13 +104,13 @@ corr = corr.merge(gb)
 print('1.6 Extracting Stan parameters.')
 
 ## Load StanFit.
-df = read_csv('stan_results/rstd.tsv', sep='\t')
+df = read_csv('stan_results/rstd.tsv.gz', sep='\t', compression='gzip')
 
 ## Extract parameters of interest.
 beta  = df.filter(regex='beta').median().values
 eta_p = df.filter(regex='^eta_p').median().values
 eta_n = df.filter(regex='^eta_n').median().values
-kappa = df.filter(regex='theta_pr\[3').median().values
+kappa = (eta_p - eta_n) / (eta_p + eta_n)
 
 ## Convert to DataFrame.
 params = DataFrame(np.column_stack([beta,eta_p,eta_n,kappa]),

### 2021-04-02 manuscripts/main.tex
push updated manuscript

@@
 In the next section, we explicitly test this hypothesis in a large sample of online participants completing a battery of self-report surveys and a behavioral task.
-Specifically, we measure the correspondence between the common task- and survey-based screening methods, as identified in our literature review, so that the results are informative with respect to the average online psychiatry study.
+Specifically, we measure the empirical correspondence between common task- and survey-based screening methods---as identified in our literature review---so that results are informative with respect to typical study designs in online psychiatry research.
 
@@
 
-%In the majority of the papers reviewed above, experimenters relied solely on behavioral screening to exclude participants who engaged in C/IE responding during an experiment.
-Nevertheless, even with behavioral screening, it is still possible that spurious behavior-symptom correlations might emerge if there is low correspondence between behavioral and survey-based C/IE screening methods (since high correspondence between methods would entail that behavioral screening alone would exclude participants who would have failed survey screening).
-
 To measure the correspondence of screening measures estimated from task and self-report behavior, we conducted an online behavioral experiment involving a simple decision-making task and a battery of commonly used self-report psychiatric symptom measures (see Methods).
@@
 
-%To assess the overall quality of the data, we examined the number of participants flagged by the choice accuracy and infrequency item screening measures (i.e.
-two most common screening measures identified in our literature review).
+To assess the overall quality of the data, we examined the number of participants flagged by the choice accuracy and infrequency item screening measures.
 Only 26 participants (7\%) were flagged as exhibiting choice behavior at or below statistically chance levels in the reversal-learning task.
@@
 those that were not (Figure \ref{fig:distributions}).
-In line with our predictions, the average level of symptom endorsement was noticeably exaggerated in C/IE-responding participants for the symptom measures where symptom scores were most positively-skewed (7-up, 7-down, GAD-7; Table \ref{tab:validation}).
+In line with our predictions, the average level of symptom endorsement was noticeably exaggerated in C/IE-responding participants for the symptom measures where symptom scores were most positively-skewed (7-up, 7-down, GAD-7).
 In contrast, where there was higher rates of symptom endorsement overall, the distributions of symptom scores between the two groups of participants were less noticeably distinct.
+Permutation testing confirmed that observed mean-shifts in symptom scores for C/IE participants were statistical significant for the majority of the symptom measures (Table \ref{tab:validation}).
 
@@
 \setlength{\tabcolsep}{6pt}
-\begin{tabular}{lccccccc}
+\begin{tabular}{lcccccccc}
 \toprule
-& & \multicolumn{2}{c}{Total Score} & \multicolumn{2}{c}{Cronbach's $\alpha$} & \multicolumn{2}{c}{\% Clinical Cutoff} \\
-\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8}
- Subscale & Skew & Attentive & C/IE & Attentive & C/IE & No Screening & With Screening \\
-\midrule
-7-up   &  0.81 &    3.87 &   10.15 &    0.84 &    0.84 &     13.0\% &      4.0\% \\
-7-down &  0.76 &    4.75 &   10.68 &    0.94 &    0.88 &     17.4\% &      9.3\% \\
-GAD-7  &  0.75 &    4.86 &    9.73 &    0.92 &    0.87 &     25.9\% &     17.3\% \\
-BIS    &  0.78 &    7.74 &    7.92 &    0.83 &    0.62 &        - &        - \\
-BAS    &  0.17 &   15.73 &   16.16 &    0.84 &    0.71 &        - &        - \\
-SHAPS  &  0.26 &    8.02 &   10.85 &    0.90 &    0.81 &     17.9\% &     14.6\% \\
-PSWQ   &  0.19 &    4.78 &    6.74 &    0.93 &    0.81 &      7.3\% &      7.0\% \\
+& & \multicolumn{3}{c}{Total Score} & \multicolumn{2}{c}{Cronbach's $\alpha$} & \multicolumn{2}{c}{\% Clinical Cutoff} \\
+\cmidrule(lr){3-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
+ Subscale & Skew & Attentive & C/IE & \textit{t}-value & Attentive & C/IE & Before & After \\
+\midrule
+7-up   &  0.81 &    3.87 &   10.15 &  -13.31^* &    0.84 &    0.84 &     13.0\% &       4.0\% \\
+7-down &  0.76 &    4.75 &   10.68 &   -9.99^* &    0.94 &    0.88 &     17.4\% &       9.3\% \\
+GAD-7  &  0.75 &    4.86 &    9.73 &   -7.88^* &    0.92 &    0.87 &     25.9\% &      17.3\% \\
+BIS    &  0.78 &    7.74 &    7.92 &   -0.54 &    0.83 &    0.62 &        - &             - \\
+BAS    &  0.17 &   15.73 &   16.16 &   -0.91 &    0.84 &    0.71 &        - &             - \\
+SHAPS  &  0.26 &    8.02 &   10.85 &   -4.04^* &    0.90 &    0.81 &     17.9\% &      14.6\% \\
+PSWQ   &  0.19 &    4.78 &    6.74 &   -4.78^* &    0.93 &    0.81 &      7.3\% &       7.0\% \\
 \bottomrule
@@
 Total score: the average symptom score between attentive and C/IE participants.
+* indicates statistical significance.
 Cronbach's $\alpha$: a measure of response consistency, where greater values closer to 1 indicate greater consistency in responses.
@@
 We fit a random-intercept item factor-analysis model \cite{maydeu2006random} to self-report data (see Methods), and for each participant we estimated an intercept parameter that quantified their bias towards using responses on the left or right side of the response scale, regardless of what that response signifies for a particular self-report measure (e.g., low on one symptom scale versus high on another).
-We observed a credible difference between the average value of this intercept for the two groups ($\Delta \text{intercept} = 0.67, 95\% \ \text{HDI} = [-0.76, -0.57]$), such that C/IE participants were biased towards using the right-half of survey response options.
+We observed a credible difference between the average value of this intercept for the two groups ($\Delta \text{intercept} = 0.67, 95\% \ \text{HDI} = [-0.78, -0.55]$), such that C/IE participants were biased towards using the right-half of survey response options.
 This translates to a tendency to endorse \emph{more severe} symptoms on the 7-up/7-down and GAD-7 scales (where the rightmost options indicate greater frequency of symptoms) but \emph{less severe} symptoms on the SHAPS and BIS (where the rightmost options indicate lower frequency of symptoms) despite these inventories measuring strongly correlated constructs (i.e.
@@
 We observed a similar pattern for both major depressive disorder and anxiety\footnote{Interestingly, compared to previous literature the proportion of participants meeting threshold on the GAD-7 was elevated.
-We suspect this may reflect elevated rates of state anxiety during the COVID-19 pandemic \cite{yarrington2021impact}, when these data were collected, as well as elevated ground-truth rates of anxiety among the self-selected group of people who choose to work on online labour markets.} (population prevalence estimates of 7\% and 5\% respectively; \cite{kessler2012twelve, lowe2008validation, hinz2017psychometric}).
+We suspect this may reflect elevated rates of state anxiety during the COVID-19 pandemic \cite{yarrington2021impact}, when these data were collected.} (population prevalence estimates of 7\% and 5\% respectively; \cite{kessler2012twelve, lowe2008validation, hinz2017psychometric}).
 In line with previous research, we interpret these inflated rates of clinical symptomology in our sample prior to screening as suggestive of C/IE responding \cite{ophir2020turker}.
@@
 \captionsetup{width=0.88\textwidth}
-\caption{Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions.
+\caption{Absolute Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions.
 Only statistically significant correlations are specified (not corrected for multiple comparisons).
 Black Xs indicate significant correlations ablated under screening.
-No Screening = no exclusions; Accuracy Only = exclusions based on chance-level performance in the reversal-learning task; Infrequency Only = exclusions based on invalid or improbable responses to infrequency items; Both Types = exclusions based on the previous two measures.
+(The unthresholded correlations are included in the Supplement.) No Screening = no exclusions; Accuracy Only = exclusions based on chance-level performance in the reversal-learning task; Infrequency Only = exclusions based on invalid or improbable responses to infrequency items; Both Types = exclusions based on the previous two measures.
 Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
@@
 These findings suggest that many of the significant behavior-symptom correlations observed without strict participant screening may indeed be spurious correlations driven by C/IE responding.
-This was particularly the case for self-report instruments that have skewed response distributions resulting from uncommon symptom endorsement on average.
 Importantly, screening based on task behavior alone did not adequately protect against spurious symptom-behavior correlations in the presence of skewed distributions of symptom endorsement.
@@
 
-One possible objection to this interpretation is that the reduction in significant correlations following self-report screening and rejection was a result of the smaller sample size after removal of C/IE respondents (which comprised over 20\% of the sample).
+%One possible objection to this interpretation is that the reduction in significant correlations following self-report screening and rejection was a result of the smaller sample size after removal of C/IE respondents (which comprised over 20\% of the sample).
 To test this alternative hypothesis, we compared the average (absolute) correlation size before and after infrequency-based exclusions were applied, restricted to correlations that were no longer significant afterward screening (the complete tables of correlations are included in the supplement).
@@
 following rejections, suggesting that the reduction in significant correlations following screening was unlikely to be driven solely by a reduction in statistical power.
+
+One possible objection to this interpretation is that the reduction in significant correlations following- self-report screening and exclusion was a result of the reduced sample size after removal of C/IE respondents (which comprised over 20\% of the sample).
+To test this alternative hypothesis, we performed the same correlation analysis after removing random subsets of participants, fixing the sample size to that after excluding C/IE respondents.
+The rate of significant correlations in the bootstrapped samples are reported in Figure S\ref{fig:random}.
+Briefly, the pattern of significant correlations visually resembled the correlation structure prior to rejections (Figure \ref{fig:correlations}A), and statistical testing confirmed the pattern was more similar to that before screening than after screening using the infrequency measure (t = 262.49, p < 0.001).
+Thus, the reduction in significant correlations following screening was unlikely to be driven solely by a reduction in statistical power.
 
@@
 We found that, although estimated correlation magnitudes were independent of sample size (x-axis, left panel), the absolute magnitude of the behavior-symptom correlation increased with the proportion of C/IE participants (different coloured circles, left panel).
-Crucially, we found false-positive rates for spurious correlations \emph{increased} with increases in sample size in our data (right panel).
+Crucially, we found false-positive rates for spurious correlations \emph{increased} with increases in sample size in our data for all but the smallest rates of C/IE responding (right panel).
 This runs counter to a common assumption that larger sample sizes are protective against spurious correlations because they serve to mitigate measurement error.
@@
 The grey error bars indicate 95\% bootstrap confidence intervals.
-The thick dotted lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size.
+The thick dashed lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size.
+Markers are jittered along the x-axis for legibility.
 \textit{Right:} False positive rates for learning rate asymmetry ($\kappa$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants.
@@
 
-Finally, we employed a theory-agnostic modeling approach to better understand how participants suspected of engaging in C/IE responding performed on the probabilistic reversal-learning task.
-This analysis was motivated by two interrelated aims.
-First was to better understand why there was low correspondence between screening measures derived from task and self-report data; that is, to determine why participants flagged by the infrequency items were not necessarily more likely to perform at chance.
-The second was to better understand  the provenance of the particular pattern of behavior-symptom correlations we found.
+Finally, we employed a theory-agnostic modeling approach to investigate how C/IE participants on the probabilistic reversal-learning task compared to attentive participants.
+The motivation for this analysis was to better understand why C/IE responding was inconsistently predicted by chance-level performance, and also correlated with asymmetric learning rates.
 
 To characterize participants' choice behavior, we adapted the softmax regression model from \cite{seymour2012serotonin}.
-This model estimates, for each participant, how much their propensity to choose an option depends on the recent history of trial events (rewarding outcomes, non-rewarding outcomes, and choices from the preceding 5 trials; see Methods).
-The regression weights for each event, averaged within attentive and careless participants, are presented in Figure \ref{fig:regression}.
-Comparing attentive participants to those suspected of engaging in C/IE responding, we observed a credible difference (i.e.
+This model estimates, for each participant, how much their choice depends on the recent history of trial events (rewarding outcomes, non-rewarding outcomes, and choices from the preceding 5 trials; see Methods).
+The regression weights for each event, averaged within attentive and C/IE participants, are presented in Figure \ref{fig:regression}.
+Comparing attentive to C/IE participants, we observed a credible difference (i.e.
 95\% highest density intervals excluded zero) only for the $T-1$ weight for previous choice.
-Attentive participants were more likely to repeat their previous choice (i.e.
-greater choice hysteresis) than were careless participants.
+That is, attentive participants were more likely to repeat their previous choice (i.e.
+greater choice hysteresis) than were C/IE participants.
 
@@
 \captionsetup{width=0.88\textwidth}
-\caption{Softmax regression decision weights in attentive (red) and careless (blue) participants.
+\caption{Softmax regression decision weights in attentive (red) and C/IE (blue) participants.
 The weights dictate the extent to which the recent history of rewards, nonrewards, or previous choices influence current choice.
-$^* p<0.05$}
+Error bars indicate the 95\% highest density interval of each weight.
+* denotes where the 95\% highest density interval of the difference in weights excludes zero.}
 \label{fig:regression}
@@
 
-This result may be initially surprising, since one might expect choice hysteresis to result in more perseveration errors following contingency reversals, and since results reported in the previous section indicated that C/IE responding was associated with more perseveration errors.
+This result may be initially surprising, since one might expect choice hysteresis to result in more perseveration errors following contingency reversals, and since we observed in the previous section that C/IE responding was associated with more perseveration errors.
 However, choice hysteresis is adaptive in this probabilistic reversal-learning task.
-Since rewards in the task are probabilistic, ignoring unrewarding outcomes and instead performing the same response once the reward-maximizing response option has been identified is optimal, until the reversal occurs and is identified.
+Because rewards in the task are probabilistic, once the reward-maximizing response option has been identified ignoring an occasional unrewarding outcome and instead performing the same response is optimal (until the next reversal occurs and is identified).
 Interestingly, participants engaging in C/IE responding were also numerically (though not significantly) less affected by previous outcomes, suggesting that their behavior was not more adaptive, but rather just more random.
 
-This pattern of results, also mirrored in overall reduced outcome sensitivity ($\beta$), explains the pre-screening pattern of correlations with win-stay and lose-shift rates.
+This pattern of results also helps explain the pre-screening correlations with asymmetric learning rates.
+Previous work has established that, when choice hysteresis is not accounted for in reinforcement learning models, it can manifest as positive learning rate asymmetries \cite{Katahira2018-ke, sugawara2021dissociation}.
+Since C/IE participants showed increased hysteresis, which our reinforcement learning model did not explicitly account for, we should expect to find a negative correlation between learning-rate asymmetries and symptoms before C/IE participants are excluded.
+Indeed, this is what we observed above.
+
+% This pattern of results, also mirrored in overall reduced outcome sensitivity, explains the pre-screening pattern of correlations with win-stay and lose-shift rates.
 But what of the learning rate asymmetries?
-%That learning rate asymmetries ostensibly relate to C/IE responding is puzzling at first given that the softmax regression results show no credible differences in the sensitivity to history of rewarding and non-rewarding outcomes.
 This too can be explained by choice hysteresis.
@@
 
-To conclude, the theory-agnostic analysis of task behavior revealed that careless participants were less likely to engage in adaptive choice hysteresis and instead showed a pattern of responding more akin to win-stay lose-shift heuristic.
+In sum, the theory-agnostic analysis of task behavior revealed that C/IE participants exhibited a qualitatively distinct behavioral strategy on the probabilistic reversal-learning task.
+C/IE participants showed less adaptive choice hysteresis.
+Moreover, they were numerically (but not significantly) less sensitive to outcome sensitivities.
+This latter finding helps clarify in part why we observed low correspondence between task and self-report screening measures (that is, C/IE participants were not significantly more likely to respond randomly during the task).
+These results also present another hidden danger of C/IE responding: qualitatively distinct patterns of behavior under C/IE responding can bias the estimation of parameters of theoretical interest if not properly accounted for.
+
+%To conclude, the theory-agnostic analysis of task behavior revealed that careless participants exhibited less choice hysteresis and instead showed a pattern of responding more akin to win-stay lose-shift heuristic.
 This finding helps clarify in part why we observed low correspondence between task and self-report screening measures: on average, careless participants were not engaging in random responding (which would have been detected by the accuracy screening measure) but instead in satisficing behaviors.
@@
 Indeed, in general there are more ways to respond carelessly than to respond attentively to a task or self-report inventory (e.g., random response selection, straight-lining, zig-zagging, acquiescence bias) \cite{curran2016methods}.
-Indeed, we observed that a win-stay lose-shift pattern emerged as a dominant strategy in the behavioral task among participants suspected of C/IE responding.
+Indeed, we observed qualitatively distinct behavioral strategy of decreased adaptive hysteresis in C/IE participants in the reversal learning task.
 The specific response strategy a participant adopts is likely to reflect the idiosyncratic integration of multiple perceived benefits (e.g.
@@
 
-% offcut material below
-
-Before continuing, we wish to briefly highlight two additional results from our literature review.
-First, we found that the majority of studies used only a single method to detect C/IE responding.
-This is worrisome from the perspective of signal detection theory.
-As has been previously reported \cite{desimone2018dirty}, measures of C/IE responding vary in their sensitivities: some measures will identify only the most careless participants, whereas others will flag many more participants.
-As such, using only a single measure runs the risk of false positives (in the case of high sensitivity) and false negatives (in the case of low sensitivity).
-Similarly, screening methods vary in their sensitivity to different patterns of C/IE responding \cite{curran2016methods}.
-Using only one measure may thus only identify a subset of careless respondents.
-As has been discussed elsewhere, the use of multiple screening methods is encouraged to more accurately and sensitively identify C/IE responding in a dataset \cite{curran2016methods, barends2019noncompliant}.
-
-Second, we found that the majority of studies that did screen self-report survey data relied on instructed attention checks.
-This is potentially problematic, since a growing body of research disputes the efficacy of instructed items as attention checks for online studies \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}.
-Indeed, instructed attention checks are often discussed on forums for workers of online labour markets\footnote{Several examples of such discussions can be found at the Github repository for this project: \url{github.com/nivlab/sciops}}, and scripts have even been developed with the purpose to highlight words most commonly used in instructed attention checks.
-Unsurprisingly, then, it has been documented that subsets of participants may actively seek out instructed items in surveys and respond randomly elsewhere \cite{barends2019noncompliant}.
-In line with best-practice recommendations for online survey research, therefore, we encourage experimenters to use alternate means of screening for C/IE responding for self-report survey data (e.g., infrequency-item attention checks) \cite{huang2015detecting}.
-
-In sum, we found that almost a quarter of participants in our online sample were suspected of C/IE responding when screened using the infrequency-item measure, in contrast to only 7\% of participants flagged when using task accuracy as a screening measure.
-Importantly, participants suspected of C/IE responding were more likely to appear as symptomatic on self-report measures where symptom endorsement was rare on average.
-Furthermore, using three independent analyses, we identified evidence that validates the infrequency-item measures as sensitive to C/IE responding.
-These validation analyses also identified multiple forms of C/IE responding.
-Though the Cronbach's $\alpha$ result suggested at least some participants were engaging in random responding, the item-response model analysis identified participants who exhibited a preference for the rightmost response options regardless of their semantic content.
-That C/IE responding in these data manifested in more than one way is consistent with previous reports \cite{curran2016methods}, and further highlights the importance of utilizing multiple screening methods.
-
-It is important to note that these results do not give a complete picture of the likely effects of C/IE responding on symptom-behavior correlations.
-A full picture would require investigating the effects of C/IE responding over numerous different task designs, symptoms measures, sample sizes, and proportions of careless responders.
-Nevertheless, the results of this bootstrapping analysis suggest that spurious correlations driven by C/IE responding are likely to be a considerable source of potential error wherever large online samples are collected with asymmetric distributions of symptom endorsement.
-Indeed, it is also worth highlighting that false positive rates were inflated (well above the expected 5\% level given $\alpha = 0.05$) even with only 5\% of the bootstrapped participant samples engaging in C/IE responding, which further highlights how pernicious this issue is.
-% end offcut material
-
 %% BOX 1 %%
@@
     \item When collecting self-report questionnaire data, include attention-check items that flag participants who may be engaging in C/IE responding.
-We recommend following best-practice guidelines [citation] in using infrequency-item checks rather than instructed-item checks.
+We recommend following best-practice guidelines in using infrequency-item checks rather than instructed-item checks \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}.
 Participants flagged by suspicious responses on attention-check items should either be excluded from further analysis, or assessed using sensitivity analyses to ensure that observed full-sample correlations are robust to their exclusion.
@@
 Doing so helps an experimenter identify what screening methods would-be participants are already aware of and prepared to answer correctly.
+(Several examples of workers discussing common attention checks can be found at the Github repository for this project.)
 
@@
 In addition, we assessed the total number of screening measures each study used and how monetary bonuses were paid to participants (if at all).
-Finally, we note that this review was not meant to be systematic, but instead to provide a representative overview of common practices in online behavioral studies.
+We note that this review was not meant to be systematic, but instead to provide a representative overview of common practices in online behavioral studies.
 
@@
 Notably, the participants recruited from MTurk were older ($M = 7.7 \ \text{yrs}, t = 6.567, p < 0.001$) and comprised of fewer women ($z = 6.567, p = 0.011$).
-Interestingly, 38\% of MTurk users in our sample reported also completing work on Prolific, whereas only 14\% of Prolific users in our sample reported completing work on MTurk.
 
@@
 The original 16-item was recently abbreviated to a 3-item measure \cite{kertz2014psychometric}, which we use here.
-Items are scored on a 5-point scale from 1 (``not at all typical of me") to 5 (``very typical of me"), where higher scores indicate greater pathology.
-Total symptom scores range from 1 to 15 and are usually uniformly distributed.
+Items are scored on a 5-point scale from 0 (``not at all typical of me") to 4 (``very typical of me"), where higher scores indicate greater pathology.
+Total symptom scores range from 0 to 12 and are usually uniformly distributed.
 
@@
 
-To validate the infrequency items as an efficacious measure of C/IE responding, we performed three complimentary analyses. We describe each in turn below.
-
-\subparagraph{Cronbach's $\alpha$} In the first validation analysis we compared Cronbach's $\alpha$, a measure of internal consistency, when estimated from attentive participants and participants flagged by the infrequency items.
+To validate the infrequency items as a sensitive measure of C/IE responding, we performed three complimentary analyses. We describe each in turn below.
+
+\subparagraph{Cronbach's $\alpha$} We compared the average Cronbach's $\alpha$, a measure of internal consistency, between attentive and C/IE participants.
 To control for the unbalanced numbers of participants in these groups, we performed a permutation test.
@@
 
-\subparagraph{Random intercept item factor analysis} In the second validation analysis, we employ random intercept item factor analysis \cite{maydeu2006random} to detect heuristic patterns of responding.
+\subparagraph{Random intercept item factor analysis} We employed random intercept item factor analysis \cite{maydeu2006random} to detect heuristic patterns of responding.
 In the model, the probability of observing response level $k$ (of $K$ total levels) from participant $i$ on item $j$ is defined as:
@@
 Specifically, we defined the factor loading for each item as a one-hot vector where the only nonzero entry denoted that item's corresponding subscale.
-In other words, all of the items from a given subscale were assigned to their own unique factor (which was fixed to one).
+That is, all of the items from a given subscale were assigned to their own unique factor (which was fixed to one).
 As such, the model estimated one factor score per participant and subscale (akin to the 1-parameter ordinal logistic model).
@@
 
-\subparagraph{Clinical cutoffs} In the third and final validation analysis, we compared the proportion of participants in our sample reaching the threshold for clinical symptomology before and after applying exclusions.
+\subparagraph{Clinical cutoffs} We compared the proportion of participants in our sample reaching the threshold for clinical symptomology before and after applying exclusions.
 For the GAD-7, previous research has suggested a clinical cutoff score of 10 or higher \cite{lowe2008validation, hinz2017psychometric}.
@@
 
-We confirmed the model adequately fit participants' choice behavior through a series of posterior checks (see the Supplement).
+We confirmed the model adequately fit participants' choice behavior through a series of posterior checks (Figure S\ref{fig:posterior_check}).
 In particular, we confirmed the model recapitulated the group-average learning curves for each block of the experiment.
@@
 
-\subparagraph{Correlation analysis} behavior-symptom correlations (after various forms of screening and exclusion) were estimated using Spearman's rank correlation.
+\subparagraph{Correlation analysis} Behavior-symptom correlations (after various forms of screening and exclusion) were estimated using Spearman's rank correlation.
 Significance testing was performed using the percentile bootstrap method \cite{wilcox2018guide} so as to avoid making any parametric assumptions.
@@
 $\eta_n$ &   0.168* &   0.094* &   0.108* &   -0.050 &  -0.056 &  -0.020 &   0.042 \\
-$\kappa$ &  -0.208* &  -0.151* &  -0.161* &    0.026 &   0.016 &  -0.006 &  -0.064 \\
+$\kappa$ &  -0.175* &  -0.137* &  -0.147* &   -0.008 &  -0.020 &  -0.028 &  -0.061 \\
 \bottomrule
@@
 $\eta_n$ &   0.259* &   0.134* &   0.122* &   -0.021 &  -0.063 &   0.019 &   0.053 \\
-$\kappa$ &  -0.226* &  -0.150* &  -0.162* &    0.015 &   0.009 &  -0.015 &  -0.064 \\
+$\kappa$ &  -0.171* &  -0.125* &  -0.150* &   -0.016 &  -0.032 &  -0.033 &  -0.060 \\
 \bottomrule
@@
 $\eta_n$ &   0.165* &   0.067 &   0.141* &   -0.037 &  -0.089 &  -0.030 &   0.054 \\
-$\kappa$ &  -0.154* &  -0.071 &  -0.156* &    0.039 &   0.045 &   0.011 &  -0.068 \\
+$\kappa$ &  -0.111* &  -0.046 &  -0.137* &    0.011 &   0.015 &   0.002 &  -0.054 \\
 \bottomrule
@@
 $\eta_n$ &   0.196* &   0.046 &   0.098* &   -0.015 &  -0.085 &   0.008 &   0.024 \\
-$\kappa$ &  -0.171* &  -0.072 &  -0.145* &    0.035 &   0.043 &   0.001 &  -0.063 \\
+$\kappa$ &  -0.114* &  -0.046 &  -0.134* &    0.007 &   0.012 &  -0.004 &  -0.051 \\
 \bottomrule
@@
 
-\subsection*{Posterior predictive check}
+\subsection*{Bootstrapping Analysis}
 
@@
 \captionsetup{width=0.88\textwidth}
+\caption{The pattern of significant behavior-symptom correlations before (panel A) and after (panel B) screening compared to the resulting pattern when random subsets of participants (22\% of total, matched to screening using the infrequency measure) are removed (panel C).
+Panels A and B are reproduced from Figure \ref{fig:correlations} for convenience.
+Panel C: the fraction of significant correlations in 5000 bootstrapped samples.
+Panel D: The similarity of the pattern of correlations to that before and after screening using the infrequency measure.
+Similarity was calculated using the simple matching coefficient.
+** indicates statistical significance (t = 262.49, p < 0.001).}
+\label{fig:random}
+\end{figure}
+
+\subsection*{Posterior predictive check}
+
+\begin{figure}[!h]
+\includegraphics[width=16cm]{../figures/supp_02.png}
+\centering
+\captionsetup{width=0.88\textwidth}
 \caption{Posterior predictive checks for the risk-sensitive temporal difference learning model.
-\textit{Top:} Observed (black) and predicted (grey) learning curves averaged across the group.
-\textit{Bottom left:} Observed versus predicted choice accuracy for each participant.
-\textit{Bottom right:} Distribution of average predictive density across participants.}
+\textit{Panel A:} Observed (black) and predicted (blue) learning curves averaged across the group.
+\textit{Panel B:} Observed versus predicted choice accuracy for each participant.
+\textit{Panel C:} Distribution of average predictive density across participants.}
 \label{fig:posterior_check}

### 2021-04-09 manuscripts/main.tex
already ready for preprint

@@
 Of note, we demonstrate that false-positive rates for these spurious correlations \emph{increase} with sample size, contrary to common assumptions.
-We offer guidance on how researchers using this general experimental design can guard against this issue in future research; in particular, we recommend the adoption of screening methods for self-report measures that are currently uncommon in the field.
+We offer guidance on how researchers using this general experimental design can guard against this issue in future research; in particular, we recommend the adoption of screening methods for self-report measures that are currently uncommon in this field.
 }
@@
 Since participants recruited from online labour markets are typically completing experiments in their homes, they may be more likely to be distracted or multi-tasking during an experiment.
-Similarly, unsupervised participants may be more likely to use heuristic response strategies with the intention to minimise expenditure of time and cognitive effort (e.g., responding randomly on self-report surveys or behavioral tasks).
+They may also be more likely to use heuristic response strategies with the intention to minimise expenditure of time and cognitive effort (e.g., responding randomly on self-report surveys or behavioral tasks).
 Here, we will refer to such inattentive or low-effort behaviors as careless/insufficient effort (C/IE) responding \cite{huang2012detecting, curran2016methods}.
 Among researchers using online labour markets, a common view is that poor-quality data resulting from C/IE responding can simply be treated as a source of unsystematic measurement error that can be overcome with increased sample sizes \cite{gillan2016taking, chandler2020participant}.
-Similarly, it is common practice in online behavioral research to mitigate poor-quality data using the same screening methods that are typically used in in-person data collection (e.g., excluding participants who perform at- or below-chance on behavioral tasks).
-
-Here we wish to draw attention to an underappreciated feature of online psychiatric research using self-report symptom surveys.
+Common practice in online behavioral research is to mitigate poor-quality data using the same screening methods that are typically used in in-person data collection (e.g., excluding participants who perform at- or below-chance on behavioral tasks).
+However, these methods may be specifically inappropriate for online psychiatry studies, as we detail below.
+
+Here we wish to draw special attention to an underappreciated feature of online psychiatric research using self-report symptom surveys.
 In such surveys, participants rate their endorsement of various psychiatric symptoms and, since most individuals in the general population tend to endorse no or few symptoms in many symptom domains, the resulting ground-truth symptom distributions tend to be heavily positively skewed \cite{lowe2008validation, tomitaka2018distributional}.
@@
 First, we asked to what extent recent studies in computational psychiatry screen participants based on self-report symptom data.
-We found that the majority of these studies did not screen participants' survey data at all, and that very few followed best-practice recommendations for survey data screening \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}.
+We found that the majority of these studies did not screen participants' survey data at all, and that very few followed best-practice recommendations for survey data screening.
 We then asked whether behavioral screening alone was sufficient to identify participants engaging in C/IE responding on psychiatric symptom surveys.
@@
 Each colored dot represents the symptom score for one participant.
-The black dots display the average score within each group (error bars denote 95\% bootstrap confidence interval).
-The scales are ordered according to their estimated skew from top-left (7-up) to bottom-right (PSWQ).
+Black circles: average score within each group (error bars denote 95\% bootstrap confidence interval).
+Shaded plots: estimated distribution of responses for each group of participants.
+The scales are ordered approximately according to their estimated skew (see Table 2) from top-left (7-up) to bottom-right (PSWQ).
 The average level of symptom endorsement is most markedly different between groups in measures with lowest overall rates of endorsement.}
@@
 In turn, a mean-shift is expected to occur when the overall rate of symptom endorsement is low.
-To assess this, we visually inspected for each self-report measure the distribution of symptom scores in participants flagged by the infrequency measure vs.
-those that were not (Figure \ref{fig:distributions}).
-In line with our predictions, the average level of symptom endorsement was noticeably exaggerated in C/IE-responding participants for the symptom measures where symptom scores were most positively-skewed (7-up, 7-down, GAD-7).
+In line with our predictions, the average level of symptom endorsement was noticeably exaggerated in C/IE-responding participants for the symptom measures where symptom scores were most positively-skewed (7-up, 7-down, GAD-7; see Figure \ref{fig:distributions}).
 In contrast, where there was higher rates of symptom endorsement overall, the distributions of symptom scores between the two groups of participants were less noticeably distinct.
-Permutation testing confirmed that observed mean-shifts in symptom scores for C/IE participants were statistical significant for the majority of the symptom measures (Table \ref{tab:validation}).
+Permutation testing confirmed that observed mean-shifts in symptom scores for C/IE participants were statistically significant for the majority of symptom measures (Table \ref{tab:validation}).
 
@@
 Skew: the empirical skewness of the distribution of total symptom scores.
-Total score: the average symptom score between attentive and C/IE participants.
-* indicates statistical significance.
-Cronbach's $\alpha$: a measure of response consistency, where greater values closer to 1 indicate greater consistency in responses.
+Total score: the average symptom score across attentive and C/IE participants.
+Stars indicate statistical significance at $p<0.05$.
+Cronbach's $\alpha$: a measure of response consistency, where values closer to 1 indicate greater consistency in responses.
 \% Clinical Cutoff: the percentage of participants reaching threshold for clinical symptomology before and after screening based on the infrequency measure.
@@
 \caption{Absolute Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions.
-Only statistically significant correlations are specified (not corrected for multiple comparisons).
+Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons; all correlations are shown in the Supplement).
 Black Xs indicate significant correlations ablated under screening.
-(The unthresholded correlations are included in the Supplement.) No Screening = no exclusions; Accuracy Only = exclusions based on chance-level performance in the reversal-learning task; Infrequency Only = exclusions based on invalid or improbable responses to infrequency items; Both Types = exclusions based on the previous two measures.
+No Screening = no exclusions; Accuracy Only = exclusions based on chance-level performance in the reversal-learning task; Infrequency Only = exclusions based on invalid or improbable responses to infrequency items; Both Types = exclusions based on the previous two measures.
 Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
@@
 accuracy, inverse temperature).
-This pattern of correlations were largely similar when rejections were applied based on both task and self-report screening measures (Figure \ref{fig:correlations}D).
-We also note also that with stricter screening, the remaining significant correlations were, for the most part (but not always), weaker.
+This pattern of correlations was largely similar when rejections were applied based on both task and self-report screening measures (Figure \ref{fig:correlations}D).
+We also note that with stricter screening, the remaining significant correlations were, for the most part (but not always), weaker.
 
@@
 
-%One possible objection to this interpretation is that the reduction in significant correlations following self-report screening and rejection was a result of the smaller sample size after removal of C/IE respondents (which comprised over 20\% of the sample).
-To test this alternative hypothesis, we compared the average (absolute) correlation size before and after infrequency-based exclusions were applied, restricted to correlations that were no longer significant afterward screening (the complete tables of correlations are included in the supplement).
-On average, we observed a significant reduction in correlation effect sizes ($\Delta \rho = -0.05, t = -2.87, p = 0.012$).
-following rejections, suggesting that the reduction in significant correlations following screening was unlikely to be driven solely by a reduction in statistical power.
-
-One possible objection to this interpretation is that the reduction in significant correlations following- self-report screening and exclusion was a result of the reduced sample size after removal of C/IE respondents (which comprised over 20\% of the sample).
-To test this alternative hypothesis, we performed the same correlation analysis after removing random subsets of participants, fixing the sample size to that after excluding C/IE respondents.
-The rate of significant correlations in the bootstrapped samples are reported in Figure S\ref{fig:random}.
-Briefly, the pattern of significant correlations visually resembled the correlation structure prior to rejections (Figure \ref{fig:correlations}A), and statistical testing confirmed the pattern was more similar to that before screening than after screening using the infrequency measure (t = 262.49, p < 0.001).
+One possible objection to this interpretation is that the reduction in significant correlations following self-report screening was a result of the reduced sample size after removal of C/IE respondents (which comprised over 20\% of the sample).
+To test this alternative hypothesis, we performed the same correlation analysis after removing random subsets of participants, fixing the sample size to that obtained after excluding C/IE respondents.
+In this case, the pattern of significant correlations was more similar to that before screening than after screening using the infrequency measure (t = 262.49, $p < 0.001$; Figure \ref{fig:random}, compare to Figure \ref{fig:correlations}A).
 Thus, the reduction in significant correlations following screening was unlikely to be driven solely by a reduction in statistical power.
@@
 \textit{Right:} False positive rates for learning rate asymmetry ($\kappa$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants.
-False positive rate was calculated as the proportion of bootstrap samples in which the correlation between $\kappa$ and 7-down was statistically significant.}
+False positive rate was calculated as the proportion of bootstrap samples in which the correlation between $\kappa$ and 7-down was statistically significant.
+The horizontal dotted line denotes the expected false positive rate at $\alpha = .05$.}
 \label{fig:bootstrap}
@@
 Error bars indicate the 95\% highest density interval of each weight.
-* denotes where the 95\% highest density interval of the difference in weights excludes zero.}
+* denotes where the 95\% highest density interval of the difference in weights excluded zero.}
 \label{fig:regression}
@@
 Previous work has established that, when choice hysteresis is not accounted for in reinforcement learning models, it can manifest as positive learning rate asymmetries \cite{Katahira2018-ke, sugawara2021dissociation}.
-Since C/IE participants showed increased hysteresis, which our reinforcement learning model did not explicitly account for, we should expect to find a negative correlation between learning-rate asymmetries and symptoms before C/IE participants are excluded.
+Since C/IE participants showed decreased hysteresis, which our reinforcement learning model did not explicitly account for, we should expect to find a negative correlation between learning-rate asymmetries and symptoms before C/IE participants are excluded.
 Indeed, this is what we observed above.
-
-% This pattern of results, also mirrored in overall reduced outcome sensitivity, explains the pre-screening pattern of correlations with win-stay and lose-shift rates.
-But what of the learning rate asymmetries?
-This too can be explained by choice hysteresis.
-Previous work has established that, when choice hysteresis is not accounted for in reinforcement learning models, it can manifest as positive learning rate asymmetries \cite{Katahira2018-ke}.
-As such, given that attentive participants show increased repetition, which our reinforcement learning model did not explicitly account for, we should expect to find a negative (positive) correlation between positive (negative) learning rates and C/IE responding.
-Indeed, this is precisely the pattern of correlations observed above.
 
@@
 C/IE participants showed less adaptive choice hysteresis.
-Moreover, they were numerically (but not significantly) less sensitive to outcome sensitivities.
-This latter finding helps clarify in part why we observed low correspondence between task and self-report screening measures (that is, C/IE participants were not significantly more likely to respond randomly during the task).
+Moreover, they were numerically (but not significantly) less sensitive to outcomes.
+The latter finding helps clarify in part why we observed low correspondence between task and self-report screening measures (that is, C/IE participants were not significantly more likely to respond randomly during the task).
 These results also present another hidden danger of C/IE responding: qualitatively distinct patterns of behavior under C/IE responding can bias the estimation of parameters of theoretical interest if not properly accounted for.
-
-%To conclude, the theory-agnostic analysis of task behavior revealed that careless participants exhibited less choice hysteresis and instead showed a pattern of responding more akin to win-stay lose-shift heuristic.
-This finding helps clarify in part why we observed low correspondence between task and self-report screening measures: on average, careless participants were not engaging in random responding (which would have been detected by the accuracy screening measure) but instead in satisficing behaviors.
-Most importantly, the results present another hidden danger of C/IE responding.
-When participants utilize heuristic decision-making, this may manifest in difficult-to-predict forms when computational models are misspecified.
-Thus, C/IE responding may not only drive spurious correlations but also spurious inferences about what behavior-symptom correlations entail.
 
@@
 Viewed from the perspective of effort expenditure, our results suggest that participants appraised the cost/benefit trade-off differently for behavioral tasks and self-report surveys.
-Specifically, we found that only 7\% of participants were at chance-level performance in our (easy) task, compared to more than 22\% of participants who failed one or more (even easier) attention-check items in the self-report surveys.
+Specifically, we found that only 7\% of participants were at chance-level performance in our task, compared to more than 22\% of participants who failed one or more attention-check items in the self-report surveys.
 Moreover, different measures of C/IE responding were weakly or not at all correlated between task behavior and self-report responses.
@@
 One complicating factor for our argument is that C/IE responding may manifest in other ways than simply random responding for both behavioral tasks and self-report surveys.
-Indeed, in general there are more ways to respond carelessly than to respond attentively to a task or self-report inventory (e.g., random response selection, straight-lining, zig-zagging, acquiescence bias) \cite{curran2016methods}.
-Indeed, we observed qualitatively distinct behavioral strategy of decreased adaptive hysteresis in C/IE participants in the reversal learning task.
+Indeed, there are more ways to respond carelessly than to respond attentively to a task or self-report inventory (e.g., random response selection, straight-lining, zig-zagging, acquiescence bias) \cite{curran2016methods}.
+Here we observed that C/IE participants failed to maintain previously correct choices after an occasional non-reward in the probabilistic reversal learning task, perhaps responding more locally based on the most immediate reward.
 The specific response strategy a participant adopts is likely to reflect the idiosyncratic integration of multiple perceived benefits (e.g.
@@
 
-One concern with performing rigorous screening and exclusion of participants based on C/IE detection methods is that we might inadvertently introduce an overcontrol bias \cite{elwert2014endogenous}.
+One major concern with performing rigorous screening and exclusion of participants based on C/IE detection methods is that we might inadvertently introduce an overcontrol bias \cite{elwert2014endogenous}.
 That is, we have been treating a tendency towards C/IE responding as independent from psychopathology; however, to the extent that C/IE responding reflects lack of motivation \cite{barch2015mechanisms}, avoidance of effort \cite{cohen2001impairments, culbreth2016negative}, or more frequent lapses of attention \cite{kane2016individual, robison2017neurotic}, one might hypothesise a true underlying association between psychopathology and careless responding in online studies.
@@
 
-Although, in theory, overcontrol bias may reduce power to detect legitimate symptom-behavior correlations, for overcontrol based on self-report questionnaires to seriously impact results it would have to be the case that symptomatic participants frequently endorsed improbable or impossible responses to infrequency-item checks (e.g., responding `Agree' to ``I competed in the 1917 Olympic Games").
-We would argue that even if such participants truly are experiencing severe symptoms of motivation or attention, there is likely to be limited utility in measuring these symptoms using a self-report measure that they are unable to complete veridically.
+However, when using self-report questionnaires for screening, for overcontrol to seriously impact results it would have to be the case that symptomatic participants frequently endorse improbable or impossible responses to infrequency-item checks (e.g., responding `Agree' to ``I competed in the 1917 Olympic Games").
+In this case, and even if such participants truly are experiencing severe symptoms of motivation or attention, there is likely to be limited utility in measuring these symptoms using a self-report measure that they are unable to complete veridically.
 A similar rationale underlies the widespread use of semi-structured interviews and other clinician-report measures rather than self-report measures for in-clinic psychiatric research.
-We would argue that, if the psychiatric phenomenon being studied is such that this issue warrants concern, the research question may be better suited to an in-person study design involving participants in the clinic who meet full diagnostic criteria than a correlational design involving an online convenience sample.
+We would therefore argue that, if the psychiatric phenomenon being studied is such that this issue warrants concern, the research question may be better suited to an in-person study design involving participants in the clinic who meet full diagnostic criteria than a correlational design involving an online convenience sample.
 
@@
 Indeed, we found in our sample roughly 10\% of participants endorsing symptoms consistent with clinical levels of depression, and approximately 20\% consistent with clinical levels of acute anxiety.
-These estimates are within the realm of epidemiological norms \cite{kessler2012twelve, lowe2008validation, yarrington2021impact}..
+These estimates are within the realm of epidemiological norms \cite{kessler2012twelve, lowe2008validation, yarrington2021impact}.
 We also observed some positive correlations between anxiety and choice behavior that were consistent with effects found in previous literature \cite{huang2017computational, harle2017anhedonia, garrett2018updating}.
@@
 
-All code, data, and analysis materials are publicly available at \url{github.com/nivlab/sciops}.
+All code, data, and analysis materials are publicly available at \url{https://github.com/nivlab/sciops}.
 
@@
 The task was programmed in jsPsych \cite{deleeuw_2015_jspsych} and distributed using custom web-application software.
-The experiment code is available at \url{github.com/nivlab/ThreeArmJS}, and the web-software is available at \url{github.com/nivlab/nivturk}.
-A playable demo of the task is available at \url{nivlab.github.io/ThreeArmJS}.
+The experiment code is available at \url{https://github.com/nivlab/ThreeArmJS}, and the web-software is available at \url{https://github.com/nivlab/nivturk}.
+A playable demo of the task is available at \url{https://nivlab.github.io/ThreeArmJS}.
 
@@
 
-We confirmed the model adequately fit participants' choice behavior through a series of posterior checks (Figure S\ref{fig:posterior_check}).
+We confirmed the model adequately fit participants' choice behavior through a series of posterior checks (Figure \ref{fig:posterior_check}).
 In particular, we confirmed the model recapitulated the group-average learning curves for each block of the experiment.
@@
 Parameters were sampled with Gaussian priors with $\mu = 0$ and $\sigma = 5$.
+\section{Acknowledgements}
+
+The authors are grateful to Agnes Norbury, Alexandra Pike, and Oliver Robinson for helpful discussion.
+This work was funded in part by NIMH 5R01MH119511-02 and ., SZ was supported by an NSF Graduate Research Fellowship.
+DB was supported by an Early Career Fellowship from the Australian National Health and Medical Research Council (\#1165010).
 
@@
 \renewcommand{\thetable}{S\arabic{table}}
+\renewcommand{\thefigure}{S\arabic{figure}}
 
@@
 
-The following are the instructions given to participants for the probabalistic reversal learning task.
+The following are the instructions given to participants for the probabilistic reversal learning task.
 As a reminder, the task was given a fishing-themed cover story.
@@
 
-\begin{table}[h!]
+\begin{table}[H]
 \centering
@@
 
+\clearpage
+
 \subsection*{Bootstrapping Analysis}
-
-\begin{figure}[!h]
+\begin{figure}[H]
 \includegraphics[width=16cm]{../figures/supp_01.png}
@@
 Panel C: the fraction of significant correlations in 5000 bootstrapped samples.
-Panel D: The similarity of the pattern of correlations to that before and after screening using the infrequency measure.
+Panel D: The similarity of the pattern of correlations after removal of random subsets to that before and after screening using the infrequency measure.
 Similarity was calculated using the simple matching coefficient.
-** indicates statistical significance (t = 262.49, p < 0.001).}
+Random removal subsets were significantly more similar to the ``No Screening" than to the ``Infrequency" screening datasets (t = 262.49, $p < 0.001$).}
 \label{fig:random}
@@
 
+\clearpage
 \subsection*{Posterior predictive check}
 
-\begin{figure}[!h]
+\begin{figure}[H]
 \includegraphics[width=16cm]{../figures/supp_02.png}

### 2021-04-11 manuscripts/main.tex
ready for submission

@@
 \abstract{
-A common research design in the field of computational psychiatry involves leveraging the power of online participant recruitment to assess correlations between behaviour in cognitive tasks and the self-reported severity of psychiatric symptoms in large, diverse samples.
+A common research design in the field of computational psychiatry involves leveraging the power of online participant recruitment to assess correlations between behavior in cognitive tasks and the self-reported severity of psychiatric symptoms in large, diverse samples.
 Although large online samples have many advantages for psychiatric research, some potential pitfalls of this research design are not widely understood.
-Here we detail circumstances in which entirely spurious correlations may arise between task behaviour and symptom severity as a result of inadequate screening of careless or low-effort responding on psychiatric symptom surveys.
+Here we detail circumstances in which entirely spurious correlations may arise between task behavior and symptom severity as a result of inadequate screening of careless or low-effort responding on psychiatric symptom surveys.
 Specifically, since many psychiatric symptom surveys have asymmetric ground-truth score distributions in the general population, participants who respond carelessly on these surveys will show apparently elevated symptom levels.
-If these participants are similarly careless in their task performance, and are not excluded from analysis, this may result in a spurious association between greater symptom scores and worse behavioural task performance.
+If these participants are similarly careless in their task performance, and are not excluded from analysis, this may result in a spurious association between greater symptom scores and worse behavioral task performance.
 Here, we demonstrate exactly this pattern of results in $N = 386$ participants recruited online to complete a self-report symptom battery and a short reversal-learning choice task.
-We show that many behaviour-symptom correlations are entirely abolished when participants flagged for careless responding on surveys are excluded from analysis.
+We show that many behavior-symptom correlations are entirely abolished when participants flagged for careless responding on surveys are excluded from analysis.
 We also show that exclusion based on task performance alone is not sufficient to prevent these spurious correlations.
@@
 In recent years, online labour markets (e.g.
-Amazon Mechanical Turk, Prolific, Crowdflower) have become increasingly popular as a source of research participants in the behavioral sciences \cite{stewart2017crowdsourcing}, in no small part due to the ease with which these services allow for recruitment of large, diverse samples.
+Amazon Mechanical Turk, Prolific, Cloudresearch) have become increasingly popular as a source of research participants in the behavioral sciences \cite{stewart2017crowdsourcing}, in no small part due to the ease with which these services allow for recruitment of large, diverse samples.
 The advantages of online data collection have also begun to be recognized in psychiatric research \cite{chandler2016conducting}, where this method offers several distinct advantages over traditional approaches to participant recruitment.
@@
 
-When participants complete both symptom surveys and behavioral tasks---a common study design in computational psychiatry---this artefact has the potential to induce spurious correlations between symptom self-reports and task behavior.
+When participants complete both symptom surveys and behavioral tasks---a common study design in computational psychiatry---this artifact has the potential to induce spurious correlations between symptom self-reports and task behavior.
 That is, while C/IE behavior is traditionally thought of as a source of noise that can result in type II (false negative) errors, here we suggest that in large-scale online psychiatric studies it can instead result in type I (false positive) errors.
@@
 \textit{Left:} When symptoms are moderately common in the general population, C/IE respondents (blue) are indistinguishable from attentive participants (red) in self-report measures (x-axis, marginal distribution shown on top).
-Despite the lower task performance of C/IE respondents (y-axis), no correlation arises between symptom scores and task performance (dots are participants drawn from the shown distributions, with \~15\% C/IE participants; dashed line shows the (lack of) correlation.) \textit{Right:} When symptoms are rare in the general population, careless respondents appear symptomatic in self-report measures.
+Despite the lower task performance of C/IE respondents (y-axis), no correlation arises between symptom scores and task performance (dots are participants drawn from the shown distributions, with 15\% C/IE participants; dashed line shows the (lack of) correlation.) \textit{Right:} When symptoms are rare in the general population, careless respondents appear symptomatic in self-report measures.
 As a result, self-report symptom scores show a significant correlation with task performance.}
@@
 Taken together, these results suggest that measures of C/IE responding in task and self-report data do not identify the same set of participants.
-This means that solely excluding participants on the basis of poor behavioural performance---the most common approach in online studies---is unlikely to identify participants who engage in C/IE responding on self-report surveys.
+This means that solely excluding participants on the basis of poor behavioral performance---the most common approach in online studies---is unlikely to identify participants who engage in C/IE responding on self-report surveys.
 
@@
 Unfortunately, a literature review identified this type of screening as the most common practice in online computational psychiatry studies.
-We recommend instead to screen and exclude participants based on responding on surveys, a practice that abolished many spurious behaviour-symptom correlations in our data.
+We recommend instead to screen and exclude participants based on responding on surveys, a practice that abolished many spurious behavior-symptom correlations in our data.
 
@@
 Parameters were sampled with Gaussian priors with $\mu = 0$ and $\sigma = 5$.
+
 \section{Acknowledgements}
@@
 The authors are grateful to Agnes Norbury, Alexandra Pike, and Oliver Robinson for helpful discussion.
-This work was funded in part by NIMH 5R01MH119511-02 and ., SZ was supported by an NSF Graduate Research Fellowship.
+The research reported in this manuscript was supported in part by the National Institute of Mental Health (NIMH) under award number 5R01MH119511-02, and by the National Center for Advancing Translational Sciences (NCATS), a component of the National Institute of Health (NIH), under award number UL1TR003017.
+The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.
+SZ was supported by an NSF Graduate Research Fellowship.
 DB was supported by an Early Career Fellowship from the Australian National Health and Medical Research Council (\#1165010).

### 2022-11-09 manuscripts/main.tex
checkpoint revisions progress

@@
 
+% setup references
+\defbibheading{main}{}
+\defbibheading{supp}{}
+\addbibresource[label=main]{main.bib}
+\addbibresource[label=supp]{supp.bib}
+\renewcommand*{\bibfont}{\small}
+
 % specify link style
-\addbibresource{main.bib}
-\renewcommand*{\bibfont}{\small}
 \hypersetup{
@@
 \affil[2]{Department of Psychology, Princeton University, USA}
-\affil[3]{Department of Psychiatry, Monash University, Australia}
+\affil[3]{School of Psychological Sciences, Monash University, Australia}
 
@@
 
+\begin{refsection}[main]
 \section{Introduction}
@@
 In this situation, the assumption that C/IE responding merely increases unsystematic measurement noise becomes untenable.
-Because of the positive skew in the ground-truth symptom distribution, participants who respond carelessly to the symptom survey are more likely to report higher levels of symptom endorsement relative to participants who complete the survey accurately \cite{chandler2020participant, ophir2020turker}.
+Because of the positive skew in the ground-truth symptom distribution, participants who respond carelessly to the symptom survey are more likely to report higher levels of symptom endorsement relative to participants who complete the survey accurately \cite{chandler2020participant, ophir2020turker, king2018random}.
 Consequently, unless C/IE survey responses are carefully identified and removed, a considerable proportion of putatively symptomatic individuals in an online sample may, in fact, be participants who have not engaged with the experiment with sufficient attention or effort.
@@
 We then asked whether behavioral screening alone was sufficient to identify participants engaging in C/IE responding on psychiatric symptom surveys.
-In a new dataset from two separate online labour marketplaces, we found that screening based on task behavior fails to adequately identify participants engaging in C/IE responding on surveys.
+In two new datasets from two separate online labour marketplaces, we found that screening based on task behavior fails to completely identify participants engaging in C/IE responding on surveys.
 Lastly, we investigated whether, under these circumstances, C/IE responding led to spurious correlations between symptom severity and task performance for positively-skewed symptom measures.
-Consistent with the logic set out above, we confirmed that failure to appropriately screen out C/IE survey responding in the proof-of-concept dataset that we collected would have produced a number of spurious correlations between task behavior and self-reported symptoms of depression and anxiety that are abolished when data are screened properly.
+Consistent with the logic set out above, we confirmed that failure to appropriately screen out C/IE survey responding in the proof-of-concept datasets that we collected would have produced a number of spurious correlations between task behavior and self-reported symptoms that are abolished when data are screened more thoroughly.
 
@@
 \midrule
-7-up   &  0.81 &    3.87 &   10.15 &  -13.31^* &    0.84 &    0.84 &     13.0\% &       4.0\% \\
-7-down &  0.76 &    4.75 &   10.68 &   -9.99^* &    0.94 &    0.88 &     17.4\% &       9.3\% \\
-GAD-7  &  0.75 &    4.86 &    9.73 &   -7.88^* &    0.92 &    0.87 &     25.9\% &      17.3\% \\
+7-up   &  0.81 &    3.87 &   10.15 &  $-13.31^*$ &    0.84 &    0.84 &     13.0\% &       4.0\% \\
+7-down &  0.76 &    4.75 &   10.68 &   $-9.99^*$ &    0.94 &    0.88 &     17.4\% &       9.3\% \\
+GAD-7  &  0.75 &    4.86 &    9.73 &   $-7.88^*$ &    0.92 &    0.87 &     25.9\% &      17.3\% \\
 BIS    &  0.78 &    7.74 &    7.92 &   -0.54 &    0.83 &    0.62 &        - &             - \\
 BAS    &  0.17 &   15.73 &   16.16 &   -0.91 &    0.84 &    0.71 &        - &             - \\
-SHAPS  &  0.26 &    8.02 &   10.85 &   -4.04^* &    0.90 &    0.81 &     17.9\% &      14.6\% \\
-PSWQ   &  0.19 &    4.78 &    6.74 &   -4.78^* &    0.93 &    0.81 &      7.3\% &       7.0\% \\
+SHAPS  &  0.26 &    8.02 &   10.85 &   $-4.04^*$ &    0.90 &    0.81 &     17.9\% &      14.6\% \\
+PSWQ   &  0.19 &    4.78 &    6.74 &   $-4.78^*$ &    0.93 &    0.81 &      7.3\% &       7.0\% \\
 \bottomrule
@@
 
-\subsection{C/IE responding manifests as qualitatively distinct behavioral strategy}
-
-Finally, we employed a theory-agnostic modeling approach to investigate how C/IE participants on the probabilistic reversal-learning task compared to attentive participants.
-The motivation for this analysis was to better understand why C/IE responding was inconsistently predicted by chance-level performance, and also correlated with asymmetric learning rates.
-
-To characterize participants' choice behavior, we adapted the softmax regression model from \cite{seymour2012serotonin}.
-This model estimates, for each participant, how much their choice depends on the recent history of trial events (rewarding outcomes, non-rewarding outcomes, and choices from the preceding 5 trials; see Methods).
-The regression weights for each event, averaged within attentive and C/IE participants, are presented in Figure \ref{fig:regression}.
-Comparing attentive to C/IE participants, we observed a credible difference (i.e.
-95\% highest density intervals excluded zero) only for the $T-1$ weight for previous choice.
-That is, attentive participants were more likely to repeat their previous choice (i.e.
-greater choice hysteresis) than were C/IE participants.
-
-\begin{figure}[!b]
-\includegraphics[width=16cm]{../figures/main_03c.png}
-\centering
-\captionsetup{width=0.88\textwidth}
-\caption{Softmax regression decision weights in attentive (red) and C/IE (blue) participants.
-The weights dictate the extent to which the recent history of rewards, nonrewards, or previous choices influence current choice.
-Error bars indicate the 95\% highest density interval of each weight.
-* denotes where the 95\% highest density interval of the difference in weights excluded zero.}
-\label{fig:regression}
-\end{figure}
-
-This result may be initially surprising, since one might expect choice hysteresis to result in more perseveration errors following contingency reversals, and since we observed in the previous section that C/IE responding was associated with more perseveration errors.
-However, choice hysteresis is adaptive in this probabilistic reversal-learning task.
-Because rewards in the task are probabilistic, once the reward-maximizing response option has been identified ignoring an occasional unrewarding outcome and instead performing the same response is optimal (until the next reversal occurs and is identified).
-Interestingly, participants engaging in C/IE responding were also numerically (though not significantly) less affected by previous outcomes, suggesting that their behavior was not more adaptive, but rather just more random.
-
-This pattern of results also helps explain the pre-screening correlations with asymmetric learning rates.
-Previous work has established that, when choice hysteresis is not accounted for in reinforcement learning models, it can manifest as positive learning rate asymmetries \cite{Katahira2018-ke, sugawara2021dissociation}.
-Since C/IE participants showed decreased hysteresis, which our reinforcement learning model did not explicitly account for, we should expect to find a negative correlation between learning-rate asymmetries and symptoms before C/IE participants are excluded.
-Indeed, this is what we observed above.
-
-In sum, the theory-agnostic analysis of task behavior revealed that C/IE participants exhibited a qualitatively distinct behavioral strategy on the probabilistic reversal-learning task.
-C/IE participants showed less adaptive choice hysteresis.
-Moreover, they were numerically (but not significantly) less sensitive to outcomes.
-The latter finding helps clarify in part why we observed low correspondence between task and self-report screening measures (that is, C/IE participants were not significantly more likely to respond randomly during the task).
-These results also present another hidden danger of C/IE responding: qualitatively distinct patterns of behavior under C/IE responding can bias the estimation of parameters of theoretical interest if not properly accounted for.
+\subsection{Pattern of results generalizes to alternative tasks, self-report measures, and quality assurance protocols}
+
+One possible concern with the results presented so far is that they are specific to one specific instantiation of our experimental design.
+For example, with more stringent quality assurance protocols during participant recruitment, or perhaps a different task or set of self-report measures, one might wonder if spurious correlations would remain such a threat.
+
+To evaluate the generalizability of our findings, we therefore conducted a conceptual replication experiment in which an independent sample of N=393 participants (N=193 from MTurk, N=200 from Prolific) completed a more difficult cognitive task, the two-step task \cite{daw2011model}, and an alternate set of self-report measures (see Appendix B for complete details).
+Importantly, participants were recruited \textit{after} CloudResearch and Prolific implemented new protocols to improve data quality on their respective platforms.
+Moreover, participants completed self-report symptom measures as before, but also personality measures with no hypothesized relationship to model-based planning behavior on the two-step task.
+
+For the sake of brevity, only the main pattern of finding are reported here (the complete results are reported in Appendix B).
+In the replication sample, 55 out of 393 participants (14\%) endorsed a logically invalid or improbable response on one or more of the infrequency items when completing the self-report measures.
+This is roughly two-thirds of the number of participants who were flagged for C/IE responding in the original study, suggesting that the newer quality assurance protocols are at least partially effective.
+In the self-report symptom measures, we replicated the finding that total scores were noticeably exaggerated in participants suspected of C/IE responding only for the symptom measures where overall rates of symptom endorsement were the lowest.
+Similarly, we again found that task and self-report screening measures showed low correspondence; that is, excluding participants on the basis of poor behavioral performance was ineffective for identifying and removing participants who engaged in C/IE responding on self-report surveys.
+Finally, with no exclusions applied, we observed spurious correlations between performance on the two-step task and total scores, only for the self-report measures (both symptom and personality measures) with a mean-shift in scores between attentive participants and participants suspected of C/IE responding.
+In contrast with our original findings, however, we found that excluding participants based on self-report \textit{or} task screening measures was sufficient to ablate these spurious correlations.
+
+In sum, we replicated most of the main findings from the original study in an independent sample of participants completing a novel set of tasks and self-report measures.
+Although we found that screening on task behavior was sufficient to protect against spurious correlations in the replication sample, it is difficult to generalize and predict when or why this might be the case for other datasets.
+As such, screening for C/IE responding in both task and self-report measures still remains the best approach to protect oneself against the possibility of spurious correlations.
+
+\subsection{Individuals with and without diagnosed psychiatric disorders fail attention checks at similar rates}
+
+One major concern with performing rigorous screening and exclusion of participants based on C/IE detection methods is that we might inadvertently introduce an overcontrol bias \cite{elwert2014endogenous}.
+That is, to this point we have treated the tendency towards C/IE responding as independent from psychopathology.
+However, to the extent that C/IE responding reflects lack of motivation \cite{barch2015mechanisms}, avoidance of effort \cite{cohen2001impairments, culbreth2016negative}, or more frequent lapses of attention \cite{kane2016individual, robison2017neurotic}, one might hypothesise a true underlying association between psychopathology and careless responding in online studies.
+In such cases, it is plausible that rigorous screening of C/IE responding might lead to the differential exclusion of truly symptomatic participants.
+
+To explore this possibility, we embedded attention checks into the self-report measures of two studies of patients with major depressive disorder (see Appendix C for complete details).
+Specifically, a total of N=45 psychiatric patients and N=20 healthy controls completed a series of self-report symptom measures, online, on their computers from the comfort of their homes.
+(The psychiatric patients were confirmed to meet criteria for a diagnosis of major depressive disorder through a structured clinical interview.) In total, 16 of 65 (24.6\%) participants failed one or more attention checks.
+Subdivided by group, 6 of 20 (30\%) healthy participants and 10 of 45 (22\%) psychiatric participants were flagged for C/IE responding.
+
+Using these data, we computed pairwise Bayes factors comparing three candidate models: attention check failure rates are equal between healthy and psychiatric participants (M1); failure rates are greater in psychiatric patients (M2); and failure rates are greater in healthy participants (M3).
+A model assuming equal rates of failure between healthy and psychiatric participants was 2.88 times more likely than the model assuming greater rates for psychiatric patients.
+In turn, a model assuming lower rates of failure for psychiatric patients was 1.27 times more likely than the model assuming equal rates.
+Finally, a model assuming lower rates of failure for psychiatric patients was 3.65 times more likely than the model assuming higher rates for psychiatric patients.
+Only the final comparison exceeds the cutoff value of 3, which is conventionally treated as the minimal amount of evidence required to treat a difference in model fit as meaningful.
+Though the small sample precludes any definitive conclusion, it is noteworthy that the model least consistent with the data is the one where psychiatric patients are more likely to fail infrequency item attention checks.
+These data suggest that it is unlikely that participants flagged for C/IE responding in the main analyses were disproportionately individuals with high psychiatric symptom severity.
+Accordingly, we conclude that our results are unlikely to be overly influenced by an overcontrol bias.
 
@@
 Indeed, there are more ways to respond carelessly than to respond attentively to a task or self-report inventory (e.g., random response selection, straight-lining, zig-zagging, acquiescence bias) \cite{curran2016methods}.
-Here we observed that C/IE participants failed to maintain previously correct choices after an occasional non-reward in the probabilistic reversal learning task, perhaps responding more locally based on the most immediate reward.
 The specific response strategy a participant adopts is likely to reflect the idiosyncratic integration of multiple perceived benefits (e.g.
@@
 
-One major concern with performing rigorous screening and exclusion of participants based on C/IE detection methods is that we might inadvertently introduce an overcontrol bias \cite{elwert2014endogenous}.
-That is, we have been treating a tendency towards C/IE responding as independent from psychopathology; however, to the extent that C/IE responding reflects lack of motivation \cite{barch2015mechanisms}, avoidance of effort \cite{cohen2001impairments, culbreth2016negative}, or more frequent lapses of attention \cite{kane2016individual, robison2017neurotic}, one might hypothesise a true underlying association between psychopathology and careless responding in online studies.
-In such cases, it is plausible that rigorous screening of C/IE responding might lead to the differential exclusion of truly symptomatic participants.
-
+One objection to the rigorous screening and exclusion of participants based on C/IE detection methods is that we might inadvertently introduce an overcontrol bias.
+That is, to the extent that C/IE responding might reflect symptoms common to psychopathology (e.g.
+low motivation, effort avoidance, inattentiveness), rigorous screening of C/IE responding might lead to the differential exclusion of truly symptomatic participants.
+To explore this possibility, we embedded attention checks into the self-report measures of two studies of patients with major depressive disorder.
+Though our final sample was small, we did not find evidence for the proposition that patients were more likely to fail attention checks than healthy controls (if anything, non-psychiatric participants were more likely to be flagged by C/IE screening).
+These results provide preliminary evidence that rigorous C/IE screening is unlikely to result in overcontrol bias.
+
+Given that the results of our patient study are preliminary and warrant further investigation, researchers might still be wary of possible overcontrol bias.
 However, when using self-report questionnaires for screening, for overcontrol to seriously impact results it would have to be the case that symptomatic participants frequently endorse improbable or impossible responses to infrequency-item checks (e.g., responding `Agree' to ``I competed in the 1917 Olympic Games").
@@
 Specifically, 208 participants were recruited from Amazon Mechanical Turk (MTurk) and 201 participants were recruited from Prolific.
-This study was approved by the Institutional Review Board of Princeton University (\#5291), and all participants provided written informed consent.
+This study was approved by the Institutional Review Board of Princeton University (\#5291), and all participants provided informed consent.
 Total study duration was approximately 10 minutes per participant.
@@
 
-\subsubsection{Theory-agnostic choice analysis} In the final analysis, we use a theory-agnostic modeling approach to characterize the choice behavior of attentive participants and those suspected of C/IE responding.
-To do so, we adapted the softmax regression model from \cite{seymour2012serotonin}.
-The softmax regression model estimates the influence of the history of past rewards, non-rewards, and choices on a participant's current choice.
-
-Specifically, the influence of the history of particular type of event is defined as:
-
-\begin{equation*}
-    \sum_i^K w = x_{t-1} \cdot w_{t-1} + x_{t-2} \cdot w_{t-2} +  \ldots + x_{t-k} \cdot w_{t-k}
-\end{equation*}
-
-where $x_{t-i}$ is a binary indicator [0,1] denoting if an event (i.e.
-reward, non-reward, previous choice) occurred on trial $t-i$ and $w_{t-1}$ is the associated decision weight.
-These weights were estimated for rewards, non-rewards, and previous choices up to five trials in the past.
-
-The overall tendency to choose a particular choice option is dictated by a softmax choice rule:
-
-\begin{equation*}
-    p(y_t = i) = \frac{ \exp \left( \sum w_i^\text{reward} + \sum w_i^\text{nonreward} + \sum w_i^\text{choice} \right) }{ \sum_i \exp \left( \sum w_i^\text{reward} + \sum w_i^\text{nonreward} + \sum w_i^\text{choice} \right) }
-\end{equation*}
-
-Note that these weights were fit independently; that is, we did not employ an exponential kernel to parameterize the decay of the weights at successively distant trial lags.
-In sum then, the theory-agnostic model describes a participant's choice behavior as a function of 15 parameters.
-
-We fit the softmax regression model using Stan (details above).Participant parameters were fit individually (i.e.
-not hierarchically)  so as to prevent bias during parameter estimation from partial-pooling between attentive and C/IE participants.
-Parameters were sampled with Gaussian priors with $\mu = 0$ and $\sigma = 5$.
-
 \section{Acknowledgements}
@@
 
-\printbibliography
-\pagebreak
+\section*{References}
+
+\printbibliography[heading=main]
+\end{refsection}
+
+\break
 
@@
 
-\section*{Supplement}
+\begin{refsection}[supp]
+\section*{Appendix A}
 \setcounter{figure}{0}
@@
 \renewcommand{\thefigure}{S\arabic{figure}}
+
+\subsection*{Bootstrapping Analysis}
+\begin{figure}[H]
+\includegraphics[width=16cm]{../figures/supp_01.png}
+\centering
+\captionsetup{width=0.88\textwidth}
+\caption{The pattern of significant behavior-symptom correlations before (panel A) and after (panel B) screening compared to the resulting pattern when random subsets of participants (22\% of total, matched to screening using the infrequency measure) are removed (panel C).
+Panels A and B are reproduced from Figure \ref{fig:correlations} for convenience.
+Panel C: the fraction of significant correlations in 5000 bootstrapped samples.
+Panel D: The similarity of the pattern of correlations after removal of random subsets to that before and after screening using the infrequency measure.
+Similarity was calculated using the simple matching coefficient.
+Random removal subsets were significantly more similar to the ``No Screening" than to the ``Infrequency" screening datasets (t = 262.49, $p < 0.001$).}
+\label{fig:random}
+\end{figure}
+
+\clearpage
+
+\subsection*{Posterior predictive checks}
+
+\begin{figure}[H]
+\includegraphics[width=16cm]{../figures/supp_02.png}
+\centering
+\captionsetup{width=0.88\textwidth}
+\caption{Posterior predictive checks for the risk-sensitive temporal difference learning model.
+\textit{Panel A:} Observed (black) and predicted (blue) learning curves averaged across the group.
+\textit{Panel B:} Observed versus predicted choice accuracy for each participant.
+\textit{Panel C:} Distribution of average predictive density across participants.}
+\label{fig:posterior_check}
+\end{figure}
+
+\clearpage
 
@@
 
-\subsection*{Task Instructions}
-
-The following are the instructions given to participants for the probabilistic reversal learning task.
-As a reminder, the task was given a fishing-themed cover story.
-Each paragraph below denotes one screen of instructions.
-
-\textit{Welcome to the fishing game! We will now give you some instructions on how to play the game. Use the buttons below (or the arrow keys) to navigate the instructions.}
-
-\textit{In the fishing game, there are three beaches you can fish at.
-Each beach has its own unique surfboard.
-(The colors and pictures on the surfboards are there just to help you tell the beaches apart – they don’t have any special meaning other than that.)}
-
-\textit{On each turn you will be shown three beaches, and you will choose which one you want to fish at. You can make your choice using the left, up, and right arrow keys.}
-
-\textit{When you fish at a beach, you will either catch a fish or you will catch trash. Try to catch fish, and try not to catch trash!}
-
-\textit{Some beaches are better than others.
-You are more likely to catch fish at some beaches (though you will still sometimes catch trash), and you are more likely to catch trash at other beaches (though you still sometimes catch fish).}
-
-\textit{The beaches will change over time. As times goes by, you may be less likely to catch fish at a beach where you were previously catching many fish.}
-
-\textit{Your goal is to catch as many fish as you can. You will receive a performance bonus up to \$0.25 that depends on how many fish you catch.}
-
-\textit{Now we will ask you some questions about the game.
-You must answer all questions correctly to proceed.
-Feel free to read back through the instructions if there is anything you are not certain about.}
-
-Following the instructions, participants completed a brief comprehension check where they were asked the following questions about the task:
-
-\begin{enumerate}
-    \item True or False: Your goal is to catch as many fish as you can. (True)
-    \item True or False: You are more likely to catch fish at some beaches than others. (True)
-    \item True or False: You will always catch fish at the best beach. (False)
-    \item True or False: How likely you are to catch a fish at a beach stays the same over time. (False)
-    \item True or False: The number of fish you catch will affect your final performance bonus. (True)
-\end{enumerate}
-
-Participants were required to answer all of the items correctly before they could proceed to the task.
-If they failed to do so, they restarted the instructions.
-There was no upper limit as to how many times a participant could loop through the instructions (the large majority of participants passed the comprehension check on their first try).
+\clearpage
 
@@
 
-\clearpage
-
-\subsection*{Bootstrapping Analysis}
-\begin{figure}[H]
-\includegraphics[width=16cm]{../figures/supp_01.png}
-\centering
-\captionsetup{width=0.88\textwidth}
-\caption{The pattern of significant behavior-symptom correlations before (panel A) and after (panel B) screening compared to the resulting pattern when random subsets of participants (22\% of total, matched to screening using the infrequency measure) are removed (panel C).
-Panels A and B are reproduced from Figure \ref{fig:correlations} for convenience.
-Panel C: the fraction of significant correlations in 5000 bootstrapped samples.
-Panel D: The similarity of the pattern of correlations after removal of random subsets to that before and after screening using the infrequency measure.
-Similarity was calculated using the simple matching coefficient.
-Random removal subsets were significantly more similar to the ``No Screening" than to the ``Infrequency" screening datasets (t = 262.49, $p < 0.001$).}
-\label{fig:random}
+\subsection*{Task Instructions}
+
+The following are the instructions given to participants for the probabilistic reversal learning task.
+As a reminder, the task was given a fishing-themed cover story.
+Each paragraph below denotes one screen of instructions.
+
+\textit{Welcome to the fishing game! We will now give you some instructions on how to play the game. Use the buttons below (or the arrow keys) to navigate the instructions.}
+
+\textit{In the fishing game, there are three beaches you can fish at.
+Each beach has its own unique surfboard.
+(The colors and pictures on the surfboards are there just to help you tell the beaches apart – they don’t have any special meaning other than that.)}
+
+\textit{On each turn you will be shown three beaches, and you will choose which one you want to fish at. You can make your choice using the left, up, and right arrow keys.}
+
+\textit{When you fish at a beach, you will either catch a fish or you will catch trash. Try to catch fish, and try not to catch trash!}
+
+\textit{Some beaches are better than others.
+You are more likely to catch fish at some beaches (though you will still sometimes catch trash), and you are more likely to catch trash at other beaches (though you still sometimes catch fish).}
+
+\textit{The beaches will change over time. As times goes by, you may be less likely to catch fish at a beach where you were previously catching many fish.}
+
+\textit{Your goal is to catch as many fish as you can. You will receive a performance bonus up to \$0.25 that depends on how many fish you catch.}
+
+\textit{Now we will ask you some questions about the game.
+You must answer all questions correctly to proceed.
+Feel free to read back through the instructions if there is anything you are not certain about.}
+
+Following the instructions, participants completed a brief comprehension check where they were asked the following questions about the task:
+
+\begin{enumerate}
+    \item True or False: Your goal is to catch as many fish as you can. (True)
+    \item True or False: You are more likely to catch fish at some beaches than others. (True)
+    \item True or False: You will always catch fish at the best beach. (False)
+    \item True or False: How likely you are to catch a fish at a beach stays the same over time. (False)
+    \item True or False: The number of fish you catch will affect your final performance bonus. (True)
+\end{enumerate}
+
+Participants were required to answer all of the items correctly before they could proceed to the task.
+If they failed to do so, they restarted the instructions.
+There was no upper limit as to how many times a participant could loop through the instructions (the large majority of participants passed the comprehension check on their first try).
+
+\subsection*{C/IE responding manifests as qualitatively distinct behavioral strategy}
+
+In an exploratory analysis, we employed a theory-agnostic modeling approach to investigate how C/IE participants on the probabilistic reversal-learning task compared to attentive participants.
+The motivation for this analysis was to better understand why C/IE responding was inconsistently predicted by chance-level performance, and also correlated with asymmetric learning rates.
+
+To characterize participants' choice behavior, we adapted the softmax regression model from \cite{seymour2012serotonin}.
+This model estimates, for each participant, how much their choice depends on the recent history of trial events (rewarding outcomes, non-rewarding outcomes, and choices from the preceding 5 trials).
+Specifically, the influence of the history of particular type of event is defined as:
+
+\begin{equation*}
+    \sum_i^K w = x_{t-1} \cdot w_{t-1} + x_{t-2} \cdot w_{t-2} +  \ldots + x_{t-k} \cdot w_{t-k}
+\end{equation*}
+
+where $x_{t-i}$ is a binary indicator [0,1] denoting if an event (i.e.
+reward, non-reward, previous choice) occurred on trial $t-i$ and $w_{t-1}$ is the associated decision weight.
+These weights were estimated for rewards, non-rewards, and previous choices up to five trials in the past.
+The overall tendency to choose a particular choice option is dictated by a softmax choice rule:
+
+\begin{equation*}
+    p(y_t = i) = \frac{ \exp \left( \sum w_i^\text{reward} + \sum w_i^\text{nonreward} + \sum w_i^\text{choice} \right) }{ \sum_i \exp \left( \sum w_i^\text{reward} + \sum w_i^\text{nonreward} + \sum w_i^\text{choice} \right) }
+\end{equation*}
+
+Note that these weights were fit independently; that is, we did not employ an exponential kernel to parameterize the decay of the weights at successively distant trial lags.
+In sum then, the theory-agnostic model describes a participant's choice behavior as a function of 15 parameters.
+
+We fit the softmax regression model using Stan following the same procedure as for the theory-based analyses.
+Participant parameters were fit individually (i.e.
+not hierarchically)  so as to prevent bias during parameter estimation from partial-pooling between attentive and C/IE participants.
+Parameters were sampled with Gaussian priors with $\mu = 0$ and $\sigma = 5$.
+
+The regression weights for each event, averaged within attentive and C/IE participants, are presented in Figure \ref{fig:regression}.
+Comparing attentive to C/IE participants, we observed a credible difference (i.e.
+95\% highest density intervals excluded zero) only for the $T-1$ weight for previous choice.
+That is, attentive participants were more likely to repeat their previous choice (i.e.
+greater choice hysteresis) than were C/IE participants.
+
+\begin{figure}[!t]
+\includegraphics[width=16cm]{../figures/main_03c.png}
+\centering
+\captionsetup{width=0.88\textwidth}
+\caption{Softmax regression decision weights in attentive (red) and C/IE (blue) participants.
+The weights dictate the extent to which the recent history of rewards, nonrewards, or previous choices influence current choice.
+Error bars indicate the 95\% highest density interval of each weight.
+* denotes where the 95\% highest density interval of the difference in weights excluded zero.}
+\label{fig:regression}
 \end{figure}
 
-\clearpage
-\subsection*{Posterior predictive check}
-
-\begin{figure}[H]
-\includegraphics[width=16cm]{../figures/supp_02.png}
-\centering
-\captionsetup{width=0.88\textwidth}
-\caption{Posterior predictive checks for the risk-sensitive temporal difference learning model.
-\textit{Panel A:} Observed (black) and predicted (blue) learning curves averaged across the group.
-\textit{Panel B:} Observed versus predicted choice accuracy for each participant.
-\textit{Panel C:} Distribution of average predictive density across participants.}
-\label{fig:posterior_check}
+This result may be initially surprising, since one might expect choice hysteresis to result in more perseveration errors following contingency reversals, and since we observed in the previous section that C/IE responding was associated with more perseveration errors.
+However, choice hysteresis is adaptive in this probabilistic reversal-learning task.
+Because rewards in the task are probabilistic, once the reward-maximizing response option has been identified ignoring an occasional unrewarding outcome and instead performing the same response is optimal (until the next reversal occurs and is identified).
+Interestingly, participants engaging in C/IE responding were also numerically (though not significantly) less affected by previous outcomes, suggesting that their behavior was not more adaptive, but rather just more random.
+
+This pattern of results also helps explain the pre-screening correlations with asymmetric learning rates.
+Previous work has established that, when choice hysteresis is not accounted for in reinforcement learning models, it can manifest as positive learning rate asymmetries \cite{Katahira2018-ke, sugawara2021dissociation}.
+Since C/IE participants showed decreased hysteresis, which our reinforcement learning model did not explicitly account for, we should expect to find a negative correlation between learning-rate asymmetries and symptoms before C/IE participants are excluded.
+Indeed, this is what we observed above.
+
+In sum, the theory-agnostic analysis of task behavior revealed that C/IE participants exhibited a qualitatively distinct behavioral strategy on the probabilistic reversal-learning task.
+C/IE participants showed less adaptive choice hysteresis.
+Moreover, they were numerically (but not significantly) less sensitive to outcomes.
+The latter finding helps clarify in part why we observed low correspondence between task and self-report screening measures (that is, C/IE participants were not significantly more likely to respond randomly during the task).
+These results also present another hidden danger of C/IE responding: qualitatively distinct patterns of behavior under C/IE responding can bias the estimation of parameters of theoretical interest if not properly accounted for.
+
+\break
+\section*{Appendix B: Replication study}
+
+\subsection*{Background \& motivation}
+
+Here we report a conceptual replication of our original study.
+The motivations for conducting a replication study were threefold.
+First, we wanted to examine the generalizability of our findings under new labor platform conditions.
+Since summer 2020, when the original data were collected, online labor markets like Mechanical Turk/Cloudresearch and Prolific Academic have undergone important changes.
+To address rampant data quality issues on Mechanical Turk, Cloudresearch introduced their ``Approved Participants'' filter.
+When selected, only Mechanical Turk participants with a prior history of attentive and careful work are invited to participate in experiments \cite{cloudresearch_2020-2, hauser2021evaluating}.
+Similarly, a deluge of new, lower-quality users signed up to participate in studies on Prolific in summer, 2021 \cite{Letzter2021-bw}.
+In response, Prolific introduced new controls and filters to improve data quality on the platform \cite{prolific_2021}.
+In the wake of these changes, we wanted to explore the relevance of our original findings.
+Specifically, with these new safeguards, we wanted to examine whether the chance of spurious correlations has been seriously lessened.
+
+Second, we wanted to examine the generalizability of our findings to other behavioral measures.
+In the original study, we used a short, straightforward, and relatively easy reversal-learning task.
+Our motivation then was to demonstrate the risk of spurious correlations even for experiments where the possibility of participant fatigue (and consequently C/IE responding) had been minimized.
+One consequence of this design, however, was that the majority of participants performed reasonably well on the task (i.e.
+only 26 participants, or 7\% of the sample, exhibited choice accuracy at or below statistically chance levels).
+This fact may in part explain why we observed such low correspondence between self-report and task-based screening measures.
+As such, we wanted to repeat our experiment and analyses using a more difficult task.
+Therefore, in the replication study we used the two-step task \cite{daw2011model}, which is both more challenging and lengthy than our original reversal-learning task.
+
+Finally, we wanted to examine the generalizability of our findings to other self-report measures.
+In the original study, we found that, all else being equal, self-report symptom measures with low rates of endorsement were more likely to yield spurious correlations with behavior in the presence of C/IE responding.
+This effect should not be limited to symptom measures, however, and should extend to any self-report measure with an expected skewed or asymmetric score distribution.
+Therefore, in the current replication study, we use two sets of self-report scales: one set of psychiatric symptom measures and one set of personality measures.
+As before, both sets include scales whose score distributions are expected to be symmetric or asymmetric (skewed).
+Crucially, the two personality scales measure constructs (i.e.
+artistic interests, greed avoidance) that should have no meaningful relationship with model-based choice behavior on the two-step task.
+Therefore, the personality measures serve as a stronger test of our hypothesis that spurious correlations between self-report and behavioral measures are more likely for skewed score distributions.
+
+\subsection*{Methods}
+
+\subsubsection*{Participants}
+
+400 total participants were recruited to participate in an online behavioral experiment in February, 2022.
+Specifically, 200 participants were recruited from Amazon Mechanical Turk (MTurk) and 200 participants were recruited from Prolific.
+This study was approved by the Institutional Review Board of Princeton University (\#11968), and all participants provided informed consent.
+Total study duration was approximately 20 minutes per participant.
+Participants received monetary compensation for their time (rate USD \$12/hr), plus an incentive-compatible bonus up to \$1.00 based on task performance.
+
+Participants were eligible if they resided in the United States or Canada.
+Participants from MTurk were recruited with the aid of CloudResearch services \cite{litman2017turkprime-2} using their ``Approved participants''  data quality filters \cite{cloudresearch_2020-2}.
+As in the original study, MTurk workers were not excluded based on work approval rate or number of previous jobs approved \cite{robinson2019tapped-2}.
+No other exclusion criteria were applied during recruitment.
+
+The data from N=7 participants who completed the experiment were excluded prior to analysis.
+These participants (all from MTurk) disclosed that they had also completed the experiment on the other platform were excluded.
+This left a final sample of N=393 participants (MTurk: N=193, Prolific: N=200) for analysis.
+The demographics of the sample split by labour market is provided in Table \ref{tab:demographics_02}.
+The participants recruited from MTurk were older on average ($M = 4.9 \ \text{yrs}, t = 4.248, p < 0.001$) and comprised of fewer women ($z = 4.248, p < 0.001$).
+
+\begin{table}[!h]
+\centering
+\small
+\setlength{\tabcolsep}{15pt}
+\begin{tabular}{ lrrrr }
+\toprule
+& \multicolumn{2}{c}{MTurk} & \multicolumn{2}{c}{Prolific} \\
+\cmidrule(lr){2-3} \cmidrule(lr){4-5}
+Total & \multicolumn{2}{c}{N=193} & \multicolumn{2}{c}{N=200} \\
+\midrule
+Age & N & \% & N & \% \\
+\cmidrule(lr){1-5}
+18-25   &    11 &   5.7 &     47 &  23.5 \\
+26-35   &    71 &  36.8 &     76 &  38.0 \\
+36-45   &    60 &  31.1 &     41 &  20.5 \\
+46-55   &    29 &  15.0 &     22 &  11.0 \\
+55+     &    22 &  11.4 &     14 &   7.0 \\
+\midrule
+Gender & N & \% & N & \% \\
+\cmidrule(lr){1-5}
+Female &      68 &  35.2 &      122 &  61.0 \\
+Male   &     124 &  64.2 &       73 &  36.5 \\
+Other  &       1 &   0.5 &        5 &   2.5 \\
+\midrule
+Ethnicity & N & \% & N & \% \\
+\cmidrule(lr){1-5}
+Hispanic or Latino     &    16 &   8.3 &     12 &   6.0 \\
+Not Hispanic or Latino &   177 &  91.7 &    180 &  90.0 \\
+Rather not say         &     0 &   0.0 &      8 &   4.0 \\
+\midrule
+Race & N & \% & N & \% \\
+\cmidrule(lr){1-5}
+American Indian/Alaska Native &     2 &   1.0 &      0 &   0.0 \\
+Asian                         &    15 &   7.8 &     41 &  20.5 \\
+Black or African American     &    13 &   6.7 &     12 &   6.0 \\
+White                         &   156 &  80.8 &    133 &  66.5 \\
+Multiracial                   &     6 &   3.1 &     10 &   5.0 \\
+Rather not say                &     1 &   0.5 &      4 &   2.0 \\
+\bottomrule
+\end{tabular}
+\captionsetup{width=0.88\textwidth}
+\caption{The demographics of each sample by online labour market.}
+\label{tab:demographics_02}
+\end{table}
+
+\subsubsection*{Experiment}
+
+Participants completed a gamified version of the two-step task \cite{daw2011model} designed to dissociate ``model-free'' and ``model-based'' decision-making.
+On every trial of the task, participants were presented with two choice options that led probabilistically to either of two second-stage ``states''.
+From there, participants made an additional choice between two options that were associated with a unique probability of returning either a reward (1 point) or a non-reward (0 points).
+Crucially, each first-stage choice option led mostly (70\% of the time) to one of the two second-stage states; this probability was fixed throughout the experiment.
+The probabilities of reward for each of the four second-stage options changed slowly and independently, according to Gaussian random walks.
+Participants completed 201 trials of the task, with an optional break after the first half.
+
+As a cover story, the two-step task was introduced to participants as a ``space treasure'' game \cite{decker2016creatures}.
+In the game, participants made choices between two different colored rocket ships (first stage choice) that probabilistically took them to one of two planets.
+On each planet, there were two alien creatures to ``trade'' with.
+If chosen as a trading partner, an alien would either give ``treasure'' (1 point) or ``junk'' (0 points).
+Participants were told their goal was to collect as much treasure as possible.
+Participants were informed that the rocket ships mostly traveled to one planet, but sometimes went to the other.
+Participants were also instructed that the chance an alien would give them treasure would change slowly over the course of the task.
+Prior to beginning the experiment, participants had to correctly answer three sets of comprehension questions about the instructions.
+Failing to correctly answer all items forced the participant to start a section of the instructions over.
+
+The task was programmed in jsPsych \cite{deleeuw_2015_jspsych-2} and distributed using custom web-application software.
+The experiment code is available at \url{https://github.com/nivlab/sciops}, and the web-software is available at \url{https://github.com/nivlab/nivturk}.
+A playable demo of the task is available at \url{https://nivlab.github.io/jspsych-demos/tasks/two-step/experiment.html}.
+
+\subsubsection*{Self-report measures}
+
+Prior to the start of the two-step task, participants completed four self-report measures (in a randomized order).
+The first was the 14-item seven-up/seven-down scale (7u/7d; \cite{youngstrom_2013_susd-2}), which measures lifetime incidence of depressive and (hypo)mania symptoms.
+These scales are expected to elicit lower rates of symptom endorsement, thereby resulting in asymmetric (right-skewed) score distributions.
+Participants also completed a 7-item measure of general anxiety symptoms over the last year (e.g.
+``I was overwhelmed by anxiety.''; \cite{watson2022development}).
+This scale is expected to elicit moderate rates of symptom endorsement, thereby resulting in symmetric score distributions.
+We expected the depression and mania measures to be at greater risk than the anxiety measure for spurious correlations with behavior on the two-step task.
+
+In addition, participants completed a 6-item measure of artistic interests (e.g.
+``I believe in the importance of art''; \cite{ashton2007empirical}).
+Based on previous studies, this scale is expected to elicit high rates of endorsement, thereby resulting in an asymmetric (left-skewed) score distribution.
+Finally, participants completed a 6-item measure of greed avoidance, which measures tendencies towards status-seeking (e.g.
+``I am out for my own personal gain''; \cite{ashton2007empirical}).
+Based on previous studies, this scale is expected to elicit moderate rates of endorsement, thereby resulting in a symmetric score distribution.
+We  expected the artistic interests scale to be at greater risk than the greed avoidance scale for spurious correlations with behavior on the two-step task.
+
+\subsubsection*{Correspondence of screening measures}
+
+As in the original study, we measured the correspondence of screening measures based on the task and self-report behavior.
+We calculated a number of standard measures of data quality from each participant's task behavior (four in total) and self-report responses (five in total).
+The self-report screening measures were identical to those used in the original study, except that we used (mostly) new infrequency items.
+We describe each of the new screening measures below.
+
+\subparagraph{Infrequency items}
+
+Infrequency items are questions for which all or virtually all attentive participants should provide the same response.
+We embedded four infrequency items across the self-report measures.
+Specifically, we used the following questions:
+
+\begin{enumerate}
+  \item Have there been times in your life where you blinked your eyes at least once per day?
+  \item Have there been times of a couple days or more when you were able to breathe underwater (without an oxygen tank)?
+  \item I was worried about the canine World Cup.
+  \item I have used a computer.
+\end{enumerate}
+
+Prior to conducting the study, the infrequency items were piloted on an independent sample of participants to ensure that they elicited one dominant response.
+We also included one instructed item (``Please select "Neutral" as your response'') to compare to the infrequency items.
+We measured the number of suspicious responses made by each participant to these questions.
+For thresholded analyses, participants were flagged if they responded incorrectly to one or more of these items.
+
+\subparagraph{Key variability} Key variability was defined as the fraction of trials a participant pressed the left arrow key across first stage choices during the two-step task.
+Key variability could range from 0.00 (only right arrow key used) to 1.00 (only left arrow key used).
+Extreme values (i.e.
+closer to zero or one) are indicative of more careless responding during the task.
+
+\subparagraph{Choice variability} Choice variability was defined as the fraction of trials a participant chose the same first-stage choice option during the two-step task.
+(The left-right position of first-stage choice options were randomized across trials, such that response key and response choice were orthogonalized.) Choice variability could range from 0.00 (only selected the first option) to 1.00 (only selected the second option).
+Extreme values (i.e.
+closer to zero or one) are indicative of more careless responding during the task.
+
+\subparagraph{Win-Stay Lose-Shift} Win-stay lose-shift (WSLS) measures a participant's tendency to stay with a first-stage choice option following a second-stage reward versus shifting to a new choice option following a non-reward.
+WSLS thus measures a participant's sensitivity to reward feedback.
+WSLS was estimated per participant via regression, where the current first-stage choice (stay, switch) predicted by the previous trial's outcome (reward, non-reward) and a stationary intercept.
+Here we used the first (slope) term to represent a participant's WSLS tendency.
+Lower values of this term indicate less sensitivity to reward feedback and are thus indicative of more careless responding during the task.
+
+\subparagraph{Response Times} Suspicious response time was defined as the proportion of first-stage choices with an outlier response time, here measured as responses faster than 200ms.
+Greater proportions of outlier response times are indicative of more careless responding during the task.
+
+\subparagraph{Correspondence Analysis} We measured the correspondence of the above screening measures via two complimentary approaches.
+First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation.
+Second, we estimated the pairwise rate of agreement on the binarized measures using the Dice similarity coefficient (looking at the top 10\% most suspicious respondents for each measure).
+The former approach estimates two measures' monotonic association, whereas the latter approach estimates their agreement as to which participants were most likely engaging in C/IE responding.
+For significance testing, we used permutation testing wherein a null distribution of similarity scores (i.e.
+Spearman's correlation, Dice coefficient) was generated for each pair of screening measures by iteratively permuting participants' identities within measures and re-estimating the similarity.
+P-values were computed by comparing the observed score to its respective null distribution.
+We corrected for multiple comparisons using family-wise error rates \cite{winkler2014permutation-2}.
+
+\subsubsection*{Correlations between behavior and symptom measures}
+
+To quantify the effects of both task and self-report data screening on behavior-symptom correlations, we estimated the pairwise correlations between the scale scores of each self-report measure and several measures of performance on the two-step task.
+For each participant, we computed model-agnostic measures of performance on the two-step task \cite{gillan2016characterizing}.
+Logistic regression analyses were conducted with the \textit{statsmodels} package \cite{seabold2010statsmodels} in the python programming language.
+The model tested if participants' first-stage choice behavior (coded as Stay = 1, Switch = 0) was influenced by the previous trial's reward (coded as Rewarded = 1, Unrewarded = 0), previous trial's transition (coded as Common = 1, Uncommon = 0), and their interaction.
+Importantly, the interaction term between previous reward and transition is a proxy for the contribution of model-based learning to choice behavior \cite{gillan2016characterizing}.
+
+Correlations between the behavioral measures (i.e.
+logistic regression coefficients) and self-report measures were calculated (after various forms of screening and exclusion) using Spearman's rank correlation.
+Significance testing was performed using the percentile bootstrap method \cite{wilcox2018guide-2} so as to avoid making any parametric assumptions.
+These correlation analyses were not corrected for multiple comparisons, since our overarching purpose was to demonstrate the extent of this issue across multiple behavioral measures and self-report symptoms.
+Any one of these correlations considered individually can be thought of as emulating a conventional analysis where fewer statistical tests would be performed.
+
+\subsection*{Results}
+
+\subsubsection*{Careless participants (often) appear symptomatic when the overall level of symptom endorsement is low}
+
+To begin our analysis of the replication dataset, we examined the number of participants flagged by the WSLS and infrequency item screening measures.
+Only 31 participants (8\%) were flagged as exhibiting choice behavior at or below statistically chance levels in the two-step task.
+In contrast, 55 participants (14\%) endorsed a logically invalid or improbable response on one or more of the infrequency items when completing the self-report measures.
+The proportion of participants flagged for C/IE responding was significantly greater on Mechanical Turk compared to Prolific for both task (MTurk: N=23/193; Prolific: N=8/200; $z=2.91, p=0.004$) and survey data (MTurk: 34/193; Prolific: 21/200; $z = 2.03, p = 0.042$).
+Across the four infrequency items, the average failure rate was 5.3\% (range: 2.5\% -- 8.9\%).
+In contrast, no participant failed the instructed item.
+This discrepancy in the proportion of participants flagged by each type of attention check is consistent with previous research, which found that instructed items are insensitive measures of C/IE responding \cite{barends2019noncompliant-2, thomas2017validity-2, hauser2016attentive-2}.
+
+\begin{figure}[t!]
+\includegraphics[width=15cm]{../figures/repl_02a.png}
+\centering
+\captionsetup{width=0.88\textwidth}
+\caption{Raincloud plots of total symptom scores in attentive (red) and C/IE (blue) participants.
+Each colored dot represents the symptom score for one participant.
+Black circles: average score within each group (error bars denote 95\% bootstrap confidence interval).
+Shaded plots: estimated distribution of responses for each group of participants.}
+\label{fig:repl_distributions}
 \end{figure}
 
-%TC:endignore
+Previously we observed a mean-shift in the average level of symptom endorsement for participants suspected of engaging in C/IE responding, relative to attentive participants, when the overall rate of symptom endorsement is low.
+This result was (mostly) replicated in the current dataset.
+Total scores were noticeably exaggerated in participants suspected of C/IE responding for the symptom measures where overall rates of symptom endorsement were the lowest (e.g.
+mania; Figure \ref{fig:repl_distributions}).
+Furthermore, where there was higher rates of symptom endorsement overall (e.g.
+anxiety), the distributions of symptom scores between the two groups of participants were more similar.
+Permutation testing confirmed that observed mean-shifts in symptom scores for C/IE participants were statistically significant for the most skewed symptom measures (Table \ref{tab:rep_validation}).
+
+For the personality measures, an interesting pattern emerged.
+We did not observe a statistically significant mean-shift in total scores for the subscale with the most skewed score distribution (i.e.
+artistic interests; $t = 1.87$, $p = 0.061$).
+However, an unexpected and statistically significant mean-shift in the average level of endorsement was observed for the more symmetrically-distributed greed avoidance subscale ($t = 16.44$, $p < 0.001$).
+The reason for this finding is unclear.
+Regardless, this finding presents an opportunity to test for spurious correlations between behavioral and self-report measures in the presence of a mean-shift in scores in the absence of (substantially) skewed score distributions.
+
+\begin{table}[!t]
+\centering
+\small
+\begin{tabular}{lcccc}
+\toprule
+& & \multicolumn{3}{c}{Total Score} \\
+\cmidrule(lr){3-5}
+Subscale & Skew &  Attentive & C/IE & $t$-value \\
+\midrule
+Mania      &  1.07 &   3.25 &   6.27 & $-6.05^*$ \\
+Depression &  0.89 &   5.72 &   6.95 & $-1.57$   \\
+Anxiety    &  0.44 &   8.54 &   8.65 & $-0.13$   \\
+Artistic interests   & -0.92 &  28.07 &  26.29 & $1.87$    \\
+Greed avoidance     &  0.55 &  11.77 &  16.44 & $-4.17^*$  \\
+\bottomrule
+\end{tabular}
+\captionsetup{width=0.88\textwidth}
+\caption{Descriptive statistics of the self-report measures between attentive and C/IE participants.
+Skew: the empirical skewness of the distribution of total symptom scores.
+Total score: the average symptom score across attentive and C/IE participants.
+Stars indicate statistical significance at $p<0.05$.}
+\label{tab:rep_validation}
+\end{table}
+
+\subsubsection*{Low correspondence between task and self-report measures of C/IE responding}
+
+Next, we evaluated the degree of correspondence between behavioral and self-report screening measures in order to determine whether screening on behavior alone was sufficient to identify and remove careless participants.
+To measure the degree of correspondence between these behavioral and self-report screening measures, we performed two complementary analyses.
+First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation.
+The resulting pairwise similarity matrices are presented in Figure \ref{fig:repl_correspondence} (left panel).
+After correcting for multiple comparisons, there were a handful of significant correlations between the behavioral and self-report screening measures.
+Abnormal response times emerged as the metric most correlated with the self-report screening measure.
+Crucially, as in the original study, the sizes of these observed correlations were roughly half those observed for the correlations between the self-report measures.
+
+\begin{figure}[!t]
+\includegraphics[width=16cm, trim=0 0 3cm 0]{../figures/repl_02b.png}
+\centering
+\captionsetup{width=0.88\textwidth}
+\caption{Similarity of task and self-report data screening measures.
+Each tile corresponds to the Spearman rank correlation (left) and Dice similarity coefficient (right) between two screening measures.
+Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; KV = key variability; CV = choice variability; WSLS = win-stay lose-shift rate; RT = suspicious response times.
+Similarity scores have been thresholded after correcting for multiple comparisons.
+Numbers denote the strength of statistically significant correlations.
+Cross-modality correlations between task-behavior (left) and infrequency-item self-report measures (bottom) are in the dashed rectangle.}
+\label{fig:repl_correspondence}
+\end{figure}
+
+Second, we used the Dice similarity coefficient to quantify agreement between different screening methods in the set of participants flagged for exclusion (Figure \ref{fig:repl_correspondence}, right panel).
+This approach quantifies the degree of overlap between the set of would-be excluded participants based on different screening measures under a common exclusion rate.
+Results were largely consistent with the correlation analysis: only a handful of task and self-report screening measures achieved levels of agreement greater than what would be expected by chance.
+Of the significant cross-modality pairs, the average similarly coefficient was less than 0.4.
+In other words, when any of these sets of two measures are used to identify the top 10\% of participants most strongly suspected of C/IE responding, they agree on only two out of every five participants.
+Screening on task behavior alone would fail to identify the majority of participants most likely engaging in C/IE responding.
+
+Taken together, these findings corroborate the results of the original study: measures of C/IE responding in task and self-report data do not identify the same set of participants.
+This means that solely excluding participants on the basis of poor behavioral performance---the most common approach in online studies---is unlikely to identify participants who engage in C/IE responding on self-report surveys.
+
+\subsubsection*{Spurious symptom-behavior correlations produced by C/IE responding}
+
+To understand the effects of applying different forms of screening, we estimated the correlations between each unique pairing of a self-report measure and measure of behavior under four different conditions: no screening, screening only on task behavior (i.e.
+only participants whose win-stay lose-shift behavior was above chance), screening only on self-report responses (i.e.
+only participants who responded correctly on all infrequency items), or both.
+The resulting pairwise behavior-symptom correlations following each screening procedure are presented in Figure \ref{fig:repl_correlations}.
+We note that we did not correct these correlation analyses for multiple comparisons, since our purpose was to demonstrate the extent of this issue across multiple behavioral measures and self-report symptoms.
+Any one of these correlations considered individually can be thought of as emulating a conventional analysis where fewer statistical tests would be performed.
+
+When no rejections based on C/IE responding was applied (i.e.
+all participants were included in the analysis; Figure \ref{fig:repl_correlations}A), we observed multiple significant correlations between measures of task behavior and symptom scores, in particular for hypomania and depression.
+Consistent with our predictions, these correlations involved measures with low overall endorsement rates and mean-shifts in total scores distributions between attentive and C/IE participants.
+Conversely, we found no significant correlations with the symmetrically-distributed anxiety scores.
+This is despite the fact this scale measures comorbid symptoms and syndromes.
+Crucially, of the two personality measures, we observed significant correlations only for the measure found to exhibit a mean-shift in scores between attentive and C/IE participants (i.e.
+greed avoidance).
+Crucially, this included a significant correlation with the interaction term, which is used as a proxy measure for model-based choice behavior.
+That is, significant correlations were not restricted only to general behavioral measures but also to measures of specific theoretical interest.
+
+Next, we excluded participants from analysis based on task-behavior screening (i.e.
+win-stay lose-shift, removing the 8\% of participants exhibiting behavior indistinguishable from chance; Figure \ref{fig:repl_correlations}B).
+In contrast to the findings of the original study, the pattern of correlations was meaningfully changed: the putatively spurious correlations between greed avoidance and performance on the two-step task were ablated.
+Two previously significant correlations between hypomania and two-step performance were also rendered non-significant.
+A similar pattern of results was observed when we rejected participants based on self-report screening (removing 14\% of participants who endorsed one or more invalid or improbable responses on the infrequency items; Figure \ref{fig:repl_correlations}C) and when rejections were applied based on both task and self-report screening measures (Figure \ref{fig:repl_correlations}D).
+
+\begin{figure}[!t]
+\includegraphics[width=17cm]{../figures/repl_03a.png}
+\centering
+\captionsetup{width=0.88\textwidth}
+\caption{Absolute Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions.
+Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons).
+Black Xs indicate significant correlations ablated under screening.
+No Screening = no exclusions; WSLS Only = exclusions based on chance-level performance in the two-step task; Infrequency Only = exclusions based on invalid or improbable responses to infrequency items; Both Types = exclusions based on the previous two measures.
+Acronyms: PrevRew = sensitivity to reward on the previous trial; PrevTrans = sensitivity to transition type on previous trial; MB/MF = index of model-based/model-free behavior (interaction between \textit{PrevRew} \& \textit{PrevTrans}).}
+\label{fig:repl_correlations}
+\end{figure}
+
+These findings suggest that some of the significant behavior-symptom correlations observed without strict participant screening may indeed be spurious correlations driven by C/IE responding.
+Interestingly, in contrast to the original study, screening based on task behavior or self-report behavior alone was sufficient to protect against spurious symptom-behavior correlations in the presence of mean-shifts in scores between attentive and C/IE participants.
+For example, both forms of screening ablatated the would-be significant correlation between model-based behavior and greed avoidance.
+The discrepancy in results between the original and replication studies may reflect the fewer numbers of participants failing attention checks in the replication study (14\%) compared to the original study (22\%).
+Regardless, we replicate the findings of the original study in that screening on self-report data allowed us to identify symptom-behavior correlations most likely to be spurious.
+
+\subsection*{Discussion}
+
+Here we reported the findings from a replication study, the purpose of which was to examine the generalizability of our original findings under new labor market conditions, behavioral measures, and self-report measures.
+To this end, we recruited an independent sample of almost 400 participants, using Cloudresearch's and Prolific's latest data quality filters, to complete the two-step task and a novel set of self-report measures.
+As evidence of the efficacy of these filters, the proportion of participants flagged for C/IE responding in the self-report measures was noticeably smaller in the replication sample (14\%) compared to original sample (22\%).
+This decrease in the number of participants suspected of C/IE responding was observed for both MTurk and Prolific (though, as in the original study, the proportion of low-quality participants was significantly, albeit marginally, smaller for Prolific than MTurk).
+Regardless, though these online labor platform quality control measures seem to be effective, they do not completely solve the problem.
+That is, a non-negligible number of participants on both platforms continue to engage in C/IE responding.
+
+Next, we compared the distribution of self-report scale scores for attentive participants and participants suspected of engaging in C/IE responding.
+Replicating our previous result, we observed a mean-shift in the average level of symptom endorsement for participants suspected of C/IE responding, relative to attentive participants, only when the overall rate of symptom endorsement was low.
+Specifically, flagged participants showed significantly elevated scores on the hypomania scale (with its right-skewed score distribution) but not so on the anxiety scale (with its symmetric score distribution).
+Interestingly, we found the opposite pattern for the personality measures: scores for participants engaging in C/IE responding were not significantly different than their attentive counterparts on the artistic interests scale (with its left-skewed score distribution), but was so for the greed avoidance scale (with its more symmetric score distribution).
+The cause for the discrepancy in findings between the symptom and personality measures is unclear.
+One possible explanation is the direction of the skew for the artistic interests scale.
+Previously, using random intercept item factor analysis, we observed that participants engaging in C/IE responding were more likely to use the right-half of the response scale.
+As such, such a pattern of responding is more likely to produce a mean-shift in scale scores, compared to attentive participants, on a scale with a right-skewed distribution (e.g.
+mania, depression scales) than a scale with a left-skewed distribution (e.g.
+artistic interests scale).
+Further research is still needed to characterize patterns of C/IE responding.
+
+After, we evaluated the degree of correspondence between behavioral and self-report screening measures.
+The results in the replication study corroborate the findings of the original study: measures of C/IE responding in task and self-report data do not identify the same set of participants.
+Using a different and more difficult task (i.e.
+two-step task), we again observed relatively low correspondence between self-report and task-based screening measures.
+Thus, we are more confident that both forms of screening are necessary to identify participants providing low-quality responses.
+Finally, examined the consequences of various types of screening methods for correlations between behavioral and self-report measures.
+As in the original study, we detected significant spurious correlations when no screening was applied.
+This included correlations between model-based planning on the two-step task and scores on the greed avoidance scale, for which there is no theoretical reason to predict a correlation.
+Instead, this almost certainly reflects the mean-shift in scores between attentive participants and participants flagged for C/IE responding on the greed avoidance scale.
+As evidence of this, excluding participants who failed one or more infrequency items ablated this correlation.
+In contrast to the original study, excluding participants based on poor performance on the two-step task was also sufficient to ablate this correlation.
+Thus, there may be instances where screening on poor behavioral performance is sufficient to prevent spurious correlations.
+However, in the absence of perfect information as to when those situations should arise, we conclude that it is simply safer to screen participants on both dimensions of performance.
+
+In summary, we conclude that the results of the original study largely hold in replication.
+Despite legitimate advances in data quality controls, online labor platforms still suffer from participants engaging in C/IE responding.
+Screening based on task measures alone is still insufficient for reliably detecting inattentive responding on self-report measures.
+Finally, and most importantly, C/IE responding is still likely to result in mean-shifts in scores for symptom scales with overall low rates of endorsement, which are in turn capable of yielding spurious correlations between self-report and behavioral measures.
+The best safeguard against such spurious correlations continues to be screening in both domains.
+
+\break
+\section*{Appendix C: Attention checks in healthy and psychiatric patients}
+
+\subsection*{Background \& motivation}
+
+One concern with using attention checks for use in screening and exclusion of participants is that we might inadvertently introduce an overcontrol bias \cite{elwert2014endogenous-2}.
+That is, to the extent that C/IE responding reflects lack of motivation \cite{barch2015mechanisms-2}, avoidance of effort \cite{cohen2001impairments-2, culbreth2016negative-2}, or more frequent lapses of attention \cite{kane2016individual-2, robison2017neurotic-2}, one might hypothesise a true underlying association between psychopathology and careless responding in online studies.
+In such cases, it is plausible that rigorous screening of C/IE responding might lead to the differential exclusion of truly symptomatic participants.
+The purpose of the current preliminary and exploratory study was to examine whether actual psychiatric patients --- individuals with a confirmed psychiatric disorder --- were equally or more likely than healthy controls to fail attention checks embedded in self-report symptom scales.
+
+\subsection*{Methods}
+
+\subsubsection*{Participants}
+
+Participants were recruited as part of two independent studies to investigate reward processing in individuals with and without a history of major depression and bipolar disorder.
+Crucially, for present purposes, both studies required participants to complete (1) a series of computerized self-report surveys and cognitive tasks from their home, and (2) a structured clinical interview (the SCID-5) with a trained interviewer to verify whether they met the criteria for one or more psychiatric disorders.
+
+In both studies, participants volunteered for a 3-session study conducted via video conferencing.
+Specifically, participants completed each session from their homes while on Zoom with a study coordinator.
+During each session, the study coordinator turned off their camera and microphone, but were available if the participant had any questions.
+Participants were recruited through clinician referral and Google ads targeting individuals with a history of depression, anhedonia, apathy, and/or (hypo)mania symptoms.
+Participants were eligible for participation if they (1) had no history of head injury resulting in loss of consciousness for more than 20 minutes; (2) had not been diagnosed with intellectual disability; (3) had not been diagnosed with any neurological condition; (4) did not meet criteria for substance dependence (excluding nicotine) in the past 6 months; (5) had not received electroconvulsive therapy in the past 8 weeks; and (6) were aged between 18-65.
+For one of the two studies, participants were also required to score 6 or higher on the Wechsler Test of Adult Reading to be included in the study.
+Furthermore, non-clinical participants were eligible if they did not meet criteria for any psychiatric diagnosis and were not currently taking any medication used to treat psychiatric disorders.
+In turn, clinical participants were eligible if they met criteria for a diagnosis of major depressive disorder and, if they were on medication, they had been on on stable treatment with this medication for at least the past 4 weeks.
+
+\subsubsection*{Infrequency items}
+
+To measure C/IE responding in healthy and psychiatric participants, we used two sets of attention checks.
+Each set was composed of three infrequency items and one instructed item.
+Participants were assigned one or the other set.
+The six infrequency items were:
+
+\begin{enumerate}
+    \item Worrying too much about the 1977 Olympics.
+    \item I have never used a computer.
+    \item I would be able to lift a small (1 lb) weight.
+    \item Have there been times of a couple days or more when you were able to stop breathing entirely (without the aid of medical equipment)?
+    \item Over the past year, how often did you have days where you were able to blink your eyes without difficulty?
+    \item I am generally able to remember my own name.
+\end{enumerate}
+
+\subsubsection*{Analysis}
+
+Of primary interest here is whether psychiatric patients fail infrequency item attention checks at equal or greater rates than healthy participants.
+To test this, we conducted Bayesian hypothesis testing using Bayes factors \cite{harms2018making}.
+Specifically, we defined three competing models:
+
+\begin{itemize}
+    \item $M_0: \text{Binom}(N_1, p), \text{Binom}(N_2, p)$  
+    \item $M_1: \text{Binom}(N_1, p - \delta), \text{Binom}(N_2, p + \delta)$  
+    \item $M_2: \text{Binom}(N_1, p + \delta), \text{Binom}(N_2, p - \delta)$  
+\end{itemize}
+
+where $N_1$ and $N_2$ are the observed number of healthy and psychiatric patients; $p$ is the latent probability of a participant failing one or more attention checks; and $\delta$ is an offset parameter specifying the hypothesized difference in failure rates between groups.
+Thus, $M_0$ assumes equal rates of failures between healthy and psychiatric participants, whereas $M_1$ and $M_2$  assume greater and lower rates, respectively, for psychiatric participants compared to healthy participants.
+The common latent probability, $p$, was set to the observed average rate across the two groups.
+The offset, $\delta$, was set to 0.05.
+This value was selected because it signifies a difference in portions of $\Delta p = 0.1$, corresponding to a small effect for a difference in proportions test ($h = 0.2$; \cite{cohen2013statistical}).
+
+\subsection*{Results}
+
+In total, 16 of 65 (24.6\%) participants failed one or more attention checks.
+Interestingly, the overall proportion of flagged participants is similar to that observed for the original study.
+Subdivided by group, 6 of 20 (30\%) healthy participants and 10 of 45 (22\%) psychiatric participants were flagged for C/IE responding.
+Unsurprisingly, given the sample size, the difference in the two proportions was not significantly different than zero ($z = 0.672$, $p = 0.502$).
+Across six infrequency items, the average failure rate was 8.5\% (range: 0.0\% -- 19.7\%).
+In contrast, no participant failed either instructed item.
+This result further corroborates previous research, which has found that instructed items are poor measures of C/IE responding \cite{barends2019noncompliant-2, thomas2017validity-2, hauser2016attentive-2}.
+
+Next, we computed the Bayes factor for each pair of candidate models.
+A model assuming equal rates of failure between healthy and psychiatric participants was 2.88 times more likely than the model assuming greater rates for psychiatric patients.
+In turn, a model assuming lower rates of failure for psychiatric patients was 1.27 times more likely than the model assuming equal rates.
+Finally, a model assuming lower rates of failure for psychiatric patients was 3.65 times more likely than the model assuming higher rates for psychiatric patients.
+Only the final comparison exceeds the cutoff value of 3, which is conventionally treated as the minimal amount of evidence required to treat a model comparison as meaningful.
+
+\subsection*{Discussion}
+
+Here we sought to examine whether actual psychiatric patients were equally or more likely to fail infrequency items than healthy controls in settings similar to those experienced by online participants.
+Though the small sample precludes any definitive conclusion, it is noteworthy that the model least consistent with the data is the one where psychiatric patients are more likely to fail infrequency item attention checks.
+Indeed, a model where healthy controls failed attention checks at a greater rate than patients was credibly preferred to the alternative.
+This preliminary finding may reflect differences in motivation between patients and controls for participating in psychiatric research.
+Indeed, whereas healthy controls may be primarily motivated to participate for monetary purposes, patients may be motivated to participate to further scientific research that may ultimately benefit them (or others suffering from the same conditions).
+That is, patients may have more ``stakes in the game'' and therefore be motivated to provide higher-quality responses.
+Regardless, further research is required to examine whether this preliminary finding holds in larger samples and other testing contexts.
+
+\section*{Supplementary references}
+
+\printbibliography[heading=supp]
+\end{refsection}
 

### 2022-11-16 manuscripts/main.tex
dan's edits

@@
 
-Here we wish to draw special attention to an underappreciated feature of online psychiatric research using self-report symptom surveys.
+Here we wish to draw special attention to an underappreciated feature of psychiatric research using self-report symptom surveys.
 In such surveys, participants rate their endorsement of various psychiatric symptoms and, since most individuals in the general population tend to endorse no or few symptoms in many symptom domains, the resulting ground-truth symptom distributions tend to be heavily positively skewed \cite{lowe2008validation, tomitaka2018distributional}.
 In this situation, the assumption that C/IE responding merely increases unsystematic measurement noise becomes untenable.
-Because of the positive skew in the ground-truth symptom distribution, participants who respond carelessly to the symptom survey are more likely to report higher levels of symptom endorsement relative to participants who complete the survey accurately \cite{chandler2020participant, ophir2020turker, king2018random}.
+Because of the positive skew in the ground-truth symptom distribution, participants who respond carelessly to the symptom survey are more likely to report higher levels of symptom endorsement relative to participants who complete the survey attentively \cite{chandler2020participant, ophir2020turker, king2018random}.
 Consequently, unless C/IE survey responses are carefully identified and removed, a considerable proportion of putatively symptomatic individuals in an online sample may, in fact, be participants who have not engaged with the experiment with sufficient attention or effort.
@@
 We hypothesise that spurious behavior-symptom correlations may emerge due to a mean-shift in the average level of symptom endorsement in participants engaging in C/IE responding relative to attentive participants.
-In turn, a mean-shift is expected to occur when the overall rate of symptom endorsement is low.
+In turn, a mean-shift is expected to occur when the overall rate of symptom endorsement is low; that is, comparably higher scores are more likely for C/IE participants responding at random on a right skewed questionnaire.
 In line with our predictions, the average level of symptom endorsement was noticeably exaggerated in C/IE-responding participants for the symptom measures where symptom scores were most positively-skewed (7-up, 7-down, GAD-7; see Figure \ref{fig:distributions}).
@@
 We observed a credible difference between the average value of this intercept for the two groups ($\Delta \text{intercept} = 0.67, 95\% \ \text{HDI} = [-0.78, -0.55]$), such that C/IE participants were biased towards using the right-half of survey response options.
-This translates to a tendency to endorse \emph{more severe} symptoms on the 7-up/7-down and GAD-7 scales (where the rightmost options indicate greater frequency of symptoms) but \emph{less severe} symptoms on the SHAPS and BIS (where the rightmost options indicate lower frequency of symptoms) despite these inventories measuring strongly correlated constructs (i.e.
+This translates to a tendency to endorse \emph{more severe} symptoms on the 7-up/7-down and GAD-7 scales (where the rightmost options indicate greater frequency of symptoms) but \emph{less extreme} symptoms or personality traits on the SHAPS and BIS (where the rightmost options indicate lower frequency of symptoms or personality traits) despite these inventories measuring strongly correlated constructs (i.e.
 depression and anhedonia, anxiety and behavioral inhibition).
@@
 \caption{Absolute Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions.
-Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons; all correlations are shown in the Supplement).
+Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons; all signed correlations are shown in the Supplement).
 Black Xs indicate significant correlations ablated under screening.
@@
 Across all analyses, we measured the correlation and between the 7-down depression scale and learning-rate asymmetry ($\kappa$), which we previously identified as likely exhibiting a spurious association.
+(The following results are not specific to learning-rate asymmetry and generalize to other pairs of variables; Figure \ref{fig:bootstrap_s1}).
 
@@
 Although this assumption is correct for unsystematic measurement error, it no longer holds in the regime of systematic measurement error (where larger sample sizes reduce the variance of estimates, but do not alter their bias).
-Instead, our results suggest that, holding the proportion of C/IE responding constant, the false-positive rate for behavioral-symptom correlations will become increasingly inflated as the sample size increases.
+Instead, our results suggest that, except for low rates of C/IE responding, the false-positive rate for behavioral-symptom correlations will become increasingly inflated as the sample size increases.
 
@@
 These estimates are within the realm of epidemiological norms \cite{kessler2012twelve, lowe2008validation, yarrington2021impact}.
-We also observed some positive correlations between anxiety and choice behavior that were consistent with effects found in previous literature \cite{huang2017computational, harle2017anhedonia, garrett2018updating}.
+(We should note, however, that some studies have found elevated rates of psychiatric symptomology in online participants even after controlling for C/IE responding \cite{ophir2020turker}.) We also observed some positive correlations between anxiety and choice behavior that were consistent with effects found in previous literature \cite{huang2017computational, harle2017anhedonia, garrett2018updating}.
 For example, we found higher lose-shift rates and higher learning rates following negative prediction errors correlated with self-reported anxiety.
@@
     \item When collecting self-report questionnaire data, include attention-check items that flag participants who may be engaging in C/IE responding.
-We recommend following best-practice guidelines in using infrequency-item checks rather than instructed-item checks \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}.
+We recommend following best-practice guidelines in using infrequency-item checks rather than instructed-item checks, as multiple studies have now shown that online participants are habituated to and circumvent the latter  \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}.
 Participants flagged by suspicious responses on attention-check items should either be excluded from further analysis, or assessed using sensitivity analyses to ensure that observed full-sample correlations are robust to their exclusion.
@@
 ``psychiatry", ``mental illness", ``depression").
+We note that it was not feasible to conduct a systematic review, which would require using a publication database other than Google Scholar (i.e.
+this is because search results from Google Scholar are tailored to individual users and are therefore by definition unsystematic and unreproducible).
+Our science librarian nevertheless recommended we use Google Scholar because it performs full-text search, which was necessary here to identify papers; that is, recruitment methods (e.g.
+``Mechanical Turk'') are infrequently reported in the title or abstract of a paper.
 We included studies that (a) recruited participants online through a labour platform, (b) measured behavior on at least one experimental task, and (c) measured responses on at least one self-report symptom measure.
 Through this approach, we identified for inclusion 49 studies spanning 2015 through 2020.
+The complete list of studies, and search terms used to find them, are included in the Github repository for this study.
 
 Two of the authors (S.Z., D.B.) then evaluated whether and how each of these studies performed data quality screening for both the collected task and self-report data.
-Specifically, we confirmed whether a study had performed a particular type of data screening, where the categories were themselves chosen based on commonalities in methods which emerged across the studies.
+Specifically, we confirmed whether a study had performed a particular type of data screening.
+The categories were determined based on previous taxonomies of screening methods (e.g.
+\cite{curran2016methods}).
 In addition, we assessed the total number of screening measures each study used and how monetary bonuses were paid to participants (if at all).
@@
 Participants were eligible if they resided in the United States or Canada; participants from MTurk were recruited with the aid of CloudResearch services \cite{litman2017turkprime}.
-(Note: This study was conducted prior to the introduction of CloudResearch's new data quality filters \cite{cloudresearch_2020}).
+(Note: This study was conducted prior to the introduction of CloudResearch's newest data quality filters \cite{cloudresearch_2020}).
 Following recent recommendations \cite{robinson2019tapped}, MTurk workers were not excluded based on work approval rate or number of previous jobs approved.
 No other exclusion criteria were applied during recruitment.
+It is important to note that both CloudResearch and Prolific internally use a number of tools (e.g.
+IP-address screening) to filter out the lowest quality participants.
+In addition, our custom experiment delivery software (NivTurk; see below) has bot-checking functionality built into it.
+We are confident that our study is not strongly affected by participants using software to automatically complete the experiment.
 
@@
 Three participants (all MTurk) were excluded due to missing data.
-In addition, we excluded 20 participants who disclosed that they had also completed the experiment on the other platform (MTurk: N=19, Prolific: N=1).
+In addition, we excluded 20 participants who disclosed that they had also completed the experiment on the other platform.
 This left a final sample of N=386 participants (MTurk: N=186, Prolific: N=200) for analysis.
@@
 The task was programmed in jsPsych \cite{deleeuw_2015_jspsych} and distributed using custom web-application software.
-The experiment code is available at \url{https://github.com/nivlab/ThreeArmJS}, and the web-software is available at \url{https://github.com/nivlab/nivturk}.
-A playable demo of the task is available at \url{https://nivlab.github.io/ThreeArmJS}.
+The experiment code is available at \url{https://github.com/nivlab/sciops}, and the web-software is available at \url{https://github.com/nivlab/nivturk}.
+A playable demo of the task is available at \url{https://nivlab.github.io/jspsych-demos/tasks/3arm/experiment.html}.
 
@@
 
-Prior to completing the reversal learning task, participants completed five self-report symptom measures.
+Prior to completing the reversal learning task, participants completed five self-report symptom and personality-trait measures.
 The symptom measures were selected for inclusion based on their frequency in clinical research, and for having an expected mixture of symmetric and asymmetric score distributions.
@@
 
+\subparagraph{Task-based screening variables}
+
 \subparagraph{Variability} Choice variability was defined as the fraction of trials of the most used response option per participant.
@@
 
+\subsection*{Signed correlation analysis}
+
+\begin{figure}[H]
+\includegraphics[width=17cm]{../figures/supp_01.png}
+\centering
+\captionsetup{width=0.88\textwidth}
+\caption{Signed Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions.
+Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons).
+Black Xs indicate significant correlations ablated under screening.
+No Screening = no exclusions; Accuracy Only = exclusions based on chance-level performance in the reversal-learning task; Infrequency Only = exclusions based on invalid or improbable responses to infrequency items; Both Types = exclusions based on the previous two measures.
+Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
+\label{fig:correlations_s1}
+\end{figure}
+
+\clearpage
+
 \subsection*{Bootstrapping Analysis}
 \begin{figure}[H]
-\includegraphics[width=16cm]{../figures/supp_01.png}
+\includegraphics[width=16cm]{../figures/supp_02.png}
 \centering
@@
 
+\subsection*{The relationship between sample size and false positive rates generalize to other sets of variables}
+
+\begin{figure}[H]
+\includegraphics[width=16cm]{../figures/supp_03.png}
+\centering
+\captionsetup{width=0.88\textwidth}
+\caption{False positive rates for spurious correlations \emph{increase} with sample size.
+\textit{Left:} Bootstrapped Spearman correlations between inverse temperature ($\beta$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants.
+The grey error bars indicate 95\% bootstrap confidence intervals.
+The thick dashed lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size.
+Markers are jittered along the x-axis for legibility.
+\textit{Right:} False positive rates for inverse temperature ($\beta$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants.
+False positive rate was calculated as the proportion of bootstrap samples in which the correlation between $\beta$ and 7-down was statistically significant.
+The horizontal dotted line denotes the expected false positive rate at $\alpha = .05$.}
+\label{fig:bootstrap_s1}
+\end{figure}
+
+\clearpage
+
+\subsection*{The relationship between sample size and true positive rates for true correlations}
+
+\begin{figure}[H]
+\includegraphics[width=16cm]{../figures/supp_04.png}
+\centering
+\captionsetup{width=0.88\textwidth}
+\caption{True correlations are independent of the proportion of C/IE participants in the sample.
+\textit{Left:} Bootstrapped Spearman correlations between learning rate asymmetry ($\kappa$) and anxiety scores (GAD-7) as a function of sample size and proportion of C/IE participants.
+The grey error bars indicate 95\% bootstrap confidence intervals.
+The thick dashed lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size.
+Markers are jittered along the x-axis for legibility.
+\textit{Right:} True positive rates for learning rate asymmetry ($\kappa$) and anxiety scores (GAD-7) as a function of sample size and proportion of C/IE participants.
+True positive rate was calculated as the proportion of bootstrap samples in which the correlation between $\kappa$ and GAD-7 was statistically significant.
+The horizontal dotted line denotes the expected false positive rate at $\alpha = .05$.}
+\label{fig:bootstrap_s2}
+\end{figure}
+
+\clearpage
+
 \subsection*{Posterior predictive checks}
@@
 \begin{figure}[H]
-\includegraphics[width=16cm]{../figures/supp_02.png}
+\includegraphics[width=16cm]{../figures/supp_05.png}
 \centering
@@
 
-\subsection*{Participant Demographics}
+\subsection*{Participant demographics}
 
@@
 On average, the samples were similar though the sample from Mechanical Turk was older (t = 6.567, p $<$ 0.001) and comprised of fewer women (z = 6.567, p = 0.011).
-Note: the demographics do not include 20 participants (MTurk: N=19; Prolific: N=1) excluded for participating in the study twice, once per platform.}
+Note: the demographics do not include 20 participants excluded for participating in the study twice, once per platform.}
 \label{tab:demographics}
+\end{table}
+
+\clearpage
+
+\subsection*{Careless participants show different behaviors on the reversal learning task}
+
+\begin{table}[H]
+\centering
+\begin{tabular}{lrrr}
+\toprule
+{} &  Attentive &    C/IE &   $t$-value \\
+\midrule
+Acc      &      0.587 &   0.532 &  $4.008^*$  \\
+Pts      &     50.163 &  47.729 &  $2.376^*$  \\
+WS       &      0.898 &   0.776 &  $5.387^*$  \\
+LS       &      0.609 &   0.751 &  $-5.335^*$ \\
+Pers     &      0.245 &   0.259 &  $-1.505$ \ \\
+$\beta$  &      6.754 &   4.082 &  $5.404^*$  \\
+$\eta_p$ &      0.643 &   0.551 &  $2.846^*$  \\
+$\eta_n$ &      0.738 &   0.784 & $-1.516$ \  \\
+$\kappa$ &     -0.069 &  -0.218 &  $3.729^*$  \\
+\bottomrule
+\end{tabular}
+\captionsetup{width=0.88\textwidth}
+\caption{Measures of task behavior compared between attentive and C/IE participants.
+Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.
+* Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
 \end{table}
@@
 
-This result may be initially surprising, since one might expect choice hysteresis to result in more perseveration errors following contingency reversals, and since we observed in the previous section that C/IE responding was associated with more perseveration errors.
+This result may be initially surprising, since one might expect choice hysteresis to result in more perseveration errors following contingency reversals.
 However, choice hysteresis is adaptive in this probabilistic reversal-learning task.
@@
 For thresholded analyses, participants were flagged if they responded incorrectly to one or more of these items.
+
+\subparagraph{Task-based screening variables}
 

### 2023-01-13 02_Replication/scripts/compute_metrics.py
rename 'key variability' to 'side variability'

@@ -158,16 +158,16 @@ rt['survey_rt'] = rt.filter(regex='rt').sum(axis=1)
 metrics = metrics.merge(rt)
 
 #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
-### 1.6 Key Variability.
+### 1.6 Side Variability.
 #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
-print('1.6 Computing key variability.')
+print('1.6 Computing side variability.')
 
 ## Compute most chosen option within subjects.
 f = lambda x: np.abs(np.mean(x) - 0.5)
 gb = data.groupby(['platform','subject']).state_1_key.apply(f).reset_index()
 
 ## Rename columns.
-gb = gb.rename(columns={'state_1_key':'key_var'})
+gb = gb.rename(columns={'state_1_key':'side_var'})
 
 ## Merge with reject.
 metrics = metrics.merge(gb)

### 2023-01-16 manuscripts/letter.tex
latest drafts

% set document class
\documentclass[a4paper,notitlepage,12pt]{article}

% load packages
\usepackage[utf8]{inputenc}
\usepackage[a4paper, margin=0.8in]{geometry}
\usepackage{authblk}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{indentfirst}
\usepackage{hyperref}
\usepackage{float}
\usepackage{amsmath}
\usepackage[backend=biber,style=nature]{biblatex}
\usepackage[flushmargin]{footmisc}
\usepackage[flushleft]{threeparttable}
\usepackage[font=small, labelfont=it]{caption}
\usepackage{csquotes}
\usepackage{soul}

% specify footnote margins
\renewcommand\footnotelayout{%
  \advance\leftskip 0.7cm
  \advance\rightskip 0.7cm
 }

% specific images path relative to the main .tex file 
\graphicspath{ {./figures/} }

% setup references
\addbibresource{letter.bib}
\renewcommand*{\bibfont}{\small}

% specify link style
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    citecolor=blue
}

% specify some custom commands
\renewcommand{\baselinestretch}{1.2}
\renewcommand*{\Authsep}{, }
\renewcommand*{\Authand}{, }
\renewcommand*{\Authands}{, }
\renewcommand*{\Affilfont}{\normalsize}

% set up the author block
\setlength{\affilsep}{2em}   % set the space between author and affiliation
\author[1]{Samuel Zorowitz}
\author[1,2]{Yael Niv}
\author[1,3]{Daniel Bennett}
\affil[1]{Princeton Neuroscience Institute, Princeton University, USA}
\affil[2]{Department of Psychology, Princeton University, USA}
\affil[3]{School of Psychological Sciences, Monash University, Australia}

% specify the title
\title{Response to reviewers for ``Inattentive responding can induce spurious associations between task behavior and symptom measures''}

% turn date off
\date{}

% Define paragraph formatting
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

\begin{document}
%TC:ignore

\maketitle

\section*{Formatting note}

In the document below, reviewers' comments are indicated in bold typeface. Quoted text from the revised manuscript is presented in quotation blocks; within these excerpts, text that is new is indicated in italicized typeface. All updates to text in the revised manuscript are detailed below.

\section*{Reviewer \#1}

\textbf{The authors presented an interesting paper in which they argued that spurious correlations may arise between task behavior and psychiatric symptoms if online studies do not conduct attention or effort level check. Specifically, the authors launched an online study themselves using two common subject pool platforms: Amazon mTurk and Prolific. They found that behavior-symptom correlations were completely abolished when inattentive subjects were removed. The authors also suggested that excluding subjects based on task behavior alone was not sufficient, and that larger sample size further inflated the problem. I find this study timely and important, as online studies are increasingly popular amongst behavioral researchers, particularly since the pandemic started. I also generally agree with the recommendation that online studies should include careful attention check. However, several major flaws in the rationale and design of this study and lack of novelty significantly diminished my enthusiasm.
}

\textbf{1. A key assumption here is that people who failed attention check artificially inflated the self-reported mental health symptoms (which then subsequently inflated correlations with behavior). This would only be true if the ``failed'' subjects are actually healthy with low mental health symptoms. However, a very likely alternative is that these so called inattentive/low effort subjects indeed have higher mental health symptoms (as the authors acknowledged in the discussion). In fact, there is a very rich literature demonstrating that many psychiatric disorders and symptoms are strongly accompanied by deficits in attention as well as lack of effort. For example, attention deficits have been well established in depression (e.g. Paelecke-Habermann et al, 2005 JAD) and anxiety (Bishop, 2009 Nat Neurosci), the two main types of mental health symptoms measured in this study. Deficits in effort-based behaviors have also been recently documented in these disorders (see Treadway et al, 2012; Bishop and Gagne, 2018). Thus, there is a reason to believe that the ``careless'' subjects' carelessness might not be random and may be contributed by their underlying mental health issues. This possibility can actually be (at least partially) supported by the last analysis conducted by the authors, where they found that ``careless'' participants behaviorally showed less adaptive choice hysteresis and reduced outcome sensitivity (a finding that has been reported to be associated with depressive and other psychiatric symptoms; e.g. see Huys et al 2013 for a meta-analysis). Of course, the ``ground truth'' is unreachable in this case, since subjects are completely anonymous on these platforms (and the best way to validate the current set of analyses would be to conduct an in-person study where mental health status could be verified by trained clinicians). But based on the data available, the assumption that subjects who were flagged ``careless /low effort'' should be mentally healthier than their reported status may just not hold for the current study.}

We thank the reviewer for this important point. We agree that the best way to validate our analyses would be to conduct an in-person study where mental health status could be verified by trained clinicians. In line with the reviewer's suggestion, we have now undertaken this additional study. The results of the new study (reported in a new section in the main text under the heading \textit{``Individuals with and without diagnosed psychiatric disorders fail attention checks at similar rates''}) provide further evidence for the overall conclusions of our manuscript.

Briefly, in the additional study we embedded attention checks within the self-report measures of two ongoing studies of patients with major depressive disorder (total N=45 patients with diagnosis verified by a structured clinical interview, and N=20 controls whose lack of psychopathology was also verified using the same interview). We did not find any evidence that patients with diagnosed major depressive disorder were more likely to fail attention checks than healthy controls, when completing the self-report symptom questionnaires online from their home (that is, under conditions as similar as possible to those in the main study we reported). Indeed, if anything, we found that non-psychiatric participants were more likely to be flagged by C/IE screening. Our results, though preliminary, suggest that rigorous C/IE screening is not likely to result in the differential exclusion of participants with elevated mental health symptoms.

The results of this additional study relate to a point that we originally made in the Discussion of our manuscript: if psychiatric participants would be more likely to fail attention checks in self-report surveys, this would entirely undermine a very large body of research in which self-report survey measures are considered a standard tool for psychiatric symptom measurement \cite{Demetriou2015-bq}. If it were truly the case that symptomatic participants were more likely to fail attention checks (i.e. because they are experiencing severe symptoms affecting their motivation or attention that render them unable to veridically complete a survey), then there would be little-to-no reason to use self-report symptom measures at all for these clinical populations. Reassuringly, our results suggest that this is not the case.

Of course, it may be the case that there are some psychiatric syndromes for which patients are unable to complete self-report surveys accurately. However, except for individuals experiencing acute mental health crises (e.g. mania, psychosis), we suggest that our results are in line with the common usage of self-report surveys in psychiatric research. As such, although we do not dispute that overcontrol bias is an important conceptual issue, we conclude that there are both empirical and theoretical reasons to believe that this issue does not undermine our results.

In addition, if these results are not yet sufficient to ease your mind regarding psychiatric overcontrol, in another new study that we detail on in response to your critique 3 below, we tested a new sample for correlations between self report of non-symptom measures (greed avoidance and artistic interests), and also found these measures to have spurious correlations with task performance when no C/IE screening was applied. Since there is no reason to expect that the correlation is specifically driven by psychopathology, an overcontrol of those suffering from psychiatric conditions should not have affected these correlations in the way it did. See more details below, and in Appendix B of the paper.

\textbf{2. Lack of novelty: If the noise in the data is real, then the current findings become unsurprising because similar ``spurious correlations'' due to inadequate quality control have been well documented in other areas of science, including cognitive neuroscience (e.g. effect of poor motion control on imaging results, as shown in Friston et al 1996; Feller et al 2016 and many others). The presented data represents a specific manifestation of a general issue in experimental science and statistics, but is not something completely new.}

We agree with the reviewer that our overarching point (i.e., that poor data quality controls can lead to spurious inferences) has been discussed, in the most general sense, elsewhere in science. Nevertheless, delineating specific instances of under-appreciated methodological biases can have major impact on methodological and empirical work within a field, as reflected in the reviewer's own suggested citations (as well as, e.g., \cite{eklund2016cluster, bradley2021unrepresentative}). In addition, our manuscript is able, by very virtue of its specificity, to make actionable recommendations for researchers studying individual differences in cognitive processes (including in computational psychiatry). We would argue that these recommendations are a major novel contribution of our work that could not readily have been extracted from, for example, publications demonstrating motion-induced artefacts in fMRI analyses. Indeed, since the publication of our initial manuscript on PsyArxiv, many researchers in computational psychiatry have changed their experiment designs to include infrequency items as we suggest (with the preprint already cited 24 times). If the need for this design feature were obvious from the extant literature, our paper should not have made such a difference in the practices in the field.

We would like to reiterate our case for the novelty of our findings. Though the perils of C/IE responding for individual-differences questionnaire research has been documented before \cite{chandler2020participant, arias2020little}, we are unaware of any manuscript prior to ours addressing the risk of spurious correlations from C/IE responding for individual-differences cognitive science research (including computational psychiatry). To this point, our literature review revealed that, whereas the majority of behavioral researchers were applying quality controls to their behavioral data, only the minority of researchers were doing the same for their self-report data (and fewer still were following best-practices). This suggests that, although behavioral researchers were aware of the need for data quality assurance protocols in general, few were aware of the need for rigorous screening of their self-report data. We feel this suggests that the arguments and results we present are indeed novel for many individual-differences cognitive science researchers (including computational psychiatry researchers).

\textbf{3. All analyses and conclusions were based on a single cognitive task. The lack of at least one more comparison task leaves the generalizability of the findings questionable. Although the chosen task is quite representative of value-based decision paradigms, it certainty does not represent the rich repertoire of cognitive processes and paradigms used in computational psychiatry research. Nevertheless, the authors made claims about how applicable the findings are to computational psychiatry in general.}

We thank the reviewer for this suggestion. Indeed, our original conclusions rested on the findings from a single task. Therefore, in this revision, we have conducted a conceptual replication study where we repeated the entire experiment and analysis with a second task (the commonly-used, considerably more complex two-step task), as well as a second set of self-report measures (including personality scales), and more stringent quality control protocols (based on changes made by CloudResearch and Prolific to their respective platforms). The results of this additional study are reported in a new section in the main text under the heading \textit{``Pattern of results generalizes to alternative tasks, self-report measures, and quality assurance protocols''}. The complete details of the methods and results for this study can be found in Appendix B of the supplementary materials. In brief, we successfully replicated the majority of findings from the original study in the second dataset. Of course, we have not confirmed our results across all task paradigms used in computational psychiatry, but we nevertheless hope that this new study goes some way towards establishing the robustness and generalizability of our original findings.

\textbf{4. The claim about larger sample size further inflating false positive rates is based on one particular index – the correlation between kappa (learning rate asymmetry) and 7-up. This particular correlation is small to start with. It is unclear if the sample size-amplified false positive rate finding is truly robust across effects with different sizes, or could be an effect size-dependent finding.}

We thank the reviewer for this point. We wish to clarify two things. First, this result is not specific to the learning rate asymmetry and 7-down scale. As we show in a new supplementary figure (Appendix A, Figure S3), this finding generalizes to other pairs of variables.

Second, we note that this result reflects a more general point concerning statistical power. When an effect is truly non-zero, then an increase in sample size increases the power to detect that effect \cite{cohen2013statistical}. However, if a bias is present in the data (e.g. a non-zero correlation between behavioral and self-report measures, driven by the presence of C/IE responding), then increasing the sample size will also increase the probability of detecting it as a significant (spurious) effect \cite{meng2018statistical}. To the reviewer's point, this is moderated by the true magnitude of the effect; larger effects require fewer observations for reliable detection (and vice-versa). If, in another dataset, the bias is larger than what was observed here (i.e. a stronger coupling between C/IE responding in task and self-report), then a smaller proportion of C/IE-responding participants would be necessary to induce a detectable spurious correlation. In sum, we suggest that there is little reason to suspect our results are effect-size dependent except insofar as they reflect general statistical principles.

\section*{Reviewer \#2}

\textbf{This manuscript has multiple strengths. The writing is generally clear (though, I recommend keeping an eye on use of jargon and unnecessarily complex grammar. Writing could be more direct and I would encourage use of plain language). The figures are well done and informative. The study is technically well done. However, while the authors frame this research as significantly progressing the field, it is my view that the contribution is much narrower and I think this makes it a poor fit for Nature Human Behaviour.}

\textbf{1. It has been well-established elsewhere that inattentive responding leads to increased symptom report on psychiatric measures. It is also well-established that inattention impacts responding on behavioral measures; for example, one measure of inattentive responding is speeding through instruments. This paper extends this finding to speeding in non-survey measures. In particular, I recommend that you take a closer look at Curran (2016), who notes a correlation between speeding and other measures of inattention and (of relevance for the discussion section) provides alternative methods of using multiple measures to screen participants.}

We thank the reviewer for this recommendation. We were indeed guided by the paper by Curran (2016) in the design, analysis, and write-up of our manuscript. In line with this influence, the article by Curran (2016) article is cited at three separate points in our manuscript.

\textbf{2. Essentially, the authors show that correlations between different measures of inattentiveness (i.e., unusually high symptom levels on psychiatric measures and performance on behavioral measures) should not be interpreted as meaningful. While this is certainly true, this is a very incremental point vs. a significant and novel contribution. In another point to narrowness, this spurious correlation should affect between-subjects measures only; did the authors look at outcomes that are within subjects and how might these be affected?}

We respectfully disagree with the reviewer's view that the results here lack novelty (see also response to Reviewer 1, point \#2). Though the perils of C/IE responding for individual-differences questionnaire research has been documented before \cite{chandler2020participant, arias2020little}, we are unaware of any manuscript prior to ours addressing the risk of spurious correlations from C/IE responding for individual-differences cognitive science research (including computational psychiatry). To this point, our literature review revealed that, whereas the majority of behavioral researchers were applying quality controls to their behavioral data, only the minority of researchers were doing the same for their self-report data (and fewer still were following best practices). This suggests that, although behavioral researchers were aware of the need for data quality assurance protocols in general, few in this growing and impactful field were aware of the need for rigorous screening of their self-report data. Importantly, this may have already led to spurious results in the field. If it were commonly accepted that correlations between unusually high symptom levels on psychiatric measures and performance on behavioral measures are not meaningful, this would have been a cornerstone in the field of computational psychiatry, as this field is predominantly interested in such correlations. Nevertheless, we had not heard of this idea prior to doing our own research on the matter.

\textbf{3. I recommend taking a look at Itay Sisso's tool to identify ``bots'' who may have completed the survey: \url{http://mail.sjdm.org/pipermail/jdm-society/2018-November/008014.html} as the ``bot'' respondents would provide a gold-standard for higher versus lower quality workers.}

We thank the reviewer for pointing out this resource. We were aware of this tool before conducting our study. Unfortunately, Sisso's bot check tool requires the collection of participants' IP addresses, which is explicitly against Prolific's terms of service for researchers \cite{prolific_ip_address}. As such, we are unable to use this particular tool for detecting ``bots'' (or organizations of workers using private servers \cite{dennis2020online}). We should note, however, that we recruited participants through CloudResearch and Prolific, which both use IP addresses to monitor and filter out suspicious participants \cite{cloudresearch_ip_address, prolific_ip_address_2}. Moreover, our custom experiment delivery software (NivTurk, \url{https://nivlab.github.io/nivturk}) has bot-checking functionality built into it. As such, we are confident that the results of the manuscript are not strongly affected by participants automatically completing the experiment. We have added additional text to the methods detailing the bot-checking functionality that our software employed:

\begin{displayquote}
Participants were eligible if they resided in the United States or Canada; participants from MTurk were recruited with the aid of CloudResearch services [51]. (Note: This study was conducted prior to the introduction of CloudResearch’s newest data quality filters [52]). Following recent recommendations [53], MTurk workers were not excluded based on work approval rate or number of previous jobs approved. No other exclusion criteria were applied during recruitment. \textit{It is important to note that both CloudResearch and Prolific use a number of tools (e.g. IP-address screening) to filter out the lowest quality participants. In addition, our custom experiment delivery software (NivTurk; see below) has bot-checking functionality built into it, and rejects from the start participants who are likely to not be human. We are therefore confident that our study is not strongly affected by participants using software to automatically complete the experiment.}
\end{displayquote}

\textbf{4. It is important to note that the authors deliberately let in lower quality workers and draw conclusions about what would be observed assuming no restrictions on worker quality or data cleaning. In practice, this combination of recruiting and data cleaning strategies is likely rare (and these are areas where detailed reporting are often lacking) and is not best practice.}

We understand the reviewer's concern, and respectfully wish to clarify an inaccuracy in their appraisal of our methods. In our main analysis (in the section, \textit{``Spurious symptom-behavior correlations produced by C/IE responding''}), we examine the consequences of multiple different types of data screening on correlations between behavioral and self-report measures. While it is true we examine a ``no screening'' condition (i.e. no exclusions are applied based on either self-report or behavioral screening measures, which our literature review corroborates as a rare strategy), we also examine conditions where we apply exclusions based on behavioral and/or self-report screening measures. Crucially, we found that screening only on behavioral screening measures (which is the most common screening strategy according to our literature review) is insufficient for ablating spurious correlations. In sum, we do evaluate data cleaning strategies common to the individual-differences cognitive science literature and find they are often lacking.

\textbf{5. Screening participants out based on their response to self-report items or behavioral measures is one approach to managing quality concerns such as inattentiveness, but only an element of best practice if a researcher is looking to maximize sample size or perhaps sample diversity. This is one consideration among many and weeding participants out earlier, such as by IP address, is another approach that may help to circumvent these issues altogether. In practice, many researchers use multiple approaches in tandem.}

We agree with the reviewer that some researchers use multiple approaches to screen for C/IE responding, and we also recommend this strategy in the manuscript (recommendation \#1 in Box 1). However, we found in our literature review that the majority of researchers used only a single method to screen their data. As such, we believe our results and recommendations are relevant to many individual-difference researchers.

We also agree with the reviewer that there approaches to screening out participants even earlier during recruitment, such as through the use of IP addresses. We again note that, unfortunately,  screening by IP address is not permitted at some commonly used online labor platforms (e.g., Prolific). Furthermore, we note that major online labor platforms perform this sort of screening as a service for researchers (including the two platforms studied here; i.e. CloudResearch, Prolific). Despite these data quality assurance protocols, however, we still found ample evidence of C/IE responding and risk for spurious correlations.

\textbf{6. The recommendations the authors provide for best practice may not be used frequently in the field of computational psychiatry, but they, and other strategies, are well described by others (see in particular work by Jesse Chandler) and, as noted above, are not universally applicable depending on the goals of a research study. Redundancy with the existing literature and narrow applicability of recommendations further limits the scope and novelty of the current manuscript.}

\textbf{Taken together, this is a well designed study and well written manuscript. If it were modified to better include the existing literature and generally be more circumspect, it would likely be of interest to a narrower journal in computational psychiatry.}

We respectfully disagree with the reviewer's suggestion that our recommendations are narrowly applicable. With the growing use of online platforms for data collection, the use of self-report surveys alongside online behavioural tasks is becoming more frequent not only in computational psychiatry, but also in fields as broad as cognitive psychology, behavioral economics, business studies, and psycholinguistics. The recommendations that we make in this manuscript complement those of Chandler and colleagues, but apply broadly to all of the fields above. Indeed, the breadth of the potential consequences of careless responding was our primary motivation for submitting this manuscript to a generalist journal such as \textit{Nature Human Behavior}.

\section*{Reviewer \#3}

\textbf{This paper addresses an important question for studies that use online testing to assess associations between cognitive processing and symptom questionnaire data, an approach that has increased dramatically (not least due to the COVID-19 pandemic) as online participant pools have been established.}

\textbf{The key finding is that such designs may produce spurious correlations – specifically, that participants who do not engage attentively in questionnaires, making random and/or ``straight-lined'' responses, will typically score higher than those who do attend, when symptoms are rare and population scores are therefore skewed. If those same participants also perform more noisily/poorly/differently on cognitive tests, then a spurious correlation between symptoms and cognitive processing may be observed. This should not happen for questionnaires without skew. The authors suggest several recommendations to minimize these effects.}

\textbf{The writing is generally clear and the authors do a good job of explaining what they did and why. I applaud the authors on a timely and detailed piece of work, which is technically sophisticated and accompanied by clearly annotated open code and data. I do however have several concerns which reduced my enthusiasm for the manuscript, as there remains a lot of ambiguity as to what is driving these effects. These are listed immediately below, followed by some more minor points.}

\textbf{Major concerns}

\textbf{1) The most serious concern relates to the potential for selection bias to influence the results. Essentially, the key result of the study is that when participants who fail attention checks (C/IE) are removed from the analysis, this reduces some symptom-behaviour correlations. However, because of the nature of the questionnaires used in the study (i.e. depression, anxiety, and mania), performance on attention checks cannot be assumed to be orthogonal to the actual construct of interest. This is because difficulty concentrating is *part of the diagnosis* of all three of these syndromes. Consequently, the authors' approach may result in genuine associations being removed/attenuated, as a large section of the population of interest (e.g. those with genuine low mood, hypomania, anxiety) have been excluded from the data. To put it another way, these participants may be failing attention checks *precisely because* they are depressed, hypomanic or anxious, and therefore suffer concentration difficulties. This is analogous to the common statistical error of ``controlling for'' cognitive impairment in case-control studies of schizophrenia – by doing so, one removes important variance that is inherent to the construct of interest (Miller and Chapman, Journal of Abnormal Psychology 2001).}

We thank the reviewer for this important point (see also Reviewer 1, point \#1). We agree with the reviewer that the best way to validate our analyses would be to conduct an in-person study where mental health status could be verified by trained clinicians. Indeed, this is precisely what we have now done. Specifically, we embedded attention checks into the self-report measures of two ongoing studies of patients with major depressive disorder (total N=45 patients with diagnosis verified by a structured clinical interview, and N=20 controls whose lack of psychopathology was also verified using the same interview). The results of this study are reported in a new section in the main text under the heading \textit{``Individuals with and without diagnosed psychiatric disorders fail attention checks at similar rates''}. The complete methodological and analytic details of the study can be found in Appendix C of the supplementary materials. In brief, we did not find any evidence that patients with diagnosed major depressive disorder were more likely to fail attention checks than healthy controls (if anything, non-psychiatric participants were more likely to be flagged by C/IE screening). Our results, though preliminary, suggest that rigorous C/IE screening is unlikely to result in the differential exclusion of participants with elevated mental health symptoms.

\textbf{A more convincing demonstration of the hypothesized spurious correlations would require data from a questionnaire that resulted in substantial skew due to rare endorsement, but where difficulty concentrating was *not* an inherent part of the construct in question. An example might be computer programming experience.}

We thank the reviewer for this excellent suggestion, and agree that a stronger demonstration of our hypotheses would be to demonstrate the main result using a questionnaire where difficulty concentrating was not an inherent part of the construct in question. To do so, we conducted a conceptual replication study where we repeated the entire experiment and analysis with a new task (the two-step task), a second set of self-report measures, and more stringent quality control protocols (based on changes made by CloudResearch and Prolific to their respective platforms). Crucially, in this new study, we used self-report personality measures (i.e. HEXACO greed avoidance and artistic interests subscales) that are (a) not related to psychiatric symptoms, including difficulty concentrating, and (b) not hypothesized to have any relation to the behavior of interest (i.e. model-based choice on the two-step task). The results of this study are reported in a new section in the main text under the heading \textit{``Pattern of results generalizes to alternative tasks, self-report measures, and quality assurance protocols''}. The complete methodological and analytic details of the study can be found in Appendix B of the supplementary materials. In brief, we observed a mean-shift in scores on the greed avoidance scale between attentive participants and participants flagged for C/IE responding. In the absence of screening, this translated into a significant, spurious correlation between greed avoidance and model-based planning behavior; this correlation was ablated when proper screening and exclusion protocols were applied. We hope that this new study demonstrates the robustness and generalizability of our original findings.

\textbf{2) The authors do touch on the above point in their discussion. They suggest that any participant who fails even a single attention check must presumably not be responding veridically throughout the entire data collection procedure, thus that all of their data is untrustworthy, undermining the suitability of online testing to examine syndromes such as depression. I felt this discussion lacked nuance. In fact, it is likely that participants will adopt several strategies to answer self-report questionnaires (e.g. skimming the questions before starting), which may be incentivized by how studies are designed and rewarded, and indeed the nature of the questionnaire itself.}

We agree that it is somewhat simplistic to assume that a participant who fails an attention check must therefore not be responding veridically for any part of the study. Nevertheless, we suggest that, given the potential for spurious correlations that we have documented, it is prudent to take a conservative approach to data collection by excluding these participants. Though it may be the case that a participant is inattentive on some questionnaires but attentive on others, upon observing a failed attention check we cannot determine exactly how inattentive a participant has been. In this manuscript, we therefore suggest  a conservative approach to experimental rigor in which any participant suspected of inattentive responding in any part of the experiment is excluded, precisely because we cannot know exactly how much of their dataset is likely to be contaminated.

Notwithstanding the above, one response to this legitimate concern is to take a graded approach to screening and excluding participants \cite{Kim2018-ev}. That is, participants could be screened with respect to a multitude of measures and only the consistently flagged participants be removed, thereby reducing the risk of inducing bias. Another possibility is to use sensitivity analysis as an alternative to exclusion, testing whether full-sample observed correlations are robust to the exclusion of participants flagged by measures of C/IE responding. We note these alternative possibilities in the discussion of our manuscript. For example, we write:

\begin{displayquote}
Notwithstanding the above, one response to this legitimate concern is to take a graded approach to screening and excluding participants [41]. That is, participants could be screened with respect to a multitude of measures and only the consistently flagged participants be removed, thereby reducing the risk of inducing bias. Another possibility is to use sensitivity analysis as an alternative to exclusion, testing whether full-sample observed correlations are robust to the exclusion of participants flagged by measures of C/IE responding.
\end{displayquote}

\textbf{3) Other than a model-agnostic analysis examining trial-by-trial effects, the authors do not show to what extent C/IE participants and the rest of sample differ on behavioural measures (although they do this for questionnaire measures). If C/IE participants also differ on behavioural measures, it is likely that a statistical artifact, known as collider bias (also driven by selection bias), may occur when they are excluded, as participants who have *both* high depression (for example) and poor performance are being removed through this procedure. The effect of this would then be to either reduce real associations between depression and cognitive variables, or even induce counter-intuitive associations where none were present before.}

We thank the reviewer for this very interesting point. We respectfully disagree, however, that collider bias poses a threat in this study. To illustrate our arguments, we visualize below two candidate causal models of the relationships between two latent variables, major depression and a tendency towards C/IE responding, and three observed indicators, self-report scores, task performance, and failures on infrequency items (Figure \ref{fig:dag}). Before we discuss each model, we note that a collider variable is defined as a variable that is affected by an independent (exposure) and dependent (outcome) variable \cite{elwert2014endogenous, wysocki2022statistical}. In turn, collider bias is defined as a spurious association between those two antecedent variables that is caused by controlling for a collider.

\begin{figure}[t]
\includegraphics[width=\textwidth, trim={0 1cm 0 1cm}]{../figures/r2r_01.png}
\centering
\captionsetup{width=\textwidth}
\caption{Directed acyclic graphs (DAG) depicting the hypothesized causal relations between latent variables (circles) and observed indicators (squares). (A) A causal model where major depression (MDD) and a tendency towards C/IE responding are independent common causes that affect self-report scores and task performance, but only C/IE tendencies affect the probability of failing infrequency-item checks. Here, excluding participants based on infrequency items (dotted line) controls only for C/IE tendencies, thereby unconfounding the correlation between task and self-report measures. (B) A causal model where major depression (MDD) is a common cause---mediated by a tendency towards C/IE responding---that affects self-report scores, task performance, and the probability of failing infrequency-item checks. Here, excluding participants based on infrequency items (dotted line) would be tantamount to controlling for depression, thereby attenuating correlations between task and self-report measures (i.e. overcontrol bias).}
\label{fig:dag}
\end{figure}

The first candidate model is where major depression (MDD) and a tendency towards C/IE responding are independent common causes that affect self-report scores and task performance, but where only C/IE tendencies affect the probability of failing infrequency-item checks (Figure \ref{fig:dag}A). To elaborate, latent depression straightforwardly affects self-report scores as individuals experiencing depression are more likely to endorse having symptoms; latent depression also affects task performance through changes in cognitive processing (e.g. lower reward sensitivity). In turn, a tendency towards C/IE responding affects self-report scores, task performance, and infrequency-item failure rates via the mechanisms proposed in this manuscript (e.g. random responding). In this model, excluding participants based on infrequency items controls only for C/IE tendencies, thereby unconfounding the correlation between task and self-report measures caused by latent depression.

The second candidate model, as suggested by the reviewer, is where major depression (MDD) is a common cause---mediated by a tendency towards C/IE responding---that affects self-report scores, task performance, and infrequency-item failure rates (Figure \ref{fig:dag}B). In this model, latent depression affects attentiveness and/or motivation, which in turn affects performance on all three outcome measures. (We note that this illustration omits possible direct paths between depression and self-report scores \& task performance, caused by other facets of the disorder [e.g. anhedonia]; this omission, however, does not affect our conclusions.) Here, excluding participants based on infrequency items would be tantamount to controlling for depression, thereby attenuating correlations between task and self-report measures (i.e. overcontrol bias).

We add three brief remarks. First, model 1 motivates much of our manuscript, whereas model 2 represents the reviewer's aforementioned hypothesis. Second, model 1 is more consistent with the results of our new patient study. That is, in this study, depression status is seemingly uncorrelated with the probability of failing attention checks and, as such, a tendency towards C/IE responding. Third, none of the outcome variables in either candidate model are collider variables. That is, none of the outcome variables, directly or indirectly, affect the latent variables (e.g. task performance does not change depression status). As such, we do not believe we are at risk for collider bias.

\textbf{Therefore, it would be important to include a data table analogous to Table 2, but including the behavioural outcome measures shown in Figure 4. Apologies if this was already included, but I couldn't see it. This is particularly important because the example given in Figure 1 appears to depend on poorer task accuracy in the C/IE group, but we have no evidence presented in the paper that this is actually the case.}

We thank the reviewer for this point. We agree such a table would be instructive for readers and have included it in the supplementary materials (see Appendix A, Table S2). As can be found there, we observed a number of significant differences in task performance between attentive and C/IE participants, including a significant decrease in accuracy in the C/IE group.

\textbf{4) Interestingly, the study shows minimal evidence that C/IE participants are generally inattentive on tasks, as assessed for example through chance performance. The model-agnostic analysis presented in Figure 6 suggests that the groups are really quite similar in their task strategies, with no clear difference in reward/punishment sensitivity. A complement to the above point is that if C/IE are performing very similarly to the rest of the sample, it is hard to understand how their inclusion could induce spurious correlations.}

While it is true that relatively few participants showed performance on the task at or below chance level, we do not necessarily agree that C/IE participants performed quite similarly. As shown in Table S2, there are quite a number of metrics on which C/IE participants were different than attentive participants (e.g. choice accuracy, proportion of win-stay and lose-shift choices, sensitivity to positive prediction errors). We hope that the inclusion of this table addresses the reviewer's concern by illustrating that C/IE participants differed in several important aspects of task behaviour compared with more attentive participants.

\textbf{5) Despite the significant difference between the groups in Cronbach's alpha, it is still high (in some cases identical) in the C/IE sample for almost all questionnaires (other than BIS/BAS) which appears inconsistent with the suggestion that these participants are making completely random responses. In any case, this is not a strong argument for the authors' position (as I understand it), as what they define as ``C/IE'' responding could equally involve random selection or ``straight-lining'' (i.e. choosing the same response for all items), which would produce either very low or high alpha, respectively.}

Indeed, on average, the internal consistency of scale scores remains high among participants flagged for C/IE responding. We disagree, however, that this is inconsistent with our suggestion that these participants are responding without regard to the actual questions. Our rationale is based on a study by DeSimone et al. (2018) \cite{desimone2018differential}. In Figure 2 of this paper, the authors show that, even when 20\% of a sample is composed of truly random responding participants (i.e. approximately the same proportion of participants we flagged for C/IE responding), Cronbach's alpha decreases visibly but not dramatically. This suggests that we should not expect \textit{colossal} reductions in internal consistency even with non-negligible numbers of C/IE participants. (In fact, Cronbach's alpha does not reach unacceptably low values [$\alpha < 0.8$] until more than half the sample is composed of C/IE participants.)

We do agree with the reviewer that C/IE responding, as we have defined it, could equally involve true random responding or straight-lining. As they note, these two response behaviors have opposite impacts on internal consistency \cite{desimone2018differential}. Averaging across scales, however, we found that only approximately 10\% of participants flagged for C/IE responding show evidence of straight-lining (i.e. choosing the same response for all items). Thus, we can expect that the majority of C/IE participants were engaging in heuristic response strategies closer to random responding, which should in turn lead to a decrease in internal consistency. Indeed, this is what we observed on average across scales. In sum, we believe this analysis is an effective sanity check to show C/IE participants are appropriately flagged as such.

\textbf{Minor}

\textbf{Results}

\textbf{P2 – it isn't clear why this is specifically an issue for online research. Why would such spurious associations not arise for in-person testing?}

We agree with the reviewer that this is not necessarily an issue specific to online research. We have removed the word ``online'' to make this point clearer. The text now reads:

\begin{displayquote}
Here we wish to draw special attention to an underappreciated feature of \st{online} psychiatric research using self-report symptom surveys.
\end{displayquote}

\textbf{P2 – ``complete the survey accurately''. Since there is no objective truth for many such questionnaires, this is not an appropriate description – I suggest ``attentively''.}

We agree with the reviewer and have modified the text as suggested. The sentence now reads:

\begin{displayquote}
Because of the positive skew in the ground-truth symptom distribution, participants who respond carelessly to the symptom survey are more likely to report higher levels of symptom endorsement relative to participants who complete the survey \st{accurately} \textit{attentively}.
\end{displayquote}

\textbf{P4 - it would be useful to clarify in the text why instructed-item checks are not useful, especially as avoiding them is listed as a recommendation in Box 1.}

We agree with the reviewer that this would be a helpful clarification. We have expanded the text in our recommendations (Box 1) to include this point:

\begin{displayquote}
When collecting self-report questionnaire data, include attention-check items that flag participants who may be engaging in C/IE responding. We recommend following best-practice guidelines in using infrequency-item checks rather than instructed-item checks, \textit{as multiple studies have now shown that online participants are habituated to and circumvent the latter} [18-20]. Participants flagged by suspicious responses on attention-check items should either be excluded from further analysis, or assessed using sensitivity analyses to ensure that observed full-sample correlations are robust to their exclusion.
\end{displayquote}

\textbf{P5 - the hypothesis could be worded more clearly. The ‘mean-shift' terminology could be complemented by explanation of what a mean-shift would result in (e.g. higher scores would be likely in C/IE participants responding at random to a right skewed questionnaire).}

We thank the reviewer for this suggestion. We have updated the text, which now reads:

\begin{displayquote}
We hypothesise that spurious behavior-symptom correlations may emerge due to a mean-shift in the average level of symptom endorsement in participants engaging in C/IE responding relative to attentive participants. In turn, a mean-shift is expected to occur when the overall rate of symptom endorsement is low; \textit{that is, comparably higher scores are more likely for C/IE participants responding at random on a right skewed questionnaire.} In line with our predictions, the average level of symptom endorsement was noticeably exaggerated in C/IE-responding participants for the symptom measures where symptom scores were most positively-skewed (7-up, 7-down, GAD-7; see Figure 2). 
\end{displayquote}

\textbf{P7 – it isn't really appropriate to term BIS/BAS ``symptom'' measurements, really these are personality constructs}

We agree that the BIS/BAS constructs are better understood as personality measurements rather than symptom measures (their frequent use in clinical research notwithstanding). We have therefore updated our description of the questionnaires to reflect this:

\begin{displayquote}
Prior to completing the reversal learning task, participants completed five self-report symptom \textit{and personality-trait} measures.
\end{displayquote}

\begin{displayquote}
This translates to a tendency to endorse more severe symptoms on the 7-up/7-down and GAD-7 scales (where the rightmost options indicate greater frequency of symptoms) but less \st{severe} extreme symptoms \textit{or personality traits} on the SHAPS and BIS (where the rightmost options indicate lower frequency of symptoms\textit{ or personality traits}) despite these inventories measuring strongly correlated constructs (i.e. depression and anhedonia, anxiety and behavioral inhibition).
\end{displayquote}

\textbf{P11 – Figure 4, it would be easier to understand the results if signed, not absolute, correlations were indicated (e.g. using both blue and red colours).}

We thank the reviewer for this helpful suggestion. At the reviewer's request, we have included such a figure in the supplement (Appendix A, Figure S1). We elected not to make this change in the main text because we felt that a version of Figure 4 using a diverging colormap (e.g. red-blue) was more difficult to parse and detracted from our overall point about the absolute strength of associations.

\textbf{P12 - it is not completely clear why the $\kappa$ parameter was chosen for the bootstrapped correlation analyses. It would be interesting to see if the effects still hold for another potentially `spuriously-correlated' parameter, such as learning rate or inverse temperature; and for a parameter that wasn't considered to have a spurious relationship and continued to be significant, such as the 7up and inverse temperature.}

We thank the reviewer for this helpful suggestion. We agree that the choice of the $\kappa$ parameter was not well-motivated. We have added an additional figure (Appendix A, Figure S2) to show that the results are not specific to $\kappa$ and indeed generalize to other pairs of variables. Furthermore, we have amended the main text to reflect this change:

\begin{displayquote}
Next, we investigated how spurious correlations depended on sample size. To do so, we performed a bootstrapping analysis where we held fixed the proportion of participants engaging in C/IE responding (i.e. 5\%, 10\%, 15\%, 20\%) and increased the total number of participants. Across all analyses, we measured the correlation and between the 7-down depression scale and learning-rate asymmetry ($\kappa$), which we previously identified as likely exhibiting a spurious association. \textit{(The following results are not specific to learning-rate asymmetry and generalize to other model parameters; Figure S2).}
\end{displayquote}

In addition, we have added a figure (Appendix A, Figure S3) showing the effects of sample size and proportion of C/IE participants on the true positive rate for a correlation that we expect to be non-spurious for theoretical reasons (the correlation between learning rate asymmetry, $\kappa$, and GAD-7 scores). As can be observed, the true positive rate is essentially unaffected by the proportion of C/IE participants, supporting the hypothesis that this reflects a non-spurious association.

\textbf{P13 - the authors should temper their discussion on spurious correlations and ensure they caveat that the false-positive rate did not depend only on sample size, but proportion of C/IE respondents in the population (e.g. at 5\% the FPR actually seemed stable).}

We agree with this suggestion and have tempered our language regarding the relationship between false-positive rate, sample size, and proportion of C/IE participants. The text now reads:

\begin{displayquote}
Instead, our results suggest that, \st{holding the proportion of C/IE responding constant,} when there is significant C/IE responding, the false-positive rate for behavioral-symptom correlations will become increasingly inflated as the sample size increases.
\end{displayquote}

\textbf{P14 - the substantially greater perseveration shown by C/IE participants may indicate that they were pursuing a different strategy on the task which may have also been at play in their responses to questionnaires (e.g. ``straight-lining''), and may therefore form a distinct sub-population who could be studied more.}

We thank the reviewer for this interesting suggestion. We wish to clarify that C/IE participants do not appear to be more perseverative on average (Table S2). Instead, as the model-agnostic analyses (now moved to Appendix A) suggest, C/IE participants fail to maintain a reward-maximizing policy (e.g. stay with the previous choice following a reward).

\textbf{Discussion}

\textbf{P17 - the authors argue that the elevated rate of symptoms in their sample compared to epidemiological estimates is evidence that some of these participants are inattentive. However, the authors should acknowledge that depression and anxiety symptoms may be more enriched in those doing online research – those who participate in these studies are not chosen at random from the population, but self-select.}

We thank the reviewer for this important point. We have amended the discussion to note this:

\begin{displayquote}
Notwithstanding the above, one response to this legitimate concern is to take a graded approach to screening and excluding participants [41]. That is, participants could be screened with respect to a multitude of measures and only the consistently flagged participants be removed, thereby reducing the risk of inducing bias. Another possibility is to use sensitivity analysis as an alternative to exclusion, testing whether full-sample observed correlations are robust to the exclusion of participants flagged by measures of C/IE responding. We note that the strict screening approach used in the present study did not preclude us from identifying symptomatic participants or behavior-symptom correlations. Indeed, we found in our sample roughly 10\% of participants endorsing symptoms consistent with clinical levels of depression, and approximately 20\% consistent with clinical levels of acute anxiety. These estimates are within the realm of epidemiological norms [11, 30, 31]. \textit{(We should note, however, that some studies have found elevated rates of psychiatric symptomology in online participants even after controlling for C/IE responding [13].)}
\end{displayquote}

\textbf{Methods}

\textbf{P22 - it would be useful for the reader to have more information about the narrative search. It isn't clear what permutations of the search terms were used, or why a more systematic search wasn't performed. It is also unclear how the categories of different checks were determined.}

We thank the reviewer for this suggestion. We have added more detail concerning the methods of our literature review, specifically addressing why we could not perform a systematic review and where the full search terms and their permutations can be found. We have also clarified that the categories of different checks were determined based on previous taxonomies of screening methods (e.g. \cite{curran2016methods}).

\begin{displayquote}
To characterize common data screening practices in online computational psychiatry studies, we performed a narrative literature review [50]. We identified studies for inclusion through searches on Google Scholar using permutations of query terms related to online labour platforms (e.g. ``mechanical turk", ``prolific", ``online"), experimental paradigms (e.g. ``experiment", ``cognitive control", ``reinforcement learning"), and symptom measures (e.g. ``psychiatry", ``mental illness", ``depression"). \textit{We note that it was not feasible to conduct a systematic review, which requires the use of a publication database with reproducible search, because we required Google Scholar's full-text search in order to identify papers by recruitment method (e.g., Mechanical Turk).} We included in the review studies that (a) recruited participants online through a labour platform, (b) measured behavior on at least one experimental task, and (c) measured responses on at least one self-report symptom measure. Through this approach, we identified for inclusion 49 studies spanning 2015 through 2020. \textit{The complete list of studies, and search terms used to find them, are included in the Github repository for this study.}
\end{displayquote}

\begin{displayquote}
Two of the authors (S.Z., D.B.) then evaluated whether and how each of these studies performed data quality screening for both the collected task and self-report data. Specifically, we confirmed whether a study had performed a particular type of data screening,  \textit{with screening categories determined based on previous taxonomies of screening methods (e.g. [9]).} In addition, we assessed the total number of screening measures each study used and if and how monetary bonuses were paid to participants. This review was not meant to be systematic, but instead to provide a representative overview of common practices in online behavioral studies.
\end{displayquote}

\textbf{P22 - why is the N excluded for Prolific/mTurk participants who had done the study on the other platform not the same for each platform?}

The difference in numbers of excluded participants (i.e., MTurk: N=19; Prolific: N=1) reflects on which platform the participant admitted to having already completed the experiment. That is, N=19 MTurk participants admitted to completing the experiment twice (presumably after previously completing the experiment first on Prolific). We agree this demarcation is confusing and extraneous, and have thus removed it from the text.

\textbf{P22 - why did the authors not choose to select participants based on Prolific or mTurk scores? These should be reported in the paper. Do these scores correlate with C/IE responding?}

If by ``MTurk/Prolific scores'' the reviewer is referring to platform-specific metrics like HIT Approval Rate, we did not use these as inclusion criteria because previous research has found they are not discriminating between low- and high-quality participants \cite{robinson2019tapped}. This is noted in the methods under the ``Sample'' section:

\begin{displayquote}
Following recent recommendations, MTurk workers were not excluded based on work approval rate or number of previous jobs approved [53].
\end{displayquote}

Though we agree it would be interesting correlate these platform metrics with measures of C/IE responding, we are unable to do so with these data at this point. This is because our IRB requires us to discard the mapping between participants' platform IDs (i.e. MTurk worker ID, Prolific ID) and anonymized IDs after participants are paid. As such, we are presently unable to map participants' platform metrics to their anonymized data.

\textbf{P28 - it would be useful to add a subheading to clarify that the measures being described relate to the bandit task.}

We thank the reviewer for this helpful suggestion. We have added subheadings to better distinguish the self-report screening measures from the task-based screening measures.

\textbf{P28 - what the authors term ``choice variability'' does not seem to be a meaningful measure of inattentive responding on this task, as values close to either 1.00 (always choosing the same bandit) or 0.33 (always choosing a different bandit) could indicate inattention. The extent to which this is the case will of course vary depending on the precise reward history, which is why a computational approach is instructive. Equally, these extremes could be caused by low or high learning rates, and could even be adaptive.}

We thank the reviewer for this insightful point. We agree with the reviewer that, in principle, extreme values in either direction on this metric could indicate inattentive behavior. As such, one might wonder if we should have used a bidirectional coding of this variable; that is, recode the variable such that values of 0.33 and 1.00 in the native scale have the same resulting value. In practice, however, we found that such an approach actually \textit{reduces} the correlation between choice variability and the other screening measures (unidirectional: $\rho_\mu$ = 0.042; bidirectional: $\rho_\mu$ = 0.027), especially for the other task-based screening measures (unidirectional: $\rho_\mu$ = 0.097; bidirectional: $\rho_\mu$ = 0.045). This is likely because the vast majority of participants do not exhibit large choice perseveration (mean variability = 0.437, IQR = 0.381 -- 0.467). As such, we elected not to include this suggested analysis in the revised manuscript, so as not to bias the correspondence analyses in support of our arguments (that is, to avoid artificially reducing the correlation between task and self-report screening measures).

\printbibliography

\end{document}

### 2023-01-16 manuscripts/main.tex
last of dan's edits
latest drafts

@@
 \usepackage[font=small, labelfont=it]{caption}
-\usepackage{booktabs} % for pretty tables
+\usepackage{booktabs}
+\usepackage{xcolor,soul}
+
+% define highlight style
+% \colorlet{usercolorname}{yellow!00}    % use for public version
+\colorlet{usercolorname}{yellow!30}    % use for reviewer version
+\sethlcolor{usercolorname}
 
@@
 
-% specific images path relative to the main .tex file 
+% define highlight style
+% \colorlet{usercolorname}{yellow!00}    % use for public version
+\colorlet{usercolorname}{yellow!30}    % use for reviewer version
+\sethlcolor{usercolorname}
+
+% specify images path relative to the main .tex file 
 \graphicspath{ {./figures/} }
@@
 \author[1]{Samuel Zorowitz}
-\author[1,2]{Yael Niv}
-\author[1,3]{Daniel Bennett}
-\affil[1]{Princeton Neuroscience Institute, Princeton University, USA}
-\affil[2]{Department of Psychology, Princeton University, USA}
-\affil[3]{School of Psychological Sciences, Monash University, Australia}
+\author[2]{Johanne Solis}
+\author[1,3]{Yael Niv}
+\author[4]{Daniel Bennett}
+\affil[1]{Princeton Neuroscience Institute, Princeton University, NJ, USA}
+\affil[2]{Rutgers-Princeton Center for Computational Cognitive Neuropsychiatry, Rutgers University, NJ, USA}
+\affil[3]{Department of Psychology, Princeton University, NJ, USA}
+\affil[4]{School of Psychological Sciences, Monash University, Victoria, Australia}
 
@@
 In recent years, online labour markets (e.g.
-Amazon Mechanical Turk, Prolific, Cloudresearch) have become increasingly popular as a source of research participants in the behavioral sciences \cite{stewart2017crowdsourcing}, in no small part due to the ease with which these services allow for recruitment of large, diverse samples.
+Amazon Mechanical Turk, Prolific, CloudResearch) have become increasingly popular as a source of research participants in the behavioral sciences \cite{stewart2017crowdsourcing}, in no small part due to the ease with which these services allow for recruitment of large, diverse samples.
 The advantages of online data collection have also begun to be recognized in psychiatric research \cite{chandler2016conducting}, where this method offers several distinct advantages over traditional approaches to participant recruitment.
@@
 In this situation, the assumption that C/IE responding merely increases unsystematic measurement noise becomes untenable.
-Because of the positive skew in the ground-truth symptom distribution, participants who respond carelessly to the symptom survey are more likely to report higher levels of symptom endorsement relative to participants who complete the survey attentively \cite{chandler2020participant, ophir2020turker, king2018random}.
+Because of the positive skew in the ground-truth symptom distribution, participants who respond carelessly to the symptom survey are more likely to report higher levels of symptom endorsement relative to participants who complete the survey \hl{attentively} \cite{chandler2020participant, ophir2020turker, king2018random}.
 Consequently, unless C/IE survey responses are carefully identified and removed, a considerable proportion of putatively symptomatic individuals in an online sample may, in fact, be participants who have not engaged with the experiment with sufficient attention or effort.
@@
 We then asked whether behavioral screening alone was sufficient to identify participants engaging in C/IE responding on psychiatric symptom surveys.
-In two new datasets from two separate online labour marketplaces, we found that screening based on task behavior fails to completely identify participants engaging in C/IE responding on surveys.
+\hl{In two new datasets} from two separate online labour marketplaces, we found that screening based on task behavior fails to completely identify participants engaging in C/IE responding on surveys.
 Lastly, we investigated whether, under these circumstances, C/IE responding led to spurious correlations between symptom severity and task performance for positively-skewed symptom measures.
@@
 We hypothesise that spurious behavior-symptom correlations may emerge due to a mean-shift in the average level of symptom endorsement in participants engaging in C/IE responding relative to attentive participants.
-In turn, a mean-shift is expected to occur when the overall rate of symptom endorsement is low; that is, comparably higher scores are more likely for C/IE participants responding at random on a right skewed questionnaire.
-In line with our predictions, the average level of symptom endorsement was noticeably exaggerated in C/IE-responding participants for the symptom measures where symptom scores were most positively-skewed (7-up, 7-down, GAD-7; see Figure \ref{fig:distributions}).
+In turn, a mean-shift is expected to occur when the overall rate of symptom endorsement is low; \hl{that is, comparably higher scores are more likely for C/IE participants responding at random on a right skewed questionnaire.} In line with our predictions, the average level of symptom endorsement was noticeably exaggerated in C/IE-responding participants for the symptom measures where symptom scores were most positively-skewed (7-up, 7-down, GAD-7; see Figure \ref{fig:distributions}).
 In contrast, where there was higher rates of symptom endorsement overall, the distributions of symptom scores between the two groups of participants were less noticeably distinct.
@@
 We observed a credible difference between the average value of this intercept for the two groups ($\Delta \text{intercept} = 0.67, 95\% \ \text{HDI} = [-0.78, -0.55]$), such that C/IE participants were biased towards using the right-half of survey response options.
-This translates to a tendency to endorse \emph{more severe} symptoms on the 7-up/7-down and GAD-7 scales (where the rightmost options indicate greater frequency of symptoms) but \emph{less extreme} symptoms or personality traits on the SHAPS and BIS (where the rightmost options indicate lower frequency of symptoms or personality traits) despite these inventories measuring strongly correlated constructs (i.e.
+This translates to a tendency to endorse \emph{more severe} symptoms on the 7-up/7-down and GAD-7 scales (where the rightmost options indicate greater frequency of symptoms) but \emph{less extreme} symptoms or \hl{personality traits on the SHAPS and BIS (where the rightmost options indicate lower frequency of symptoms or personality traits)} despite these inventories measuring strongly correlated constructs (i.e.
 depression and anhedonia, anxiety and behavioral inhibition).
@@
 \caption{Absolute Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions.
-Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons; all signed correlations are shown in the Supplement).
+Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons; \hl{all signed correlations are shown in the Supplementary Figure} \ref{fig:correlations_s1}).
 Black Xs indicate significant correlations ablated under screening.
@@
 Across all analyses, we measured the correlation and between the 7-down depression scale and learning-rate asymmetry ($\kappa$), which we previously identified as likely exhibiting a spurious association.
-(The following results are not specific to learning-rate asymmetry and generalize to other pairs of variables; Figure \ref{fig:bootstrap_s1}).
+(\hl{The following results are not specific to learning-rate asymmetry and generalize to other pairs of variables; Figure} \ref{fig:bootstrap_s1}).
 
@@
 Although this assumption is correct for unsystematic measurement error, it no longer holds in the regime of systematic measurement error (where larger sample sizes reduce the variance of estimates, but do not alter their bias).
-Instead, our results suggest that, except for low rates of C/IE responding, the false-positive rate for behavioral-symptom correlations will become increasingly inflated as the sample size increases.
+Instead, our results suggest that, \hl{except for low rates of C/IE responding}, the false-positive rate for behavioral-symptom correlations will become increasingly inflated as the sample size increases.
 
@@
 
-\subsection{Pattern of results generalizes to alternative tasks, self-report measures, and quality assurance protocols}
-
-One possible concern with the results presented so far is that they are specific to one specific instantiation of our experimental design.
-For example, with more stringent quality assurance protocols during participant recruitment, or perhaps a different task or set of self-report measures, one might wonder if spurious correlations would remain such a threat.
-
-To evaluate the generalizability of our findings, we therefore conducted a conceptual replication experiment in which an independent sample of N=393 participants (N=193 from MTurk, N=200 from Prolific) completed a more difficult cognitive task, the two-step task \cite{daw2011model}, and an alternate set of self-report measures (see Appendix B for complete details).
+\subsection{\texorpdfstring{\hl{Pattern of results generalizes to alternative tasks, self-report measures, and quality assurance protocols}}{}}
+
+One possible concern with the results presented so far is that they are specific to one instantiation of our experimental design.
+With more stringent quality assurance protocols during participant recruitment, or perhaps a different task or set of self-report measures, one might wonder if spurious correlations would remain such a threat.
+
+To evaluate the generalizability of our findings, we therefore conducted a conceptual replication experiment in which an independent sample of N=393 participants (N=193 from MTurk using CloudResearch, N=200 from Prolific) completed a more difficult cognitive task, the well-known ``two-step task'' \cite{daw2011model}, and an alternate set of self-report measures (see Appendix B for details).
 Importantly, participants were recruited \textit{after} CloudResearch and Prolific implemented new protocols to improve data quality on their respective platforms.
-Moreover, participants completed self-report symptom measures as before, but also personality measures with no hypothesized relationship to model-based planning behavior on the two-step task.
-
-For the sake of brevity, only the main pattern of finding are reported here (the complete results are reported in Appendix B).
+As a final control measure, participants completed self-report symptom measures as before, but also personality measures with no hypothesized relationship to model-based planning behavior on the two-step task.
+
+For the sake of brevity, we report here only the main pattern of findings (all results are reported in Appendix B).
 In the replication sample, 55 out of 393 participants (14\%) endorsed a logically invalid or improbable response on one or more of the infrequency items when completing the self-report measures.
-This is roughly two-thirds of the number of participants who were flagged for C/IE responding in the original study, suggesting that the newer quality assurance protocols are at least partially effective.
-In the self-report symptom measures, we replicated the finding that total scores were noticeably exaggerated in participants suspected of C/IE responding only for the symptom measures where overall rates of symptom endorsement were the lowest.
-Similarly, we again found that task and self-report screening measures showed low correspondence; that is, excluding participants on the basis of poor behavioral performance was ineffective for identifying and removing participants who engaged in C/IE responding on self-report surveys.
-Finally, with no exclusions applied, we observed spurious correlations between performance on the two-step task and total scores, only for the self-report measures (both symptom and personality measures) with a mean-shift in scores between attentive participants and participants suspected of C/IE responding.
+This is roughly two-thirds of the number of participants who were flagged for C/IE responding in the original study, suggesting that the newer quality assurance protocols used by the online platforms are at least partially effective.
+
+In the self-report symptom measures, we replicated the finding that total scores were noticeably exaggerated in participants suspected of C/IE responding, but only for symptom measures where overall rates of symptom endorsement were the lowest (i.e., measures that have normative endorsements skewed towards 0).
+Similarly, we again found that task-based screening and self-report screening measures showed low correspondence; that is, excluding participants on the basis of poor behavioral performance would not have identified and removed participants who engaged in C/IE responding on self-report surveys.
+
+Finally, when we did not apply any exclusions, we observed spurious correlations between performance on the two-step task and total scores for both symptom and personality self-report measures with a mean-shift in scores between attentive participants and participants suspected of C/IE responding.
 In contrast with our original findings, however, we found that excluding participants based on self-report \textit{or} task screening measures was sufficient to ablate these spurious correlations.
 
-In sum, we replicated most of the main findings from the original study in an independent sample of participants completing a novel set of tasks and self-report measures.
+In sum, we replicated most of the main findings from the original study in an independent sample of participants completing a different task and other self-report measures.
 Although we found that screening on task behavior was sufficient to protect against spurious correlations in the replication sample, it is difficult to generalize and predict when or why this might be the case for other datasets.
-As such, screening for C/IE responding in both task and self-report measures still remains the best approach to protect oneself against the possibility of spurious correlations.
-
-\subsection{Individuals with and without diagnosed psychiatric disorders fail attention checks at similar rates}
+As such, we still believe that screening for C/IE responding in both task and self-report measures is the best approach to protect oneself against the possibility of spurious correlations.
+
+\subsection{\texorpdfstring{\hl{Individuals with and without diagnosed psychiatric disorders fail attention checks at similar rates}}{}}
 
@@
 However, to the extent that C/IE responding reflects lack of motivation \cite{barch2015mechanisms}, avoidance of effort \cite{cohen2001impairments, culbreth2016negative}, or more frequent lapses of attention \cite{kane2016individual, robison2017neurotic}, one might hypothesise a true underlying association between psychopathology and careless responding in online studies.
-In such cases, it is plausible that rigorous screening of C/IE responding might lead to the differential exclusion of truly symptomatic participants.
-
-To explore this possibility, we embedded attention checks into the self-report measures of two studies of patients with major depressive disorder (see Appendix C for complete details).
-Specifically, a total of N=45 psychiatric patients and N=20 healthy controls completed a series of self-report symptom measures, online, on their computers from the comfort of their homes.
-(The psychiatric patients were confirmed to meet criteria for a diagnosis of major depressive disorder through a structured clinical interview.) In total, 16 of 65 (24.6\%) participants failed one or more attention checks.
+It is thus plausible that rigorous screening of C/IE responding might lead to the differential exclusion of truly symptomatic participants.
+
+To explore this possibility, we embedded attention checks into the self-report measures of two studies of patients with major depressive disorder (see Appendix C for details).
+Specifically, N=45 psychiatric patients (confirmed to meet criteria for a diagnosis of major depressive disorder through a structured clinical interview) and N=20 healthy controls, all recruited through the Rutgers-Princeton Center for Computational Cognitive NeuroPsychiatry (i.e., personal recruitment, not on online platforms), completed a series of self-report symptom measures, online, on their computers from the comfort of their homes.
+In total, 16 of 65 (24.6\%) participants failed one or more attention checks.
 Subdivided by group, 6 of 20 (30\%) healthy participants and 10 of 45 (22\%) psychiatric participants were flagged for C/IE responding.
@@
 Using these data, we computed pairwise Bayes factors comparing three candidate models: attention check failure rates are equal between healthy and psychiatric participants (M1); failure rates are greater in psychiatric patients (M2); and failure rates are greater in healthy participants (M3).
-A model assuming equal rates of failure between healthy and psychiatric participants was 2.88 times more likely than the model assuming greater rates for psychiatric patients.
-In turn, a model assuming lower rates of failure for psychiatric patients was 1.27 times more likely than the model assuming equal rates.
-Finally, a model assuming lower rates of failure for psychiatric patients was 3.65 times more likely than the model assuming higher rates for psychiatric patients.
+The model assuming equal rates of failure between healthy and psychiatric participants was 2.88 times more likely than the model assuming greater rates for psychiatric patients.
+In turn, the model assuming lower rates of failure for psychiatric patients was 1.27 times more likely than the model assuming equal rates.
+Finally, the model assuming lower rates of failure for psychiatric patients was 3.65 times more likely than the model assuming higher rates for psychiatric patients.
 Only the final comparison exceeds the cutoff value of 3, which is conventionally treated as the minimal amount of evidence required to treat a difference in model fit as meaningful.
-Though the small sample precludes any definitive conclusion, it is noteworthy that the model least consistent with the data is the one where psychiatric patients are more likely to fail infrequency item attention checks.
-These data suggest that it is unlikely that participants flagged for C/IE responding in the main analyses were disproportionately individuals with high psychiatric symptom severity.
-Accordingly, we conclude that our results are unlikely to be overly influenced by an overcontrol bias.
+Although the size of the sample precludes any definitive conclusion, it is noteworthy that the model least consistent with the data was the one where psychiatric patients are more likely to fail infrequency item attention checks.
+These data suggest, therefore, that it is unlikely that individuals with high psychiatric symptom severity were disproportionately flagged for C/IE responding in the main analyses.
+Accordingly, we conclude that the screening measures we are suggesting are not likely to result in overcontrol bias and false-negative correlations between tasks and symptom measures.
 
@@
 A less careful pattern of responding on tasks used to measure cognitive constructs can then masquerade as a correlation between alteration in these constructs and symptom dimensions.
-We found empirical evidence for this pernicious pattern in participants recruited from two popular online labour platforms.
+We found repeated evidence for this pernicious pattern in participants recruited from two popular online labour platforms.
 False-positive rates for these spurious correlations \emph{increased} with sample size, because the correlations are due to measurement bias, not measurement noise.
@@
 Viewed from the perspective of effort expenditure, our results suggest that participants appraised the cost/benefit trade-off differently for behavioral tasks and self-report surveys.
-Specifically, we found that only 7\% of participants were at chance-level performance in our task, compared to more than 22\% of participants who failed one or more attention-check items in the self-report surveys.
+Specifically, we found that only 7\% of participants were at chance-level performance in our task, compared to more than 22\% of participants who failed one or more attention-check items in the self-report surveys \hl{(a finding that replicated in a second study involving a different task)}.
 Moreover, different measures of C/IE responding were weakly or not at all correlated between task behavior and self-report responses.
@@
 low motivation, effort avoidance, inattentiveness), rigorous screening of C/IE responding might lead to the differential exclusion of truly symptomatic participants.
-To explore this possibility, we embedded attention checks into the self-report measures of two studies of patients with major depressive disorder.
+\hl{To explore this possibility, we embedded attention checks into the self-report measures of two studies of patients with major depressive disorder.
 Though our final sample was small, we did not find evidence for the proposition that patients were more likely to fail attention checks than healthy controls (if anything, non-psychiatric participants were more likely to be flagged by C/IE screening).
-These results provide preliminary evidence that rigorous C/IE screening is unlikely to result in overcontrol bias.
-
-Given that the results of our patient study are preliminary and warrant further investigation, researchers might still be wary of possible overcontrol bias.
-However, when using self-report questionnaires for screening, for overcontrol to seriously impact results it would have to be the case that symptomatic participants frequently endorse improbable or impossible responses to infrequency-item checks (e.g., responding `Agree' to ``I competed in the 1917 Olympic Games").
+These results provide preliminary evidence that rigorous C/IE screening is unlikely to result in overcontrol bias.}
+
+\hl{Given that the results of our patient study are preliminary and warrant further investigation, researchers might still be wary of possible overcontrol bias.} However, when using self-report questionnaires for screening, for overcontrol to seriously impact results it would have to be the case that symptomatic participants frequently endorse improbable or impossible responses to infrequency-item checks (e.g., responding `Agree' to ``I competed in the 1917 Olympic Games").
 In this case, and even if such participants truly are experiencing severe symptoms of motivation or attention, there is likely to be limited utility in measuring these symptoms using a self-report measure that they are unable to complete veridically.
@@
 These estimates are within the realm of epidemiological norms \cite{kessler2012twelve, lowe2008validation, yarrington2021impact}.
-(We should note, however, that some studies have found elevated rates of psychiatric symptomology in online participants even after controlling for C/IE responding \cite{ophir2020turker}.) We also observed some positive correlations between anxiety and choice behavior that were consistent with effects found in previous literature \cite{huang2017computational, harle2017anhedonia, garrett2018updating}.
+\hl{(We should note, however, that some studies have found elevated rates of psychiatric symptomology in online participants even after controlling for C/IE responding} \cite{ophir2020turker}.) We also observed some positive correlations between anxiety and choice behavior that were consistent with effects found in previous literature \cite{huang2017computational, harle2017anhedonia, garrett2018updating}.
 For example, we found higher lose-shift rates and higher learning rates following negative prediction errors correlated with self-reported anxiety.
@@
 Thus, we cannot be confident that all of the flagged participants were indeed engaging in C/IE responding; similarly, we cannot be certain that we correctly excluded all participants engaged in C/IE responding.
-We studied behavior-symptom correlations for only one task and a small self-report symptom battery.
+We studied behavior-symptom correlations for only two tasks and a small self-report symptom batteries.
 It remains to be seen how generalizable our findings are, although our study design was inspired by experiments prevalent in the online computational psychiatry literature.
@@
     \item When collecting self-report questionnaire data, include attention-check items that flag participants who may be engaging in C/IE responding.
-We recommend following best-practice guidelines in using infrequency-item checks rather than instructed-item checks, as multiple studies have now shown that online participants are habituated to and circumvent the latter  \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}.
+We recommend following best-practice guidelines in using infrequency-item checks rather than instructed-item checks, \hl{as multiple studies have now shown that online participants are habituated to and circumvent the latter} \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}.
 Participants flagged by suspicious responses on attention-check items should either be excluded from further analysis, or assessed using sensitivity analyses to ensure that observed full-sample correlations are robust to their exclusion.
@@
 ``psychiatry", ``mental illness", ``depression").
-We note that it was not feasible to conduct a systematic review, which would require using a publication database other than Google Scholar (i.e.
-this is because search results from Google Scholar are tailored to individual users and are therefore by definition unsystematic and unreproducible).
-Our science librarian nevertheless recommended we use Google Scholar because it performs full-text search, which was necessary here to identify papers; that is, recruitment methods (e.g.
-``Mechanical Turk'') are infrequently reported in the title or abstract of a paper.
-We included studies that (a) recruited participants online through a labour platform, (b) measured behavior on at least one experimental task, and (c) measured responses on at least one self-report symptom measure.
+\hl{We note that it was not feasible to conduct a systematic review, which requires the use of a publication database with reproducible search, because we required Google Scholar's full-text search in order to identify papers by recruitment method (e.g., Mechanical Turk).} We included in the review studies that (a) recruited participants online through a labour platform, (b) measured behavior on at least one experimental task, and (c) measured responses on at least one self-report symptom measure.
 Through this approach, we identified for inclusion 49 studies spanning 2015 through 2020.
@@
 Two of the authors (S.Z., D.B.) then evaluated whether and how each of these studies performed data quality screening for both the collected task and self-report data.
-Specifically, we confirmed whether a study had performed a particular type of data screening.
-The categories were determined based on previous taxonomies of screening methods (e.g.
+Specifically, we confirmed whether a study had performed a particular type of data screening, \hl{with screening categories determined based on previous taxonomies of screening methods} (e.g.
 \cite{curran2016methods}).
-In addition, we assessed the total number of screening measures each study used and how monetary bonuses were paid to participants (if at all).
-We note that this review was not meant to be systematic, but instead to provide a representative overview of common practices in online behavioral studies.
+In addition, we assessed the total number of screening measures each study used and if monetary bonuses were paid to participants.
+This review was not meant to be systematic, but instead to provide a representative overview of common practices in online behavioral studies.
 
@@
 No other exclusion criteria were applied during recruitment.
-It is important to note that both CloudResearch and Prolific internally use a number of tools (e.g.
+\hl{It is important to note that both CloudResearch and Prolific use a number of tools (e.g.
 IP-address screening) to filter out the lowest quality participants.
-In addition, our custom experiment delivery software (NivTurk; see below) has bot-checking functionality built into it.
-We are confident that our study is not strongly affected by participants using software to automatically complete the experiment.
+In addition, our custom experiment delivery software (NivTurk; see below) has bot-checking functionality built into it, and rejects from the start participants who are likely to not be human.
+We are therefore confident that our study is not strongly affected by participants using software to automatically complete the experiment.}
 
@@
 
-Prior to completing the reversal learning task, participants completed five self-report symptom and personality-trait measures.
+Prior to completing the reversal learning task, participants completed five self-report symptom \hl{and personality-trait measures}.
 The symptom measures were selected for inclusion based on their frequency in clinical research, and for having an expected mixture of symmetric and asymmetric score distributions.
 
-\textbf{Seven-Up/Seven-Down}: The Seven-Up/Seven-Down (7u/7d; \cite{youngstrom_2013_susd}) scale is a 14-item measure of lifetime propensity towards depressive and hypomanic symptoms.
+\textbf{Seven-Up/Seven-Down.} The Seven-Up/Seven-Down (7u/7d; \cite{youngstrom_2013_susd}) scale is a 14-item measure of lifetime propensity towards depressive and hypomanic symptoms.
 It is an abbreviation of the General Behavior Inventory \cite{depue1981behavioral}, wherein only items that maximally discriminated between depression and mania were included.
@@
 
-\textbf{Generalized Anxiety Disorder-7}: the Generalized Anxiety Disorder-7 (GAD-7; \cite{spitzer2006brief}) is a 7-item measure of general anxiety.
+\textbf{Generalized Anxiety Disorder-7.} the Generalized Anxiety Disorder-7 (GAD-7; \cite{spitzer2006brief}) is a 7-item measure of general anxiety.
 The GAD-7 assesses how much a respondent has been bothered by each of seven core anxiety symptoms over the last 2 weeks.
@@
 
-\textbf{Behavioral Inhibition/Behavioral Activation Scales}: the Behavioral Inhibition and Behavioral Activation Scales (BIS/BAS; \cite{carver1994behavioral}) are a measure of reward and punishment sensitivity.
+\textbf{Behavioral Inhibition/Behavioral Activation Scales.} the Behavioral Inhibition and Behavioral Activation Scales (BIS/BAS; \cite{carver1994behavioral}) are a measure of reward and punishment sensitivity.
 The original 42-item measure was recently abbreviated to a 14-item measure \cite{pagliaccio2016revising}, which we use here.
@@
 
-\textbf{Snaith-Hamilton Pleasure Scale}: the Snaith-Hamilton Pleasure Scale is a 14-item measure of anhedonia \cite{snaith1995scale}.
+\textbf{Snaith-Hamilton Pleasure Scale.} the Snaith-Hamilton Pleasure Scale is a 14-item measure of anhedonia \cite{snaith1995scale}.
 Items are scored on a 4-point scale from 0 (``strongly agree") to 3 (``strongly disagree"), where higher scores indicate greater pathology.
@@
 
-\textbf{Penn State Worry Questionnaire}: the Penn State Worry Questionnaire is a measure of worry symptoms \cite{meyer1990development}.
+\textbf{Penn State Worry Questionnaire.} the Penn State Worry Questionnaire is a measure of worry symptoms \cite{meyer1990development}.
 The original 16-item was recently abbreviated to a 3-item measure \cite{kertz2014psychometric}, which we use here.
@@
 
-\subparagraph{Cronbach's $\alpha$} We compared the average Cronbach's $\alpha$, a measure of internal consistency, between attentive and C/IE participants.
+\subparagraph{Cronbach's $\alpha$.} We compared the average Cronbach's $\alpha$, a measure of internal consistency, between attentive and C/IE participants.
 To control for the unbalanced numbers of participants in these groups, we performed a permutation test.
@@
 
-\subparagraph{Random intercept item factor analysis} We employed random intercept item factor analysis \cite{maydeu2006random} to detect heuristic patterns of responding.
+\subparagraph{Random intercept item factor analysis.} We employed random intercept item factor analysis \cite{maydeu2006random} to detect heuristic patterns of responding.
 In the model, the probability of observing response level $k$ (of $K$ total levels) from participant $i$ on item $j$ is defined as:
@@
 
-\subparagraph{Clinical cutoffs} We compared the proportion of participants in our sample reaching the threshold for clinical symptomology before and after applying exclusions.
+\subparagraph{Clinical cutoffs.} We compared the proportion of participants in our sample reaching the threshold for clinical symptomology before and after applying exclusions.
 For the GAD-7, previous research has suggested a clinical cutoff score of 10 or higher \cite{lowe2008validation, hinz2017psychometric}.
@@
 
-\subparagraph{Infrequency items}
-
-Infrequency items are questions for which all or virtually all attentive participants should provide the same response.
+\subparagraph{Self-report screening measure: Infrequency items.} Infrequency items are questions for which all or virtually all attentive participants should provide the same response.
 We embedded four infrequency items across the self-report measures.
@@
 \begin{enumerate}
-  \item Over the last two weeks, how much time did you spend worrying about the 1977 Olympics? 
-  \item Have there been times of a couple days or more when you were able to stop breathing entirely (without the aid of medical equipment)?
-  \item I would feel bad if a loved one unexpectedly died.
-  \item I would be able to lift a 1 lb (0.5 kg) weight.
+  \item Over the last two weeks, how much time did you spend worrying about the 1977 Olympics? \hl{(Expected response: \textit{Not at all})}
+  \item Have there been times of a couple days or more when you were able to stop breathing entirely (without the aid of medical equipment)? \hl{(Expected response: \textit{Never or hardly ever})}
+  \item I would feel bad if a loved one unexpectedly died. \hl{(Expected response: \textit{Somewhat true for me} or \textit{Very true for me})}
+  \item I would be able to lift a 1 lb (0.5 kg) weight. \hl{(Expected response: \textit{Agree} or \textit{Strongly agree})}
 \end{enumerate}
@@
 
-\subparagraph{Inter-item standard deviation} The inter-item standard deviation (ISD) is an estimate of a participant's response consistency on a self-report measure \cite{marjanovic2015inter}, defined as:
+\subparagraph{Self-report screening measure: Inter-item standard deviation.} The inter-item standard deviation (ISD) is an estimate of a participant's response consistency on a self-report measure \cite{marjanovic2015inter}, defined as:
 
@@
 
-\subparagraph{Personal reliability}
-
-The personal reliability coefficient is an estimate of a participant's response consistency on a self-report measure, estimated by correlating the average scores from split-halves of their responses.
+\subparagraph{Self-report screening measure: Personal reliability.} The personal reliability coefficient is an estimate of a participant's response consistency on a self-report measure, estimated by correlating the average scores from split-halves of their responses.
 To avoid any item-order bias, a participant's personal reliability coefficient for a particular self-report measure was computed from the average correlation from 1000 random split-halves.
@@
 Smaller reliability coefficients indicate lower response consistency.
-\subparagraph{Mahalanobis D} The Mahalanobis distance is a multivariate outlier detection measure, which estimates how dissimilar a participant is relative to all others.
+
+\subparagraph{Self-report screening measure: Mahalanobis D.} The Mahalanobis distance is a multivariate outlier detection measure, which estimates how dissimilar a participant is relative to all others.
 For a participant $i$, the Mahalanobis D is defined as:
@@
 
-\subparagraph{Reading Time} The reading time is the total number of seconds spent filling out a particular self-report measure, adjusted for that measure's total number of items \cite{ophir2020turker}.
+\subparagraph{Self-report screening measure: Reading time.} The reading time is the total number of seconds spent filling out a particular self-report measure, adjusted for that measure's total number of items \cite{ophir2020turker}.
 A total reading time estimate was estimated for each participant by summing across the adjusted time for each of the seven self-report measures.
@@
 
-\subparagraph{Task-based screening variables}
-
-\subparagraph{Variability} Choice variability was defined as the fraction of trials of the most used response option per participant.
+\subparagraph{Task-based screening variable: Choice variability.} Choice variability was defined as the fraction of trials of the most used response option per participant.
 Choice variability could range from 0.33 (all response options used equally) to 1.00 (only one response option used).
@@
 
-\subparagraph{Accuracy} Choice accuracy was defined as the fraction of choices of the reward-maximizing response option.
+\subparagraph{Task-based screening variable: Choice accuracy.} Choice accuracy was defined as the fraction of choices of the reward-maximizing response option.
 For a task with 90 trials and three response options, a one-tailed binomial test at $\alpha=0.05$ reveals chance-level performance to be 37 or fewer correct choices (41\%).
@@
 
-\subparagraph{Win-Stay Lose-Shift} Win-stay lose-shift (WSLS) measures a participant's tendency to stay with a choice option following a reward versus shifting to a new choice option following a non-reward.
+\subparagraph{Task-based screening variable: Win-Stay Lose-Shift.} Win-stay lose-shift (WSLS) measures a participant's tendency to stay with a choice option following a reward versus shifting to a new choice option following a non-reward.
 WSLS thus measures a participant's sensitivity to reward feedback on the screen.
@@
 
-\subparagraph{Response Times} Suspicious response time was defined as the proportion of trials with an outlier response time, here measured as responses faster than 200ms.
+\subparagraph{Task-based screening variable: Response times.} ``Suspicious response time'' was defined as the proportion of trials with an outlier response time, here measured as responses faster than 200ms.
 Greater proportions of outlier response times are indicative of more careless responding during the task.
 
-\subparagraph{Correspondence Analysis} We measured the correspondence of the above screening measures via two complimentary approaches.
+\subparagraph{Correspondence Analysis.} We measured the correspondence of the above screening measures via two complimentary approaches.
 First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation.
@@
 
-\subparagraph{Descriptive measures} Descriptive task measures included the following: accuracy (the fraction of choices of the reward-maximizing response option), points (the total number of points accumulated over the game), win-stay rates (the fraction of trials on which a participant repeated the previous trial's choice following a reward outcome), lose-shift rates (the fraction of trials on which a participant deviated from the previous trial's choice following a non-reward outcome), and perseveration (the number of trials on which a participant continued to choose the previously dominant response option following a reversal in task contingencies).
-
-\subparagraph{Model-based measures} The model-based measures were derived from a common reinforcement learning model of choice behavior, the risk-sensitive temporal difference learning model \cite{niv2012neural}.
+\subparagraph{Descriptive measures.} Descriptive task measures included the following: accuracy (the fraction of choices of the reward-maximizing response option), points (the total number of points accumulated over the game), win-stay rates (the fraction of trials on which a participant repeated the previous trial's choice following a reward outcome), lose-shift rates (the fraction of trials on which a participant deviated from the previous trial's choice following a non-reward outcome), and perseveration (the number of trials on which a participant continued to choose the previously dominant response option following a reversal in task contingencies).
+
+\subparagraph{Model-based measures.} The model-based measures were derived from a common reinforcement learning model of choice behavior, the risk-sensitive temporal difference learning model \cite{niv2012neural}.
 In this model, the expected value of a choice option, $Q(s)$, is learned through cycle of choice and reward feedback.
@@
 
-\subparagraph{Correlation analysis} Behavior-symptom correlations (after various forms of screening and exclusion) were estimated using Spearman's rank correlation.
+\subparagraph{Correlation analysis.} Behavior-symptom correlations (after various forms of screening and exclusion) were estimated using Spearman's rank correlation.
 Significance testing was performed using the percentile bootstrap method \cite{wilcox2018guide} so as to avoid making any parametric assumptions.
@@
 
-\subsection*{Signed correlation analysis}
+\subsection*{\texorpdfstring{\hl{Signed correlation analysis}{}}}
 
@@
 
-\subsection*{The relationship between sample size and false positive rates generalize to other sets of variables}
+\subsection*{\texorpdfstring{\hl{The relationship between sample size and false positive rates generalize to other sets of variables}{}}}
 
@@
 
-\subsection*{The relationship between sample size and true positive rates for true correlations}
+\subsection*{\texorpdfstring{\hl{The relationship between sample size and true positive rates for true correlations}{}}}
 
@@
 
-\subsection*{Careless participants show different behaviors on the reversal learning task}
+\subsection*{\texorpdfstring{\hl{Careless participants show different behaviors on the reversal learning task}{}}}
 
@@
 \break
-\section*{Appendix B: Replication study}
+
+\section*{\texorpdfstring{\hl{Appendix B: Replication study}{}}}
 
@@
 The motivations for conducting a replication study were threefold.
-First, we wanted to examine the generalizability of our findings under new labor platform conditions.
-Since summer 2020, when the original data were collected, online labor markets like Mechanical Turk/Cloudresearch and Prolific Academic have undergone important changes.
-To address rampant data quality issues on Mechanical Turk, Cloudresearch introduced their ``Approved Participants'' filter.
+First, we wanted to examine the generalizability of our findings under new labor-platform conditions.
+Since summer 2020, when the original data were collected, online labor markets like Mechanical Turk/CloudResearch and Prolific Academic have undergone important changes.
+To address rampant data quality issues on Mechanical Turk, CloudResearch introduced their ``Approved Participants'' filter.
 When selected, only Mechanical Turk participants with a prior history of attentive and careful work are invited to participate in experiments \cite{cloudresearch_2020-2, hauser2021evaluating}.
@@
 In the wake of these changes, we wanted to explore the relevance of our original findings.
-Specifically, with these new safeguards, we wanted to examine whether the chance of spurious correlations has been seriously lessened.
+Specifically, with these new safeguards, we wanted to examine whether the chance of spurious correlations has been considerably reduced.
 
@@
 Our motivation then was to demonstrate the risk of spurious correlations even for experiments where the possibility of participant fatigue (and consequently C/IE responding) had been minimized.
-One consequence of this design, however, was that the majority of participants performed reasonably well on the task (i.e.
-only 26 participants, or 7\% of the sample, exhibited choice accuracy at or below statistically chance levels).
-This fact may in part explain why we observed such low correspondence between self-report and task-based screening measures.
+One consequence of this design, however, was that the majority of participants performed reasonably well on the task (only 26 participants, or 7\% of the sample, exhibited choice accuracy at or below chance levels).
+This could in part explain why we observed such low correspondence between self-report and task-based screening measures.
 As such, we wanted to repeat our experiment and analyses using a more difficult task.
-Therefore, in the replication study we used the two-step task \cite{daw2011model}, which is both more challenging and lengthy than our original reversal-learning task.
+Therefore, in the replication study we used the two-step task \cite{daw2011model}, which is both more challenging and takes longer than our original reversal-learning task.
 
 Finally, we wanted to examine the generalizability of our findings to other self-report measures.
-In the original study, we found that, all else being equal, self-report symptom measures with low rates of endorsement were more likely to yield spurious correlations with behavior in the presence of C/IE responding.
-This effect should not be limited to symptom measures, however, and should extend to any self-report measure with an expected skewed or asymmetric score distribution.
-Therefore, in the current replication study, we use two sets of self-report scales: one set of psychiatric symptom measures and one set of personality measures.
-As before, both sets include scales whose score distributions are expected to be symmetric or asymmetric (skewed).
-Crucially, the two personality scales measure constructs (i.e.
-artistic interests, greed avoidance) that should have no meaningful relationship with model-based choice behavior on the two-step task.
+In the original study, we found that self-report symptom measures with low rates of endorsement were more likely to yield spurious correlations with behavior in the presence of C/IE responding, as C/IE participants were more likely to endorse symptoms, as well as to perform poorly on the task.
+In principle, this effect should not be limited to symptom measures, and should extend to any self-report measure with an expected skewed or asymmetric score distribution.
+Therefore, in the current replication study, we used two sets of self-report scales: one set of psychiatric symptom measures and one set of personality measures.
+As before, each set includes scales whose score distributions are expected to be symmetric as well as scales with asymmetric (skewed) score distributions.
+Crucially, the two personality scales we chose, artistic interests and greed avoidance, measure constructs that should have no meaningful relationship with model-based choice behavior on the two-step task.
 Therefore, the personality measures serve as a stronger test of our hypothesis that spurious correlations between self-report and behavioral measures are more likely for skewed score distributions.
@@
 Specifically, 200 participants were recruited from Amazon Mechanical Turk (MTurk) and 200 participants were recruited from Prolific.
-This study was approved by the Institutional Review Board of Princeton University (\#11968), and all participants provided informed consent.
-Total study duration was approximately 20 minutes per participant.
+The study was approved by the Institutional Review Board of Princeton University (\#11968), and all participants provided informed consent.
+Total study duration was approximately 20 minutes.
 Participants received monetary compensation for their time (rate USD \$12/hr), plus an incentive-compatible bonus up to \$1.00 based on task performance.
@@
 
-The data from N=7 participants who completed the experiment were excluded prior to analysis.
-These participants (all from MTurk) disclosed that they had also completed the experiment on the other platform were excluded.
+Data from N=7 participants who completed the experiment were excluded prior to analysis because these participants (all from MTurk) disclosed that they had also completed the same experiment on the other platform.
 This left a final sample of N=393 participants (MTurk: N=193, Prolific: N=200) for analysis.
 The demographics of the sample split by labour market is provided in Table \ref{tab:demographics_02}.
-The participants recruited from MTurk were older on average ($M = 4.9 \ \text{yrs}, t = 4.248, p < 0.001$) and comprised of fewer women ($z = 4.248, p < 0.001$).
+Participants recruited from MTurk were older on average ($\Delta M = 4.9 \ \text{yrs}, t = 4.248, p < 0.001$) and comprised of fewer women (35.2\% versus 61\%, $z = 4.248, p < 0.001$).
 
@@
 Participants completed a gamified version of the two-step task \cite{daw2011model} designed to dissociate ``model-free'' and ``model-based'' decision-making.
-On every trial of the task, participants were presented with two choice options that led probabilistically to either of two second-stage ``states''.
-From there, participants made an additional choice between two options that were associated with a unique probability of returning either a reward (1 point) or a non-reward (0 points).
-Crucially, each first-stage choice option led mostly (70\% of the time) to one of the two second-stage states; this probability was fixed throughout the experiment.
-The probabilities of reward for each of the four second-stage options changed slowly and independently, according to Gaussian random walks.
+On every trial of the task, participants' goal is to collect as much ``space treasure'' as possible by traveling to one of two different planets and ``trading'' with one of two aliens who live on that planet.
+Participants first chose between two different-colored rocket ships (first-stage choice).
+Each rocket ship had a 70\% chance of traveling to one particular planet (e.g., the green rocket ship to the blue planet and the purple rocket ship to the red planet; common transitions) and a 30\% chance of traveling to the other planet (uncommon transition).
+The rocket ship and planet colors were randomized across participants, as were the mappings between rocket ships and planets.
+On each planet, participants chose which of two aliens to ``trade'' with (second-stage choice).
+If chosen, an alien would give the participant ``treasure'' with some slowly-changing probability, otherwise it would give ``junk''.
+The reward probabilities for each alien and trial were generated according to independent Gaussian random walks.
 Participants completed 201 trials of the task, with an optional break after the first half.
 
-As a cover story, the two-step task was introduced to participants as a ``space treasure'' game \cite{decker2016creatures}.
-In the game, participants made choices between two different colored rocket ships (first stage choice) that probabilistically took them to one of two planets.
-On each planet, there were two alien creatures to ``trade'' with.
-If chosen as a trading partner, an alien would either give ``treasure'' (1 point) or ``junk'' (0 points).
-Participants were told their goal was to collect as much treasure as possible.
-Participants were informed that the rocket ships mostly traveled to one planet, but sometimes went to the other.
-Participants were also instructed that the chance an alien would give them treasure would change slowly over the course of the task.
-Prior to beginning the experiment, participants had to correctly answer three sets of comprehension questions about the instructions.
-Failing to correctly answer all items forced the participant to start a section of the instructions over.
+Prior to the beginning of the experiment, participants had to read a set of instructions in which they were told that the rocket ships mostly traveled to one planet, but sometimes went to the other, and that the chance an alien would give them treasure would change slowly over the course of the task.
+Before they could start the task, participants had to correctly answer three sets of comprehension questions about the instructions.
+Failing to correctly answer all items forced the participant to reread a section of the instructions.
+Participants were permitted up to ten retries of the comprehension questions before they were removed from the experiment; however, no participant exceeded this limit.
 
@@
 
-Prior to the start of the two-step task, participants completed four self-report measures (in a randomized order).
-The first was the 14-item seven-up/seven-down scale (7u/7d; \cite{youngstrom_2013_susd-2}), which measures lifetime incidence of depressive and (hypo)mania symptoms.
-These scales are expected to elicit lower rates of symptom endorsement, thereby resulting in asymmetric (right-skewed) score distributions.
+Prior to the start of the two-step task, participants completed four self-report measures in a randomized order.
+One was the 14-item seven-up/seven-down scale (7u/7d; \cite{youngstrom_2013_susd-2}), which measures lifetime incidence of depressive and (hypo)mania symptoms.
+This scale is expected to elicit lower rates of symptom endorsement, thereby resulting in asymmetric (right-skewed) score distributions.
 Participants also completed a 7-item measure of general anxiety symptoms over the last year (e.g.
 ``I was overwhelmed by anxiety.''; \cite{watson2022development}).
-This scale is expected to elicit moderate rates of symptom endorsement, thereby resulting in symmetric score distributions.
-We expected the depression and mania measures to be at greater risk than the anxiety measure for spurious correlations with behavior on the two-step task.
+This scale is expected to elicit moderate rates of symptom endorsement, thereby resulting in a symmetric score distribution.
+We therefore expected the depression and mania measures to be at greater risk for spurious correlations with behavior on the two-step task than the anxiety measure.
 
@@
 ``I believe in the importance of art''; \cite{ashton2007empirical}).
-Based on previous studies, this scale is expected to elicit high rates of endorsement, thereby resulting in an asymmetric (left-skewed) score distribution.
-Finally, participants completed a 6-item measure of greed avoidance, which measures tendencies towards status-seeking (e.g.
+Based on previous studies, this scale is expected to elicit high rates of endorsement, thereby resulting in an asymmetric score distribution.
+Finally, participants completed a 6-item measure of greed avoidance, which measures attitudes towards wealth and status (e.g.
 ``I am out for my own personal gain''; \cite{ashton2007empirical}).
 Based on previous studies, this scale is expected to elicit moderate rates of endorsement, thereby resulting in a symmetric score distribution.
-We  expected the artistic interests scale to be at greater risk than the greed avoidance scale for spurious correlations with behavior on the two-step task.
+We therefore expected the artistic interests scale to be at greater risk for spurious correlations with behavior on the two-step task than the greed avoidance scale .
 
@@
 
-\subparagraph{Infrequency items}
-
-Infrequency items are questions for which all or virtually all attentive participants should provide the same response.
+\subparagraph{Self-report screening measure: Infrequency items.} Infrequency items are questions for which all (or virtually all) attentive participants should provide the same response.
 We embedded four infrequency items across the self-report measures.
@@
 \begin{enumerate}
-  \item Have there been times in your life where you blinked your eyes at least once per day?
-  \item Have there been times of a couple days or more when you were able to breathe underwater (without an oxygen tank)?
-  \item I was worried about the canine World Cup.
-  \item I have used a computer.
+  \item Have there been times in your life where you blinked your eyes at least once per day? (Expected response: \textit{Very often})
+  \item Have there been times of a couple days or more when you were able to breathe underwater (without an oxygen tank)? (Expected response: \textit{Never or hardly ever})
+  \item I was worried about the canine World Cup. (Expected response: \textit{Not at all})
+  \item I have used a computer. (Expected response: \textit{Slightly Agree}, \textit{Agree}, or \textit{Strongly agree})
 \end{enumerate}
@@
 Prior to conducting the study, the infrequency items were piloted on an independent sample of participants to ensure that they elicited one dominant response.
-We also included one instructed item (``Please select "Neutral" as your response'') to compare to the infrequency items.
-We measured the number of suspicious responses made by each participant to these questions.
+We also included one instructed item (``Please select `Neutral' as your response'') to compare to the infrequency items.
+We measured the number of `suspicious' (i.e., incorrect) responses made by each participant to these questions.
 For thresholded analyses, participants were flagged if they responded incorrectly to one or more of these items.
 
-\subparagraph{Task-based screening variables}
-
-\subparagraph{Key variability} Key variability was defined as the fraction of trials a participant pressed the left arrow key across first stage choices during the two-step task.
-Key variability could range from 0.00 (only right arrow key used) to 1.00 (only left arrow key used).
+\subparagraph{Task-based screening variable: Side variability.} Side variability was defined as the fraction of trials a participant chose the left option (by pressing the left arrow key) across first stage choices during the two-step task.
+Side variability could range from 0.00 (only right arrow key used) to 1.00 (only left arrow key used).
 Extreme values (i.e.
-closer to zero or one) are indicative of more careless responding during the task.
-
-\subparagraph{Choice variability} Choice variability was defined as the fraction of trials a participant chose the same first-stage choice option during the two-step task.
-(The left-right position of first-stage choice options were randomized across trials, such that response key and response choice were orthogonalized.) Choice variability could range from 0.00 (only selected the first option) to 1.00 (only selected the second option).
+closer to zero or one) are indicative of more careless responding during the task, as the sides for which each choice option was displayed was determined randomly on each trial.
+
+\subparagraph{Task-based screening variable: Choice variability.} Choice variability was defined as the fraction of trials a participant chose the same first-stage choice option (randomized to the right or left side of the screen) during the two-step task.
+Choice variability could range from 0.00 (selected the green rocket ship exclusively) to 1.00 (selected the purple rocket ship exclusively).
 Extreme values (i.e.
-closer to zero or one) are indicative of more careless responding during the task.
-
-\subparagraph{Win-Stay Lose-Shift} Win-stay lose-shift (WSLS) measures a participant's tendency to stay with a first-stage choice option following a second-stage reward versus shifting to a new choice option following a non-reward.
+closer to zero or one) are indicative of more careless responding during the task as the most rewarding option changed throughout the task.
+
+\subparagraph{Task-based screening variable: Win-Stay Lose-Shift.} Win-stay lose-shift (WSLS) measures a participant's tendency to stay with a first-stage choice option following a second-stage reward versus shifting to a the other choice option following a non-reward.
 WSLS thus measures a participant's sensitivity to reward feedback.
-WSLS was estimated per participant via regression, where the current first-stage choice (stay, switch) predicted by the previous trial's outcome (reward, non-reward) and a stationary intercept.
-Here we used the first (slope) term to represent a participant's WSLS tendency.
+WSLS was estimated per participant via regression, predicting each first-stage choice (stay, switch) by the previous trial's outcome (reward, non-reward) and an intercept.
+We used the first (slope) term to represent a participant's WSLS tendency.
 Lower values of this term indicate less sensitivity to reward feedback and are thus indicative of more careless responding during the task.
-
-\subparagraph{Response Times} Suspicious response time was defined as the proportion of first-stage choices with an outlier response time, here measured as responses faster than 200ms.
+Thresholds for chance-level WSLS performance were determined by fitting the same regression model to 5000 randomly-generated datasets of first-stage choice (datasets were generated by matching the probability of staying with the previous trial's choice to the distribution observed empirically, but choices were otherwise independent across trials; that is, independent of previous outcome).
+The threshold for above-chance WSLS was defined as the 95th percentile of the distribution of slope estimates for the random data, corresponding to a one-tailed hypothesis test ($\alpha = 0.05$) that the slope coefficient is greater than zero.
+
+\subparagraph{Task-based screening variable: Response times.} ``Suspicious response time'' was defined as the proportion of first-stage choices with a response faster than 200ms.
 Greater proportions of outlier response times are indicative of more careless responding during the task.
 
-\subparagraph{Correspondence Analysis} We measured the correspondence of the above screening measures via two complimentary approaches.
+\subparagraph{Correspondence Analysis.} We measured the correspondence of the above screening measures via two complementary approaches.
 First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation.
@@
 The former approach estimates two measures' monotonic association, whereas the latter approach estimates their agreement as to which participants were most likely engaging in C/IE responding.
-For significance testing, we used permutation testing wherein a null distribution of similarity scores (i.e.
-Spearman's correlation, Dice coefficient) was generated for each pair of screening measures by iteratively permuting participants' identities within measures and re-estimating the similarity.
+For significance testing, we used permutation testing wherein a null distribution of similarity scores (Spearman's correlations or Dice coefficients) was generated for each pair of screening measures by iteratively permuting participants' identities within measures and re-estimating the similarity.
 P-values were computed by comparing the observed score to its respective null distribution.
@@
 
-To quantify the effects of both task and self-report data screening on behavior-symptom correlations, we estimated the pairwise correlations between the scale scores of each self-report measure and several measures of performance on the two-step task.
-For each participant, we computed model-agnostic measures of performance on the two-step task \cite{gillan2016characterizing}.
+To quantify the effects of both task and self-report data screening on behavior-symptom correlations, we estimated the pairwise correlations between the scale scores of each self-report measure and several measures of model-agnostic performance on the two-step task \cite{gillan2016characterizing}.
 Logistic regression analyses were conducted with the \textit{statsmodels} package \cite{seabold2010statsmodels} in the python programming language.
@@
 Correlations between the behavioral measures (i.e.
-logistic regression coefficients) and self-report measures were calculated (after various forms of screening and exclusion) using Spearman's rank correlation.
+logistic regression coefficients) and self-report measures were calculated using Spearman's rank correlation, after various forms of screening and exclusion.
 Significance testing was performed using the percentile bootstrap method \cite{wilcox2018guide-2} so as to avoid making any parametric assumptions.
@@
 
-Previously we observed a mean-shift in the average level of symptom endorsement for participants suspected of engaging in C/IE responding, relative to attentive participants, when the overall rate of symptom endorsement is low.
+Previously, we observed a mean-shift in the average level of symptom endorsement for participants suspected of engaging in C/IE responding relative to attentive participants on measures for which the overall rate of symptom endorsement is low.
 This result was (mostly) replicated in the current dataset.
 Total scores were noticeably exaggerated in participants suspected of C/IE responding for the symptom measures where overall rates of symptom endorsement were the lowest (e.g.
-mania; Figure \ref{fig:repl_distributions}).
-Furthermore, where there was higher rates of symptom endorsement overall (e.g.
-anxiety), the distributions of symptom scores between the two groups of participants were more similar.
+mania; Figure \ref{fig:repl_distributions}, leftmost plot).
+Where there were higher rates of symptom endorsement overall (e.g.
+anxiety), the distributions of symptom scores between the two groups of participants were more similar (Figure \ref{fig:repl_distributions}, middle plots).
 Permutation testing confirmed that observed mean-shifts in symptom scores for C/IE participants were statistically significant for the most skewed symptom measures (Table \ref{tab:rep_validation}).
 
-For the personality measures, an interesting pattern emerged.
+For the personality measures, however, an interesting pattern emerged (Figure \ref{fig:repl_distributions}, rightmost plots).
 We did not observe a statistically significant mean-shift in total scores for the subscale with the most skewed score distribution (i.e.
 artistic interests; $t = 1.87$, $p = 0.061$).
-However, an unexpected and statistically significant mean-shift in the average level of endorsement was observed for the more symmetrically-distributed greed avoidance subscale ($t = 16.44$, $p < 0.001$).
+However, an unexpected and statistically significant mean-shift in the average level of endorsement was observed for the more symmetrically-distributed greed-avoidance subscale ($t = 16.44$, $p < 0.001$).
 The reason for this finding is unclear.
@@
 
-Next, we evaluated the degree of correspondence between behavioral and self-report screening measures in order to determine whether screening on behavior alone was sufficient to identify and remove careless participants.
+Next, we evaluated the degree of correspondence between behavioral and self-report screening measures to determine whether screening on behavior alone was sufficient to identify and remove careless participants.
 To measure the degree of correspondence between these behavioral and self-report screening measures, we performed two complementary analyses.
-First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation.
-The resulting pairwise similarity matrices are presented in Figure \ref{fig:repl_correspondence} (left panel).
+First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation (Figure \ref{fig:repl_correspondence}, left panel).
 After correcting for multiple comparisons, there were a handful of significant correlations between the behavioral and self-report screening measures.
@@
 Each tile corresponds to the Spearman rank correlation (left) and Dice similarity coefficient (right) between two screening measures.
-Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; KV = key variability; CV = choice variability; WSLS = win-stay lose-shift rate; RT = suspicious response times.
+Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; SV = side variability; CV = choice variability; WSLS = win-stay lose-shift rate; RT = suspicious response times.
 Similarity scores have been thresholded after correcting for multiple comparisons.
@@
 To understand the effects of applying different forms of screening, we estimated the correlations between each unique pairing of a self-report measure and measure of behavior under four different conditions: no screening, screening only on task behavior (i.e.
-only participants whose win-stay lose-shift behavior was above chance), screening only on self-report responses (i.e.
-only participants who responded correctly on all infrequency items), or both.
+removing participants whose win-stay lose-shift behavior was not above chance), screening only on self-report responses (i.e.
+removing only participants who responded incorrectly on one or more infrequency items), or both.
 The resulting pairwise behavior-symptom correlations following each screening procedure are presented in Figure \ref{fig:repl_correlations}.
@@
 
-When no rejections based on C/IE responding was applied (i.e.
-all participants were included in the analysis; Figure \ref{fig:repl_correlations}A), we observed multiple significant correlations between measures of task behavior and symptom scores, in particular for hypomania and depression.
-Consistent with our predictions, these correlations involved measures with low overall endorsement rates and mean-shifts in total scores distributions between attentive and C/IE participants.
+When no rejections were applied (i.e.
+all participants were included; Figure \ref{fig:repl_correlations}A), we observed multiple significant correlations between measures of task behavior and symptom scores for hypomania and depression.
+Consistent with our predictions, these correlations involved measures with low overall endorsement rates and mean-shifts in score distributions between attentive and C/IE participants.
 Conversely, we found no significant correlations with the symmetrically-distributed anxiety scores.
-This is despite the fact this scale measures comorbid symptoms and syndromes.
+This is despite the fact this scale measures symptoms that are comorbid with depression and mania.
 Crucially, of the two personality measures, we observed significant correlations only for the measure found to exhibit a mean-shift in scores between attentive and C/IE participants (i.e.
 greed avoidance).
-Crucially, this included a significant correlation with the interaction term, which is used as a proxy measure for model-based choice behavior.
+These included a significant correlation with the interaction term, which is used as a proxy measure for model-based choice behavior.
 That is, significant correlations were not restricted only to general behavioral measures but also to measures of specific theoretical interest.
 
-Next, we excluded participants from analysis based on task-behavior screening (i.e.
-win-stay lose-shift, removing the 8\% of participants exhibiting behavior indistinguishable from chance; Figure \ref{fig:repl_correlations}B).
+Next, we excluded participants from the analysis based on task-behavior screening (i.e.
+lack of win-stay lose-shift behavior, removing the 8\% of participants exhibiting behavior indistinguishable from chance; Figure \ref{fig:repl_correlations}B).
 In contrast to the findings of the original study, the pattern of correlations was meaningfully changed: the putatively spurious correlations between greed avoidance and performance on the two-step task were ablated.
 Two previously significant correlations between hypomania and two-step performance were also rendered non-significant.
-A similar pattern of results was observed when we rejected participants based on self-report screening (removing 14\% of participants who endorsed one or more invalid or improbable responses on the infrequency items; Figure \ref{fig:repl_correlations}C) and when rejections were applied based on both task and self-report screening measures (Figure \ref{fig:repl_correlations}D).
+A similar pattern of results was observed when we rejected participants based on self-report screening (removing 14\% of participants who endorsed one or more invalid or improbable responses on the infrequency items; Figure \ref{fig:repl_correlations}C) and when rejections were applied based on both task and self-report screening measures (removing 18\% of participants; Figure \ref{fig:repl_correlations}D).
 
@@
 \caption{Absolute Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions.
-Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons).
+Only statistically significant correlations are shown ($p<0.05$, not corrected for multiple comparisons).
 Black Xs indicate significant correlations ablated under screening.
@@
 These findings suggest that some of the significant behavior-symptom correlations observed without strict participant screening may indeed be spurious correlations driven by C/IE responding.
-Interestingly, in contrast to the original study, screening based on task behavior or self-report behavior alone was sufficient to protect against spurious symptom-behavior correlations in the presence of mean-shifts in scores between attentive and C/IE participants.
-For example, both forms of screening ablatated the would-be significant correlation between model-based behavior and greed avoidance.
-The discrepancy in results between the original and replication studies may reflect the fewer numbers of participants failing attention checks in the replication study (14\%) compared to the original study (22\%).
+Interestingly, in contrast to the original study, with a more demanding behavioral task, screening based on either task behavior or self-report behavior alone was sufficient to protect against spurious symptom-behavior correlations in the presence of mean-shifts in scores between attentive and C/IE participants.
+For example, both forms of screening ablated the would-be significant correlation between model-based behavior and greed avoidance.
+The discrepancy in results between the original and replication studies may reflect the smaller numbers of participants failing attention checks in the replication study (14\%) compared to the original study (22\%), as well as differences in the behavioral tasks.
 Regardless, we replicate the findings of the original study in that screening on self-report data allowed us to identify symptom-behavior correlations most likely to be spurious.
@@
 
-Here we reported the findings from a replication study, the purpose of which was to examine the generalizability of our original findings under new labor market conditions, behavioral measures, and self-report measures.
-To this end, we recruited an independent sample of almost 400 participants, using Cloudresearch's and Prolific's latest data quality filters, to complete the two-step task and a novel set of self-report measures.
-As evidence of the efficacy of these filters, the proportion of participants flagged for C/IE responding in the self-report measures was noticeably smaller in the replication sample (14\%) compared to original sample (22\%).
+Here we reported findings from a replication study whose purpose was to examine the generalizability of our original findings under new labor market conditions, different behavioral measures, and different self-report measures.
+To this end, we recruited an independent sample of almost 400 participants, using CloudResearch's and Prolific's latest data-quality filters, to complete the two-step task and a novel set of self-report measures.
+As evidence of the efficacy of the new data-quality filters, the proportion of participants flagged for C/IE responding in the self-report measures was noticeably smaller in the replication sample (14\%) compared to original sample (22\%).
 This decrease in the number of participants suspected of C/IE responding was observed for both MTurk and Prolific (though, as in the original study, the proportion of low-quality participants was significantly, albeit marginally, smaller for Prolific than MTurk).
-Regardless, though these online labor platform quality control measures seem to be effective, they do not completely solve the problem.
-That is, a non-negligible number of participants on both platforms continue to engage in C/IE responding.
+Regardless, although the new online labor platform quality-control measures seem to be effective, they did not completely solve the problem; indeed, the proportion of participants engaging in C/IE responding was reduced only by one-third.
 
 Next, we compared the distribution of self-report scale scores for attentive participants and participants suspected of engaging in C/IE responding.
-Replicating our previous result, we observed a mean-shift in the average level of symptom endorsement for participants suspected of C/IE responding, relative to attentive participants, only when the overall rate of symptom endorsement was low.
+Replicating our previous result, we observed a mean-shift in the average level of symptom endorsement for participants suspected of C/IE responding relative to attentive participants, only when the overall rate of symptom endorsement was low.
 Specifically, flagged participants showed significantly elevated scores on the hypomania scale (with its right-skewed score distribution) but not so on the anxiety scale (with its symmetric score distribution).
-Interestingly, we found the opposite pattern for the personality measures: scores for participants engaging in C/IE responding were not significantly different than their attentive counterparts on the artistic interests scale (with its left-skewed score distribution), but was so for the greed avoidance scale (with its more symmetric score distribution).
-The cause for the discrepancy in findings between the symptom and personality measures is unclear.
-One possible explanation is the direction of the skew for the artistic interests scale.
-Previously, using random intercept item factor analysis, we observed that participants engaging in C/IE responding were more likely to use the right-half of the response scale.
+Interestingly, we found the opposite pattern for the personality measures: scores for participants engaging in C/IE responding were not significantly different than those of their attentive counterparts on the artistic interests scale (with its left-skewed score distribution), but was so for the greed avoidance scale (with its more symmetric score distribution).
+One possible explanation for the discrepancy in findings between the symptom and personality measures is the direction of the skew for the artistic interests scale.
+Previously, using random-intercept item factor analysis, we observed that participants engaging in C/IE responding were more likely to use the right-half of the response scale.
 As such, such a pattern of responding is more likely to produce a mean-shift in scale scores, compared to attentive participants, on a scale with a right-skewed distribution (e.g.
@@
 
-After, we evaluated the degree of correspondence between behavioral and self-report screening measures.
-The results in the replication study corroborate the findings of the original study: measures of C/IE responding in task and self-report data do not identify the same set of participants.
-Using a different and more difficult task (i.e.
-two-step task), we again observed relatively low correspondence between self-report and task-based screening measures.
-Thus, we are more confident that both forms of screening are necessary to identify participants providing low-quality responses.
-Finally, examined the consequences of various types of screening methods for correlations between behavioral and self-report measures.
+The results in the replication study did corroborate the findings of the original study in terms of the degree of correspondence between behavioral and self-report screening measures, suggesting that measures of C/IE responding in task and self-report data do not identify the same set of participants.
+Even with a more difficult task (i.e., the two-step task), we observed relatively low correspondence between self-report and task-based screening measures.
+This supports our suggestion that both forms of screening are necessary to identify participants providing low-quality responses.
+Finally, we examined the consequences of various types of screening methods for correlations between behavioral and self-report measures.
 As in the original study, we detected significant spurious correlations when no screening was applied.
 This included correlations between model-based planning on the two-step task and scores on the greed avoidance scale, for which there is no theoretical reason to predict a correlation.
-Instead, this almost certainly reflects the mean-shift in scores between attentive participants and participants flagged for C/IE responding on the greed avoidance scale.
+Instead, this correlation almost certainly reflects the mean-shift in scores between attentive participants and participants flagged for C/IE responding on the greed avoidance scale.
 As evidence of this, excluding participants who failed one or more infrequency items ablated this correlation.
 In contrast to the original study, excluding participants based on poor performance on the two-step task was also sufficient to ablate this correlation.
-Thus, there may be instances where screening on poor behavioral performance is sufficient to prevent spurious correlations.
+Thus, there may be instances where screening based on poor behavioral performance is sufficient to prevent spurious correlations.
 However, in the absence of perfect information as to when those situations should arise, we conclude that it is simply safer to screen participants on both dimensions of performance.
 
-In summary, we conclude that the results of the original study largely hold in replication.
+In summary, we conclude that the results of the original study are not limited to the task and self-report measures used in that study, or to online platforms at a particular point in time.
 Despite legitimate advances in data quality controls, online labor platforms still suffer from participants engaging in C/IE responding.
-Screening based on task measures alone is still insufficient for reliably detecting inattentive responding on self-report measures.
-Finally, and most importantly, C/IE responding is still likely to result in mean-shifts in scores for symptom scales with overall low rates of endorsement, which are in turn capable of yielding spurious correlations between self-report and behavioral measures.
+Given \textit{a priori} uncertainty regarding the ability of task measures alone to screen such participants, we recommend also using infrequency items to detect inattentive responding on self-report measures.
+Finally, and most importantly, this second study strengthened the finding that C/IE responding is likely to result in mean-shifts in scores for symptom scales with overall low rates of endorsement, which are in turn capable of yielding spurious correlations between self-report and behavioral measures.
 The best safeguard against such spurious correlations continues to be screening in both domains.
@@
 \break
-\section*{Appendix C: Attention checks in healthy and psychiatric patients}
+
+\section*{\texorpdfstring{\hl{Appendix C: Attention checks in healthy and psychiatric patients}{}}}
 
@@
 
-One concern with using attention checks for use in screening and exclusion of participants is that we might inadvertently introduce an overcontrol bias \cite{elwert2014endogenous-2}.
-That is, to the extent that C/IE responding reflects lack of motivation \cite{barch2015mechanisms-2}, avoidance of effort \cite{cohen2001impairments-2, culbreth2016negative-2}, or more frequent lapses of attention \cite{kane2016individual-2, robison2017neurotic-2}, one might hypothesise a true underlying association between psychopathology and careless responding in online studies.
-In such cases, it is plausible that rigorous screening of C/IE responding might lead to the differential exclusion of truly symptomatic participants.
-The purpose of the current preliminary and exploratory study was to examine whether actual psychiatric patients --- individuals with a confirmed psychiatric disorder --- were equally or more likely than healthy controls to fail attention checks embedded in self-report symptom scales.
+One concern with using attention checks for screening and exclusion of participants is that we might inadvertently introduce an overcontrol bias \cite{elwert2014endogenous-2}.
+That is, to the extent that C/IE responding reflects symptoms of psychopathology such as lack of motivation \cite{barch2015mechanisms-2}, avoidance of effort \cite{cohen2001impairments-2, culbreth2016negative-2}, or more frequent lapses of attention \cite{kane2016individual-2, robison2017neurotic-2}, it is plausible that rigorous screening of C/IE responding might lead to the differential exclusion of truly symptomatic participants.
+As a result, true associations between poor or different task performance and psychopathology symptoms could go undetected (type II error).
+The purpose of the below preliminary and exploratory study was to examine whether individuals with a confirmed psychiatric disorder were indeed more likely than healthy controls to fail attention checks embedded in self-report symptom scales.
 
@@
 
-Participants were recruited as part of two independent studies to investigate reward processing in individuals with and without a history of major depression and bipolar disorder.
-Crucially, for present purposes, both studies required participants to complete (1) a series of computerized self-report surveys and cognitive tasks from their home, and (2) a structured clinical interview (the SCID-5) with a trained interviewer to verify whether they met the criteria for one or more psychiatric disorders.
-
-In both studies, participants volunteered for a 3-session study conducted via video conferencing.
+Participants were recruited as part of two independent studies to investigate reward processing in individuals with and without a history of major depression and bipolar disorder (results of those studies not reported here).
+Both studies required participants to complete (1) a structured clinical interview (the SCID-5) with a trained interviewer to verify that they met the criteria for one or more psychiatric disorders, and (2) a series of computerized self-report surveys and cognitive tasks.
+
+In both studies, participants volunteered for a 3-session study conducted online via video conferencing.
 Specifically, participants completed each session from their homes while on Zoom with a study coordinator.
-During each session, the study coordinator turned off their camera and microphone, but were available if the participant had any questions.
+During each session, while participants were completing self-report questionnaires or behavioral tasks, the study coordinator turned off their camera and microphone, but was available if the participant had any questions.
+
 Participants were recruited through clinician referral and Google ads targeting individuals with a history of depression, anhedonia, apathy, and/or (hypo)mania symptoms.
@@
 For one of the two studies, participants were also required to score 6 or higher on the Wechsler Test of Adult Reading to be included in the study.
-Furthermore, non-clinical participants were eligible if they did not meet criteria for any psychiatric diagnosis and were not currently taking any medication used to treat psychiatric disorders.
-In turn, clinical participants were eligible if they met criteria for a diagnosis of major depressive disorder and, if they were on medication, they had been on on stable treatment with this medication for at least the past 4 weeks.
+Furthermore, clinical participants were eligible if they met criteria for a diagnosis of major depressive disorder and, if they were on medication, they had been on on stable treatment with this medication for at least the past 4 weeks.
+Non-clinical (control group) participants were eligible if they did not meet criteria for any psychiatric diagnosis and were not currently taking any medication used to treat psychiatric disorders.
 
@@
 
-To measure C/IE responding in healthy and psychiatric participants, we used two sets of attention checks.
+To measure and compare C/IE responding between healthy and psychiatric participants, we used two sets of attention checks.
 Each set was composed of three infrequency items and one instructed item.
@@
 
-Of primary interest here is whether psychiatric patients fail infrequency item attention checks at equal or greater rates than healthy participants.
+Of primary interest here was whether psychiatric patients fail infrequency item attention checks at equal or at greater rates than healthy participants.
 To test this, we conducted Bayesian hypothesis testing using Bayes factors \cite{harms2018making}.
@@
 
-where $N_1$ and $N_2$ are the observed number of healthy and psychiatric patients; $p$ is the latent probability of a participant failing one or more attention checks; and $\delta$ is an offset parameter specifying the hypothesized difference in failure rates between groups.
+where $N_1$ and $N_2$ are the observed number of healthy and psychiatric participants, respectively; $p$ is the latent probability of a participant failing one or more attention checks; and $\delta$ is an offset parameter specifying the hypothesized difference in failure rates between groups.
 Thus, $M_0$ assumes equal rates of failures between healthy and psychiatric participants, whereas $M_1$ and $M_2$  assume greater and lower rates, respectively, for psychiatric participants compared to healthy participants.
@@
 In total, 16 of 65 (24.6\%) participants failed one or more attention checks.
-Interestingly, the overall proportion of flagged participants is similar to that observed for the original study.
-Subdivided by group, 6 of 20 (30\%) healthy participants and 10 of 45 (22\%) psychiatric participants were flagged for C/IE responding.
-Unsurprisingly, given the sample size, the difference in the two proportions was not significantly different than zero ($z = 0.672$, $p = 0.502$).
-Across six infrequency items, the average failure rate was 8.5\% (range: 0.0\% -- 19.7\%).
+Interestingly, the overall proportion of flagged participants was similar to that observed for the original study.
+Subdivided by group, 6 of 20 healthy participants (30\%) and 10 of 45 psychiatric participants (22\%) were flagged for C/IE responding.
+Unsurprisingly, given the modest sample size, the difference between the two proportions was not significantly different from zero ($z = 0.672$, $p = 0.502$).
+Across the six infrequency items, the average failure rate was 8.5\% (range: 0.0\% -- 19.7\%).
 In contrast, no participant failed either instructed item.
@@
 
-Here we sought to examine whether actual psychiatric patients were equally or more likely to fail infrequency items than healthy controls in settings similar to those experienced by online participants.
-Though the small sample precludes any definitive conclusion, it is noteworthy that the model least consistent with the data is the one where psychiatric patients are more likely to fail infrequency item attention checks.
-Indeed, a model where healthy controls failed attention checks at a greater rate than patients was credibly preferred to the alternative.
+Here we sought to examine whether actual psychiatric patients were equally or more likely to fail infrequency items than healthy controls in settings similar to those experienced by online participants (i.e., completing an experiment online, on a computer in one's home or otherwise chosen environment).
+Although the small sample precludes any definitive conclusion, it is noteworthy that the model least consistent with the data was the one where psychiatric patients were more likely to fail infrequency-item attention checks.
+Indeed, a model in which healthy controls failed attention checks at a greater rate than patients was credibly preferred to the alternative.
 This preliminary finding may reflect differences in motivation between patients and controls for participating in psychiatric research.
 Indeed, whereas healthy controls may be primarily motivated to participate for monetary purposes, patients may be motivated to participate to further scientific research that may ultimately benefit them (or others suffering from the same conditions).
-That is, patients may have more ``stakes in the game'' and therefore be motivated to provide higher-quality responses.
+That is, patients may have more ``stakes in the game,'' and therefore may be motivated to provide higher-quality responses.
 Regardless, further research is required to examine whether this preliminary finding holds in larger samples and other testing contexts.

### 2023-01-17 manuscripts/letter.tex
ready for resubmission (probably)

@@
 As such, although we do not dispute that overcontrol bias is an important conceptual issue, we conclude that there are both empirical and theoretical reasons to believe that this issue does not undermine our results.
-
-In addition, if these results are not yet sufficient to ease your mind regarding psychiatric overcontrol, in another new study that we detail on in response to your critique 3 below, we tested a new sample for correlations between self report of non-symptom measures (greed avoidance and artistic interests), and also found these measures to have spurious correlations with task performance when no C/IE screening was applied.
-Since there is no reason to expect that the correlation is specifically driven by psychopathology, an overcontrol of those suffering from psychiatric conditions should not have affected these correlations in the way it did.
-See more details below, and in Appendix B of the paper.
 
@@
 This suggests that, although behavioral researchers were aware of the need for data quality assurance protocols in general, few in this growing and impactful field were aware of the need for rigorous screening of their self-report data.
-Importantly, this may have already led to spurious results in the field.
-If it were commonly accepted that correlations between unusually high symptom levels on psychiatric measures and performance on behavioral measures are not meaningful, this would have been a cornerstone in the field of computational psychiatry, as this field is predominantly interested in such correlations.
-Nevertheless, we had not heard of this idea prior to doing our own research on the matter.
 
@@
 If by ``MTurk/Prolific scores'' the reviewer is referring to platform-specific metrics like HIT Approval Rate, we did not use these as inclusion criteria because previous research has found they are not discriminating between low- and high-quality participants \cite{robinson2019tapped}.
-This is noted in the methods under the ``Sample'' section:
+This is already noted in the methods under the ``Sample'' section:
 

### 2023-01-17 manuscripts/main.tex
ready for resubmission (probably)

@@
 % define highlight style
-% \colorlet{usercolorname}{yellow!00}    % use for public version
-\colorlet{usercolorname}{yellow!30}    % use for reviewer version
+\colorlet{usercolorname}{yellow!00}    % use for public version
+% \colorlet{usercolorname}{yellow!30}    % use for reviewer version
 \sethlcolor{usercolorname}
@@
 If these participants are similarly careless in their task performance, and are not excluded from analysis, this may result in a spurious association between greater symptom scores and worse behavioral task performance.
-Here, we demonstrate exactly this pattern of results in $N = 386$ participants recruited online to complete a self-report symptom battery and a short reversal-learning choice task.
+Here, we demonstrate exactly this pattern of results in \hl{two independent samples of participants (total $N = 779$)} recruited online to complete a self-report symptom battery and \hl{one of two common cognitive tasks}.
 We show that many behavior-symptom correlations are entirely abolished when participants flagged for careless responding on surveys are excluded from analysis.
-We also show that exclusion based on task performance alone is not sufficient to prevent these spurious correlations.
+We also show that exclusion based on task performance alone is \hl{often insufficient} to prevent these spurious correlations.
 Of note, we demonstrate that false-positive rates for these spurious correlations \emph{increase} with sample size, contrary to common assumptions.
@@
 The reversal-learning task required participants to learn through trial-and-error which of three options yielded reward most often, and was modeled after similar tasks used to probe reinforcement-learning deficits in psychiatric disorders \cite{waltz2007probabilistic, mukherjee_reward_2020}.
-The five self-report symptom measures were the 7-up (which measures symptoms of hypomania), the 7-down (which measures symptoms of depression), the GAD-7, (which measures generalized anxiety symptoms), the BIS/BAS (which measures reward and punishment motivations), the SHAPS (which measures anhedonia symptoms), and the PSWQ (which measures worry symptoms), and were chosen based on previous literature to have a variety of expected response distributions (symmetric and asymmetric).
+The five self-report measures were the 7-up (which measures symptoms of hypomania), the 7-down (which measures symptoms of depression), the GAD-7, (which measures generalized anxiety symptoms), the BIS/BAS (which measures reward and punishment motivations), the SHAPS (which measures anhedonia symptoms), and the PSWQ (which measures worry symptoms), and were chosen based on previous literature to have a variety of expected response distributions (symmetric and asymmetric).
 In line with current best-practice recommendations in personality psychology \cite{huang2015detecting}, each self-report instrument included one `infrequency' item that could be used to identify C/IE responses in survey data (see Methods for a list of infrequency items).
@@
 Though some measures have relatively clear threshold cutoffs (e.g., chance level performance for task accuracy), the majority of the measures evaluated here do not.
-As such, we evaluated the measures with respect to the top 10\% of ``suspect" participants flagged by each measure, corresponding roughly to the fraction of participants having performed at chance levels on the reversal-learning task \footnote{Results of the same analysis repeated for the top 25\% of ``suspicious" participants (corresponding roughly to the fraction of participants flagged by the infrequency-item measure) produced similar results, and are included in the supplement.}.
-Results were largely consistent with the correlation analysis: few pairs of task and self-report screening measures achieved levels of agreement greater than what would be expected by chance.
+As such, we evaluated the measures with respect to the top 10\% of ``suspect" participants flagged by each measure, corresponding roughly to the fraction of participants having performed at chance levels on the reversal-learning task.\footnote{Results of the same analysis repeated for the top 25\% of ``suspicious" participants (corresponding roughly to the fraction of participants flagged by the infrequency-item measure) produced similar results, and are included in the supplement.} Results were largely consistent with the correlation analysis: few pairs of task and self-report screening measures achieved levels of agreement greater than what would be expected by chance.
 The only significant cross-modality pair identified --- between the infrequency item and choice accuracy measures --- has a similarly coefficient less than 0.4.
@@
 \caption{Absolute Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions.
-Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons; \hl{all signed correlations are shown in the Supplementary Figure} \ref{fig:correlations_s1}).
+Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons; \hl{all signed correlations are shown in Supplementary Figure} \ref{fig:correlations_s1}).
 Black Xs indicate significant correlations ablated under screening.
@@
 
-In the self-report symptom measures, we replicated the finding that total scores were noticeably exaggerated in participants suspected of C/IE responding, but only for symptom measures where overall rates of symptom endorsement were the lowest (i.e., measures that have normative endorsements skewed towards 0).
+In the self-report symptom measures, we replicated the finding that total scores were noticeably exaggerated in participants suspected of C/IE responding, but only for symptom measures where overall rates of symptom endorsement were the lowest.
 Similarly, we again found that task-based screening and self-report screening measures showed low correspondence; that is, excluding participants on the basis of poor behavioral performance would not have identified and removed participants who engaged in C/IE responding on self-report surveys.
@@
 To explore this possibility, we embedded attention checks into the self-report measures of two studies of patients with major depressive disorder (see Appendix C for details).
-Specifically, N=45 psychiatric patients (confirmed to meet criteria for a diagnosis of major depressive disorder through a structured clinical interview) and N=20 healthy controls, all recruited through the Rutgers-Princeton Center for Computational Cognitive NeuroPsychiatry (i.e., personal recruitment, not on online platforms), completed a series of self-report symptom measures, online, on their computers from the comfort of their homes.
+Specifically, N=45 psychiatric patients (confirmed to meet criteria for a diagnosis of major depressive disorder through a structured clinical interview) and N=20 healthy controls, all recruited through the Rutgers-Princeton Center for Computational Cognitive Neuropsychiatry (i.e., personal recruitment, not on online labour platforms), completed a series of self-report symptom measures, online, on their computers from the comfort of their homes.
 In total, 16 of 65 (24.6\%) participants failed one or more attention checks.
@@
 As such, participants completing an online task must perform a cost-benefit analysis---implicitly or otherwise---to decide how much effort to exert in responding.
-The variables that factor into such calculations are presumably manifold and likely include features of the experiment (e.g., task difficulty, monetary incentives), facets of the participant (e.g., subjective effort costs, intrinsic motivation, conscientiousness), and features of the online labor market itself (e.g., opportunity costs, repercussions for careless responding).
+The variables that factor into such calculations are presumably manifold and likely include features of the experiment (e.g., task difficulty, monetary incentives), facets of the participant (e.g., subjective effort costs, intrinsic motivation, conscientiousness), and features of the online labour market itself (e.g., opportunity costs, repercussions for careless responding).
 
 Viewed from the perspective of effort expenditure, our results suggest that participants appraised the cost/benefit trade-off differently for behavioral tasks and self-report surveys.
-Specifically, we found that only 7\% of participants were at chance-level performance in our task, compared to more than 22\% of participants who failed one or more attention-check items in the self-report surveys \hl{(a finding that replicated in a second study involving a different task)}.
+Specifically, we found that only 7\% of participants were at chance-level performance in our task, compared to more than 22\% of participants who failed one or more attention-check items in the self-report surveys \hl{(a finding that qualitatively replicated in a second study involving a different task)}.
 Moreover, different measures of C/IE responding were weakly or not at all correlated between task behavior and self-report responses.
@@
 Thus, we cannot be confident that all of the flagged participants were indeed engaging in C/IE responding; similarly, we cannot be certain that we correctly excluded all participants engaged in C/IE responding.
-We studied behavior-symptom correlations for only two tasks and a small self-report symptom batteries.
+We studied behavior-symptom correlations for only two tasks and two short self-report symptom batteries.
 It remains to be seen how generalizable our findings are, although our study design was inspired by experiments prevalent in the online computational psychiatry literature.
@@
 Through this approach, we identified for inclusion 49 studies spanning 2015 through 2020.
-The complete list of studies, and search terms used to find them, are included in the Github repository for this study.
+\hl{The complete list of studies, and search terms used to find them, are included in the Github repository for this study.}
 
@@
 The motivations for conducting a replication study were threefold.
-First, we wanted to examine the generalizability of our findings under new labor-platform conditions.
-Since summer 2020, when the original data were collected, online labor markets like Mechanical Turk/CloudResearch and Prolific Academic have undergone important changes.
+First, we wanted to examine the generalizability of our findings under new labour-platform conditions.
+Since summer 2020, when the original data were collected, online labour markets like Mechanical Turk/CloudResearch and Prolific Academic have undergone important changes.
 To address rampant data quality issues on Mechanical Turk, CloudResearch introduced their ``Approved Participants'' filter.
@@
 
-Here we reported findings from a replication study whose purpose was to examine the generalizability of our original findings under new labor market conditions, different behavioral measures, and different self-report measures.
+Here we reported findings from a replication study whose purpose was to examine the generalizability of our original findings under new labour market conditions, different behavioral measures, and different self-report measures.
 To this end, we recruited an independent sample of almost 400 participants, using CloudResearch's and Prolific's latest data-quality filters, to complete the two-step task and a novel set of self-report measures.
@@
 This decrease in the number of participants suspected of C/IE responding was observed for both MTurk and Prolific (though, as in the original study, the proportion of low-quality participants was significantly, albeit marginally, smaller for Prolific than MTurk).
-Regardless, although the new online labor platform quality-control measures seem to be effective, they did not completely solve the problem; indeed, the proportion of participants engaging in C/IE responding was reduced only by one-third.
+Regardless, although the new online labour platform quality-control measures seem to be effective, they did not completely solve the problem; indeed, the proportion of participants engaging in C/IE responding was reduced only by one-third.
 
@@
 In summary, we conclude that the results of the original study are not limited to the task and self-report measures used in that study, or to online platforms at a particular point in time.
-Despite legitimate advances in data quality controls, online labor platforms still suffer from participants engaging in C/IE responding.
+Despite legitimate advances in data quality controls, online labour platforms still suffer from participants engaging in C/IE responding.
 Given \textit{a priori} uncertainty regarding the ability of task measures alone to screen such participants, we recommend also using infrequency items to detect inattentive responding on self-report measures.
@@
 
-In both studies, participants volunteered for a 3-session study conducted online via video conferencing.
+In both studies, participants volunteered for a multi-session study conducted online via video conferencing.
 Specifically, participants completed each session from their homes while on Zoom with a study coordinator.
@@
 
-Participants were recruited through clinician referral and Google ads targeting individuals with a history of depression, anhedonia, apathy, and/or (hypo)mania symptoms.
+Participants were recruited through clinician referral and online ads (i.e., Google ads, Craigslist) targeting individuals with a history of depression, anhedonia, apathy, and/or (hypo)mania symptoms.
 Participants were eligible for participation if they (1) had no history of head injury resulting in loss of consciousness for more than 20 minutes; (2) had not been diagnosed with intellectual disability; (3) had not been diagnosed with any neurological condition; (4) did not meet criteria for substance dependence (excluding nicotine) in the past 6 months; (5) had not received electroconvulsive therapy in the past 8 weeks; and (6) were aged between 18-65.
@@
 \begin{enumerate}
-    \item Worrying too much about the 1977 Olympics.
-    \item I have never used a computer.
-    \item I would be able to lift a small (1 lb) weight.
-    \item Have there been times of a couple days or more when you were able to stop breathing entirely (without the aid of medical equipment)?
-    \item Over the past year, how often did you have days where you were able to blink your eyes without difficulty?
-    \item I am generally able to remember my own name.
+    \item Worrying too much about the 1977 Olympics. (Expected response: \textit{Not at all})
+    \item I have never used a computer. (Expected response: \textit{Completely untrue} or \textit{Quite untrue})
+    \item I would be able to lift a small (1 lb) weight. (Expected response: \textit{Extremely characteristic of me} or \textit{Somewhat characteristic of me})
+    \item Have there been times of a couple days or more when you were able to stop breathing entirely (without the aid of medical equipment)? (Expected response: \textit{Never})
+    \item Over the past year, how often did you have days where you were able to blink your eyes without difficulty? (Expected response: \textit{Often} or \textit{Very often})
+    \item I am generally able to remember my own name. (Expected response: \textit{True})
 \end{enumerate}

### 2023-04-01 manuscripts/main.tex
checkpointing revisions progress

@@
 
-% define highlight style
-% \colorlet{usercolorname}{yellow!00}    % use for public version
-\colorlet{usercolorname}{yellow!30}    % use for reviewer version
-\sethlcolor{usercolorname}
-
 % specify footnote margins
@@
 \defbibheading{main}{}
-\defbibheading{supp}{}
 \addbibresource[label=main]{main.bib}
-\addbibresource[label=supp]{supp.bib}
 \renewcommand*{\bibfont}{\small}
@@
 \setlength{\affilsep}{2em}   % set the space between author and affiliation
-\author[1]{Samuel Zorowitz}
+\author[1,*]{Samuel Zorowitz}
 \author[2]{Johanne Solis}
@@
 \affil[4]{School of Psychological Sciences, Monash University, Victoria, Australia}
+\affil[*]{Corresponding author (zorowitz@princeton.edu)}
 
@@
 If these participants are similarly careless in their task performance, and are not excluded from analysis, this may result in a spurious association between greater symptom scores and worse behavioral task performance.
-Here, we demonstrate exactly this pattern of results in \hl{two independent samples of participants (total $N = 779$)} recruited online to complete a self-report symptom battery and \hl{one of two common cognitive tasks}.
+Here, we demonstrate exactly this pattern of results in two independent samples of participants (total $N = 779$) recruited online to complete a self-report symptom battery and one of two common cognitive tasks.
 We show that many behavior-symptom correlations are entirely abolished when participants flagged for careless responding on surveys are excluded from analysis.
-We also show that exclusion based on task performance alone is \hl{often insufficient} to prevent these spurious correlations.
+We also show that exclusion based on task performance alone is often insufficient to prevent these spurious correlations.
 Of note, we demonstrate that false-positive rates for these spurious correlations \emph{increase} with sample size, contrary to common assumptions.
@@
 \begin{refsection}[main]
-\section{Introduction}
-
-In recent years, online labour markets (e.g.
-Amazon Mechanical Turk, Prolific, CloudResearch) have become increasingly popular as a source of research participants in the behavioral sciences \cite{stewart2017crowdsourcing}, in no small part due to the ease with which these services allow for recruitment of large, diverse samples.
+\section*{Introduction}
+
+In recent years, online labor markets (e.g., Amazon Mechanical Turk, Prolific, CloudResearch) have become increasingly popular as a source of research participants in the behavioral sciences \cite{stewart2017crowdsourcing}, in no small part due to the ease with which these services allow for recruitment of large, diverse samples.
 The advantages of online data collection have also begun to be recognized in psychiatric research \cite{chandler2016conducting}, where this method offers several distinct advantages over traditional approaches to participant recruitment.
 The ability to assess psychiatric symptom severity in large general-population samples makes possible large-scale transdiagnostic analysis \cite{gillan2016taking, rutledge2019machine}, and facilitates recruitment from difficult-to-reach participant populations \cite{strickland2019use}.
-Online labour markets also facilitate re-recruitment, making them an attractive option for validating the psychometric properties of assessment tools \cite{enkavi2019large} or studying clinical processes longitudinally \cite{kothe2019retention}.
+Online labor markets also facilitate re-recruitment, making them an attractive option for validating the psychometric properties of assessment tools \cite{enkavi2019large} or studying clinical processes longitudinally \cite{kothe2019retention}.
 
 With the advantages of online data collection also come specific drawbacks.
-Since participants recruited from online labour markets are typically completing experiments in their homes, they may be more likely to be distracted or multi-tasking during an experiment.
+Since participants recruited from online labor markets are typically completing experiments in their homes, they may be more likely to be distracted or multi-tasking during an experiment.
 They may also be more likely to use heuristic response strategies with the intention to minimise expenditure of time and cognitive effort (e.g., responding randomly on self-report surveys or behavioral tasks).
 Here, we will refer to such inattentive or low-effort behaviors as careless/insufficient effort (C/IE) responding \cite{huang2012detecting, curran2016methods}.
-Among researchers using online labour markets, a common view is that poor-quality data resulting from C/IE responding can simply be treated as a source of unsystematic measurement error that can be overcome with increased sample sizes \cite{gillan2016taking, chandler2020participant}.
+Among researchers using online labor markets, a common view is that poor-quality data resulting from C/IE responding can simply be treated as a source of unsystematic measurement error that can be overcome with increased sample sizes \cite{gillan2016taking, chandler2020participant}.
 Common practice in online behavioral research is to mitigate poor-quality data using the same screening methods that are typically used in in-person data collection (e.g., excluding participants who perform at- or below-chance on behavioral tasks).
@@
 In this situation, the assumption that C/IE responding merely increases unsystematic measurement noise becomes untenable.
-Because of the positive skew in the ground-truth symptom distribution, participants who respond carelessly to the symptom survey are more likely to report higher levels of symptom endorsement relative to participants who complete the survey \hl{attentively} \cite{chandler2020participant, ophir2020turker, king2018random}.
+Because of the positive skew in the ground-truth symptom distribution, participants who respond carelessly to the symptom survey are more likely to report higher levels of symptom endorsement relative to participants who complete the survey attentively \cite{chandler2020participant, ophir2020turker, king2018random}.
 Consequently, unless C/IE survey responses are carefully identified and removed, a considerable proportion of putatively symptomatic individuals in an online sample may, in fact, be participants who have not engaged with the experiment with sufficient attention or effort.
@@
 
-\begin{figure}[t]
-\includegraphics[width=16cm]{../figures/main_01.png}
-\centering
-\captionsetup{width=0.88\textwidth}
-\caption{Simulated example of how spurious behavior-symptom correlations can arise when symptom endorsement is rare.
-\textit{Left:} When symptoms are moderately common in the general population, C/IE respondents (blue) are indistinguishable from attentive participants (red) in self-report measures (x-axis, marginal distribution shown on top).
-Despite the lower task performance of C/IE respondents (y-axis), no correlation arises between symptom scores and task performance (dots are participants drawn from the shown distributions, with 15\% C/IE participants; dashed line shows the (lack of) correlation.) \textit{Right:} When symptoms are rare in the general population, careless respondents appear symptomatic in self-report measures.
-As a result, self-report symptom scores show a significant correlation with task performance.}
-\label{fig:simulation}
-\end{figure}
-
 Here, we demonstrate the real risk that C/IE responding can lead to spurious symptom-task correlations in computational psychiatry research.
@@
 We then asked whether behavioral screening alone was sufficient to identify participants engaging in C/IE responding on psychiatric symptom surveys.
-\hl{In two new datasets} from two separate online labour marketplaces, we found that screening based on task behavior fails to completely identify participants engaging in C/IE responding on surveys.
+In two new datasets from two separate online labor marketplaces, we found that screening based on task behavior fails to completely identify participants engaging in C/IE responding on surveys.
 Lastly, we investigated whether, under these circumstances, C/IE responding led to spurious correlations between symptom severity and task performance for positively-skewed symptom measures.
@@
 
-\section{Results}
-
-\subsection{Screening for C/IE responding is common for task behavior but not for self-report surveys}
+\section*{Results}
+
+\subsection*{Screening for C/IE responding is common for task behavior but not for self-report surveys}
 
@@
 
-\begin{table}[t]
+\subsection*{Careless participants appear symptomatic when the overall level of symptom endorsement is low}
+
+To measure the correspondence of screening measures estimated from task and self-report behavior, we conducted an online behavioral experiment involving a simple decision-making task and a battery of commonly used self-report psychiatric symptom measures (see Methods).
+A final sample of 386 participants from the Amazon Mechanical Turk (N=186) and Prolific (N=200) online labor markets completed a probabilistic reversal-learning task and 5 self-report symptom measures.
+The reversal-learning task required participants to learn through trial-and-error which of three options yielded reward most often, and was modeled after similar tasks used to probe reinforcement-learning deficits in psychiatric disorders \cite{waltz2007probabilistic, mukherjee_reward_2020}.
+The five self-report measures were the 7-up (which measures symptoms of hypomania), the 7-down (which measures symptoms of depression), the GAD-7, (which measures generalized anxiety symptoms), the BIS/BAS (which measures reward and punishment motivations), the SHAPS (which measures anhedonia symptoms), and the PSWQ (which measures worry symptoms), and were chosen based on previous literature to have a variety of expected response distributions (symmetric and asymmetric).
+In line with current best-practice recommendations in personality psychology \cite{huang2015detecting}, each self-report instrument included one `infrequency' item that could be used to identify C/IE responses in survey data (see Methods for a list of infrequency items).
+The entire experiment (surveys and task) was designed to require 10 minutes on average to complete (observed mean = 10.28 minutes).
+To minimize any influence of fatigue on survey responding, participants completed the surveys prior to beginning the task.
+
+To assess the overall quality of the data, we examined the number of participants flagged by the choice accuracy and infrequency item screening measures.
+Only 26 participants (7\%) were flagged as exhibiting choice behavior at or below statistically chance levels in the reversal-learning task.
+In contrast, 85 participants (22\%) endorsed a logically invalid or improbable response on one or more of the infrequency items when completing the self-report symptom measures.
+This discrepancy in the proportion of participants flagged by each method is consistent with previous research, which found varying levels of sensitivity to C/IE responding across screening methods \cite{desimone2018dirty}.
+The proportion of participants flagged for C/IE responding was marginally but significantly greater on Mechanical Turk compared to Prolific for both task (MTurk: N=18/186; Prolific: N=8/200; two-tailed, two-sample proportions test: $z(384)=2.224$, $p=0.026$, $h=0.230$, 95\% CI = [0.006, 0.107]) and survey data (MTurk: 50/186; Prolific: 35/200; two-tailed, two-sample proportions test: $z(384)=2.223$, $p=0.026$, $h=0.227$, 95\% CI = [0.011, 0.176]).
+
+We hypothesise that spurious behavior-symptom correlations may emerge due to a mean-shift in the average level of symptom endorsement in participants engaging in C/IE responding relative to attentive participants.
+In turn, a mean-shift is expected to occur when the overall rate of symptom endorsement is low; that is, comparably higher scores are more likely for C/IE participants responding at random on a right skewed questionnaire.
+In line with our predictions, the average level of symptom endorsement was noticeably exaggerated in C/IE-responding participants for the symptom measures where symptom scores were most positively-skewed (7-up, 7-down, GAD-7; see Figure \ref{fig:distributions}).
+In contrast, where there was higher rates of symptom endorsement overall, the distributions of symptom scores between the two groups of participants were less noticeably distinct.
+Permutation testing confirmed that observed mean-shifts in symptom scores for C/IE participants were statistically significant for the majority of symptom measures (Table \ref{tab:validation}).
+
+Hereafter, we use the infrequency-item method as a primary means of identifying C/IE responding in our data.
+To verify this approach, we conducted three validation analyses.
+The first analysis compared estimated internal consistency of self-report measures between the C/IE and attentive groups.
+The logic is that, if C/IE responding manifests as a tendency to respond randomly, we should expect to see a decrease in the consistency of a measure in the C/IE responding group \cite{maniaci2014caring, desimone2018dirty, desimone2018differential}.
+In line with this reasoning, we observed a reduction in Cronbach's $\alpha$ in the C/IE group for the majority of survey instruments (Table \ref{tab:validation}).
+A permutation test confirmed that the average decrease in internal consistency across measures was greater than would be expected by chance given the difference in participant numbers between groups (two-tailed, paired-samples $t$-test: $t(6)=3.689$, $p=0.021$, $d=1.506$, 95\% CI = [0.048, 0.141]).
+
+Second, we quantified the degree to which participants responded to self-report symptom surveys in a stereotyped fashion; that is, we determined if participants exhibited patterns in their responses that were independent of the contents of the survey items.
+We fit a random-intercept item factor-analysis model \cite{maydeu2006random} to self-report data (see Methods), and for each participant we estimated an intercept parameter that quantified their bias towards using responses on the left or right side of the response scale, regardless of what that response signifies for a particular self-report measure (e.g., low on one symptom scale versus high on another).
+We observed a credible difference between the average value of this intercept for the two groups ($\Delta \text{intercept} = 0.67, 95\% \ \text{HDI} = [-0.78, -0.55]$), such that C/IE participants were biased towards using the right-half of survey response options.
+This translates to a tendency to endorse \emph{more severe} symptoms on the 7-up/7-down and GAD-7 scales (where the rightmost options indicate greater frequency of symptoms) but \emph{less extreme} symptoms or personality traits on the SHAPS and BIS (where the rightmost options indicate lower frequency of symptoms or personality traits) despite these inventories measuring strongly correlated constructs (i.e., depression and anhedonia, anxiety and behavioral inhibition).
+
+Finally, we compared the proportion of participants meeting the cutoff for clinical levels of psychopathology before and after excluding participants based on their responses to the infrequency items.
+Previous studies have found that applying such measures reduced the prevalence of clinical symptomology in online samples towards ground truth rates from epidemiological studies \cite{ophir2020turker}.
+On the most positively-skewed measures, the fraction of participants reaching clinical levels of symptom endorsement prior to screening was greater than what would be expected (Table \ref{tab:validation}).
+For example, 13.0\% of participants scored at or above clinical thresholds for (hypo)mania on the 7-up scale in our sample prior to screening, compared with a 12-month prevalence of 5\% in the general population \cite{merikangas2007lifetime, merikangas2012true}, but this rate was reduced to 4.0\% (in line with the population prevalence estimates) after exclusion of C/IE respondents.
+We observed a similar pattern for both major depressive disorder and anxiety\footnote{Interestingly, compared to previous literature the proportion of participants meeting threshold on the GAD-7 was elevated.
+We suspect this may reflect elevated rates of state anxiety during the COVID-19 pandemic \cite{yarrington2021impact}, when these data were collected.} (population prevalence estimates of 7\% and 5\% respectively; \cite{kessler2012twelve, lowe2008validation, hinz2017psychometric}).
+In line with previous research, we interpret these inflated rates of clinical symptomology in our sample prior to screening as suggestive of C/IE responding \cite{ophir2020turker}.
+
+\subsection*{Low correspondence between task and self-report measures of C/IE responding}
+
+Next, we evaluated the degree of correspondence between behavioral and self-report screening measures in order to determine whether screening on behavior alone was sufficient to identify and remove careless participants.
+In line with the literature review, we computed multiple measures of C/IE responding from each participant's task behavior and survey responses (see Methods for description of measures).
+To measure the degree of correspondence between these behavioral and self-report screening measures, we performed two complementary analyses.
+First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation.
+The resulting pairwise similarity matrices are presented in Figure \ref{fig:correspondence} (left panel).
+After correcting for multiple comparisons, there were few significant correlations between the behavioral and self-report screening measures.
+Only choice accuracy showed significant associations with any self-report measure (specifically, the infrequency and Mahalonobis distance measures).
+Crucially, the sizes of these observed correlations were roughly half those observed for the correlations between the self-report measures.
+This is worrisome as it suggests that, although there is some relationship between C/IE responding on tasks and self-report inventories, the relationship is not strong enough to ensure reliable detection of careless participants using task data alone.
+
+Second, we used the Dice similarity coefficient to quantify agreement between different screening methods in the set of participants flagged for exclusion (Figure \ref{fig:correspondence}, right panel).
+This approach quantifies the degree of overlap between the set of would-be excluded participants based on different screening measures under a common exclusion rate.
+Though some measures have relatively clear threshold cutoffs (e.g., chance level performance for task accuracy), the majority of the measures evaluated here do not.
+As such, we evaluated the measures with respect to the top 10\% of ``suspect" participants flagged by each measure, corresponding roughly to the fraction of participants having performed at chance levels on the reversal-learning task.\footnote{Results of the same analysis repeated for the top 25\% of ``suspicious" participants (corresponding roughly to the fraction of participants flagged by the infrequency-item measure) produced similar results, and are included in the supplement.} Results were largely consistent with the correlation analysis: few pairs of task and self-report screening measures achieved levels of agreement greater than what would be expected by chance.
+The only significant cross-modality pair identified --- between the infrequency item and choice accuracy measures --- has a similarly coefficient less than 0.4.
+In other words, when these two measures are used to identify the top 10\% of participants most strongly suspected of C/IE responding, they agree on only two out of every five participants.
+Screening on choice accuracy alone (the most common method identified in our literature review) would fail to identify the majority of participants most likely engaging in C/IE responding as determined by the infrequency items.
+
+Taken together, these results suggest that measures of C/IE responding in task and self-report data do not identify the same set of participants.
+This means that solely excluding participants on the basis of poor behavioral performance---the most common approach in online studies---is unlikely to identify participants who engage in C/IE responding on self-report surveys.
+
+\subsection*{Spurious symptom-behavior correlations produced by C/IE responding}
+
+Here we examine the potential consequences of screening only on task behavior in our data.
+To do this, we estimated the pairwise correlations between the symptom scores of each of the self-report measures and several measures of performance on the reversal learning task.
+This analysis emulated a typical computational psychiatry analysis, in which the results of primary interest are the correlations between task behavior and self-reported psychiatric symptom severity.
+
+For each participant, we computed both descriptive and computational-model-based measures of behavior on the reversal learning task (see Methods).
+To understand the effects of applying different forms of screening, we estimated the correlations between each unique pairing of a self-report symptom measure and measure of behavior under four different conditions: no screening, screening only on task behavior (i.e., only participants whose choice accuracy was above chance), screening only on self-report responses (i.e., only participants who responded correctly on all infrequency items), or both.
+The resulting pairwise behavior-symptom correlations following each screening procedure are presented in Figure \ref{fig:correlations}.
+We note that we did not correct these correlation analyses for multiple comparisons, since our purpose was to demonstrate the extent of this issue across multiple behavioral measures and self-report symptoms.
+Any one of these correlations considered individually can be thought of as emulating a conventional analysis where fewer statistical tests would be performed.
+
+When no rejections based on C/IE responding was applied (i.e., all participants were included in the analysis; Figure \ref{fig:correlations}A), many significant correlations emerged between measures of task behavior and symptom scores, in particular for 4 of the self-report instruments (7-up, which measures symptoms of hypomania; 7-down, which measures symptoms of depression; GAD-7, which measures generalized anxiety symptoms; and BIS, which measures tendencies related to behavioral inhibition).
+Consistent with our predictions, the majority of these correlations involved symptom measures with asymmetric total score distributions.
+Attending to only the most skewed measures (i.e., 7-up, 7-down, GAD-7), symptom endorsement was correlated with almost every behavioral measure.
+That is, significant correlations were not restricted only to general behavioral measures often used as proxies for participant effort (e.g., accuracy, inverse temperature $\beta$) but also to measures of specific theoretical interest, such as asymmetry of learning from positive and negative reward prediction errors ($\kappa$).
+Conversely, we found few significant correlations among symptom measures with more symmetric distributions.
+This is despite the fact these scales measure similar symptoms and syndromes (e.g., anxiety as measured by the GAD-7 and worry as measured by the PSWQ; depression as measured by the 7-down and anhedonia as measured by the SHAPS).
+
+Next, we excluded participants from analysis based on task-behavior screening (i.e., choice accuracy, removing the 7\% of participants exhibiting behavior indistinguishable from chance; Figure \ref{fig:correlations}B).
+The pattern of correlations was largely unchanged: we again found many significant correlations between measures of behavior and asymmetric symptom measures, but almost no significant correlations involving symmetric symptom measures.
+This suggests that rejection of participants based on the most common form of behavioral screening (i.e., performance accuracy) had little effect on behavior-symptom correlations as compared to no screening.
+
+In stark contrast, when we rejected participants based on self-report screening  (removing 22\% of participants who endorsed one or more invalid or improbable responses on the infrequency items; Figure \ref{fig:correlations}C), the number of significant correlations was markedly reduced, particularly for several of the most skewed symptom measures (7-down, GAD-7) and proxy measures of task attentiveness (e.g., accuracy, inverse temperature).
+This pattern of correlations was largely similar when rejections were applied based on both task and self-report screening measures (Figure \ref{fig:correlations}D).
+We also note that with stricter screening, the remaining significant correlations were, for the most part (but not always), weaker.
+
+These findings suggest that many of the significant behavior-symptom correlations observed without strict participant screening may indeed be spurious correlations driven by C/IE responding.
+Importantly, screening based on task behavior alone did not adequately protect against spurious symptom-behavior correlations in the presence of skewed distributions of symptom endorsement.
+For instance, consider the 7-down scale, a measure of trait depression: had we not screened participants based on infrequency items, we would have erroneously concluded that there were many significant associations between reversal-learning task performance and self-reported depression.
+Screening on self-report data allowed us to identify that each of these depression-behavior correlations was likely to be entirely spurious.
+
+One possible objection to this interpretation is that the reduction in significant correlations following self-report screening was a result of the reduced sample size after removal of C/IE respondents (which comprised over 20\% of the sample).
+To test this alternative hypothesis, we performed the same correlation analysis after removing random subsets of participants, fixing the sample size to that obtained after excluding C/IE respondents.
+In this case, the pattern of significant correlations was more similar to that before screening than after screening using the infrequency measure (two-tailed, paired-samples $t$-test: $t = 262.490$, $p < 0.001$, $d = 3.713$, 95\% CI = [0.136, 0.138]; Figure \ref{fig:random}, compare to Figure \ref{fig:correlations}A).
+Thus, the reduction in significant correlations following screening was unlikely to be driven solely by a reduction in statistical power.
+
+Next, we investigated how spurious correlations depended on sample size.
+To do so, we performed a bootstrapping analysis where we held fixed the proportion of participants engaging in C/IE responding (i.e., 5\%, 10\%, 15\%, 20\%) and increased the total number of participants.
+Across all analyses, we measured the correlation and between the 7-down depression scale and learning-rate asymmetry ($\kappa$), which we previously identified as likely exhibiting a spurious association.
+(The following results are not specific to learning-rate asymmetry and generalize to other pairs of variables; Figure \ref{fig:bootstrap_s1}).
+
+The outputs of the bootstrapping analysis are presented in Figure \ref{fig:bootstrap}.
+We found that, although estimated correlation magnitudes were independent of sample size (x-axis, left panel), the absolute magnitude of the behavior-symptom correlation increased with the proportion of C/IE participants (different coloured circles, left panel).
+Crucially, we found false-positive rates for spurious correlations \emph{increased} with increases in sample size in our data for all but the smallest rates of C/IE responding (right panel).
+This runs counter to a common assumption that larger sample sizes are protective against spurious correlations because they serve to mitigate measurement error.
+Although this assumption is correct for unsystematic measurement error, it no longer holds in the regime of systematic measurement error (where larger sample sizes reduce the variance of estimates, but do not alter their bias).
+Instead, our results suggest that, except for low rates of C/IE responding, the false-positive rate for behavioral-symptom correlations will become increasingly inflated as the sample size increases.
+
+\subsection*{Pattern of results generalizes to alternative tasks, self-report measures, and quality assurance protocols}
+
+One possible concern with the results presented so far is that they are specific to one instantiation of our experimental design.
+With more stringent quality assurance protocols during participant recruitment, or perhaps a different task or set of self-report measures, one might wonder if spurious correlations would remain such a threat.
+
+To evaluate the generalizability of our findings, we therefore conducted a conceptual replication experiment in which an independent sample of N=393 participants (N=193 from MTurk using CloudResearch, N=200 from Prolific) completed a more difficult cognitive task, the well-known ``two-step task'' \cite{daw2011model}, and an alternate set of self-report measures (see Appendix B for details).
+Importantly, participants were recruited \textit{after} CloudResearch and Prolific implemented new protocols to improve data quality on their respective platforms.
+As a final control measure, participants completed self-report symptom measures as before, but also personality measures with no hypothesized relationship to model-based planning behavior on the two-step task.
+
+For the sake of brevity, we report here only the main pattern of findings (all results are reported in Appendix B).
+In the replication sample, 55 out of 393 participants (14\%) endorsed a logically invalid or improbable response on one or more of the infrequency items when completing the self-report measures.
+This is roughly two-thirds of the number of participants who were flagged for C/IE responding in the original study, suggesting that the newer quality assurance protocols used by the online platforms are at least partially effective.
+
+In the self-report symptom measures, we replicated the finding that total scores were noticeably exaggerated in participants suspected of C/IE responding, but only for symptom measures where overall rates of symptom endorsement were the lowest.
+Similarly, we again found that task-based screening and self-report screening measures showed low correspondence; that is, excluding participants on the basis of poor behavioral performance would not have identified and removed participants who engaged in C/IE responding on self-report surveys.
+
+Finally, when we did not apply any exclusions, we observed spurious correlations between performance on the two-step task and total scores for both symptom and personality self-report measures with a mean-shift in scores between attentive participants and participants suspected of C/IE responding.
+In contrast with our original findings, however, we found that excluding participants based on self-report \textit{or} task screening measures was sufficient to ablate these spurious correlations.
+
+In sum, we replicated most of the main findings from the original study in an independent sample of participants completing a different task and other self-report measures.
+Although we found that screening on task behavior was sufficient to protect against spurious correlations in the replication sample, it is difficult to generalize and predict when or why this might be the case for other datasets.
+As such, we still believe that screening for C/IE responding in both task and self-report measures is the best approach to protect oneself against the possibility of spurious correlations.
+
+\subsection*{Individuals with and without diagnosed psychiatric disorders fail attention checks at similar rates}
+
+One major concern with performing rigorous screening and exclusion of participants based on C/IE detection methods is that we might inadvertently introduce an overcontrol bias \cite{elwert2014endogenous}.
+That is, to this point we have treated the tendency towards C/IE responding as independent from psychopathology.
+However, to the extent that C/IE responding reflects lack of motivation \cite{barch2015mechanisms}, avoidance of effort \cite{cohen2001impairments, culbreth2016negative}, or more frequent lapses of attention \cite{kane2016individual, robison2017neurotic}, one might hypothesise a true underlying association between psychopathology and careless responding in online studies.
+It is thus plausible that rigorous screening of C/IE responding might lead to the differential exclusion of truly symptomatic participants.
+
+To explore this possibility, we embedded attention checks into the self-report measures of two studies of patients with major depressive disorder (see Appendix C for details).
+Specifically, N=45 psychiatric patients (confirmed to meet criteria for a diagnosis of major depressive disorder through a structured clinical interview) and N=20 healthy controls, all recruited through the Rutgers-Princeton Center for Computational Cognitive Neuropsychiatry (i.e., personal recruitment, not on online labor platforms), completed a series of self-report symptom measures, online, on their computers from the comfort of their homes.
+In total, 16 of 65 (24.6\%) participants failed one or more attention checks.
+Subdivided by group, 6 of 20 (30\%) healthy participants and 10 of 45 (22\%) psychiatric participants were flagged for C/IE responding.
+
+Using these data, we computed pairwise Bayes factors comparing three candidate models: attention check failure rates are equal between healthy and psychiatric participants (M1); failure rates are greater in psychiatric patients (M2); and failure rates are greater in healthy participants (M3).
+The model assuming equal rates of failure between healthy and psychiatric participants was 2.88 times more likely than the model assuming greater rates for psychiatric patients.
+In turn, the model assuming lower rates of failure for psychiatric patients was 1.27 times more likely than the model assuming equal rates.
+Finally, the model assuming lower rates of failure for psychiatric patients was 3.65 times more likely than the model assuming higher rates for psychiatric patients.
+Only the final comparison exceeds the cutoff value of 3, which is conventionally treated as the minimal amount of evidence required to treat a difference in model fit as meaningful.
+Although the size of the sample precludes any definitive conclusion, it is noteworthy that the model least consistent with the data was the one where psychiatric patients are more likely to fail infrequency item attention checks.
+These data suggest, therefore, that it is unlikely that individuals with high psychiatric symptom severity were disproportionately flagged for C/IE responding in the main analyses.
+Accordingly, we conclude that the screening measures we are suggesting are not likely to result in overcontrol bias and false-negative correlations between tasks and symptom measures.
+
+\section*{Discussion}
+
+In this manuscript, we highlighted a particular set of circumstances, common in computational psychiatry research done on large online samples, in which spurious correlations may arise between task behavior and self-reported symptomology.
+When the ground-truth prevalence of a symptom is low in the general population, participants who respond carelessly on measures assessing this symptom may erroneously appear as symptomatic.
+A less careful pattern of responding on tasks used to measure cognitive constructs can then masquerade as a correlation between alteration in these constructs and symptom dimensions.
+We found repeated evidence for this pernicious pattern in participants recruited from two popular online labor platforms.
+False-positive rates for these spurious correlations \emph{increased} with sample size, because the correlations are due to measurement bias, not measurement noise.
+Importantly, we found that screening on task behavior alone was insufficient to identify participants engaging in C/IE responding and avoid the false-positive correlations.
+Unfortunately, a literature review identified this type of screening as the most common practice in online computational psychiatry studies.
+We recommend instead to screen and exclude participants based on responding on surveys, a practice that abolished many spurious behavior-symptom correlations in our data.
+
+One way of conceptualizing our results is through the lens of rational allocation of mental effort \cite{kool2018mental}.
+In any experiment, attentive responding is more effortful than careless responding.
+As such, participants completing an online task must perform a cost-benefit analysis---implicitly or otherwise---to decide how much effort to exert in responding.
+The variables that factor into such calculations are presumably manifold and likely include features of the experiment (e.g., task difficulty, monetary incentives), facets of the participant (e.g., subjective effort costs, intrinsic motivation, conscientiousness), and features of the online labor market itself (e.g., opportunity costs, repercussions for careless responding).
+
+Viewed from the perspective of effort expenditure, our results suggest that participants appraised the cost/benefit trade-off differently for behavioral tasks and self-report surveys.
+Specifically, we found that only 7\% of participants were at chance-level performance in our task, compared to more than 22\% of participants who failed one or more attention-check items in the self-report surveys (a finding that qualitatively replicated in a second study involving a different task).
+Moreover, different measures of C/IE responding were weakly or not at all correlated between task behavior and self-report responses.
+This suggests the motivation for effortful responding was greater in the behavioral task, though precisely why is unclear.
+One possibility is that we gave participants a monetary incentive for attentive responding only during the task (a common practice, according to our literature review).
+A second possibility is that participants expected fewer consequences for C/IE responding during the self-report surveys, a reasonable assumption in light of how infrequently previous experiments have screened self-report data.
+Alternatively, participants may have found the gamified behavioral task more engaging or the self-report inventory more tedious.
+Regardless of the reason, this discrepancy reinforces our observations concerning the inadequacy of behavioral-task screening as a stand-alone method for identifying C/IE responding.
+Since, in general, participants may appraise costs and benefits of effortful responding differently for behavioral tasks and self-report surveys, screening for C/IE responding on one data modality may in general be unsuitable for identifying it in the other.
+We therefore recommend screening on each component of an experiment.
+
+One complicating factor for our argument is that C/IE responding may manifest in other ways than simply random responding for both behavioral tasks and self-report surveys.
+Indeed, there are more ways to respond carelessly than to respond attentively to a task or self-report inventory (e.g., random response selection, straight-lining, zig-zagging, acquiescence bias) \cite{curran2016methods}.
+The specific response strategy a participant adopts is likely to reflect the idiosyncratic integration of multiple perceived benefits (e.g., time saved, effort avoided) and costs (e.g., loss of performance bonuses, risk of detection and pay forfeited).
+As has been previously documented \cite{desimone2018dirty}, the presence of multiple response strategies makes it clear why certain screening measures are more or less likely to correlate.
+For example, the inter-item standard deviation and personal reliability measures are both sensitive to statistically random responding, but less sensitive to straight-lining.
+Most importantly, a diversity of heuristic response strategies highlights the need for many screening measures of C/IE responding, each sensitive to different heuristic strategies.
+
+Here we have focused on the potential for C/IE responding to result in spurious symptom-behavior correlations when rates of symptom endorsement are low, a case common to online computational psychiatry research.
+Beyond this, we should emphasize that a diversity of heuristic response strategies entails that there is more than one mechanism by which spurious correlations can emerge.
+To the extent that the only prerequisite is a mean-shift between attentive and careless participants, ours is not the only situation where one might expect spurious correlations to emerge \cite{huang2015insufficient}.
+For example, random responding on items with \emph{high} base-rate endorsement could yield spurious correlations with precisely the opposite pattern observed here.
+Conversely, straight-lining may actually suppress correlations when symptom endorsement is low.
+In sum, without more understanding about the various types of heuristic responding and when each is likely to occur in a sample, it is difficult to predict {\it a priori} the patterns of systematic bias that may arise for a given study.
+This is further impetus for experimenters to be wary of C/IE responding and to use a variety of screening measures to detect it.
+
+One objection to the rigorous screening and exclusion of participants based on C/IE detection methods is that we might inadvertently introduce an overcontrol bias.
+That is, to the extent that C/IE responding might reflect symptoms common to psychopathology (e.g., low motivation, effort avoidance, inattentiveness), rigorous screening of C/IE responding might lead to the differential exclusion of truly symptomatic participants.
+To explore this possibility, we embedded attention checks into the self-report measures of two studies of patients with major depressive disorder.
+Though our final sample was small, we did not find evidence for the proposition that patients were more likely to fail attention checks than healthy controls (if anything, non-psychiatric participants were more likely to be flagged by C/IE screening).
+These results provide preliminary evidence that rigorous C/IE screening is unlikely to result in overcontrol bias.
+
+Given that the results of our patient study are preliminary and warrant further investigation, researchers might still be wary of possible overcontrol bias.
+However, when using self-report questionnaires for screening, for overcontrol to seriously impact results it would have to be the case that symptomatic participants frequently endorse improbable or impossible responses to infrequency-item checks (e.g., responding `Agree' to ``I competed in the 1917 Olympic Games").
+In this case, and even if such participants truly are experiencing severe symptoms of motivation or attention, there is likely to be limited utility in measuring these symptoms using a self-report measure that they are unable to complete veridically.
+A similar rationale underlies the widespread use of semi-structured interviews and other clinician-report measures rather than self-report measures for in-clinic psychiatric research.
+We would therefore argue that, if the psychiatric phenomenon being studied is such that this issue warrants concern, the research question may be better suited to an in-person study design involving participants in the clinic who meet full diagnostic criteria than a correlational design involving an online convenience sample.
+
+Notwithstanding the above, one response to this legitimate concern is to take a graded approach to screening and excluding participants \cite{Kim2018-ev}.
+That is, participants could be screened with respect to a multitude of measures and only the consistently flagged participants be removed, thereby reducing the risk of inducing bias.
+Another possibility is to use sensitivity analysis as an alternative to exclusion, testing whether full-sample observed correlations are robust to the exclusion of participants flagged by measures of C/IE responding.
+We note that the strict screening approach used in the present study did not preclude us from identifying symptomatic participants or behavior-symptom correlations.
+Indeed, we found in our sample roughly 10\% of participants endorsing symptoms consistent with clinical levels of depression, and approximately 20\% consistent with clinical levels of acute anxiety.
+These estimates are within the realm of epidemiological norms \cite{kessler2012twelve, lowe2008validation, yarrington2021impact}.
+(We should note, however, that some studies have found elevated rates of psychiatric symptomology in online participants even after controlling for C/IE responding \cite{ophir2020turker}.) We also observed some positive correlations between anxiety and choice behavior that were consistent with effects found in previous literature \cite{huang2017computational, harle2017anhedonia, garrett2018updating}.
+For example, we found higher lose-shift rates and higher learning rates following negative prediction errors correlated with self-reported anxiety.
+This suggests that the screening methods we employed were not so aggressive as to attenuate behavior-symptom correlations that would be expected from the literature.
+
+There are several notable limitations to this proof-of-concept study.
+We used a small set of screening measures, and did not employ other recommended procedures (e.g., logging each key/mouse interaction during survey administration to detect form-filling software or other forms of speeded responding \cite{buchanan2018methods}).
+Thus, we cannot be confident that all of the flagged participants were indeed engaging in C/IE responding; similarly, we cannot be certain that we correctly excluded all participants engaged in C/IE responding.
+We studied behavior-symptom correlations for only two tasks and two short self-report symptom batteries.
+It remains to be seen how generalizable our findings are, although our study design was inspired by experiments prevalent in the online computational psychiatry literature.
+As suggested above, future studies may find greater correspondence between task and self-report screening measures for more difficult behavioral experiments.
+Finally, we should note that, unlike previous studies in which some participants were explicitly instructed to respond carelessly \cite{buchanan2018methods}, we do not have access to ``ground truth'' regarding which participants were engaging in C/IE responding.
+Future work testing the efficacy of different screening metrics for identifying instructed C/IE responding may help to identify some of the issues that we have identified here.
+
+The present study highlights the need for future work on the prevalence of C/IE responding in online samples and its interactions with task-symptom correlations.
+Many open questions remain, including under what conditions task- and symptom-screening measures might better correspond, what screening measures are most effective and when, and under what conditions spurious correlations are more likely to arise.
+One especially pressing question is how sample size affects the likelihood of obtaining spurious correlations.
+The results of a bootstrapping analysis in our data suggest that false positive rates are likely to increase with sample size.
+As computational psychiatry studies move towards larger samples to characterize heterogeneity in symptoms (and to increase statistical power), it will be important to understand how sample size may exaggerate the effects of systematic error.
+
+\section*{Conclusions}
+
+Moving forward, we would strongly recommend that experimenters employ some form of self-report screening method, preferably one recommended by the best-practices literature (see Box 1 for a list of concrete recommendations).
+Our literature review found that, to date, the majority of online studies assessing behavior-symptom correlations have not used self-report screening, and our results demonstrate that stand-alone task-behavior screening is likely to be insufficient.
+Our results also demonstrate that inadequate screening is likely not merely to result in increased measurement error, as commonly assumed, but may also induce spurious correlations between behavioral task metrics and self-reported psychiatric symptom levels.
+For these reasons, we encourage experimenters to use a variety of data-quality checks for online studies and to be transparent in their reporting of how screening was conducted, how many participants are flagged under each measure, and what thresholds are used for rejection.
+
+More broadly, we encourage experimenters in computational psychiatry to be mindful of the myriad reasons why participants may perform worse on a behavioral task.
+Wherever possible, researchers are encouraged to design experiments where the signature of some symptomology could not also be explained by C/IE responding (e.g., \cite{eldar2015interaction, hunter2019excessive}).
+Finally, we conclude by noting that it is preferable to prevent C/IE responding than to account for it after the fact \cite{ward2018applying}.
+As such, we recommend researchers take pains to ensure their experiments promote engagement, minimize fatigue and confusion, and reimburse participants fairly and ethically.
+
+%% BOX 1 %%
+\newpage
+\textbf{Box 1: Recommendations for future research}
+
+Here we offer several concrete recommendations for future research investigating symptom-behavior correlations in online samples.
+
+\begin{itemize}
+
+    \item Use multiple screening methods to detect different types of C/IE responding.
+At a minimum, we recommend screening of both behavioral and self-report data.
+Within self-report data, we recommend using methods sensitive to multiple distinct patterns of C/IE responding (e.g., random responding, straight-lining, side bias) and, if possible, to log all page interactions (e.g., mouse clicks, keyboard presses).
+
+    \item When collecting self-report questionnaire data, include attention-check items that flag participants who may be engaging in C/IE responding.
+We recommend following best-practice guidelines in using infrequency-item checks rather than instructed-item checks, as multiple studies have now shown that online participants are habituated to and circumvent the latter \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}.
+Participants flagged by suspicious responses on attention-check items should either be excluded from further analysis, or assessed using sensitivity analyses to ensure that observed full-sample correlations are robust to their exclusion.
+
+    \item We found that spurious correlations predominantly affected self-report instruments for which the expected distributions of symptom scores were asymmetric (either positively or negatively skewed).
+As such, symmetrically-distributed measures of a given construct should be preferred to asymmetrically-distributed measures (though this will often be infeasible given that the frequency of many psychiatric symptoms in the general population is itself positively skewed).
+
+    \item Scales with reverse-coded items can be used to quantify the consistency of participants' responses between reverse-coded and non-reverse-coded measures of the same latent construct.
+With some care, this may be used to identify C/IE responding even for measures that do not include attention-check items \cite{emons2009detection}.
+Similarly, it may be beneficial to include multiple self-report surveys of the same construct to measure consistency across scales.
+
+    \item In our experience, we have found it instructive to review discussions on public forums for participants of online labor markets (e.g., Reddit, TurkerNation).
+Doing so helps an experimenter identify what screening methods would-be participants are already aware of and prepared to answer correctly.
+(Several examples of workers discussing common attention checks can be found at the Github repository for this project.)
+
+    \item Consider carefully whether the online methodology is truly appropriate for the research question.
+In particular, if the project studies syndromes associated with considerable difficulty in task or survey engagement (e.g., severe ADHD, acute mania), symptomatic participants are likely to produce responses that cannot be distinguished from C/IE responding.
+In this case, correlational research with online samples is likely not the best methodology for the research question.
+
+\end{itemize}
+
+This is not an exhaustive list, and one overarching recommendation is that researchers studying individual differences in psychiatric symptom endorsement should engage meaningfully with methodological research from the psychological measurement literature, where many of these questions have long been studied \cite{huang2015insufficient, curran2016methods, thomas2017validity, desimone2018dirty, ophir2020turker}.
+
+%% END BOX 1 %%
+
+\section*{Methods}
+
+\subsection*{Experiment}
+
+\subsubsection*{Sample}
+
+409 total participants were recruited to participate in an online behavioral experiment in late June - early July, 2020.
+Specifically, 208 participants were recruited from Amazon Mechanical Turk (MTurk) and 201 participants were recruited from Prolific.
+This study was approved by the Institutional Review Board of Princeton University (\#5291), and all participants provided informed consent.
+Total study duration was approximately 10 minutes per participant.
+Participants received monetary compensation for their time (rate USD \$12/hr), plus an incentive-compatible bonus up to \$0.25 based on task performance.
+
+Participants were eligible if they resided in the United States or Canada; participants from MTurk were recruited with the aid of CloudResearch services \cite{litman2017turkprime}.
+(Note: This study was conducted prior to the introduction of CloudResearch's newest data quality filters \cite{cloudresearch_2020}).
+Following recent recommendations \cite{robinson2019tapped}, MTurk workers were not excluded based on work approval rate or number of previous jobs approved.
+No other exclusion criteria were applied during recruitment.
+It is important to note that both CloudResearch and Prolific use a number of tools (e.g., IP-address screening) to filter out the lowest quality participants.
+In addition, our custom experiment delivery software (NivTurk; see below) has bot-checking functionality built into it, and rejects from the start participants who are likely to not be human.
+We are therefore confident that our study is not strongly affected by participants using software to automatically complete the experiment.
+
+The data from multiple participants who completed the experiment were excluded prior to analysis.
+Three participants (all MTurk) were excluded due to missing data.
+In addition, we excluded 20 participants who disclosed that they had also completed the experiment on the other platform.
+This left a final sample of N=386 participants (MTurk: N=186, Prolific: N=200) for analysis.
+The demographics of the sample split by labor market is provided in Table S1.
+Notably, the participants recruited from MTurk were older ($M = 7.7 \ \text{yrs}$, two-tailed, two-sample $t$-test: $t(384)=6.567$, $p<0.001$, $d=0.669$, 95\% CI = [5.4, 10.0]) and comprised of fewer women (two-tailed, two-sample proportions test: $z(384)=2.529$, $p=0.011$, $h=0.258$, 95\% CI = [0.030, 0.228]).
+
+\subsubsection*{Experimental Task}
+
+Participants performed a probabilistic reversal learning task, explicitly designed to be similar to previous computational psychiatry studies \cite{waltz2007probabilistic, mukherjee_reward_2020}.
+On every trial of the task, participants were presented with three choice options and were required to choose one.
+After their choice, participants were presented with probabilistic feedback: a reward (1 point) or a non-reward (0 points).
+On any trial one choice option dominated the others.
+When chosen, the dominant option yielded reward with 80\% probability; the subordinate options yielded reward with only 20\% probability.
+The dominant option changed randomly to one of the two previously subordinate options every 15 trials.
+Participants completed 90 trials of the task (1 learning block, 5 reversal blocks).
+
+As a cover story, the probabilistic reversal learning task was introduced to participants as a fishing game in which each choice option was a beach scene made distinguishable by a colored surfboard with unique symbol.
+Participants were told they were choosing which beach to fish at.
+Feedback was presented as either a fish (1 point) or trash (0 points).
+Participants were instructed to earn the most points possible by learning (through trial-and-error) and choosing the best choice option.
+Participants were also instructed that the best option could change during the task, but were not informed about how often or when this would occur (see the Supplement for the complete instructions).
+Prior to beginning the experiment, participants had to correctly answer four comprehension questions about the instructions.
+Failing to correctly answer all items forced the participant to start the instructions over.
+
+The task was programmed in jsPsych \cite{deleeuw_2015_jspsych} and distributed using custom web-application software.
+All experiment code is publicly available (see Code Availability statement).
+A playable demo of the task is available at \url{https://nivlab.github.io/jspsych-demos/tasks/3arm/experiment.html}.
+
+\subsubsection*{Symptom Measures}
+
+Prior to completing the reversal learning task, participants completed five self-report symptom and personality-trait measures.
+The symptom measures were selected for inclusion based on their frequency in clinical research, and for having an expected mixture of symmetric and asymmetric score distributions.
+
+\textbf{Seven-Up/Seven-Down.} The Seven-Up/Seven-Down (7u/7d; \cite{youngstrom_2013_susd}) scale is a 14-item measure of lifetime propensity towards depressive and hypomanic symptoms.
+It is an abbreviation of the General Behavior Inventory \cite{depue1981behavioral}, wherein only items that maximally discriminated between depression and mania were included.
+Items are scored on a 4-point scale from 0 (``Never or hardly ever") to 3 (``Very often or almost constantly").
+Total symptom scores on both subscales range from 0 to 21, and are usually strongly right-skewed, with few participants exhibiting moderate to high levels of symptom endorsement.
+
+\textbf{Generalized Anxiety Disorder-7.} the Generalized Anxiety Disorder-7 (GAD-7; \cite{spitzer2006brief}) is a 7-item measure of general anxiety.
+The GAD-7 assesses how much a respondent has been bothered by each of seven core anxiety symptoms over the last 2 weeks.
+Items are scored on a 4-point scale from 0 (``not at all") to 3 (``nearly every day").
+Total scores on the GAD-7 range from 0 to 21, and are usually right-skewed, with few participants exhibiting moderate to high levels of symptom endorsement.
+
+\textbf{Behavioral Inhibition/Behavioral Activation Scales.} the Behavioral Inhibition and Behavioral Activation Scales (BIS/BAS; \cite{carver1994behavioral}) are a measure of reward and punishment sensitivity.
+The original 42-item measure was recently abbreviated to a 14-item measure \cite{pagliaccio2016revising}, which we use here.
+Items are scored on a 4-point scale from 1 (``very true for me") to 4 (``very false for me").
+Total scores on the BAS subscale range from 8 to 32, whereas total scores on the BIS subscale range from 4 to 16.
+Previous reports have found total scores to be symmetrically distributed \cite{cooper2007behavioural}.
+Importantly, in order to maintain presentation consistency with the other symptom measures, the order of the BIS/BAS response options was reversed during administration such that ``very false for me" and ``very true for me" were the left- and rightmost anchors, respectively.
+
+\textbf{Snaith-Hamilton Pleasure Scale.} the Snaith-Hamilton Pleasure Scale is a 14-item measure of anhedonia \cite{snaith1995scale}.
+Items are scored on a 4-point scale from 0 (``strongly agree") to 3 (``strongly disagree"), where higher scores indicate greater pathology.
+Total scores on the SHAPS range from 0 to 42, and have previously been found to be somewhat right-skewed \cite{franken2007assessment, leventhal2015measuring}, with only the minority of participants exhibiting moderate to high levels of symptom endorsement.
+Importantly, as with the BIS/BAS, the order of the SHAPS response options was reversed during administration such that ``strongly disagree" and ``strongly agree" were the left- and rightmost anchors, respectively.
+
+\textbf{Penn State Worry Questionnaire.} the Penn State Worry Questionnaire is a measure of worry symptoms \cite{meyer1990development}.
+The original 16-item was recently abbreviated to a 3-item measure \cite{kertz2014psychometric}, which we use here.
+Items are scored on a 5-point scale from 0 (``not at all typical of me") to 4 (``very typical of me"), where higher scores indicate greater pathology.
+Total symptom scores range from 0 to 12 and are usually uniformly distributed.
+
+\subsection*{Analysis}
+
+All statistical models fit as part of the analyses (described in detail below) were estimated within a Bayesian framework using Hamiltonian Monte Carlo as implemented in Stan (v2.26) \cite{stan}.
+For all models, four separate chains with randomised start values each took 2000 samples from the posterior.
+The first 1500 samples from each chain were discarded.
+As a result, 2000 post-warmup samples from the joint posterior were retained.
+Unless otherwise noted, the $\hat{R}$ values for all parameters was less than 1.1, indicating acceptable convergence between chains, and there were no divergent transitions in any chain.
+
+\subsubsection*{Validation analyses}
+
+To validate the infrequency items as a sensitive measure of C/IE responding, we performed three complimentary analyses. We describe each in turn below.
+
+\subparagraph{Cronbach's $\alpha$.} We compared the average Cronbach's $\alpha$, a measure of internal consistency, between attentive and C/IE participants.
+To control for the unbalanced numbers of participants in these groups, we performed a permutation test.
+First, we estimated Cronbach's $\alpha$ was estimated for each subscale and group.
+Next, we computed the average difference in Cronbach's $\alpha$ between the two groups.
+Then we created a null distribution for this statistic by repeating the same analysis but permuting group membership (i.e., randomly assigning participants to either group), holding fixed the sizes of both groups.
+This procedure was performed 5000 times.
+To compute a p-value, we tallied the number of null statistics equal to or (absolutely) greater than the observed test statistic.
+
+\subparagraph{Random intercept item factor analysis.} We employed random intercept item factor analysis \cite{maydeu2006random} to detect heuristic patterns of responding.
+In the model, the probability of observing response level $k$ (of $K$ total levels) from participant $i$ on item $j$ is defined as:
+
+\begin{equation*}
+    p( \ y_{ij} = k \ ) = \left\{ \begin{array}{ll}
+1 - \text{logit}^{-1}( \mu_i + x_j\cdot \theta_i - c_{j,1})  &  \text{if } y = 1 \\[4pt]
+\text{logit}^{-1}( \mu_i + x_j\cdot \theta_i - c_{j,y-1}) - \text{logit}^{-1}( \mu_i + x_j\cdot \theta_i - c_{j,y}) & \text{if } 1 < y < K \\[4pt]
+\text{logit}^{-1}( \mu_i + x_j\cdot \theta_i - c_{j,K-1}) - 0  &  \text{if } y = K
+\end{array} \right.
+\end{equation*}
+
+where $\mu_i$ is an intercept for participant $i$; $\theta_i$ is a vector of latent factor scores for participant $i$; $x_j$ is a vector of factor loadings for item $j$; $c_j$ is a vector of ordinal cutpoints for item $j$; and $y_{ij}$ is the observed response for participant $i$ on item $j$.
+
+In this analysis, we did not estimate the factor loadings but instead treated them as observed.
+Specifically, we defined the factor loading for each item as a one-hot vector where the only nonzero entry denoted that item's corresponding subscale.
+That is, all of the items from a given subscale were assigned to their own unique factor (which was fixed to one).
+As such, the model estimated one factor score per participant and subscale (akin to the 1-parameter ordinal logistic model).
+
+Crucially, each participant's responses were also predicted by a random intercept term, $\mu_i$, which was not factor specific but instead was fit across all items.
+This intercept then reflects a participant's overall bias towards a response level.
+In our analysis, we coded the response levels such that the smallest value indicated endorsing the leftmost anchor (irrespective of semantic content) and the largest value indicated endorsing the rightmost anchor (irrespective of semantic content).
+Because the leftmost response option corresponds to symptomology on some scales (SHAPS), and a lack of symptomology for others (GAD-7, 7-up/7-down), we would not expect a consistent nonzero bias in this random intercept term for an attentive participant.
+
+\subparagraph{Clinical cutoffs.} We compared the proportion of participants in our sample reaching the threshold for clinical symptomology before and after applying exclusions.
+For the GAD-7, previous research has suggested a clinical cutoff score of 10 or higher \cite{lowe2008validation, hinz2017psychometric}.
+Though the 7-up/7-down scales do not have firmly established clinical cutoffs recent work has suggested a cutoff score of 12 or higher \cite{youngstrom2020evaluating}, which we use here.
+Finally, the original authors of the SHAPS scale recommended as a cutoff a score of 3 or more when the items are binarized (1 = ``strongly disagree", ``agree"; 0 = ``strongly agree", ``agree").
+We use this scoring approach in Table \ref{tab:validation}.
+
+\subsubsection*{Correspondence of screening measures}
+
+To measure the correspondence of task- and self-report-based screening measures, we estimated a number of standard measures of data quality from each participant's task behavior (four in total) and self-report responses (five in total).
+Beginning first with the self-report data, we describe each below.
+
+\subparagraph{Self-report screening measure: Infrequency items.} Infrequency items are questions for which all or virtually all attentive participants should provide the same response.
+We embedded four infrequency items across the self-report measures.
+Specifically, we used the following questions:
+
+\begin{enumerate}
+  \item Over the last two weeks, how much time did you spend worrying about the 1977 Olympics? (Expected response: \textit{Not at all})
+  \item Have there been times of a couple days or more when you were able to stop breathing entirely (without the aid of medical equipment)? (Expected response: \textit{Never or hardly ever})
+  \item I would feel bad if a loved one unexpectedly died. (Expected response: \textit{Somewhat true for me} or \textit{Very true for me})
+  \item I would be able to lift a 1 lb (0.5 kg) weight. Expected response: \textit{Agree} or \textit{Strongly agree})
+\end{enumerate}
+
+Prior to conducting the study, the infrequency items were piloted on an independent sample of participants to ensure that they elicited one dominant response.
+In the main study, we measured the number of suspicious responses made by each participant to these questions.
+For thresholded analyses, participants were flagged if they responded incorrectly to one or more of these items.
+
+\subparagraph{Self-report screening measure: Inter-item standard deviation.} The inter-item standard deviation (ISD) is an estimate of a participant's response consistency on a self-report measure \cite{marjanovic2015inter}, defined as:
+
+\begin{equation*}
+    ISD = \sqrt{\frac{\sum^k_{i=1}(y_j - \bar{y})^2}{k-1}}
+\end{equation*}
+
+where $y_i$ is a participant's response to item $i$, $x_i$ is a participant's average score across all  items, and $k$ is the total number of items for a self-report measure.
+A composite ISD measure was estimated per participant by summing across each of the seven self-report scales.
+Larger ISD values indicate lower response consistency.
+
+\subparagraph{Self-report screening measure: Personal reliability.} The personal reliability coefficient is an estimate of a participant's response consistency on a self-report measure, estimated by correlating the average scores from split-halves of their responses.
+To avoid any item-order bias, a participant's personal reliability coefficient for a particular self-report measure was computed from the average correlation from 1000 random split-halves.
+A composite reliability measure was generated per participant by averaging across each of the seven self-report scales.
+Smaller reliability coefficients indicate lower response consistency.
+
+\subparagraph{Self-report screening measure: Mahalanobis D.} The Mahalanobis distance is a multivariate outlier detection measure, which estimates how dissimilar a participant is relative to all others.
+For a participant $i$, the Mahalanobis D is defined as:
+
+\begin{equation*}
+    D = \sqrt{(X_i - \bar{X})^T \cdot \Sigma^{-1}_{XX} \cdot (X_i - \bar{X})^T }
+\end{equation*}
+
+where $(X_i - \bar{X})$ represents the vector of mean-centered item responses for participant $i$ and $\Sigma^{-1}_{XX}$ represents the inverted covariance matrix of all items.
+Greater Mahalanobis D values indicate larger deviations from the average pattern of responding.
+
+\subparagraph{Self-report screening measure: Reading time.} The reading time is the total number of seconds spent filling out a particular self-report measure, adjusted for that measure's total number of items \cite{ophir2020turker}.
+A total reading time estimate was estimated for each participant by summing across the adjusted time for each of the seven self-report measures.
+Shorter scores are indicative of less time having been spent on each item.
+
+\subparagraph{Task-based screening variable: Choice variability.} Choice variability was defined as the fraction of trials of the most used response option per participant.
+Choice variability could range from 0.33 (all response options used equally) to 1.00 (only one response option used).
+Values closer to 1.00 are indicative of more careless responding during the task.
+
+\subparagraph{Task-based screening variable: Choice accuracy.} Choice accuracy was defined as the fraction of choices of the reward-maximizing response option.
+For a task with 90 trials and three response options, a one-tailed binomial test at $\alpha=0.05$ reveals chance-level performance to be 37 or fewer correct choices (41\%).
+Lower accuracy values are indicative of more inattentive responding during the task.
+
+\subparagraph{Task-based screening variable: Win-Stay Lose-Shift.} Win-stay lose-shift (WSLS) measures a participant's tendency to stay with a choice option following a reward versus shifting to a new choice option following a non-reward.
+WSLS thus measures a participant's sensitivity to reward feedback on the screen.
+WSLS was estimated per participant via regression, where the current choice (stay, switch) predicted by the previous trial's outcome (reward, non-reward) and a stationary intercept.
+Here we used the first (slope) term to represent a participant's WSLS tendency.
+Lower values of this term indicate less sensitivity to reward feedback and are thus indicative of more careless responding during the task.
+
+\subparagraph{Task-based screening variable: Response times.} ``Suspicious response time'' was defined as the proportion of trials with an outlier response time, here measured as responses faster than 200ms.
+Greater proportions of outlier response times are indicative of more careless responding during the task.
+
+\subparagraph{Correspondence Analysis.} We measured the correspondence of the above screening measures via two complimentary approaches.
+First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation.
+Second, we estimated the pairwise rate of agreement on the binarized measures using the Dice similarity coefficient (looking at the top 10\% and 25\% most suspicious respondents for each measure).
+The former approach estimates two measures' monotonic association, whereas the latter approach estimates their agreement as to which participants were most likely engaging in C/IE responding.
+For significance testing, we used permutation testing wherein a null distribution of similarity scores (i.e., Spearman's correlation, Dice coefficient) was generated for each pair of screening measures by iteratively permuting participants' identities within measures and re-estimating the similarity.
+P-values were computed by comparing the observed score to its respective null distribution.
+We corrected for multiple comparisons using family-wise error rates \cite{winkler2014permutation}.
+
+\subsubsection*{Correlations between behavior and symptom measures}
+
+To quantify the effects of both task and self-report data screening on behavior-symptom correlations, we estimated the pairwise correlations between the symptom scores of each of the self-report measures and several measures of performance on the reversal learning task.
+For each participant, we computed both descriptive and model-based measures of behavior on the reversal learning task.
+We describe each in turn below.
+
+\subparagraph{Descriptive measures.} Descriptive task measures included the following: accuracy (the fraction of choices of the reward-maximizing response option), points (the total number of points accumulated over the game), win-stay rates (the fraction of trials on which a participant repeated the previous trial's choice following a reward outcome), lose-shift rates (the fraction of trials on which a participant deviated from the previous trial's choice following a non-reward outcome), and perseveration (the number of trials on which a participant continued to choose the previously dominant response option following a reversal in task contingencies).
+
+\subparagraph{Model-based measures.} The model-based measures were derived from a common reinforcement learning model of choice behavior, the risk-sensitive temporal difference learning model \cite{niv2012neural}.
+In this model, the expected value of a choice option, $Q(s)$, is learned through cycle of choice and reward feedback.
+Specifically, following a decision and reward feedback, the value of the chosen option is updated according to:
+
+\begin{equation*}
+    Q_{t+1}(s) = Q_{t}(s) + \eta \cdot \delta_{t}
+\end{equation*}
+
+where $\eta$ is the learning rate bounded in the range $[0,1]$ (controlling the extent to which value reflects the most recent outcomes) and $\delta$ is the reward prediction error, defined as:
+
+\begin{equation*}
+    \delta_t = r_t - Q_{t}(s)
+\end{equation*}
+
+In the risk-sensitive temporal difference learning model, there are separate learning rates for positive and negative prediction errors, such that positive and negative prediction errors have asymmetric effects on learning.
+For example, the effect of negative prediction errors on learned values is larger than that of positive errors if $\eta_p+ < \eta_n$, and vice versa if $\eta_p > \eta_n$.
+
+Finally, decision-making according to the model is dictated by a softmax choice rule:
+
+\begin{equation*}
+    p(y_t = s) = \frac{\exp \left( \beta \cdot Q(s) \right)}{\sum_i^S \exp \left( \beta \cdot Q(s) \right)}
+\end{equation*}
+
+where $\beta$ is the inverse temperature, controlling a participant's sensitivity to the expected value of the choice options.
+In sum then, the model-based approach describes a participant's choice behavior as a function of three parameters ($\beta, \eta_p, \eta_n$).
+
+We fit the reinforcement learning model to each participants' choice behavior using Stan (details above).
+Notably, 11 participants (3\% of sample) had parameter estimates with poor convergence, i.e., $\hat{R} > 1.1$; their parameters were removed from the correlation analysis.
+Participants' parameters were fit individually (i.e., not hierarchically) so as to prevent bias during parameter estimation from partial-pooling between attentive and C/IE participants.
+Parameters were sampled using non-centred parameterisations (i.e., all parameters were sampled separately from a unit normal before being transformed to the appropriate range).
+Of note, the learning rates were estimated via an offset method such that $\eta_p = \eta + \kappa$ and $\eta_n = \eta - \kappa$, where $\kappa$ is an offset parameter controlling the extent of an asymmetry between the two learning rates.
+This parameter was also entered into the behavior-symptom correlation analyses.
+
+We confirmed the model adequately fit participants' choice behavior through a series of posterior checks (Figure \ref{fig:posterior_check}).
+In particular, we confirmed the model recapitulated the group-average learning curves for each block of the experiment.
+Moreover, we confirmed that the model was able to recover reasonably well the choice accuracy for each participant.
+
+The model-based measures included for analysis were: choice sensitivity ($\beta$,  inverse temperature), positive learning rate ($\eta_p$), negative learning rate ($\eta_n$), and learning rate asymmetry ($\kappa = \frac{\eta_p-\eta_n}{\eta_p+\eta_n}$, normalized difference between $\eta_p$ and $\eta_n$).
+We chose these measures as they have been previously used to assess performance in clinical samples \cite{huang2017computational, brolsma2020challenging, mukherjee_reward_2020, ritschel2017neural}.
+
+\subparagraph{Correlation analysis.} Behavior-symptom correlations (after various forms of screening and exclusion) were estimated using Spearman's rank correlation.
+Significance testing was performed using the percentile bootstrap method \cite{wilcox2018guide} so as to avoid making any parametric assumptions.
+These correlation analyses were not corrected for multiple comparisons, since our overarching purpose was to demonstrate the extent of this issue across multiple behavioral measures and self-report symptoms.
+Any one of these correlations considered individually can be thought of as emulating a conventional analysis where fewer statistical tests would be performed.
+
+\subsection*{Literature Review}
+
+To characterize common data screening practices in online computational psychiatry studies, we performed a narrative literature review \cite{grant2009typology}.
+We identified studies for inclusion through searches on Google Scholar using permutations of query terms related to online labor platforms (e.g., ``mechanical turk", ``prolific", ``online"), experimental paradigms (e.g., ``experiment", ``cognitive control", ``reinforcement learning"), and symptom measures (e.g., ``psychiatry", ``mental illness", ``depression").
+We note that it was not feasible to conduct a systematic review, which requires the use of a publication database with reproducible search, because we required Google Scholar's full-text search in order to identify papers by recruitment method (e.g., Mechanical Turk).
+We included in the review studies that (a) recruited participants online through a labor platform, (b) measured behavior on at least one experimental task, and (c) measured responses on at least one self-report symptom measure.
+Through this approach, we identified for inclusion 49 studies spanning 2015 through 2020.
+The complete list of studies, and search terms used to find them, are included in the Github repository for this study.
+
+Two of the authors (S.Z., D.B.) then evaluated whether and how each of these studies performed data quality screening for both the collected task and self-report data.
+Specifically, we confirmed whether a study had performed a particular type of data screening, with screening categories determined based on previous taxonomies of screening methods (e.g., \cite{curran2016methods}).
+In addition, we assessed the total number of screening measures each study used and if monetary bonuses were paid to participants.
+This review was not meant to be systematic, but instead to provide a representative overview of common practices in online behavioral studies.
+
+\section*{Data availability}
+
+The data that support the findings of this study are openly available on Github at \url{https://github.com/nivlab/sciops}.
+
+\section*{Code availability}
+
+All code for data cleaning and analysis associated with this study is available at \url{https://github.com/nivlab/sciops}.
+The experiment code is available at the same link.
+The custom web-software for serving online experiments is available at \url{https://github.com/nivlab/nivturk}.
+
+\section*{Acknowledgements}
+
+The authors are grateful to Agnes Norbury, Alexandra Pike, and Oliver Robinson for helpful discussion.
+The research reported in this manuscript was supported in part by the National Institute of Mental Health (NIMH) under award number 5R01MH119511-02 (YN), and by the National Center for Advancing Translational Sciences (NCATS), a component of the National Institute of Health (NIH), under award number UL1TR003017 (YN).
+The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.
+SZ was supported by an NSF Graduate Research Fellowship.
+DB was supported by an Early Career Fellowship from the Australian National Health and Medical Research Council (\#1165010).
+The funders had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
+
+\section*{Author Contributions Statement}
+
+\textbf{Samuel Zorowitz:} Conceptualization (equal); Software development (lead); Formal analysis (lead); Writing - Original Draft (lead); Writing - Review \& Editing (supporting); Visualization (lead).
+\textbf{Johanne Solis:} Software development (supporting); Writing - Review \& Editing (supporting).
+\textbf{Yael Niv:} Writing - Review \& Editing (equal); Funding acquisition.
+\textbf{Daniel Bennett:} Conceptualization (equal); Software development (supporting); Formal analysis (supporting); Writing - Review \& Editing (equal); Visualization (supporting).
+
+\section*{Competing Interests Statement}
+
+The authors declare no competing interests.
+
+\clearpage
+\section*{Tables}
+
+\begin{table}[h]
     \centering
@@
 
-\subsection{Careless participants appear symptomatic when the overall level of symptom endorsement is low}
-
-To measure the correspondence of screening measures estimated from task and self-report behavior, we conducted an online behavioral experiment involving a simple decision-making task and a battery of commonly used self-report psychiatric symptom measures (see Methods).
-A final sample of 386 participants from the Amazon Mechanical Turk (N=186) and Prolific (N=200) online labour markets completed a probabilistic reversal-learning task and 5 self-report symptom measures.
-The reversal-learning task required participants to learn through trial-and-error which of three options yielded reward most often, and was modeled after similar tasks used to probe reinforcement-learning deficits in psychiatric disorders \cite{waltz2007probabilistic, mukherjee_reward_2020}.
-The five self-report measures were the 7-up (which measures symptoms of hypomania), the 7-down (which measures symptoms of depression), the GAD-7, (which measures generalized anxiety symptoms), the BIS/BAS (which measures reward and punishment motivations), the SHAPS (which measures anhedonia symptoms), and the PSWQ (which measures worry symptoms), and were chosen based on previous literature to have a variety of expected response distributions (symmetric and asymmetric).
-In line with current best-practice recommendations in personality psychology \cite{huang2015detecting}, each self-report instrument included one `infrequency' item that could be used to identify C/IE responses in survey data (see Methods for a list of infrequency items).
-The entire experiment (surveys and task) was designed to require 10 minutes on average to complete (observed mean = 10.28 minutes).
-To minimize any influence of fatigue on survey responding, participants completed the surveys prior to beginning the task.
-
-To assess the overall quality of the data, we examined the number of participants flagged by the choice accuracy and infrequency item screening measures.
-Only 26 participants (7\%) were flagged as exhibiting choice behavior at or below statistically chance levels in the reversal-learning task.
-In contrast, 85 participants (22\%) endorsed a logically invalid or improbable response on one or more of the infrequency items when completing the self-report symptom measures.
-This discrepancy in the proportion of participants flagged by each method is consistent with previous research, which found varying levels of sensitivity to C/IE responding across screening methods \cite{desimone2018dirty}.
-The proportion of participants flagged for C/IE responding was marginally but significantly greater on Mechanical Turk compared to Prolific for both task (MTurk: N=18/186; Prolific: N=8/200; $z=2.22, p=0.026$) and survey data (MTurk: 50/186; Prolific: 35/200; $z = 2.22, p = 0.026$).
-
-\begin{figure}[t!]
-\includegraphics[width=16cm]{../figures/main_02a.png}
-\centering
-\captionsetup{width=0.88\textwidth}
-\caption{Raincloud plots of total symptom scores in attentive (red) and C/IE (blue) participants.
-Each colored dot represents the symptom score for one participant.
-Black circles: average score within each group (error bars denote 95\% bootstrap confidence interval).
-Shaded plots: estimated distribution of responses for each group of participants.
-The scales are ordered approximately according to their estimated skew (see Table 2) from top-left (7-up) to bottom-right (PSWQ).
-The average level of symptom endorsement is most markedly different between groups in measures with lowest overall rates of endorsement.}
-\label{fig:distributions}
-\end{figure}
-
-We hypothesise that spurious behavior-symptom correlations may emerge due to a mean-shift in the average level of symptom endorsement in participants engaging in C/IE responding relative to attentive participants.
-In turn, a mean-shift is expected to occur when the overall rate of symptom endorsement is low; \hl{that is, comparably higher scores are more likely for C/IE participants responding at random on a right skewed questionnaire.} In line with our predictions, the average level of symptom endorsement was noticeably exaggerated in C/IE-responding participants for the symptom measures where symptom scores were most positively-skewed (7-up, 7-down, GAD-7; see Figure \ref{fig:distributions}).
-In contrast, where there was higher rates of symptom endorsement overall, the distributions of symptom scores between the two groups of participants were less noticeably distinct.
-Permutation testing confirmed that observed mean-shifts in symptom scores for C/IE participants were statistically significant for the majority of symptom measures (Table \ref{tab:validation}).
-
-\begin{table}[!t]
+\clearpage
+\begin{table}[h]
     \centering
@@
 
-Hereafter, we use the infrequency-item method as a primary means of identifying C/IE responding in our data.
-To verify this approach, we conducted three validation analyses.
-The first analysis compared estimated internal consistency of self-report measures between the C/IE and attentive groups.
-The logic is that, if C/IE responding manifests as a tendency to respond randomly, we should expect to see a decrease in the consistency of a measure in the C/IE responding group \cite{maniaci2014caring, desimone2018dirty, desimone2018differential}.
-In line with this reasoning, we observed a reduction in Cronbach's $\alpha$ in the C/IE group for the majority of survey instruments (Table \ref{tab:validation}).
-A permutation test confirmed that the average decrease in internal consistency across measures was greater than would be expected by chance given the difference in participant numbers between groups ($t = 3.69, p = 0.021$).
-
-Second, we quantified the degree to which participants responded to self-report symptom surveys in a stereotyped fashion; that is, we determined if participants exhibited patterns in their responses that were independent of the contents of the survey items.
-We fit a random-intercept item factor-analysis model \cite{maydeu2006random} to self-report data (see Methods), and for each participant we estimated an intercept parameter that quantified their bias towards using responses on the left or right side of the response scale, regardless of what that response signifies for a particular self-report measure (e.g., low on one symptom scale versus high on another).
-We observed a credible difference between the average value of this intercept for the two groups ($\Delta \text{intercept} = 0.67, 95\% \ \text{HDI} = [-0.78, -0.55]$), such that C/IE participants were biased towards using the right-half of survey response options.
-This translates to a tendency to endorse \emph{more severe} symptoms on the 7-up/7-down and GAD-7 scales (where the rightmost options indicate greater frequency of symptoms) but \emph{less extreme} symptoms or \hl{personality traits on the SHAPS and BIS (where the rightmost options indicate lower frequency of symptoms or personality traits)} despite these inventories measuring strongly correlated constructs (i.e.
-depression and anhedonia, anxiety and behavioral inhibition).
-
-Finally, we compared the proportion of participants meeting the cutoff for clinical levels of psychopathology before and after excluding participants based on their responses to the infrequency items.
-Previous studies have found that applying such measures reduced the prevalence of clinical symptomology in online samples towards ground truth rates from epidemiological studies \cite{ophir2020turker}.
-On the most positively-skewed measures, the fraction of participants reaching clinical levels of symptom endorsement prior to screening was greater than what would be expected (Table \ref{tab:validation}).
-For example, 13.0\% of participants scored at or above clinical thresholds for (hypo)mania on the 7-up scale in our sample prior to screening, compared with a 12-month prevalence of 5\% in the general population \cite{merikangas2007lifetime, merikangas2012true}, but this rate was reduced to 4.0\% (in line with the population prevalence estimates) after exclusion of C/IE respondents.
-We observed a similar pattern for both major depressive disorder and anxiety\footnote{Interestingly, compared to previous literature the proportion of participants meeting threshold on the GAD-7 was elevated.
-We suspect this may reflect elevated rates of state anxiety during the COVID-19 pandemic \cite{yarrington2021impact}, when these data were collected.} (population prevalence estimates of 7\% and 5\% respectively; \cite{kessler2012twelve, lowe2008validation, hinz2017psychometric}).
-In line with previous research, we interpret these inflated rates of clinical symptomology in our sample prior to screening as suggestive of C/IE responding \cite{ophir2020turker}.
-
-\subsection{Low correspondence between task and self-report measures of C/IE responding}
-
-Next, we evaluated the degree of correspondence between behavioral and self-report screening measures in order to determine whether screening on behavior alone was sufficient to identify and remove careless participants.
-In line with the literature review, we computed multiple measures of C/IE responding from each participant's task behavior and survey responses (see Methods for description of measures).
-To measure the degree of correspondence between these behavioral and self-report screening measures, we performed two complementary analyses.
-First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation.
-The resulting pairwise similarity matrices are presented in Figure \ref{fig:correspondence} (left panel).
-After correcting for multiple comparisons, there were few significant correlations between the behavioral and self-report screening measures.
-Only choice accuracy showed significant associations with any self-report measure (specifically, the infrequency and Mahalonobis distance measures).
-Crucially, the sizes of these observed correlations were roughly half those observed for the correlations between the self-report measures.
-This is worrisome as it suggests that, although there is some relationship between C/IE responding on tasks and self-report inventories, the relationship is not strong enough to ensure reliable detection of careless participants using task data alone.
-
-\begin{figure}[!t]
-\includegraphics[width=16cm, trim=0 0 3cm 0]{../figures/main_02b.png}
+\clearpage
+\section*{Figures}
+
+\begin{figure}[h]
+    % \includegraphics[width=16cm]{../figures/main_01.png}
+    \centering
+    \captionsetup{width=0.88\textwidth}
+    \caption{Simulated example of how spurious behavior-symptom correlations can arise when symptom endorsement is rare.
+\textit{Left:} When symptoms are moderately common in the general population, C/IE respondents (blue) are indistinguishable from attentive participants (red) in self-report measures (x-axis, marginal distribution shown on top).
+Despite the lower task performance of C/IE respondents (y-axis), no correlation arises between symptom scores and task performance (dots are participants drawn from the shown distributions, with 15\% C/IE participants; dashed line shows the (lack of) correlation.) \textit{Right:} When symptoms are rare in the general population, careless respondents appear symptomatic in self-report measures.
+As a result, self-report symptom scores show a significant correlation with task performance.}
+    \label{fig:simulation}
+\end{figure}
+
+\clearpage
+\begin{figure}[h]
+    % \includegraphics[width=16cm]{../figures/main_02a.png}
+    \centering
+    \captionsetup{width=0.88\textwidth}
+    \caption{Raincloud plots of total symptom scores in attentive (red) and C/IE (blue) participants.
+Each colored dot represents the symptom score for one participant.
+Black circles: average score within each group (error bars denote 95\% bootstrap confidence interval).
+Shaded plots: estimated distribution of responses for each group of participants.
+The scales are ordered approximately according to their estimated skew (see Table 2) from top-left (7-up) to bottom-right (PSWQ).
+The average level of symptom endorsement is most markedly different between groups in measures with lowest overall rates of endorsement.}
+    \label{fig:distributions}
+\end{figure}
+
+\clearpage
+\begin{figure}[h]
+    % \includegraphics[width=16cm, trim=0 0 3cm 0]{../figures/main_02b.png}
     \centering
@@
 
-Second, we used the Dice similarity coefficient to quantify agreement between different screening methods in the set of participants flagged for exclusion (Figure \ref{fig:correspondence}, right panel).
-This approach quantifies the degree of overlap between the set of would-be excluded participants based on different screening measures under a common exclusion rate.
-Though some measures have relatively clear threshold cutoffs (e.g., chance level performance for task accuracy), the majority of the measures evaluated here do not.
-As such, we evaluated the measures with respect to the top 10\% of ``suspect" participants flagged by each measure, corresponding roughly to the fraction of participants having performed at chance levels on the reversal-learning task.\footnote{Results of the same analysis repeated for the top 25\% of ``suspicious" participants (corresponding roughly to the fraction of participants flagged by the infrequency-item measure) produced similar results, and are included in the supplement.} Results were largely consistent with the correlation analysis: few pairs of task and self-report screening measures achieved levels of agreement greater than what would be expected by chance.
-The only significant cross-modality pair identified --- between the infrequency item and choice accuracy measures --- has a similarly coefficient less than 0.4.
-In other words, when these two measures are used to identify the top 10\% of participants most strongly suspected of C/IE responding, they agree on only two out of every five participants.
-Screening on choice accuracy alone (the most common method identified in our literature review) would fail to identify the majority of participants most likely engaging in C/IE responding as determined by the infrequency items.
-
-Taken together, these results suggest that measures of C/IE responding in task and self-report data do not identify the same set of participants.
-This means that solely excluding participants on the basis of poor behavioral performance---the most common approach in online studies---is unlikely to identify participants who engage in C/IE responding on self-report surveys.
-
-\subsection{Spurious symptom-behavior correlations produced by C/IE responding}
-
-Here we examine the potential consequences of screening only on task behavior in our data.
-To do this, we estimated the pairwise correlations between the symptom scores of each of the self-report measures and several measures of performance on the reversal learning task.
-This analysis emulated a typical computational psychiatry analysis, in which the results of primary interest are the correlations between task behavior and self-reported psychiatric symptom severity.
-
-For each participant, we computed both descriptive and computational-model-based measures of behavior on the reversal learning task (see Methods).
-To understand the effects of applying different forms of screening, we estimated the correlations between each unique pairing of a self-report symptom measure and measure of behavior under four different conditions: no screening, screening only on task behavior (i.e.
-only participants whose choice accuracy was above chance), screening only on self-report responses (i.e.
-only participants who responded correctly on all infrequency items), or both.
-The resulting pairwise behavior-symptom correlations following each screening procedure are presented in Figure \ref{fig:correlations}.
-We note that we did not correct these correlation analyses for multiple comparisons, since our purpose was to demonstrate the extent of this issue across multiple behavioral measures and self-report symptoms.
-Any one of these correlations considered individually can be thought of as emulating a conventional analysis where fewer statistical tests would be performed.
-
-\begin{figure}[!t]
-\includegraphics[width=17cm]{../figures/main_03a.png}
+\clearpage
+\begin{figure}[h]
+    % \includegraphics[width=17cm]{../figures/main_03a.png}
     \centering
@@
     \caption{Absolute Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions.
-Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons; \hl{all signed correlations are shown in Supplementary Figure} \ref{fig:correlations_s1}).
+Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons; all signed correlations are shown in Supplementary Figure \ref{fig:correlations_s1}).
 Black Xs indicate significant correlations ablated under screening.
@@
 
-When no rejections based on C/IE responding was applied (i.e.
-all participants were included in the analysis; Figure \ref{fig:correlations}A), many significant correlations emerged between measures of task behavior and symptom scores, in particular for 4 of the self-report instruments (7-up, which measures symptoms of hypomania; 7-down, which measures symptoms of depression; GAD-7, which measures generalized anxiety symptoms; and BIS, which measures tendencies related to behavioral inhibition).
-Consistent with our predictions, the majority of these correlations involved symptom measures with asymmetric total score distributions.
-Attending to only the most skewed measures (i.e.
-7-up, 7-down, GAD-7), symptom endorsement was correlated with almost every behavioral measure.
-That is, significant correlations were not restricted only to general behavioral measures often used as proxies for participant effort (e.g.
-accuracy, inverse temperature $\beta$) but also to measures of specific theoretical interest, such as asymmetry of learning from positive and negative reward prediction errors ($\kappa$).
-Conversely, we found few significant correlations among symptom measures with more symmetric distributions.
-This is despite the fact these scales measure similar symptoms and syndromes (e.g.
-anxiety as measured by the GAD-7 and worry as measured by the PSWQ; depression as measured by the 7-down and anhedonia as measured by the SHAPS).
-
-Next, we excluded participants from analysis based on task-behavior screening (i.e.
-choice accuracy, removing the 7\% of participants exhibiting behavior indistinguishable from chance; Figure \ref{fig:correlations}B).
-The pattern of correlations was largely unchanged: we again found many significant correlations between measures of behavior and asymmetric symptom measures, but almost no significant correlations involving symmetric symptom measures.
-This suggests that rejection of participants based on the most common form of behavioral screening (i.e.
-performance accuracy) had little effect on behavior-symptom correlations as compared to no screening.
-
-In stark contrast, when we rejected participants based on self-report screening  (removing 22\% of participants who endorsed one or more invalid or improbable responses on the infrequency items; Figure \ref{fig:correlations}C), the number of significant correlations was markedly reduced, particularly for several of the most skewed symptom measures (7-down, GAD-7) and proxy measures of task attentiveness (e.g.
-accuracy, inverse temperature).
-This pattern of correlations was largely similar when rejections were applied based on both task and self-report screening measures (Figure \ref{fig:correlations}D).
-We also note that with stricter screening, the remaining significant correlations were, for the most part (but not always), weaker.
-
-These findings suggest that many of the significant behavior-symptom correlations observed without strict participant screening may indeed be spurious correlations driven by C/IE responding.
-Importantly, screening based on task behavior alone did not adequately protect against spurious symptom-behavior correlations in the presence of skewed distributions of symptom endorsement.
-For instance, consider the 7-down scale, a measure of trait depression: had we not screened participants based on infrequency items, we would have erroneously concluded that there were many significant associations between reversal-learning task performance and self-reported depression.
-Screening on self-report data allowed us to identify that each of these depression-behavior correlations was likely to be entirely spurious.
-
-One possible objection to this interpretation is that the reduction in significant correlations following self-report screening was a result of the reduced sample size after removal of C/IE respondents (which comprised over 20\% of the sample).
-To test this alternative hypothesis, we performed the same correlation analysis after removing random subsets of participants, fixing the sample size to that obtained after excluding C/IE respondents.
-In this case, the pattern of significant correlations was more similar to that before screening than after screening using the infrequency measure (t = 262.49, $p < 0.001$; Figure \ref{fig:random}, compare to Figure \ref{fig:correlations}A).
-Thus, the reduction in significant correlations following screening was unlikely to be driven solely by a reduction in statistical power.
-
-Next, we investigated how spurious correlations depended on sample size.
-To do so, we performed a bootstrapping analysis where we held fixed the proportion of participants engaging in C/IE responding (i.e.
-5\%, 10\%, 15\%, 20\%) and increased the total number of participants.
-Across all analyses, we measured the correlation and between the 7-down depression scale and learning-rate asymmetry ($\kappa$), which we previously identified as likely exhibiting a spurious association.
-(\hl{The following results are not specific to learning-rate asymmetry and generalize to other pairs of variables; Figure} \ref{fig:bootstrap_s1}).
-
-The outputs of the bootstrapping analysis are presented in Figure \ref{fig:bootstrap}.
-We found that, although estimated correlation magnitudes were independent of sample size (x-axis, left panel), the absolute magnitude of the behavior-symptom correlation increased with the proportion of C/IE participants (different coloured circles, left panel).
-Crucially, we found false-positive rates for spurious correlations \emph{increased} with increases in sample size in our data for all but the smallest rates of C/IE responding (right panel).
-This runs counter to a common assumption that larger sample sizes are protective against spurious correlations because they serve to mitigate measurement error.
-Although this assumption is correct for unsystematic measurement error, it no longer holds in the regime of systematic measurement error (where larger sample sizes reduce the variance of estimates, but do not alter their bias).
-Instead, our results suggest that, \hl{except for low rates of C/IE responding}, the false-positive rate for behavioral-symptom correlations will become increasingly inflated as the sample size increases.
-
-\begin{figure}[!t]
-\includegraphics[width=16cm]{../figures/main_03b.png}
+\clearpage
+\begin{figure}[h]
+    % \includegraphics[width=16cm]{../figures/main_03b.png}
     \centering
@@
 
-\subsection{\texorpdfstring{\hl{Pattern of results generalizes to alternative tasks, self-report measures, and quality assurance protocols}}{}}
-
-One possible concern with the results presented so far is that they are specific to one instantiation of our experimental design.
-With more stringent quality assurance protocols during participant recruitment, or perhaps a different task or set of self-report measures, one might wonder if spurious correlations would remain such a threat.
-
-To evaluate the generalizability of our findings, we therefore conducted a conceptual replication experiment in which an independent sample of N=393 participants (N=193 from MTurk using CloudResearch, N=200 from Prolific) completed a more difficult cognitive task, the well-known ``two-step task'' \cite{daw2011model}, and an alternate set of self-report measures (see Appendix B for details).
-Importantly, participants were recruited \textit{after} CloudResearch and Prolific implemented new protocols to improve data quality on their respective platforms.
-As a final control measure, participants completed self-report symptom measures as before, but also personality measures with no hypothesized relationship to model-based planning behavior on the two-step task.
-
-For the sake of brevity, we report here only the main pattern of findings (all results are reported in Appendix B).
-In the replication sample, 55 out of 393 participants (14\%) endorsed a logically invalid or improbable response on one or more of the infrequency items when completing the self-report measures.
-This is roughly two-thirds of the number of participants who were flagged for C/IE responding in the original study, suggesting that the newer quality assurance protocols used by the online platforms are at least partially effective.
-
-In the self-report symptom measures, we replicated the finding that total scores were noticeably exaggerated in participants suspected of C/IE responding, but only for symptom measures where overall rates of symptom endorsement were the lowest.
-Similarly, we again found that task-based screening and self-report screening measures showed low correspondence; that is, excluding participants on the basis of poor behavioral performance would not have identified and removed participants who engaged in C/IE responding on self-report surveys.
-
-Finally, when we did not apply any exclusions, we observed spurious correlations between performance on the two-step task and total scores for both symptom and personality self-report measures with a mean-shift in scores between attentive participants and participants suspected of C/IE responding.
-In contrast with our original findings, however, we found that excluding participants based on self-report \textit{or} task screening measures was sufficient to ablate these spurious correlations.
-
-In sum, we replicated most of the main findings from the original study in an independent sample of participants completing a different task and other self-report measures.
-Although we found that screening on task behavior was sufficient to protect against spurious correlations in the replication sample, it is difficult to generalize and predict when or why this might be the case for other datasets.
-As such, we still believe that screening for C/IE responding in both task and self-report measures is the best approach to protect oneself against the possibility of spurious correlations.
-
-\subsection{\texorpdfstring{\hl{Individuals with and without diagnosed psychiatric disorders fail attention checks at similar rates}}{}}
-
-One major concern with performing rigorous screening and exclusion of participants based on C/IE detection methods is that we might inadvertently introduce an overcontrol bias \cite{elwert2014endogenous}.
-That is, to this point we have treated the tendency towards C/IE responding as independent from psychopathology.
-However, to the extent that C/IE responding reflects lack of motivation \cite{barch2015mechanisms}, avoidance of effort \cite{cohen2001impairments, culbreth2016negative}, or more frequent lapses of attention \cite{kane2016individual, robison2017neurotic}, one might hypothesise a true underlying association between psychopathology and careless responding in online studies.
-It is thus plausible that rigorous screening of C/IE responding might lead to the differential exclusion of truly symptomatic participants.
-
-To explore this possibility, we embedded attention checks into the self-report measures of two studies of patients with major depressive disorder (see Appendix C for details).
-Specifically, N=45 psychiatric patients (confirmed to meet criteria for a diagnosis of major depressive disorder through a structured clinical interview) and N=20 healthy controls, all recruited through the Rutgers-Princeton Center for Computational Cognitive Neuropsychiatry (i.e., personal recruitment, not on online labour platforms), completed a series of self-report symptom measures, online, on their computers from the comfort of their homes.
-In total, 16 of 65 (24.6\%) participants failed one or more attention checks.
-Subdivided by group, 6 of 20 (30\%) healthy participants and 10 of 45 (22\%) psychiatric participants were flagged for C/IE responding.
-
-Using these data, we computed pairwise Bayes factors comparing three candidate models: attention check failure rates are equal between healthy and psychiatric participants (M1); failure rates are greater in psychiatric patients (M2); and failure rates are greater in healthy participants (M3).
-The model assuming equal rates of failure between healthy and psychiatric participants was 2.88 times more likely than the model assuming greater rates for psychiatric patients.
-In turn, the model assuming lower rates of failure for psychiatric patients was 1.27 times more likely than the model assuming equal rates.
-Finally, the model assuming lower rates of failure for psychiatric patients was 3.65 times more likely than the model assuming higher rates for psychiatric patients.
-Only the final comparison exceeds the cutoff value of 3, which is conventionally treated as the minimal amount of evidence required to treat a difference in model fit as meaningful.
-Although the size of the sample precludes any definitive conclusion, it is noteworthy that the model least consistent with the data was the one where psychiatric patients are more likely to fail infrequency item attention checks.
-These data suggest, therefore, that it is unlikely that individuals with high psychiatric symptom severity were disproportionately flagged for C/IE responding in the main analyses.
-Accordingly, we conclude that the screening measures we are suggesting are not likely to result in overcontrol bias and false-negative correlations between tasks and symptom measures.
-
-\section{Discussion}
-
-In this manuscript, we highlighted a particular set of circumstances, common in computational psychiatry research done on large online samples, in which spurious correlations may arise between task behavior and self-reported symptomology.
-When the ground-truth prevalence of a symptom is low in the general population, participants who respond carelessly on measures assessing this symptom may erroneously appear as symptomatic.
-A less careful pattern of responding on tasks used to measure cognitive constructs can then masquerade as a correlation between alteration in these constructs and symptom dimensions.
-We found repeated evidence for this pernicious pattern in participants recruited from two popular online labour platforms.
-False-positive rates for these spurious correlations \emph{increased} with sample size, because the correlations are due to measurement bias, not measurement noise.
-Importantly, we found that screening on task behavior alone was insufficient to identify participants engaging in C/IE responding and avoid the false-positive correlations.
-Unfortunately, a literature review identified this type of screening as the most common practice in online computational psychiatry studies.
-We recommend instead to screen and exclude participants based on responding on surveys, a practice that abolished many spurious behavior-symptom correlations in our data.
-
-One way of conceptualizing our results is through the lens of rational allocation of mental effort \cite{kool2018mental}.
-In any experiment, attentive responding is more effortful than careless responding.
-As such, participants completing an online task must perform a cost-benefit analysis---implicitly or otherwise---to decide how much effort to exert in responding.
-The variables that factor into such calculations are presumably manifold and likely include features of the experiment (e.g., task difficulty, monetary incentives), facets of the participant (e.g., subjective effort costs, intrinsic motivation, conscientiousness), and features of the online labour market itself (e.g., opportunity costs, repercussions for careless responding).
-
-Viewed from the perspective of effort expenditure, our results suggest that participants appraised the cost/benefit trade-off differently for behavioral tasks and self-report surveys.
-Specifically, we found that only 7\% of participants were at chance-level performance in our task, compared to more than 22\% of participants who failed one or more attention-check items in the self-report surveys \hl{(a finding that qualitatively replicated in a second study involving a different task)}.
-Moreover, different measures of C/IE responding were weakly or not at all correlated between task behavior and self-report responses.
-This suggests the motivation for effortful responding was greater in the behavioral task, though precisely why is unclear.
-One possibility is that we gave participants a monetary incentive for attentive responding only during the task (a common practice, according to our literature review).
-A second possibility is that participants expected fewer consequences for C/IE responding during the self-report surveys, a reasonable assumption in light of how infrequently previous experiments have screened self-report data.
-Alternatively, participants may have found the gamified behavioral task more engaging or the self-report inventory more tedious.
-Regardless of the reason, this discrepancy reinforces our observations concerning the inadequacy of behavioral-task screening as a stand-alone method for identifying C/IE responding.
-Since, in general, participants may appraise costs and benefits of effortful responding differently for behavioral tasks and self-report surveys, screening for C/IE responding on one data modality may in general be unsuitable for identifying it in the other.
-We therefore recommend screening on each component of an experiment.
-
-One complicating factor for our argument is that C/IE responding may manifest in other ways than simply random responding for both behavioral tasks and self-report surveys.
-Indeed, there are more ways to respond carelessly than to respond attentively to a task or self-report inventory (e.g., random response selection, straight-lining, zig-zagging, acquiescence bias) \cite{curran2016methods}.
-The specific response strategy a participant adopts is likely to reflect the idiosyncratic integration of multiple perceived benefits (e.g.
-time saved, effort avoided) and costs (e.g.
-loss of performance bonuses, risk of detection and pay forfeited).
-As has been previously documented \cite{desimone2018dirty}, the presence of multiple response strategies makes it clear why certain screening measures are more or less likely to correlate.
-For example, the inter-item standard deviation and personal reliability measures are both sensitive to statistically random responding, but less sensitive to straight-lining.
-Most importantly, a diversity of heuristic response strategies highlights the need for many screening measures of C/IE responding, each sensitive to different heuristic strategies.
-
-Here we have focused on the potential for C/IE responding to result in spurious symptom-behavior correlations when rates of symptom endorsement are low, a case common to online computational psychiatry research.
-Beyond this, we should emphasize that a diversity of heuristic response strategies entails that there is more than one mechanism by which spurious correlations can emerge.
-To the extent that the only prerequisite is a mean-shift between attentive and careless participants, ours is not the only situation where one might expect spurious correlations to emerge \cite{huang2015insufficient}.
-For example, random responding on items with \emph{high} base-rate endorsement could yield spurious correlations with precisely the opposite pattern observed here.
-Conversely, straight-lining may actually suppress correlations when symptom endorsement is low.
-In sum, without more understanding about the various types of heuristic responding and when each is likely to occur in a sample, it is difficult to predict {\it a priori} the patterns of systematic bias that may arise for a given study.
-This is further impetus for experimenters to be wary of C/IE responding and to use a variety of screening measures to detect it.
-
-One objection to the rigorous screening and exclusion of participants based on C/IE detection methods is that we might inadvertently introduce an overcontrol bias.
-That is, to the extent that C/IE responding might reflect symptoms common to psychopathology (e.g.
-low motivation, effort avoidance, inattentiveness), rigorous screening of C/IE responding might lead to the differential exclusion of truly symptomatic participants.
-\hl{To explore this possibility, we embedded attention checks into the self-report measures of two studies of patients with major depressive disorder.
-Though our final sample was small, we did not find evidence for the proposition that patients were more likely to fail attention checks than healthy controls (if anything, non-psychiatric participants were more likely to be flagged by C/IE screening).
-These results provide preliminary evidence that rigorous C/IE screening is unlikely to result in overcontrol bias.}
-
-\hl{Given that the results of our patient study are preliminary and warrant further investigation, researchers might still be wary of possible overcontrol bias.} However, when using self-report questionnaires for screening, for overcontrol to seriously impact results it would have to be the case that symptomatic participants frequently endorse improbable or impossible responses to infrequency-item checks (e.g., responding `Agree' to ``I competed in the 1917 Olympic Games").
-In this case, and even if such participants truly are experiencing severe symptoms of motivation or attention, there is likely to be limited utility in measuring these symptoms using a self-report measure that they are unable to complete veridically.
-A similar rationale underlies the widespread use of semi-structured interviews and other clinician-report measures rather than self-report measures for in-clinic psychiatric research.
-We would therefore argue that, if the psychiatric phenomenon being studied is such that this issue warrants concern, the research question may be better suited to an in-person study design involving participants in the clinic who meet full diagnostic criteria than a correlational design involving an online convenience sample.
-
-Notwithstanding the above, one response to this legitimate concern is to take a graded approach to screening and excluding participants \cite{Kim2018-ev}.
-That is, participants could be screened with respect to a multitude of measures and only the consistently flagged participants be removed, thereby reducing the risk of inducing bias.
-Another possibility is to use sensitivity analysis as an alternative to exclusion, testing whether full-sample observed correlations are robust to the exclusion of participants flagged by measures of C/IE responding.
-We note that the strict screening approach used in the present study did not preclude us from identifying symptomatic participants or behavior-symptom correlations.
-Indeed, we found in our sample roughly 10\% of participants endorsing symptoms consistent with clinical levels of depression, and approximately 20\% consistent with clinical levels of acute anxiety.
-These estimates are within the realm of epidemiological norms \cite{kessler2012twelve, lowe2008validation, yarrington2021impact}.
-\hl{(We should note, however, that some studies have found elevated rates of psychiatric symptomology in online participants even after controlling for C/IE responding} \cite{ophir2020turker}.) We also observed some positive correlations between anxiety and choice behavior that were consistent with effects found in previous literature \cite{huang2017computational, harle2017anhedonia, garrett2018updating}.
-For example, we found higher lose-shift rates and higher learning rates following negative prediction errors correlated with self-reported anxiety.
-This suggests that the screening methods we employed were not so aggressive as to attenuate behavior-symptom correlations that would be expected from the literature.
-
-There are several notable limitations to this proof-of-concept study.
-We used a small set of screening measures, and did not employ other recommended procedures (e.g.
-logging each key/mouse interaction during survey administration to detect form-filling software or other forms of speeded responding \cite{buchanan2018methods}).
-Thus, we cannot be confident that all of the flagged participants were indeed engaging in C/IE responding; similarly, we cannot be certain that we correctly excluded all participants engaged in C/IE responding.
-We studied behavior-symptom correlations for only two tasks and two short self-report symptom batteries.
-It remains to be seen how generalizable our findings are, although our study design was inspired by experiments prevalent in the online computational psychiatry literature.
-As suggested above, future studies may find greater correspondence between task and self-report screening measures for more difficult behavioral experiments.
-Finally, we should note that, unlike previous studies in which some participants were explicitly instructed to respond carelessly \cite{buchanan2018methods}, we do not have access to ``ground truth'' regarding which participants were engaging in C/IE responding.
-Future work testing the efficacy of different screening metrics for identifying instructed C/IE responding may help to identify some of the issues that we have identified here.
-
-The present study highlights the need for future work on the prevalence of C/IE responding in online samples and its interactions with task-symptom correlations.
-Many open questions remain, including under what conditions task- and symptom-screening measures might better correspond, what screening measures are most effective and when, and under what conditions spurious correlations are more likely to arise.
-One especially pressing question is how sample size affects the likelihood of obtaining spurious correlations.
-The results of a bootstrapping analysis in our data suggest that false positive rates are likely to increase with sample size.
-As computational psychiatry studies move towards larger samples to characterize heterogeneity in symptoms (and to increase statistical power), it will be important to understand how sample size may exaggerate the effects of systematic error.
-
-\section{Conclusions}
-
-Moving forward, we would strongly recommend that experimenters employ some form of self-report screening method, preferably one recommended by the best-practices literature (see Box 1 for a list of concrete recommendations).
-Our literature review found that, to date, the majority of online studies assessing behavior-symptom correlations have not used self-report screening, and our results demonstrate that stand-alone task-behavior screening is likely to be insufficient.
-Our results also demonstrate that inadequate screening is likely not merely to result in increased measurement error, as commonly assumed, but may also induce spurious correlations between behavioral task metrics and self-reported psychiatric symptom levels.
-For these reasons, we encourage experimenters to use a variety of data-quality checks for online studies and to be transparent in their reporting of how screening was conducted, how many participants are flagged under each measure, and what thresholds are used for rejection.
-
-More broadly, we encourage experimenters in computational psychiatry to be mindful of the myriad reasons why participants may perform worse on a behavioral task.
-Wherever possible, researchers are encouraged to design experiments where the signature of some symptomology could not also be explained by C/IE responding (e.g.
-\cite{eldar2015interaction, hunter2019excessive}).
-Finally, we conclude by noting that it is preferable to prevent C/IE responding than to account for it after the fact \cite{ward2018applying}.
-As such, we recommend researchers take pains to ensure their experiments promote engagement, minimize fatigue and confusion, and reimburse participants fairly and ethically.
-
-%% BOX 1 %%
-\newpage
-\textbf{Box 1: Recommendations for future research}
-
-Here we offer several concrete recommendations for future research investigating symptom-behavior correlations in online samples.
-
-\begin{itemize}
-
-    \item Use multiple screening methods to detect different types of C/IE responding.
-At a minimum, we recommend screening of both behavioral and self-report data.
-Within self-report data, we recommend using methods sensitive to multiple distinct patterns of C/IE responding (e.g., random responding, straight-lining, side bias) and, if possible, to log all page interactions (e.g., mouse clicks, keyboard presses).
-
-    \item When collecting self-report questionnaire data, include attention-check items that flag participants who may be engaging in C/IE responding.
-We recommend following best-practice guidelines in using infrequency-item checks rather than instructed-item checks, \hl{as multiple studies have now shown that online participants are habituated to and circumvent the latter} \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}.
-Participants flagged by suspicious responses on attention-check items should either be excluded from further analysis, or assessed using sensitivity analyses to ensure that observed full-sample correlations are robust to their exclusion.
-
-    \item We found that spurious correlations predominantly affected self-report instruments for which the expected distributions of symptom scores were asymmetric (either positively or negatively skewed).
-As such, symmetrically-distributed measures of a given construct should be preferred to asymmetrically-distributed measures (though this will often be infeasible given that the frequency of many psychiatric symptoms in the general population is itself positively skewed).
-
-    \item Scales with reverse-coded items can be used to quantify the consistency of participants' responses between reverse-coded and non-reverse-coded measures of the same latent construct.
-With some care, this may be used to identify C/IE responding even for measures that do not include attention-check items \cite{emons2009detection}.
-Similarly, it may be beneficial to include multiple self-report surveys of the same construct to measure consistency across scales.
-
-    \item In our experience, we have found it instructive to review discussions on public forums for participants of online labour markets (e.g.
-Reddit, TurkerNation).
-Doing so helps an experimenter identify what screening methods would-be participants are already aware of and prepared to answer correctly.
-(Several examples of workers discussing common attention checks can be found at the Github repository for this project.)
-
-    \item Consider carefully whether the online methodology is truly appropriate for the research question.
-In particular, if the project studies syndromes associated with considerable difficulty in task or survey engagement (e.g., severe ADHD, acute mania), symptomatic participants are likely to produce responses that cannot be distinguished from C/IE responding.
-In this case, correlational research with online samples is likely not the best methodology for the research question.
-
-\end{itemize}
-
-This is not an exhaustive list, and one overarching recommendation is that researchers studying individual differences in psychiatric symptom endorsement should engage meaningfully with methodological research from the psychological measurement literature, where many of these questions have long been studied \cite{huang2015insufficient, curran2016methods, thomas2017validity, desimone2018dirty, ophir2020turker}.
-
-\newpage
-%% END BOX 1 %%
-
-\section{Methods}
-
-All code, data, and analysis materials are publicly available at \url{https://github.com/nivlab/sciops}.
-
-\subsection{Literature Review}
-
-To characterize common data screening practices in online computational psychiatry studies, we performed a narrative literature review \cite{grant2009typology}.
-We identified studies for inclusion through searches on Google Scholar using permutations of query terms related to online labour platforms (e.g.
-``mechanical turk", ``prolific", ``online"), experimental paradigms (e.g.
-``experiment", ``cognitive control", ``reinforcement learning"), and symptom measures (e.g.
-``psychiatry", ``mental illness", ``depression").
-\hl{We note that it was not feasible to conduct a systematic review, which requires the use of a publication database with reproducible search, because we required Google Scholar's full-text search in order to identify papers by recruitment method (e.g., Mechanical Turk).} We included in the review studies that (a) recruited participants online through a labour platform, (b) measured behavior on at least one experimental task, and (c) measured responses on at least one self-report symptom measure.
-Through this approach, we identified for inclusion 49 studies spanning 2015 through 2020.
-\hl{The complete list of studies, and search terms used to find them, are included in the Github repository for this study.}
-
-Two of the authors (S.Z., D.B.) then evaluated whether and how each of these studies performed data quality screening for both the collected task and self-report data.
-Specifically, we confirmed whether a study had performed a particular type of data screening, \hl{with screening categories determined based on previous taxonomies of screening methods} (e.g.
-\cite{curran2016methods}).
-In addition, we assessed the total number of screening measures each study used and if monetary bonuses were paid to participants.
-This review was not meant to be systematic, but instead to provide a representative overview of common practices in online behavioral studies.
-
-\subsection{Experiment}
-
-\subsubsection{Sample}
-
-409 total participants were recruited to participate in an online behavioral experiment in late June - early July, 2020.
-Specifically, 208 participants were recruited from Amazon Mechanical Turk (MTurk) and 201 participants were recruited from Prolific.
-This study was approved by the Institutional Review Board of Princeton University (\#5291), and all participants provided informed consent.
-Total study duration was approximately 10 minutes per participant.
-Participants received monetary compensation for their time (rate USD \$12/hr), plus an incentive-compatible bonus up to \$0.25 based on task performance.
-
-Participants were eligible if they resided in the United States or Canada; participants from MTurk were recruited with the aid of CloudResearch services \cite{litman2017turkprime}.
-(Note: This study was conducted prior to the introduction of CloudResearch's newest data quality filters \cite{cloudresearch_2020}).
-Following recent recommendations \cite{robinson2019tapped}, MTurk workers were not excluded based on work approval rate or number of previous jobs approved.
-No other exclusion criteria were applied during recruitment.
-\hl{It is important to note that both CloudResearch and Prolific use a number of tools (e.g.
-IP-address screening) to filter out the lowest quality participants.
-In addition, our custom experiment delivery software (NivTurk; see below) has bot-checking functionality built into it, and rejects from the start participants who are likely to not be human.
-We are therefore confident that our study is not strongly affected by participants using software to automatically complete the experiment.}
-
-The data from multiple participants who completed the experiment were excluded prior to analysis.
-Three participants (all MTurk) were excluded due to missing data.
-In addition, we excluded 20 participants who disclosed that they had also completed the experiment on the other platform.
-This left a final sample of N=386 participants (MTurk: N=186, Prolific: N=200) for analysis.
-The demographics of the sample split by labour market is provided in Table S1.
-Notably, the participants recruited from MTurk were older ($M = 7.7 \ \text{yrs}, t = 6.567, p < 0.001$) and comprised of fewer women ($z = 6.567, p = 0.011$).
-
-\subsubsection{Experimental Task}
-
-Participants performed a probabilistic reversal learning task, explicitly designed to be similar to previous computational psychiatry studies \cite{waltz2007probabilistic, mukherjee_reward_2020}.
-On every trial of the task, participants were presented with three choice options and were required to choose one.
-After their choice, participants were presented with probabilistic feedback: a reward (1 point) or a non-reward (0 points).
-On any trial one choice option dominated the others.
-When chosen, the dominant option yielded reward with 80\% probability; the subordinate options yielded reward with only 20\% probability.
-The dominant option changed randomly to one of the two previously subordinate options every 15 trials.
-Participants completed 90 trials of the task (1 learning block, 5 reversal blocks).
-
-As a cover story, the probabilistic reversal learning task was introduced to participants as a fishing game in which each choice option was a beach scene made distinguishable by a colored surfboard with unique symbol.
-Participants were told they were choosing which beach to fish at.
-Feedback was presented as either a fish (1 point) or trash (0 points).
-Participants were instructed to earn the most points possible by learning (through trial-and-error) and choosing the best choice option.
-Participants were also instructed that the best option could change during the task, but were not informed about how often or when this would occur (see the Supplement for the complete instructions).
-Prior to beginning the experiment, participants had to correctly answer four comprehension questions about the instructions.
-Failing to correctly answer all items forced the participant to start the instructions over.
-
-The task was programmed in jsPsych \cite{deleeuw_2015_jspsych} and distributed using custom web-application software.
-The experiment code is available at \url{https://github.com/nivlab/sciops}, and the web-software is available at \url{https://github.com/nivlab/nivturk}.
-A playable demo of the task is available at \url{https://nivlab.github.io/jspsych-demos/tasks/3arm/experiment.html}.
-
-\subsubsection{Symptom Measures}
-
-Prior to completing the reversal learning task, participants completed five self-report symptom \hl{and personality-trait measures}.
-The symptom measures were selected for inclusion based on their frequency in clinical research, and for having an expected mixture of symmetric and asymmetric score distributions.
-
-\textbf{Seven-Up/Seven-Down.} The Seven-Up/Seven-Down (7u/7d; \cite{youngstrom_2013_susd}) scale is a 14-item measure of lifetime propensity towards depressive and hypomanic symptoms.
-It is an abbreviation of the General Behavior Inventory \cite{depue1981behavioral}, wherein only items that maximally discriminated between depression and mania were included.
-Items are scored on a 4-point scale from 0 (``Never or hardly ever") to 3 (``Very often or almost constantly").
-Total symptom scores on both subscales range from 0 to 21, and are usually strongly right-skewed, with few participants exhibiting moderate to high levels of symptom endorsement.
-
-\textbf{Generalized Anxiety Disorder-7.} the Generalized Anxiety Disorder-7 (GAD-7; \cite{spitzer2006brief}) is a 7-item measure of general anxiety.
-The GAD-7 assesses how much a respondent has been bothered by each of seven core anxiety symptoms over the last 2 weeks.
-Items are scored on a 4-point scale from 0 (``not at all") to 3 (``nearly every day").
-Total scores on the GAD-7 range from 0 to 21, and are usually right-skewed, with few participants exhibiting moderate to high levels of symptom endorsement.
-
-\textbf{Behavioral Inhibition/Behavioral Activation Scales.} the Behavioral Inhibition and Behavioral Activation Scales (BIS/BAS; \cite{carver1994behavioral}) are a measure of reward and punishment sensitivity.
-The original 42-item measure was recently abbreviated to a 14-item measure \cite{pagliaccio2016revising}, which we use here.
-Items are scored on a 4-point scale from 1 (``very true for me") to 4 (``very false for me").
-Total scores on the BAS subscale range from 8 to 32, whereas total scores on the BIS subscale range from 4 to 16.
-Previous reports have found total scores to be symmetrically distributed \cite{cooper2007behavioural}.
-Importantly, in order to maintain presentation consistency with the other symptom measures, the order of the BIS/BAS response options was reversed during administration such that ``very false for me" and ``very true for me" were the left- and rightmost anchors, respectively.
-
-\textbf{Snaith-Hamilton Pleasure Scale.} the Snaith-Hamilton Pleasure Scale is a 14-item measure of anhedonia \cite{snaith1995scale}.
-Items are scored on a 4-point scale from 0 (``strongly agree") to 3 (``strongly disagree"), where higher scores indicate greater pathology.
-Total scores on the SHAPS range from 0 to 42, and have previously been found to be somewhat right-skewed \cite{franken2007assessment, leventhal2015measuring}, with only the minority of participants exhibiting moderate to high levels of symptom endorsement.
-Importantly, as with the BIS/BAS, the order of the SHAPS response options was reversed during administration such that ``strongly disagree" and ``strongly agree" were the left- and rightmost anchors, respectively.
-
-\textbf{Penn State Worry Questionnaire.} the Penn State Worry Questionnaire is a measure of worry symptoms \cite{meyer1990development}.
-The original 16-item was recently abbreviated to a 3-item measure \cite{kertz2014psychometric}, which we use here.
-Items are scored on a 5-point scale from 0 (``not at all typical of me") to 4 (``very typical of me"), where higher scores indicate greater pathology.
-Total symptom scores range from 0 to 12 and are usually uniformly distributed.
-
-\subsection{Analysis}
-
-All statistical models fit as part of the analyses (described in detail below) were estimated within a Bayesian framework using Hamiltonian Monte Carlo as implemented in Stan (v2.26) \cite{stan}.
-For all models, four separate chains with randomised start values each took 2000 samples from the posterior.
-The first 1500 samples from each chain were discarded.
-As a result, 2000 post-warmup samples from the joint posterior were retained.
-Unless otherwise noted, the $\hat{R}$ values for all parameters was less than 1.1, indicating acceptable convergence between chains, and there were no divergent transitions in any chain.
-
-\subsubsection{Validation analyses}
-
-To validate the infrequency items as a sensitive measure of C/IE responding, we performed three complimentary analyses. We describe each in turn below.
-
-\subparagraph{Cronbach's $\alpha$.} We compared the average Cronbach's $\alpha$, a measure of internal consistency, between attentive and C/IE participants.
-To control for the unbalanced numbers of participants in these groups, we performed a permutation test.
-First, we estimated Cronbach's $\alpha$ was estimated for each subscale and group.
-Next, we computed the average difference in Cronbach's $\alpha$ between the two groups.
-Then we created a null distribution for this statistic by repeating the same analysis but permuting group membership (i.e.
-randomly assigning participants to either group), holding fixed the sizes of both groups.
-This procedure was performed 5000 times.
-To compute a p-value, we tallied the number of null statistics equal to or (absolutely) greater than the observed test statistic.
-
-\subparagraph{Random intercept item factor analysis.} We employed random intercept item factor analysis \cite{maydeu2006random} to detect heuristic patterns of responding.
-In the model, the probability of observing response level $k$ (of $K$ total levels) from participant $i$ on item $j$ is defined as:
-
-\begin{equation*}
-    p( \ y_{ij} = k \ ) = \left\{ \begin{array}{ll}
-1 - \text{logit}^{-1}( \mu_i + x_j\cdot \theta_i - c_{j,1})  &  \text{if } y = 1 \\[4pt]
-\text{logit}^{-1}( \mu_i + x_j\cdot \theta_i - c_{j,y-1}) - \text{logit}^{-1}( \mu_i + x_j\cdot \theta_i - c_{j,y}) & \text{if } 1 < y < K \\[4pt]
-\text{logit}^{-1}( \mu_i + x_j\cdot \theta_i - c_{j,K-1}) - 0  &  \text{if } y = K
-\end{array} \right.
-\end{equation*}
-
-where $\mu_i$ is an intercept for participant $i$; $\theta_i$ is a vector of latent factor scores for participant $i$; $x_j$ is a vector of factor loadings for item $j$; $c_j$ is a vector of ordinal cutpoints for item $j$; and $y_{ij}$ is the observed response for participant $i$ on item $j$.
-
-In this analysis, we did not estimate the factor loadings but instead treated them as observed.
-Specifically, we defined the factor loading for each item as a one-hot vector where the only nonzero entry denoted that item's corresponding subscale.
-That is, all of the items from a given subscale were assigned to their own unique factor (which was fixed to one).
-As such, the model estimated one factor score per participant and subscale (akin to the 1-parameter ordinal logistic model).
-
-Crucially, each participant's responses were also predicted by a random intercept term, $\mu_i$, which was not factor specific but instead was fit across all items.
-This intercept then reflects a participant's overall bias towards a response level.
-In our analysis, we coded the response levels such that the smallest value indicated endorsing the leftmost anchor (irrespective of semantic content) and the largest value indicated endorsing the rightmost anchor (irrespective of semantic content).
-Because the leftmost response option corresponds to symptomology on some scales (SHAPS), and a lack of symptomology for others (GAD-7, 7-up/7-down), we would not expect a consistent nonzero bias in this random intercept term for an attentive participant.
-
-\subparagraph{Clinical cutoffs.} We compared the proportion of participants in our sample reaching the threshold for clinical symptomology before and after applying exclusions.
-For the GAD-7, previous research has suggested a clinical cutoff score of 10 or higher \cite{lowe2008validation, hinz2017psychometric}.
-Though the 7-up/7-down scales do not have firmly established clinical cutoffs recent work has suggested a cutoff score of 12 or higher \cite{youngstrom2020evaluating}, which we use here.
-Finally, the original authors of the SHAPS scale recommended as a cutoff a score of 3 or more when the items are binarized (1 = ``strongly disagree", ``agree"; 0 = ``strongly agree", ``agree").
-We use this scoring approach in Table \ref{tab:validation}.
-
-\subsubsection{Correspondence of screening measures}
-
-To measure the correspondence of task- and self-report-based screening measures, we estimated a number of standard measures of data quality from each participant's task behavior (four in total) and self-report responses (five in total).
-Beginning first with the self-report data, we describe each below.
-
-\subparagraph{Self-report screening measure: Infrequency items.} Infrequency items are questions for which all or virtually all attentive participants should provide the same response.
-We embedded four infrequency items across the self-report measures.
-Specifically, we used the following questions:
-
-\begin{enumerate}
-  \item Over the last two weeks, how much time did you spend worrying about the 1977 Olympics? \hl{(Expected response: \textit{Not at all})}
-  \item Have there been times of a couple days or more when you were able to stop breathing entirely (without the aid of medical equipment)? \hl{(Expected response: \textit{Never or hardly ever})}
-  \item I would feel bad if a loved one unexpectedly died. \hl{(Expected response: \textit{Somewhat true for me} or \textit{Very true for me})}
-  \item I would be able to lift a 1 lb (0.5 kg) weight. \hl{(Expected response: \textit{Agree} or \textit{Strongly agree})}
-\end{enumerate}
-
-Prior to conducting the study, the infrequency items were piloted on an independent sample of participants to ensure that they elicited one dominant response.
-In the main study, we measured the number of suspicious responses made by each participant to these questions.
-For thresholded analyses, participants were flagged if they responded incorrectly to one or more of these items.
-
-\subparagraph{Self-report screening measure: Inter-item standard deviation.} The inter-item standard deviation (ISD) is an estimate of a participant's response consistency on a self-report measure \cite{marjanovic2015inter}, defined as:
-
-\begin{equation*}
-    ISD = \sqrt{\frac{\sum^k_{i=1}(y_j - \bar{y})^2}{k-1}}
-\end{equation*}
-
-where $y_i$ is a participant's response to item $i$, $x_i$ is a participant's average score across all  items, and $k$ is the total number of items for a self-report measure.
-A composite ISD measure was estimated per participant by summing across each of the seven self-report scales.
-Larger ISD values indicate lower response consistency.
-
-\subparagraph{Self-report screening measure: Personal reliability.} The personal reliability coefficient is an estimate of a participant's response consistency on a self-report measure, estimated by correlating the average scores from split-halves of their responses.
-To avoid any item-order bias, a participant's personal reliability coefficient for a particular self-report measure was computed from the average correlation from 1000 random split-halves.
-A composite reliability measure was generated per participant by averaging across each of the seven self-report scales.
-Smaller reliability coefficients indicate lower response consistency.
-
-\subparagraph{Self-report screening measure: Mahalanobis D.} The Mahalanobis distance is a multivariate outlier detection measure, which estimates how dissimilar a participant is relative to all others.
-For a participant $i$, the Mahalanobis D is defined as:
-
-\begin{equation*}
-    D = \sqrt{(X_i - \bar{X})^T \cdot \Sigma^{-1}_{XX} \cdot (X_i - \bar{X})^T }
-\end{equation*}
-
-where $(X_i - \bar{X})$ represents the vector of mean-centered item responses for participant $i$ and $\Sigma^{-1}_{XX}$ represents the inverted covariance matrix of all items.
-Greater Mahalanobis D values indicate larger deviations from the average pattern of responding.
-
-\subparagraph{Self-report screening measure: Reading time.} The reading time is the total number of seconds spent filling out a particular self-report measure, adjusted for that measure's total number of items \cite{ophir2020turker}.
-A total reading time estimate was estimated for each participant by summing across the adjusted time for each of the seven self-report measures.
-Shorter scores are indicative of less time having been spent on each item.
-
-\subparagraph{Task-based screening variable: Choice variability.} Choice variability was defined as the fraction of trials of the most used response option per participant.
-Choice variability could range from 0.33 (all response options used equally) to 1.00 (only one response option used).
-Values closer to 1.00 are indicative of more careless responding during the task.
-
-\subparagraph{Task-based screening variable: Choice accuracy.} Choice accuracy was defined as the fraction of choices of the reward-maximizing response option.
-For a task with 90 trials and three response options, a one-tailed binomial test at $\alpha=0.05$ reveals chance-level performance to be 37 or fewer correct choices (41\%).
-Lower accuracy values are indicative of more inattentive responding during the task.
-
-\subparagraph{Task-based screening variable: Win-Stay Lose-Shift.} Win-stay lose-shift (WSLS) measures a participant's tendency to stay with a choice option following a reward versus shifting to a new choice option following a non-reward.
-WSLS thus measures a participant's sensitivity to reward feedback on the screen.
-WSLS was estimated per participant via regression, where the current choice (stay, switch) predicted by the previous trial's outcome (reward, non-reward) and a stationary intercept.
-Here we used the first (slope) term to represent a participant's WSLS tendency.
-Lower values of this term indicate less sensitivity to reward feedback and are thus indicative of more careless responding during the task.
-
-\subparagraph{Task-based screening variable: Response times.} ``Suspicious response time'' was defined as the proportion of trials with an outlier response time, here measured as responses faster than 200ms.
-Greater proportions of outlier response times are indicative of more careless responding during the task.
-
-\subparagraph{Correspondence Analysis.} We measured the correspondence of the above screening measures via two complimentary approaches.
-First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation.
-Second, we estimated the pairwise rate of agreement on the binarized measures using the Dice similarity coefficient (looking at the top 10\% and 25\% most suspicious respondents for each measure).
-The former approach estimates two measures' monotonic association, whereas the latter approach estimates their agreement as to which participants were most likely engaging in C/IE responding.
-For significance testing, we used permutation testing wherein a null distribution of similarity scores (i.e.
-Spearman's correlation, Dice coefficient) was generated for each pair of screening measures by iteratively permuting participants' identities within measures and re-estimating the similarity.
-P-values were computed by comparing the observed score to its respective null distribution.
-We corrected for multiple comparisons using family-wise error rates \cite{winkler2014permutation}.
-
-\subsubsection{Correlations between behavior and symptom measures}
-
-To quantify the effects of both task and self-report data screening on behavior-symptom correlations, we estimated the pairwise correlations between the symptom scores of each of the self-report measures and several measures of performance on the reversal learning task.
-For each participant, we computed both descriptive and model-based measures of behavior on the reversal learning task.
-We describe each in turn below.
-
-\subparagraph{Descriptive measures.} Descriptive task measures included the following: accuracy (the fraction of choices of the reward-maximizing response option), points (the total number of points accumulated over the game), win-stay rates (the fraction of trials on which a participant repeated the previous trial's choice following a reward outcome), lose-shift rates (the fraction of trials on which a participant deviated from the previous trial's choice following a non-reward outcome), and perseveration (the number of trials on which a participant continued to choose the previously dominant response option following a reversal in task contingencies).
-
-\subparagraph{Model-based measures.} The model-based measures were derived from a common reinforcement learning model of choice behavior, the risk-sensitive temporal difference learning model \cite{niv2012neural}.
-In this model, the expected value of a choice option, $Q(s)$, is learned through cycle of choice and reward feedback.
-Specifically, following a decision and reward feedback, the value of the chosen option is updated according to:
-
-\begin{equation*}
-    Q_{t+1}(s) = Q_{t}(s) + \eta \cdot \delta_{t}
-\end{equation*}
-
-where $\eta$ is the learning rate bounded in the range $[0,1]$ (controlling the extent to which value reflects the most recent outcomes) and $\delta$ is the reward prediction error, defined as:
-
-\begin{equation*}
-    \delta_t = r_t - Q_{t}(s)
-\end{equation*}
-
-In the risk-sensitive temporal difference learning model, there are separate learning rates for positive and negative prediction errors, such that positive and negative prediction errors have asymmetric effects on learning.
-For example, the effect of negative prediction errors on learned values is larger than that of positive errors if $\eta_p+ < \eta_n$, and vice versa if $\eta_p > \eta_n$.
-
-Finally, decision-making according to the model is dictated by a softmax choice rule:
-
-\begin{equation*}
-    p(y_t = s) = \frac{\exp \left( \beta \cdot Q(s) \right)}{\sum_i^S \exp \left( \beta \cdot Q(s) \right)}
-\end{equation*}
-
-where $\beta$ is the inverse temperature, controlling a participant's sensitivity to the expected value of the choice options.
-In sum then, the model-based approach describes a participant's choice behavior as a function of three parameters ($\beta, \eta_p, \eta_n$).
-
-We fit the reinforcement learning model to each participants' choice behavior using Stan (details above).
-Notably, 11 participants (3\% of sample) had parameter estimates with poor convergence, i.e.
-$\hat{R} > 1.1$; their parameters were removed from the correlation analysis.
-Participants' parameters were fit individually (i.e.
-not hierarchically) so as to prevent bias during parameter estimation from partial-pooling between attentive and C/IE participants.
-Parameters were sampled using non-centred parameterisations (i.e., all parameters were sampled separately from a unit normal before being transformed to the appropriate range).
-Of note, the learning rates were estimated via an offset method such that $\eta_p = \eta + \kappa$ and $\eta_n = \eta - \kappa$, where $\kappa$ is an offset parameter controlling the extent of an asymmetry between the two learning rates.
-This parameter was also entered into the behavior-symptom correlation analyses.
-
-We confirmed the model adequately fit participants' choice behavior through a series of posterior checks (Figure \ref{fig:posterior_check}).
-In particular, we confirmed the model recapitulated the group-average learning curves for each block of the experiment.
-Moreover, we confirmed that the model was able to recover reasonably well the choice accuracy for each participant.
-
-The model-based measures included for analysis were: choice sensitivity ($\beta$,  inverse temperature), positive learning rate ($\eta_p$), negative learning rate ($\eta_n$), and learning rate asymmetry ($\kappa = \frac{\eta_p-\eta_n}{\eta_p+\eta_n}$, normalized difference between $\eta_p$ and $\eta_n$).
-We chose these measures as they have been previously used to assess performance in clinical samples \cite{huang2017computational, brolsma2020challenging, mukherjee_reward_2020, ritschel2017neural}.
-
-\subparagraph{Correlation analysis.} Behavior-symptom correlations (after various forms of screening and exclusion) were estimated using Spearman's rank correlation.
-Significance testing was performed using the percentile bootstrap method \cite{wilcox2018guide} so as to avoid making any parametric assumptions.
-These correlation analyses were not corrected for multiple comparisons, since our overarching purpose was to demonstrate the extent of this issue across multiple behavioral measures and self-report symptoms.
-Any one of these correlations considered individually can be thought of as emulating a conventional analysis where fewer statistical tests would be performed.
-
-\section{Acknowledgements}
-
-The authors are grateful to Agnes Norbury, Alexandra Pike, and Oliver Robinson for helpful discussion.
-The research reported in this manuscript was supported in part by the National Institute of Mental Health (NIMH) under award number 5R01MH119511-02, and by the National Center for Advancing Translational Sciences (NCATS), a component of the National Institute of Health (NIH), under award number UL1TR003017.
-The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.
-SZ was supported by an NSF Graduate Research Fellowship.
-DB was supported by an Early Career Fellowship from the Australian National Health and Medical Research Council (\#1165010).
-
+\clearpage
 \section*{References}
@@
 
-\break
-
-%TC:ignore
-
-\begin{refsection}[supp]
-\section*{Appendix A}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-\renewcommand{\thetable}{S\arabic{table}}
-\renewcommand{\thefigure}{S\arabic{figure}}
-
-\subsection*{\texorpdfstring{\hl{Signed correlation analysis}{}}}
-
-\begin{figure}[H]
-\includegraphics[width=17cm]{../figures/supp_01.png}
-\centering
-\captionsetup{width=0.88\textwidth}
-\caption{Signed Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions.
-Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons).
-Black Xs indicate significant correlations ablated under screening.
-No Screening = no exclusions; Accuracy Only = exclusions based on chance-level performance in the reversal-learning task; Infrequency Only = exclusions based on invalid or improbable responses to infrequency items; Both Types = exclusions based on the previous two measures.
-Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
-\label{fig:correlations_s1}
-\end{figure}
-
-\clearpage
-
-\subsection*{Bootstrapping Analysis}
-\begin{figure}[H]
-\includegraphics[width=16cm]{../figures/supp_02.png}
-\centering
-\captionsetup{width=0.88\textwidth}
-\caption{The pattern of significant behavior-symptom correlations before (panel A) and after (panel B) screening compared to the resulting pattern when random subsets of participants (22\% of total, matched to screening using the infrequency measure) are removed (panel C).
-Panels A and B are reproduced from Figure \ref{fig:correlations} for convenience.
-Panel C: the fraction of significant correlations in 5000 bootstrapped samples.
-Panel D: The similarity of the pattern of correlations after removal of random subsets to that before and after screening using the infrequency measure.
-Similarity was calculated using the simple matching coefficient.
-Random removal subsets were significantly more similar to the ``No Screening" than to the ``Infrequency" screening datasets (t = 262.49, $p < 0.001$).}
-\label{fig:random}
-\end{figure}
-
-\clearpage
-
-\subsection*{\texorpdfstring{\hl{The relationship between sample size and false positive rates generalize to other sets of variables}{}}}
-
-\begin{figure}[H]
-\includegraphics[width=16cm]{../figures/supp_03.png}
-\centering
-\captionsetup{width=0.88\textwidth}
-\caption{False positive rates for spurious correlations \emph{increase} with sample size.
-\textit{Left:} Bootstrapped Spearman correlations between inverse temperature ($\beta$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants.
-The grey error bars indicate 95\% bootstrap confidence intervals.
-The thick dashed lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size.
-Markers are jittered along the x-axis for legibility.
-\textit{Right:} False positive rates for inverse temperature ($\beta$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants.
-False positive rate was calculated as the proportion of bootstrap samples in which the correlation between $\beta$ and 7-down was statistically significant.
-The horizontal dotted line denotes the expected false positive rate at $\alpha = .05$.}
-\label{fig:bootstrap_s1}
-\end{figure}
-
-\clearpage
-
-\subsection*{\texorpdfstring{\hl{The relationship between sample size and true positive rates for true correlations}{}}}
-
-\begin{figure}[H]
-\includegraphics[width=16cm]{../figures/supp_04.png}
-\centering
-\captionsetup{width=0.88\textwidth}
-\caption{True correlations are independent of the proportion of C/IE participants in the sample.
-\textit{Left:} Bootstrapped Spearman correlations between learning rate asymmetry ($\kappa$) and anxiety scores (GAD-7) as a function of sample size and proportion of C/IE participants.
-The grey error bars indicate 95\% bootstrap confidence intervals.
-The thick dashed lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size.
-Markers are jittered along the x-axis for legibility.
-\textit{Right:} True positive rates for learning rate asymmetry ($\kappa$) and anxiety scores (GAD-7) as a function of sample size and proportion of C/IE participants.
-True positive rate was calculated as the proportion of bootstrap samples in which the correlation between $\kappa$ and GAD-7 was statistically significant.
-The horizontal dotted line denotes the expected false positive rate at $\alpha = .05$.}
-\label{fig:bootstrap_s2}
-\end{figure}
-
-\clearpage
-
-\subsection*{Posterior predictive checks}
-
-\begin{figure}[H]
-\includegraphics[width=16cm]{../figures/supp_05.png}
-\centering
-\captionsetup{width=0.88\textwidth}
-\caption{Posterior predictive checks for the risk-sensitive temporal difference learning model.
-\textit{Panel A:} Observed (black) and predicted (blue) learning curves averaged across the group.
-\textit{Panel B:} Observed versus predicted choice accuracy for each participant.
-\textit{Panel C:} Distribution of average predictive density across participants.}
-\label{fig:posterior_check}
-\end{figure}
-
-\clearpage
-
-\subsection*{Participant demographics}
-
-\begin{table}[!h]
-\centering
-\small
-\setlength{\tabcolsep}{15pt}
-\begin{tabular}{ rrrrr }
-\toprule
-& \multicolumn{2}{c}{MTurk} & \multicolumn{2}{c}{Prolific} \\
-\cmidrule(lr){2-3} \cmidrule(lr){4-5}
-Total & \multicolumn{2}{c}{N=186} & \multicolumn{2}{c}{N=200} \\
-\midrule
-Age & N & \% & N & \% \\
-\cmidrule(lr){1-5}
-18-25   &      16 &   8.6 &       78 &  39.0 \\
-26-35   &      76 &  40.9 &       69 &  34.5 \\
-36-45   &      46 &  24.7 &       31 &  15.5 \\
-46-55   &      22 &  11.8 &       13 &   6.5 \\
-55+     &      26 &  14.0 &        9 &   4.5 \\
-\midrule
-Gender & N & \% & N & \% \\
-\cmidrule(lr){1-5}
-Female             &    83 &  44.6 &    112 &  56.0 \\
-Male               &   103 &  55.4 &     85 &  42.5 \\
-Other              &     0 &   0.0 &      3 &   1.5 \\
-\midrule
-Ethnicity & N & \% & N & \% \\
-\cmidrule(lr){1-5}
-Hispanic or Latino     &    15 &   8.1 &     10 &   5.0 \\
-Not Hispanic or Latino &   168 &  90.3 &    183 &  91.5 \\
-Rather not say         &     2 &   1.1 &      7 &   3.5 \\
-Unknown                &     1 &   0.5 &      0 &   0.0 \\
-\midrule
-Race & N & \% & N & \% \\
-\cmidrule(lr){1-5}
-African American                 &    21 &  11.3 &      7 &   3.5 \\
-Asian                                     &     5 &   2.7 &     53 &  26.5 \\
-White                                     &   151 &  81.2 &    121 &  60.5 \\
-Multiracial                               &     6 &   3.2 &      4 &   2.0 \\
-Rather not say                            &     1 &   0.5 &     12 &   6.0 \\
-\midrule
-Use other platform & N & \% & N & \% \\
-\cmidrule(lr){1-5}
-Yes            &      71 &  38.2 &       28 &  14.0 \\
-No             &     115 &  61.8 &      172 &  86.0 \\
-\bottomrule
-\end{tabular}
-\captionsetup{width=0.88\textwidth}
-\caption{The demographics of each sample by online labour market.
-On average, the samples were similar though the sample from Mechanical Turk was older (t = 6.567, p $<$ 0.001) and comprised of fewer women (z = 6.567, p = 0.011).
-Note: the demographics do not include 20 participants excluded for participating in the study twice, once per platform.}
-\label{tab:demographics}
-\end{table}
-
-\clearpage
-
-\subsection*{\texorpdfstring{\hl{Careless participants show different behaviors on the reversal learning task}{}}}
-
-\begin{table}[H]
-\centering
-\begin{tabular}{lrrr}
-\toprule
-{} &  Attentive &    C/IE &   $t$-value \\
-\midrule
-Acc      &      0.587 &   0.532 &  $4.008^*$  \\
-Pts      &     50.163 &  47.729 &  $2.376^*$  \\
-WS       &      0.898 &   0.776 &  $5.387^*$  \\
-LS       &      0.609 &   0.751 &  $-5.335^*$ \\
-Pers     &      0.245 &   0.259 &  $-1.505$ \ \\
-$\beta$  &      6.754 &   4.082 &  $5.404^*$  \\
-$\eta_p$ &      0.643 &   0.551 &  $2.846^*$  \\
-$\eta_n$ &      0.738 &   0.784 & $-1.516$ \  \\
-$\kappa$ &     -0.069 &  -0.218 &  $3.729^*$  \\
-\bottomrule
-\end{tabular}
-\captionsetup{width=0.88\textwidth}
-\caption{Measures of task behavior compared between attentive and C/IE participants.
-Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.
-* Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
-\end{table}
-
-\clearpage
-
-\subsection*{Correspondence of screening measures}
-
-The following are the unthresholded results of the screening measure correspondence analyses.
-
-\begin{table}[H]
-\centering
-\small
-\begin{tabular}{rccccccccc}
-\toprule
-{} &      INF &      ISD &      REL &      MAH &    READ &     VAR &     ACC &   WSLS & RT \\
-\midrule
-INF  &        - &          &          &          &         &         &         &        &    \\
-ISD  &   0.372* &        - &          &          &         &         &         &        &    \\
-REL  &  -0.408* &  -0.811* &        - &          &         &         &         &        &    \\
-MAH  &   0.406* &   0.843* &  -0.643* &        - &         &         &         &        &    \\
-READ &   -0.111 &   0.193* &  -0.168* &    0.138 &       - &         &         &        &    \\
-VAR  &   -0.061 &   -0.029 &    0.058 &   -0.024 &  -0.026 &       - &         &        &    \\
-ACC  &  -0.206* &   -0.154 &    0.099 &  -0.182* &  -0.074 &   0.027 &       - &        &    \\
-WSLS &    0.060 &    0.102 &   -0.089 &    0.115 &   0.103 &  -0.060 &  0.221* &      - &    \\
-RT   &    0.040 &   -0.019 &    0.014 &    0.013 &  -0.158 &  -0.007 &  -0.094 &  -0.05 &  - \\
-\bottomrule
-\end{tabular}
-\captionsetup{width=0.88\textwidth}
-\caption{Spearman's rank correlations of task and self-report data screening measures.
-Each entry corresponds to the Spearman correlation between two screening measures.
-Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times.
-*Denotes statistical significance after correcting for multiple comparisons.}
-\end{table}
-
-\begin{table}[H]
-\centering
-\small
-\begin{tabular}{rccccccccc}
-\toprule
-{} &     INF &     ISD &     REL &    MAH &   READ &    VAR &     ACC &  WSLS & RT \\
-\midrule
-INF  &       - &         &         &        &        &        &         &       &    \\
-ISD  &  0.462* &       - &         &        &        &        &         &       &    \\
-REL  &  0.484* &  0.691* &       - &        &        &        &         &       &    \\
-MAH  &  0.516* &  0.732* &  0.619* &      - &        &        &         &       &    \\
-READ &   0.319 &   0.165 &   0.165 &  0.216 &      - &        &         &       &    \\
-VAR  &   0.208 &   0.216 &   0.238 &  0.259 &  0.292 &      - &         &       &    \\
-ACC  &  0.379* &   0.312 &   0.258 &  0.344 &  0.237 &  0.282 &       - &       &    \\
-WSLS &   0.253 &   0.247 &   0.227 &  0.258 &  0.299 &  0.303 &  0.505* &     - &    \\
-RT   &   0.267 &   0.219 &   0.271 &  0.271 &  0.333 &  0.251 &   0.239 &  0.26 &  - \\
-\bottomrule
-\end{tabular}
-\captionsetup{width=0.88\textwidth}
-\caption{Dice similarity coefficients (top 10\%) for task and self-report data screening measures.
-Each entry corresponds to the Dice coefficient between two screening measures for the 10\% most suspicious participants.
-Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times.
-*Denotes statistical significance after correcting for multiple comparisons.}
-\end{table}
-
-\begin{table}[H]
-\centering
-\small
-\begin{tabular}{rccccccccc}
-\toprule
-{} &     INF &     ISD &     REL &    MAH &    READ &    VAR &     ACC &   WSLS & RT \\
-\midrule
-INF  &       - &         &         &        &         &        &         &        &    \\
-ISD  &  0.355* &       - &         &        &         &        &         &        &    \\
-REL  &  0.355* &  0.564* &       - &        &         &        &         &        &    \\
-MAH  &  0.355* &  0.667* &  0.359* &      - &         &        &         &        &    \\
-READ &  0.290* &   0.231 &   0.154 &  0.231 &       - &        &         &        &    \\
-VAR  &   0.116 &   0.080 &   0.080 &  0.160 &   0.133 &      - &         &        &    \\
-ACC  &  0.269* &   0.137 &   0.164 &  0.192 &   0.247 &  0.171 &       - &        &    \\
-WSLS &   0.242 &   0.103 &   0.154 &  0.205 &   0.231 &  0.240 &  0.630* &      - &    \\
-RT   &   0.164 &   0.105 &   0.132 &  0.184 &  0.289* &  0.164 &   0.225 &  0.237 &  - \\
-\bottomrule
-\end{tabular}
-\captionsetup{width=0.88\textwidth}
-\caption{Dice similarity coefficients (top 25\%) for task and self-report data screening measures.
-Each entry corresponds to the Dice coefficient between two screening measures for the 25\% most suspicious participants.
-Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times.
-*Denotes statistical significance after correcting for multiple comparisons.}
-\end{table}
-
-\subsection*{Correlations between behavior and symptom measures}
-
-The following are the unthresholded results of the correlation analyses between task behavior and self-reported symptoms.
-
-\begin{table}[H]
-\centering
-\small
-\begin{tabular}{rccccccc}
-\toprule
-{} &       7u &       7d &    GAD-7 &      BIS &     BAS &   SHAPS &    PSWQ \\
-\midrule
-Acc      &  -0.295* &  -0.166* &  -0.093* &  -0.134* &  -0.020 &  -0.051 &  -0.037 \\
-Pts      &  -0.225* &   -0.076 &   -0.023 &  -0.144* &  -0.061 &  -0.051 &   0.024 \\
-WS       &  -0.327* &  -0.160* &  -0.129* &  -0.171* &  -0.006 &  -0.048 &  -0.062 \\
-LS       &   0.285* &   0.158* &   0.146* &    0.050 &  -0.037 &   0.000 &  0.110* \\
-Pers     &   0.134* &    0.066 &    0.032 &   0.166* &   0.018 &   0.080 &  -0.004 \\
-$\beta$  &  -0.370* &  -0.157* &  -0.114* &  -0.185* &   0.017 &  -0.063 &  -0.043 \\
-$\eta_p$ &  -0.097* &  -0.105* &  -0.101* &   -0.033 &  -0.020 &  -0.015 &  -0.041 \\
-$\eta_n$ &   0.168* &   0.094* &   0.108* &   -0.050 &  -0.056 &  -0.020 &   0.042 \\
-$\kappa$ &  -0.175* &  -0.137* &  -0.147* &   -0.008 &  -0.020 &  -0.028 &  -0.061 \\
-\bottomrule
-\end{tabular}
-\captionsetup{width=0.88\textwidth}
-\caption{Spearman correlations between task behavior and self-report symptom measures when no screening and rejections have been applied.
-Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.
-*Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
-\end{table}
-
-\begin{table}[H]
-\centering
-\small
-\begin{tabular}{rccccccc}
-\toprule
-{} &       7u &       7d &    GAD-7 &      BIS &     BAS &   SHAPS &    PSWQ \\
-\midrule
-Acc      &  -0.263* &  -0.144* &  -0.105* &  -0.106* &  -0.009 &  -0.020 &  -0.033 \\
-Pts      &  -0.187* &   -0.042 &   -0.020 &  -0.126* &  -0.055 &  -0.028 &   0.036 \\
-WS       &  -0.291* &  -0.137* &  -0.123* &  -0.161* &  -0.019 &   0.006 &  -0.044 \\
-LS       &   0.314* &   0.170* &   0.156* &    0.034 &  -0.036 &  -0.037 &  0.124* \\
-Pers     &    0.083 &    0.022 &    0.011 &   0.151* &   0.010 &   0.076 &  -0.021 \\
-$\beta$  &  -0.332* &  -0.134* &  -0.109* &  -0.173* &   0.010 &  -0.040 &  -0.023 \\
-$\eta_p$ &   -0.056 &   -0.089 &  -0.105* &   -0.013 &  -0.029 &   0.034 &  -0.035 \\
-$\eta_n$ &   0.259* &   0.134* &   0.122* &   -0.021 &  -0.063 &   0.019 &   0.053 \\
-$\kappa$ &  -0.171* &  -0.125* &  -0.150* &   -0.016 &  -0.032 &  -0.033 &  -0.060 \\
-\bottomrule
-\end{tabular}
-\captionsetup{width=0.88\textwidth}
-\caption{Spearman correlations between task behavior and self-report symptom measures after applying rejections based on choice accuracy (7\% of sample).
-Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.
-*Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
-\end{table}
-
-\begin{table}[H]
-\centering
-\small
-\begin{tabular}{rccccccc}
-\toprule
-{} &       7u &      7d &    GAD-7 &      BIS &     BAS &   SHAPS &    PSWQ \\
-\midrule
-Acc      &  -0.210* &  -0.048 &    0.009 &   -0.082 &  -0.020 &  -0.005 &   0.009 \\
-Pts      &  -0.167* &   0.040 &    0.070 &  -0.107* &  -0.046 &  -0.011 &   0.071 \\
-WS       &  -0.220* &  -0.045 &   -0.008 &  -0.143* &  -0.025 &   0.001 &   0.016 \\
-LS       &   0.219* &   0.084 &   0.113* &    0.019 &  -0.021 &  -0.050 &   0.082 \\
-Pers     &    0.088 &  -0.028 &   -0.024 &   0.127* &   0.006 &   0.048 &  -0.052 \\
-$\beta$  &  -0.257* &  -0.038 &    0.047 &  -0.180* &  -0.011 &  -0.032 &   0.056 \\
-$\eta_p$ &   -0.052 &  -0.064 &   -0.079 &   -0.015 &  -0.008 &   0.004 &  -0.055 \\
-$\eta_n$ &   0.165* &   0.067 &   0.141* &   -0.037 &  -0.089 &  -0.030 &   0.054 \\
-$\kappa$ &  -0.111* &  -0.046 &  -0.137* &    0.011 &   0.015 &   0.002 &  -0.054 \\
-\bottomrule
-\end{tabular}
-\caption{Spearman correlations between task behavior and self-report symptom measures after applying rejections based on infrequency items (22\% of sample).
-Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.
-*Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
-\end{table}
-
-\begin{table}[H]
-\centering
-\small
-\begin{tabular}{rccccccc}
-\toprule
-{} &       7u &      7d &    GAD-7 &      BIS &     BAS &   SHAPS &    PSWQ \\
-\midrule
-Acc      &  -0.229* &  -0.090 &   -0.072 &   -0.053 &   0.016 &   0.034 &  -0.040 \\
-Pts      &  -0.177* &   0.016 &    0.011 &   -0.086 &  -0.013 &   0.025 &   0.038 \\
-WS       &  -0.227* &  -0.085 &   -0.057 &  -0.131* &  -0.025 &   0.049 &  -0.007 \\
-LS       &   0.236* &   0.094 &   0.107* &    0.008 &  -0.016 &  -0.075 &   0.079 \\
-Pers     &    0.095 &  -0.007 &    0.014 &   0.110* &  -0.015 &   0.037 &  -0.025 \\
-$\beta$  &  -0.255* &  -0.072 &   -0.008 &  -0.165* &  -0.011 &  -0.015 &   0.028 \\
-$\eta_p$ &   -0.045 &  -0.088 &  -0.108* &    0.004 &  -0.000 &   0.049 &  -0.073 \\
-$\eta_n$ &   0.196* &   0.046 &   0.098* &   -0.015 &  -0.085 &   0.008 &   0.024 \\
-$\kappa$ &  -0.114* &  -0.046 &  -0.134* &    0.007 &   0.012 &  -0.004 &  -0.051 \\
-\bottomrule
-\end{tabular}
-\captionsetup{width=0.88\textwidth}
-\caption{Spearman correlations between task behavior and self-report symptom measures after applying rejections based on both choice accuracy and infrequency items.
-Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.
-*Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
-\end{table}
-
-\subsection*{Task Instructions}
-
-The following are the instructions given to participants for the probabilistic reversal learning task.
-As a reminder, the task was given a fishing-themed cover story.
-Each paragraph below denotes one screen of instructions.
-
-\textit{Welcome to the fishing game! We will now give you some instructions on how to play the game. Use the buttons below (or the arrow keys) to navigate the instructions.}
-
-\textit{In the fishing game, there are three beaches you can fish at.
-Each beach has its own unique surfboard.
-(The colors and pictures on the surfboards are there just to help you tell the beaches apart – they don’t have any special meaning other than that.)}
-
-\textit{On each turn you will be shown three beaches, and you will choose which one you want to fish at. You can make your choice using the left, up, and right arrow keys.}
-
-\textit{When you fish at a beach, you will either catch a fish or you will catch trash. Try to catch fish, and try not to catch trash!}
-
-\textit{Some beaches are better than others.
-You are more likely to catch fish at some beaches (though you will still sometimes catch trash), and you are more likely to catch trash at other beaches (though you still sometimes catch fish).}
-
-\textit{The beaches will change over time. As times goes by, you may be less likely to catch fish at a beach where you were previously catching many fish.}
-
-\textit{Your goal is to catch as many fish as you can. You will receive a performance bonus up to \$0.25 that depends on how many fish you catch.}
-
-\textit{Now we will ask you some questions about the game.
-You must answer all questions correctly to proceed.
-Feel free to read back through the instructions if there is anything you are not certain about.}
-
-Following the instructions, participants completed a brief comprehension check where they were asked the following questions about the task:
-
-\begin{enumerate}
-    \item True or False: Your goal is to catch as many fish as you can. (True)
-    \item True or False: You are more likely to catch fish at some beaches than others. (True)
-    \item True or False: You will always catch fish at the best beach. (False)
-    \item True or False: How likely you are to catch a fish at a beach stays the same over time. (False)
-    \item True or False: The number of fish you catch will affect your final performance bonus. (True)
-\end{enumerate}
-
-Participants were required to answer all of the items correctly before they could proceed to the task.
-If they failed to do so, they restarted the instructions.
-There was no upper limit as to how many times a participant could loop through the instructions (the large majority of participants passed the comprehension check on their first try).
-
-\subsection*{C/IE responding manifests as qualitatively distinct behavioral strategy}
-
-In an exploratory analysis, we employed a theory-agnostic modeling approach to investigate how C/IE participants on the probabilistic reversal-learning task compared to attentive participants.
-The motivation for this analysis was to better understand why C/IE responding was inconsistently predicted by chance-level performance, and also correlated with asymmetric learning rates.
-
-To characterize participants' choice behavior, we adapted the softmax regression model from \cite{seymour2012serotonin}.
-This model estimates, for each participant, how much their choice depends on the recent history of trial events (rewarding outcomes, non-rewarding outcomes, and choices from the preceding 5 trials).
-Specifically, the influence of the history of particular type of event is defined as:
-
-\begin{equation*}
-    \sum_i^K w = x_{t-1} \cdot w_{t-1} + x_{t-2} \cdot w_{t-2} +  \ldots + x_{t-k} \cdot w_{t-k}
-\end{equation*}
-
-where $x_{t-i}$ is a binary indicator [0,1] denoting if an event (i.e.
-reward, non-reward, previous choice) occurred on trial $t-i$ and $w_{t-1}$ is the associated decision weight.
-These weights were estimated for rewards, non-rewards, and previous choices up to five trials in the past.
-The overall tendency to choose a particular choice option is dictated by a softmax choice rule:
-
-\begin{equation*}
-    p(y_t = i) = \frac{ \exp \left( \sum w_i^\text{reward} + \sum w_i^\text{nonreward} + \sum w_i^\text{choice} \right) }{ \sum_i \exp \left( \sum w_i^\text{reward} + \sum w_i^\text{nonreward} + \sum w_i^\text{choice} \right) }
-\end{equation*}
-
-Note that these weights were fit independently; that is, we did not employ an exponential kernel to parameterize the decay of the weights at successively distant trial lags.
-In sum then, the theory-agnostic model describes a participant's choice behavior as a function of 15 parameters.
-
-We fit the softmax regression model using Stan following the same procedure as for the theory-based analyses.
-Participant parameters were fit individually (i.e.
-not hierarchically)  so as to prevent bias during parameter estimation from partial-pooling between attentive and C/IE participants.
-Parameters were sampled with Gaussian priors with $\mu = 0$ and $\sigma = 5$.
-
-The regression weights for each event, averaged within attentive and C/IE participants, are presented in Figure \ref{fig:regression}.
-Comparing attentive to C/IE participants, we observed a credible difference (i.e.
-95\% highest density intervals excluded zero) only for the $T-1$ weight for previous choice.
-That is, attentive participants were more likely to repeat their previous choice (i.e.
-greater choice hysteresis) than were C/IE participants.
-
-\begin{figure}[!t]
-\includegraphics[width=16cm]{../figures/main_03c.png}
-\centering
-\captionsetup{width=0.88\textwidth}
-\caption{Softmax regression decision weights in attentive (red) and C/IE (blue) participants.
-The weights dictate the extent to which the recent history of rewards, nonrewards, or previous choices influence current choice.
-Error bars indicate the 95\% highest density interval of each weight.
-* denotes where the 95\% highest density interval of the difference in weights excluded zero.}
-\label{fig:regression}
-\end{figure}
-
-This result may be initially surprising, since one might expect choice hysteresis to result in more perseveration errors following contingency reversals.
-However, choice hysteresis is adaptive in this probabilistic reversal-learning task.
-Because rewards in the task are probabilistic, once the reward-maximizing response option has been identified ignoring an occasional unrewarding outcome and instead performing the same response is optimal (until the next reversal occurs and is identified).
-Interestingly, participants engaging in C/IE responding were also numerically (though not significantly) less affected by previous outcomes, suggesting that their behavior was not more adaptive, but rather just more random.
-
-This pattern of results also helps explain the pre-screening correlations with asymmetric learning rates.
-Previous work has established that, when choice hysteresis is not accounted for in reinforcement learning models, it can manifest as positive learning rate asymmetries \cite{Katahira2018-ke, sugawara2021dissociation}.
-Since C/IE participants showed decreased hysteresis, which our reinforcement learning model did not explicitly account for, we should expect to find a negative correlation between learning-rate asymmetries and symptoms before C/IE participants are excluded.
-Indeed, this is what we observed above.
-
-In sum, the theory-agnostic analysis of task behavior revealed that C/IE participants exhibited a qualitatively distinct behavioral strategy on the probabilistic reversal-learning task.
-C/IE participants showed less adaptive choice hysteresis.
-Moreover, they were numerically (but not significantly) less sensitive to outcomes.
-The latter finding helps clarify in part why we observed low correspondence between task and self-report screening measures (that is, C/IE participants were not significantly more likely to respond randomly during the task).
-These results also present another hidden danger of C/IE responding: qualitatively distinct patterns of behavior under C/IE responding can bias the estimation of parameters of theoretical interest if not properly accounted for.
-
-\break
-
-\section*{\texorpdfstring{\hl{Appendix B: Replication study}{}}}
-
-\subsection*{Background \& motivation}
-
-Here we report a conceptual replication of our original study.
-The motivations for conducting a replication study were threefold.
-First, we wanted to examine the generalizability of our findings under new labour-platform conditions.
-Since summer 2020, when the original data were collected, online labour markets like Mechanical Turk/CloudResearch and Prolific Academic have undergone important changes.
-To address rampant data quality issues on Mechanical Turk, CloudResearch introduced their ``Approved Participants'' filter.
-When selected, only Mechanical Turk participants with a prior history of attentive and careful work are invited to participate in experiments \cite{cloudresearch_2020-2, hauser2021evaluating}.
-Similarly, a deluge of new, lower-quality users signed up to participate in studies on Prolific in summer, 2021 \cite{Letzter2021-bw}.
-In response, Prolific introduced new controls and filters to improve data quality on the platform \cite{prolific_2021}.
-In the wake of these changes, we wanted to explore the relevance of our original findings.
-Specifically, with these new safeguards, we wanted to examine whether the chance of spurious correlations has been considerably reduced.
-
-Second, we wanted to examine the generalizability of our findings to other behavioral measures.
-In the original study, we used a short, straightforward, and relatively easy reversal-learning task.
-Our motivation then was to demonstrate the risk of spurious correlations even for experiments where the possibility of participant fatigue (and consequently C/IE responding) had been minimized.
-One consequence of this design, however, was that the majority of participants performed reasonably well on the task (only 26 participants, or 7\% of the sample, exhibited choice accuracy at or below chance levels).
-This could in part explain why we observed such low correspondence between self-report and task-based screening measures.
-As such, we wanted to repeat our experiment and analyses using a more difficult task.
-Therefore, in the replication study we used the two-step task \cite{daw2011model}, which is both more challenging and takes longer than our original reversal-learning task.
-
-Finally, we wanted to examine the generalizability of our findings to other self-report measures.
-In the original study, we found that self-report symptom measures with low rates of endorsement were more likely to yield spurious correlations with behavior in the presence of C/IE responding, as C/IE participants were more likely to endorse symptoms, as well as to perform poorly on the task.
-In principle, this effect should not be limited to symptom measures, and should extend to any self-report measure with an expected skewed or asymmetric score distribution.
-Therefore, in the current replication study, we used two sets of self-report scales: one set of psychiatric symptom measures and one set of personality measures.
-As before, each set includes scales whose score distributions are expected to be symmetric as well as scales with asymmetric (skewed) score distributions.
-Crucially, the two personality scales we chose, artistic interests and greed avoidance, measure constructs that should have no meaningful relationship with model-based choice behavior on the two-step task.
-Therefore, the personality measures serve as a stronger test of our hypothesis that spurious correlations between self-report and behavioral measures are more likely for skewed score distributions.
-
-\subsection*{Methods}
-
-\subsubsection*{Participants}
-
-400 total participants were recruited to participate in an online behavioral experiment in February, 2022.
-Specifically, 200 participants were recruited from Amazon Mechanical Turk (MTurk) and 200 participants were recruited from Prolific.
-The study was approved by the Institutional Review Board of Princeton University (\#11968), and all participants provided informed consent.
-Total study duration was approximately 20 minutes.
-Participants received monetary compensation for their time (rate USD \$12/hr), plus an incentive-compatible bonus up to \$1.00 based on task performance.
-
-Participants were eligible if they resided in the United States or Canada.
-Participants from MTurk were recruited with the aid of CloudResearch services \cite{litman2017turkprime-2} using their ``Approved participants''  data quality filters \cite{cloudresearch_2020-2}.
-As in the original study, MTurk workers were not excluded based on work approval rate or number of previous jobs approved \cite{robinson2019tapped-2}.
-No other exclusion criteria were applied during recruitment.
-
-Data from N=7 participants who completed the experiment were excluded prior to analysis because these participants (all from MTurk) disclosed that they had also completed the same experiment on the other platform.
-This left a final sample of N=393 participants (MTurk: N=193, Prolific: N=200) for analysis.
-The demographics of the sample split by labour market is provided in Table \ref{tab:demographics_02}.
-Participants recruited from MTurk were older on average ($\Delta M = 4.9 \ \text{yrs}, t = 4.248, p < 0.001$) and comprised of fewer women (35.2\% versus 61\%, $z = 4.248, p < 0.001$).
-
-\begin{table}[!h]
-\centering
-\small
-\setlength{\tabcolsep}{15pt}
-\begin{tabular}{ lrrrr }
-\toprule
-& \multicolumn{2}{c}{MTurk} & \multicolumn{2}{c}{Prolific} \\
-\cmidrule(lr){2-3} \cmidrule(lr){4-5}
-Total & \multicolumn{2}{c}{N=193} & \multicolumn{2}{c}{N=200} \\
-\midrule
-Age & N & \% & N & \% \\
-\cmidrule(lr){1-5}
-18-25   &    11 &   5.7 &     47 &  23.5 \\
-26-35   &    71 &  36.8 &     76 &  38.0 \\
-36-45   &    60 &  31.1 &     41 &  20.5 \\
-46-55   &    29 &  15.0 &     22 &  11.0 \\
-55+     &    22 &  11.4 &     14 &   7.0 \\
-\midrule
-Gender & N & \% & N & \% \\
-\cmidrule(lr){1-5}
-Female &      68 &  35.2 &      122 &  61.0 \\
-Male   &     124 &  64.2 &       73 &  36.5 \\
-Other  &       1 &   0.5 &        5 &   2.5 \\
-\midrule
-Ethnicity & N & \% & N & \% \\
-\cmidrule(lr){1-5}
-Hispanic or Latino     &    16 &   8.3 &     12 &   6.0 \\
-Not Hispanic or Latino &   177 &  91.7 &    180 &  90.0 \\
-Rather not say         &     0 &   0.0 &      8 &   4.0 \\
-\midrule
-Race & N & \% & N & \% \\
-\cmidrule(lr){1-5}
-American Indian/Alaska Native &     2 &   1.0 &      0 &   0.0 \\
-Asian                         &    15 &   7.8 &     41 &  20.5 \\
-Black or African American     &    13 &   6.7 &     12 &   6.0 \\
-White                         &   156 &  80.8 &    133 &  66.5 \\
-Multiracial                   &     6 &   3.1 &     10 &   5.0 \\
-Rather not say                &     1 &   0.5 &      4 &   2.0 \\
-\bottomrule
-\end{tabular}
-\captionsetup{width=0.88\textwidth}
-\caption{The demographics of each sample by online labour market.}
-\label{tab:demographics_02}
-\end{table}
-
-\subsubsection*{Experiment}
-
-Participants completed a gamified version of the two-step task \cite{daw2011model} designed to dissociate ``model-free'' and ``model-based'' decision-making.
-On every trial of the task, participants' goal is to collect as much ``space treasure'' as possible by traveling to one of two different planets and ``trading'' with one of two aliens who live on that planet.
-Participants first chose between two different-colored rocket ships (first-stage choice).
-Each rocket ship had a 70\% chance of traveling to one particular planet (e.g., the green rocket ship to the blue planet and the purple rocket ship to the red planet; common transitions) and a 30\% chance of traveling to the other planet (uncommon transition).
-The rocket ship and planet colors were randomized across participants, as were the mappings between rocket ships and planets.
-On each planet, participants chose which of two aliens to ``trade'' with (second-stage choice).
-If chosen, an alien would give the participant ``treasure'' with some slowly-changing probability, otherwise it would give ``junk''.
-The reward probabilities for each alien and trial were generated according to independent Gaussian random walks.
-Participants completed 201 trials of the task, with an optional break after the first half.
-
-Prior to the beginning of the experiment, participants had to read a set of instructions in which they were told that the rocket ships mostly traveled to one planet, but sometimes went to the other, and that the chance an alien would give them treasure would change slowly over the course of the task.
-Before they could start the task, participants had to correctly answer three sets of comprehension questions about the instructions.
-Failing to correctly answer all items forced the participant to reread a section of the instructions.
-Participants were permitted up to ten retries of the comprehension questions before they were removed from the experiment; however, no participant exceeded this limit.
-
-The task was programmed in jsPsych \cite{deleeuw_2015_jspsych-2} and distributed using custom web-application software.
-The experiment code is available at \url{https://github.com/nivlab/sciops}, and the web-software is available at \url{https://github.com/nivlab/nivturk}.
-A playable demo of the task is available at \url{https://nivlab.github.io/jspsych-demos/tasks/two-step/experiment.html}.
-
-\subsubsection*{Self-report measures}
-
-Prior to the start of the two-step task, participants completed four self-report measures in a randomized order.
-One was the 14-item seven-up/seven-down scale (7u/7d; \cite{youngstrom_2013_susd-2}), which measures lifetime incidence of depressive and (hypo)mania symptoms.
-This scale is expected to elicit lower rates of symptom endorsement, thereby resulting in asymmetric (right-skewed) score distributions.
-Participants also completed a 7-item measure of general anxiety symptoms over the last year (e.g.
-``I was overwhelmed by anxiety.''; \cite{watson2022development}).
-This scale is expected to elicit moderate rates of symptom endorsement, thereby resulting in a symmetric score distribution.
-We therefore expected the depression and mania measures to be at greater risk for spurious correlations with behavior on the two-step task than the anxiety measure.
-
-In addition, participants completed a 6-item measure of artistic interests (e.g.
-``I believe in the importance of art''; \cite{ashton2007empirical}).
-Based on previous studies, this scale is expected to elicit high rates of endorsement, thereby resulting in an asymmetric score distribution.
-Finally, participants completed a 6-item measure of greed avoidance, which measures attitudes towards wealth and status (e.g.
-``I am out for my own personal gain''; \cite{ashton2007empirical}).
-Based on previous studies, this scale is expected to elicit moderate rates of endorsement, thereby resulting in a symmetric score distribution.
-We therefore expected the artistic interests scale to be at greater risk for spurious correlations with behavior on the two-step task than the greed avoidance scale .
-
-\subsubsection*{Correspondence of screening measures}
-
-As in the original study, we measured the correspondence of screening measures based on the task and self-report behavior.
-We calculated a number of standard measures of data quality from each participant's task behavior (four in total) and self-report responses (five in total).
-The self-report screening measures were identical to those used in the original study, except that we used (mostly) new infrequency items.
-We describe each of the new screening measures below.
-
-\subparagraph{Self-report screening measure: Infrequency items.} Infrequency items are questions for which all (or virtually all) attentive participants should provide the same response.
-We embedded four infrequency items across the self-report measures.
-Specifically, we used the following questions:
-
-\begin{enumerate}
-  \item Have there been times in your life where you blinked your eyes at least once per day? (Expected response: \textit{Very often})
-  \item Have there been times of a couple days or more when you were able to breathe underwater (without an oxygen tank)? (Expected response: \textit{Never or hardly ever})
-  \item I was worried about the canine World Cup. (Expected response: \textit{Not at all})
-  \item I have used a computer. (Expected response: \textit{Slightly Agree}, \textit{Agree}, or \textit{Strongly agree})
-\end{enumerate}
-
-Prior to conducting the study, the infrequency items were piloted on an independent sample of participants to ensure that they elicited one dominant response.
-We also included one instructed item (``Please select `Neutral' as your response'') to compare to the infrequency items.
-We measured the number of `suspicious' (i.e., incorrect) responses made by each participant to these questions.
-For thresholded analyses, participants were flagged if they responded incorrectly to one or more of these items.
-
-\subparagraph{Task-based screening variable: Side variability.} Side variability was defined as the fraction of trials a participant chose the left option (by pressing the left arrow key) across first stage choices during the two-step task.
-Side variability could range from 0.00 (only right arrow key used) to 1.00 (only left arrow key used).
-Extreme values (i.e.
-closer to zero or one) are indicative of more careless responding during the task, as the sides for which each choice option was displayed was determined randomly on each trial.
-
-\subparagraph{Task-based screening variable: Choice variability.} Choice variability was defined as the fraction of trials a participant chose the same first-stage choice option (randomized to the right or left side of the screen) during the two-step task.
-Choice variability could range from 0.00 (selected the green rocket ship exclusively) to 1.00 (selected the purple rocket ship exclusively).
-Extreme values (i.e.
-closer to zero or one) are indicative of more careless responding during the task as the most rewarding option changed throughout the task.
-
-\subparagraph{Task-based screening variable: Win-Stay Lose-Shift.} Win-stay lose-shift (WSLS) measures a participant's tendency to stay with a first-stage choice option following a second-stage reward versus shifting to a the other choice option following a non-reward.
-WSLS thus measures a participant's sensitivity to reward feedback.
-WSLS was estimated per participant via regression, predicting each first-stage choice (stay, switch) by the previous trial's outcome (reward, non-reward) and an intercept.
-We used the first (slope) term to represent a participant's WSLS tendency.
-Lower values of this term indicate less sensitivity to reward feedback and are thus indicative of more careless responding during the task.
-Thresholds for chance-level WSLS performance were determined by fitting the same regression model to 5000 randomly-generated datasets of first-stage choice (datasets were generated by matching the probability of staying with the previous trial's choice to the distribution observed empirically, but choices were otherwise independent across trials; that is, independent of previous outcome).
-The threshold for above-chance WSLS was defined as the 95th percentile of the distribution of slope estimates for the random data, corresponding to a one-tailed hypothesis test ($\alpha = 0.05$) that the slope coefficient is greater than zero.
-
-\subparagraph{Task-based screening variable: Response times.} ``Suspicious response time'' was defined as the proportion of first-stage choices with a response faster than 200ms.
-Greater proportions of outlier response times are indicative of more careless responding during the task.
-
-\subparagraph{Correspondence Analysis.} We measured the correspondence of the above screening measures via two complementary approaches.
-First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation.
-Second, we estimated the pairwise rate of agreement on the binarized measures using the Dice similarity coefficient (looking at the top 10\% most suspicious respondents for each measure).
-The former approach estimates two measures' monotonic association, whereas the latter approach estimates their agreement as to which participants were most likely engaging in C/IE responding.
-For significance testing, we used permutation testing wherein a null distribution of similarity scores (Spearman's correlations or Dice coefficients) was generated for each pair of screening measures by iteratively permuting participants' identities within measures and re-estimating the similarity.
-P-values were computed by comparing the observed score to its respective null distribution.
-We corrected for multiple comparisons using family-wise error rates \cite{winkler2014permutation-2}.
-
-\subsubsection*{Correlations between behavior and symptom measures}
-
-To quantify the effects of both task and self-report data screening on behavior-symptom correlations, we estimated the pairwise correlations between the scale scores of each self-report measure and several measures of model-agnostic performance on the two-step task \cite{gillan2016characterizing}.
-Logistic regression analyses were conducted with the \textit{statsmodels} package \cite{seabold2010statsmodels} in the python programming language.
-The model tested if participants' first-stage choice behavior (coded as Stay = 1, Switch = 0) was influenced by the previous trial's reward (coded as Rewarded = 1, Unrewarded = 0), previous trial's transition (coded as Common = 1, Uncommon = 0), and their interaction.
-Importantly, the interaction term between previous reward and transition is a proxy for the contribution of model-based learning to choice behavior \cite{gillan2016characterizing}.
-
-Correlations between the behavioral measures (i.e.
-logistic regression coefficients) and self-report measures were calculated using Spearman's rank correlation, after various forms of screening and exclusion.
-Significance testing was performed using the percentile bootstrap method \cite{wilcox2018guide-2} so as to avoid making any parametric assumptions.
-These correlation analyses were not corrected for multiple comparisons, since our overarching purpose was to demonstrate the extent of this issue across multiple behavioral measures and self-report symptoms.
-Any one of these correlations considered individually can be thought of as emulating a conventional analysis where fewer statistical tests would be performed.
-
-\subsection*{Results}
-
-\subsubsection*{Careless participants (often) appear symptomatic when the overall level of symptom endorsement is low}
-
-To begin our analysis of the replication dataset, we examined the number of participants flagged by the WSLS and infrequency item screening measures.
-Only 31 participants (8\%) were flagged as exhibiting choice behavior at or below statistically chance levels in the two-step task.
-In contrast, 55 participants (14\%) endorsed a logically invalid or improbable response on one or more of the infrequency items when completing the self-report measures.
-The proportion of participants flagged for C/IE responding was significantly greater on Mechanical Turk compared to Prolific for both task (MTurk: N=23/193; Prolific: N=8/200; $z=2.91, p=0.004$) and survey data (MTurk: 34/193; Prolific: 21/200; $z = 2.03, p = 0.042$).
-Across the four infrequency items, the average failure rate was 5.3\% (range: 2.5\% -- 8.9\%).
-In contrast, no participant failed the instructed item.
-This discrepancy in the proportion of participants flagged by each type of attention check is consistent with previous research, which found that instructed items are insensitive measures of C/IE responding \cite{barends2019noncompliant-2, thomas2017validity-2, hauser2016attentive-2}.
-
-\begin{figure}[t!]
-\includegraphics[width=15cm]{../figures/repl_02a.png}
-\centering
-\captionsetup{width=0.88\textwidth}
-\caption{Raincloud plots of total symptom scores in attentive (red) and C/IE (blue) participants.
-Each colored dot represents the symptom score for one participant.
-Black circles: average score within each group (error bars denote 95\% bootstrap confidence interval).
-Shaded plots: estimated distribution of responses for each group of participants.}
-\label{fig:repl_distributions}
-\end{figure}
-
-Previously, we observed a mean-shift in the average level of symptom endorsement for participants suspected of engaging in C/IE responding relative to attentive participants on measures for which the overall rate of symptom endorsement is low.
-This result was (mostly) replicated in the current dataset.
-Total scores were noticeably exaggerated in participants suspected of C/IE responding for the symptom measures where overall rates of symptom endorsement were the lowest (e.g.
-mania; Figure \ref{fig:repl_distributions}, leftmost plot).
-Where there were higher rates of symptom endorsement overall (e.g.
-anxiety), the distributions of symptom scores between the two groups of participants were more similar (Figure \ref{fig:repl_distributions}, middle plots).
-Permutation testing confirmed that observed mean-shifts in symptom scores for C/IE participants were statistically significant for the most skewed symptom measures (Table \ref{tab:rep_validation}).
-
-For the personality measures, however, an interesting pattern emerged (Figure \ref{fig:repl_distributions}, rightmost plots).
-We did not observe a statistically significant mean-shift in total scores for the subscale with the most skewed score distribution (i.e.
-artistic interests; $t = 1.87$, $p = 0.061$).
-However, an unexpected and statistically significant mean-shift in the average level of endorsement was observed for the more symmetrically-distributed greed-avoidance subscale ($t = 16.44$, $p < 0.001$).
-The reason for this finding is unclear.
-Regardless, this finding presents an opportunity to test for spurious correlations between behavioral and self-report measures in the presence of a mean-shift in scores in the absence of (substantially) skewed score distributions.
-
-\begin{table}[!t]
-\centering
-\small
-\begin{tabular}{lcccc}
-\toprule
-& & \multicolumn{3}{c}{Total Score} \\
-\cmidrule(lr){3-5}
-Subscale & Skew &  Attentive & C/IE & $t$-value \\
-\midrule
-Mania      &  1.07 &   3.25 &   6.27 & $-6.05^*$ \\
-Depression &  0.89 &   5.72 &   6.95 & $-1.57$   \\
-Anxiety    &  0.44 &   8.54 &   8.65 & $-0.13$   \\
-Artistic interests   & -0.92 &  28.07 &  26.29 & $1.87$    \\
-Greed avoidance     &  0.55 &  11.77 &  16.44 & $-4.17^*$  \\
-\bottomrule
-\end{tabular}
-\captionsetup{width=0.88\textwidth}
-\caption{Descriptive statistics of the self-report measures between attentive and C/IE participants.
-Skew: the empirical skewness of the distribution of total symptom scores.
-Total score: the average symptom score across attentive and C/IE participants.
-Stars indicate statistical significance at $p<0.05$.}
-\label{tab:rep_validation}
-\end{table}
-
-\subsubsection*{Low correspondence between task and self-report measures of C/IE responding}
-
-Next, we evaluated the degree of correspondence between behavioral and self-report screening measures to determine whether screening on behavior alone was sufficient to identify and remove careless participants.
-To measure the degree of correspondence between these behavioral and self-report screening measures, we performed two complementary analyses.
-First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation (Figure \ref{fig:repl_correspondence}, left panel).
-After correcting for multiple comparisons, there were a handful of significant correlations between the behavioral and self-report screening measures.
-Abnormal response times emerged as the metric most correlated with the self-report screening measure.
-Crucially, as in the original study, the sizes of these observed correlations were roughly half those observed for the correlations between the self-report measures.
-
-\begin{figure}[!t]
-\includegraphics[width=16cm, trim=0 0 3cm 0]{../figures/repl_02b.png}
-\centering
-\captionsetup{width=0.88\textwidth}
-\caption{Similarity of task and self-report data screening measures.
-Each tile corresponds to the Spearman rank correlation (left) and Dice similarity coefficient (right) between two screening measures.
-Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; SV = side variability; CV = choice variability; WSLS = win-stay lose-shift rate; RT = suspicious response times.
-Similarity scores have been thresholded after correcting for multiple comparisons.
-Numbers denote the strength of statistically significant correlations.
-Cross-modality correlations between task-behavior (left) and infrequency-item self-report measures (bottom) are in the dashed rectangle.}
-\label{fig:repl_correspondence}
-\end{figure}
-
-Second, we used the Dice similarity coefficient to quantify agreement between different screening methods in the set of participants flagged for exclusion (Figure \ref{fig:repl_correspondence}, right panel).
-This approach quantifies the degree of overlap between the set of would-be excluded participants based on different screening measures under a common exclusion rate.
-Results were largely consistent with the correlation analysis: only a handful of task and self-report screening measures achieved levels of agreement greater than what would be expected by chance.
-Of the significant cross-modality pairs, the average similarly coefficient was less than 0.4.
-In other words, when any of these sets of two measures are used to identify the top 10\% of participants most strongly suspected of C/IE responding, they agree on only two out of every five participants.
-Screening on task behavior alone would fail to identify the majority of participants most likely engaging in C/IE responding.
-
-Taken together, these findings corroborate the results of the original study: measures of C/IE responding in task and self-report data do not identify the same set of participants.
-This means that solely excluding participants on the basis of poor behavioral performance---the most common approach in online studies---is unlikely to identify participants who engage in C/IE responding on self-report surveys.
-
-\subsubsection*{Spurious symptom-behavior correlations produced by C/IE responding}
-
-To understand the effects of applying different forms of screening, we estimated the correlations between each unique pairing of a self-report measure and measure of behavior under four different conditions: no screening, screening only on task behavior (i.e.
-removing participants whose win-stay lose-shift behavior was not above chance), screening only on self-report responses (i.e.
-removing only participants who responded incorrectly on one or more infrequency items), or both.
-The resulting pairwise behavior-symptom correlations following each screening procedure are presented in Figure \ref{fig:repl_correlations}.
-We note that we did not correct these correlation analyses for multiple comparisons, since our purpose was to demonstrate the extent of this issue across multiple behavioral measures and self-report symptoms.
-Any one of these correlations considered individually can be thought of as emulating a conventional analysis where fewer statistical tests would be performed.
-
-When no rejections were applied (i.e.
-all participants were included; Figure \ref{fig:repl_correlations}A), we observed multiple significant correlations between measures of task behavior and symptom scores for hypomania and depression.
-Consistent with our predictions, these correlations involved measures with low overall endorsement rates and mean-shifts in score distributions between attentive and C/IE participants.
-Conversely, we found no significant correlations with the symmetrically-distributed anxiety scores.
-This is despite the fact this scale measures symptoms that are comorbid with depression and mania.
-Crucially, of the two personality measures, we observed significant correlations only for the measure found to exhibit a mean-shift in scores between attentive and C/IE participants (i.e.
-greed avoidance).
-These included a significant correlation with the interaction term, which is used as a proxy measure for model-based choice behavior.
-That is, significant correlations were not restricted only to general behavioral measures but also to measures of specific theoretical interest.
-
-Next, we excluded participants from the analysis based on task-behavior screening (i.e.
-lack of win-stay lose-shift behavior, removing the 8\% of participants exhibiting behavior indistinguishable from chance; Figure \ref{fig:repl_correlations}B).
-In contrast to the findings of the original study, the pattern of correlations was meaningfully changed: the putatively spurious correlations between greed avoidance and performance on the two-step task were ablated.
-Two previously significant correlations between hypomania and two-step performance were also rendered non-significant.
-A similar pattern of results was observed when we rejected participants based on self-report screening (removing 14\% of participants who endorsed one or more invalid or improbable responses on the infrequency items; Figure \ref{fig:repl_correlations}C) and when rejections were applied based on both task and self-report screening measures (removing 18\% of participants; Figure \ref{fig:repl_correlations}D).
-
-\begin{figure}[!t]
-\includegraphics[width=17cm]{../figures/repl_03a.png}
-\centering
-\captionsetup{width=0.88\textwidth}
-\caption{Absolute Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions.
-Only statistically significant correlations are shown ($p<0.05$, not corrected for multiple comparisons).
-Black Xs indicate significant correlations ablated under screening.
-No Screening = no exclusions; WSLS Only = exclusions based on chance-level performance in the two-step task; Infrequency Only = exclusions based on invalid or improbable responses to infrequency items; Both Types = exclusions based on the previous two measures.
-Acronyms: PrevRew = sensitivity to reward on the previous trial; PrevTrans = sensitivity to transition type on previous trial; MB/MF = index of model-based/model-free behavior (interaction between \textit{PrevRew} \& \textit{PrevTrans}).}
-\label{fig:repl_correlations}
-\end{figure}
-
-These findings suggest that some of the significant behavior-symptom correlations observed without strict participant screening may indeed be spurious correlations driven by C/IE responding.
-Interestingly, in contrast to the original study, with a more demanding behavioral task, screening based on either task behavior or self-report behavior alone was sufficient to protect against spurious symptom-behavior correlations in the presence of mean-shifts in scores between attentive and C/IE participants.
-For example, both forms of screening ablated the would-be significant correlation between model-based behavior and greed avoidance.
-The discrepancy in results between the original and replication studies may reflect the smaller numbers of participants failing attention checks in the replication study (14\%) compared to the original study (22\%), as well as differences in the behavioral tasks.
-Regardless, we replicate the findings of the original study in that screening on self-report data allowed us to identify symptom-behavior correlations most likely to be spurious.
-
-\subsection*{Discussion}
-
-Here we reported findings from a replication study whose purpose was to examine the generalizability of our original findings under new labour market conditions, different behavioral measures, and different self-report measures.
-To this end, we recruited an independent sample of almost 400 participants, using CloudResearch's and Prolific's latest data-quality filters, to complete the two-step task and a novel set of self-report measures.
-As evidence of the efficacy of the new data-quality filters, the proportion of participants flagged for C/IE responding in the self-report measures was noticeably smaller in the replication sample (14\%) compared to original sample (22\%).
-This decrease in the number of participants suspected of C/IE responding was observed for both MTurk and Prolific (though, as in the original study, the proportion of low-quality participants was significantly, albeit marginally, smaller for Prolific than MTurk).
-Regardless, although the new online labour platform quality-control measures seem to be effective, they did not completely solve the problem; indeed, the proportion of participants engaging in C/IE responding was reduced only by one-third.
-
-Next, we compared the distribution of self-report scale scores for attentive participants and participants suspected of engaging in C/IE responding.
-Replicating our previous result, we observed a mean-shift in the average level of symptom endorsement for participants suspected of C/IE responding relative to attentive participants, only when the overall rate of symptom endorsement was low.
-Specifically, flagged participants showed significantly elevated scores on the hypomania scale (with its right-skewed score distribution) but not so on the anxiety scale (with its symmetric score distribution).
-Interestingly, we found the opposite pattern for the personality measures: scores for participants engaging in C/IE responding were not significantly different than those of their attentive counterparts on the artistic interests scale (with its left-skewed score distribution), but was so for the greed avoidance scale (with its more symmetric score distribution).
-One possible explanation for the discrepancy in findings between the symptom and personality measures is the direction of the skew for the artistic interests scale.
-Previously, using random-intercept item factor analysis, we observed that participants engaging in C/IE responding were more likely to use the right-half of the response scale.
-As such, such a pattern of responding is more likely to produce a mean-shift in scale scores, compared to attentive participants, on a scale with a right-skewed distribution (e.g.
-mania, depression scales) than a scale with a left-skewed distribution (e.g.
-artistic interests scale).
-Further research is still needed to characterize patterns of C/IE responding.
-
-The results in the replication study did corroborate the findings of the original study in terms of the degree of correspondence between behavioral and self-report screening measures, suggesting that measures of C/IE responding in task and self-report data do not identify the same set of participants.
-Even with a more difficult task (i.e., the two-step task), we observed relatively low correspondence between self-report and task-based screening measures.
-This supports our suggestion that both forms of screening are necessary to identify participants providing low-quality responses.
-Finally, we examined the consequences of various types of screening methods for correlations between behavioral and self-report measures.
-As in the original study, we detected significant spurious correlations when no screening was applied.
-This included correlations between model-based planning on the two-step task and scores on the greed avoidance scale, for which there is no theoretical reason to predict a correlation.
-Instead, this correlation almost certainly reflects the mean-shift in scores between attentive participants and participants flagged for C/IE responding on the greed avoidance scale.
-As evidence of this, excluding participants who failed one or more infrequency items ablated this correlation.
-In contrast to the original study, excluding participants based on poor performance on the two-step task was also sufficient to ablate this correlation.
-Thus, there may be instances where screening based on poor behavioral performance is sufficient to prevent spurious correlations.
-However, in the absence of perfect information as to when those situations should arise, we conclude that it is simply safer to screen participants on both dimensions of performance.
-
-In summary, we conclude that the results of the original study are not limited to the task and self-report measures used in that study, or to online platforms at a particular point in time.
-Despite legitimate advances in data quality controls, online labour platforms still suffer from participants engaging in C/IE responding.
-Given \textit{a priori} uncertainty regarding the ability of task measures alone to screen such participants, we recommend also using infrequency items to detect inattentive responding on self-report measures.
-Finally, and most importantly, this second study strengthened the finding that C/IE responding is likely to result in mean-shifts in scores for symptom scales with overall low rates of endorsement, which are in turn capable of yielding spurious correlations between self-report and behavioral measures.
-The best safeguard against such spurious correlations continues to be screening in both domains.
-
-\break
-
-\section*{\texorpdfstring{\hl{Appendix C: Attention checks in healthy and psychiatric patients}{}}}
-
-\subsection*{Background \& motivation}
-
-One concern with using attention checks for screening and exclusion of participants is that we might inadvertently introduce an overcontrol bias \cite{elwert2014endogenous-2}.
-That is, to the extent that C/IE responding reflects symptoms of psychopathology such as lack of motivation \cite{barch2015mechanisms-2}, avoidance of effort \cite{cohen2001impairments-2, culbreth2016negative-2}, or more frequent lapses of attention \cite{kane2016individual-2, robison2017neurotic-2}, it is plausible that rigorous screening of C/IE responding might lead to the differential exclusion of truly symptomatic participants.
-As a result, true associations between poor or different task performance and psychopathology symptoms could go undetected (type II error).
-The purpose of the below preliminary and exploratory study was to examine whether individuals with a confirmed psychiatric disorder were indeed more likely than healthy controls to fail attention checks embedded in self-report symptom scales.
-
-\subsection*{Methods}
-
-\subsubsection*{Participants}
-
-Participants were recruited as part of two independent studies to investigate reward processing in individuals with and without a history of major depression and bipolar disorder (results of those studies not reported here).
-Both studies required participants to complete (1) a structured clinical interview (the SCID-5) with a trained interviewer to verify that they met the criteria for one or more psychiatric disorders, and (2) a series of computerized self-report surveys and cognitive tasks.
-
-In both studies, participants volunteered for a multi-session study conducted online via video conferencing.
-Specifically, participants completed each session from their homes while on Zoom with a study coordinator.
-During each session, while participants were completing self-report questionnaires or behavioral tasks, the study coordinator turned off their camera and microphone, but was available if the participant had any questions.
-
-Participants were recruited through clinician referral and online ads (i.e., Google ads, Craigslist) targeting individuals with a history of depression, anhedonia, apathy, and/or (hypo)mania symptoms.
-Participants were eligible for participation if they (1) had no history of head injury resulting in loss of consciousness for more than 20 minutes; (2) had not been diagnosed with intellectual disability; (3) had not been diagnosed with any neurological condition; (4) did not meet criteria for substance dependence (excluding nicotine) in the past 6 months; (5) had not received electroconvulsive therapy in the past 8 weeks; and (6) were aged between 18-65.
-For one of the two studies, participants were also required to score 6 or higher on the Wechsler Test of Adult Reading to be included in the study.
-Furthermore, clinical participants were eligible if they met criteria for a diagnosis of major depressive disorder and, if they were on medication, they had been on on stable treatment with this medication for at least the past 4 weeks.
-Non-clinical (control group) participants were eligible if they did not meet criteria for any psychiatric diagnosis and were not currently taking any medication used to treat psychiatric disorders.
-
-\subsubsection*{Infrequency items}
-
-To measure and compare C/IE responding between healthy and psychiatric participants, we used two sets of attention checks.
-Each set was composed of three infrequency items and one instructed item.
-Participants were assigned one or the other set.
-The six infrequency items were:
-
-\begin{enumerate}
-    \item Worrying too much about the 1977 Olympics. (Expected response: \textit{Not at all})
-    \item I have never used a computer. (Expected response: \textit{Completely untrue} or \textit{Quite untrue})
-    \item I would be able to lift a small (1 lb) weight. (Expected response: \textit{Extremely characteristic of me} or \textit{Somewhat characteristic of me})
-    \item Have there been times of a couple days or more when you were able to stop breathing entirely (without the aid of medical equipment)? (Expected response: \textit{Never})
-    \item Over the past year, how often did you have days where you were able to blink your eyes without difficulty? (Expected response: \textit{Often} or \textit{Very often})
-    \item I am generally able to remember my own name. (Expected response: \textit{True})
-\end{enumerate}
-
-\subsubsection*{Analysis}
-
-Of primary interest here was whether psychiatric patients fail infrequency item attention checks at equal or at greater rates than healthy participants.
-To test this, we conducted Bayesian hypothesis testing using Bayes factors \cite{harms2018making}.
-Specifically, we defined three competing models:
-
-\begin{itemize}
-    \item $M_0: \text{Binom}(N_1, p), \text{Binom}(N_2, p)$  
-    \item $M_1: \text{Binom}(N_1, p - \delta), \text{Binom}(N_2, p + \delta)$  
-    \item $M_2: \text{Binom}(N_1, p + \delta), \text{Binom}(N_2, p - \delta)$  
-\end{itemize}
-
-where $N_1$ and $N_2$ are the observed number of healthy and psychiatric participants, respectively; $p$ is the latent probability of a participant failing one or more attention checks; and $\delta$ is an offset parameter specifying the hypothesized difference in failure rates between groups.
-Thus, $M_0$ assumes equal rates of failures between healthy and psychiatric participants, whereas $M_1$ and $M_2$  assume greater and lower rates, respectively, for psychiatric participants compared to healthy participants.
-The common latent probability, $p$, was set to the observed average rate across the two groups.
-The offset, $\delta$, was set to 0.05.
-This value was selected because it signifies a difference in portions of $\Delta p = 0.1$, corresponding to a small effect for a difference in proportions test ($h = 0.2$; \cite{cohen2013statistical}).
-
-\subsection*{Results}
-
-In total, 16 of 65 (24.6\%) participants failed one or more attention checks.
-Interestingly, the overall proportion of flagged participants was similar to that observed for the original study.
-Subdivided by group, 6 of 20 healthy participants (30\%) and 10 of 45 psychiatric participants (22\%) were flagged for C/IE responding.
-Unsurprisingly, given the modest sample size, the difference between the two proportions was not significantly different from zero ($z = 0.672$, $p = 0.502$).
-Across the six infrequency items, the average failure rate was 8.5\% (range: 0.0\% -- 19.7\%).
-In contrast, no participant failed either instructed item.
-This result further corroborates previous research, which has found that instructed items are poor measures of C/IE responding \cite{barends2019noncompliant-2, thomas2017validity-2, hauser2016attentive-2}.
-
-Next, we computed the Bayes factor for each pair of candidate models.
-A model assuming equal rates of failure between healthy and psychiatric participants was 2.88 times more likely than the model assuming greater rates for psychiatric patients.
-In turn, a model assuming lower rates of failure for psychiatric patients was 1.27 times more likely than the model assuming equal rates.
-Finally, a model assuming lower rates of failure for psychiatric patients was 3.65 times more likely than the model assuming higher rates for psychiatric patients.
-Only the final comparison exceeds the cutoff value of 3, which is conventionally treated as the minimal amount of evidence required to treat a model comparison as meaningful.
-
-\subsection*{Discussion}
-
-Here we sought to examine whether actual psychiatric patients were equally or more likely to fail infrequency items than healthy controls in settings similar to those experienced by online participants (i.e., completing an experiment online, on a computer in one's home or otherwise chosen environment).
-Although the small sample precludes any definitive conclusion, it is noteworthy that the model least consistent with the data was the one where psychiatric patients were more likely to fail infrequency-item attention checks.
-Indeed, a model in which healthy controls failed attention checks at a greater rate than patients was credibly preferred to the alternative.
-This preliminary finding may reflect differences in motivation between patients and controls for participating in psychiatric research.
-Indeed, whereas healthy controls may be primarily motivated to participate for monetary purposes, patients may be motivated to participate to further scientific research that may ultimately benefit them (or others suffering from the same conditions).
-That is, patients may have more ``stakes in the game,'' and therefore may be motivated to provide higher-quality responses.
-Regardless, further research is required to examine whether this preliminary finding holds in larger samples and other testing contexts.
-
-\section*{Supplementary references}
-
-\printbibliography[heading=supp]
-\end{refsection}
-
 \end{document}

### 2023-04-01 manuscripts/supp.tex
checkpointing revisions progress

% set document class
\documentclass[a4paper,notitlepage,12pt]{article}

% load packages
\usepackage[utf8]{inputenc}
\usepackage[a4paper, margin=0.8in]{geometry}
\usepackage{authblk}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{indentfirst}
\usepackage{xr-hyper} % for cross-referencing between documents
\usepackage{hyperref}
\usepackage{float}
\usepackage{amsmath}
\usepackage[backend=biber,style=nature]{biblatex}
\usepackage[flushmargin]{footmisc}
\usepackage[flushleft]{threeparttable}
\usepackage{array}
\usepackage[font=small, labelfont=it]{caption}
\usepackage{booktabs}
\usepackage{xcolor,soul}

% specify footnote margins
\renewcommand\footnotelayout{%
  \advance\leftskip 0.7cm
  \advance\rightskip 0.7cm
 }

% setup references
\defbibheading{supp}{}
\addbibresource[label=supp]{supp.bib}
\renewcommand*{\bibfont}{\small}

% specify link style
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    citecolor=blue
}

% define highlight style
\colorlet{usercolorname}{yellow!00}    % use for public version
% \colorlet{usercolorname}{yellow!30}    % use for reviewer version
\sethlcolor{usercolorname}

% specify images path relative to the main .tex file 
\graphicspath{ {./figures/} }

% specify some custom commands
\renewcommand{\baselinestretch}{1.2}
\renewcommand*{\Authsep}{, }
\renewcommand*{\Authand}{, }
\renewcommand*{\Authands}{, }
\renewcommand*{\Affilfont}{\normalsize}

% set up the author block
\setlength{\affilsep}{2em}   % set the space between author and affiliation
\author[1,*]{Samuel Zorowitz}
\author[2]{Johanne Solis}
\author[1,3]{Yael Niv}
\author[4]{Daniel Bennett}
\affil[1]{Princeton Neuroscience Institute, Princeton University, NJ, USA}
\affil[2]{Rutgers-Princeton Center for Computational Cognitive Neuropsychiatry, Rutgers University, NJ, USA}
\affil[3]{Department of Psychology, Princeton University, NJ, USA}
\affil[4]{School of Psychological Sciences, Monash University, Victoria, Australia}
\affil[*]{Corresponding author (zorowitz@princeton.edu)}

% specify the title
\title{Supplementary materials for ``Inattentive responding can induce spurious associations between task behavior and symptom measures''}

% turn date off
\date{}

% Define paragraph formatting
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

\begin{document}

\maketitle
\begin{refsection}[supp]

\clearpage
\section*{Appendix A}
\setcounter{figure}{0}
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\thefigure}{S\arabic{figure}}

\subsection*{Signed correlation analysis}

\begin{figure}[h]
    \includegraphics[width=17cm]{../figures/supp_01.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{Signed Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions. Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons). Black Xs indicate significant correlations ablated under screening. No Screening = no exclusions; Accuracy Only = exclusions based on chance-level performance in the reversal-learning task; Infrequency Only = exclusions based on invalid or improbable responses to infrequency items; Both Types = exclusions based on the previous two measures. Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
    \label{fig:correlations_s1}
\end{figure}

\clearpage
\subsection*{Bootstrapping Analysis}
\begin{figure}[H]
    \includegraphics[width=16cm]{../figures/supp_02.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{The pattern of significant behavior-symptom correlations before (panel A) and after (panel B) screening compared to the resulting pattern when random subsets of participants (22\% of total, matched to screening using the infrequency measure) are removed (panel C). Panels A and B are reproduced from Figure \ref{fig:correlations} for convenience. Panel C: the fraction of significant correlations in 5000 bootstrapped samples. Panel D: The similarity of the pattern of correlations after removal of random subsets to that before and after screening using the infrequency measure. Similarity was calculated using the simple matching coefficient. Random removal subsets were significantly more similar to the ``No Screening" than to the ``Infrequency" screening datasets (two-tailed, paired-samples $t$-test: $t = 262.490$, $p < 0.001$, $d = 3.713$, 95\% CI = [0.136, 0.138]).}
    \label{fig:random}
\end{figure}

\clearpage
\subsection*{The relationship between sample size and false positive rates generalize to other sets of variables}
\begin{figure}[H]
    \includegraphics[width=16cm]{../figures/supp_03.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{False positive rates for spurious correlations \emph{increase} with sample size. \textit{Left:} Bootstrapped Spearman correlations between inverse temperature ($\beta$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants. The grey error bars indicate 95\% bootstrap confidence intervals. The thick dashed lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size. Markers are jittered along the x-axis for legibility. \textit{Right:} False positive rates for inverse temperature ($\beta$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants. False positive rate was calculated as the proportion of bootstrap samples in which the correlation between $\beta$ and 7-down was statistically significant. The horizontal dotted line denotes the expected false positive rate at $\alpha = 0.05$.}
    \label{fig:bootstrap_s1}
\end{figure}

\clearpage
\subsection*{The relationship between sample size and true positive rates for true correlations}
\begin{figure}[H]
    \includegraphics[width=16cm]{../figures/supp_04.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{True correlations are independent of the proportion of C/IE participants in the sample. \textit{Left:} Bootstrapped Spearman correlations between learning rate asymmetry ($\kappa$) and anxiety scores (GAD-7) as a function of sample size and proportion of C/IE participants. The grey error bars indicate 95\% bootstrap confidence intervals. The thick dashed lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size. Markers are jittered along the x-axis for legibility. \textit{Right:} True positive rates for learning rate asymmetry ($\kappa$) and anxiety scores (GAD-7) as a function of sample size and proportion of C/IE participants. True positive rate was calculated as the proportion of bootstrap samples in which the correlation between $\kappa$ and GAD-7 was statistically significant. The horizontal dotted line denotes the expected false positive rate at $\alpha = 0.05$.}
    \label{fig:bootstrap_s2}
\end{figure}

\clearpage

\subsection*{Posterior predictive checks}
\begin{figure}[H]
    \includegraphics[width=16cm]{../figures/supp_05.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{Posterior predictive checks for the risk-sensitive temporal difference learning model. \textit{Panel A:} Observed (black) and predicted (blue) learning curves averaged across the group. \textit{Panel B:} Observed versus predicted choice accuracy for each participant. \textit{Panel C:} Distribution of average predictive density across participants.}
    \label{fig:posterior_check}
\end{figure}

\clearpage
\subsection*{Participant demographics}
\begin{table}[!h]
    \centering
    \small
    \setlength{\tabcolsep}{15pt}
    \begin{tabular}{ rrrrr }
        \toprule
        & \multicolumn{2}{c}{MTurk} & \multicolumn{2}{c}{Prolific} \\
        \cmidrule(lr){2-3} \cmidrule(lr){4-5}
        Total & \multicolumn{2}{c}{N=186} & \multicolumn{2}{c}{N=200} \\
        \midrule
        Age & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        18-25   &      16 &   8.6 &       78 &  39.0 \\
        26-35   &      76 &  40.9 &       69 &  34.5 \\
        36-45   &      46 &  24.7 &       31 &  15.5 \\
        46-55   &      22 &  11.8 &       13 &   6.5 \\
        55+     &      26 &  14.0 &        9 &   4.5 \\
        \midrule
        Gender & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        Female             &    83 &  44.6 &    112 &  56.0 \\
        Male               &   103 &  55.4 &     85 &  42.5 \\
        Other              &     0 &   0.0 &      3 &   1.5 \\
        \midrule
        Ethnicity & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        Hispanic or Latino     &    15 &   8.1 &     10 &   5.0 \\
        Not Hispanic or Latino &   168 &  90.3 &    183 &  91.5 \\
        Rather not say         &     2 &   1.1 &      7 &   3.5 \\
        Unknown                &     1 &   0.5 &      0 &   0.0 \\
        \midrule
        Race & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        African American                 &    21 &  11.3 &      7 &   3.5 \\
        Asian                                     &     5 &   2.7 &     53 &  26.5 \\
        White                                     &   151 &  81.2 &    121 &  60.5 \\
        Multiracial                               &     6 &   3.2 &      4 &   2.0 \\
        Rather not say                            &     1 &   0.5 &     12 &   6.0 \\
        \midrule
        Use other platform & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        Yes            &      71 &  38.2 &       28 &  14.0 \\
        No             &     115 &  61.8 &      172 &  86.0 \\
        \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{The demographics of each sample by online labor market. On average, the samples were similar though the sample from Mechanical Turk was older (two-tailed, two-sample $t$-test: $t(384)=6.567$, $p<0.001$, $d=0.669$, 95\% CI = [5.4, 10.0]) and comprised of fewer women (two-tailed, two-sample proportions test: $z(384)=2.529$, $p=0.011$, $h=0.258$, 95\% CI = [0.030, 0.228]). Note: the demographics do not include 20 participants excluded for participating in the study twice, once per platform.}
    \label{tab:demographics}
\end{table}

\clearpage
\subsection*{Careless participants show different behaviors on the reversal learning task}
\begin{table}[H]
    \centering
    \begin{tabular}{lrrr}
    \toprule
    {} &  Attentive &    C/IE &   $t$-value \\
    \midrule
    Acc      &      0.587 &   0.532 &  $4.008^*$  \\
    Pts      &     50.163 &  47.729 &  $2.376^*$  \\
    WS       &      0.898 &   0.776 &  $5.387^*$  \\
    LS       &      0.609 &   0.751 &  $-5.335^*$ \\
    Pers     &      0.245 &   0.259 &  $-1.505$ \ \\
    $\beta$  &      6.754 &   4.082 &  $5.404^*$  \\
    $\eta_p$ &      0.643 &   0.551 &  $2.846^*$  \\
    $\eta_n$ &      0.738 &   0.784 & $-1.516$ \  \\
    $\kappa$ &     -0.069 &  -0.218 &  $3.729^*$  \\
    \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{Measures of task behavior compared between attentive and C/IE participants. Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry. *Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
\end{table}

\clearpage
\subsection*{Correspondence of screening measures}

The following are the unthresholded results of the screening measure correspondence analyses.

\begin{table}[H]
    \centering
    \small
    \begin{tabular}{rccccccccc}
    \toprule
    {} &      INF &      ISD &      REL &      MAH &    READ &     VAR &     ACC &   WSLS & RT \\
    \midrule
    INF  &        - &          &          &          &         &         &         &        &    \\
    ISD  &   0.372* &        - &          &          &         &         &         &        &    \\
    REL  &  -0.408* &  -0.811* &        - &          &         &         &         &        &    \\
    MAH  &   0.406* &   0.843* &  -0.643* &        - &         &         &         &        &    \\
    READ &   -0.111 &   0.193* &  -0.168* &    0.138 &       - &         &         &        &    \\
    VAR  &   -0.061 &   -0.029 &    0.058 &   -0.024 &  -0.026 &       - &         &        &    \\
    ACC  &  -0.206* &   -0.154 &    0.099 &  -0.182* &  -0.074 &   0.027 &       - &        &    \\
    WSLS &    0.060 &    0.102 &   -0.089 &    0.115 &   0.103 &  -0.060 &  0.221* &      - &    \\
    RT   &    0.040 &   -0.019 &    0.014 &    0.013 &  -0.158 &  -0.007 &  -0.094 &  -0.05 &  - \\
    \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{Spearman's rank correlations of task and self-report data screening measures. Each entry corresponds to the Spearman correlation between two screening measures. Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times. *Denotes statistical significance after correcting for multiple comparisons.}
\end{table}

\begin{table}[H]
    \centering
    \small
    \begin{tabular}{rccccccccc}
    \toprule
    {} &     INF &     ISD &     REL &    MAH &   READ &    VAR &     ACC &  WSLS & RT \\
    \midrule
    INF  &       - &         &         &        &        &        &         &       &    \\
    ISD  &  0.462* &       - &         &        &        &        &         &       &    \\
    REL  &  0.484* &  0.691* &       - &        &        &        &         &       &    \\
    MAH  &  0.516* &  0.732* &  0.619* &      - &        &        &         &       &    \\
    READ &   0.319 &   0.165 &   0.165 &  0.216 &      - &        &         &       &    \\
    VAR  &   0.208 &   0.216 &   0.238 &  0.259 &  0.292 &      - &         &       &    \\
    ACC  &  0.379* &   0.312 &   0.258 &  0.344 &  0.237 &  0.282 &       - &       &    \\
    WSLS &   0.253 &   0.247 &   0.227 &  0.258 &  0.299 &  0.303 &  0.505* &     - &    \\
    RT   &   0.267 &   0.219 &   0.271 &  0.271 &  0.333 &  0.251 &   0.239 &  0.26 &  - \\
    \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{Dice similarity coefficients (top 10\%) for task and self-report data screening measures. Each entry corresponds to the Dice coefficient between two screening measures for the 10\% most suspicious participants. Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times. *Denotes statistical significance after correcting for multiple comparisons.}
\end{table}

\begin{table}[H]
    \centering
    \small
    \begin{tabular}{rccccccccc}
    \toprule
    {} &     INF &     ISD &     REL &    MAH &    READ &    VAR &     ACC &   WSLS & RT \\
    \midrule
    INF  &       - &         &         &        &         &        &         &        &    \\
    ISD  &  0.355* &       - &         &        &         &        &         &        &    \\
    REL  &  0.355* &  0.564* &       - &        &         &        &         &        &    \\
    MAH  &  0.355* &  0.667* &  0.359* &      - &         &        &         &        &    \\
    READ &  0.290* &   0.231 &   0.154 &  0.231 &       - &        &         &        &    \\
    VAR  &   0.116 &   0.080 &   0.080 &  0.160 &   0.133 &      - &         &        &    \\
    ACC  &  0.269* &   0.137 &   0.164 &  0.192 &   0.247 &  0.171 &       - &        &    \\
    WSLS &   0.242 &   0.103 &   0.154 &  0.205 &   0.231 &  0.240 &  0.630* &      - &    \\
    RT   &   0.164 &   0.105 &   0.132 &  0.184 &  0.289* &  0.164 &   0.225 &  0.237 &  - \\
    \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{Dice similarity coefficients (top 25\%) for task and self-report data screening measures. Each entry corresponds to the Dice coefficient between two screening measures for the 25\% most suspicious participants. Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times. *Denotes statistical significance after correcting for multiple comparisons.}
\end{table}

\clearpage
\subsection*{Correlations between behavior and symptom measures}

The following are the unthresholded results of the correlation analyses between task behavior and self-reported symptoms.

\begin{table}[H]
    \centering
    \small
    \begin{tabular}{rccccccc}
    \toprule
    {} &       7u &       7d &    GAD-7 &      BIS &     BAS &   SHAPS &    PSWQ \\
    \midrule
    Acc      &  -0.295* &  -0.166* &  -0.093* &  -0.134* &  -0.020 &  -0.051 &  -0.037 \\
    Pts      &  -0.225* &   -0.076 &   -0.023 &  -0.144* &  -0.061 &  -0.051 &   0.024 \\
    WS       &  -0.327* &  -0.160* &  -0.129* &  -0.171* &  -0.006 &  -0.048 &  -0.062 \\
    LS       &   0.285* &   0.158* &   0.146* &    0.050 &  -0.037 &   0.000 &  0.110* \\
    Pers     &   0.134* &    0.066 &    0.032 &   0.166* &   0.018 &   0.080 &  -0.004 \\
    $\beta$  &  -0.370* &  -0.157* &  -0.114* &  -0.185* &   0.017 &  -0.063 &  -0.043 \\
    $\eta_p$ &  -0.097* &  -0.105* &  -0.101* &   -0.033 &  -0.020 &  -0.015 &  -0.041 \\
    $\eta_n$ &   0.168* &   0.094* &   0.108* &   -0.050 &  -0.056 &  -0.020 &   0.042 \\
    $\kappa$ &  -0.175* &  -0.137* &  -0.147* &   -0.008 &  -0.020 &  -0.028 &  -0.061 \\
    \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{Spearman correlations between task behavior and self-report symptom measures when no screening and rejections have been applied. Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry. *Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
\end{table}

\begin{table}[H]
    \centering
    \small
    \begin{tabular}{rccccccc}
    \toprule
    {} &       7u &       7d &    GAD-7 &      BIS &     BAS &   SHAPS &    PSWQ \\
    \midrule
    Acc      &  -0.263* &  -0.144* &  -0.105* &  -0.106* &  -0.009 &  -0.020 &  -0.033 \\
    Pts      &  -0.187* &   -0.042 &   -0.020 &  -0.126* &  -0.055 &  -0.028 &   0.036 \\
    WS       &  -0.291* &  -0.137* &  -0.123* &  -0.161* &  -0.019 &   0.006 &  -0.044 \\
    LS       &   0.314* &   0.170* &   0.156* &    0.034 &  -0.036 &  -0.037 &  0.124* \\
    Pers     &    0.083 &    0.022 &    0.011 &   0.151* &   0.010 &   0.076 &  -0.021 \\
    $\beta$  &  -0.332* &  -0.134* &  -0.109* &  -0.173* &   0.010 &  -0.040 &  -0.023 \\
    $\eta_p$ &   -0.056 &   -0.089 &  -0.105* &   -0.013 &  -0.029 &   0.034 &  -0.035 \\
    $\eta_n$ &   0.259* &   0.134* &   0.122* &   -0.021 &  -0.063 &   0.019 &   0.053 \\
    $\kappa$ &  -0.171* &  -0.125* &  -0.150* &   -0.016 &  -0.032 &  -0.033 &  -0.060 \\
    \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{Spearman correlations between task behavior and self-report symptom measures after applying rejections based on choice accuracy (7\% of sample). Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry. *Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
\end{table}

\begin{table}[H]
    \centering
    \small
    \begin{tabular}{rccccccc}
    \toprule
    {} &       7u &      7d &    GAD-7 &      BIS &     BAS &   SHAPS &    PSWQ \\
    \midrule
    Acc      &  -0.210* &  -0.048 &    0.009 &   -0.082 &  -0.020 &  -0.005 &   0.009 \\
    Pts      &  -0.167* &   0.040 &    0.070 &  -0.107* &  -0.046 &  -0.011 &   0.071 \\
    WS       &  -0.220* &  -0.045 &   -0.008 &  -0.143* &  -0.025 &   0.001 &   0.016 \\
    LS       &   0.219* &   0.084 &   0.113* &    0.019 &  -0.021 &  -0.050 &   0.082 \\
    Pers     &    0.088 &  -0.028 &   -0.024 &   0.127* &   0.006 &   0.048 &  -0.052 \\
    $\beta$  &  -0.257* &  -0.038 &    0.047 &  -0.180* &  -0.011 &  -0.032 &   0.056 \\
    $\eta_p$ &   -0.052 &  -0.064 &   -0.079 &   -0.015 &  -0.008 &   0.004 &  -0.055 \\
    $\eta_n$ &   0.165* &   0.067 &   0.141* &   -0.037 &  -0.089 &  -0.030 &   0.054 \\
    $\kappa$ &  -0.111* &  -0.046 &  -0.137* &    0.011 &   0.015 &   0.002 &  -0.054 \\
    \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{Spearman correlations between task behavior and self-report symptom measures after applying rejections based on infrequency items (22\% of sample). Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry. *Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
\end{table}

\begin{table}[H]
    \centering
    \small
    \begin{tabular}{rccccccc}
    \toprule
    {} &       7u &      7d &    GAD-7 &      BIS &     BAS &   SHAPS &    PSWQ \\
    \midrule
    Acc      &  -0.229* &  -0.090 &   -0.072 &   -0.053 &   0.016 &   0.034 &  -0.040 \\
    Pts      &  -0.177* &   0.016 &    0.011 &   -0.086 &  -0.013 &   0.025 &   0.038 \\
    WS       &  -0.227* &  -0.085 &   -0.057 &  -0.131* &  -0.025 &   0.049 &  -0.007 \\
    LS       &   0.236* &   0.094 &   0.107* &    0.008 &  -0.016 &  -0.075 &   0.079 \\
    Pers     &    0.095 &  -0.007 &    0.014 &   0.110* &  -0.015 &   0.037 &  -0.025 \\
    $\beta$  &  -0.255* &  -0.072 &   -0.008 &  -0.165* &  -0.011 &  -0.015 &   0.028 \\
    $\eta_p$ &   -0.045 &  -0.088 &  -0.108* &    0.004 &  -0.000 &   0.049 &  -0.073 \\
    $\eta_n$ &   0.196* &   0.046 &   0.098* &   -0.015 &  -0.085 &   0.008 &   0.024 \\
    $\kappa$ &  -0.114* &  -0.046 &  -0.134* &    0.007 &   0.012 &  -0.004 &  -0.051 \\
    \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{Spearman correlations between task behavior and self-report symptom measures after applying rejections based on both choice accuracy and infrequency items. Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry. *Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
\end{table}

\clearpage
\subsection*{Task Instructions}

The following are the instructions given to participants for the probabilistic reversal learning task. As a reminder, the task was given a fishing-themed cover story. Each paragraph below denotes one screen of instructions.

\textit{Welcome to the fishing game! We will now give you some instructions on how to play the game. Use the buttons below (or the arrow keys) to navigate the instructions.}

\textit{In the fishing game, there are three beaches you can fish at. Each beach has its own unique surfboard. (The colors and pictures on the surfboards are there just to help you tell the beaches apart – they don’t have any special meaning other than that.)}

\textit{On each turn you will be shown three beaches, and you will choose which one you want to fish at. You can make your choice using the left, up, and right arrow keys.}

\textit{When you fish at a beach, you will either catch a fish or you will catch trash. Try to catch fish, and try not to catch trash!}

\textit{Some beaches are better than others. You are more likely to catch fish at some beaches (though you will still sometimes catch trash), and you are more likely to catch trash at other beaches (though you still sometimes catch fish).}

\textit{The beaches will change over time. As times goes by, you may be less likely to catch fish at a beach where you were previously catching many fish.}

\textit{Your goal is to catch as many fish as you can. You will receive a performance bonus up to \$0.25 that depends on how many fish you catch.}

\textit{Now we will ask you some questions about the game. You must answer all questions correctly to proceed. Feel free to read back through the instructions if there is anything you are not certain about.}

Following the instructions, participants completed a brief comprehension check where they were asked the following questions about the task:

\begin{enumerate}
    \item True or False: Your goal is to catch as many fish as you can. (True)
    \item True or False: You are more likely to catch fish at some beaches than others. (True)
    \item True or False: You will always catch fish at the best beach. (False)
    \item True or False: How likely you are to catch a fish at a beach stays the same over time. (False)
    \item True or False: The number of fish you catch will affect your final performance bonus. (True)
\end{enumerate}

Participants were required to answer all of the items correctly before they could proceed to the task. If they failed to do so, they restarted the instructions. There was no upper limit as to how many times a participant could loop through the instructions (the large majority of participants passed the comprehension check on their first try).

\subsection*{C/IE responding manifests as qualitatively distinct behavioral strategy}

In an exploratory analysis, we employed a theory-agnostic modeling approach to investigate how C/IE participants on the probabilistic reversal-learning task compared to attentive participants. The motivation for this analysis was to better understand why C/IE responding was inconsistently predicted by chance-level performance, and also correlated with asymmetric learning rates.

To characterize participants' choice behavior, we adapted the softmax regression model from \cite{seymour2012serotonin}. This model estimates, for each participant, how much their choice depends on the recent history of trial events (rewarding outcomes, non-rewarding outcomes, and choices from the preceding 5 trials). Specifically, the influence of the history of particular type of event is defined as:

\begin{equation*}
    \sum_i^K w = x_{t-1} \cdot w_{t-1} + x_{t-2} \cdot w_{t-2} +  \ldots + x_{t-k} \cdot w_{t-k}
\end{equation*}

where $x_{t-i}$ is a binary indicator [0,1] denoting if an event (i.e., reward, non-reward, previous choice) occurred on trial $t-i$ and $w_{t-1}$ is the associated decision weight. These weights were estimated for rewards, non-rewards, and previous choices up to five trials in the past. The overall tendency to choose a particular choice option is dictated by a softmax choice rule:

\begin{equation*}
    p(y_t = i) = \frac{ \exp \left( \sum w_i^\text{reward} + \sum w_i^\text{nonreward} + \sum w_i^\text{choice} \right) }{ \sum_i \exp \left( \sum w_i^\text{reward} + \sum w_i^\text{nonreward} + \sum w_i^\text{choice} \right) }
\end{equation*}

Note that these weights were fit independently; that is, we did not employ an exponential kernel to parameterize the decay of the weights at successively distant trial lags. In sum then, the theory-agnostic model describes a participant's choice behavior as a function of 15 parameters.

We fit the softmax regression model using Stan following the same procedure as for the theory-based analyses. Participant parameters were fit individually (i.e., not hierarchically)  so as to prevent bias during parameter estimation from partial-pooling between attentive and C/IE participants. Parameters were sampled with Gaussian priors with $\mu = 0$ and $\sigma = 5$.

The regression weights for each event, averaged within attentive and C/IE participants, are presented in Figure \ref{fig:regression}. Comparing attentive to C/IE participants, we observed a credible difference (i.e., 95\% highest density intervals excluded zero) only for the $T-1$ weight for previous choice. That is, attentive participants were more likely to repeat their previous choice (i.e., greater choice hysteresis) than were C/IE participants.

\begin{figure}[!t]
    \includegraphics[width=16cm]{../figures/main_03c.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{Softmax regression decision weights in attentive (red) and C/IE (blue) participants. The weights dictate the extent to which the recent history of rewards, nonrewards, or previous choices influence current choice. Error bars indicate the 95\% highest density interval of each weight. *Denotes where the 95\% highest density interval of the difference in weights excluded zero.}
    \label{fig:regression}
\end{figure}

This result may be initially surprising, since one might expect choice hysteresis to result in more perseveration errors following contingency reversals. However, choice hysteresis is adaptive in this probabilistic reversal-learning task. Because rewards in the task are probabilistic, once the reward-maximizing response option has been identified ignoring an occasional unrewarding outcome and instead performing the same response is optimal (until the next reversal occurs and is identified). Interestingly, participants engaging in C/IE responding were also numerically (though not significantly) less affected by previous outcomes, suggesting that their behavior was not more adaptive, but rather just more random.

This pattern of results also helps explain the pre-screening correlations with asymmetric learning rates. Previous work has established that, when choice hysteresis is not accounted for in reinforcement learning models, it can manifest as positive learning rate asymmetries \cite{Katahira2018-ke, sugawara2021dissociation}. Since C/IE participants showed decreased hysteresis, which our reinforcement learning model did not explicitly account for, we should expect to find a negative correlation between learning-rate asymmetries and symptoms before C/IE participants are excluded. Indeed, this is what we observed above.

In sum, the theory-agnostic analysis of task behavior revealed that C/IE participants exhibited a qualitatively distinct behavioral strategy on the probabilistic reversal-learning task. C/IE participants showed less adaptive choice hysteresis. Moreover, they were numerically (but not significantly) less sensitive to outcomes. The latter finding helps clarify in part why we observed low correspondence between task and self-report screening measures (that is, C/IE participants were not significantly more likely to respond randomly during the task). These results also present another hidden danger of C/IE responding: qualitatively distinct patterns of behavior under C/IE responding can bias the estimation of parameters of theoretical interest if not properly accounted for.

\break
\section*{Appendix B: Replication study}

\subsection*{Background \& motivation}

Here we report a conceptual replication of our original study. The motivations for conducting a replication study were threefold. First, we wanted to examine the generalizability of our findings under new labor-platform conditions. Since summer 2020, when the original data were collected, online labor markets like Mechanical Turk/CloudResearch and Prolific Academic have undergone important changes. To address rampant data quality issues on Mechanical Turk, CloudResearch introduced their ``Approved Participants'' filter. When selected, only Mechanical Turk participants with a prior history of attentive and careful work are invited to participate in experiments \cite{cloudresearch_2020-2, hauser2021evaluating}. Similarly, a deluge of new, lower-quality users signed up to participate in studies on Prolific in summer, 2021 \cite{Letzter2021-bw}. In response, Prolific introduced new controls and filters to improve data quality on the platform \cite{prolific_2021}. In the wake of these changes, we wanted to explore the relevance of our original findings. Specifically, with these new safeguards, we wanted to examine whether the chance of spurious correlations has been considerably reduced.

Second, we wanted to examine the generalizability of our findings to other behavioral measures. In the original study, we used a short, straightforward, and relatively easy reversal-learning task. Our motivation then was to demonstrate the risk of spurious correlations even for experiments where the possibility of participant fatigue (and consequently C/IE responding) had been minimized. One consequence of this design, however, was that the majority of participants performed reasonably well on the task (only 26 participants, or 7\% of the sample, exhibited choice accuracy at or below chance levels). This could in part explain why we observed such low correspondence between self-report and task-based screening measures. As such, we wanted to repeat our experiment and analyses using a more difficult task. Therefore, in the replication study we used the two-step task \cite{daw2011model}, which is both more challenging and takes longer than our original reversal-learning task.

Finally, we wanted to examine the generalizability of our findings to other self-report measures. In the original study, we found that self-report symptom measures with low rates of endorsement were more likely to yield spurious correlations with behavior in the presence of C/IE responding, as C/IE participants were more likely to endorse symptoms, as well as to perform poorly on the task. In principle, this effect should not be limited to symptom measures, and should extend to any self-report measure with an expected skewed or asymmetric score distribution. Therefore, in the current replication study, we used two sets of self-report scales: one set of psychiatric symptom measures and one set of personality measures. As before, each set includes scales whose score distributions are expected to be symmetric as well as scales with asymmetric (skewed) score distributions. Crucially, the two personality scales we chose, artistic interests and greed avoidance, measure constructs that should have no meaningful relationship with model-based choice behavior on the two-step task. Therefore, the personality measures serve as a stronger test of our hypothesis that spurious correlations between self-report and behavioral measures are more likely for skewed score distributions.

\subsection*{Methods}

\subsubsection*{Participants}

400 total participants were recruited to participate in an online behavioral experiment in February, 2022. Specifically, 200 participants were recruited from Amazon Mechanical Turk (MTurk) and 200 participants were recruited from Prolific. The study was approved by the Institutional Review Board of Princeton University (\#11968), and all participants provided informed consent. Total study duration was approximately 20 minutes. Participants received monetary compensation for their time (rate USD \$12/hr), plus an incentive-compatible bonus up to \$1.00 based on task performance.

Participants were eligible if they resided in the United States or Canada. Participants from MTurk were recruited with the aid of CloudResearch services \cite{litman2017turkprime-2} using their ``Approved participants''  data quality filters \cite{cloudresearch_2020-2}. As in the original study, MTurk workers were not excluded based on work approval rate or number of previous jobs approved \cite{robinson2019tapped-2}. No other exclusion criteria were applied during recruitment.

Data from N=7 participants who completed the experiment were excluded prior to analysis because these participants (all from MTurk) disclosed that they had also completed the same experiment on the other platform. This left a final sample of N=393 participants (MTurk: N=193, Prolific: N=200) for analysis. The demographics of the sample split by labor market is provided in Table \ref{tab:demographics_02}. Participants recruited from MTurk were older on average ($\Delta M = 4.9$ yrs; two-tailed, two-sample $t$-test: $t(391)=4.248$, $p<0.001$, $d = 0.429$, 95\% CI = [2.7, 7.2]) and comprised of fewer women (35.2\% versus 61\%; two-tailed, two-sample proportions test: $z(391)=5.500$, $p<0.001$, $h=0.562$, 95\% CI = [0.182, 0.372]).

\begin{table}[!h]
    \centering
    \small
    \setlength{\tabcolsep}{15pt}
    \begin{tabular}{lrrrr}
        \toprule
        & \multicolumn{2}{c}{MTurk} & \multicolumn{2}{c}{Prolific} \\
        \cmidrule(lr){2-3} \cmidrule(lr){4-5}
        Total & \multicolumn{2}{c}{N=193} & \multicolumn{2}{c}{N=200} \\
        \midrule
        Age & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        18-25   &    11 &   5.7 &     47 &  23.5 \\
        26-35   &    71 &  36.8 &     76 &  38.0 \\
        36-45   &    60 &  31.1 &     41 &  20.5 \\
        46-55   &    29 &  15.0 &     22 &  11.0 \\
        55+     &    22 &  11.4 &     14 &   7.0 \\
        \midrule
        Gender & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        Female &      68 &  35.2 &      122 &  61.0 \\
        Male   &     124 &  64.2 &       73 &  36.5 \\
        Other  &       1 &   0.5 &        5 &   2.5 \\
        \midrule
        Ethnicity & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        Hispanic or Latino     &    16 &   8.3 &     12 &   6.0 \\
        Not Hispanic or Latino &   177 &  91.7 &    180 &  90.0 \\
        Rather not say         &     0 &   0.0 &      8 &   4.0 \\
        \midrule
        Race & N & \% & N & \% \\
        \cmidrule(lr){1-5}
        American Indian/Alaska Native &     2 &   1.0 &      0 &   0.0 \\
        Asian                         &    15 &   7.8 &     41 &  20.5 \\
        Black or African American     &    13 &   6.7 &     12 &   6.0 \\
        White                         &   156 &  80.8 &    133 &  66.5 \\
        Multiracial                   &     6 &   3.1 &     10 &   5.0 \\
        Rather not say                &     1 &   0.5 &      4 &   2.0 \\
        \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{The demographics of each sample by online labor market.}
    \label{tab:demographics_02}
\end{table}

\subsubsection*{Experiment}

Participants completed a gamified version of the two-step task \cite{daw2011model} designed to dissociate ``model-free'' and ``model-based'' decision-making. On every trial of the task, participants' goal is to collect as much ``space treasure'' as possible by traveling to one of two different planets and ``trading'' with one of two aliens who live on that planet. Participants first chose between two different-colored rocket ships (first-stage choice). Each rocket ship had a 70\% chance of traveling to one particular planet (e.g., the green rocket ship to the blue planet and the purple rocket ship to the red planet; common transitions) and a 30\% chance of traveling to the other planet (uncommon transition). The rocket ship and planet colors were randomized across participants, as were the mappings between rocket ships and planets. On each planet, participants chose which of two aliens to ``trade'' with (second-stage choice). If chosen, an alien would give the participant ``treasure'' with some slowly-changing probability, otherwise it would give ``junk''. The reward probabilities for each alien and trial were generated according to independent Gaussian random walks. Participants completed 201 trials of the task, with an optional break after the first half.

Prior to the beginning of the experiment, participants had to read a set of instructions in which they were told that the rocket ships mostly traveled to one planet, but sometimes went to the other, and that the chance an alien would give them treasure would change slowly over the course of the task. Before they could start the task, participants had to correctly answer three sets of comprehension questions about the instructions. Failing to correctly answer all items forced the participant to reread a section of the instructions. Participants were permitted up to ten retries of the comprehension questions before they were removed from the experiment; however, no participant exceeded this limit.

The task was programmed in jsPsych \cite{deleeuw_2015_jspsych-2} and distributed using custom web-application software. The experiment code is available at \url{https://github.com/nivlab/sciops}, and the web-software is available at \url{https://github.com/nivlab/nivturk}. A playable demo of the task is available at \url{https://nivlab.github.io/jspsych-demos/tasks/two-step/experiment.html}.

\subsubsection*{Self-report measures}

Prior to the start of the two-step task, participants completed four self-report measures in a randomized order. One was the 14-item seven-up/seven-down scale (7u/7d; \cite{youngstrom_2013_susd-2}), which measures lifetime incidence of depressive and (hypo)mania symptoms. This scale is expected to elicit lower rates of symptom endorsement, thereby resulting in asymmetric (right-skewed) score distributions. Participants also completed a 7-item measure of general anxiety symptoms over the last year (e.g. ``I was overwhelmed by anxiety.''; \cite{watson2022development}). This scale is expected to elicit moderate rates of symptom endorsement, thereby resulting in a symmetric score distribution. We therefore expected the depression and mania measures to be at greater risk for spurious correlations with behavior on the two-step task than the anxiety measure.

In addition, participants completed a 6-item measure of artistic interests (e.g. ``I believe in the importance of art''; \cite{ashton2007empirical}). Based on previous studies, this scale is expected to elicit high rates of endorsement, thereby resulting in an asymmetric score distribution. Finally, participants completed a 6-item measure of greed avoidance, which measures attitudes towards wealth and status (e.g. ``I am out for my own personal gain''; \cite{ashton2007empirical}). Based on previous studies, this scale is expected to elicit moderate rates of endorsement, thereby resulting in a symmetric score distribution. We therefore expected the artistic interests scale to be at greater risk for spurious correlations with behavior on the two-step task than the greed avoidance scale .

\subsubsection*{Correspondence of screening measures}

As in the original study, we measured the correspondence of screening measures based on the task and self-report behavior. We calculated a number of standard measures of data quality from each participant's task behavior (four in total) and self-report responses (five in total). The self-report screening measures were identical to those used in the original study, except that we used (mostly) new infrequency items. We describe each of the new screening measures below.

\subparagraph{Self-report screening measure: Infrequency items.} Infrequency items are questions for which all (or virtually all) attentive participants should provide the same response. We embedded four infrequency items across the self-report measures. Specifically, we used the following questions:

\begin{enumerate}
  \item Have there been times in your life where you blinked your eyes at least once per day? (Expected response: \textit{Very often})
  \item Have there been times of a couple days or more when you were able to breathe underwater (without an oxygen tank)? (Expected response: \textit{Never or hardly ever})
  \item I was worried about the canine World Cup. (Expected response: \textit{Not at all})
  \item I have used a computer. (Expected response: \textit{Slightly Agree}, \textit{Agree}, or \textit{Strongly agree})
\end{enumerate}

Prior to conducting the study, the infrequency items were piloted on an independent sample of participants to ensure that they elicited one dominant response. We also included one instructed item (``Please select `Neutral' as your response'') to compare to the infrequency items. We measured the number of `suspicious' (i.e., incorrect) responses made by each participant to these questions. For thresholded analyses, participants were flagged if they responded incorrectly to one or more of these items.

\subparagraph{Task-based screening variable: Side variability.} Side variability was defined as the fraction of trials a participant chose the left option (by pressing the left arrow key) across first stage choices during the two-step task. Side variability could range from 0.00 (only right arrow key used) to 1.00 (only left arrow key used). Extreme values (i.e., closer to zero or one) are indicative of more careless responding during the task, as the sides for which each choice option was displayed was determined randomly on each trial.

\subparagraph{Task-based screening variable: Choice variability.} Choice variability was defined as the fraction of trials a participant chose the same first-stage choice option (randomized to the right or left side of the screen) during the two-step task. Choice variability could range from 0.00 (selected the green rocket ship exclusively) to 1.00 (selected the purple rocket ship exclusively). Extreme values (i.e., closer to zero or one) are indicative of more careless responding during the task as the most rewarding option changed throughout the task.

\subparagraph{Task-based screening variable: Win-Stay Lose-Shift.} Win-stay lose-shift (WSLS) measures a participant's tendency to stay with a first-stage choice option following a second-stage reward versus shifting to a the other choice option following a non-reward. WSLS thus measures a participant's sensitivity to reward feedback. WSLS was estimated per participant via regression, predicting each first-stage choice (stay, switch) by the previous trial's outcome (reward, non-reward) and an intercept. We used the first (slope) term to represent a participant's WSLS tendency. Lower values of this term indicate less sensitivity to reward feedback and are thus indicative of more careless responding during the task. Thresholds for chance-level WSLS performance were determined by fitting the same regression model to 5000 randomly-generated datasets of first-stage choice (datasets were generated by matching the probability of staying with the previous trial's choice to the distribution observed empirically, but choices were otherwise independent across trials; that is, independent of previous outcome). The threshold for above-chance WSLS was defined as the 95th percentile of the distribution of slope estimates for the random data, corresponding to a one-tailed hypothesis test ($\alpha = 0.05$) that the slope coefficient is greater than zero.

\subparagraph{Task-based screening variable: Response times.} ``Suspicious response time'' was defined as the proportion of first-stage choices with a response faster than 200ms. Greater proportions of outlier response times are indicative of more careless responding during the task.

\subparagraph{Correspondence Analysis.} We measured the correspondence of the above screening measures via two complementary approaches. First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation. Second, we estimated the pairwise rate of agreement on the binarized measures using the Dice similarity coefficient (looking at the top 10\% most suspicious respondents for each measure). The former approach estimates two measures' monotonic association, whereas the latter approach estimates their agreement as to which participants were most likely engaging in C/IE responding. For significance testing, we used permutation testing wherein a null distribution of similarity scores (Spearman's correlations or Dice coefficients) was generated for each pair of screening measures by iteratively permuting participants' identities within measures and re-estimating the similarity. P-values were computed by comparing the observed score to its respective null distribution. We corrected for multiple comparisons using family-wise error rates \cite{winkler2014permutation-2}.

\subsubsection*{Correlations between behavior and symptom measures}

To quantify the effects of both task and self-report data screening on behavior-symptom correlations, we estimated the pairwise correlations between the scale scores of each self-report measure and several measures of model-agnostic performance on the two-step task \cite{gillan2016characterizing}. Logistic regression analyses were conducted with the \textit{statsmodels} package \cite{seabold2010statsmodels} in the python programming language. The model tested if participants' first-stage choice behavior (coded as Stay = 1, Switch = 0) was influenced by the previous trial's reward (coded as Rewarded = 1, Unrewarded = 0), previous trial's transition (coded as Common = 1, Uncommon = 0), and their interaction. Importantly, the interaction term between previous reward and transition is a proxy for the contribution of model-based learning to choice behavior \cite{gillan2016characterizing}.

Correlations between the behavioral measures (i.e., logistic regression coefficients) and self-report measures were calculated using Spearman's rank correlation, after various forms of screening and exclusion. Significance testing was performed using the percentile bootstrap method \cite{wilcox2018guide-2} so as to avoid making any parametric assumptions. These correlation analyses were not corrected for multiple comparisons, since our overarching purpose was to demonstrate the extent of this issue across multiple behavioral measures and self-report symptoms. Any one of these correlations considered individually can be thought of as emulating a conventional analysis where fewer statistical tests would be performed.

\subsection*{Results}

\subsubsection*{Careless participants (often) appear symptomatic when the overall level of symptom endorsement is low}

To begin our analysis of the replication dataset, we examined the number of participants flagged by the WSLS and infrequency item screening measures. Only 31 participants (8\%) were flagged as exhibiting choice behavior at or below statistically chance levels in the two-step task. In contrast, 55 participants (14\%) endorsed a logically invalid or improbable response on one or more of the infrequency items when completing the self-report measures. The proportion of participants flagged for C/IE responding was significantly greater on Mechanical Turk compared to Prolific for both task (MTurk: N=23/193; Prolific: N=8/200; two-tailed, two-sample proportions test: $z(391)=2.911$, $p=0.004$, $h=0.305$, 95\% CI = [0.026, 0.132]) and survey data (MTurk: 34/193; Prolific: 21/200; two-tailed, two-sample proportions test: $z(391)= 2.033$, $p=0.042$, $h=0.206$, 95\% CI = [0.003, 0.140]). Across the four infrequency items, the average failure rate was 5.3\% (range: 2.5\% -- 8.9\%). In contrast, no participant failed the instructed item. This discrepancy in the proportion of participants flagged by each type of attention check is consistent with previous research, which found that instructed items are insensitive measures of C/IE responding \cite{barends2019noncompliant-2, thomas2017validity-2, hauser2016attentive-2}.

\begin{figure}[t!]
    \includegraphics[width=15cm]{../figures/repl_02a.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{Raincloud plots of total symptom scores in attentive (red) and C/IE (blue) participants. Each colored dot represents the symptom score for one participant. Black circles: average score within each group (error bars denote 95\% bootstrap confidence interval). Shaded plots: estimated distribution of responses for each group of participants.}
    \label{fig:repl_distributions}
\end{figure}

Previously, we observed a mean-shift in the average level of symptom endorsement for participants suspected of engaging in C/IE responding relative to attentive participants on measures for which the overall rate of symptom endorsement is low. This result was (mostly) replicated in the current dataset. Total scores were noticeably exaggerated in participants suspected of C/IE responding for the symptom measures where overall rates of symptom endorsement were the lowest (e.g. mania; Figure \ref{fig:repl_distributions}, leftmost plot). Where there were higher rates of symptom endorsement overall (e.g. anxiety), the distributions of symptom scores between the two groups of participants were more similar (Figure \ref{fig:repl_distributions}, middle plots). Permutation testing confirmed that observed mean-shifts in symptom scores for C/IE participants were statistically significant for the most skewed symptom measures (Table \ref{tab:rep_validation}).

For the personality measures, however, an interesting pattern emerged (Figure \ref{fig:repl_distributions}, rightmost plots). We did not observe a statistically significant mean-shift in total scores for the subscale with the most skewed score distribution (i.e., artistic interests). However, an unexpected and statistically significant mean-shift in the average level of endorsement was observed for the more symmetrically-distributed greed-avoidance subscale. The reason for this finding is unclear. Regardless, this finding presents an opportunity to test for spurious correlations between behavioral and self-report measures in the presence of a mean-shift in scores in the absence of (substantially) skewed score distributions.

\begin{table}[!t]
    \centering
    \small
    \begin{tabular}{lcccc}
        \toprule
        & & \multicolumn{3}{c}{Total Score} \\
        \cmidrule(lr){3-5}
        Subscale & Skew &  Attentive & C/IE & $t$-value \\
        \midrule
        Mania      &  1.07 &   3.25 &   6.27 & $-6.05^*$ \\
        Depression &  0.89 &   5.72 &   6.95 & $-1.57$   \\
        Anxiety    &  0.44 &   8.54 &   8.65 & $-0.13$   \\
        Artistic interests   & -0.92 &  28.07 &  26.29 & $1.87$    \\
        Greed avoidance     &  0.55 &  11.77 &  16.44 & $-4.17^*$  \\
        \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{Descriptive statistics of the self-report measures between attentive and C/IE participants. Skew: the empirical skewness of the distribution of total symptom scores. Total score: the average symptom score across attentive and C/IE participants. *Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
    \label{tab:rep_validation}
\end{table}

\subsubsection*{Low correspondence between task and self-report measures of C/IE responding}

Next, we evaluated the degree of correspondence between behavioral and self-report screening measures to determine whether screening on behavior alone was sufficient to identify and remove careless participants. To measure the degree of correspondence between these behavioral and self-report screening measures, we performed two complementary analyses. First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation (Figure \ref{fig:repl_correspondence}, left panel). After correcting for multiple comparisons, there were a handful of significant correlations between the behavioral and self-report screening measures. Abnormal response times emerged as the metric most correlated with the self-report screening measure. Crucially, as in the original study, the sizes of these observed correlations were roughly half those observed for the correlations between the self-report measures.

\begin{figure}[!t]
    \includegraphics[width=16cm, trim=0 0 3cm 0]{../figures/repl_02b.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{Similarity of task and self-report data screening measures. Each tile corresponds to the Spearman rank correlation (left) and Dice similarity coefficient (right) between two screening measures. Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; SV = side variability; CV = choice variability; WSLS = win-stay lose-shift rate; RT = suspicious response times. Similarity scores have been thresholded after correcting for multiple comparisons. Numbers denote the strength of statistically significant correlations. Cross-modality correlations between task-behavior (left) and infrequency-item self-report measures (bottom) are in the dashed rectangle.}
    \label{fig:repl_correspondence}
\end{figure}

Second, we used the Dice similarity coefficient to quantify agreement between different screening methods in the set of participants flagged for exclusion (Figure \ref{fig:repl_correspondence}, right panel). This approach quantifies the degree of overlap between the set of would-be excluded participants based on different screening measures under a common exclusion rate. Results were largely consistent with the correlation analysis: only a handful of task and self-report screening measures achieved levels of agreement greater than what would be expected by chance. Of the significant cross-modality pairs, the average similarly coefficient was less than 0.4. In other words, when any of these sets of two measures are used to identify the top 10\% of participants most strongly suspected of C/IE responding, they agree on only two out of every five participants. Screening on task behavior alone would fail to identify the majority of participants most likely engaging in C/IE responding.

Taken together, these findings corroborate the results of the original study: measures of C/IE responding in task and self-report data do not identify the same set of participants. This means that solely excluding participants on the basis of poor behavioral performance---the most common approach in online studies---is unlikely to identify participants who engage in C/IE responding on self-report surveys.

\subsubsection*{Spurious symptom-behavior correlations produced by C/IE responding}

To understand the effects of applying different forms of screening, we estimated the correlations between each unique pairing of a self-report measure and measure of behavior under four different conditions: no screening, screening only on task behavior (i.e., removing participants whose win-stay lose-shift behavior was not above chance), screening only on self-report responses (i.e., removing only participants who responded incorrectly on one or more infrequency items), or both. The resulting pairwise behavior-symptom correlations following each screening procedure are presented in Figure \ref{fig:repl_correlations}. We note that we did not correct these correlation analyses for multiple comparisons, since our purpose was to demonstrate the extent of this issue across multiple behavioral measures and self-report symptoms. Any one of these correlations considered individually can be thought of as emulating a conventional analysis where fewer statistical tests would be performed.

When no rejections were applied (i.e., all participants were included; Figure \ref{fig:repl_correlations}A), we observed multiple significant correlations between measures of task behavior and symptom scores for hypomania and depression. Consistent with our predictions, these correlations involved measures with low overall endorsement rates and mean-shifts in score distributions between attentive and C/IE participants. Conversely, we found no significant correlations with the symmetrically-distributed anxiety scores. This is despite the fact this scale measures symptoms that are comorbid with depression and mania. Crucially, of the two personality measures, we observed significant correlations only for the measure found to exhibit a mean-shift in scores between attentive and C/IE participants (i.e., greed avoidance). These included a significant correlation with the interaction term, which is used as a proxy measure for model-based choice behavior. That is, significant correlations were not restricted only to general behavioral measures but also to measures of specific theoretical interest.

Next, we excluded participants from the analysis based on task-behavior screening (i.e., lack of win-stay lose-shift behavior, removing the 8\% of participants exhibiting behavior indistinguishable from chance; Figure \ref{fig:repl_correlations}B). In contrast to the findings of the original study, the pattern of correlations was meaningfully changed: the putatively spurious correlations between greed avoidance and performance on the two-step task were ablated. Two previously significant correlations between hypomania and two-step performance were also rendered non-significant. A similar pattern of results was observed when we rejected participants based on self-report screening (removing 14\% of participants who endorsed one or more invalid or improbable responses on the infrequency items; Figure \ref{fig:repl_correlations}C) and when rejections were applied based on both task and self-report screening measures (removing 18\% of participants; Figure \ref{fig:repl_correlations}D).

\begin{figure}[!t]
    \includegraphics[width=17cm]{../figures/repl_03a.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{Absolute Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions. Only statistically significant correlations are shown ($p<0.05$, not corrected for multiple comparisons). Black Xs indicate significant correlations ablated under screening. No Screening = no exclusions; WSLS Only = exclusions based on chance-level performance in the two-step task; Infrequency Only = exclusions based on invalid or improbable responses to infrequency items; Both Types = exclusions based on the previous two measures. Acronyms: PrevRew = sensitivity to reward on the previous trial; PrevTrans = sensitivity to transition type on previous trial; MB/MF = index of model-based/model-free behavior (interaction between \textit{PrevRew} \& \textit{PrevTrans}).}
    \label{fig:repl_correlations}
\end{figure}

These findings suggest that some of the significant behavior-symptom correlations observed without strict participant screening may indeed be spurious correlations driven by C/IE responding. Interestingly, in contrast to the original study, with a more demanding behavioral task, screening based on either task behavior or self-report behavior alone was sufficient to protect against spurious symptom-behavior correlations in the presence of mean-shifts in scores between attentive and C/IE participants. For example, both forms of screening ablated the would-be significant correlation between model-based behavior and greed avoidance. The discrepancy in results between the original and replication studies may reflect the smaller numbers of participants failing attention checks in the replication study (14\%) compared to the original study (22\%), as well as differences in the behavioral tasks. Regardless, we replicate the findings of the original study in that screening on self-report data allowed us to identify symptom-behavior correlations most likely to be spurious.

\subsection*{Discussion}

Here we reported findings from a replication study whose purpose was to examine the generalizability of our original findings under new labor market conditions, different behavioral measures, and different self-report measures. To this end, we recruited an independent sample of almost 400 participants, using CloudResearch's and Prolific's latest data-quality filters, to complete the two-step task and a novel set of self-report measures. As evidence of the efficacy of the new data-quality filters, the proportion of participants flagged for C/IE responding in the self-report measures was noticeably smaller in the replication sample (14\%) compared to original sample (22\%). This decrease in the number of participants suspected of C/IE responding was observed for both MTurk and Prolific (though, as in the original study, the proportion of low-quality participants was significantly, albeit marginally, smaller for Prolific than MTurk). Regardless, although the new online labor platform quality-control measures seem to be effective, they did not completely solve the problem; indeed, the proportion of participants engaging in C/IE responding was reduced only by one-third.

Next, we compared the distribution of self-report scale scores for attentive participants and participants suspected of engaging in C/IE responding. Replicating our previous result, we observed a mean-shift in the average level of symptom endorsement for participants suspected of C/IE responding relative to attentive participants, only when the overall rate of symptom endorsement was low. Specifically, flagged participants showed significantly elevated scores on the hypomania scale (with its right-skewed score distribution) but not so on the anxiety scale (with its symmetric score distribution). Interestingly, we found the opposite pattern for the personality measures: scores for participants engaging in C/IE responding were not significantly different than those of their attentive counterparts on the artistic interests scale (with its left-skewed score distribution), but was so for the greed avoidance scale (with its more symmetric score distribution). One possible explanation for the discrepancy in findings between the symptom and personality measures is the direction of the skew for the artistic interests scale. Previously, using random-intercept item factor analysis, we observed that participants engaging in C/IE responding were more likely to use the right-half of the response scale. As such, such a pattern of responding is more likely to produce a mean-shift in scale scores, compared to attentive participants, on a scale with a right-skewed distribution (e.g. mania, depression scales) than a scale with a left-skewed distribution (e.g. artistic interests scale). Further research is still needed to characterize patterns of C/IE responding.

The results in the replication study did corroborate the findings of the original study in terms of the degree of correspondence between behavioral and self-report screening measures, suggesting that measures of C/IE responding in task and self-report data do not identify the same set of participants. Even with a more difficult task (i.e., the two-step task), we observed relatively low correspondence between self-report and task-based screening measures. This supports our suggestion that both forms of screening are necessary to identify participants providing low-quality responses. Finally, we examined the consequences of various types of screening methods for correlations between behavioral and self-report measures. As in the original study, we detected significant spurious correlations when no screening was applied. This included correlations between model-based planning on the two-step task and scores on the greed avoidance scale, for which there is no theoretical reason to predict a correlation. Instead, this correlation almost certainly reflects the mean-shift in scores between attentive participants and participants flagged for C/IE responding on the greed avoidance scale. As evidence of this, excluding participants who failed one or more infrequency items ablated this correlation. In contrast to the original study, excluding participants based on poor performance on the two-step task was also sufficient to ablate this correlation. Thus, there may be instances where screening based on poor behavioral performance is sufficient to prevent spurious correlations. However, in the absence of perfect information as to when those situations should arise, we conclude that it is simply safer to screen participants on both dimensions of performance.

In summary, we conclude that the results of the original study are not limited to the task and self-report measures used in that study, or to online platforms at a particular point in time. Despite legitimate advances in data quality controls, online labor platforms still suffer from participants engaging in C/IE responding. Given \textit{a priori} uncertainty regarding the ability of task measures alone to screen such participants, we recommend also using infrequency items to detect inattentive responding on self-report measures. Finally, and most importantly, this second study strengthened the finding that C/IE responding is likely to result in mean-shifts in scores for symptom scales with overall low rates of endorsement, which are in turn capable of yielding spurious correlations between self-report and behavioral measures. The best safeguard against such spurious correlations continues to be screening in both domains.

\break
\section*{Appendix C: Attention checks in healthy and psychiatric patients}

\subsection*{Background \& motivation}

One concern with using attention checks for screening and exclusion of participants is that we might inadvertently introduce an overcontrol bias \cite{elwert2014endogenous-2}. That is, to the extent that C/IE responding reflects symptoms of psychopathology such as lack of motivation \cite{barch2015mechanisms-2}, avoidance of effort \cite{cohen2001impairments-2, culbreth2016negative-2}, or more frequent lapses of attention \cite{kane2016individual-2, robison2017neurotic-2}, it is plausible that rigorous screening of C/IE responding might lead to the differential exclusion of truly symptomatic participants. As a result, true associations between poor or different task performance and psychopathology symptoms could go undetected (type II error). The purpose of the below preliminary and exploratory study was to examine whether individuals with a confirmed psychiatric disorder were indeed more likely than healthy controls to fail attention checks embedded in self-report symptom scales.

\subsection*{Methods}

\subsubsection*{Participants}

Participants were recruited as part of two independent studies to investigate reward processing in individuals with and without a history of major depression and bipolar disorder (results of those studies not reported here). Both studies required participants to complete (1) a structured clinical interview (the SCID-5) with a trained interviewer to verify that they met the criteria for one or more psychiatric disorders, and (2) a series of computerized self-report surveys and cognitive tasks.

In both studies, participants volunteered for a multi-session study conducted online via video conferencing. Specifically, participants completed each session from their homes while on Zoom with a study coordinator. During each session, while participants were completing self-report questionnaires or behavioral tasks, the study coordinator turned off their camera and microphone, but was available if the participant had any questions.

Participants were recruited through clinician referral and online ads (i.e., Google ads, Craigslist) targeting individuals with a history of depression, anhedonia, apathy, and/or (hypo)mania symptoms. Participants were eligible for participation if they (1) had no history of head injury resulting in loss of consciousness for more than 20 minutes; (2) had not been diagnosed with intellectual disability; (3) had not been diagnosed with any neurological condition; (4) did not meet criteria for substance dependence (excluding nicotine) in the past 6 months; (5) had not received electroconvulsive therapy in the past 8 weeks; and (6) were aged between 18-65. For one of the two studies, participants were also required to score 6 or higher on the Wechsler Test of Adult Reading to be included in the study. Furthermore, clinical participants were eligible if they met criteria for a diagnosis of major depressive disorder and, if they were on medication, they had been on on stable treatment with this medication for at least the past 4 weeks. Non-clinical (control group) participants were eligible if they did not meet criteria for any psychiatric diagnosis and were not currently taking any medication used to treat psychiatric disorders.

\subsubsection*{Infrequency items}

To measure and compare C/IE responding between healthy and psychiatric participants, we used two sets of attention checks. Each set was composed of three infrequency items and one instructed item. Participants were assigned one or the other set. The six infrequency items were:

\begin{enumerate}
    \item Worrying too much about the 1977 Olympics. (Expected response: \textit{Not at all})
    \item I have never used a computer. (Expected response: \textit{Completely untrue} or \textit{Quite untrue})
    \item I would be able to lift a small (1 lb) weight. (Expected response: \textit{Extremely characteristic of me} or \textit{Somewhat characteristic of me})
    \item Have there been times of a couple days or more when you were able to stop breathing entirely (without the aid of medical equipment)? (Expected response: \textit{Never})
    \item Over the past year, how often did you have days where you were able to blink your eyes without difficulty? (Expected response: \textit{Often} or \textit{Very often})
    \item I am generally able to remember my own name. (Expected response: \textit{True})
\end{enumerate}

\subsubsection*{Analysis}

Of primary interest here was whether psychiatric patients fail infrequency item attention checks at equal or at greater rates than healthy participants. To test this, we conducted Bayesian hypothesis testing using Bayes factors \cite{harms2018making}. Specifically, we defined three competing models:

\begin{itemize}
    \item $M_0: \text{Binom}(N_1, p), \text{Binom}(N_2, p)$  
    \item $M_1: \text{Binom}(N_1, p - \delta), \text{Binom}(N_2, p + \delta)$  
    \item $M_2: \text{Binom}(N_1, p + \delta), \text{Binom}(N_2, p - \delta)$  
\end{itemize}

where $N_1$ and $N_2$ are the observed number of healthy and psychiatric participants, respectively; $p$ is the latent probability of a participant failing one or more attention checks; and $\delta$ is an offset parameter specifying the hypothesized difference in failure rates between groups. Thus, $M_0$ assumes equal rates of failures between healthy and psychiatric participants, whereas $M_1$ and $M_2$  assume greater and lower rates, respectively, for psychiatric participants compared to healthy participants. The common latent probability, $p$, was set to the observed average rate across the two groups. The offset, $\delta$, was set to 0.05. This value was selected because it signifies a difference in portions of $\Delta p = 0.1$, corresponding to a small effect for a difference in proportions test ($h = 0.2$; \cite{cohen2013statistical}).

\subsection*{Results}

In total, 16 of 65 (24.6\%) participants failed one or more attention checks. Interestingly, the overall proportion of flagged participants was similar to that observed for the original study. Subdivided by group, 6 of 20 healthy participants (30\%) and 10 of 45 psychiatric participants (22\%) were flagged for C/IE responding. Unsurprisingly, given the modest sample size, the difference between the two proportions was not significantly different from zero (two-tailed, two-sample proportions test: $z(63)=0.672$, $p=0.502$, $h=0.178$, 95\% CI = [-0.157, 0.312]). Across the six infrequency items, the average failure rate was 8.5\% (range: 0.0\% -- 19.7\%). In contrast, no participant failed either instructed item. This result further corroborates previous research, which has found that instructed items are poor measures of C/IE responding \cite{barends2019noncompliant-2, thomas2017validity-2, hauser2016attentive-2}.

Next, we computed the Bayes factor for each pair of candidate models. A model assuming equal rates of failure between healthy and psychiatric participants was 2.88 times more likely than the model assuming greater rates for psychiatric patients. In turn, a model assuming lower rates of failure for psychiatric patients was 1.27 times more likely than the model assuming equal rates. Finally, a model assuming lower rates of failure for psychiatric patients was 3.65 times more likely than the model assuming higher rates for psychiatric patients. Only the final comparison exceeds the cutoff value of 3, which is conventionally treated as the minimal amount of evidence required to treat a model comparison as meaningful.

\subsection*{Discussion}

Here we sought to examine whether actual psychiatric patients were equally or more likely to fail infrequency items than healthy controls in settings similar to those experienced by online participants (i.e., completing an experiment online, on a computer in one's home or otherwise chosen environment). Although the small sample precludes any definitive conclusion, it is noteworthy that the model least consistent with the data was the one where psychiatric patients were more likely to fail infrequency-item attention checks. Indeed, a model in which healthy controls failed attention checks at a greater rate than patients was credibly preferred to the alternative. This preliminary finding may reflect differences in motivation between patients and controls for participating in psychiatric research. Indeed, whereas healthy controls may be primarily motivated to participate for monetary purposes, patients may be motivated to participate to further scientific research that may ultimately benefit them (or others suffering from the same conditions). That is, patients may have more ``stakes in the game,'' and therefore may be motivated to provide higher-quality responses. Regardless, further research is required to examine whether this preliminary finding holds in larger samples and other testing contexts.

\section*{Supplementary references}

\printbibliography[heading=supp]
\end{refsection}

\end{document}

### 2023-04-03 manuscripts/main.tex
checkpointing manuscript progress

@@
 To explore this possibility, we embedded attention checks into the self-report measures of two studies of patients with major depressive disorder (see Appendix C for details).
-Specifically, N=45 psychiatric patients (confirmed to meet criteria for a diagnosis of major depressive disorder through a structured clinical interview) and N=20 healthy controls, all recruited through the Rutgers-Princeton Center for Computational Cognitive Neuropsychiatry (i.e., personal recruitment, not on online labor platforms), completed a series of self-report symptom measures, online, on their computers from the comfort of their homes.
+Specifically, N=45 psychiatric patients (confirmed to meet criteria for a diagnosis of major depressive disorder through a structured clinical interview) and N=20 healthy controls, all recruited through the Rutgers-Princeton Center for Computational Cognitive Neuropsychiatry (i.e., not on online labor platforms), completed a series of self-report symptom measures, online, on their computers from the comfort of their homes.
 In total, 16 of 65 (24.6\%) participants failed one or more attention checks.
@@
 False-positive rates for these spurious correlations \emph{increased} with sample size, because the correlations are due to measurement bias, not measurement noise.
-Importantly, we found that screening on task behavior alone was insufficient to identify participants engaging in C/IE responding and avoid the false-positive correlations.
+Importantly, we found that screening on task behavior alone was insufficient to identify participants engaging in C/IE responding and prevent some false-positive correlations.
 Unfortunately, a literature review identified this type of screening as the most common practice in online computational psychiatry studies.
@@
 Viewed from the perspective of effort expenditure, our results suggest that participants appraised the cost/benefit trade-off differently for behavioral tasks and self-report surveys.
-Specifically, we found that only 7\% of participants were at chance-level performance in our task, compared to more than 22\% of participants who failed one or more attention-check items in the self-report surveys (a finding that qualitatively replicated in a second study involving a different task).
+Specifically, we found that only 7\% of participants in the first study were at chance-level performance in the task, compared to more than 22\% of participants who failed one or more attention-check items in the self-report surveys (a finding that qualitatively replicated in a second study involving a different task).
 Moreover, different measures of C/IE responding were weakly or not at all correlated between task behavior and self-report responses.
@@
 To explore this possibility, we embedded attention checks into the self-report measures of two studies of patients with major depressive disorder.
-Though our final sample was small, we did not find evidence for the proposition that patients were more likely to fail attention checks than healthy controls (if anything, non-psychiatric participants were more likely to be flagged by C/IE screening).
+Though our final sample was small, we did not find evidence that depressed patients were more likely to fail attention checks than healthy controls (if anything, non-psychiatric participants were more likely to be flagged by C/IE screening).
 These results provide preliminary evidence that rigorous C/IE screening is unlikely to result in overcontrol bias.
+However, further research with larger samples is necessary to validate attention checks in depressed and other patient populations.
 
@@
 Thus, we cannot be confident that all of the flagged participants were indeed engaging in C/IE responding; similarly, we cannot be certain that we correctly excluded all participants engaged in C/IE responding.
-We studied behavior-symptom correlations for only two tasks and two short self-report symptom batteries.
+We studied behavior-symptom correlations for only two tasks and two sets of self-report instruments.
 It remains to be seen how generalizable our findings are, although our study design was inspired by experiments prevalent in the online computational psychiatry literature.
@@
 Many open questions remain, including under what conditions task- and symptom-screening measures might better correspond, what screening measures are most effective and when, and under what conditions spurious correlations are more likely to arise.
+For example, in the present study, we found that screening on task behavior alone was insufficient to prevent putatively spurious correlations for one task (reversal learning) but not for another (two-step task).
+This discrepancy may reflect differences in the tasks (e.g., the two-step task may be more challenging and thus more sensitive to C/IE responding) or differences in the screening measures (e.g., choice accuracy across 90 trials may be a noisier measure than win-stay lose-shift choice behavior across 200 trials).
 One especially pressing question is how sample size affects the likelihood of obtaining spurious correlations.
@@
 As computational psychiatry studies move towards larger samples to characterize heterogeneity in symptoms (and to increase statistical power), it will be important to understand how sample size may exaggerate the effects of systematic error.
+It will also be important to understand how this is moderated by overall C/IE responding rates, which we observed to vary across platforms and time, and will presumably continue to change with evolving labor platform and researcher screening practices.
 
-\section*{Conclusions}
+% \section*{Conclusions}
 
@@
 \begin{figure}[h]
-    % \includegraphics[width=16cm]{../figures/main_01.png}
+    \includegraphics[width=16cm]{../figures/main_01.png}
     \centering
@@
     \caption{Simulated example of how spurious behavior-symptom correlations can arise when symptom endorsement is rare.
-\textit{Left:} When symptoms are moderately common in the general population, C/IE respondents (blue) are indistinguishable from attentive participants (red) in self-report measures (x-axis, marginal distribution shown on top).
-Despite the lower task performance of C/IE respondents (y-axis), no correlation arises between symptom scores and task performance (dots are participants drawn from the shown distributions, with 15\% C/IE participants; dashed line shows the (lack of) correlation.) \textit{Right:} When symptoms are rare in the general population, careless respondents appear symptomatic in self-report measures.
-As a result, self-report symptom scores show a significant correlation with task performance.}
+\textit{Left:} When symptoms are moderately common in the general population, C/IE respondents ($N=15$; blue) are indistinguishable from attentive participants ($N=85$; red) in self-report measures (x-axis, marginal distribution shown on top).
+Despite the worse task performance of C/IE respondents (y-axis), no correlation arises between symptom scores and task performance (dots are participants drawn from the shown distributions, with 15\% C/IE participants; dashed line shows the (lack of) Spearman rank correlation.) \textit{Right:} When symptoms are rare in the general population, careless respondents appear symptomatic in self-report measures.
+As a result, self-report symptom scores show a significant two-sided Spearman rank correlation with task performance.
+}
     \label{fig:simulation}
@@
 \begin{figure}[h]
-    % \includegraphics[width=16cm]{../figures/main_02a.png}
+    \includegraphics[width=16cm]{../figures/main_02a.png}
     \centering
     \captionsetup{width=0.88\textwidth}
-    \caption{Raincloud plots of total symptom scores in attentive (red) and C/IE (blue) participants.
+    \caption{Raincloud plots of total symptom scores in attentive ($N=301$; red) and C/IE ($N=85$; blue) participants.
 Each colored dot represents the symptom score for one participant.
@@
 \begin{figure}[h]
-    % \includegraphics[width=16cm, trim=0 0 3cm 0]{../figures/main_02b.png}
+    \includegraphics[width=16cm, trim=0 0 3cm 0]{../figures/main_02b.png}
     \centering
@@
     \caption{Similarity of task and self-report data screening measures.
-Each tile corresponds to the Spearman rank correlation (left) and Dice similarity coefficient (right) between two screening measures.
+Each tile corresponds to the Spearman rank correlation (left) and Dice similarity coefficient (right) between two screening measures across $N=386$ participants.
 Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times.
@@
 \begin{figure}[h]
-    % \includegraphics[width=17cm]{../figures/main_03a.png}
+    \includegraphics[width=17cm]{../figures/main_03a.png}
     \centering
@@
     \caption{Absolute Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions.
+(A) No Screening = no exclusions ($N=386$).
+(B) Accuracy Only = exclusions based on chance-level performance in the reversal-learning task ($N=352$).
+(C) Infrequency Only = exclusions based on invalid or improbable responses to infrequency items ($N=301$).
+(D) Both Types = exclusions based on the previous two measures ($N=283$).
 Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons; all signed correlations are shown in Supplementary Figure \ref{fig:correlations_s1}).
 Black Xs indicate significant correlations ablated under screening.
-No Screening = no exclusions; Accuracy Only = exclusions based on chance-level performance in the reversal-learning task; Infrequency Only = exclusions based on invalid or improbable responses to infrequency items; Both Types = exclusions based on the previous two measures.
 Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
@@
 \begin{figure}[h]
-    % \includegraphics[width=16cm]{../figures/main_03b.png}
+    \includegraphics[width=16cm]{../figures/main_03b.png}
     \centering
@@
     \caption{False positive rates for spurious correlations \emph{increase} with sample size.
-\textit{Left:} Bootstrapped Spearman correlations between learning rate asymmetry ($\kappa$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants.
-The grey error bars indicate 95\% bootstrap confidence intervals.
+\textit{Left:} Spearman correlations and 95\% bootstrap confidence intervals between learning rate asymmetry ($\kappa$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants.
 The thick dashed lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size.

### 2023-04-03 manuscripts/supp.tex
checkpointing manuscript progress

@@
 \usepackage{xcolor,soul}
+\usepackage[export]{adjustbox}    % center wide tables on page
 
@@
     \caption{Signed Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions.
+(A) No Screening = no exclusions ($N=386$).
+(B) Accuracy Only = exclusions based on chance-level performance in the reversal-learning task ($N=352$).
+(C) Infrequency Only = exclusions based on invalid or improbable responses to infrequency items ($N=301$).
+(D) Both Types = exclusions based on the previous two measures ($N=283$).
 Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons).
 Black Xs indicate significant correlations ablated under screening.
-No Screening = no exclusions; Accuracy Only = exclusions based on chance-level performance in the reversal-learning task; Infrequency Only = exclusions based on invalid or improbable responses to infrequency items; Both Types = exclusions based on the previous two measures.
 Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
@@
     \captionsetup{width=0.88\textwidth}
-    \caption{The pattern of significant behavior-symptom correlations before (panel A) and after (panel B) screening compared to the resulting pattern when random subsets of participants (22\% of total, matched to screening using the infrequency measure) are removed (panel C).
-Panels A and B are reproduced from Figure \ref{fig:correlations} for convenience.
-Panel C: the fraction of significant correlations in 5000 bootstrapped samples.
-Panel D: The similarity of the pattern of correlations after removal of random subsets to that before and after screening using the infrequency measure.
+    \caption{The pattern of significant behavior-symptom correlations before (A; $N=386$) and after (B; $N=301$) screening compared to the resulting pattern when random subsets of participants ($N=301$, matched to screening using the infrequency measure) are removed (C).
+Panels (A) and (B) are reproduced from Figure 4 for convenience.
+(C) The fraction of significant correlations in 5000 bootstrapped samples.
+(D) The similarity of the pattern of correlations after removal of random subsets to that before and after screening using the infrequency measure ($N=5000$ bootstrapped samples).
 Similarity was calculated using the simple matching coefficient.
@@
     \caption{False positive rates for spurious correlations \emph{increase} with sample size.
-\textit{Left:} Bootstrapped Spearman correlations between inverse temperature ($\beta$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants.
-The grey error bars indicate 95\% bootstrap confidence intervals.
+\textit{Left:} Spearman rank correlations and 95\% bootstrap confidence intervals between inverse temperature ($\beta$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants.
 The thick dashed lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size.
@@
     \caption{True correlations are independent of the proportion of C/IE participants in the sample.
-\textit{Left:} Bootstrapped Spearman correlations between learning rate asymmetry ($\kappa$) and anxiety scores (GAD-7) as a function of sample size and proportion of C/IE participants.
-The grey error bars indicate 95\% bootstrap confidence intervals.
+\textit{Left:} Spearman rank correlations and 95\% bootstrap confidence intervals between learning rate asymmetry ($\kappa$) and anxiety scores (GAD-7) as a function of sample size and proportion of C/IE participants.
 The thick dashed lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size.
@@
     \caption{Posterior predictive checks for the risk-sensitive temporal difference learning model.
-\textit{Panel A:} Observed (black) and predicted (blue) learning curves averaged across the group.
-\textit{Panel B:} Observed versus predicted choice accuracy for each participant.
-\textit{Panel C:} Distribution of average predictive density across participants.}
+(A) Observed (black) and predicted (blue) learning curves averaged across the group ($N=375$).
+(B) Observed versus predicted choice accuracy across participants ($N=375$).
+(C) Distribution of average predictive density across participants ($N=375$).}
     \label{fig:posterior_check}
@@
     \centering
-    \begin{tabular}{lrrr}
-    \toprule
-    {} &  Attentive &    C/IE &   $t$-value \\
-    \midrule
-    Acc      &      0.587 &   0.532 &  $4.008^*$  \\
-    Pts      &     50.163 &  47.729 &  $2.376^*$  \\
-    WS       &      0.898 &   0.776 &  $5.387^*$  \\
-    LS       &      0.609 &   0.751 &  $-5.335^*$ \\
-    Pers     &      0.245 &   0.259 &  $-1.505$ \ \\
-    $\beta$  &      6.754 &   4.082 &  $5.404^*$  \\
-    $\eta_p$ &      0.643 &   0.551 &  $2.846^*$  \\
-    $\eta_n$ &      0.738 &   0.784 & $-1.516$ \  \\
-    $\kappa$ &     -0.069 &  -0.218 &  $3.729^*$  \\
-    \bottomrule
-    \end{tabular}
-    \captionsetup{width=0.88\textwidth}
-    \caption{Measures of task behavior compared between attentive and C/IE participants.
-Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.
-*Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
+    \begin{tabular}{lcccccc}
+    \toprule
+    {} &  Attentive &    C/IE &   $t$-value &   $p$-value &  Cohen's $D$ & 95\% CI \\
+    \midrule
+    Acc      &      0.587 &   0.532 &  4.008 &  $<$0.001 &  0.492 &    [0.028, 0.082] \\
+    Pts      &     50.163 &  47.729 &  2.376 &     0.019 &  0.292 &    [0.426, 4.441] \\
+    WS       &      0.898 &   0.776 &  5.387 &  $<$0.001 &  0.662 &    [0.077, 0.165] \\
+    LS       &      0.609 &   0.751 & -5.335 &  $<$0.001 &  0.655 &  [-0.195, -0.090] \\
+    Pers     &      0.245 &   0.259 & -1.505 &     0.139 &  0.185 &   [-0.033, 0.004] \\
+    $\beta$  &      6.754 &   4.082 &  5.404 &  $<$0.001 &  0.664 &    [1.702, 3.640] \\
+    $\eta_p$ &      0.643 &   0.551 &  2.846 &     0.007 &  0.350 &    [0.029, 0.157] \\
+    $\eta_n$ &      0.738 &   0.784 & -1.516 &     0.120 &  0.186 &   [-0.106, 0.013] \\
+    $\kappa$ &     -0.069 &  -0.218 &  3.729 &  $<$0.001 &  0.458 &    [0.071, 0.227] \\
+    \bottomrule
+    \end{tabular}
+    \captionsetup{width=0.88\textwidth}
+    \caption{Measures of task behavior compared between attentive ($N=301$) and C/IE ($N=85$) participants.
+Metrics compared using two-tailed, two-sample permutation $t$-test with $df=384$ ($\alpha = 0.05$, not corrected for multiple comparisons).
+Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
 \end{table}
@@
     \centering
-    \small
+    \begin{adjustbox}{center}
+    \tiny
     \begin{tabular}{rccccccccc}
@@
         INF  &                           - &                             &                             &                          &                 &                 &                            &                 &    \\
-    ISD  &   0.372* &        - &          &          &         &         &         &        &    \\
-    REL  &  -0.408* &  -0.811* &        - &          &         &         &         &        &    \\
-    MAH  &   0.406* &   0.843* &  -0.643* &        - &         &         &         &        &    \\
-    READ &   -0.111 &   0.193* &  -0.168* &    0.138 &       - &         &         &        &    \\
-    VAR  &   -0.061 &   -0.029 &    0.058 &   -0.024 &  -0.026 &       - &         &        &    \\
-    ACC  &  -0.206* &   -0.154 &    0.099 &  -0.182* &  -0.074 &   0.027 &       - &        &    \\
-    WSLS &    0.060 &    0.102 &   -0.089 &    0.115 &   0.103 &  -0.060 &  0.221* &      - &    \\
-    RT   &    0.040 &   -0.019 &    0.014 &    0.013 &  -0.158 &  -0.007 &  -0.094 &  -0.05 &  - \\
-    \bottomrule
-    \end{tabular}
-    \captionsetup{width=0.88\textwidth}
-    \caption{Spearman's rank correlations of task and self-report data screening measures.
+    ISD  &   \textbf{0.337 ($<$0.001)} &                           - &                             &                          &                 &                 &                            &                 &    \\
+    REL  &  \textbf{-0.360 ($<$0.001)} &  \textbf{-0.804 ($<$0.001)} &                           - &                          &                 &                 &                            &                 &    \\
+    MAH  &   \textbf{0.406 ($<$0.001)} &   \textbf{0.836 ($<$0.001)} &  \textbf{-0.608 ($<$0.001)} &                        - &                 &                 &                            &                 &    \\
+    READ &              -0.111 (0.644) &   \textbf{0.209 ($<$0.001)} &     \textbf{-0.193 (0.002)} &            0.138 (0.220) &               - &                 &                            &                 &    \\
+    VAR  &              -0.061 (1.000) &              -0.038 (1.000) &               0.068 (0.999) &           -0.024 (1.000) &  -0.026 (1.000) &               - &                            &                 &    \\
+    ACC  &  \textbf{-0.206 ($<$0.001)} &              -0.133 (0.273) &               0.044 (1.000) &  \textbf{-0.182 (0.009)} &  -0.074 (0.996) &   0.027 (1.000) &                          - &                 &    \\
+    WSLS &               0.060 (1.000) &               0.103 (0.794) &              -0.085 (0.971) &            0.115 (0.574) &   0.103 (0.790) &  -0.060 (1.000) &  \textbf{0.221 ($<$0.001)} &               - &    \\
+    RT   &               0.040 (1.000) &              -0.025 (1.000) &               0.017 (1.000) &            0.013 (1.000) &  -0.158 (0.067) &  -0.007 (1.000) &             -0.094 (0.910) &  -0.050 (1.000) &  - \\
+        \bottomrule
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Spearman rank correlations ($p$-value) of task and self-report data screening measures ($N=386$).
 Each entry corresponds to the Spearman correlation between two screening measures.
 Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times.
-*Denotes statistical significance after correcting for multiple comparisons.}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \small
+Bolded entries indicate statistical significance for a two-sided rank correlation test ($\alpha = 0.05$, corrected for multiple comparisons).}
+\end{table}
+
+\begin{table}[H]
+    \centering
+    \begin{adjustbox}{center}
+    \tiny
     \begin{tabular}{rccccccccc}
@@
         INF  &                          - &                            &                            &                &                &                &                            &                &    \\
-    ISD  &  0.462* &       - &         &        &        &        &         &       &    \\
-    REL  &  0.484* &  0.691* &       - &        &        &        &         &       &    \\
-    MAH  &  0.516* &  0.732* &  0.619* &      - &        &        &         &       &    \\
-    READ &   0.319 &   0.165 &   0.165 &  0.216 &      - &        &         &       &    \\
-    VAR  &   0.208 &   0.216 &   0.238 &  0.259 &  0.292 &      - &         &       &    \\
-    ACC  &  0.379* &   0.312 &   0.258 &  0.344 &  0.237 &  0.282 &       - &       &    \\
-    WSLS &   0.253 &   0.247 &   0.227 &  0.258 &  0.299 &  0.303 &  0.505* &     - &    \\
-    RT   &   0.267 &   0.219 &   0.271 &  0.271 &  0.333 &  0.251 &   0.239 &  0.26 &  - \\
-    \bottomrule
-    \end{tabular}
-    \captionsetup{width=0.88\textwidth}
-    \caption{Dice similarity coefficients (top 10\%) for task and self-report data screening measures.
+    ISD  &  \textbf{0.462 ($<$0.001)} &                          - &                            &                &                &                &                            &                &    \\
+    REL  &  \textbf{0.484 ($<$0.001)} &  \textbf{0.691 ($<$0.001)} &                          - &                &                &                &                            &                &    \\
+    MAH  &  \textbf{0.516 ($<$0.001)} &  \textbf{0.732 ($<$0.001)} &  \textbf{0.619 ($<$0.001)} &              - &                &                &                            &                &    \\
+    READ &              0.319 (0.688) &              0.165 (1.000) &              0.165 (1.000) &  0.216 (1.000) &              - &                &                            &                &    \\
+    VAR  &              0.208 (1.000) &              0.216 (1.000) &              0.238 (1.000) &  0.259 (1.000) &  0.292 (0.981) &              - &                            &                &    \\
+    ACC  &     \textbf{0.379 (0.011)} &              0.312 (0.792) &              0.258 (1.000) &  0.344 (0.180) &  0.237 (1.000) &  0.282 (0.998) &                          - &                &    \\
+    WSLS &              0.253 (1.000) &              0.247 (1.000) &              0.227 (1.000) &  0.258 (1.000) &  0.299 (0.964) &  0.303 (0.901) &  \textbf{0.505 ($<$0.001)} &              - &    \\
+    RT   &              0.267 (1.000) &              0.219 (1.000) &              0.271 (1.000) &  0.271 (1.000) &  0.333 (0.363) &  0.251 (1.000) &              0.239 (1.000) &  0.260 (1.000) &  - \\
+        \bottomrule
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Dice similarity coefficients ($p$-value) for task and self-report data screening measures for the top 10\% most suspicious participants.
 Each entry corresponds to the Dice coefficient between two screening measures for the 10\% most suspicious participants.
 Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times.
-*Denotes statistical significance after correcting for multiple comparisons.}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \small
+Bolded entries indicate statistical significance for a two-sided Dice similarity permutation test ($\alpha = 0.05$, corrected for multiple comparisons).}
+\end{table}
+
+\begin{table}[H]
+    \centering
+    \begin{adjustbox}{center}
+    \tiny
     \begin{tabular}{rccccccccc}
@@
         INF  &                          - &                            &                            &                &                         &                &                            &                &    \\
-    ISD  &  0.355* &       - &         &        &         &        &         &        &    \\
-    REL  &  0.355* &  0.564* &       - &        &         &        &         &        &    \\
-    MAH  &  0.355* &  0.667* &  0.359* &      - &         &        &         &        &    \\
-    READ &  0.290* &   0.231 &   0.154 &  0.231 &       - &        &         &        &    \\
-    VAR  &   0.116 &   0.080 &   0.080 &  0.160 &   0.133 &      - &         &        &    \\
-    ACC  &  0.269* &   0.137 &   0.164 &  0.192 &   0.247 &  0.171 &       - &        &    \\
-    WSLS &   0.242 &   0.103 &   0.154 &  0.205 &   0.231 &  0.240 &  0.630* &      - &    \\
-    RT   &   0.164 &   0.105 &   0.132 &  0.184 &  0.289* &  0.164 &   0.225 &  0.237 &  - \\
-    \bottomrule
-    \end{tabular}
-    \captionsetup{width=0.88\textwidth}
-    \caption{Dice similarity coefficients (top 25\%) for task and self-report data screening measures.
+    ISD  &  \textbf{0.355 ($<$0.001)} &                          - &                            &                &                         &                &                            &                &    \\
+    REL  &  \textbf{0.355 ($<$0.001)} &  \textbf{0.564 ($<$0.001)} &                          - &                &                         &                &                            &                &    \\
+    MAH  &  \textbf{0.355 ($<$0.001)} &  \textbf{0.667 ($<$0.001)} &  \textbf{0.359 ($<$0.001)} &              - &                         &                &                            &                &    \\
+    READ &     \textbf{0.290 (0.006)} &              0.231 (0.231) &              0.154 (0.999) &  0.231 (0.231) &                       - &                &                            &                &    \\
+    VAR  &              0.116 (1.000) &              0.080 (1.000) &              0.080 (1.000) &  0.160 (0.996) &           0.133 (1.000) &              - &                            &                &    \\
+    ACC  &     \textbf{0.269 (0.020)} &              0.137 (1.000) &              0.164 (0.985) &  0.192 (0.809) &           0.247 (0.088) &  0.171 (0.968) &                          - &                &    \\
+    WSLS &              0.242 (0.121) &              0.103 (1.000) &              0.154 (0.999) &  0.205 (0.635) &           0.231 (0.231) &  0.240 (0.140) &  \textbf{0.630 ($<$0.001)} &              - &    \\
+    RT   &              0.164 (0.988) &              0.105 (1.000) &              0.132 (1.000) &  0.184 (0.879) &  \textbf{0.289 (0.007)} &  0.164 (0.985) &              0.225 (0.307) &  0.237 (0.162) &  - \\
+        \bottomrule
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Dice similarity coefficients ($p$-value) for task and self-report data screening measures for the top 25\% most suspicious participants.
 Each entry corresponds to the Dice coefficient between two screening measures for the 25\% most suspicious participants.
 Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times.
-*Denotes statistical significance after correcting for multiple comparisons.}
+Bolded entries indicate statistical significance for a two-sided Dice similarity permutation test ($\alpha = 0.05$, corrected for multiple comparisons).}
 \end{table}
@@
     \centering
-    \small
+    \begin{adjustbox}{center}   
+    \scriptsize
     \begin{tabular}{rccccccc}
@@
         \midrule
-    Acc      &  -0.295* &  -0.166* &  -0.093* &  -0.134* &  -0.020 &  -0.051 &  -0.037 \\
-    Pts      &  -0.225* &   -0.076 &   -0.023 &  -0.144* &  -0.061 &  -0.051 &   0.024 \\
-    WS       &  -0.327* &  -0.160* &  -0.129* &  -0.171* &  -0.006 &  -0.048 &  -0.062 \\
-    LS       &   0.285* &   0.158* &   0.146* &    0.050 &  -0.037 &   0.000 &  0.110* \\
-    Pers     &   0.134* &    0.066 &    0.032 &   0.166* &   0.018 &   0.080 &  -0.004 \\
-    $\beta$  &  -0.370* &  -0.157* &  -0.114* &  -0.185* &   0.017 &  -0.063 &  -0.043 \\
-    $\eta_p$ &  -0.097* &  -0.105* &  -0.101* &   -0.033 &  -0.020 &  -0.015 &  -0.041 \\
-    $\eta_n$ &   0.168* &   0.094* &   0.108* &   -0.050 &  -0.056 &  -0.020 &   0.042 \\
-    $\kappa$ &  -0.175* &  -0.137* &  -0.147* &   -0.008 &  -0.020 &  -0.028 &  -0.061 \\
-    \bottomrule
-    \end{tabular}
-    \captionsetup{width=0.88\textwidth}
-    \caption{Spearman correlations between task behavior and self-report symptom measures when no screening and rejections have been applied.
+        Acc      &  \textbf{-0.295 ($<$0.001)} &     \textbf{-0.166 (0.001)} &  \textbf{-0.093 (0.041)} &     \textbf{-0.134 (0.006)} &  -0.020 (0.328) &  -0.051 (0.158) &          -0.037 (0.232) \\
+    Pts      &  \textbf{-0.225 ($<$0.001)} &              -0.076 (0.065) &           -0.023 (0.315) &     \textbf{-0.144 (0.003)} &  -0.061 (0.104) &  -0.051 (0.154) &           0.024 (0.321) \\
+    WS       &  \textbf{-0.327 ($<$0.001)} &  \textbf{-0.160 ($<$0.001)} &  \textbf{-0.129 (0.009)} &  \textbf{-0.171 ($<$0.001)} &  -0.006 (0.449) &  -0.048 (0.178) &          -0.062 (0.116) \\
+    LS       &   \textbf{0.285 ($<$0.001)} &   \textbf{0.158 ($<$0.001)} &   \textbf{0.146 (0.002)} &               0.050 (0.157) &  -0.037 (0.241) &   0.000 (0.494) &  \textbf{0.110 (0.015)} \\
+    Pers     &      \textbf{0.134 (0.004)} &               0.066 (0.111) &            0.032 (0.271) &   \textbf{0.166 ($<$0.001)} &   0.018 (0.370) &   0.080 (0.064) &          -0.004 (0.469) \\
+    $\beta$  &  \textbf{-0.370 ($<$0.001)} &  \textbf{-0.157 ($<$0.001)} &  \textbf{-0.114 (0.019)} &  \textbf{-0.185 ($<$0.001)} &   0.017 (0.377) &  -0.063 (0.105) &          -0.043 (0.204) \\
+    $\eta_p$ &     \textbf{-0.097 (0.037)} &     \textbf{-0.105 (0.023)} &  \textbf{-0.101 (0.029)} &              -0.033 (0.274) &  -0.020 (0.351) &  -0.015 (0.402) &          -0.041 (0.213) \\
+    $\eta_n$ &   \textbf{0.168 ($<$0.001)} &      \textbf{0.094 (0.032)} &   \textbf{0.108 (0.016)} &              -0.050 (0.165) &  -0.056 (0.143) &  -0.020 (0.351) &           0.042 (0.205) \\
+    $\kappa$ &  \textbf{-0.175 ($<$0.001)} &     \textbf{-0.137 (0.004)} &  \textbf{-0.147 (0.002)} &              -0.008 (0.444) &  -0.020 (0.356) &  -0.028 (0.294) &          -0.061 (0.118) \\
+        \bottomrule
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Spearman rank correlation ($p$-value) between task behavior and self-report symptom measures when no screening and rejections have been applied ($N=386$).
 Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.
-*Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \small
+Bolded entries indicate statistical significance for a two-sided rank correlation test ($\alpha = 0.05$, not corrected for multiple comparisons).}
+\end{table}
+
+\begin{table}[H]
+    \centering
+    \begin{adjustbox}{center}
+    \scriptsize
     \begin{tabular}{rccccccc}
@@
         \midrule
-    Acc      &  -0.263* &  -0.144* &  -0.105* &  -0.106* &  -0.009 &  -0.020 &  -0.033 \\
-    Pts      &  -0.187* &   -0.042 &   -0.020 &  -0.126* &  -0.055 &  -0.028 &   0.036 \\
-    WS       &  -0.291* &  -0.137* &  -0.123* &  -0.161* &  -0.019 &   0.006 &  -0.044 \\
-    LS       &   0.314* &   0.170* &   0.156* &    0.034 &  -0.036 &  -0.037 &  0.124* \\
-    Pers     &    0.083 &    0.022 &    0.011 &   0.151* &   0.010 &   0.076 &  -0.021 \\
-    $\beta$  &  -0.332* &  -0.134* &  -0.109* &  -0.173* &   0.010 &  -0.040 &  -0.023 \\
-    $\eta_p$ &   -0.056 &   -0.089 &  -0.105* &   -0.013 &  -0.029 &   0.034 &  -0.035 \\
-    $\eta_n$ &   0.259* &   0.134* &   0.122* &   -0.021 &  -0.063 &   0.019 &   0.053 \\
-    $\kappa$ &  -0.171* &  -0.125* &  -0.150* &   -0.016 &  -0.032 &  -0.033 &  -0.060 \\
-    \bottomrule
-    \end{tabular}
-    \captionsetup{width=0.88\textwidth}
-    \caption{Spearman correlations between task behavior and self-report symptom measures after applying rejections based on choice accuracy (7\% of sample).
+        Acc      &  \textbf{-0.263 ($<$0.001)} &  \textbf{-0.144 (0.006)} &  \textbf{-0.105 (0.025)} &     \textbf{-0.106 (0.022)} &  -0.009 (0.436) &  -0.020 (0.363) &          -0.033 (0.272) \\
+    Pts      &  \textbf{-0.187 ($<$0.001)} &           -0.042 (0.219) &           -0.020 (0.355) &     \textbf{-0.126 (0.009)} &  -0.055 (0.149) &  -0.028 (0.300) &           0.036 (0.254) \\
+    WS       &  \textbf{-0.291 ($<$0.001)} &  \textbf{-0.137 (0.004)} &  \textbf{-0.123 (0.012)} &     \textbf{-0.161 (0.001)} &  -0.019 (0.358) &   0.006 (0.457) &          -0.044 (0.210) \\
+    LS       &   \textbf{0.314 ($<$0.001)} &   \textbf{0.170 (0.001)} &   \textbf{0.156 (0.002)} &               0.034 (0.255) &  -0.036 (0.253) &  -0.037 (0.236) &  \textbf{0.124 (0.008)} \\
+    Pers     &               0.083 (0.057) &            0.022 (0.348) &            0.011 (0.429) &      \textbf{0.151 (0.002)} &   0.010 (0.437) &   0.076 (0.090) &          -0.021 (0.338) \\
+    $\beta$  &  \textbf{-0.332 ($<$0.001)} &  \textbf{-0.134 (0.004)} &  \textbf{-0.109 (0.027)} &  \textbf{-0.173 ($<$0.001)} &   0.010 (0.430) &  -0.040 (0.239) &          -0.023 (0.335) \\
+    $\eta_p$ &              -0.056 (0.165) &           -0.089 (0.051) &  \textbf{-0.105 (0.024)} &              -0.013 (0.397) &  -0.029 (0.287) &   0.034 (0.271) &          -0.035 (0.265) \\
+    $\eta_n$ &   \textbf{0.259 ($<$0.001)} &   \textbf{0.134 (0.004)} &   \textbf{0.122 (0.011)} &              -0.021 (0.351) &  -0.063 (0.130) &   0.019 (0.362) &           0.053 (0.161) \\
+    $\kappa$ &     \textbf{-0.171 (0.001)} &  \textbf{-0.125 (0.008)} &  \textbf{-0.150 (0.002)} &              -0.016 (0.386) &  -0.032 (0.265) &  -0.033 (0.277) &          -0.060 (0.127) \\
+        \bottomrule
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Spearman rank correlation ($p$-value) between task behavior and self-report symptom measures after applying rejections based on choice accuracy ($N=352$).
 Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.
-*Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \small
+Bolded entries indicate statistical significance for a two-sided rank correlation test ($\alpha = 0.05$, not corrected for multiple comparisons).}
+\end{table}
+
+\begin{table}[H]
+    \centering
+    \begin{adjustbox}{center}        
+    \scriptsize
     \begin{tabular}{rccccccc}
@@
         \midrule
-    Acc      &  -0.210* &  -0.048 &    0.009 &   -0.082 &  -0.020 &  -0.005 &   0.009 \\
-    Pts      &  -0.167* &   0.040 &    0.070 &  -0.107* &  -0.046 &  -0.011 &   0.071 \\
-    WS       &  -0.220* &  -0.045 &   -0.008 &  -0.143* &  -0.025 &   0.001 &   0.016 \\
-    LS       &   0.219* &   0.084 &   0.113* &    0.019 &  -0.021 &  -0.050 &   0.082 \\
-    Pers     &    0.088 &  -0.028 &   -0.024 &   0.127* &   0.006 &   0.048 &  -0.052 \\
-    $\beta$  &  -0.257* &  -0.038 &    0.047 &  -0.180* &  -0.011 &  -0.032 &   0.056 \\
-    $\eta_p$ &   -0.052 &  -0.064 &   -0.079 &   -0.015 &  -0.008 &   0.004 &  -0.055 \\
-    $\eta_n$ &   0.165* &   0.067 &   0.141* &   -0.037 &  -0.089 &  -0.030 &   0.054 \\
-    $\kappa$ &  -0.111* &  -0.046 &  -0.137* &    0.011 &   0.015 &   0.002 &  -0.054 \\
-    \bottomrule
-    \end{tabular}
-    \captionsetup{width=0.88\textwidth}
-    \caption{Spearman correlations between task behavior and self-report symptom measures after applying rejections based on infrequency items (22\% of sample).
+        Acc      &  \textbf{-0.210 ($<$0.001)} &  -0.048 (0.203) &            0.009 (0.433) &              -0.082 (0.078) &  -0.020 (0.360) &  -0.005 (0.454) &   0.009 (0.431) \\
+    Pts      &     \textbf{-0.167 (0.001)} &   0.040 (0.234) &            0.070 (0.114) &     \textbf{-0.107 (0.030)} &  -0.046 (0.205) &  -0.011 (0.410) &   0.071 (0.114) \\
+    WS       &  \textbf{-0.220 ($<$0.001)} &  -0.045 (0.226) &           -0.008 (0.450) &     \textbf{-0.143 (0.007)} &  -0.025 (0.322) &   0.001 (0.494) &   0.016 (0.386) \\
+    LS       &   \textbf{0.219 ($<$0.001)} &   0.084 (0.069) &   \textbf{0.113 (0.026)} &               0.019 (0.364) &  -0.021 (0.351) &  -0.050 (0.186) &   0.082 (0.076) \\
+    Pers     &               0.088 (0.068) &  -0.028 (0.312) &           -0.024 (0.347) &      \textbf{0.127 (0.015)} &   0.006 (0.457) &   0.048 (0.204) &  -0.052 (0.176) \\
+    $\beta$  &  \textbf{-0.257 ($<$0.001)} &  -0.038 (0.254) &            0.047 (0.205) &  \textbf{-0.180 ($<$0.001)} &  -0.011 (0.428) &  -0.032 (0.301) &   0.056 (0.158) \\
+    $\eta_p$ &              -0.052 (0.184) &  -0.064 (0.138) &           -0.079 (0.082) &              -0.015 (0.409) &  -0.008 (0.449) &   0.004 (0.474) &  -0.055 (0.173) \\
+    $\eta_n$ &      \textbf{0.165 (0.002)} &   0.067 (0.120) &   \textbf{0.141 (0.007)} &              -0.037 (0.266) &  -0.089 (0.064) &  -0.030 (0.312) &   0.054 (0.174) \\
+    $\kappa$ &     \textbf{-0.111 (0.029)} &  -0.046 (0.225) &  \textbf{-0.137 (0.008)} &               0.011 (0.426) &   0.015 (0.396) &   0.002 (0.484) &  -0.054 (0.180) \\
+        \bottomrule
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Spearman rank correlation ($p$-value) between task behavior and self-report symptom measures after applying rejections based on infrequency items ($N=301$).
 Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.
-*Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
-\end{table}
-
-\begin{table}[H]
-    \centering
-    \small
+Bolded entries indicate statistical significance for a two-sided rank correlation test ($\alpha = 0.05$, not corrected for multiple comparisons).}
+\end{table}
+
+\begin{table}[H]
+    \centering
+    \begin{adjustbox}{center}        
+    \scriptsize
     \begin{tabular}{rccccccc}
@@
         \midrule
-    Acc      &  -0.229* &  -0.090 &   -0.072 &   -0.053 &   0.016 &   0.034 &  -0.040 \\
-    Pts      &  -0.177* &   0.016 &    0.011 &   -0.086 &  -0.013 &   0.025 &   0.038 \\
-    WS       &  -0.227* &  -0.085 &   -0.057 &  -0.131* &  -0.025 &   0.049 &  -0.007 \\
-    LS       &   0.236* &   0.094 &   0.107* &    0.008 &  -0.016 &  -0.075 &   0.079 \\
-    Pers     &    0.095 &  -0.007 &    0.014 &   0.110* &  -0.015 &   0.037 &  -0.025 \\
-    $\beta$  &  -0.255* &  -0.072 &   -0.008 &  -0.165* &  -0.011 &  -0.015 &   0.028 \\
-    $\eta_p$ &   -0.045 &  -0.088 &  -0.108* &    0.004 &  -0.000 &   0.049 &  -0.073 \\
-    $\eta_n$ &   0.196* &   0.046 &   0.098* &   -0.015 &  -0.085 &   0.008 &   0.024 \\
-    $\kappa$ &  -0.114* &  -0.046 &  -0.134* &    0.007 &   0.012 &  -0.004 &  -0.051 \\
-    \bottomrule
-    \end{tabular}
-    \captionsetup{width=0.88\textwidth}
-    \caption{Spearman correlations between task behavior and self-report symptom measures after applying rejections based on both choice accuracy and infrequency items.
+        Acc      &  \textbf{-0.229 ($<$0.001)} &  -0.090 (0.065) &           -0.072 (0.116) &           -0.053 (0.190) &   0.016 (0.383) &   0.034 (0.280) &  -0.040 (0.247) \\
+    Pts      &     \textbf{-0.177 (0.003)} &   0.016 (0.388) &            0.011 (0.436) &           -0.086 (0.075) &  -0.013 (0.414) &   0.025 (0.324) &   0.038 (0.267) \\
+    WS       &  \textbf{-0.227 ($<$0.001)} &  -0.085 (0.081) &           -0.057 (0.179) &  \textbf{-0.131 (0.016)} &  -0.025 (0.341) &   0.049 (0.201) &  -0.007 (0.461) \\
+    LS       &   \textbf{0.236 ($<$0.001)} &   0.094 (0.059) &   \textbf{0.107 (0.036)} &            0.008 (0.453) &  -0.016 (0.387) &  -0.075 (0.101) &   0.079 (0.080) \\
+    Pers     &               0.095 (0.056) &  -0.007 (0.459) &            0.014 (0.411) &   \textbf{0.110 (0.038)} &  -0.015 (0.392) &   0.037 (0.274) &  -0.025 (0.332) \\
+    $\beta$  &  \textbf{-0.255 ($<$0.001)} &  -0.072 (0.121) &           -0.008 (0.457) &  \textbf{-0.165 (0.003)} &  -0.011 (0.426) &  -0.015 (0.405) &   0.028 (0.326) \\
+    $\eta_p$ &              -0.045 (0.233) &  -0.088 (0.072) &  \textbf{-0.108 (0.029)} &            0.004 (0.473) &  -0.000 (0.505) &   0.049 (0.211) &  -0.073 (0.119) \\
+    $\eta_n$ &   \textbf{0.196 ($<$0.001)} &   0.046 (0.213) &   \textbf{0.098 (0.047)} &           -0.015 (0.389) &  -0.085 (0.088) &   0.008 (0.459) &   0.024 (0.342) \\
+    $\kappa$ &     \textbf{-0.114 (0.032)} &  -0.046 (0.228) &  \textbf{-0.134 (0.007)} &            0.007 (0.442) &   0.012 (0.425) &  -0.004 (0.495) &  -0.051 (0.209) \\
+        \bottomrule
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Spearman rank correlation ($p$-value) between task behavior and self-report symptom measures after applying rejections based on both choice accuracy and infrequency items ($N=283$).
 Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.
-*Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
+Bolded entries indicate statistical significance for a two-sided rank correlation test ($\alpha = 0.05$, not corrected for multiple comparisons).}
 \end{table}
@@
     \captionsetup{width=0.88\textwidth}
-    \caption{Softmax regression decision weights in attentive (red) and C/IE (blue) participants.
-The weights dictate the extent to which the recent history of rewards, nonrewards, or previous choices influence current choice.
-Error bars indicate the 95\% highest density interval of each weight.
+    \caption{Softmax regression decision weights and 95\% highest density intervals in attentive (red) and C/IE (blue) participants.
+The weights reflect the extent to which the recent history of rewards, nonrewards, or previous choices influence current choice.
 *Denotes where the 95\% highest density interval of the difference in weights excluded zero.}
@@
 This scale is expected to elicit lower rates of symptom endorsement, thereby resulting in asymmetric (right-skewed) score distributions.
-Participants also completed a 7-item measure of general anxiety symptoms over the last year (e.g.
-``I was overwhelmed by anxiety.''; \cite{watson2022development}).
+Participants also completed a 7-item measure of general anxiety symptoms over the last year (e.g., ``I was overwhelmed by anxiety.''; \cite{watson2022development}).
 This scale is expected to elicit moderate rates of symptom endorsement, thereby resulting in a symmetric score distribution.
@@
 
-In addition, participants completed a 6-item measure of artistic interests (e.g.
-``I believe in the importance of art''; \cite{ashton2007empirical}).
+In addition, participants completed a 6-item measure of artistic interests (e.g., ``I believe in the importance of art''; \cite{ashton2007empirical}).
 Based on previous studies, this scale is expected to elicit high rates of endorsement, thereby resulting in an asymmetric score distribution.
-Finally, participants completed a 6-item measure of greed avoidance, which measures attitudes towards wealth and status (e.g.
-``I am out for my own personal gain''; \cite{ashton2007empirical}).
+Finally, participants completed a 6-item measure of greed avoidance, which measures attitudes towards wealth and status (e.g., ``I am out for my own personal gain''; \cite{ashton2007empirical}).
 Based on previous studies, this scale is expected to elicit moderate rates of endorsement, thereby resulting in a symmetric score distribution.
-We therefore expected the artistic interests scale to be at greater risk for spurious correlations with behavior on the two-step task than the greed avoidance scale .
+We therefore expected the artistic interests scale to be at greater risk for spurious correlations with behavior on the two-step task than the greed avoidance scale.
 
@@
     \captionsetup{width=0.88\textwidth}
-    \caption{Raincloud plots of total symptom scores in attentive (red) and C/IE (blue) participants.
+    \caption{Raincloud plots of total symptom scores in attentive ($N=338$; red) and C/IE ($N=55$; blue) participants.
 Each colored dot represents the symptom score for one participant.
@@
 This result was (mostly) replicated in the current dataset.
-Total scores were noticeably exaggerated in participants suspected of C/IE responding for the symptom measures where overall rates of symptom endorsement were the lowest (e.g.
-mania; Figure \ref{fig:repl_distributions}, leftmost plot).
-Where there were higher rates of symptom endorsement overall (e.g.
-anxiety), the distributions of symptom scores between the two groups of participants were more similar (Figure \ref{fig:repl_distributions}, middle plots).
+Total scores were noticeably exaggerated in participants suspected of C/IE responding for the symptom measures where overall rates of symptom endorsement were the lowest (e.g., mania; Figure \ref{fig:repl_distributions}, leftmost plot).
+Where there were higher rates of symptom endorsement overall (e.g., anxiety), the distributions of symptom scores between the two groups of participants were more similar (Figure \ref{fig:repl_distributions}, middle plots).
 Permutation testing confirmed that observed mean-shifts in symptom scores for C/IE participants were statistically significant for the most skewed symptom measures (Table \ref{tab:rep_validation}).
@@
     \small
-    \begin{tabular}{lcccc}
-        \toprule
-        & & \multicolumn{3}{c}{Total Score} \\
-        \cmidrule(lr){3-5}
-        Subscale & Skew &  Attentive & C/IE & $t$-value \\
-        \midrule
-        Mania      &  1.07 &   3.25 &   6.27 & $-6.05^*$ \\
-        Depression &  0.89 &   5.72 &   6.95 & $-1.57$   \\
-        Anxiety    &  0.44 &   8.54 &   8.65 & $-0.13$   \\
-        Artistic interests   & -0.92 &  28.07 &  26.29 & $1.87$    \\
-        Greed avoidance     &  0.55 &  11.77 &  16.44 & $-4.17^*$  \\
-        \bottomrule
-    \end{tabular}
-    \captionsetup{width=0.88\textwidth}
-    \caption{Descriptive statistics of the self-report measures between attentive and C/IE participants.
-Skew: the empirical skewness of the distribution of total symptom scores.
-Total score: the average symptom score across attentive and C/IE participants.
-*Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
+    \begin{tabular}{lccccccc}
+        \toprule
+        Subscale & Skew &  Attentive & C/IE & $t$-value & $p$-value & Cohen's $D$ & 95\% CI \\
+        \midrule
+        Mania                &  1.065 &      3.249 &   6.273 & -6.054 &  $<$0.001 &  0.880 &  [-4.003, -2.045] \\
+        Depression           &  0.889 &      5.719 &   6.945 & -1.572 &  0.119 &  0.229 &   [-2.756, 0.303] \\
+        Anxiety              &  0.438 &      8.536 &   8.655 & -0.127 &  0.900 &  0.019 &   [-1.950, 1.712] \\
+        Artistic interests   & -0.918 &     28.068 &  26.291 &  1.872 &  0.061 &  0.272 &   [-0.083, 3.637] \\
+        Greed avoidance      &  0.550 &     11.769 &  16.436 & -4.166 &  $<$0.001 &  0.606 &  [-6.863, -2.472] \\
+        \bottomrule
+    \end{tabular}
+    \caption{Comparison of the self-report total scores between attentive ($N=338$) and C/IE ($N=55$) participants.
+Scores compared using two-tailed, two-sample permutation $t$-test with $df=391$ ($\alpha = 0.05$, not corrected for multiple comparisons).}
     \label{tab:rep_validation}
@@
     \caption{Similarity of task and self-report data screening measures.
-Each tile corresponds to the Spearman rank correlation (left) and Dice similarity coefficient (right) between two screening measures.
+Each tile corresponds to the Spearman rank correlation (left) and Dice similarity coefficient (right) between two screening measures across $N=393$ participants.
 Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; SV = side variability; CV = choice variability; WSLS = win-stay lose-shift rate; RT = suspicious response times.
@@
     \caption{Absolute Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions.
+(A) No Screening = no exclusions.
+(B) WSLS Only = exclusions based on chance-level performance in the two-step task.
+(C) Infrequency Only = exclusions based on invalid or improbable responses to infrequency items.
+(D) Both Types = exclusions based on the previous two measures.
 Only statistically significant correlations are shown ($p<0.05$, not corrected for multiple comparisons).
 Black Xs indicate significant correlations ablated under screening.
-No Screening = no exclusions; WSLS Only = exclusions based on chance-level performance in the two-step task; Infrequency Only = exclusions based on invalid or improbable responses to infrequency items; Both Types = exclusions based on the previous two measures.
 Acronyms: PrevRew = sensitivity to reward on the previous trial; PrevTrans = sensitivity to transition type on previous trial; MB/MF = index of model-based/model-free behavior (interaction between \textit{PrevRew} \& \textit{PrevTrans}).}
@@
 Previously, using random-intercept item factor analysis, we observed that participants engaging in C/IE responding were more likely to use the right-half of the response scale.
-As such, such a pattern of responding is more likely to produce a mean-shift in scale scores, compared to attentive participants, on a scale with a right-skewed distribution (e.g.
-mania, depression scales) than a scale with a left-skewed distribution (e.g.
-artistic interests scale).
+As such, such a pattern of responding is more likely to produce a mean-shift in scale scores, compared to attentive participants, on a scale with a right-skewed distribution (e.g., mania, depression scales) than a scale with a left-skewed distribution (e.g., artistic interests scale).
 Further research is still needed to characterize patterns of C/IE responding.
@@
 \break
+\subsection*{Correlations between behavior and symptom measures}
+
+The following are the unthresholded results of the correlation analyses between task behavior and self-report scores.
+
+\begin{table}[H]
+    \centering
+    \begin{adjustbox}{center}   
+    \small
+    \begin{tabular}{rccccc}
+        \toprule
+        {} & Mania & Depression & Anxiety & Artistic Interests & Greed Avoidance \\
+        \midrule
+        Stay      &  \textbf{-0.262 ($<$0.001)} &           -0.078 (0.055) &   0.017 (0.366) &  -0.000 (0.509) &  \textbf{-0.127 (0.007)} \\
+        PrevRew   &     \textbf{-0.115 (0.013)} &  \textbf{-0.104 (0.019)} &  -0.035 (0.255) &   0.059 (0.119) &           -0.058 (0.126) \\
+        PrevTrans &     \textbf{-0.093 (0.032)} &           -0.059 (0.115) &  -0.039 (0.215) &  -0.041 (0.215) &            0.006 (0.452) \\
+        MB/MF     &  \textbf{-0.224 ($<$0.001)} &           -0.012 (0.410) &   0.004 (0.476) &   0.018 (0.362) &  \textbf{-0.092 (0.037)} \\
+        \bottomrule
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Spearman rank correlation ($p$-value) between task behavior and self-report symptom when no screening and rejections have been applied.
+Acronyms: PrevRew = sensitivity to reward on the previous trial; PrevTrans = sensitivity to transition type on previous trial; MB/MF = index of model-based/model-free behavior (interaction between \textit{PrevRew} \& \textit{PrevTrans}).
+Bolded entries indicate statistical significance for a two-sided rank correlation test ($\alpha = 0.05$, not corrected for multiple comparisons).}
+\end{table}
+
+\begin{table}[H]
+    \centering
+    \begin{adjustbox}{center}   
+    \small
+    \begin{tabular}{rccccc}
+        \toprule
+        {} & Mania & Depression & Anxiety & Artistic Interests & Greed Avoidance \\
+        \midrule
+        Stay      &  \textbf{-0.201 ($<$0.001)} &           -0.050 (0.154) &   0.018 (0.373) &  -0.042 (0.215) &  -0.082 (0.061) \\
+        PrevRew   &              -0.088 (0.051) &  \textbf{-0.097 (0.044)} &  -0.046 (0.204) &   0.039 (0.242) &  -0.020 (0.341) \\
+        PrevTrans &              -0.084 (0.057) &           -0.048 (0.187) &  -0.022 (0.339) &  -0.036 (0.264) &   0.006 (0.451) \\
+        MB/MF     &  \textbf{-0.195 ($<$0.001)} &            0.036 (0.265) &   0.028 (0.304) &  -0.013 (0.395) &  -0.064 (0.123) \\
+        \bottomrule
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Spearman rank correlation ($p$-value) between task behavior and self-report symptom after applying rejections based on WSLS behavior.
+Acronyms: PrevRew = sensitivity to reward on the previous trial; PrevTrans = sensitivity to transition type on previous trial; MB/MF = index of model-based/model-free behavior (interaction between \textit{PrevRew} \& \textit{PrevTrans}).
+Bolded entries indicate statistical significance for a two-sided rank correlation test ($\alpha = 0.05$, not corrected for multiple comparisons).}
+\end{table}
+
+\begin{table}[H]
+    \centering
+    \begin{adjustbox}{center}   
+    \small
+    \begin{tabular}{rccccc}
+        \toprule
+        {} & Mania & Depression & Anxiety & Artistic Interests & Greed Avoidance \\
+        \midrule
+        Stay      &  \textbf{-0.159 (0.002)} &           -0.043 (0.211) &   0.029 (0.307) &  -0.080 (0.076) &  -0.052 (0.185) \\
+        PrevRew   &           -0.085 (0.075) &           -0.091 (0.058) &  -0.032 (0.297) &   0.041 (0.230) &  -0.028 (0.314) \\
+        PrevTrans &           -0.064 (0.120) &  \textbf{-0.107 (0.026)} &  -0.053 (0.157) &  -0.040 (0.226) &   0.026 (0.328) \\
+        MB/MF     &  \textbf{-0.139 (0.005)} &            0.016 (0.387) &   0.004 (0.478) &  -0.062 (0.129) &   0.015 (0.395) \\
+        \bottomrule
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Spearman rank correlation ($p$-value) between task behavior and self-report symptom after applying rejections based on infrequency items.
+Acronyms: PrevRew = sensitivity to reward on the previous trial; PrevTrans = sensitivity to transition type on previous trial; MB/MF = index of model-based/model-free behavior (interaction between \textit{PrevRew} \& \textit{PrevTrans}).
+Bolded entries indicate statistical significance for a two-sided rank correlation test ($\alpha = 0.05$, not corrected for multiple comparisons).}
+\end{table}
+
+\begin{table}[H]
+    \centering
+    \begin{adjustbox}{center}   
+    \small
+    \begin{tabular}{rccccc}
+        \toprule
+        {} & Mania & Depression & Anxiety & Artistic Interests & Greed Avoidance \\
+        \midrule
+        Stay      &  \textbf{-0.141 (0.007)} &           -0.049 (0.188) &   0.025 (0.340) &  -0.081 (0.072) &  -0.057 (0.166) \\
+        PrevRew   &           -0.081 (0.078) &  \textbf{-0.097 (0.049)} &  -0.032 (0.289) &   0.033 (0.281) &  -0.018 (0.381) \\
+        PrevTrans &           -0.050 (0.192) &           -0.093 (0.054) &  -0.031 (0.299) &  -0.033 (0.286) &   0.027 (0.321) \\
+        MB/MF     &  \textbf{-0.138 (0.008)} &            0.038 (0.242) &   0.026 (0.322) &  -0.063 (0.135) &   0.001 (0.488) \\
+        \bottomrule
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Spearman rank correlation ($p$-value) between task behavior and self-report symptom after applying rejections based on both WSLS behavior and infrequency items.
+Acronyms: PrevRew = sensitivity to reward on the previous trial; PrevTrans = sensitivity to transition type on previous trial; MB/MF = index of model-based/model-free behavior (interaction between \textit{PrevRew} \& \textit{PrevTrans}).
+Bolded entries indicate statistical significance for a two-sided rank correlation test ($\alpha = 0.05$, not corrected for multiple comparisons).}
+\end{table}
+
+\break
 \section*{Appendix C: Attention checks in healthy and psychiatric patients}
@@
 Non-clinical (control group) participants were eligible if they did not meet criteria for any psychiatric diagnosis and were not currently taking any medication used to treat psychiatric disorders.
+
+51 unique participants were recruited to participate in a behavioral experiment.
+Of these, 14 participated in both studies.
+In total, there was data from 20 sessions involving a healthy participant and data from 45 sessions involving a psychiatric participant.
+Of the 17 healthy participants, 6 identified as men and 11 identified as women.
+Of the 34 psychiatric patients, 6 identified as men, 27 identified as women, and 1 identified as non-binary.
+The healthy participants were 24.2 years old on average (sd = 3.5), whereas the psychiatric patients were 27.4 years old on average (sd = 10.6).
 
@@
 
-In total, 16 of 65 (24.6\%) participants failed one or more attention checks.
-Interestingly, the overall proportion of flagged participants was similar to that observed for the original study.
-Subdivided by group, 6 of 20 healthy participants (30\%) and 10 of 45 psychiatric participants (22\%) were flagged for C/IE responding.
+In total, 16 of 65 (24.6\%) sessions involved one or more failed attention checks.
+Interestingly, the overall proportion of flagged sessions was similar to that observed for the original study.
+Subdivided by group, 6 of 20 healthy participant sessions (30\%) and 10 of 45 psychiatric participant sessions (22\%) were flagged for C/IE responding.
 Unsurprisingly, given the modest sample size, the difference between the two proportions was not significantly different from zero (two-tailed, two-sample proportions test: $z(63)=0.672$, $p=0.502$, $h=0.178$, 95\% CI = [-0.157, 0.312]).

### 2023-04-04 manuscripts/main.tex
checkpointing manuscript progress

@@
 \usepackage{indentfirst}
-\usepackage{xr-hyper} % for cross-referencing between documents
 \usepackage{hyperref}
@@
 
-% specify footnote margins
-\renewcommand\footnotelayout{%
-  \advance\leftskip 0.7cm
-  \advance\rightskip 0.7cm
- }
-
-% setup references
-\defbibheading{main}{}
-\addbibresource[label=main]{main.bib}
-\renewcommand*{\bibfont}{\small}
-
 % specify link style
@@
 \graphicspath{ {./figures/} }
+
+% ----------------------------------%
+% Define references
+% ----------------------------------%
+
+% setup references
+\renewcommand*{\bibfont}{\small}
+
+% define references
+\begin{filecontents}{main.bib}
+@article{stewart2017crowdsourcing,
+  title={Crowdsourcing samples in cognitive science},
+  author={Stewart, Neil and Chandler, Jesse and Paolacci, Gabriele},
+  journal={Trends in cognitive sciences},
+  volume={21},
+  number={10},
+  pages={736--748},
+  year={2017},
+  publisher={Elsevier}
+}
+
+@article{chandler2016conducting,
+  title={Conducting clinical research using crowdsourced convenience samples},
+  author={Chandler, Jesse and Shapiro, Danielle},
+  journal={Annual review of clinical psychology},
+  volume={12},
+  year={2016}
+}
+
+@article{gillan2016taking,
+  title={Taking psychiatry research online},
+  author={Gillan, Claire M and Daw, Nathaniel D},
+  journal={Neuron},
+  volume={91},
+  number={1},
+  pages={19--23},
+  year={2016},
+  publisher={Elsevier}
+}
+
+@article{rutledge2019machine,
+  title={Machine learning and big data in psychiatry: toward clinical applications},
+  author={Rutledge, Robb B and Chekroud, Adam M and Huys, Quentin JM},
+  journal={Current opinion in neurobiology},
+  volume={55},
+  pages={152--159},
+  year={2019},
+  publisher={Elsevier}
+}
+
+@article{strickland2019use,
+  title={The use of crowdsourcing in addiction science research: Amazon Mechanical Turk.},
+  author={Strickland, Justin C and Stoops, William W},
+  journal={Experimental and Clinical Psychopharmacology},
+  volume={27},
+  number={1},
+  pages={1},
+  year={2019},
+  publisher={American Psychological Association}
+}
+
+@article{enkavi2019large,
+  title={Large-scale analysis of test--retest reliabilities of self-regulation measures},
+  author={Enkavi, A Zeynep and Eisenberg, Ian W and Bissett, Patrick G and Mazza, Gina L and MacKinnon, David P and Marsch, Lisa A and Poldrack, Russell A},
+  journal={Proceedings of the National Academy of Sciences},
+  volume={116},
+  number={12},
+  pages={5472--5477},
+  year={2019},
+  publisher={National Acad Sciences}
+}
+
+@article{kothe2019retention,
+  title={Retention of participants recruited to a one-year longitudinal study via Prolific},
+  author={Kothe, Emily and Ling, Mathew},
+  year={2019},
+  journal={PsyArXiv},
+  publisher={PsyArXiv}
+}
+
+@article{chandler2020participant,
+  title={Participant carelessness and fraud: Consequences for clinical research and potential solutions.},
+  author={Chandler, Jesse and Sisso, Itay and Shapiro, Danielle},
+  journal={Journal of Abnormal Psychology},
+  volume={129},
+  number={1},
+  pages={49},
+  year={2020},
+  publisher={American Psychological Association}
+}
+
+@article{ophir2020turker,
+  title={The turker blues: Hidden factors behind increased depression rates among Amazon’s Mechanical Turkers},
+  author={Ophir, Yaakov and Sisso, Itay and Asterhan, Christa SC and Tikochinski, Refael and Reichart, Roi},
+  journal={Clinical Psychological Science},
+  volume={8},
+  number={1},
+  pages={65--83},
+  year={2020},
+  publisher={Sage Publications Sage CA: Los Angeles, CA}
+}
+
+@article{curran2016methods,
+  title={Methods for the detection of carelessly invalid responses in survey data},
+  author={Curran, Paul G},
+  journal={Journal of Experimental Social Psychology},
+  volume={66},
+  pages={4--19},
+  year={2016},
+  publisher={Elsevier}
+}
+
+@article{desimone2018dirty,
+  title={Dirty data: The effects of screening respondents who provide low-quality data in survey research},
+  author={DeSimone, Justin A and Harms, PD},
+  journal={Journal of Business and Psychology},
+  volume={33},
+  number={5},
+  pages={559--577},
+  year={2018},
+  publisher={Springer}
+}
+
+@article{desimone2018differential,
+  title={The differential impacts of two forms of insufficient effort responding},
+  author={DeSimone, Justin A and DeSimone, Alice J and Harms, PD and Wood, Dustin},
+  journal={Applied Psychology},
+  volume={67},
+  number={2},
+  pages={309--338},
+  year={2018},
+  publisher={Wiley Online Library}
+}
+
+@article{hauser2016attentive,
+  title={Attentive Turkers: MTurk participants perform better on online attention checks than do subject pool participants},
+  author={Hauser, David J and Schwarz, Norbert},
+  journal={Behavior research methods},
+  volume={48},
+  number={1},
+  pages={400--407},
+  year={2016},
+  publisher={Springer}
+}
+
+@article{thomas2017validity,
+  title={Validity and Mechanical Turk: An assessment of exclusion methods and interactive experiments},
+  author={Thomas, Kyle A and Clifford, Scott},
+  journal={Computers in Human Behavior},
+  volume={77},
+  pages={184--197},
+  year={2017},
+  publisher={Elsevier}
+}
+
+@article{barends2019noncompliant,
+  title={Noncompliant responding: Comparing exclusion criteria in MTurk personality research to improve data quality},
+  author={Barends, Ard J and de Vries, Reinout E},
+  journal={Personality and individual differences},
+  volume={143},
+  pages={84--89},
+  year={2019},
+  publisher={Elsevier}
+}
+
+@article{mukherjee_reward_2020,
+  title={Reward and punishment reversal-learning in major depressive disorder},
+  author={Mukherjee, D and Filipwicz, A L S and Vo, K and Satterthwaite, T D and Kable, J W},
+  journal={Journal of Abnormal Psychology},
+  volume={129},
+  number={8},
+  pages={810--823},
+  year={2020}
+}
+
+@article{waltz2007probabilistic,
+  title={Probabilistic reversal learning impairments in schizophrenia: further evidence of orbitofrontal dysfunction},
+  author={Waltz, James A and Gold, James M},
+  journal={Schizophrenia Research},
+  volume={93},
+  number={1-3},
+  pages={296--303},
+  year={2007},
+  publisher={Elsevier}
+}
+
+@article{lowe2008validation,
+  title={Validation and standardization of the Generalized Anxiety Disorder Screener (GAD-7) in the general population},
+  author={Lowe, Bernd and Decker, Oliver and Muller, Stefanie and Brahler, Elmar and Schellberg, Dieter and Herzog, Wolfgang and Herzberg, Philipp Yorck},
+  journal={Medical care},
+  pages={266--274},
+  year={2008},
+  publisher={JSTOR}
+}
+
+@article{hinz2017psychometric,
+  title={Psychometric evaluation of the Generalized Anxiety Disorder Screener GAD-7, based on a large German general population sample},
+  author={Hinz, Andreas and Klein, Annette M and Brahler, Elmar and Glaesmer, Heide and Luck, Tobias and Riedel-Heller, Steffi G and Wirkner, Kerstin and Hilbert, Anja},
+  journal={Journal of affective disorders},
+  volume={210},
+  pages={338--344},
+  year={2017},
+  publisher={Elsevier}
+}
+
+@article{maydeu2006random,
+  title={Random intercept item factor analysis.},
+  author={Maydeu-Olivares, Albert and Coffman, Donna L},
+  journal={Psychological methods},
+  volume={11},
+  number={4},
+  pages={344},
+  year={2006},
+  publisher={American Psychological Association}
+}
+
+@article{deleeuw_2015_jspsych,
+  title={{jsPsych: A JavaScript} library for creating behavioral experiments in a web browser. },
+  author={de Leeuw, J R},
+  journal={Behavior Research Methods},
+  volume={47},
+  number={1},
+  pages={1--12},
+  year={2015}
+}
+
+@article{youngstrom_2013_susd,
+  title={The {7 Up 7 Down Inventory}: A 14-item measure of manic and depressive tendencies carved from the {General Behavior Inventory}},
+  author={Youngstrom, Eric A and Murray, Greg and Johnson, Sheri L and Findling, Robert L},
+  journal={Psychological Assessment},
+  volume={25},
+  number={4},
+  pages={1377--1383},
+  year={2013},
+  publisher={American Psychological Association}
+}
+
+@article{depue1981behavioral,
+  title={A behavioral paradigm for identifying persons at risk for bipolar depressive disorder: a conceptual framework and five validation studies},
+  author={Depue, Richard A and Slater, Judith F and Wolfstetter-Kausch, Heidi and Klein, Daniel and Goplerud, Eric and Farr, David},
+  journal={Journal of Abnormal Psychology},
+  volume={90},
+  number={5},
+  pages={381--437},
+  year={1981},
+  publisher={American Psychological Association}
+}
+
+@article{spitzer2006brief,
+  title={A brief measure for assessing generalized anxiety disorder: the {GAD-7}},
+  author={Spitzer, Robert L and Kroenke, Kurt and Williams, Janet BW and Lowe, Bernd},
+  journal={Archives of Internal Medicine},
+  volume={166},
+  number={10},
+  pages={1092--1097},
+  year={2006},
+  publisher={American Medical Association}
+}
+
+@article{carver1994behavioral,
+  title={Behavioral inhibition, behavioral activation, and affective responses to impending reward and punishment: the {BIS/BAS} scales.},
+  author={Carver, Charles S and White, Teri L},
+  journal={Journal of Personality and Social Psychology},
+  volume={67},
+  number={2},
+  pages={319--333},
+  year={1994},
+  publisher={American Psychological Association}
+}
+
+@article{pagliaccio2016revising,
+  title={Revising the {BIS/BAS} Scale to study development: measurement invariance and normative effects of age and sex from childhood through adulthood},
+  author={Pagliaccio, David and Luking, Katherine R and Anokhin, Andrey P and Gotlib, Ian H and Hayden, Elizabeth P and Olino, Thomas M and Peng, Chun-Zi and Hajcak, Greg and Barch, Deanna M},
+  journal={Psychological ssessment},
+  volume={28},
+  number={4},
+  pages={429--442},
+  year={2016},
+  publisher={American Psychological Association}
+}
+
+@article{snaith1995scale,
+  title={A scale for the assessment of hedonic tone: the Snaith--Hamilton Pleasure Scale},
+  author={Snaith, RP and Hamilton, M and Morley, S and Humayan, A and Hargreaves, D and Trigwell, P},
+  journal={The British Journal of Psychiatry},
+  volume={167},
+  number={1},
+  pages={99--103},
+  year={1995},
+  publisher={Cambridge University Press}
+}
+
+@article{meyer1990development,
+  title={Development and validation of the {Penn State Worry Questionnaire}},
+  author={Meyer, Thomas J and Miller, Mark L and Metzger, Richard L and Borkovec, Thomas D},
+  journal={Behaviour Research and Therapy},
+  volume={28},
+  number={6},
+  pages={487--495},
+  year={1990},
+  publisher={Elsevier}
+}
+
+@article{kertz2014psychometric,
+  title={Psychometric properties of abbreviated and ultra-brief versions of the {Penn State Worry Questionnaire}},
+  author={Kertz, Sarah J and Lee, Josephine and Bjorgvinsson, Throstur},
+  journal={Psychological Assessment},
+  volume={26},
+  number={4},
+  pages={1146--1154},
+  year={2014},
+  publisher={American Psychological Association}
+}
+
+@article{youngstrom2020evaluating,
+  title={Evaluating and Validating GBI Mania and Depression Short Forms for Self-Report of Mood Symptoms},
+  author={Youngstrom, Eric A and Perez Algorta, Guillermo and Youngstrom, Jennifer Kogos and Frazier, Thomas W and Findling, Robert L},
+  journal={Journal of Clinical Child \& Adolescent Psychology},
+  pages={1--17},
+  year={2020},
+  publisher={Taylor \& Francis}
+}
+
+@article{franken2007assessment,
+  title={The assessment of anhedonia in clinical and non-clinical populations: further validation of the Snaith--Hamilton Pleasure Scale (SHAPS)},
+  author={Franken, Ingmar HA and Rassin, Eric and Muris, Peter},
+  journal={Journal of affective disorders},
+  volume={99},
+  number={1-3},
+  pages={83--89},
+  year={2007},
+  publisher={Elsevier}
+}
+
+@article{marjanovic2015inter,
+  title={The inter-item standard deviation (ISD): An index that discriminates between conscientious and random responders},
+  author={Marjanovic, Zdravko and Holden, Ronald and Struthers, Ward and Cribbie, Robert and Greenglass, Esther},
+  journal={Personality and Individual Differences},
+  volume={84},
+  pages={79--83},
+  year={2015},
+  publisher={Elsevier}
+}
+
+@article{ward2018applying,
+  title={Applying social psychology to prevent careless responding during online surveys},
+  author={Ward, MK and Meade, Adam W},
+  journal={Applied Psychology},
+  volume={67},
+  number={2},
+  pages={231--263},
+  year={2018},
+  publisher={Wiley Online Library}
+}
+
+@article{emons2009detection,
+  title={Detection and diagnosis of person misfit from patterns of summed polytomous item scores},
+  author={Emons, Wilco HM},
+  journal={Applied Psychological Measurement},
+  volume={33},
+  number={8},
+  pages={599--619},
+  year={2009},
+  publisher={Sage Publications Sage CA: Los Angeles, CA}
+}
+
+@article{robinson2014inaccurate,
+  title={Inaccurate estimation of disparities due to mischievous responders: Several suggestions to assess conclusions},
+  author={Robinson-Cimpian, Joseph P},
+  journal={Educational Researcher},
+  volume={43},
+  number={4},
+  pages={171--185},
+  year={2014},
+  publisher={Sage Publications Sage CA: Los Angeles, CA}
+}
+
+@article{arias2020little,
+  title={A little garbage in, lots of garbage out: Assessing the impact of careless responding in personality survey data},
+  author={Arias, Victor B and Garrido, LE and Jenaro, C and Martinez-Molina, A and Arias, B},
+  journal={Behavior Research Methods},
+  pages={1--17},
+  year={2020},
+  publisher={Springer}
+}
+
+@article{huang2012detecting,
+  title={Detecting and deterring insufficient effort responding to surveys},
+  author={Huang, Jason L and Curran, Paul G and Keeney, Jessica and Poposki, Elizabeth M and DeShon, Richard P},
+  journal={Journal of Business and Psychology},
+  volume={27},
+  number={1},
+  pages={99--114},
+  year={2012},
+  publisher={Springer}
+}
+
+@article{maniaci2014caring,
+  title={Caring about carelessness: Participant inattention and its effects on research},
+  author={Maniaci, Michael R and Rogge, Ronald D},
+  journal={Journal of Research in Personality},
+  volume={48},
+  pages={61--83},
+  year={2014},
+  publisher={Elsevier}
+}
+
+@article{huang2015detecting,
+  title={Detecting insufficient effort responding with an infrequency scale: Evaluating validity and participant reactions},
+  author={Huang, Jason L and Bowling, Nathan A and Liu, Mengqiao and Li, Yuhui},
+  journal={Journal of Business and Psychology},
+  volume={30},
+  number={2},
+  pages={299--311},
+  year={2015},
+  publisher={Springer}
+}
+
+@article{huang2015insufficient,
+  title={Insufficient effort responding: Examining an insidious confound in survey data.},
+  author={Huang, Jason L and Liu, Mengqiao and Bowling, Nathan A},
+  journal={Journal of Applied Psychology},
+  volume={100},
+  number={3},
+  pages={828},
+  year={2015},
+  publisher={American Psychological Association}
+}
+
+@article{huang2017computational,
+  title={Computational dysfunctions in anxiety: Failure to differentiate signal from noise},
+  author={Huang, He and Thompson, Wesley and Paulus, Martin P},
+  journal={Biological psychiatry},
+  volume={82},
+  number={6},
+  pages={440--446},
+  year={2017},
+  publisher={Elsevier}
+}
+
+@article{brolsma2020challenging,
+  title={Challenging the negative learning bias hypothesis of depression: reversal learning in a naturalistic psychiatric sample},
+  author={Brolsma, Sophie CA and Vrijsen, Janna N and Vassena, Eliana and Kandroodi, Mojtaba Rostami and Bergman, M Annemiek and van Eijndhoven, Philip F and Collard, Rose M and den Ouden, Hanneke EM and Schene, Aart H and Cools, Roshan},
+  journal={Psychological Medicine},
+  pages={1--11},
+  year={2020},
+  publisher={Cambridge University Press}
+}
+
+@article{ritschel2017neural,
+  title={Neural correlates of altered feedback learning in women recovered from anorexia nervosa},
+  author={Ritschel, Franziska and Geisler, Daniel and King, Joseph A and Bernardoni, Fabio and Seidel, Maria and Boehm, Ilka and Vettermann, Richard and Biemann, Ronald and Roessner, Veit and Smolka, Michael N and others},
+  journal={Scientific reports},
+  volume={7},
+  number={1},
+  pages={1--10},
+  year={2017},
+  publisher={Nature Publishing Group}
+}
+
+@article{kool2018mental,
+  title={Mental labour},
+  author={Kool, Wouter and Botvinick, Matthew},
+  journal={Nature human behaviour},
+  volume={2},
+  number={12},
+  pages={899--908},
+  year={2018},
+  publisher={Nature Publishing Group}
+}
+
+@article{elwert2014endogenous,
+  title={Endogenous selection bias: The problem of conditioning on a collider variable},
+  author={Elwert, Felix and Winship, Christopher},
+  journal={Annual review of sociology},
+  volume={40},
+  pages={31--53},
+  year={2014},
+  publisher={Annual Reviews}
+}
+
+@ARTICLE{Kim2018-ev,
+  title    = "Detecting random responders with infrequency scales using an
+              error-balancing threshold",
+  author   = "Kim, Dale S and McCabe, Connor J and Yamasaki, Brianna L and
+              Louie, Kristine A and King, Kevin M",
+  journal  = "Behav. Res. Methods",
+  volume   =  50,
+  number   =  5,
+  pages    = "1960--1970",
+  month    =  oct,
+  year     =  2018,
+  keywords = "Careless responding; Data cleaning; Infrequency scales; Random
+              responding",
+  language = "en"
+}
+
+@article{culbreth2016negative,
+  title={Negative symptoms are associated with an increased subjective cost of cognitive effort.},
+  author={Culbreth, Adam and Westbrook, Andrew and Barch, Deanna},
+  journal={Journal of abnormal psychology},
+  volume={125},
+  number={4},
+  pages={528},
+  year={2016},
+  publisher={American Psychological Association}
+}
+
+@article{kane2016individual,
+  title={Individual differences in the executive control of attention, memory, and thought, and their associations with schizotypy.},
+  author={Kane, Michael J and Meier, Matt E and Smeekens, Bridget A and Gross, Georgina M and Chun, Charlotte A and Silvia, Paul J and Kwapil, Thomas R},
+  journal={Journal of Experimental Psychology: General},
+  volume={145},
+  number={8},
+  pages={1017},
+  year={2016},
+  publisher={American Psychological Association}
+}
+
+@article{robison2017neurotic,
+  title={The neurotic wandering mind: An individual differences investigation of neuroticism, mind-wandering, and executive control},
+  author={Robison, Matthew K and Gath, Katherine I and Unsworth, Nash},
+  journal={The Quarterly Journal of Experimental Psychology},
+  volume={70},
+  number={4},
+  pages={649--663},
+  year={2017},
+  publisher={Taylor \& Francis}
+}
+
+@article{cohen2001impairments,
+  title={Impairments of attention and effort among patients with major affective disorders},
+  author={Cohen, Ronald and Lohr, Ilan and Paul, Robert and Boland, Robert},
+  journal={The Journal of neuropsychiatry and clinical neurosciences},
+  volume={13},
+  number={3},
+  pages={385--395},
+  year={2001},
+  publisher={Am Neuropsych Assoc}
+}
+
+@article{barch2015mechanisms,
+  title={Mechanisms underlying motivational deficits in psychopathology: similarities and differences in depression and schizophrenia},
+  author={Barch, Deanna M and Pagliaccio, David and Luking, Katherine},
+  journal={Behavioral neuroscience of motivation},
+  pages={411--449},
+  year={2015},
+  publisher={Springer}
+}
+
+@article{buchanan2018methods,
+  title={Methods to detect low quality data and its implication for psychological research},
+  author={Buchanan, Erin M and Scofield, John E},
+  journal={Behavior research methods},
+  volume={50},
+  number={6},
+  pages={2586--2596},
+  year={2018},
+  publisher={Springer}
+}
+
+@article{hunter2019excessive,
+  title={Excessive deliberation in social anxiety},
+  author={Hunter, Lindsay E and Meer, Elana A and Gillan, Claire M and Hsu, Ming and Daw, Nathaniel D},
+  journal={bioRxiv},
+  pages={522433},
+  year={2019},
+  publisher={Cold Spring Harbor Laboratory}
+}
+
+@article{litman2017turkprime,
+  title={TurkPrime. com: A versatile crowdsourcing data acquisition platform for the behavioral sciences},
+  author={Litman, Leib and Robinson, Jonathan and Abberbock, Tzvi},
+  journal={Behavior research methods},
+  volume={49},
+  number={2},
+  pages={433--442},
+  year={2017},
+  publisher={Springer}
+}
+
+@article{robinson2019tapped,
+  title={Tapped out or barely tapped? Recommendations for how to harness the vast and largely unused potential of the Mechanical Turk participant pool},
+  author={Robinson, Jonathan and Rosenzweig, Cheskie and Moss, Aaron J and Litman, Leib},
+  journal={PloS one},
+  volume={14},
+  number={12},
+  pages={e0226394},
+  year={2019},
+  publisher={Public Library of Science San Francisco, CA USA}
+}
+
+@online{cloudresearch_2020,
+    author = "Leib Litman",
+    title = "New Solutions Dramatically Improve Research Data Quality on {MTurk}",
+    url  = "https://www.cloudresearch.com/resources/blog/new-tools-improve-research-data-quality-mturk/",
+    addendum = "(Accessed: 2021-02-23)",
+    month = jul,
+    year = 2020
+}
+
+@article{winkler2014permutation,
+  title={Permutation inference for the general linear model},
+  author={Winkler, Anderson M and Ridgway, Gerard R and Webster, Matthew A and Smith, Stephen M and Nichols, Thomas E},
+  journal={Neuroimage},
+  volume={92},
+  pages={381--397},
+  year={2014},
+  publisher={Elsevier}
+}
+
+@article{grant2009typology,
+  title={A typology of reviews: an analysis of 14 review types and associated methodologies},
+  author={Grant, Maria J and Booth, Andrew},
+  journal={Health information \& libraries journal},
+  volume={26},
+  number={2},
+  pages={91--108},
+  year={2009},
+  publisher={Wiley Online Library}
+}
+
+@article{niv2012neural,
+  title={Neural prediction errors reveal a risk-sensitive reinforcement-learning process in the human brain},
+  author={Niv, Yael and Edlund, Jeffrey A and Dayan, Peter and O'Doherty, John P},
+  journal={Journal of Neuroscience},
+  volume={32},
+  number={2},
+  pages={551--562},
+  year={2012},
+  publisher={Soc Neuroscience}
+}
+
+@online{stan,
+    title={Stan Modeling Language Users Guide and Reference Manual},
+    author={{Stan Development Team}},
+    year={2021},
+     url  = "https://mc-stan.org",
+}
+
+@article{wilcox2018guide,
+  title={A guide to robust statistical methods in neuroscience},
+  author={Wilcox, Rand R and Rousselet, Guillaume A},
+  journal={Current protocols in neuroscience},
+  volume={82},
+  number={1},
+  pages={8--42},
+  year={2018},
+  publisher={Wiley Online Library}
+}
+
+@article{tomitaka2018distributional,
+  title={Distributional patterns of item responses and total scores on the PHQ-9 in the general population: data from the National Health and Nutrition Examination Survey},
+  author={Tomitaka, Shinichiro and Kawasaki, Yohei and Ide, Kazuki and Akutagawa, Maiko and Yamada, Hiroshi and Ono, Yutaka and Furukawa, Toshiaki A},
+  journal={BMC psychiatry},
+  volume={18},
+  number={1},
+  pages={1--9},
+  year={2018},
+  publisher={Springer}
+}
+
+@article{eldar2015interaction,
+  title={Interaction between emotional state and learning underlies mood instability},
+  author={Eldar, Eran and Niv, Yael},
+  journal={Nature communications},
+  volume={6},
+  number={1},
+  pages={1--10},
+  year={2015},
+  publisher={Nature Publishing Group}
+}
+
+@article{cooper2007behavioural,
+  title={The behavioural inhibition system and behavioural approach system (BIS/BAS) scales: Measurement and structural invariance across adults and adolescents},
+  author={Cooper, Andrew and Gomez, Rapson and Aucote, Helen},
+  journal={Personality and individual differences},
+  volume={43},
+  number={2},
+  pages={295--305},
+  year={2007},
+  publisher={Elsevier}
+}
+
+@article{leventhal2015measuring,
+  title={Measuring anhedonia in adolescents: a psychometric analysis},
+  author={Leventhal, Adam M and Unger, Jennifer B and Audrain-McGovern, Janet and Sussman, Steve and Volk, Heather E and Strong, David R},
+  journal={Journal of personality assessment},
+  volume={97},
+  number={5},
+  pages={506--514},
+  year={2015},
+  publisher={Taylor \& Francis}
+}
+
+@article{merikangas2007lifetime,
+  title={Lifetime and 12-month prevalence of bipolar spectrum disorder in the National Comorbidity Survey replication},
+  author={Merikangas, Kathleen R and Akiskal, Hagop S and Angst, Jules and Greenberg, Paul E and Hirschfeld, Robert MA and Petukhova, Maria and Kessler, Ronald C},
+  journal={Archives of general psychiatry},
+  volume={64},
+  number={5},
+  pages={543--552},
+  year={2007},
+  publisher={American Medical Association}
+}
+
+@article{merikangas2012true,
+  title={The ‘true’ prevalence of bipolar II disorder},
+  author={Merikangas, Kathleen R and Lamers, Femke},
+  journal={Current opinion in psychiatry},
+  volume={25},
+  number={1},
+  pages={19--23},
+  year={2012},
+  publisher={LWW}
+}
+
+@article{kessler2012twelve,
+  title={Twelve-month and lifetime prevalence and lifetime morbid risk of anxiety and mood disorders in the United States},
+  author={Kessler, Ronald C and Petukhova, Maria and Sampson, Nancy A and Zaslavsky, Alan M and Wittchen, Hans-Ullrich},
+  journal={International journal of methods in psychiatric research},
+  volume={21},
+  number={3},
+  pages={169--184},
+  year={2012},
+  publisher={Wiley Online Library}
+}
+
+@article{yarrington2021impact,
+  title={Impact of the COVID-19 Pandemic on Mental Health among 157,213 Americans},
+  author={Yarrington, Julia S and Lasser, Jana and Garcia, David and Vargas, Jose Hamilton and Couto, Diego Dotta and Marafon, Thiago and Craske, Michelle G and Niles, Andrea N},
+  journal={Journal of Affective Disorders},
+  year={2021},
+  publisher={Elsevier}
+}
+
+@article{harle2017anhedonia,
+  title={Anhedonia and anxiety underlying depressive symptomatology have distinct effects on reward-based decision-making},
+  author={Harl{\'e}, Katia M and Guo, Dalin and Zhang, Shunan and Paulus, Martin P and Yu, Angela J},
+  journal={PloS one},
+  volume={12},
+  number={10},
+  pages={e0186473},
+  year={2017},
+  publisher={Public Library of Science San Francisco, CA USA}
+}
+
+@article{garrett2018updating,
+  title={Updating beliefs under perceived threat},
+  author={Garrett, Neil and Gonz{\'a}lez-Garz{\'o}n, Ana Mar{\'\i}a and Foulkes, Lucy and Levita, Liat and Sharot, Tali},
+  journal={Journal of Neuroscience},
+  volume={38},
+  number={36},
+  pages={7901--7911},
+  year={2018},
+  publisher={Soc Neuroscience}
+}
+
+@article{daw2011model,
+  title={Model-based influences on humans' choices and striatal prediction errors},
+  author={Daw, Nathaniel D and Gershman, Samuel J and Seymour, Ben and Dayan, Peter and Dolan, Raymond J},
+  journal={Neuron},
+  volume={69},
+  number={6},
+  pages={1204--1215},
+  year={2011},
+  publisher={Elsevier}
+}
+
+@article{king2018random,
+  title={Random responses inflate statistical estimates in heavily skewed addictions data},
+  author={King, Kevin M and Kim, Dale S and McCabe, Connor J},
+  journal={Drug and alcohol dependence},
+  volume={183},
+  pages={102--110},
+  year={2018},
+  publisher={Elsevier}
+}
+\end{filecontents}
+\addbibresource{main.bib}
+
+% ----------------------------------%
+% Define author / abstract block
+% ----------------------------------%
 
@@
 
+% ----------------------------------%
+% Main text
+% ----------------------------------%
+
+\begin{document}
+
+\maketitle
+
+% make abstract
+\abstract{
+\noindent Although online samples have many advantages for psychiatric research, some potential pitfalls of this approach are not widely understood.
+Here, we detail circumstances in which spurious correlations may arise between task behavior and symptom scores.
+The problem arises because many psychiatric symptom surveys have asymmetric score distributions in the general population, meaning that careless responders on these surveys will show apparently elevated symptom levels.
+If these participants are similarly careless in their task performance, this may result in a spurious association between symptom scores and task behavior.
+We demonstrate this pattern of results in two samples of participants (total N = 779) recruited online who performed one of two common cognitive tasks.
+False-positive rates for these spurious correlations increase with sample size, contrary to common assumptions.
+Excluding participants flagged for careless responding on surveys abolished these spurious correlations, but exclusion based on task performance alone was less effective.
+}
+
+% page break before introduction
+\clearpage
+
 % Define paragraph formatting
@@
 
-\begin{document}
-%TC:ignore
-
-\maketitle
-
-% make abstract
-\abstract{
-A common research design in the field of computational psychiatry involves leveraging the power of online participant recruitment to assess correlations between behavior in cognitive tasks and the self-reported severity of psychiatric symptoms in large, diverse samples.
-Although large online samples have many advantages for psychiatric research, some potential pitfalls of this research design are not widely understood.
-Here we detail circumstances in which entirely spurious correlations may arise between task behavior and symptom severity as a result of inadequate screening of careless or low-effort responding on psychiatric symptom surveys.
-Specifically, since many psychiatric symptom surveys have asymmetric ground-truth score distributions in the general population, participants who respond carelessly on these surveys will show apparently elevated symptom levels.
-If these participants are similarly careless in their task performance, and are not excluded from analysis, this may result in a spurious association between greater symptom scores and worse behavioral task performance.
-Here, we demonstrate exactly this pattern of results in two independent samples of participants (total $N = 779$) recruited online to complete a self-report symptom battery and one of two common cognitive tasks.
-We show that many behavior-symptom correlations are entirely abolished when participants flagged for careless responding on surveys are excluded from analysis.
-We also show that exclusion based on task performance alone is often insufficient to prevent these spurious correlations.
-Of note, we demonstrate that false-positive rates for these spurious correlations \emph{increase} with sample size, contrary to common assumptions.
-We offer guidance on how researchers using this general experimental design can guard against this issue in future research; in particular, we recommend the adoption of screening methods for self-report measures that are currently uncommon in this field.
-}
-
-% page break before introduction
-\clearpage
-
-% Define paragraph formatting
-\setlength{\parindent}{0em}
-\setlength{\parskip}{1em}
-
-%TC:endignore
-
-\begin{refsection}[main]
 \section*{Introduction}
@@
 
-\subsection*{Screening for C/IE responding is common for task behavior but not for self-report surveys}
+% \subsection*{Screening for C/IE responding is common for task behavior but not for self-report surveys}
+\subsection*{Narrative review of task and self-report screening practices}
 
@@
 
-Among studies that we reviewed, approximately 80\% (39/49) used at least one method to identify C/IE responding in task behavior (see Table \ref{tab:screening}).
+Among studies that we reviewed, approximately 80\% (39/49) used at least one method to identify C/IE responding in task behavior (see Table \ref{tab:tab01}).
 Of these, just over half relied on a single screening method, with considerable heterogeneity in behavior screening methods across studies.
@@
 
-\subsection*{Careless participants appear symptomatic when the overall level of symptom endorsement is low}
+% \subsection*{Careless participants appear symptomatic when the overall level of symptom endorsement is low}
+\subsection*{C/IE participants appear psychiatric when symptoms are rare}
 
@@
 In turn, a mean-shift is expected to occur when the overall rate of symptom endorsement is low; that is, comparably higher scores are more likely for C/IE participants responding at random on a right skewed questionnaire.
-In line with our predictions, the average level of symptom endorsement was noticeably exaggerated in C/IE-responding participants for the symptom measures where symptom scores were most positively-skewed (7-up, 7-down, GAD-7; see Figure \ref{fig:distributions}).
+In line with our predictions, the average level of symptom endorsement was noticeably exaggerated in C/IE-responding participants for the symptom measures where symptom scores were most positively-skewed (7-up, 7-down, GAD-7; see Figure \ref{fig:fig01}).
 In contrast, where there was higher rates of symptom endorsement overall, the distributions of symptom scores between the two groups of participants were less noticeably distinct.
-Permutation testing confirmed that observed mean-shifts in symptom scores for C/IE participants were statistically significant for the majority of symptom measures (Table \ref{tab:validation}).
+Permutation testing confirmed that observed mean-shifts in symptom scores for C/IE participants were statistically significant for the majority of symptom measures (Table \ref{tab:tab02}).
 
@@
 The logic is that, if C/IE responding manifests as a tendency to respond randomly, we should expect to see a decrease in the consistency of a measure in the C/IE responding group \cite{maniaci2014caring, desimone2018dirty, desimone2018differential}.
-In line with this reasoning, we observed a reduction in Cronbach's $\alpha$ in the C/IE group for the majority of survey instruments (Table \ref{tab:validation}).
+In line with this reasoning, we observed a reduction in Cronbach's $\alpha$ in the C/IE group for the majority of survey instruments (Table \ref{tab:tab02}).
 A permutation test confirmed that the average decrease in internal consistency across measures was greater than would be expected by chance given the difference in participant numbers between groups (two-tailed, paired-samples $t$-test: $t(6)=3.689$, $p=0.021$, $d=1.506$, 95\% CI = [0.048, 0.141]).
@@
 Previous studies have found that applying such measures reduced the prevalence of clinical symptomology in online samples towards ground truth rates from epidemiological studies \cite{ophir2020turker}.
-On the most positively-skewed measures, the fraction of participants reaching clinical levels of symptom endorsement prior to screening was greater than what would be expected (Table \ref{tab:validation}).
+On the most positively-skewed measures, the fraction of participants reaching clinical levels of symptom endorsement prior to screening was greater than what would be expected (Table \ref{tab:tab02}).
 For example, 13.0\% of participants scored at or above clinical thresholds for (hypo)mania on the 7-up scale in our sample prior to screening, compared with a 12-month prevalence of 5\% in the general population \cite{merikangas2007lifetime, merikangas2012true}, but this rate was reduced to 4.0\% (in line with the population prevalence estimates) after exclusion of C/IE respondents.
-We observed a similar pattern for both major depressive disorder and anxiety\footnote{Interestingly, compared to previous literature the proportion of participants meeting threshold on the GAD-7 was elevated.
-We suspect this may reflect elevated rates of state anxiety during the COVID-19 pandemic \cite{yarrington2021impact}, when these data were collected.} (population prevalence estimates of 7\% and 5\% respectively; \cite{kessler2012twelve, lowe2008validation, hinz2017psychometric}).
+We observed a similar pattern for both major depressive disorder and anxiety (population prevalence estimates of 7\% and 5\% respectively; \cite{kessler2012twelve, lowe2008validation, hinz2017psychometric}).
+Interestingly, the proportion of participants meeting threshold on the GAD-7 was elevated compared to previous literature.
+We suspect this may reflect elevated rates of state anxiety during the COVID-19 pandemic \cite{yarrington2021impact}, when these data were collected.
 In line with previous research, we interpret these inflated rates of clinical symptomology in our sample prior to screening as suggestive of C/IE responding \cite{ophir2020turker}.
 
-\subsection*{Low correspondence between task and self-report measures of C/IE responding}
+% \subsection*{Low correspondence between task and self-report measures of C/IE responding}
+\subsection*{Low agreement between task and self-report screening measures}
 
@@
 First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation.
-The resulting pairwise similarity matrices are presented in Figure \ref{fig:correspondence} (left panel).
+The resulting pairwise similarity matrices are presented in Figure \ref{fig:fig02} (left panel).
 After correcting for multiple comparisons, there were few significant correlations between the behavioral and self-report screening measures.
@@
 
-Second, we used the Dice similarity coefficient to quantify agreement between different screening methods in the set of participants flagged for exclusion (Figure \ref{fig:correspondence}, right panel).
+Second, we used the Dice similarity coefficient to quantify agreement between different screening methods in the set of participants flagged for exclusion (Figure \ref{fig:fig02}, right panel).
 This approach quantifies the degree of overlap between the set of would-be excluded participants based on different screening measures under a common exclusion rate.
 Though some measures have relatively clear threshold cutoffs (e.g., chance level performance for task accuracy), the majority of the measures evaluated here do not.
-As such, we evaluated the measures with respect to the top 10\% of ``suspect" participants flagged by each measure, corresponding roughly to the fraction of participants having performed at chance levels on the reversal-learning task.\footnote{Results of the same analysis repeated for the top 25\% of ``suspicious" participants (corresponding roughly to the fraction of participants flagged by the infrequency-item measure) produced similar results, and are included in the supplement.} Results were largely consistent with the correlation analysis: few pairs of task and self-report screening measures achieved levels of agreement greater than what would be expected by chance.
+As such, we evaluated the measures with respect to the top 10\% of ``suspect" participants flagged by each measure, corresponding roughly to the fraction of participants having performed at chance levels on the reversal-learning task.
+(Results of the same analysis repeated for the top 25\% of ``suspicious" participants --- corresponding roughly to the fraction of participants flagged by the infrequency-item measure --- produced similar results; see Table SXX.) Results were largely consistent with the correlation analysis: few pairs of task and self-report screening measures achieved levels of agreement greater than what would be expected by chance.
 The only significant cross-modality pair identified --- between the infrequency item and choice accuracy measures --- has a similarly coefficient less than 0.4.
@@
 
-\subsection*{Spurious symptom-behavior correlations produced by C/IE responding}
+% \subsection*{Spurious symptom-behavior correlations produced by C/IE responding}
+\subsection*{C/IE responding yields spurious symptom-behavior correlations}
 
@@
 To understand the effects of applying different forms of screening, we estimated the correlations between each unique pairing of a self-report symptom measure and measure of behavior under four different conditions: no screening, screening only on task behavior (i.e., only participants whose choice accuracy was above chance), screening only on self-report responses (i.e., only participants who responded correctly on all infrequency items), or both.
-The resulting pairwise behavior-symptom correlations following each screening procedure are presented in Figure \ref{fig:correlations}.
+The resulting pairwise behavior-symptom correlations following each screening procedure are presented in Figure \ref{fig:fig03}.
 We note that we did not correct these correlation analyses for multiple comparisons, since our purpose was to demonstrate the extent of this issue across multiple behavioral measures and self-report symptoms.
@@
 
-When no rejections based on C/IE responding was applied (i.e., all participants were included in the analysis; Figure \ref{fig:correlations}A), many significant correlations emerged between measures of task behavior and symptom scores, in particular for 4 of the self-report instruments (7-up, which measures symptoms of hypomania; 7-down, which measures symptoms of depression; GAD-7, which measures generalized anxiety symptoms; and BIS, which measures tendencies related to behavioral inhibition).
+When no rejections based on C/IE responding was applied (i.e., all participants were included in the analysis; Figure \ref{fig:fig03}A), many significant correlations emerged between measures of task behavior and symptom scores, in particular for 4 of the self-report instruments (7-up, which measures symptoms of hypomania; 7-down, which measures symptoms of depression; GAD-7, which measures generalized anxiety symptoms; and BIS, which measures tendencies related to behavioral inhibition).
 Consistent with our predictions, the majority of these correlations involved symptom measures with asymmetric total score distributions.
@@
 
-Next, we excluded participants from analysis based on task-behavior screening (i.e., choice accuracy, removing the 7\% of participants exhibiting behavior indistinguishable from chance; Figure \ref{fig:correlations}B).
+Next, we excluded participants from analysis based on task-behavior screening (i.e., choice accuracy, removing the 7\% of participants exhibiting behavior indistinguishable from chance; Figure \ref{fig:fig03}B).
 The pattern of correlations was largely unchanged: we again found many significant correlations between measures of behavior and asymmetric symptom measures, but almost no significant correlations involving symmetric symptom measures.
@@
 
-In stark contrast, when we rejected participants based on self-report screening  (removing 22\% of participants who endorsed one or more invalid or improbable responses on the infrequency items; Figure \ref{fig:correlations}C), the number of significant correlations was markedly reduced, particularly for several of the most skewed symptom measures (7-down, GAD-7) and proxy measures of task attentiveness (e.g., accuracy, inverse temperature).
-This pattern of correlations was largely similar when rejections were applied based on both task and self-report screening measures (Figure \ref{fig:correlations}D).
+In stark contrast, when we rejected participants based on self-report screening  (removing 22\% of participants who endorsed one or more invalid or improbable responses on the infrequency items; Figure \ref{fig:fig03}C), the number of significant correlations was markedly reduced, particularly for several of the most skewed symptom measures (7-down, GAD-7) and proxy measures of task attentiveness (e.g., accuracy, inverse temperature).
+This pattern of correlations was largely similar when rejections were applied based on both task and self-report screening measures (Figure \ref{fig:fig03}D).
 We also note that with stricter screening, the remaining significant correlations were, for the most part (but not always), weaker.
@@
 To test this alternative hypothesis, we performed the same correlation analysis after removing random subsets of participants, fixing the sample size to that obtained after excluding C/IE respondents.
-In this case, the pattern of significant correlations was more similar to that before screening than after screening using the infrequency measure (two-tailed, paired-samples $t$-test: $t = 262.490$, $p < 0.001$, $d = 3.713$, 95\% CI = [0.136, 0.138]; Figure \ref{fig:random}, compare to Figure \ref{fig:correlations}A).
+In this case, the pattern of significant correlations was more similar to that before screening than after screening using the infrequency measure (two-tailed, paired-samples $t$-test: $t = 262.490$, $p < 0.001$, $d = 3.713$, 95\% CI = [0.136, 0.138]; Figure S2, compare to Figure \ref{fig:fig03}A).
 Thus, the reduction in significant correlations following screening was unlikely to be driven solely by a reduction in statistical power.
@@
 Across all analyses, we measured the correlation and between the 7-down depression scale and learning-rate asymmetry ($\kappa$), which we previously identified as likely exhibiting a spurious association.
-(The following results are not specific to learning-rate asymmetry and generalize to other pairs of variables; Figure \ref{fig:bootstrap_s1}).
-
-The outputs of the bootstrapping analysis are presented in Figure \ref{fig:bootstrap}.
+(The following results are not specific to learning-rate asymmetry and generalize to other pairs of variables; Figure S3).
+
+The outputs of the bootstrapping analysis are presented in Figure \ref{fig:fig04}.
 We found that, although estimated correlation magnitudes were independent of sample size (x-axis, left panel), the absolute magnitude of the behavior-symptom correlation increased with the proportion of C/IE participants (different coloured circles, left panel).
@@
 
-\subsection*{Pattern of results generalizes to alternative tasks, self-report measures, and quality assurance protocols}
+% \subsection*{Pattern of results generalizes to alternative tasks, self-report measures, and quality assurance protocols}
+\subsection*{Findings replicate in second study with alternative measures}
 
@@
 
-\subsection*{Individuals with and without diagnosed psychiatric disorders fail attention checks at similar rates}
+% \subsection*{Individuals with and without diagnosed psychiatric disorders fail attention checks at similar rates}
+\subsection*{Psychiatric patients do not fail attention checks more often}
 
@@
 
-% \section*{Conclusions}
-
-Moving forward, we would strongly recommend that experimenters employ some form of self-report screening method, preferably one recommended by the best-practices literature (see Box 1 for a list of concrete recommendations).
-Our literature review found that, to date, the majority of online studies assessing behavior-symptom correlations have not used self-report screening, and our results demonstrate that stand-alone task-behavior screening is likely to be insufficient.
-Our results also demonstrate that inadequate screening is likely not merely to result in increased measurement error, as commonly assumed, but may also induce spurious correlations between behavioral task metrics and self-reported psychiatric symptom levels.
+We conclude with a list of concrete recommendations for future research online studies involving correlations between task behavior and self-report surveys.
+Moving forward, we would strongly recommend that experimenters employ some form of self-report screening method, preferably one recommended by the best-practices literature (e.g., \cite{huang2015insufficient, curran2016methods, thomas2017validity, desimone2018dirty, ophir2020turker}).
+Our literature review found that, to date, the majority of online studies assessing behavior-symptom correlations have not used self-report screening, and our results demonstrate that stand-alone task-behavior screening is often insufficent to prevent spurious symptom-behavior correlations induced by C/IE responding.
 For these reasons, we encourage experimenters to use a variety of data-quality checks for online studies and to be transparent in their reporting of how screening was conducted, how many participants are flagged under each measure, and what thresholds are used for rejection.
 
-More broadly, we encourage experimenters in computational psychiatry to be mindful of the myriad reasons why participants may perform worse on a behavioral task.
-Wherever possible, researchers are encouraged to design experiments where the signature of some symptomology could not also be explained by C/IE responding (e.g., \cite{eldar2015interaction, hunter2019excessive}).
-Finally, we conclude by noting that it is preferable to prevent C/IE responding than to account for it after the fact \cite{ward2018applying}.
-As such, we recommend researchers take pains to ensure their experiments promote engagement, minimize fatigue and confusion, and reimburse participants fairly and ethically.
-
-%% BOX 1 %%
-\newpage
-\textbf{Box 1: Recommendations for future research}
-
-Here we offer several concrete recommendations for future research investigating symptom-behavior correlations in online samples.
-
-\begin{itemize}
-
-    \item Use multiple screening methods to detect different types of C/IE responding.
-At a minimum, we recommend screening of both behavioral and self-report data.
-Within self-report data, we recommend using methods sensitive to multiple distinct patterns of C/IE responding (e.g., random responding, straight-lining, side bias) and, if possible, to log all page interactions (e.g., mouse clicks, keyboard presses).
-
-    \item When collecting self-report questionnaire data, include attention-check items that flag participants who may be engaging in C/IE responding.
-We recommend following best-practice guidelines in using infrequency-item checks rather than instructed-item checks, as multiple studies have now shown that online participants are habituated to and circumvent the latter \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}.
+When collecting self-report questionnaire data, we encourage experimenters to use screening methods sensitive to multiple distinct patterns of C/IE responding (e.g., random responding, straight-lining, side bias) and, if possible, to log all page interactions (e.g., mouse clicks, keyboard presses).
+We specifically recommend experimenters follow best-practice guidelines and use infrequency-item attention checks rather than instructed-item checks, as multiple studies have now shown that online participants are habituated to and circumvent the latter \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}.
 Participants flagged by suspicious responses on attention-check items should either be excluded from further analysis, or assessed using sensitivity analyses to ensure that observed full-sample correlations are robust to their exclusion.
 
-    \item We found that spurious correlations predominantly affected self-report instruments for which the expected distributions of symptom scores were asymmetric (either positively or negatively skewed).
-As such, symmetrically-distributed measures of a given construct should be preferred to asymmetrically-distributed measures (though this will often be infeasible given that the frequency of many psychiatric symptoms in the general population is itself positively skewed).
-
-    \item Scales with reverse-coded items can be used to quantify the consistency of participants' responses between reverse-coded and non-reverse-coded measures of the same latent construct.
+We found that spurious correlations predominantly affected self-report instruments for which the expected distributions of symptom scores were asymmetric (either positively or negatively skewed).
+As such, symmetrically-distributed measures of a given construct should be preferred to asymmetrically-distributed measures (though this will often be infeasible given that the prevalence of many psychiatric symptoms in the general population is typically small).
+Scales with reverse-coded items can be used to quantify the consistency of participants' responses between reverse-coded and non-reverse-coded measures of the same latent construct.
 With some care, this may be used to identify C/IE responding even for measures that do not include attention-check items \cite{emons2009detection}.
@@
 
-    \item In our experience, we have found it instructive to review discussions on public forums for participants of online labor markets (e.g., Reddit, TurkerNation).
+In our experience, we have found it instructive to review discussions on public forums for participants of online labor markets (e.g., Reddit, TurkerNation).
 Doing so helps an experimenter identify what screening methods would-be participants are already aware of and prepared to answer correctly.
@@
 
-    \item Consider carefully whether the online methodology is truly appropriate for the research question.
-In particular, if the project studies syndromes associated with considerable difficulty in task or survey engagement (e.g., severe ADHD, acute mania), symptomatic participants are likely to produce responses that cannot be distinguished from C/IE responding.
-In this case, correlational research with online samples is likely not the best methodology for the research question.
-
-\end{itemize}
-
-This is not an exhaustive list, and one overarching recommendation is that researchers studying individual differences in psychiatric symptom endorsement should engage meaningfully with methodological research from the psychological measurement literature, where many of these questions have long been studied \cite{huang2015insufficient, curran2016methods, thomas2017validity, desimone2018dirty, ophir2020turker}.
-
-%% END BOX 1 %%
+More broadly, we encourage experimenters in individual-differences cognitive science research (including computational psychiatry) to be mindful of the myriad reasons why participants may perform worse on a behavioral task.
+Wherever possible, researchers are encouraged to design experiments where the signature of some psychiatric phenomenon could not also be explained by C/IE responding (e.g., \cite{eldar2015interaction, hunter2019excessive}).
+Experimenters should also carefully consider whether an online study is truly appropriate for the research question.
+In particular, if the project aims to study syndromes associated with considerable difficulty in task or survey engagement (e.g., severe ADHD, acute mania), symptomatic participants are likely to produce responses that cannot be distinguished from C/IE responding.
+In such a case, correlational research in online samples is likely not the best approach for the research question.
+Finally, we conclude by noting that it is preferable to prevent C/IE responding than to account for it after the fact \cite{ward2018applying}.
+As such, we recommend researchers take pains to ensure their experiments promote engagement, minimize fatigue and confusion, and compensate participants fairly and ethically.
 
@@
 Participants were instructed to earn the most points possible by learning (through trial-and-error) and choosing the best choice option.
-Participants were also instructed that the best option could change during the task, but were not informed about how often or when this would occur (see the Supplement for the complete instructions).
+Participants were also instructed that the best option could change during the task, but were not informed about how often or when this would occur (see the Appendix A -- \textit{Task Instructions} for the complete instructions).
 Prior to beginning the experiment, participants had to correctly answer four comprehension questions about the instructions.
@@
 Finally, the original authors of the SHAPS scale recommended as a cutoff a score of 3 or more when the items are binarized (1 = ``strongly disagree", ``agree"; 0 = ``strongly agree", ``agree").
-We use this scoring approach in Table \ref{tab:validation}.
+We use this scoring approach in Table \ref{tab:tab02}.
 
@@
 
-We confirmed the model adequately fit participants' choice behavior through a series of posterior checks (Figure \ref{fig:posterior_check}).
+We confirmed the model adequately fit participants' choice behavior through a series of posterior checks (Figure S5).
 In particular, we confirmed the model recapitulated the group-average learning curves for each block of the experiment.
@@
     \caption{The prevalence and types of task and self-report data screening practices in a sample (N=49) of recent online behavioral studies.}
-    \label{tab:screening}
+    \label{tab:tab01}
 \end{table}
@@
 (The BIS/BAS scales do not have clinical thresholds.)}
-    \label{tab:validation}
+    \label{tab:tab02}
 \end{table}
@@
 \begin{figure}[h]
-    \includegraphics[width=16cm]{../figures/main_01.png}
+    % \includegraphics[width=16cm]{../figures/main_01.png}
     \centering
@@
 \begin{figure}[h]
-    \includegraphics[width=16cm]{../figures/main_02a.png}
+    % \includegraphics[width=16cm]{../figures/main_02a.png}
     \centering
@@
 The average level of symptom endorsement is most markedly different between groups in measures with lowest overall rates of endorsement.}
-    \label{fig:distributions}
+    \label{fig:fig01}
 \end{figure}
@@
 \begin{figure}[h]
-    \includegraphics[width=16cm, trim=0 0 3cm 0]{../figures/main_02b.png}
+    % \includegraphics[width=16cm, trim=0 0 3cm 0]{../figures/main_02b.png}
     \centering
@@
 Cross-modality correlations between task-behavior (left) and infrequency-item self-report measures (bottom) are in the dashed rectangle.}
-    \label{fig:correspondence}
+    \label{fig:fig02}
 \end{figure}
@@
 \begin{figure}[h]
-    \includegraphics[width=17cm]{../figures/main_03a.png}
+    % \includegraphics[width=17cm]{../figures/main_03a.png}
     \centering
@@
 (D) Both Types = exclusions based on the previous two measures ($N=283$).
-Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons; all signed correlations are shown in Supplementary Figure \ref{fig:correlations_s1}).
+Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons; all signed correlations are shown in Figure S1).
 Black Xs indicate significant correlations ablated under screening.
 Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
-    \label{fig:correlations}
+    \label{fig:fig03}
 \end{figure}
@@
 \begin{figure}[h]
-    \includegraphics[width=16cm]{../figures/main_03b.png}
+    % \includegraphics[width=16cm]{../figures/main_03b.png}
     \centering
@@
 The horizontal dotted line denotes the expected false positive rate at $\alpha = .05$.}
-    \label{fig:bootstrap}
+    \label{fig:fig04}
 \end{figure}
@@
 \clearpage
-\section*{References}
-
-\printbibliography[heading=main]
-\end{refsection}
+\printbibliography
 

### 2023-04-04 manuscripts/supp.tex
checkpointing manuscript progress

@@
 \usepackage{xcolor,soul}
-\usepackage[export]{adjustbox}    % center wide tables on page
-
-% specify footnote margins
-\renewcommand\footnotelayout{%
-  \advance\leftskip 0.7cm
-  \advance\rightskip 0.7cm
- }
-
-% setup references
-\defbibheading{supp}{}
-\addbibresource[label=supp]{supp.bib}
-\renewcommand*{\bibfont}{\small}
+\usepackage{adjustbox}
 
@@
 \graphicspath{ {./figures/} }
+
+% ----------------------------------%
+% Define references
+% ----------------------------------%
+
+% setup references
+\renewcommand*{\bibfont}{\small}
+
+% define references
+\begin{filecontents}{supp.bib}
+@article{seymour2012serotonin,
+  title={Serotonin selectively modulates reward value in human decision-making},
+  author={Seymour, Ben and Daw, Nathaniel D and Roiser, Jonathan P and Dayan, Peter and Dolan, Ray},
+  journal={Journal of Neuroscience},
+  volume={32},
+  number={17},
+  pages={5833--5842},
+  year={2012},
+  publisher={Soc Neuroscience}
+}
+
+@ARTICLE{Katahira2018-ke,
+  title    = "The statistical structures of reinforcement learning with
+              asymmetric value updates",
+  author   = "Katahira, Kentaro",
+  journal  = "J. Math. Psychol.",
+  volume   =  87,
+  pages    = "31--45",
+  month    =  dec,
+  year     =  2018,
+  keywords = "Reinforcement learning; Asymmetric value update; Learning rate;
+              Choice perseverance; Model fitting; Logistic regression"
+}
+
+@article{sugawara2021dissociation,
+  title={Dissociation between asymmetric value updating and perseverance in human reinforcement learning},
+  author={Sugawara, Michiyo and Katahira, Kentaro},
+  journal={Scientific reports},
+  volume={11},
+  number={1},
+  pages={1--13},
+  year={2021},
+  publisher={Nature Publishing Group}
+}
+
+@online{cloudresearch_2020-2,
+    author = "Leib Litman",
+    title = "New Solutions Dramatically Improve Research Data Quality on {MTurk}",
+    url  = "https://www.cloudresearch.com/resources/blog/new-tools-improve-research-data-quality-mturk/",
+    addendum = "(Accessed: 2021-02-23)",
+    month = jul,
+    year = 2020
+}
+
+@article{hauser2021evaluating,
+  title={Evaluating CloudResearch’s Approved Group as a Solution for Problematic Data Quality on MTurk},
+  author={Hauser, David and Moss, Aaron J and Rosenzweig, Cheskie and Jaffe, Shalom Noach and Robinson, Jonathan and LItman, Leib},
+  year={2021},
+  publisher={PsyArXiv}
+}
+
+@MISC{Letzter2021-bw,
+  title        = "A teenager on {TikTok} disrupted thousands of scientific
+                  studies with a single video",
+  author       = "Letzter, Rafi",
+  month        =  sep,
+  year         =  2021,
+  howpublished = "\url{https://www.theverge.com/2021/9/24/22688278/tiktok-science-study-survey-prolific}",
+  note         = "Accessed: 2022-10-17"
+}
+
+@MISC{prolific_2021,
+  title        = "We recently went viral on {TikTok} - here's what we learned",
+  howpublished = "\url{https://www.prolific.co/blog/we-recently-went-viral-on-tiktok-heres-what-we-learned}",
+  note         = "Accessed: 2022-10-17",
+  language     = "en"
+}
+
+@article{daw2011model,
+  title={Model-based influences on humans' choices and striatal prediction errors},
+  author={Daw, Nathaniel D and Gershman, Samuel J and Seymour, Ben and Dayan, Peter and Dolan, Raymond J},
+  journal={Neuron},
+  volume={69},
+  number={6},
+  pages={1204--1215},
+  year={2011},
+  publisher={Elsevier}
+}
+
+@article{litman2017turkprime-2,
+  title={TurkPrime. com: A versatile crowdsourcing data acquisition platform for the behavioral sciences},
+  author={Litman, Leib and Robinson, Jonathan and Abberbock, Tzvi},
+  journal={Behavior research methods},
+  volume={49},
+  number={2},
+  pages={433--442},
+  year={2017},
+  publisher={Springer}
+}
+
+@article{robinson2019tapped-2,
+  title={Tapped out or barely tapped? Recommendations for how to harness the vast and largely unused potential of the Mechanical Turk participant pool},
+  author={Robinson, Jonathan and Rosenzweig, Cheskie and Moss, Aaron J and Litman, Leib},
+  journal={PloS one},
+  volume={14},
+  number={12},
+  pages={e0226394},
+  year={2019},
+  publisher={Public Library of Science San Francisco, CA USA}
+}
+
+@article{decker2016creatures,
+  title={From creatures of habit to goal-directed learners: Tracking the developmental emergence of model-based reinforcement learning},
+  author={Decker, Johannes H and Otto, A Ross and Daw, Nathaniel D and Hartley, Catherine A},
+  journal={Psychological science},
+  volume={27},
+  number={6},
+  pages={848--858},
+  year={2016},
+  publisher={Sage Publications Sage CA: Los Angeles, CA}
+}
+
+@article{watson2022development,
+  title={The development of preliminary HiTOP internalizing spectrum scales},
+  author={Watson, David and Forbes, Miriam K and Levin-Aspenson, Holly F and Ruggero, Camilo J and Kotelnikova, Yuliya and Khoo, Shereen and Bagby, R Michael and Sunderland, Matthew and Patalay, Praveetha and Kotov, Roman},
+  journal={Assessment},
+  volume={29},
+  number={1},
+  pages={17--33},
+  year={2022},
+  publisher={Sage Publications Sage CA: Los Angeles, CA}
+}
+
+@article{ashton2007empirical,
+  title={Empirical, theoretical, and practical advantages of the HEXACO model of personality structure},
+  author={Ashton, Michael C and Lee, Kibeom},
+  journal={Personality and social psychology review},
+  volume={11},
+  number={2},
+  pages={150--166},
+  year={2007},
+  publisher={SAGE publications Sage CA: Los Angeles, CA}
+}
+
+@article{deleeuw_2015_jspsych-2,
+  title={{jsPsych: A JavaScript} library for creating behavioral experiments in a web browser. },
+  author={de Leeuw, J R},
+  journal={Behavior Research Methods},
+  volume={47},
+  number={1},
+  pages={1--12},
+  year={2015}
+}
+
+@article{youngstrom_2013_susd-2,
+  title={The {7 Up 7 Down Inventory}: A 14-item measure of manic and depressive tendencies carved from the {General Behavior Inventory}},
+  author={Youngstrom, Eric A and Murray, Greg and Johnson, Sheri L and Findling, Robert L},
+  journal={Psychological Assessment},
+  volume={25},
+  number={4},
+  pages={1377--1383},
+  year={2013},
+  publisher={American Psychological Association}
+}
+
+@article{winkler2014permutation-2,
+  title={Permutation inference for the general linear model},
+  author={Winkler, Anderson M and Ridgway, Gerard R and Webster, Matthew A and Smith, Stephen M and Nichols, Thomas E},
+  journal={Neuroimage},
+  volume={92},
+  pages={381--397},
+  year={2014},
+  publisher={Elsevier}
+}
+
+@article{wilcox2018guide-2,
+  title={A guide to robust statistical methods in neuroscience},
+  author={Wilcox, Rand R and Rousselet, Guillaume A},
+  journal={Current protocols in neuroscience},
+  volume={82},
+  number={1},
+  pages={8--42},
+  year={2018},
+  publisher={Wiley Online Library}
+}
+
+@article{harms2018making,
+  title={Making'null effects' informative: statistical techniques and inferential frameworks},
+  author={Harms, Christopher and Lakens, Dani{\"e}l},
+  journal={Journal of Clinical and Translational Research},
+  volume={3},
+  number={Suppl 2},
+  pages={382},
+  year={2018},
+  publisher={Whioce Publishing Pte. Ltd.}
+}
+
+@book{cohen2013statistical,
+  title={Statistical power analysis for the behavioral sciences},
+  author={Cohen, Jacob},
+  year={2013},
+  publisher={Routledge}
+}
+
+@article{gillan2016characterizing,
+  title={Characterizing a psychiatric symptom dimension related to deficits in goal-directed control},
+  author={Gillan, Claire M and Kosinski, Michal and Whelan, Robert and Phelps, Elizabeth A and Daw, Nathaniel D},
+  journal={elife},
+  volume={5},
+  pages={e11305},
+  year={2016},
+  publisher={eLife Sciences Publications Limited}
+}
+
+@inproceedings{seabold2010statsmodels,
+  title={Statsmodels: Econometric and statistical modeling with python},
+  author={Seabold, Skipper and Perktold, Josef},
+  booktitle={Proceedings of the 9th Python in Science Conference},
+  volume={57},
+  number={61},
+  pages={10--25080},
+  year={2010},
+  organization={Austin, TX}
+}
+
+@article{barends2019noncompliant-2,
+  title={Noncompliant responding: Comparing exclusion criteria in MTurk personality research to improve data quality},
+  author={Barends, Ard J and de Vries, Reinout E},
+  journal={Personality and individual differences},
+  volume={143},
+  pages={84--89},
+  year={2019},
+  publisher={Elsevier}
+}
+
+@article{hauser2016attentive-2,
+  title={Attentive Turkers: MTurk participants perform better on online attention checks than do subject pool participants},
+  author={Hauser, David J and Schwarz, Norbert},
+  journal={Behavior research methods},
+  volume={48},
+  number={1},
+  pages={400--407},
+  year={2016},
+  publisher={Springer}
+}
+
+@article{thomas2017validity-2,
+  title={Validity and Mechanical Turk: An assessment of exclusion methods and interactive experiments},
+  author={Thomas, Kyle A and Clifford, Scott},
+  journal={Computers in Human Behavior},
+  volume={77},
+  pages={184--197},
+  year={2017},
+  publisher={Elsevier}
+}
+
+@article{barch2015mechanisms-2,
+  title={Mechanisms underlying motivational deficits in psychopathology: similarities and differences in depression and schizophrenia},
+  author={Barch, Deanna M and Pagliaccio, David and Luking, Katherine},
+  journal={Behavioral neuroscience of motivation},
+  pages={411--449},
+  year={2015},
+  publisher={Springer}
+}
+
+@article{elwert2014endogenous-2,
+  title={Endogenous selection bias: The problem of conditioning on a collider variable},
+  author={Elwert, Felix and Winship, Christopher},
+  journal={Annual review of sociology},
+  volume={40},
+  pages={31--53},
+  year={2014},
+  publisher={Annual Reviews}
+}
+
+@article{cohen2001impairments-2,
+  title={Impairments of attention and effort among patients with major affective disorders},
+  author={Cohen, Ronald and Lohr, Ilan and Paul, Robert and Boland, Robert},
+  journal={The Journal of neuropsychiatry and clinical neurosciences},
+  volume={13},
+  number={3},
+  pages={385--395},
+  year={2001},
+  publisher={Am Neuropsych Assoc}
+}
+
+@article{culbreth2016negative-2,
+  title={Negative symptoms are associated with an increased subjective cost of cognitive effort.},
+  author={Culbreth, Adam and Westbrook, Andrew and Barch, Deanna},
+  journal={Journal of abnormal psychology},
+  volume={125},
+  number={4},
+  pages={528},
+  year={2016},
+  publisher={American Psychological Association}
+}
+
+@article{kane2016individual-2,
+  title={Individual differences in the executive control of attention, memory, and thought, and their associations with schizotypy.},
+  author={Kane, Michael J and Meier, Matt E and Smeekens, Bridget A and Gross, Georgina M and Chun, Charlotte A and Silvia, Paul J and Kwapil, Thomas R},
+  journal={Journal of Experimental Psychology: General},
+  volume={145},
+  number={8},
+  pages={1017},
+  year={2016},
+  publisher={American Psychological Association}
+}
+
+@article{robison2017neurotic-2,
+  title={The neurotic wandering mind: An individual differences investigation of neuroticism, mind-wandering, and executive control},
+  author={Robison, Matthew K and Gath, Katherine I and Unsworth, Nash},
+  journal={The Quarterly Journal of Experimental Psychology},
+  volume={70},
+  number={4},
+  pages={649--663},
+  year={2017},
+  publisher={Taylor \& Francis}
+}
+\end{filecontents}
+\addbibresource{supp.bib}
+
+% ----------------------------------%
+% Define author / abstract block
+% ----------------------------------%
 
@@
 
+% ----------------------------------%
+% Main text
+% ----------------------------------%
+
+\begin{document}
+
+\maketitle
+
 % Define paragraph formatting
@@
 \setlength{\parskip}{1em}
-
-\begin{document}
-
-\maketitle
-\begin{refsection}[supp]
 
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
     \includegraphics[width=17cm]{../figures/supp_01.png}
@@
 Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
-    \label{fig:correlations_s1}
+    \label{fig:figS01}
 \end{figure}
@@
 Random removal subsets were significantly more similar to the ``No Screening" than to the ``Infrequency" screening datasets (two-tailed, paired-samples $t$-test: $t = 262.490$, $p < 0.001$, $d = 3.713$, 95\% CI = [0.136, 0.138]).}
-    \label{fig:random}
+    \label{fig:figS02}
 \end{figure}
@@
 The horizontal dotted line denotes the expected false positive rate at $\alpha = 0.05$.}
-    \label{fig:bootstrap_s1}
+    \label{fig:figS03}
 \end{figure}
@@
 The horizontal dotted line denotes the expected false positive rate at $\alpha = 0.05$.}
-    \label{fig:bootstrap_s2}
+    \label{fig:figS04}
 \end{figure}
@@
 (C) Distribution of average predictive density across participants ($N=375$).}
-    \label{fig:posterior_check}
+    \label{fig:figS05}
 \end{figure}
@@
 Note: the demographics do not include 20 participants excluded for participating in the study twice, once per platform.}
-    \label{tab:demographics}
+    \label{tab:tabS01}
 \end{table}
@@
 Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
+    \label{tab:tabS02}
 \end{table}
@@
 Bolded entries indicate statistical significance for a two-sided rank correlation test ($\alpha = 0.05$, corrected for multiple comparisons).}
+    \label{tab:tabS03}
 \end{table}
@@
 Bolded entries indicate statistical significance for a two-sided Dice similarity permutation test ($\alpha = 0.05$, corrected for multiple comparisons).}
+    \label{tab:tabS04}
 \end{table}
@@
 Bolded entries indicate statistical significance for a two-sided Dice similarity permutation test ($\alpha = 0.05$, corrected for multiple comparisons).}
+    \label{tab:tabS05}
 \end{table}
@@
 Bolded entries indicate statistical significance for a two-sided rank correlation test ($\alpha = 0.05$, not corrected for multiple comparisons).}
+    \label{tab:tabS06}
 \end{table}
@@
 Bolded entries indicate statistical significance for a two-sided rank correlation test ($\alpha = 0.05$, not corrected for multiple comparisons).}
+    \label{tab:tabS07}
 \end{table}
@@
 Bolded entries indicate statistical significance for a two-sided rank correlation test ($\alpha = 0.05$, not corrected for multiple comparisons).}
+    \label{tab:tabS08}
 \end{table}
@@
 Bolded entries indicate statistical significance for a two-sided rank correlation test ($\alpha = 0.05$, not corrected for multiple comparisons).}
+    \label{tab:tabS09}
 \end{table}
@@
 
-\subsection*{C/IE responding manifests as qualitatively distinct behavioral strategy}
+\subsection*{C/IE responding manifests as a distinct behavioral strategy}
 
@@
     \centering
-    \captionsetup{width=0.88\textwidth}
     \caption{Softmax regression decision weights and 95\% highest density intervals in attentive (red) and C/IE (blue) participants.
@@
 Participants were recruited as part of two independent studies to investigate reward processing in individuals with and without a history of major depression and bipolar disorder (results of those studies not reported here).
-Both studies required participants to complete (1) a structured clinical interview (the SCID-5) with a trained interviewer to verify that they met the criteria for one or more psychiatric disorders, and (2) a series of computerized self-report surveys and cognitive tasks.
+The studies were approved by the Institutional Review Board of Rutgers University (\#2019000738, \#2018000629), and all participants provided informed consent.
+Participants received monetary compensation for their time (rate USD \$12/hr), plus an incentive-compatible bonus based on task performance.
 
@@
 Specifically, participants completed each session from their homes while on Zoom with a study coordinator.
+Both studies required participants to complete (1) a structured clinical interview (the SCID-5) with a trained interviewer to verify that they met the criteria for one or more psychiatric disorders, and (2) a series of computerized self-report surveys and cognitive tasks.
 During each session, while participants were completing self-report questionnaires or behavioral tasks, the study coordinator turned off their camera and microphone, but was available if the participant had any questions.
@@
 
-51 unique participants were recruited to participate in a behavioral experiment.
+52 unique participants were recruited to participate in a behavioral experiment.
 Of these, 14 participated in both studies.
@@
 Of the 17 healthy participants, 6 identified as men and 11 identified as women.
-Of the 34 psychiatric patients, 6 identified as men, 27 identified as women, and 1 identified as non-binary.
+Of the 35 psychiatric patients, 6 identified as men, 27 identified as women, 1 identified as non-binary, and 1 preferred not to say.
 The healthy participants were 24.2 years old on average (sd = 3.5), whereas the psychiatric patients were 27.4 years old on average (sd = 10.6).
@@
 
-\section*{Supplementary references}
-
-\printbibliography[heading=supp]
-\end{refsection}
+\printbibliography[title=Supplementary References]
 

### 2023-04-10 manuscripts/main.tex
checkpointing manuscript progress

@@
 
-@article{hunter2019excessive,
-  title={Excessive deliberation in social anxiety},
+@article{hunter2022increased,
+  title={Increased and biased deliberation in social anxiety},
   author={Hunter, Lindsay E and Meer, Elana A and Gillan, Claire M and Hsu, Ming and Daw, Nathaniel D},
-  journal={bioRxiv},
-  pages={522433},
-  year={2019},
-  publisher={Cold Spring Harbor Laboratory}
+  journal={Nature Human Behaviour},
+  volume={6},
+  number={1},
+  pages={146--154},
+  year={2022},
+  publisher={Nature Publishing Group UK London}
 }
@@
 Since participants recruited from online labor markets are typically completing experiments in their homes, they may be more likely to be distracted or multi-tasking during an experiment.
-They may also be more likely to use heuristic response strategies with the intention to minimise expenditure of time and cognitive effort (e.g., responding randomly on self-report surveys or behavioral tasks).
+They may also be more likely to use heuristic response strategies with the intention to minimize expenditure of time and cognitive effort (e.g., responding randomly on self-report surveys or behavioral tasks).
 Here, we will refer to such inattentive or low-effort behaviors as careless/insufficient effort (C/IE) responding \cite{huang2012detecting, curran2016methods}.
@@
 Here we wish to draw special attention to an underappreciated feature of psychiatric research using self-report symptom surveys.
-In such surveys, participants rate their endorsement of various psychiatric symptoms and, since most individuals in the general population tend to endorse no or few symptoms in many symptom domains, the resulting ground-truth symptom distributions tend to be heavily positively skewed \cite{lowe2008validation, tomitaka2018distributional}.
+In such surveys, participants rate their endorsement of various psychiatric symptoms and, since most individuals in the general population tend to endorse no or few symptoms in many symptom domains, the resulting ground-truth symptom score distributions tend to be heavily positively skewed \cite{lowe2008validation, tomitaka2018distributional}.
 In this situation, the assumption that C/IE responding merely increases unsystematic measurement noise becomes untenable.
@@
 
-When participants complete both symptom surveys and behavioral tasks---a common study design in computational psychiatry---this artifact has the potential to induce spurious correlations between symptom self-reports and task behavior.
+When participants complete both symptom surveys and behavioral tasks---a common study design in computational psychiatry---this artifact has the potential to induce spurious correlations between symptom self-report scores and task behavior.
 That is, while C/IE behavior is traditionally thought of as a source of noise that can result in type II (false negative) errors, here we suggest that in large-scale online psychiatric studies it can instead result in type I (false positive) errors.
 Concretely, if the same participants who engage in C/IE responding on surveys (and who therefore inaccurately report high levels of psychiatric symptoms) also respond with insufficient effort on behavioral tasks, this can cause experimenters to observe an entirely spurious correlation between greater symptom severity and worse task performance (see Figure \ref{fig:simulation}).
-A similar effect has been well documented in personality psychology, where the presence of C/IE responding can induce correlations between questionnaires, and bias estimated factors in factor analysis \cite{huang2012detecting, robinson2014inaccurate, huang2015insufficient, chandler2020participant, arias2020little}.
+A similar effect has been well documented in personality psychology, where the presence of C/IE responding can induce correlations between questionnaires, and bias factor estimation in factor analysis \cite{huang2012detecting, robinson2014inaccurate, huang2015insufficient, chandler2020participant, arias2020little}.
 
@@
 We then asked whether behavioral screening alone was sufficient to identify participants engaging in C/IE responding on psychiatric symptom surveys.
-In two new datasets from two separate online labor marketplaces, we found that screening based on task behavior fails to completely identify participants engaging in C/IE responding on surveys.
+In two new datasets from two separate online labor markets, we found that screening based on task behavior fails to completely identify participants engaging in C/IE responding on surveys.
 Lastly, we investigated whether, under these circumstances, C/IE responding led to spurious correlations between symptom severity and task performance for positively-skewed symptom measures.
@@
 
-Among studies that we reviewed, approximately 80\% (39/49) used at least one method to identify C/IE responding in task behavior (see Table \ref{tab:tab01}).
+Among studies that we reviewed, approximately 80\% (39/49) used at least one method to identify C/IE responding in task behavior (Table \ref{tab:tab01}).
 Of these, just over half relied on a single screening method, with considerable heterogeneity in behavior screening methods across studies.
@@
 The five self-report measures were the 7-up (which measures symptoms of hypomania), the 7-down (which measures symptoms of depression), the GAD-7, (which measures generalized anxiety symptoms), the BIS/BAS (which measures reward and punishment motivations), the SHAPS (which measures anhedonia symptoms), and the PSWQ (which measures worry symptoms), and were chosen based on previous literature to have a variety of expected response distributions (symmetric and asymmetric).
-In line with current best-practice recommendations in personality psychology \cite{huang2015detecting}, each self-report instrument included one `infrequency' item that could be used to identify C/IE responses in survey data (see Methods for a list of infrequency items).
+In line with current best-practice recommendations \cite{huang2015detecting}, each self-report instrument included one `infrequency' item that could be used to identify C/IE responses in survey data (see Methods for a list of infrequency items).
 The entire experiment (surveys and task) was designed to require 10 minutes on average to complete (observed mean = 10.28 minutes).
@@
 We hypothesise that spurious behavior-symptom correlations may emerge due to a mean-shift in the average level of symptom endorsement in participants engaging in C/IE responding relative to attentive participants.
-In turn, a mean-shift is expected to occur when the overall rate of symptom endorsement is low; that is, comparably higher scores are more likely for C/IE participants responding at random on a right skewed questionnaire.
-In line with our predictions, the average level of symptom endorsement was noticeably exaggerated in C/IE-responding participants for the symptom measures where symptom scores were most positively-skewed (7-up, 7-down, GAD-7; see Figure \ref{fig:fig01}).
+In turn, a mean-shift is expected to occur when the overall rate of symptom endorsement is low; that is, comparably higher scores are more likely for C/IE participants responding at random on a questionnaire with a right-skewed score distribution.
+In line with our predictions, the average level of symptom endorsement was noticeably exaggerated in C/IE-responding participants for the symptom measures where symptom scores were most positively-skewed (7-up, 7-down, GAD-7; Figure \ref{fig:fig01}).
 In contrast, where there was higher rates of symptom endorsement overall, the distributions of symptom scores between the two groups of participants were less noticeably distinct.
@@
 In line with this reasoning, we observed a reduction in Cronbach's $\alpha$ in the C/IE group for the majority of survey instruments (Table \ref{tab:tab02}).
-A permutation test confirmed that the average decrease in internal consistency across measures was greater than would be expected by chance given the difference in participant numbers between groups (two-tailed, paired-samples $t$-test: $t(6)=3.689$, $p=0.021$, $d=1.506$, 95\% CI = [0.048, 0.141]).
+A permutation test confirmed that the average decrease in internal consistency across measures was greater than would be expected by chance given the difference in participant numbers between groups (two-tailed, paired-samples $t$-test: $t(6)=-3.689$, $p=0.021$, $d=1.506$, 95\% CI = [-0.048, -0.141]).
 
@@
 We fit a random-intercept item factor-analysis model \cite{maydeu2006random} to self-report data (see Methods), and for each participant we estimated an intercept parameter that quantified their bias towards using responses on the left or right side of the response scale, regardless of what that response signifies for a particular self-report measure (e.g., low on one symptom scale versus high on another).
-We observed a credible difference between the average value of this intercept for the two groups ($\Delta \text{intercept} = 0.67, 95\% \ \text{HDI} = [-0.78, -0.55]$), such that C/IE participants were biased towards using the right-half of survey response options.
+We observed a credible difference between the average value of this intercept for the two groups ($\Delta \text{intercept} = -0.67, 95\% \ \text{HDI} = [-0.78, -0.55]$), such that C/IE participants were biased towards using the right-half of survey response options.
 This translates to a tendency to endorse \emph{more severe} symptoms on the 7-up/7-down and GAD-7 scales (where the rightmost options indicate greater frequency of symptoms) but \emph{less extreme} symptoms or personality traits on the SHAPS and BIS (where the rightmost options indicate lower frequency of symptoms or personality traits) despite these inventories measuring strongly correlated constructs (i.e., depression and anhedonia, anxiety and behavioral inhibition).
@@
 As such, we evaluated the measures with respect to the top 10\% of ``suspect" participants flagged by each measure, corresponding roughly to the fraction of participants having performed at chance levels on the reversal-learning task.
-(Results of the same analysis repeated for the top 25\% of ``suspicious" participants --- corresponding roughly to the fraction of participants flagged by the infrequency-item measure --- produced similar results; see Table SXX.) Results were largely consistent with the correlation analysis: few pairs of task and self-report screening measures achieved levels of agreement greater than what would be expected by chance.
-The only significant cross-modality pair identified --- between the infrequency item and choice accuracy measures --- has a similarly coefficient less than 0.4.
+(Results of the same analysis repeated for the top 25\% of ``suspicious" participants --- corresponding roughly to the fraction of participants flagged by the infrequency-item measure --- produced similar results; see Table S5.) Results were largely consistent with the correlation analysis: few pairs of task and self-report screening measures achieved levels of agreement greater than what would be expected by chance.
+The only significant cross-modality pair identified --- between the infrequency item and choice accuracy measures --- has a Dice similarity coefficient less than 0.4.
 In other words, when these two measures are used to identify the top 10\% of participants most strongly suspected of C/IE responding, they agree on only two out of every five participants.
@@
 When no rejections based on C/IE responding was applied (i.e., all participants were included in the analysis; Figure \ref{fig:fig03}A), many significant correlations emerged between measures of task behavior and symptom scores, in particular for 4 of the self-report instruments (7-up, which measures symptoms of hypomania; 7-down, which measures symptoms of depression; GAD-7, which measures generalized anxiety symptoms; and BIS, which measures tendencies related to behavioral inhibition).
-Consistent with our predictions, the majority of these correlations involved symptom measures with asymmetric total score distributions.
+Consistent with our predictions, the majority of these correlations involved symptom measures with asymmetric score distributions.
 Attending to only the most skewed measures (i.e., 7-up, 7-down, GAD-7), symptom endorsement was correlated with almost every behavioral measure.
@@
 This pattern of correlations was largely similar when rejections were applied based on both task and self-report screening measures (Figure \ref{fig:fig03}D).
-We also note that with stricter screening, the remaining significant correlations were, for the most part (but not always), weaker.
+We also note that with stricter screening, the remaining significant correlations were, for the mostly but not always, weaker (Tables S6--S9).
 
@@
 For instance, consider the 7-down scale, a measure of trait depression: had we not screened participants based on infrequency items, we would have erroneously concluded that there were many significant associations between reversal-learning task performance and self-reported depression.
-Screening on self-report data allowed us to identify that each of these depression-behavior correlations was likely to be entirely spurious.
+Screening on self-report data allowed us to identify that each of these depression-behavior correlations was likely to be spurious.
 
@@
 To test this alternative hypothesis, we performed the same correlation analysis after removing random subsets of participants, fixing the sample size to that obtained after excluding C/IE respondents.
-In this case, the pattern of significant correlations was more similar to that before screening than after screening using the infrequency measure (two-tailed, paired-samples $t$-test: $t = 262.490$, $p < 0.001$, $d = 3.713$, 95\% CI = [0.136, 0.138]; Figure S2, compare to Figure \ref{fig:fig03}A).
+In this case, the pattern of significant correlations was more similar to that before screening than after screening using the infrequency measure (two-tailed, paired-samples $t$-test: $t(4999) = 262.490$, $p < 0.001$, $d = 3.713$, 95\% CI = [0.136, 0.138]; Figure S2, compare to Figure \ref{fig:fig03}A).
 Thus, the reduction in significant correlations following screening was unlikely to be driven solely by a reduction in statistical power.
@@
 In the replication sample, 55 out of 393 participants (14\%) endorsed a logically invalid or improbable response on one or more of the infrequency items when completing the self-report measures.
-This is roughly two-thirds of the number of participants who were flagged for C/IE responding in the original study, suggesting that the newer quality assurance protocols used by the online platforms are at least partially effective.
-
-In the self-report symptom measures, we replicated the finding that total scores were noticeably exaggerated in participants suspected of C/IE responding, but only for symptom measures where overall rates of symptom endorsement were the lowest.
-Similarly, we again found that task-based screening and self-report screening measures showed low correspondence; that is, excluding participants on the basis of poor behavioral performance would not have identified and removed participants who engaged in C/IE responding on self-report surveys.
-
-Finally, when we did not apply any exclusions, we observed spurious correlations between performance on the two-step task and total scores for both symptom and personality self-report measures with a mean-shift in scores between attentive participants and participants suspected of C/IE responding.
-In contrast with our original findings, however, we found that excluding participants based on self-report \textit{or} task screening measures was sufficient to ablate these spurious correlations.
+This is roughly two-thirds of the fraction of participants who were flagged for C/IE responding in the original study, suggesting that the newer quality assurance protocols used by the online platforms are at least partially effective.
+
+In the self-report symptom measures, we replicated the finding that total scores were noticeably exaggerated in participants suspected of C/IE responding, but only for symptom measures where overall rates of symptom endorsement were the lowest (Figure S7; Table S11).
+Similarly, we again found that task-based screening and self-report screening measures showed low correspondence (Figure S8; Tables S12--S13); that is, excluding participants on the basis of poor behavioral performance would not have identified and removed participants who engaged in C/IE responding on self-report surveys.
+
+Finally, when we did not apply any exclusions, we observed spurious correlations between performance on the two-step task and total scores for both symptom and personality self-report measures with a mean-shift in scores between attentive participants and participants suspected of C/IE responding (Figure S9).
+In contrast with our original findings, however, we found that excluding participants based on self-report \textit{or} task screening measures was sufficient to abolish these spurious correlations.
 
@@
 To explore this possibility, we embedded attention checks into the self-report measures of two studies of patients with major depressive disorder (see Appendix C for details).
-Specifically, N=45 psychiatric patients (confirmed to meet criteria for a diagnosis of major depressive disorder through a structured clinical interview) and N=20 healthy controls, all recruited through the Rutgers-Princeton Center for Computational Cognitive Neuropsychiatry (i.e., not on online labor platforms), completed a series of self-report symptom measures, online, on their computers from the comfort of their homes.
+Specifically, N=35 psychiatric patients (confirmed to meet criteria for a diagnosis of major depressive disorder through a structured clinical interview) across 45 unique testing sessions and N=17 healthy controls across 20 unique testing sessions, all recruited through the Rutgers-Princeton Center for Computational Cognitive Neuropsychiatry (i.e., not via online labor platforms), completed a series of self-report symptom measures, online, on their computers from the comfort of their homes.
 In total, 16 of 65 (24.6\%) participants failed one or more attention checks.
@@
 These data suggest, therefore, that it is unlikely that individuals with high psychiatric symptom severity were disproportionately flagged for C/IE responding in the main analyses.
-Accordingly, we conclude that the screening measures we are suggesting are not likely to result in overcontrol bias and false-negative correlations between tasks and symptom measures.
+Accordingly, we tentatively conclude that the screening measures we are suggesting are not likely to result in overcontrol bias and false-negative correlations between tasks and symptom measures.
 
@@
 
-In this manuscript, we highlighted a particular set of circumstances, common in computational psychiatry research done on large online samples, in which spurious correlations may arise between task behavior and self-reported symptomology.
+In this study, we highlighted a particular set of circumstances, common in computational psychiatry research done on large online samples, in which spurious correlations may arise between task behavior and self-reported symptomology.
 When the ground-truth prevalence of a symptom is low in the general population, participants who respond carelessly on measures assessing this symptom may erroneously appear as symptomatic.
-A less careful pattern of responding on tasks used to measure cognitive constructs can then masquerade as a correlation between alteration in these constructs and symptom dimensions.
-We found repeated evidence for this pernicious pattern in participants recruited from two popular online labor platforms.
+Careless responding on tasks used to measure cognitive constructs can then masquerade as a correlation between individual differences in these constructs and symptom dimensions.
+We found repeated evidence for this pernicious pattern in two samples of participants recruited from two popular online labor platforms.
 False-positive rates for these spurious correlations \emph{increased} with sample size, because the correlations are due to measurement bias, not measurement noise.
-Importantly, we found that screening on task behavior alone was insufficient to identify participants engaging in C/IE responding and prevent some false-positive correlations.
+Importantly, we found that screening on task behavior alone was often insufficient to identify participants engaging in C/IE responding and prevent the false-positive correlations.
 Unfortunately, a literature review identified this type of screening as the most common practice in online computational psychiatry studies.
@@
 Moreover, different measures of C/IE responding were weakly or not at all correlated between task behavior and self-report responses.
-This suggests the motivation for effortful responding was greater in the behavioral task, though precisely why is unclear.
-One possibility is that we gave participants a monetary incentive for attentive responding only during the task (a common practice, according to our literature review).
+This suggests the motivation for effortful responding was greater in the behavioral tasks, though precisely why is unclear.
+One possibility is that we gave participants a monetary incentive for attentive responding only during the tasks (a common practice, according to our literature review).
 A second possibility is that participants expected fewer consequences for C/IE responding during the self-report surveys, a reasonable assumption in light of how infrequently previous experiments have screened self-report data.
-Alternatively, participants may have found the gamified behavioral task more engaging or the self-report inventory more tedious.
+Alternatively, participants may have found the gamified behavioral tasks more engaging or the self-report inventory more tedious.
 Regardless of the reason, this discrepancy reinforces our observations concerning the inadequacy of behavioral-task screening as a stand-alone method for identifying C/IE responding.
@@
 Indeed, there are more ways to respond carelessly than to respond attentively to a task or self-report inventory (e.g., random response selection, straight-lining, zig-zagging, acquiescence bias) \cite{curran2016methods}.
-The specific response strategy a participant adopts is likely to reflect the idiosyncratic integration of multiple perceived benefits (e.g., time saved, effort avoided) and costs (e.g., loss of performance bonuses, risk of detection and pay forfeited).
+The specific response strategy a participant adopts is likely to reflect the idiosyncratic integration of multiple perceived benefits (e.g., time saved, effort avoided) and costs (e.g., loss of performance bonuses, risk of detection and forfeited pay).
 As has been previously documented \cite{desimone2018dirty}, the presence of multiple response strategies makes it clear why certain screening measures are more or less likely to correlate.
@@
 As computational psychiatry studies move towards larger samples to characterize heterogeneity in symptoms (and to increase statistical power), it will be important to understand how sample size may exaggerate the effects of systematic error.
-It will also be important to understand how this is moderated by overall C/IE responding rates, which we observed to vary across platforms and time, and will presumably continue to change with evolving labor platform and researcher screening practices.
-
-We conclude with a list of concrete recommendations for future research online studies involving correlations between task behavior and self-report surveys.
+It will also be important to understand how this is moderated by overall C/IE responding rates, which we observed to vary across platforms and time, and which will presumably continue to evolve with changing labor platform and researcher screening practices.
+
+We conclude with a list of concrete recommendations for future online studies involving correlations between task behavior and self-report instruments.
+We note that these recommendations are not limited to computational psychiatry studies, but are applicable to any online individual-differences cognitive science research involving similar methods (e.g., behavioral economics, psycholinguistics).
 Moving forward, we would strongly recommend that experimenters employ some form of self-report screening method, preferably one recommended by the best-practices literature (e.g., \cite{huang2015insufficient, curran2016methods, thomas2017validity, desimone2018dirty, ophir2020turker}).
@@
 When collecting self-report questionnaire data, we encourage experimenters to use screening methods sensitive to multiple distinct patterns of C/IE responding (e.g., random responding, straight-lining, side bias) and, if possible, to log all page interactions (e.g., mouse clicks, keyboard presses).
-We specifically recommend experimenters follow best-practice guidelines and use infrequency-item attention checks rather than instructed-item checks, as multiple studies have now shown that online participants are habituated to and circumvent the latter \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}.
+We specifically recommend experimenters follow best-practice guidelines and use infrequency-item attention checks rather than instructed-item checks, as multiple studies have now shown that online participants are habituated to and circumvent the latter (e.g., \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}; Appendix B).
 Participants flagged by suspicious responses on attention-check items should either be excluded from further analysis, or assessed using sensitivity analyses to ensure that observed full-sample correlations are robust to their exclusion.
@@
 
-More broadly, we encourage experimenters in individual-differences cognitive science research (including computational psychiatry) to be mindful of the myriad reasons why participants may perform worse on a behavioral task.
-Wherever possible, researchers are encouraged to design experiments where the signature of some psychiatric phenomenon could not also be explained by C/IE responding (e.g., \cite{eldar2015interaction, hunter2019excessive}).
+More broadly, we encourage experimenters in computational psychiatry to be mindful of the myriad reasons why participants may perform worse on a behavioral task.
+Wherever possible, researchers are encouraged to design experiments where the signature of some psychiatric syndrome could not also be explained by C/IE responding (e.g., \cite{eldar2015interaction, hunter2022increased}).
 Experimenters should also carefully consider whether an online study is truly appropriate for the research question.
@@
 Participants were instructed to earn the most points possible by learning (through trial-and-error) and choosing the best choice option.
-Participants were also instructed that the best option could change during the task, but were not informed about how often or when this would occur (see the Appendix A -- \textit{Task Instructions} for the complete instructions).
+Participants were also instructed that the best option could change during the task, but were not informed about how often or when this would occur (see Appendix A for the complete instructions).
 Prior to beginning the experiment, participants had to correctly answer four comprehension questions about the instructions.
@@
 
-\textbf{Samuel Zorowitz:} Conceptualization (equal); Software development (lead); Formal analysis (lead); Writing - Original Draft (lead); Writing - Review \& Editing (supporting); Visualization (lead).
-\textbf{Johanne Solis:} Software development (supporting); Writing - Review \& Editing (supporting).
+\textbf{Samuel Zorowitz:} Conceptualization (equal); Software development (lead); Data collection - online (lead); Formal analysis (lead); Writing - Original Draft (lead); Writing - Review \& Editing (supporting); Visualization (lead).
+\textbf{Johanne Solis:} Software development (supporting); Data collection - clinical (lead); Writing - Review \& Editing (supporting).
 \textbf{Yael Niv:} Writing - Review \& Editing (equal); Funding acquisition.
-\textbf{Daniel Bennett:} Conceptualization (equal); Software development (supporting); Formal analysis (supporting); Writing - Review \& Editing (equal); Visualization (supporting).
+\textbf{Daniel Bennett:} Conceptualization (equal); Software development (supporting); Data collection - online (supporting); Formal analysis (supporting); Writing - Review \& Editing (equal); Visualization (supporting).
 
@@
     \end{tabular}
-    \captionsetup{width=0.88\textwidth}
     \caption{The prevalence and types of task and self-report data screening practices in a sample (N=49) of recent online behavioral studies.}
@@
     \setlength{\tabcolsep}{6pt}
-    \begin{tabular}{lcccccccc}
+    \begin{tabular}{rcccrrcccc}
         \toprule
-        & & \multicolumn{3}{c}{Total Score} & \multicolumn{2}{c}{Cronbach's $\alpha$} & \multicolumn{2}{c}{\% Clinical Cutoff} \\
-        \cmidrule(lr){3-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
-         Subscale & Skew & Attentive & C/IE & \textit{t}-value & Attentive & C/IE & Before & After \\
+        & & \multicolumn{4}{c}{Total Score} & \multicolumn{2}{c}{Cronbach's $\alpha$} & \multicolumn{2}{c}{\% Clinical Cutoff} \\
+        \cmidrule(lr){3-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}
+         Subscale & Skew & Attentive & C/IE & \textit{t}-value & \textit{p}-value & Attentive & C/IE & Before & After \\
         \midrule
-        7-up   &  0.81 &    3.87 &   10.15 &  $-13.31^*$ &    0.84 &    0.84 &     13.0\% &       4.0\% \\
-        7-down &  0.76 &    4.75 &   10.68 &   $-9.99^*$ &    0.94 &    0.88 &     17.4\% &       9.3\% \\
-        GAD-7  &  0.75 &    4.86 &    9.73 &   $-7.88^*$ &    0.92 &    0.87 &     25.9\% &      17.3\% \\
-        BIS    &  0.78 &    7.74 &    7.92 &   -0.54 &    0.83 &    0.62 &        - &             - \\
-        BAS    &  0.17 &   15.73 &   16.16 &   -0.91 &    0.84 &    0.71 &        - &             - \\
-        SHAPS  &  0.26 &    8.02 &   10.85 &   $-4.04^*$ &    0.90 &    0.81 &     17.9\% &      14.6\% \\
-        PSWQ   &  0.19 &    4.78 &    6.74 &   $-4.78^*$ &    0.93 &    0.81 &      7.3\% &       7.0\% \\
+        7-up   &  0.806 &     3.9 &    10.2 &  -13.312 &   $<$0.001 &    0.84 &    0.84 &     13.0\% &      4.0\% \\
+        7-down &  0.759 &     4.8 &    10.7 &   -9.987 &   $<$0.001 &    0.94 &    0.88 &     17.4\% &      9.3\% \\
+        GAD-7  &  0.753 &     4.9 &     9.7 &   -7.881 &   $<$0.001 &    0.92 &    0.87 &     25.9\% &     17.3\% \\
+        BIS    &  0.780 &     7.7 &     7.9 &   -0.542 &   0.612 &    0.83 &    0.62 &        - &        - \\
+        BAS    &  0.171 &    15.7 &    16.2 &   -0.912 &   0.357 &    0.84 &    0.71 &        - &        - \\
+        SHAPS  &  0.256 &     8.0 &    10.8 &   -4.043 &   $<$0.001 &    0.90 &    0.81 &     17.9\% &     14.6\% \\
+        PSWQ   &  0.193 &     4.8 &     6.7 &   -4.784 &   $<$0.001 &    0.93 &    0.81 &      7.3\% &      7.0\% \\
         \bottomrule
     \end{tabular}
-    \captionsetup{width=0.88\textwidth}
     \caption{Descriptive statistics of the self-report symptom measures between attentive and C/IE participants.
@@
 Total score: the average symptom score across attentive and C/IE participants.
-Stars indicate statistical significance at $p<0.05$.
+Scores were compared using a two-sample $t$-test ($df = 384$, $\alpha = 0.05$, two-tailed, not corrected for multiple comparisons).
 Cronbach's $\alpha$: a measure of response consistency, where values closer to 1 indicate greater consistency in responses.
 \% Clinical Cutoff: the percentage of participants reaching threshold for clinical symptomology before and after screening based on the infrequency measure.
-(The BIS/BAS scales do not have clinical thresholds.)}
+The BIS/BAS scales do not have clinical thresholds.}
     \label{tab:tab02}
@@
     \centering
-    \captionsetup{width=0.88\textwidth}
     \caption{Simulated example of how spurious behavior-symptom correlations can arise when symptom endorsement is rare.
-\textit{Left:} When symptoms are moderately common in the general population, C/IE respondents ($N=15$; blue) are indistinguishable from attentive participants ($N=85$; red) in self-report measures (x-axis, marginal distribution shown on top).
+\textit{Left:} When symptoms are moderately common in the general population, C/IE respondents (blue) are indistinguishable from attentive participants (red) in self-report measures (x-axis, marginal distribution shown on top).
 Despite the worse task performance of C/IE respondents (y-axis), no correlation arises between symptom scores and task performance (dots are participants drawn from the shown distributions, with 15\% C/IE participants; dashed line shows the (lack of) Spearman rank correlation.) \textit{Right:} When symptoms are rare in the general population, careless respondents appear symptomatic in self-report measures.
-As a result, self-report symptom scores show a significant two-sided Spearman rank correlation with task performance.
-}
+As a result, self-report symptom scores show a significant Spearman rank correlation (two-sided) with task performance.}
     \label{fig:simulation}
@@
     \centering
-    \captionsetup{width=0.88\textwidth}
     \caption{Raincloud plots of total symptom scores in attentive ($N=301$; red) and C/IE ($N=85$; blue) participants.
@@
 Black circles: average score within each group (error bars denote 95\% bootstrap confidence interval).
-Shaded plots: estimated distribution of responses for each group of participants.
-The scales are ordered approximately according to their estimated skew (see Table 2) from top-left (7-up) to bottom-right (PSWQ).
-The average level of symptom endorsement is most markedly different between groups in measures with lowest overall rates of endorsement.}
+Shaded plots: distribution of scores for each group of participants.
+The scales are ordered approximately according to their estimated skew (see Table \ref{tab:tab02}) from top-left (7-up) to bottom-right (PSWQ).
+The average level of symptom endorsement is most markedly different between groups in symptom measures with the lowest overall rates of endorsement.}
     \label{fig:fig01}
@@
     \centering
-    \captionsetup{width=0.88\textwidth}
     \caption{Similarity of task and self-report data screening measures.
-Each tile corresponds to the Spearman rank correlation (left) and Dice similarity coefficient (right) between two screening measures across $N=386$ participants.
-Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times.
-Similarity scores have been thresholded after correcting for multiple comparisons.
-Numbers denote the strength of statistically significant correlations.
-Cross-modality correlations between task-behavior (left) and infrequency-item self-report measures (bottom) are in the dashed rectangle.}
+Each tile corresponds to the Spearman rank correlation (left) and Dice similarity coefficient (right) between two screening measures across participants ($N=386$).
+Similarity indices are thresholded such that only the magnitude of statistically-significant associations (permutation test, $p<0.05$, two-sided, corrected for multiple comparisons) are shown.
+(Unthresholded values are presented in Tables S3--S5.) Cross-modality correlations between task (y-axis) and self-report screening measures (x-axis) are in the dashed rectangle.
+Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times.}
     \label{fig:fig02}
@@
     \centering
-    \captionsetup{width=0.88\textwidth}
     \caption{Absolute Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions.
@@
 (D) Both Types = exclusions based on the previous two measures ($N=283$).
-Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons; all signed correlations are shown in Figure S1).
-Black Xs indicate significant correlations ablated under screening.
+Only statistically significant correlations are shown ($p<0.05$, two-sided, not corrected for multiple comparisons; signed correlations are shown in Figure S1 and Tables S6--S9).
+Black Xs indicate significant correlations abolished under screening.
 Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
@@
     \centering
-    \captionsetup{width=0.88\textwidth}
     \caption{False positive rates for spurious correlations \emph{increase} with sample size.
-\textit{Left:} Spearman correlations and 95\% bootstrap confidence intervals between learning rate asymmetry ($\kappa$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants.
+\textit{Left:} Spearman rank correlations and 95\% bootstrap confidence intervals between learning rate asymmetry ($\kappa$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants.
 The thick dashed lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size.
@@
 \textit{Right:} False positive rates for learning rate asymmetry ($\kappa$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants.
-False positive rate was calculated as the proportion of bootstrap samples in which the correlation between $\kappa$ and 7-down was statistically significant.
-The horizontal dotted line denotes the expected false positive rate at $\alpha = .05$.}
+False positive rate was calculated as the proportion of bootstrap samples in which the Spearman rank correlation between $\kappa$ and 7-down was statistically significant ($p<0.05$, two-sided).
+The horizontal dotted line denotes the expected false positive rate at $\alpha = 0.05$.}
     \label{fig:fig04}

### 2023-04-10 manuscripts/supp.tex
checkpointing manuscript progress

@@
     \centering
-    \captionsetup{width=0.88\textwidth}
     \caption{Signed Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions.
@@
     \centering
-    \captionsetup{width=0.88\textwidth}
     \caption{The pattern of significant behavior-symptom correlations before (A; $N=386$) and after (B; $N=301$) screening compared to the resulting pattern when random subsets of participants ($N=301$, matched to screening using the infrequency measure) are removed (C).
@@
     \centering
-    \captionsetup{width=0.88\textwidth}
     \caption{False positive rates for spurious correlations \emph{increase} with sample size.
@@
     \centering
-    \captionsetup{width=0.88\textwidth}
     \caption{True correlations are independent of the proportion of C/IE participants in the sample.
@@
     \centering
-    \captionsetup{width=0.88\textwidth}
     \caption{Posterior predictive checks for the risk-sensitive temporal difference learning model.
@@
     \end{tabular}
-    \captionsetup{width=0.88\textwidth}
     \caption{The demographics of each sample by online labor market.
@@
     \end{tabular}
-    \captionsetup{width=0.88\textwidth}
     \caption{Measures of task behavior compared between attentive ($N=301$) and C/IE ($N=85$) participants.
-Metrics compared using two-tailed, two-sample permutation $t$-test with $df=384$ ($\alpha = 0.05$, not corrected for multiple comparisons).
+Metrics compared using two-tailed, two-sample permutation $t$-tests ($df=384$, $\alpha = 0.05$, not corrected for multiple comparisons).
 Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
@@
 This left a final sample of N=393 participants (MTurk: N=193, Prolific: N=200) for analysis.
-The demographics of the sample split by labor market is provided in Table \ref{tab:demographics_02}.
+The demographics of the sample split by labor market is provided in Table \ref{tab:S10}.
 Participants recruited from MTurk were older on average ($\Delta M = 4.9$ yrs; two-tailed, two-sample $t$-test: $t(391)=4.248$, $p<0.001$, $d = 0.429$, 95\% CI = [2.7, 7.2]) and comprised of fewer women (35.2\% versus 61\%; two-tailed, two-sample proportions test: $z(391)=5.500$, $p<0.001$, $h=0.562$, 95\% CI = [0.182, 0.372]).
@@
     \end{tabular}
-    \captionsetup{width=0.88\textwidth}
     \caption{The demographics of each sample by online labor market.}
-    \label{tab:demographics_02}
+    \label{tab:S10}
 \end{table}
@@
 This scale is expected to elicit lower rates of symptom endorsement, thereby resulting in asymmetric (right-skewed) score distributions.
-Participants also completed a 7-item measure of general anxiety symptoms over the last year (e.g., ``I was overwhelmed by anxiety.''; \cite{watson2022development}).
+Participants also completed an alternative 7-item measure of general anxiety symptoms over the last year (e.g., ``I was overwhelmed by anxiety.''; \cite{watson2022development}).
 This scale is expected to elicit moderate rates of symptom endorsement, thereby resulting in a symmetric score distribution.
@@
     \centering
-    \captionsetup{width=0.88\textwidth}
     \caption{Raincloud plots of total symptom scores in attentive ($N=338$; red) and C/IE ($N=55$; blue) participants.
@@
 Shaded plots: estimated distribution of responses for each group of participants.}
-    \label{fig:repl_distributions}
+    \label{fig:S07}
 \end{figure}
@@
 This result was (mostly) replicated in the current dataset.
-Total scores were noticeably exaggerated in participants suspected of C/IE responding for the symptom measures where overall rates of symptom endorsement were the lowest (e.g., mania; Figure \ref{fig:repl_distributions}, leftmost plot).
-Where there were higher rates of symptom endorsement overall (e.g., anxiety), the distributions of symptom scores between the two groups of participants were more similar (Figure \ref{fig:repl_distributions}, middle plots).
-Permutation testing confirmed that observed mean-shifts in symptom scores for C/IE participants were statistically significant for the most skewed symptom measures (Table \ref{tab:rep_validation}).
-
-For the personality measures, however, an interesting pattern emerged (Figure \ref{fig:repl_distributions}, rightmost plots).
+Total scores were noticeably exaggerated in participants suspected of C/IE responding for the symptom measures where overall rates of symptom endorsement were the lowest (e.g., mania; Figure \ref{fig:S07}, leftmost plot).
+Where there were higher rates of symptom endorsement overall (e.g., anxiety), the distributions of symptom scores between the two groups of participants were more similar (Figure \ref{fig:S07}, middle plots).
+Permutation testing confirmed that observed mean-shifts in symptom scores for C/IE participants were statistically significant for the most skewed symptom measures (Table \ref{tab:S11}).
+
+For the personality measures, however, an interesting pattern emerged (Figure \ref{fig:S07}, rightmost plots).
 We did not observe a statistically significant mean-shift in total scores for the subscale with the most skewed score distribution (i.e., artistic interests).
@@
 Scores compared using two-tailed, two-sample permutation $t$-test with $df=391$ ($\alpha = 0.05$, not corrected for multiple comparisons).}
-    \label{tab:rep_validation}
+    \label{tab:S11}
 \end{table}
@@
 To measure the degree of correspondence between these behavioral and self-report screening measures, we performed two complementary analyses.
-First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation (Figure \ref{fig:repl_correspondence}, left panel).
+First, we computed pairwise correlations on the unthresholded (continuous) measures using Spearman's rank correlation (Figure \ref{fig:S08}, left panel).
 After correcting for multiple comparisons, there were a handful of significant correlations between the behavioral and self-report screening measures.
@@
     \centering
-    \captionsetup{width=0.88\textwidth}
     \caption{Similarity of task and self-report data screening measures.
@@
 Cross-modality correlations between task-behavior (left) and infrequency-item self-report measures (bottom) are in the dashed rectangle.}
-    \label{fig:repl_correspondence}
+    \label{fig:S08}
 \end{figure}
 
-Second, we used the Dice similarity coefficient to quantify agreement between different screening methods in the set of participants flagged for exclusion (Figure \ref{fig:repl_correspondence}, right panel).
+Second, we used the Dice similarity coefficient to quantify agreement between different screening methods in the set of participants flagged for exclusion (Figure \ref{fig:S08}, right panel).
 This approach quantifies the degree of overlap between the set of would-be excluded participants based on different screening measures under a common exclusion rate.
@@
 To understand the effects of applying different forms of screening, we estimated the correlations between each unique pairing of a self-report measure and measure of behavior under four different conditions: no screening, screening only on task behavior (i.e., removing participants whose win-stay lose-shift behavior was not above chance), screening only on self-report responses (i.e., removing only participants who responded incorrectly on one or more infrequency items), or both.
-The resulting pairwise behavior-symptom correlations following each screening procedure are presented in Figure \ref{fig:repl_correlations}.
+The resulting pairwise behavior-symptom correlations following each screening procedure are presented in Figure \ref{fig:S09}.
 We note that we did not correct these correlation analyses for multiple comparisons, since our purpose was to demonstrate the extent of this issue across multiple behavioral measures and self-report symptoms.
@@
 
-When no rejections were applied (i.e., all participants were included; Figure \ref{fig:repl_correlations}A), we observed multiple significant correlations between measures of task behavior and symptom scores for hypomania and depression.
+When no rejections were applied (i.e., all participants were included; Figure \ref{fig:S09}A), we observed multiple significant correlations between measures of task behavior and symptom scores for hypomania and depression.
 Consistent with our predictions, these correlations involved measures with low overall endorsement rates and mean-shifts in score distributions between attentive and C/IE participants.
@@
 
-Next, we excluded participants from the analysis based on task-behavior screening (i.e., lack of win-stay lose-shift behavior, removing the 8\% of participants exhibiting behavior indistinguishable from chance; Figure \ref{fig:repl_correlations}B).
+Next, we excluded participants from the analysis based on task-behavior screening (i.e., lack of win-stay lose-shift behavior, removing the 8\% of participants exhibiting behavior indistinguishable from chance; Figure \ref{fig:S09}B).
 In contrast to the findings of the original study, the pattern of correlations was meaningfully changed: the putatively spurious correlations between greed avoidance and performance on the two-step task were ablated.
 Two previously significant correlations between hypomania and two-step performance were also rendered non-significant.
-A similar pattern of results was observed when we rejected participants based on self-report screening (removing 14\% of participants who endorsed one or more invalid or improbable responses on the infrequency items; Figure \ref{fig:repl_correlations}C) and when rejections were applied based on both task and self-report screening measures (removing 18\% of participants; Figure \ref{fig:repl_correlations}D).
+A similar pattern of results was observed when we rejected participants based on self-report screening (removing 14\% of participants who endorsed one or more invalid or improbable responses on the infrequency items; Figure \ref{fig:S09}C) and when rejections were applied based on both task and self-report screening measures (removing 18\% of participants; Figure \ref{fig:S09}D).
 
@@
 Acronyms: PrevRew = sensitivity to reward on the previous trial; PrevTrans = sensitivity to transition type on previous trial; MB/MF = index of model-based/model-free behavior (interaction between \textit{PrevRew} \& \textit{PrevTrans}).}
-    \label{fig:repl_correlations}
+    \label{fig:S09}
 \end{figure}
@@
 \break
+\subsection*{Correspondence of screening measures}
+
+The following are the unthresholded results of the screening measure correspondence analyses.
+
+\begin{table}[H]
+    \centering
+    \begin{adjustbox}{center}
+    \tiny
+    \begin{tabular}{rccccccccc}
+        \toprule
+        {} & INF &      ISD &      REL &     MAH &     READ &       SV &       CV &     WSLS & RT \\
+        \midrule
+        INF  &                           - &                             &                             &                            &                          &                            &                             &                             &    \\
+        ISD  &      \textbf{0.164 (0.043)} &                           - &                             &                            &                          &                            &                             &                             &    \\
+        REL  &              -0.119 (0.490) &  \textbf{-0.842 ($<$0.001)} &                           - &                            &                          &                            &                             &                             &    \\
+        MAH  &   \textbf{0.303 ($<$0.001)} &   \textbf{0.750 ($<$0.001)} &  \textbf{-0.596 ($<$0.001)} &                          - &                          &                            &                             &                             &    \\
+        READ &     \textbf{-0.206 (0.001)} &               0.099 (0.843) &              -0.065 (1.000) &              0.059 (1.000) &                        - &                            &                             &                             &    \\
+        SV   &               0.138 (0.214) &               0.026 (1.000) &              -0.014 (1.000) &              0.071 (0.997) &           -0.028 (1.000) &                          - &                             &                             &    \\
+        CV   &              -0.119 (0.494) &              -0.007 (1.000) &              -0.002 (1.000) &             -0.063 (1.000) &   \textbf{0.179 (0.013)} &             -0.116 (0.560) &                           - &                             &    \\
+        WSLS &  \textbf{-0.260 ($<$0.001)} &              -0.064 (1.000) &               0.043 (1.000) &             -0.128 (0.348) &            0.061 (1.000) &    \textbf{-0.168 (0.029)} &               0.003 (1.000) &                           - &    \\
+        RT   &   \textbf{0.338 ($<$0.001)} &               0.127 (0.357) &              -0.102 (0.792) &  \textbf{0.274 ($<$0.001)} &  \textbf{-0.180 (0.012)} &  \textbf{0.306 ($<$0.001)} &  \textbf{-0.233 ($<$0.001)} &  \textbf{-0.351 ($<$0.001)} &  - \\
+        \bottomrule
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Spearman rank correlations ($p$-value) of task and self-report data screening measures ($N=393$).
+Each entry corresponds to the Spearman correlation between two screening measures.
+Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; SV = side variability; CV = choice variability; WSLS = win-stay lose-shift rate; RT = suspicious response times.
+Bolded entries indicate statistical significance for a two-sided rank correlation test ($\alpha = 0.05$, corrected for multiple comparisons).}
+\end{table}
+
+\begin{table}[H]
+    \centering
+    \begin{adjustbox}{center}
+    \tiny
+    \begin{tabular}{rccccccccc}
+        \toprule
+        {} & INF &      ISD &      REL &     MAH &     READ &       SV &       CV &     WSLS & RT \\
+        \midrule
+        INF  &                          - &                            &                &                         &                            &                &                &                            &    \\
+        ISD  &              0.168 (0.988) &                          - &                &                         &                            &                &                &                            &    \\
+        REL  &              0.168 (0.988) &  \textbf{0.450 ($<$0.001)} &              - &                         &                            &                &                &                            &    \\
+        MAH  &  \textbf{0.358 ($<$0.001)} &  \textbf{0.550 ($<$0.001)} &  0.250 (0.122) &                       - &                            &                &                &                            &    \\
+        READ &  \textbf{0.379 ($<$0.001)} &              0.100 (1.000) &  0.125 (1.000) &           0.150 (1.000) &                          - &                &                &                            &    \\
+        SV   &              0.211 (0.467) &              0.100 (1.000) &  0.125 (1.000) &           0.200 (0.728) &              0.175 (0.969) &              - &                &                            &    \\
+        CV   &              0.043 (1.000) &              0.076 (1.000) &  0.051 (1.000) &           0.025 (1.000) &              0.025 (1.000) &  0.000 (1.000) &              - &                            &    \\
+        WSLS &  \textbf{0.400 ($<$0.001)} &              0.175 (0.969) &  0.075 (1.000) &  \textbf{0.300 (0.007)} &     \textbf{0.300 (0.007)} &  0.100 (1.000) &  0.101 (1.000) &                          - &    \\
+        RT   &  \textbf{0.400 ($<$0.001)} &              0.150 (1.000) &  0.150 (1.000) &  \textbf{0.300 (0.007)} &  \textbf{0.375 ($<$0.001)} &  0.225 (0.358) &  0.000 (1.000) &  \textbf{0.450 ($<$0.001)} &  - \\
+        \bottomrule
+    \end{tabular}
+    \end{adjustbox}
+    \caption{Dice similarity coefficients ($p$-value) for task and self-report data screening measures for the top 10\% most suspicious participants.
+Each entry corresponds to the Dice coefficient between two screening measures for the 10\% most suspicious participants.
+Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; SV = side variability; CV = choice variability; WSLS = win-stay lose-shift rate; RT = suspicious response times.
+Bolded entries indicate statistical significance for a two-sided Dice similarity permutation test ($\alpha = 0.05$, corrected for multiple comparisons).}
+\end{table}
+
+\break
 \subsection*{Correlations between behavior and symptom measures}
@@
 
-52 unique participants were recruited to participate in a behavioral experiment.
+52 participants were recruited to participate in a behavioral experiment.
 Of these, 14 participated in both studies.

### 2023-04-27 manuscripts/letter.tex
reupload

@@
 \usepackage[flushleft]{threeparttable}
+\usepackage{array}
 \usepackage[font=small, labelfont=it]{caption}
+\usepackage{booktabs}
+\usepackage{soul}
 \usepackage{csquotes}
-\usepackage{soul}
-
-% specify footnote margins
-\renewcommand\footnotelayout{%
-  \advance\leftskip 0.7cm
-  \advance\rightskip 0.7cm
- }
-
-% specific images path relative to the main .tex file 
-\graphicspath{ {./figures/} }
-
-% setup references
-\addbibresource{letter.bib}
-\renewcommand*{\bibfont}{\small}
 
@@
 }
+
+% specify images path relative to the main .tex file 
+\graphicspath{ {./figures/} }
+
+% ----------------------------------%
+% Define references
+% ----------------------------------%
+
+% setup references
+\renewcommand*{\bibfont}{\small}
+
+% define references
+\begin{filecontents}{letter.bib}
+@INCOLLECTION{Demetriou2015-bq,
+  title     = "{Self-Report} Questionnaires",
+  booktitle = "The Encyclopedia of Clinical Psychology",
+  author    = "Demetriou, Constantina and Ozer, Bilge Uzun and Essau, Cecilia A",
+  pages     = "1--6",
+  month     =  jan,
+  year      =  2015
+}
+
+@article{eklund2016cluster,
+  title={Cluster failure: Why fMRI inferences for spatial extent have inflated false-positive rates},
+  author={Eklund, Anders and Nichols, Thomas E and Knutsson, Hans},
+  journal={Proceedings of the national academy of sciences},
+  volume={113},
+  number={28},
+  pages={7900--7905},
+  year={2016},
+  publisher={National Acad Sciences}
+}
+
+@article{bradley2021unrepresentative,
+  title={Unrepresentative big surveys significantly overestimated US vaccine uptake},
+  author={Bradley, Valerie C and Kuriwaki, Shiro and Isakov, Michael and Sejdinovic, Dino and Meng, Xiao-Li and Flaxman, Seth},
+  journal={Nature},
+  volume={600},
+  number={7890},
+  pages={695--700},
+  year={2021},
+  publisher={Nature Publishing Group}
+}
+
+@article{arias2020little,
+  title={A little garbage in, lots of garbage out: Assessing the impact of careless responding in personality survey data},
+  author={Arias, Victor B and Garrido, LE and Jenaro, C and Martinez-Molina, A and Arias, B},
+  journal={Behavior Research Methods},
+  pages={1--17},
+  year={2020},
+  publisher={Springer}
+}
+
+@article{chandler2020participant,
+  title={Participant carelessness and fraud: Consequences for clinical research and potential solutions.},
+  author={Chandler, Jesse and Sisso, Itay and Shapiro, Danielle},
+  journal={Journal of Abnormal Psychology},
+  volume={129},
+  number={1},
+  pages={49},
+  year={2020},
+  publisher={American Psychological Association}
+}
+
+@book{cohen2013statistical,
+  title={Statistical power analysis for the behavioral sciences},
+  author={Cohen, Jacob},
+  year={2013},
+  publisher={Routledge}
+}
+
+@article{meng2018statistical,
+  title={Statistical paradises and paradoxes in big data (I): Law of large populations, big data paradox, and the 2016 US presidential election.},
+  author={Meng, Xiao-Li},
+  journal={The Annals of Applied Statistics},
+  volume={12},
+  number={2},
+  pages={685--726},
+  year={2018},
+  publisher={JSTOR}
+}
+
+@MISC{prolific_ip_address,
+  title        = "Prolific {IDs}, data collection and security",
+  booktitle    = "Prolific",
+  howpublished = "\url{https://researcher-help.prolific.co/hc/en-gb/articles/360009377494-Prolific-IDs-data-collection-and-security}",
+  note         = "Accessed: 2022-11-9",
+  language     = "en"
+}
+
+@article{dennis2020online,
+  title={Online worker fraud and evolving threats to the integrity of MTurk data: A discussion of virtual private servers and the limitations of IP-based screening procedures},
+  author={Dennis, Sean A and Goodson, Brian M and Pearson, Christopher A},
+  journal={Behavioral Research in Accounting},
+  volume={32},
+  number={1},
+  pages={119--134},
+  year={2020},
+  publisher={American Accounting Association}
+}
+
+@MISC{prolific_ip_address_2,
+  title        = "How does Prolific prevent duplicate participant accounts?",
+  booktitle    = "Prolific",
+  howpublished = "\url{https://researcher-help.prolific.co/hc/en-gb/articles/360009092774-How-does-Prolific-prevent-duplicate-participant-accounts-}",
+  note         = "Accessed: 2022-11-9",
+  language     = "en"
+}
+
+@MISC{cloudresearch_ip_address,
+  title        = "Enhancing Data Quality",
+  howpublished = "\url{https://go.cloudresearch.com/en/knowledge/enhancing-data-quality}",
+  note         = "Accessed: 2022-11-9",
+  language     = "en"
+}
+
+@article{elwert2014endogenous,
+  title={Endogenous selection bias: The problem of conditioning on a collider variable},
+  author={Elwert, Felix and Winship, Christopher},
+  journal={Annual review of sociology},
+  volume={40},
+  pages={31--53},
+  year={2014},
+  publisher={Annual Reviews}
+}
+
+@article{wysocki2022statistical,
+  title={Statistical control requires causal justification},
+  author={Wysocki, Anna C and Lawson, Katherine M and Rhemtulla, Mijke},
+  journal={Advances in Methods and Practices in Psychological Science},
+  volume={5},
+  number={2},
+  pages={25152459221095823},
+  year={2022},
+  publisher={SAGE Publications Sage CA: Los Angeles, CA}
+}
+
+@article{desimone2018differential,
+  title={The differential impacts of two forms of insufficient effort responding},
+  author={DeSimone, Justin A and DeSimone, Alice J and Harms, PD and Wood, Dustin},
+  journal={Applied Psychology},
+  volume={67},
+  number={2},
+  pages={309--338},
+  year={2018},
+  publisher={Wiley Online Library}
+}
+
+@article{robinson2019tapped,
+  title={Tapped out or barely tapped? Recommendations for how to harness the vast and largely unused potential of the Mechanical Turk participant pool},
+  author={Robinson, Jonathan and Rosenzweig, Cheskie and Moss, Aaron J and Litman, Leib},
+  journal={PloS one},
+  volume={14},
+  number={12},
+  pages={e0226394},
+  year={2019},
+  publisher={Public Library of Science San Francisco, CA USA}
+}
+
+@ARTICLE{Kim2018-ev,
+  title    = "Detecting random responders with infrequency scales using an
+              error-balancing threshold",
+  author   = "Kim, Dale S and McCabe, Connor J and Yamasaki, Brianna L and
+              Louie, Kristine A and King, Kevin M",
+  journal  = "Behav. Res. Methods",
+  volume   =  50,
+  number   =  5,
+  pages    = "1960--1970",
+  month    =  oct,
+  year     =  2018,
+  keywords = "Careless responding; Data cleaning; Infrequency scales; Random
+              responding",
+  language = "en"
+}
+
+@article{curran2016methods,
+  title={Methods for the detection of carelessly invalid responses in survey data},
+  author={Curran, Paul G},
+  journal={Journal of Experimental Social Psychology},
+  volume={66},
+  pages={4--19},
+  year={2016},
+  publisher={Elsevier}
+}
+
+@article{murphy2013resting,
+  title={Resting-state fMRI confounds and cleanup},
+  author={Murphy, Kevin and Birn, Rasmus M and Bandettini, Peter A},
+  journal={Neuroimage},
+  volume={80},
+  pages={349--359},
+  year={2013},
+  publisher={Elsevier}
+}
+
+@article{fellner2016spurious,
+  title={Spurious correlations in simultaneous EEG-fMRI driven by in-scanner movement},
+  author={Fellner, Marie-Christin and Volberg, Gregor and Mullinger, Karen J and Goldhacker, Markus and Wimber, Maria and Greenlee, Mark W and Hanslmayr, Simon},
+  journal={Neuroimage},
+  volume={133},
+  pages={354--366},
+  year={2016},
+  publisher={Elsevier}
+}
+
+@article{sullivan2007spurious,
+  title={Spurious genetic associations},
+  author={Sullivan, Patrick F},
+  journal={Biological psychiatry},
+  volume={61},
+  number={10},
+  pages={1121--1126},
+  year={2007},
+  publisher={Elsevier}
+}
+
+@article{barends2019noncompliant,
+  title={Noncompliant responding: Comparing exclusion criteria in MTurk personality research to improve data quality},
+  author={Barends, Ard J and De Vries, Reinout E},
+  journal={Personality and individual differences},
+  volume={143},
+  pages={84--89},
+  year={2019},
+  publisher={Elsevier}
+}
+
+@article{chandler2019online,
+  title={Online panels in social science research: Expanding sampling methods beyond Mechanical Turk},
+  author={Chandler, Jesse and Rosenzweig, Cheskie and Moss, Aaron J and Robinson, Jonathan and Litman, Leib},
+  journal={Behavior research methods},
+  volume={51},
+  pages={2022--2038},
+  year={2019},
+  publisher={Springer}
+}
+
+@article{sulik2021delusion,
+  title={Delusion-like Beliefs and Data Quality: Are Classic Cognitive Biases Artefacts of Carelessness?},
+  author={Sulik, Justin and Ross, Robert M and Balzan, Ryan and McKay, Ryan},
+  year={2021},
+  publisher={PsyArXiv}
+}
+
+@article{hauser2016attentive, 
+  title={Attentive Turkers: MTurk participants perform better on online attention checks than do subject pool participants}, 
+  author={Hauser, David J and Schwarz, Norbert}, 
+  journal={Behavior research methods}, 
+  volume={48}, pages={400--407}, 
+  year={2016}, 
+  publisher={Springer} 
+}
+
+@MISC{Moss2018-vy,
+  title        = "After the Bot Scare: Understanding What's Been Happening With
+                  Data Collection on {MTurk} and How to Stop It",
+  booktitle    = "{CloudResearch}",
+  author       = "Moss, Aaron and Litman, Leib",
+  month        =  sep,
+  year         =  2018,
+  howpublished = "\url{https://www.cloudresearch.com/resources/blog/after-the-bot-scare-understanding-whats-been-happening-with-data-collection-on-mturk-and-how-to-stop-it/}",
+  note         = "Accessed: 2023-3-25"
+}
+
+@MISC{Charalambides2021-fd,
+  title        = "We recently went viral on {TikTok} - here's what we learned",
+  author       = "Charalambides, Nick",
+  month        =  aug,
+  year         =  2021,
+  howpublished = "\url{https://www.prolific.co/blog/we-recently-went-viral-on-tiktok-heres-what-we-learned}",
+  note         = "Accessed: 2023-3-25",
+  language     = "en"
+}
+
+@ARTICLE{Chandler2020-ja,
+  title    = "Participant carelessness and fraud: Consequences for clinical
+              research and potential solutions",
+  author   = "Chandler, Jesse and Sisso, Itay and Shapiro, Danielle",
+  journal  = "J. Abnorm. Psychol.",
+  volume   =  129,
+  number   =  1,
+  pages    = "49--55",
+  month    =  jan,
+  year     =  2020,
+  language = "en"
+}
+
+@ARTICLE{Barends2019-ud,
+  title     = "Noncompliant responding: Comparing exclusion criteria in {MTurk}
+               personality research to improve data quality",
+  author    = "Barends, Ard J and de Vries, Reinout E",
+  journal   = "Pers. Individ. Dif.",
+  publisher = "Elsevier",
+  volume    =  143,
+  pages     = "84--89",
+  month     =  jun,
+  year      =  2019
+}
+
+@article{eyal2021data,
+  title={Data quality of platforms and panels for online behavioral research},
+  author={Eyal, Peer and David, Rothschild and Andrew, Gordon and Zak, Evernden and Ekaterina, Damer},
+  journal={Behavior Research Methods},
+  pages={1--20},
+  year={2021},
+  publisher={Springer}
+}
+
+@article{decker2016creatures,
+  title={From creatures of habit to goal-directed learners: Tracking the developmental emergence of model-based reinforcement learning},
+  author={Decker, Johannes H and Otto, A Ross and Daw, Nathaniel D and Hartley, Catherine A},
+  journal={Psychological science},
+  volume={27},
+  number={6},
+  pages={848--858},
+  year={2016},
+  publisher={Sage Publications Sage CA: Los Angeles, CA}
+}
+
+@article{nussenbaum2020moving,
+  title={Moving developmental research online: comparing in-lab and web-based studies of model-based reinforcement learning},
+  author={Nussenbaum, Kate and Scheuplein, Maximilian and Phaneuf, Camille V and Evans, Michael D and Hartley, Catherine A},
+  journal={Collabra: Psychology},
+  volume={6},
+  number={1},
+  year={2020},
+  publisher={University of California Press}
+}
+
+@article{gelman2006difference,
+  title={The difference between “significant” and “not significant” is not itself statistically significant},
+  author={Gelman, Andrew and Stern, Hal},
+  journal={The American Statistician},
+  volume={60},
+  number={4},
+  pages={328--331},
+  year={2006},
+  publisher={Taylor \& Francis}
+}
+\end{filecontents}
+\addbibresource{letter.bib}
+
+% ----------------------------------%
+% Define author / abstract block
+% ----------------------------------%
 
@@
 \setlength{\parskip}{1em}
-
-\begin{document}
-%TC:ignore
-
-\maketitle
 
@@
 
-\section*{Reviewer \#1}
+\section*{Round 1 Reviews}
+
+\subsection*{Reviewer \#1}
 
@@
 
-\section*{Reviewer \#2}
+\subsection*{Reviewer \#2}
 
@@
 
-\section*{Reviewer \#3}
+\subsection*{Reviewer \#3}
 
@@
 
+\section*{Round 2 Reviews}
+
+\subsection*{Reviewer \#1}
+
+\textbf{I thank the authors for making the effort to provide new data and revise the manuscript per previous comments.
+In general, the authors did a great job with the new data they have.
+However, there are still major remaining issues that they did not address in this version of the manuscript.}
+
+\textbf{1.
+My main concern about the novelty and significance of this work still remains (which is echoed by reviewer 2).
+The take-home message of the study --- which was essentially that high quality data must be obtained to generate reliable results --- was evident prior to the actual conduction of the study.
+In fact, many experimental areas, such as experimental psychology, neuroscience, and biomedical sciences have already proven that.
+For instance, in neuroimaging, spurious correlations come up due to motion \cite{murphy2013resting, fellner2016spurious}; similar issues have been raised in genetics \cite{sullivan2007spurious}.
+In the context of behavioral research, these attention checks are typically called ``catch trials'' or ``sanity check''.
+The practice of using these procedures to filter out noisy data has been going on for decades.
+Even in the context of using online subjects, there is now a very rich literature on this very same point (e.g., \cite{barends2019noncompliant, chandler2019online} and many more).}
+
+We appreciate the reviewer's ongoing concerns about the novelty of our work, but we respectfully disagree.
+We agree with the reviewer that our ``take-home message'' (i.e., that poor data quality controls can lead to spurious inferences) has been discussed, in the most general sense, elsewhere in science.
+Nevertheless, this has not precluded previous studies that explicated particular methodological biases from having major impact on research within a field (e.g., \cite{eklund2016cluster, bradley2021unrepresentative}).
+Moreover, we argue that a general understanding of the need for high-quality data is not sufficient to obviate our findings.
+By very virtue of its specificity, our manuscript is able to offer concrete recommendations for researchers studying individual differences in cognitive processes.
+Indeed, since the publication of our initial manuscript on PsyArxiv, many researchers in computational psychiatry have changed their experiment designs to include infrequency items as we suggest (with the preprint already cited 29 times).
+If the insights and results we present were obvious from the extant literature, then our paper should not have made such a difference in the practices in the field.
+
+\textbf{2.
+In the revised paper, the authors added data demonstrating that patients with MDD show comparable attention failure rate as HCs.
+However, one of the key points in my previous comment is that patients with known attention deficits, such as ADHD (and SCZ or addiction), are likely to show heightened failure rate.
+The conclusion of the paper should be limited to the conditions they've tested (e.g., depression).}
+
+We thank the reviewer for this point.
+We first wish to note that, in the previous round of reviews, the reviewer did not explicitly mention attention deficits in patients with ADHD, schizophrenia, and/or substance use issues; instead, they wrote:
+
+\begin{displayquote}
+    In fact, there is a very rich literature demonstrating that many psychiatric disorders and symptoms are strongly accompanied by deficits in attention as well as lack of effort.
+For example, attention deficits have been well established in depression (e.g.
+Paelecke-Habermann et al, 2005 JAD) and anxiety (Bishop, 2009 Nat Neurosci), the two main types of mental health symptoms measured in this study.
+Deficits in effort-based behaviors have also been recently documented in these disorders (see Treadway et al, 2012; Bishop and Gagne, 2018).
+\end{displayquote}
+
+To address the reviewer's concerns, we therefore investigated the sensitivity of attention checks in patients diagnosed with major depressive disorder.
+While we agree that additional studies are necessary to validate attention checks in other patient populations, we respectfully disagree that we neglected to address the reviewer's stated concerns.
+
+Second, we would like to reiterate our concerns with this line of reasoning.
+If psychiatric participants were in general more likely to fail attention checks in self-report instruments, this would mean their self-reports on such instruments are also unreliable, undermining a very large body of research in which these instruments are considered a standard tool for psychiatric symptom measurement \cite{Demetriou2015-bq}.
+If it were truly the case that symptomatic participants were more likely to fail attention checks (i.e., because they are experiencing severe symptoms affecting their motivation or attention that render them unable to veridically complete a survey), then there would be little-to-no reason to use self-report symptom measures at all for these clinical populations.
+Of course, it may be the case that there are some acute psychiatric states for which patients are unable to complete self-report surveys accurately (e.g., mania, psychosis).
+Barring these, we suggest that our results are in line with the common usage of self-report surveys in psychiatric research.
+We mention this concern in the manuscript, in the Discussion:
+
+\begin{displayquote}
+Experimenters should also carefully consider whether an online study is truly appropriate for the research question.
+In particular, if the project aims to study syndromes associated with considerable difficulty in task or survey engagement (e.g., severe ADHD, acute mania), symptomatic participants are likely to produce responses that cannot be distinguished from C/IE responding.
+In such a case, correlational research in online samples is likely not the best approach for the research question.
+\end{displayquote}
+
+Regardless, we have also tempered our language describing the results of the clinical study in the Discussion. The text now reads:
+
+\begin{displayquote}
+    Though our final sample was small, we did not find evidence that \textit{depressed} patients were more likely to fail attention checks than healthy controls (if anything, non-psychiatric participants were more likely to be flagged by C/IE screening).
+These results provide preliminary evidence that rigorous C/IE screening is unlikely to result in overcontrol bias.
+\textit{However, further research with larger samples is necessary to validate attention checks in depressed and other patient populations.}
+\end{displayquote}
+
+\textbf{3.
+The authors also added a second task (two-step) to prove the point that their findings are generalizable across tasks.
+I applaud the authors for being able to replicate the findings with another task.
+But again, the two-step task is also an RL task as the original task (albeit more complex) and the study still falls short in terms of proving the findings are generalizable across experimental contexts.}
+
+We thank the reviewer for this point.
+We chose these tasks in particular due to their prevalence in computational psychiatry research, which makes heavy use of RL tasks.
+We agree that further study is required to better understand the scope of these issues.
+It is worth noting, however, that that similar results were reported (after the publication of our preprint) by an independent group using non-RL tasks and an alternative set of symptom measures \cite{sulik2021delusion}.
+Though more research is required, this suggests that our findings are likely generalizable beyond the context of RL tasks.
+
+\textbf{4.
+The overall attention failure is quite high for this study – in fact higher than many published studies \cite{hauser2016attentive}.
+This might imply a potential hidden factor which is boredom (if the main tasks are not perceived as interesting), that plays a role (even more important role) in this particular experimental context.}
+
+We thank the reviewer for this point.
+We wish to clarify three things.
+First, the quality of data collected from online labor platforms is always in flux (e.g., \cite{Moss2018-vy, Charalambides2021-fd}).
+That is, attention check failure rates on one platform at a single (distant) point in time (e.g., data collected on MTurk in 2013--2014; \cite{hauser2016attentive}) may not be an appropriate benchmark for data quality.
+Second, we do not believe our observed failure rates (i.e., 22\% and 14\% of participants failing one or more infrequency items in the original and replication studies) is abnormally high.
+Chandler et al.
+(2020) find evidence for C/IE responding in 18\% of MTurk participants \cite{Chandler2020-ja}.
+Similarly, Barends \& de Vries (2019) find evidence of C/IE responding in 12-17\% of MTurk participants \cite{Barends2019-ud}.
+In recent data quality research published by Prolific, attention check failure rates on Prolific and MTurk (using CloudResearch) was 31\% and 53\%, respectively \cite{eyal2021data}.
+Finally, our behavioral tasks were ``gamified'' and incorporated design elements previously used to sustain engagement in children \cite{decker2016creatures, nussenbaum2020moving}.
+Of course, participants may still have found our tasks boring, but arguably then C/IE responding would be worse for the majority of online studies that do not utilize task ``gamification''.
+
+\subsection*{Reviewer \#2}
+
+\textbf{I appreciate the authors' consideration and responses to my suggestions.
+I maintain that this is a technically well-executed and -written manuscript and am satisfied with their responses to my more minor points.
+However, my main concern with this paper was and remains that I find it to be too narrow in scope for Nature Human Behavior.
+The authors did not indicate that they made any substantive changes to the manuscript to address this point and while they make arguments for the paper's novelty, I ultimately continue to feel that this paper contributes an incremental step.}
+
+We thank the reviewer for taking the time to consider our revisions and for praising the technical execution of our work.
+We appreciate the reviewer's concerns about the scope of our work.
+To try to at least partially address this, we have noted in the Discussion that our results and conclusions are not applicable only to computational psychiatry research, but to any online individual-differences cognitive science research:
+
+\begin{displayquote}
+    We conclude with a list of concrete recommendations for future online studies involving correlations between task behavior and self-report instruments.
+\textit{We note that these recommendations are not limited to computational psychiatry studies, but are applicable to any online individual-differences cognitive science research involving similar methods (e.g., behavioral economics, psycholinguistics).}
+\end{displayquote}
+
+\subsection*{Reviewer \#3}
+
+\textbf{The authors have done a great job of responding to the reviewers' comments, and in particular the addition of the second online experiment provides convincing evidence that the attenuation of spurious associations is not driven by over-correction, which was my main concern.
+Unfortunately, in this second study the pattern of results with the artistic interest scale was difficult to interpret due to the negative skew on this measure, but the results relating to the greed avoidance scale, which is positively skewed like the symptom measures in the initial study, are very clear.
+I thank the authors for their work in conducting this additional study, which has greatly strengthened the paper.}
+
+\textbf{There are two remaining substantial suggestions:}
+
+\textbf{1.
+It seems a shame to relegate the results of the replication study to the Appendix, where some readers may never see them.
+At the very least Figures S7, S8 and especially S9, and Table S11, and possibly some of the supplementary text describing the results, could be promoted to the main manuscript to allow readers to compare between the two online studies more easily.}
+
+We thank the reviewer for this suggestion.
+While we sympathize with the concerns, our preference is to retain the material in Appendix B, as is, for two reasons.
+First, the main text is already quite long (over 7,000 words, not including the Methods or Figure/Table captions) and we worry about depleting our readers' attentions before they reach the Discussion (i.e., where our recommendations are).
+Second, most of the figures and tables from the replication study (e.g., Figures S7, S9; Table S11) require detailed explanation to be meaningfully interpreted.
+Promoting these to the main text would therefore necessitate adding much of the methods section from Appendix B alongside them, which we worry would counter-productively lengthen and clutter the main text.
+However, we would be willing to make this change if the editorial staff agree that having the material in the main text is essential, and allow us to extend the overall length of the article.
+
+\textbf{2.
+There are several discrepancies between the results of the two online studies, to the extent that these merit a specific paragraph in the Discussion section of the main paper.
+The main issues to cover are: i) The distributions were quite different for some variables in the initial and replication studies (in the second study there was much lower skew for GAD; and C/IE responders did not score significantly higher on anxiety or depression – which is a point that the authors should discuss, as part of the argument for how the spurious correlations arise is through an overall shift towards higher responding on common self-report mental health scales).
+It's not clear what the explanation is for this, perhaps the authors could speculate.
+ii) In the second study, exclusion based on WSLS behaviour alone was effective at attenuating spurious correlations (which does somewhat contradict one of the authors' key take-home messages in the original submission!).
+Perhaps this is due to the more difficult task, which would provide more sensitivity for exclusions based on behaviour alone?
+What do the authors think?
+iii) The lower rate of C/IE responding in the second study (which the authors ascribe to new data quality filters on the platforms).}
+
+We thank the reviewer for this important point.
+To start, we wish to clarify one misunderstanding.
+In the replication study, we employed a 7-item measure of general anxiety from the HiTOP group; this is different from the GAD-7, which we used in the original study.
+This alternative anxiety scale was expected to yield an approximately symmetric total score distribution, and thus was hypothesized \emph{not} to show differences in scores between attentive and C/IE responding participants.
+We note this in the methods section in Appendix B:
+
+\begin{displayquote}
+    Participants also completed an alternative 7-item measure of general anxiety symptoms over the last year (e.g., ``I was overwhelmed by anxiety.''; [13]).
+This scale is expected to elicit moderate rates of symptom endorsement, thereby resulting in a symmetric score distribution.
+We therefore expected the depression and mania measures to be at greater risk for spurious correlations with behavior on the two-step task than the anxiety measure.
+\end{displayquote}
+
+As such, we do not believe it additionally noteworthy that the anxiety scores were less skewed than in the original study, or that participants flagged for C/IE responding did not score significantly higher on the anxiety scale.
+That scores on the depression scale (7-down) in the replication study were not more inflated in C/IE relative to attentive participants is perplexing, though this may simply reflect the overall smaller number of participants flagged for C/IE responding in the replication study.
+
+We have attempted to address the other discrepancies in the Discussion:
+
+\begin{displayquote}
+    This study highlights the need for more research on the prevalence of C/IE responding in online samples and its interactions with task-symptom correlations.
+Many open questions remain, including under what conditions task- and symptom-screening measures might better correspond, what screening measures are most effective and when, and under what conditions spurious correlations are more likely to arise.
+\textit{For example, we found that screening on task behavior alone was insufficient to prevent putatively spurious correlations for one task (reversal learning) but was sufficient for another task (the two-step task).
+This discrepancy may reflect differences in the tasks (e.g., the two-step task may be more challenging and thus more sensitive to C/IE responding) or differences in the screening measures (e.g., choice accuracy across 90 trials may be a noisier measure than win-stay lose-shift choice behavior across 200 trials).}
+
+    One especially pressing question is how sample size affects the likelihood of obtaining spurious correlations.
+The results of a bootstrapping analysis in our data suggest that false positive rates are likely to increase with sample size.
+As computational psychiatry studies move towards larger samples to characterize heterogeneity in symptoms (and to increase statistical power), it will be important to understand how sample size may exaggerate the effects of systematic error.
+\textit{It will also be important to understand how this is moderated by overall C/IE responding rates, which we observed to vary across platforms and time, and which will presumably continue to evolve with changing labor platform and researcher screening practices.}
+\end{displayquote}
+
+\textbf{A few final minor suggestions:}
+
+\textbf{3.
+In the replication study it's notable that one of the associations with depression that was attenuated when using exclusions based on C/IE only seems to return when using both types of exclusions, and was also evident using the WSLS only exclusion – this is the association between depression and sensitivity to reward on the preceding trial (Figure S9).
+This seems to be quite a plausible association, and it's not clear whether the authors are claiming that it is spurious or not.
+This should be clarified, as if the authors don't believe it's spurious (and personally I think it's real), presumably this would be a downside to excluding based on C/IE alone, as it's an example of a real association that is actually obscured by their recommended exclusion procedure.
+Reviewing Figure 4, a similar pattern is actually evident in the initial study, between anxiety and positive learning rate – again, this only becomes non-significant when excluding using C/IE.
+Are the authors claiming this is spurious, even though it is significant when using both types of exclusion?}
+
+We thank the reviewer for this interesting point, though we wish to clarify the correlation in question (i.e., between depression and sensitivity to reward).
+Before exclusions are applied, the correlation is $\rho = -0.104$, $p = 0.019$.
+Under the three exclusion strategies, the correlation is slightly attenuated (WSLS-only: $\rho = -0.097$, $p = 0.044$; infrequency-only: $\rho = -0.091$, $p = 0.058$; both: $\rho = -0.097$, $p = 0.049$).
+As is apparent, the effect is on the border of significance under all three exclusion strategies and just happens to be, likely by chance, non-significant in one case.
+We do not believe this is a meaningful difference; that is, in this instance, the difference between ``significant'' and ``not significant'' is not itself statistically significant \cite{gelman2006difference}.
+As such, this situation does not present a clear downside to excluding based on C/IE responding on surveys alone.
+(We believe a similar explanation underlies the pattern of correlations between anxiety and positive learning rate in the original study.) We have added new supplementary tables (S14--S17) to facilitate understanding of this point.
+
+\textbf{4.
+The authors should temper their conclusions in relation to the study conducted in depressed participants (Discussion, bottom of p17).
+While this is a useful addition to the manuscript, the finding of a null result in such a small sample is quite ambiguous, and indeed the Bayes factors in favour of the null are hardly convincing.
+Additionally, the context of online vs clinical recruitment is obviously very different, and patients referred from a clinic may well be more personally invested in the research and thus potentially more attentive for this reason.}
+
+We thank the reviewer for this point (see also Reviewer \#1, point \#2). We have tempered our language describing the results of the clinical study in the Discussion. The text now reads:
+
+\begin{displayquote}
+    Though our final sample was small, we did not find evidence that \textit{depressed} patients were more likely to fail attention checks than healthy controls (if anything, non-psychiatric participants were more likely to be flagged by C/IE screening).
+These results provide preliminary evidence that rigorous C/IE screening is unlikely to result in overcontrol bias.
+\textit{However, further research with larger samples is necessary to validate attention checks in depressed and other patient populations.}
+\end{displayquote}
+
+Regarding the reviwer's last point, we wish to clarify that not all of the patients were recruited via clinician referral; many patients who agreed to participate were recruited via online ads (a process similar to how participants are recruited online from MTurk or Prolific).
+In any case, we agree that patient populations may be more invested in studies that investigate the conditions they are struggling with.
+This further suggests that our proposed methods of screening inattentive or careless participants is not likely to present an over-control bias and systematically exclude patients.
+We note this in the Discussion of Appendix C:
+
+\begin{displayquote}
+    Indeed, whereas healthy controls may be primarily motivated to participate for monetary purposes, patients may be motivated to participate to further scientific research that may ultimately benefit them (or others suffering from the same conditions).
+That is, patients may have more ``stakes in the game,'' and may therefore be more motivated to provide higher-quality responses.
+\end{displayquote}
+
+\textbf{5.
+p58 of the supplement states ``However, an unexpected and statistically significant mean-shift'' – since this measure (greed avoidance) is somewhat skewed, why would the mean shift be unexpected?
+Surely the more surprising finding here is that the attentive and C/IE groups don't differ on depression score, which is clearly skewed.}
+
+We thank the reviewer for the question.
+To clarify, the mean-shift is unexpected because previous research involving large samples observed that the total score distribution for the greed avoidance scale was relatively symmetric.
+As such, we \textit{a priori} expected minimal difference in these scores between attentive and C/IE responding participants, as we note in the methods:
+
+\begin{displayquote}
+    Finally, participants completed a 6-item measure of greed avoidance, which measures attitudes towards wealth and status (e.g., ``I am out for my own personal gain''; [14]).
+Based on previous studies, this scale is expected to elicit moderate rates of endorsement, thereby resulting in a symmetric score distribution.
+We therefore expected the artistic interests scale to be at greater risk for spurious correlations with behavior on the two-step task than the greed avoidance scale.
+\end{displayquote}
+
+\clearpage
 \printbibliography

### 2023-04-27 manuscripts/main.tex
reupload

@@
 If these participants are similarly careless in their task performance, this may result in a spurious association between symptom scores and task behavior.
-We demonstrate this pattern of results in two samples of participants (total N = 779) recruited online who performed one of two common cognitive tasks.
+We demonstrate this pattern of results in two samples of participants recruited online (total N = 779) who performed one of two common cognitive tasks.
 False-positive rates for these spurious correlations increase with sample size, contrary to common assumptions.
-Excluding participants flagged for careless responding on surveys abolished these spurious correlations, but exclusion based on task performance alone was less effective.
+Excluding participants flagged for careless responding on surveys abolished the spurious correlations, but exclusion based on task performance alone was less effective.
 }
@@
 
-The present study highlights the need for future work on the prevalence of C/IE responding in online samples and its interactions with task-symptom correlations.
+This study highlights the need for more research on the prevalence of C/IE responding in online samples and its interactions with task-symptom correlations.
 Many open questions remain, including under what conditions task- and symptom-screening measures might better correspond, what screening measures are most effective and when, and under what conditions spurious correlations are more likely to arise.
-For example, in the present study, we found that screening on task behavior alone was insufficient to prevent putatively spurious correlations for one task (reversal learning) but not for another (two-step task).
+For example, we found that screening on task behavior alone was insufficient to prevent putatively spurious correlations for one task (reversal learning) but was sufficient for another task (the two-step task).
 This discrepancy may reflect differences in the tasks (e.g., the two-step task may be more challenging and thus more sensitive to C/IE responding) or differences in the screening measures (e.g., choice accuracy across 90 trials may be a noisier measure than win-stay lose-shift choice behavior across 200 trials).
+
 One especially pressing question is how sample size affects the likelihood of obtaining spurious correlations.
@@
 We note that these recommendations are not limited to computational psychiatry studies, but are applicable to any online individual-differences cognitive science research involving similar methods (e.g., behavioral economics, psycholinguistics).
-Moving forward, we would strongly recommend that experimenters employ some form of self-report screening method, preferably one recommended by the best-practices literature (e.g., \cite{huang2015insufficient, curran2016methods, thomas2017validity, desimone2018dirty, ophir2020turker}).
-Our literature review found that, to date, the majority of online studies assessing behavior-symptom correlations have not used self-report screening, and our results demonstrate that stand-alone task-behavior screening is often insufficent to prevent spurious symptom-behavior correlations induced by C/IE responding.
-For these reasons, we encourage experimenters to use a variety of data-quality checks for online studies and to be transparent in their reporting of how screening was conducted, how many participants are flagged under each measure, and what thresholds are used for rejection.
+
+Moving forward, we strongly recommend that experimenters employ some form of self-report screening method, preferably one recommended by the best-practices literature (e.g., \cite{huang2015insufficient, curran2016methods, thomas2017validity, desimone2018dirty, ophir2020turker}).
+Our literature review found that, to date, the majority of online studies assessing behavior-symptom correlations have not used self-report screening, and our results demonstrate that stand-alone task-behavior screening is not necessarily sufficent to prevent spurious symptom-behavior correlations induced by C/IE responding.
+We therefore encourage experimenters to use a variety of data-quality checks for online studies and to be transparent in their reporting of how screening was conducted, how many participants were flagged under each measure, and what thresholds were used for rejection.
 
 When collecting self-report questionnaire data, we encourage experimenters to use screening methods sensitive to multiple distinct patterns of C/IE responding (e.g., random responding, straight-lining, side bias) and, if possible, to log all page interactions (e.g., mouse clicks, keyboard presses).
-We specifically recommend experimenters follow best-practice guidelines and use infrequency-item attention checks rather than instructed-item checks, as multiple studies have now shown that online participants are habituated to and circumvent the latter (e.g., \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}; Appendix B).
+We specifically recommend experimenters use infrequency-item attention checks rather than instructed-item checks, as multiple studies have now shown that online participants are habituated to and circumvent the latter (e.g., \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}; Appendix B).
 Participants flagged by suspicious responses on attention-check items should either be excluded from further analysis, or assessed using sensitivity analyses to ensure that observed full-sample correlations are robust to their exclusion.
@@
 We found that spurious correlations predominantly affected self-report instruments for which the expected distributions of symptom scores were asymmetric (either positively or negatively skewed).
-As such, symmetrically-distributed measures of a given construct should be preferred to asymmetrically-distributed measures (though this will often be infeasible given that the prevalence of many psychiatric symptoms in the general population is typically small).
+As such, all else equal, symmetrically-distributed measures of a given construct should be preferred to asymmetrically-distributed measures (though this will often be infeasible given that the prevalence of many psychiatric symptoms in the general population is typically small).
 Scales with reverse-coded items can be used to quantify the consistency of participants' responses between reverse-coded and non-reverse-coded measures of the same latent construct.
@@
 
-In our experience, we have found it instructive to review discussions on public forums for participants of online labor markets (e.g., Reddit, TurkerNation).
+In our experience, we have found it instructive to review discussions on public forums for participants of online labor markets (e.g., at the time of writing, Reddit, TurkerNation).
 Doing so helps an experimenter identify what screening methods would-be participants are already aware of and prepared to answer correctly.
@@
 Specifically, 208 participants were recruited from Amazon Mechanical Turk (MTurk) and 201 participants were recruited from Prolific.
-This study was approved by the Institutional Review Board of Princeton University (\#5291), and all participants provided informed consent.
+This study was approved by the Institutional Review Board of Princeton University, and all participants provided informed consent.
 Total study duration was approximately 10 minutes per participant.
@@
 
-The data from multiple participants who completed the experiment were excluded prior to analysis.
+Data from several participants were excluded prior to analysis.
 Three participants (all MTurk) were excluded due to missing data.
@@
 The authors are grateful to Agnes Norbury, Alexandra Pike, and Oliver Robinson for helpful discussion.
-The research reported in this manuscript was supported in part by the National Institute of Mental Health (NIMH) under award number 5R01MH119511-02 (YN), and by the National Center for Advancing Translational Sciences (NCATS), a component of the National Institute of Health (NIH), under award number UL1TR003017 (YN).
+Research reported in this manuscript was supported in part by the National Institute of Mental Health (R01MH119511; YN), and by the National Center for Advancing Translational Sciences (UL1TR003017; YN).
 The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.
@@
 \begin{figure}[h]
-    % \includegraphics[width=16cm]{../figures/main_02a.png}
+    \includegraphics[width=16cm]{../figures/main_02a.png}
     \centering

### 2023-04-27 manuscripts/supp.tex
reupload

@@
 The studies were approved by the Institutional Review Board of Rutgers University (\#2019000738, \#2018000629), and all participants provided informed consent.
-Participants received monetary compensation for their time (rate USD \$12/hr), plus an incentive-compatible bonus based on task performance.
+Participants received monetary compensation for their time (rate USD \$20/hr), plus an incentive-compatible bonus based on task performance.
 
@@
 Indeed, whereas healthy controls may be primarily motivated to participate for monetary purposes, patients may be motivated to participate to further scientific research that may ultimately benefit them (or others suffering from the same conditions).
-That is, patients may have more ``stakes in the game,'' and therefore may be motivated to provide higher-quality responses.
+That is, patients may have more ``stakes in the game,'' and may therefore be more motivated to provide higher-quality responses.
 Regardless, further research is required to examine whether this preliminary finding holds in larger samples and other testing contexts.

### 2023-06-21 manuscripts/main.tex
manuscript proofs

@@
 \usepackage{booktabs}
-\usepackage{xcolor,soul}
+\usepackage{fancyhdr}           % first-page header
 
@@
 
-% define highlight style
-\colorlet{usercolorname}{yellow!00}    % use for public version
-% \colorlet{usercolorname}{yellow!30}    % use for reviewer version
-\sethlcolor{usercolorname}
+% specify first-page header
+\fancypagestyle{firstpage}
+{
+    \renewcommand{\headrulewidth}{0pt}
+    \fancyhead[L]{\small Peer-reviewed publication DOI: \href{https://doi.org/10.1038/s41562-023-01640-7}{10.1038/s41562-023-01640-7}}
+    \fancyhead[R]{}
+}
 
@@
 \maketitle
+\thispagestyle{firstpage}
 
@@
 For example, 13.0\% of participants scored at or above clinical thresholds for (hypo)mania on the 7-up scale in our sample prior to screening, compared with a 12-month prevalence of 5\% in the general population \cite{merikangas2007lifetime, merikangas2012true}, but this rate was reduced to 4.0\% (in line with the population prevalence estimates) after exclusion of C/IE respondents.
-We observed a similar pattern for both major depressive disorder and anxiety (population prevalence estimates of 7\% and 5\% respectively; \cite{kessler2012twelve, lowe2008validation, hinz2017psychometric}).
+We observed a similar pattern for both major depressive disorder (MDD) and anxiety (population prevalence estimates of 7\% and 5\% respectively; \cite{kessler2012twelve, lowe2008validation, hinz2017psychometric}).
 Interestingly, the proportion of participants meeting threshold on the GAD-7 was elevated compared to previous literature.
@@
 
-To evaluate the generalizability of our findings, we therefore conducted a conceptual replication experiment in which an independent sample of N=393 participants (N=193 from MTurk using CloudResearch, N=200 from Prolific) completed a more difficult cognitive task, the well-known ``two-step task'' \cite{daw2011model}, and an alternate set of self-report measures (see Appendix B for details).
+To evaluate the generalizability of our findings, we therefore conducted a conceptual replication experiment in which an independent sample of N=393 participants (N=193 from MTurk using CloudResearch, N=200 from Prolific) completed a more difficult cognitive task, the well-known ``two-step task'' \cite{daw2011model}, and an alternate set of self-report measures (see Supplementary Materials B for details).
 Importantly, participants were recruited \textit{after} CloudResearch and Prolific implemented new protocols to improve data quality on their respective platforms.
@@
 
-For the sake of brevity, we report here only the main pattern of findings (all results are reported in Appendix B).
+For the sake of brevity, we report here only the main pattern of findings (all results are reported in Supplementary Materials B).
 In the replication sample, 55 out of 393 participants (14\%) endorsed a logically invalid or improbable response on one or more of the infrequency items when completing the self-report measures.
@@
 % \subsection*{Individuals with and without diagnosed psychiatric disorders fail attention checks at similar rates}
-\subsection*{Psychiatric patients do not fail attention checks more often}
+\subsection*{Patients with depression do not fail attention checks more often}
 
@@
 
-To explore this possibility, we embedded attention checks into the self-report measures of two studies of patients with major depressive disorder (see Appendix C for details).
+To explore this possibility, we embedded attention checks into the self-report measures of two studies of patients with major depressive disorder (see Supplementary Materials C for details).
 Specifically, N=35 psychiatric patients (confirmed to meet criteria for a diagnosis of major depressive disorder through a structured clinical interview) across 45 unique testing sessions and N=17 healthy controls across 20 unique testing sessions, all recruited through the Rutgers-Princeton Center for Computational Cognitive Neuropsychiatry (i.e., not via online labor platforms), completed a series of self-report symptom measures, online, on their computers from the comfort of their homes.
 In total, 16 of 65 (24.6\%) participants failed one or more attention checks.
-Subdivided by group, 6 of 20 (30\%) healthy participants and 10 of 45 (22\%) psychiatric participants were flagged for C/IE responding.
-
-Using these data, we computed pairwise Bayes factors comparing three candidate models: attention check failure rates are equal between healthy and psychiatric participants (M1); failure rates are greater in psychiatric patients (M2); and failure rates are greater in healthy participants (M3).
-The model assuming equal rates of failure between healthy and psychiatric participants was 2.88 times more likely than the model assuming greater rates for psychiatric patients.
-In turn, the model assuming lower rates of failure for psychiatric patients was 1.27 times more likely than the model assuming equal rates.
-Finally, the model assuming lower rates of failure for psychiatric patients was 3.65 times more likely than the model assuming higher rates for psychiatric patients.
+Subdivided by group, 6 of 20 (30\%) healthy participants and 10 of 45 (22\%) MDD patients were flagged for C/IE responding.
+
+Using these data, we computed pairwise Bayes factors comparing three candidate models: attention check failure rates are equal between healthy and MDD patients (M1); failure rates are greater in MDD patients (M2); and failure rates are greater in healthy participants (M3).
+The model assuming equal rates of failure between healthy and MDD participants was 2.88 times more likely than the model assuming greater rates for MDD patients.
+In turn, the model assuming lower rates of failure for MDD patients was 1.27 times more likely than the model assuming equal rates.
+Finally, the model assuming lower rates of failure for MDD patients was 3.65 times more likely than the model assuming higher rates for MDD patients.
 Only the final comparison exceeds the cutoff value of 3, which is conventionally treated as the minimal amount of evidence required to treat a difference in model fit as meaningful.
-Although the size of the sample precludes any definitive conclusion, it is noteworthy that the model least consistent with the data was the one where psychiatric patients are more likely to fail infrequency item attention checks.
-These data suggest, therefore, that it is unlikely that individuals with high psychiatric symptom severity were disproportionately flagged for C/IE responding in the main analyses.
-Accordingly, we tentatively conclude that the screening measures we are suggesting are not likely to result in overcontrol bias and false-negative correlations between tasks and symptom measures.
+Although the size of the sample precludes any definitive conclusion, it is noteworthy that the model least consistent with the data was the one where MDD patients are more likely to fail infrequency item attention checks.
+These data suggest, therefore, that it is unlikely that individuals with high depression symptom severity were disproportionately flagged for C/IE responding in the main analyses.
+Accordingly, we tentatively conclude that the screening measures we are suggesting are not likely to result in overcontrol bias and false-negative correlations between tasks and symptom measures, at least in the case of individuals with depression.
+It remains possible that other psychiatric symptoms might be associated with a different pattern of results.
 
@@
 To explore this possibility, we embedded attention checks into the self-report measures of two studies of patients with major depressive disorder.
-Though our final sample was small, we did not find evidence that depressed patients were more likely to fail attention checks than healthy controls (if anything, non-psychiatric participants were more likely to be flagged by C/IE screening).
+Though our final sample was small, we did not find evidence that depressed patients were more likely to fail attention checks than healthy controls (if anything, healthy participants were more likely to be flagged by C/IE screening).
 These results provide preliminary evidence that rigorous C/IE screening is unlikely to result in overcontrol bias.
@@
 When collecting self-report questionnaire data, we encourage experimenters to use screening methods sensitive to multiple distinct patterns of C/IE responding (e.g., random responding, straight-lining, side bias) and, if possible, to log all page interactions (e.g., mouse clicks, keyboard presses).
-We specifically recommend experimenters use infrequency-item attention checks rather than instructed-item checks, as multiple studies have now shown that online participants are habituated to and circumvent the latter (e.g., \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}; Appendix B).
+We specifically recommend experimenters use infrequency-item attention checks rather than instructed-item checks, as multiple studies have now shown that online participants are habituated to and circumvent the latter (e.g., \cite{barends2019noncompliant, thomas2017validity, hauser2016attentive}; Supplementary Materials B).
 Participants flagged by suspicious responses on attention-check items should either be excluded from further analysis, or assessed using sensitivity analyses to ensure that observed full-sample correlations are robust to their exclusion.
@@
 The demographics of the sample split by labor market is provided in Table S1.
-Notably, the participants recruited from MTurk were older ($M = 7.7 \ \text{yrs}$, two-tailed, two-sample $t$-test: $t(384)=6.567$, $p<0.001$, $d=0.669$, 95\% CI = [5.4, 10.0]) and comprised of fewer women (two-tailed, two-sample proportions test: $z(384)=2.529$, $p=0.011$, $h=0.258$, 95\% CI = [0.030, 0.228]).
+Notably, the participants recruited from MTurk were older (mean difference = 7.7 yrs), two-tailed, two-sample $t$-test: $t(384)=6.567$, $p<0.001$, $d=0.669$, 95\% CI = [5.4, 10.0]) and comprised of fewer women (two-tailed, two-sample proportions test: $z(384)=2.529$, $p=0.011$, $h=0.258$, 95\% CI = [0.030, 0.228]).
 
@@
 Participants were instructed to earn the most points possible by learning (through trial-and-error) and choosing the best choice option.
-Participants were also instructed that the best option could change during the task, but were not informed about how often or when this would occur (see Appendix A for the complete instructions).
+Participants were also instructed that the best option could change during the task, but were not informed about how often or when this would occur (see Supplementary Materials A for the complete instructions).
 Prior to beginning the experiment, participants had to correctly answer four comprehension questions about the instructions.
@@
 Though the 7-up/7-down scales do not have firmly established clinical cutoffs recent work has suggested a cutoff score of 12 or higher \cite{youngstrom2020evaluating}, which we use here.
-Finally, the original authors of the SHAPS scale recommended as a cutoff a score of 3 or more when the items are binarized (1 = ``strongly disagree", ``agree"; 0 = ``strongly agree", ``agree").
+Finally, the original authors of the SHAPS scale recommended as a cutoff a score of 3 or more when the items are binarized (1, `Strongly disagree' or `Disagree'; 0, `Strongly agree' or `Agree').
 We use this scoring approach in Table \ref{tab:tab02}.
@@
 
-where $y_i$ is a participant's response to item $i$, $x_i$ is a participant's average score across all  items, and $k$ is the total number of items for a self-report measure.
+where $y_i$ is a participant's response to item $i$, $y_i$ is a participant's average score across all  items, and $k$ is the total number of items for a self-report measure.
 A composite ISD measure was estimated per participant by summing across each of the seven self-report scales.
@@
 
+where $r_t$ is the observed reward on trial $t$.
 In the risk-sensitive temporal difference learning model, there are separate learning rates for positive and negative prediction errors, such that positive and negative prediction errors have asymmetric effects on learning.
@@
 
-\textbf{Samuel Zorowitz:} Conceptualization (equal); Software development (lead); Data collection - online (lead); Formal analysis (lead); Writing - Original Draft (lead); Writing - Review \& Editing (supporting); Visualization (lead).
-\textbf{Johanne Solis:} Software development (supporting); Data collection - clinical (lead); Writing - Review \& Editing (supporting).
-\textbf{Yael Niv:} Writing - Review \& Editing (equal); Funding acquisition.
-\textbf{Daniel Bennett:} Conceptualization (equal); Software development (supporting); Data collection - online (supporting); Formal analysis (supporting); Writing - Review \& Editing (equal); Visualization (supporting).
+\textbf{SZ:} Conceptualization (equal); Software development (lead); Data collection - online (lead); Formal analysis (lead); Writing - Original Draft (lead); Writing - Review \& Editing (supporting); Visualization (lead).
+\textbf{JS:} Software development (supporting); Data collection - clinical (lead); Writing - Review \& Editing (supporting).
+\textbf{YN:} Writing - Review \& Editing (equal); Funding acquisition.
+\textbf{DB:} Conceptualization (equal); Software development (supporting); Data collection - online (supporting); Formal analysis (supporting); Writing - Review \& Editing (equal); Visualization (supporting).
 

### 2023-06-21 manuscripts/supp.tex
manuscript proofs

@@
 
-% specify some custom commands
-\renewcommand{\baselinestretch}{1.2}
-\renewcommand*{\Authsep}{, }
-\renewcommand*{\Authand}{, }
-\renewcommand*{\Authands}{, }
-\renewcommand*{\Affilfont}{\normalsize}
-
-% set up the author block
-\setlength{\affilsep}{2em}   % set the space between author and affiliation
-\author[1,*]{Samuel Zorowitz}
-\author[2]{Johanne Solis}
-\author[1,3]{Yael Niv}
-\author[4]{Daniel Bennett}
-\affil[1]{Princeton Neuroscience Institute, Princeton University, NJ, USA}
-\affil[2]{Rutgers-Princeton Center for Computational Cognitive Neuropsychiatry, Rutgers University, NJ, USA}
-\affil[3]{Department of Psychology, Princeton University, NJ, USA}
-\affil[4]{School of Psychological Sciences, Monash University, Victoria, Australia}
-\affil[*]{Corresponding author (zorowitz@princeton.edu)}
-
 % specify the title
-\title{Supplementary materials for ``Inattentive responding can induce spurious associations between task behavior and symptom measures''}
+\title{}
 
@@
 
+% Define title of Table of Contents
+\addto\captionsenglish{\renewcommand{\contentsname}{Table of Contents}}
+
 \begin{document}
 
-\maketitle
+% \maketitle
+
+% Change ToC link color
+{\hypersetup{linkcolor=black, linkbordercolor=black} \tableofcontents}
 
@@
 \clearpage
-\section*{Appendix A}
+\addcontentsline{toc}{section}{Supplementary Materials A - Original Study}
+\section*{Supplementary Materials A}
 \setcounter{figure}{0}
 \setcounter{table}{0}
-\renewcommand{\thetable}{S\arabic{table}}
-\renewcommand{\thefigure}{S\arabic{figure}}
-
+\renewcommand{\figurename}{Supplementary Figure}
+\renewcommand{\tablename}{Supplementary Table}
+
+\addcontentsline{toc}{subsection}{Supplementary Figures}
 \subsection*{Signed correlation analysis}
@@
 \clearpage
-
 \subsection*{Posterior predictive checks}
@@
 \clearpage
+\addcontentsline{toc}{subsection}{Supplementary Tables}
 \subsection*{Participant demographics}
@@
 \clearpage
-\subsection*{Task Instructions}
+\addcontentsline{toc}{subsection}{Reversal learning task instructions}
+\subsection*{Reversal learning task Instructions}
 
@@
 
+\addcontentsline{toc}{subsection}{Model-based analyses of C/IE behavior}
 \subsection*{C/IE responding manifests as a distinct behavioral strategy}
@@
 \break
-\section*{Appendix B: Replication study}
+\addcontentsline{toc}{section}{Supplementary Materials B - Replication Study}
+\section*{Supplementary Materials B: Replication study}
 
@@
 
+\addcontentsline{toc}{subsection}{Methods}
 \subsection*{Methods}
 
+\addcontentsline{toc}{subsubsection}{Participants}
 \subsubsection*{Participants}
@@
 
+\addcontentsline{toc}{subsubsection}{Experiment}
 \subsubsection*{Experiment}
@@
 
+\addcontentsline{toc}{subsubsection}{Self-report measures}
 \subsubsection*{Self-report measures}
@@
 
+\addcontentsline{toc}{subsubsection}{Screening measures correspondence analysis}
 \subsubsection*{Correspondence of screening measures}
@@
 
+\addcontentsline{toc}{subsubsection}{Correlation analyses}
 \subsubsection*{Correlations between behavior and symptom measures}
@@
 
+\addcontentsline{toc}{subsection}{Results}
 \subsection*{Results}
 
+\addcontentsline{toc}{subsubsection}{Proportion and characterization of C/IE participants}
 \subsubsection*{Careless participants (often) appear symptomatic when the overall level of symptom endorsement is low}
@@
 
+\addcontentsline{toc}{subsubsection}{Screening measures correspondence analysis}
 \subsubsection*{Low correspondence between task and self-report measures of C/IE responding}
@@
 
+\addcontentsline{toc}{subsubsection}{Correlation analyses}
 \subsubsection*{Spurious symptom-behavior correlations produced by C/IE responding}
@@
 \break
+
+\addcontentsline{toc}{subsection}{Supplementary Tables}
 \subsection*{Correspondence of screening measures}
@@
 \break
-\section*{Appendix C: Attention checks in healthy and psychiatric patients}
+\addcontentsline{toc}{section}{Supplementary Materials C - Clinical Study}
+\section*{Supplementary Materials C: Attention checks in healthy and depressed patients}
 
@@
 Of these, 14 participated in both studies.
-In total, there was data from 20 sessions involving a healthy participant and data from 45 sessions involving a psychiatric participant.
+In total, there was data from 20 sessions involving a healthy participant and data from 45 sessions involving a patient with major depressive disorder.
 Of the 17 healthy participants, 6 identified as men and 11 identified as women.
@@
 
+\addcontentsline{toc}{subsubsection}{Attention checks}
 \subsubsection*{Infrequency items}
 
-To measure and compare C/IE responding between healthy and psychiatric participants, we used two sets of attention checks.
+To measure and compare C/IE responding between healthy and MDD patients, we used two sets of attention checks.
 Each set was composed of three infrequency items and one instructed item.
@@
 
+\addcontentsline{toc}{subsubsection}{Analysis}
 \subsubsection*{Analysis}
 
-Of primary interest here was whether psychiatric patients fail infrequency item attention checks at equal or at greater rates than healthy participants.
+Of primary interest here was whether MDD patients fail infrequency item attention checks at equal or at greater rates than healthy participants.
 To test this, we conducted Bayesian hypothesis testing using Bayes factors \cite{harms2018making}.
@@
 
-where $N_1$ and $N_2$ are the observed number of healthy and psychiatric participants, respectively; $p$ is the latent probability of a participant failing one or more attention checks; and $\delta$ is an offset parameter specifying the hypothesized difference in failure rates between groups.
-Thus, $M_0$ assumes equal rates of failures between healthy and psychiatric participants, whereas $M_1$ and $M_2$  assume greater and lower rates, respectively, for psychiatric participants compared to healthy participants.
+where $N_1$ and $N_2$ are the observed number of healthy and MDD participants, respectively; $p$ is the latent probability of a participant failing one or more attention checks; and $\delta$ is an offset parameter specifying the hypothesized difference in failure rates between groups.
+Thus, $M_0$ assumes equal rates of failures between healthy and MDD participants, whereas $M_1$ and $M_2$ assume greater and lower rates, respectively, for MDD participants compared to healthy participants.
 The common latent probability, $p$, was set to the observed average rate across the two groups.
@@
 
+\addcontentsline{toc}{subsection}{Results}
 \subsection*{Results}
@@
 Interestingly, the overall proportion of flagged sessions was similar to that observed for the original study.
-Subdivided by group, 6 of 20 healthy participant sessions (30\%) and 10 of 45 psychiatric participant sessions (22\%) were flagged for C/IE responding.
+Subdivided by group, 6 of 20 healthy participant sessions (30\%) and 10 of 45 MDD participant sessions (22\%) were flagged for C/IE responding.
 Unsurprisingly, given the modest sample size, the difference between the two proportions was not significantly different from zero (two-tailed, two-sample proportions test: $z(63)=0.672$, $p=0.502$, $h=0.178$, 95\% CI = [-0.157, 0.312]).
@@
 Next, we computed the Bayes factor for each pair of candidate models.
-A model assuming equal rates of failure between healthy and psychiatric participants was 2.88 times more likely than the model assuming greater rates for psychiatric patients.
-In turn, a model assuming lower rates of failure for psychiatric patients was 1.27 times more likely than the model assuming equal rates.
-Finally, a model assuming lower rates of failure for psychiatric patients was 3.65 times more likely than the model assuming higher rates for psychiatric patients.
+A model assuming equal rates of failure between healthy and MDD participants was 2.88 times more likely than the model assuming greater rates for MDD patients.
+In turn, a model assuming lower rates of failure for MDD patients was 1.27 times more likely than the model assuming equal rates.
+Finally, a model assuming lower rates of failure for MDD patients was 3.65 times more likely than the model assuming higher rates for MDD patients.
 Only the final comparison exceeds the cutoff value of 3, which is conventionally treated as the minimal amount of evidence required to treat a model comparison as meaningful.
@@
 
-Here we sought to examine whether actual psychiatric patients were equally or more likely to fail infrequency items than healthy controls in settings similar to those experienced by online participants (i.e., completing an experiment online, on a computer in one's home or otherwise chosen environment).
-Although the small sample precludes any definitive conclusion, it is noteworthy that the model least consistent with the data was the one where psychiatric patients were more likely to fail infrequency-item attention checks.
+Here we sought to examine whether actual MDD patients were equally or more likely to fail infrequency items than healthy controls in settings similar to those experienced by online participants (i.e., completing an experiment online, on a computer in one's home or otherwise chosen environment).
+Although the small sample precludes any definitive conclusion, it is noteworthy that the model least consistent with the data was the one where MDD patients were more likely to fail infrequency-item attention checks.
 Indeed, a model in which healthy controls failed attention checks at a greater rate than patients was credibly preferred to the alternative.

### 2023-06-21 manuscripts/main.tex
fix typo

@@
 The demographics of the sample split by labor market is provided in Table S1.
-Notably, the participants recruited from MTurk were older (mean difference = 7.7 yrs), two-tailed, two-sample $t$-test: $t(384)=6.567$, $p<0.001$, $d=0.669$, 95\% CI = [5.4, 10.0]) and comprised of fewer women (two-tailed, two-sample proportions test: $z(384)=2.529$, $p=0.011$, $h=0.258$, 95\% CI = [0.030, 0.228]).
+Notably, the participants recruited from MTurk were older (mean difference = 7.7 yrs, two-tailed, two-sample $t$-test: $t(384)=6.567$, $p<0.001$, $d=0.669$, 95\% CI = [5.4, 10.0]) and comprised of fewer women (two-tailed, two-sample proportions test: $z(384)=2.529$, $p=0.011$, $h=0.258$, 95\% CI = [0.030, 0.228]).
 

### 2023-06-21 manuscripts/main.tex
minor fixes

@@
 
-% \subsection*{Screening for C/IE responding is common for task behavior but not for self-report surveys}
 \subsection*{Narrative review of task and self-report screening practices}
@@
 Of these, just over half relied on a single screening method, with considerable heterogeneity in behavior screening methods across studies.
-Most common (46\% of all studies) was identifying participants whose performance was statistically indistinguishable from chance-level on some measure of accuracy.
-Almost as common (38\%) was screening based on low response variability (i.e., excluding participants who predominantly responded in the same fashion across trials, such as using only a single response key).
+Most common (46\% of these studies) was identifying participants whose performance was statistically indistinguishable from chance-level on some measure of accuracy.
+Almost as common (38\% of these studies) was screening based on low response variability (i.e., excluding participants who predominantly responded in the same fashion across trials, such as using only a single response key).
 
@@
 
-% \subsection*{Careless participants appear symptomatic when the overall level of symptom endorsement is low}
 \subsection*{C/IE participants appear psychiatric when symptoms are rare}
@@
 
-% \subsection*{Low correspondence between task and self-report measures of C/IE responding}
 \subsection*{Low agreement between task and self-report screening measures}
@@
 
-% \subsection*{Spurious symptom-behavior correlations produced by C/IE responding}
 \subsection*{C/IE responding yields spurious symptom-behavior correlations}
@@
 
-% \subsection*{Pattern of results generalizes to alternative tasks, self-report measures, and quality assurance protocols}
 \subsection*{Findings replicate in second study with alternative measures}
@@
 
-% \subsection*{Individuals with and without diagnosed psychiatric disorders fail attention checks at similar rates}
 \subsection*{Patients with depression do not fail attention checks more often}
